### 2014-10-09 Notes/cvpr2014AuthorKit/latex/egpaper_final.tex
First commit to the umich git repository.

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{times}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\begin{document}

%%%%%%%%% TITLE
\title{\LaTeX\ Author Guidelines for CVPR Proceedings}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
   The ABSTRACT is to be in fully-justified italicized text, at the top
   of the left-hand column, below the author and affiliation
   information. Use the word ``Abstract'' as the title, in 12-point
   Times, boldface type, centered relative to the column, initially
   capitalized. The abstract is to be in 10-point, single-spaced type.
   Leave two blank lines after the Abstract, then begin the main text.
   Look at previous CVPR abstracts to get a feel for style and length.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

Please follow the steps outlined below when submitting your manuscript to
the IEEE Computer Society Press.  This style guide now has several
important modifications (for example, you are no longer warned against the
use of sticky tape to attach your artwork to the paper), so all authors
should read this new version.

%-------------------------------------------------------------------------
\subsection{Language}

All manuscripts must be in English.

\subsection{Dual submission}

By submitting a manuscript to CVPR, the authors guarantee that it has 
not been previously published or accepted for publication in substantially 
similar form in an archival peer-reviewed forum. Furthermore, no paper which 
contains significant overlap with the contributions of this paper is neither 
under review at the moment of submission nor will be submitted during the 
CVPR 2014 review period to {\bf any of the following}: another conference,
a workshop, or a journal. The authors also attest that they did not submit
substantially similar submissions to CVPR 2014. {\bf Violation of any of
these conditions will lead to rejection.} If you are not sure about the
extent of overlap, you may upload a copy of the paper in question as
supplementary material. Note that a Technical Report (departmental, 
arXiv.org, etc.) that is put up without any form of direct peer-review is 
{\bf NOT} considered a publication. Likewise, mention of the work under 
review in a presentation is {\bf NOT} considered a violation.

If there are papers that may appear to the reviewers
to violate this condition, then it is your responsibility to: (1)~cite
these papers (preserving anonymity as described in Section 1.6 below),
(2)~argue in the body of your paper why your CVPR paper is non-trivially
different from these concurrent submissions, and (3)~include anonymized
versions of those papers in the supplemental material.

\subsection{Paper length}
CVPR papers may be between 6 pages and 8 pages, with a \$100 per page added
fee.  Overlength papers will simply not be reviewed.  This includes papers
where the margins and formatting are deemed to have been significantly
altered from those laid down by this style guide.  Note that this
\LaTeX\ guide already sets figure captions and references in a smaller font.
The reason such papers will not be reviewed is that there is no provision for
supervised revisions of manuscripts.  The reviewing process cannot determine
the suitability of the paper for presentation in eight pages if it is
reviewed in eleven.  If you submit 8 for review expect to pay the added page
charges for them.

%-------------------------------------------------------------------------
\subsection{The ruler}
The \LaTeX\ style defines a printed ruler which should be present in the
version submitted for review.  The ruler is provided in order that
reviewers may comment on particular lines in the paper without
circumlocution.  If you are preparing a document using a non-\LaTeX\
document preparation system, please arrange for an equivalent ruler to
appear on the final output pages.  The presence or absence of the ruler
should not change the appearance of any other content on the page.  The
camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
the \verb'\cvprfinalcopy' command in the document preamble.)  Reviewers:
note that the ruler measurements do not align well with lines in the paper
--- this turns out to be very difficult to do well when the paper contains
many figures and equations, and, when done, looks ugly.  Just use fractional
references (e.g.\ this line is $095.5$), although in most cases one would
expect that the approximate location will be adequate.

\subsection{Mathematics}

Please number all of your sections and displayed equations.  It is
important for readers to be able to refer to any particular equation.  Just
because you didn't refer to it in the text doesn't mean some future reader
might not need to refer to it.  It is cumbersome to have to use
circumlocutions like ``the equation second from the top of page 3 column
1''.  (Note that the ruler will not be present in the final copy, so is not
an alternative to equation numbers).  All authors will benefit from reading
Mermin's description of how to write mathematics:
\url{http://www.pamitc.org/documents/mermin.pdf}.

\subsection{Blind review}

Many authors misunderstand the concept of anonymizing for blind
review.  Blind review does not mean that one must remove
citations to one's own work---in fact it is often impossible to
review a paper unless the previous citations are known and
available.

Blind review means that you do not use the words ``my'' or ``our''
when citing previous work.  That is all.  (But see below for
techreports)

Saying ``this builds on the work of Lucy Smith [1]'' does not say
that you are Lucy Smith, it says that you are building on her
work.  If you are Smith and Jones, do not say ``as we show in
[7]'', say ``as Smith and Jones show in [7]'' and at the end of the
paper, include reference 7 as you would any other cited work.

An example of a bad paper just asking to be rejected:
\begin{quote}
\begin{center}
    An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of our
   previous paper [1], and show it to be inferior to all
   previously known methods.  Why the previous paper was
   accepted without this analysis is beyond me.

   [1] Removed for blind review
\end{quote}

An example of an acceptable paper:

\begin{quote}
\begin{center}
     An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of the
   paper of Smith \etal [1], and show it to be inferior to
   all previously known methods.  Why the previous paper
   was accepted without this analysis is beyond me.

   [1] Smith, L and Jones, C. ``The frobnicatable foo
   filter, a fundamental contribution to human knowledge''.
   Nature 381(12), 1-213.
\end{quote}

If you are making a submission to another conference at the same time,
which covers similar or overlapping material, you may need to refer to that
submission in order to explain the differences, just as you would if you
had previously published related work.  In such cases, include the
anonymized parallel submission~\cite{Authors14} as additional material and
cite it as
\begin{quote}
[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324,
Supplied as additional material {\tt fg324.pdf}.
\end{quote}

Finally, you may feel you need to tell the reader that more details can be
found elsewhere, and refer them to a technical report.  For conference
submissions, the paper must stand on its own, and not {\em require} the
reviewer to go to a techreport for further details.  Thus, you may say in
the body of the paper ``further details may be found
in~\cite{Authors14b}''.  Then submit the techreport as additional material.
Again, you may not assume the reviewers will read this material.

Sometimes your paper is about a problem which you tested using a tool which
is widely known to be restricted to a single institution.  For example,
let's say it's 1969, you have solved a key problem on the Apollo lander,
and you believe that the CVPR70 audience would like to hear about your
solution.  The work is a development of your celebrated 1968 paper entitled
``Zero-g frobnication: How being the only people in the world with access to
the Apollo lander source code makes us a wow at parties'', by Zeus \etal.

You can handle this paper like any other.  Don't write ``We show how to
improve our previous work [Anonymous, 1968].  This time we tested the
algorithm on a lunar lander [name of lander removed for blind review]''.
That would be silly, and would immediately identify the authors. Instead
write the following:
\begin{quotation}
\noindent
   We describe a system for zero-g frobnication.  This
   system is new because it handles the following cases:
   A, B.  Previous systems [Zeus et al. 1968] didn't
   handle case B properly.  Ours handles it by including
   a foo term in the bar integral.

   ...

   The proposed system was integrated with the Apollo
   lunar lander, and went all the way to the moon, don't
   you know.  It displayed the following behaviours
   which show how well we solved cases A and B: ...
\end{quotation}
As you can see, the above text follows standard scientific convention,
reads better than the first version, and does not explicitly name you as
the authors.  A reviewer might think it likely that the new paper was
written by Zeus \etal, but cannot make any decision based on that guess.
He or she would have to be sure that no other authors could have been
contracted to solve problem B.

FAQ: Are acknowledgements OK?  No.  Leave them for the final copy.

\begin{figure}[t]
\begin{center}
\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
\end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

\subsection{Miscellaneous}

\noindent
Compare the following:\\
\begin{tabular}{ll}
 \verb'$conf_a$' &  $conf_a$ \\
 \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
\end{tabular}\\
See The \TeX book, p165.

The space after \eg, meaning ``for example'', should not be a
sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
\verb'\eg' macro takes care of this.

When citing a multi-author paper, you may save space by using ``et alia'',
shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
However, use it only when there are three or more authors.  Thus, the
following is correct: ``
   Frobnication has been trendy lately.
   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''

This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
because reference~\cite{Alpher03} has just two authors.  If you use the
\verb'\etal' macro provided, then you need not worry about double periods
when used at the end of a sentence as in Alpher \etal.

For this citation style, keep multiple citations in numerical (not
chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
\cite{Alpher02,Alpher03,Authors14}.

\begin{figure*}
\begin{center}
\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
\end{center}
   \caption{Example of a short caption, which should be centered.}
\label{fig:short}
\end{figure*}

%------------------------------------------------------------------------
\section{Formatting your paper}

All text must be in a two-column format. The total allowable width of the
text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
$\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
first page) should begin 1.0 inch (2.54 cm) from the top edge of the
page. The second and following pages should begin 1.0 inch (2.54 cm) from
the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
page.

%-------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must be kept
within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
high.
Page numbers should be in footer with page numbers, centered and .75
inches from the bottom of the page and make it start at the correct page
number rather than the 4321 in the example.  To do this fine the line (around
line 23)  
\begin{verbatim}
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\end{verbatim}
where the number 4321 is your assigned starting page.

Make sure the first page is numbered by commenting out the first page being
empty on line 46
\begin{verbatim}
%\thispagestyle{empty}
\end{verbatim}

%-------------------------------------------------------------------------
\subsection{Type-style and fonts}

Wherever Times is specified, Times Roman may also be used. If neither is
available on your word processor, please use the font closest in
appearance to Times to which you have access.

MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
the first page. The title should be in Times 14-point, boldface type.
Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
adverbs; do not capitalize articles, coordinate conjunctions, or
prepositions (unless the title begins with such a word). Leave two blank
lines after the title.

AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
and printed in Times 12-point, non-boldface type. This information is to
be followed by two blank lines.

The ABSTRACT and MAIN TEXT are to be in a two-column format.

MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
inch or 0.422 cm). Make sure your text is fully justified---that is,
flush left and flush right. Please do not place any additional blank
lines between paragraphs.

Figure and table captions should be 9-point Roman type as in
Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.

\noindent Callouts should be 9-point Helvetica, non-boldface type.
Initially capitalize only the first word of section titles and first-,
second-, and third-order headings.

FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
should be Times 12-point boldface, initially capitalized, flush left,
with one blank line before, and one blank line after.

SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
should be Times 11-point boldface, initially capitalized, flush left,
with one blank line before, and one after. If you require a third-order
heading (we discourage it), use 10-point Times, boldface, initially
capitalized, flush left, preceded by one blank line, followed by a period
and your text on the same line.

%-------------------------------------------------------------------------
\subsection{Footnotes}

Please use footnotes\footnote {This is what a footnote looks like.  It
often distracts the reader from the main flow of the argument.} sparingly.
Indeed, try to avoid footnotes altogether and include necessary peripheral
observations in
the text (within parentheses, if you prefer, as in this sentence).  If you
wish to use a footnote, place it at the bottom of the column on the page on
which it is referenced. Use Times 8-point type, single-spaced.

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times,
single-spaced, at the end of your paper. When referenced in the text,
enclose the citation number in square brackets, for
example~\cite{Authors14}.  Where appropriate, include the name(s) of
editors of referenced books.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Method & Frobnability \\
\hline\hline
Theirs & Frumpy \\
Yours & Frobbly \\
Ours & Makes one's heart Frob\\
\hline
\end{tabular}
\end{center}
\caption{Results.   Ours is better.}
\end{table}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.  Please ensure that any point you wish to
make is resolvable in a printed copy of the paper.  Resize fonts in figures
to match the font in the body text, and choose line widths which render
effectively in print.  Many readers (and reviewers), even of an electronic
copy, will choose to print your paper in order to read it.  You cannot
insist that they do otherwise, and therefore must not assume that they can
zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use
\verb+\includegraphics+, and to specify the  figure width as a multiple of
the line width as in the example below
{\small\begin{verbatim}
   \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.eps}
\end{verbatim}
}

%-------------------------------------------------------------------------
\subsection{Color}

Color is valuable, and will be visible to readers of the electronic copy.
However ensure that, when printed on a monochrome printer, no important
information is lost by the conversion to grayscale.

%------------------------------------------------------------------------
\section{Final copy}

You must include your signed IEEE copyright release form when you submit
your finished paper. We MUST have this form before your paper can be
published in the proceedings.

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2014-10-09 Notes/densecrf.tex
First commit to the umich git repository.

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{verbatim} % for comment environment
% \usepackage{soul} % for \hl highlighting
% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
%\setcounter{page}{4321}
%\DeclareMathSymbol{\Tangent}
\begin{document}
\title{Unmentioned approximations in Dense CRF}
\author{Vikas Dhiman\\
{\tt\small vdhiman@nec-labs.com}
}
\maketitle
\begin{abstract}
  Fully connected CRF like those presented in \cite{krahenbuhl2012efficient}
  use some approximations that are neither mentioned nor justified in the
  paper.
\end{abstract}

% What is a random field? A graphical representation defining the probabilistic
% interdependencies among different random variables. When you are modeling
% something as dense CRF, you are basically claiming that every variable is
% dependent on each other.
% 
% The pairwise Gibbs energy claimed in 
% \cite[Eq(1)]{krahenbuhl2012efficient} is not a Gibbs energy because it is not defined
% on cliques rather than pair of variables. The term used \emph{fully connected
% pairwise CRF model} is itself contradictory because the CRF if fully connected
% cannot be pairwise.
% 
% As far as I can understand the authors have not presented or referred to any
% results as to why the \emph{dense CRF} can be factorized into pairwise
% energies.
% 
% If higher order graphical models were representable as pairwise energies,
% there would have been no problem in inferring on them.
\section{Dense CRF}

% \subsection{Correct factorization of a dense CRF}
By Hammersley Clifford theorem, there exists a factorization of a graphical
model such that total probability of any part of the graph can be written as
product of positive functions of its cliques
\cite[145]{grimmett2010probability}. Writing the factorization domain, the
energy of dense CRF should be 
\begin{multline}
  E(\mathbf{x}) = \sum_i \psi_u(x_i) + \sum_{i < j} \psi_p(x_i, x_j)\\
  + \sum_{i < j < k} \psi_t(x_i, x_j, x_k)
  + \dots
  + \psi(\mathbf{x})
\end{multline}

This does not help because we get a term $\psi_{\mathbf{x}}$ that is as big as
$E(\mathbf{x})$. This shows that dense CRFs are anti-thesis of CRF which are
meant to define sparse interdependencies between variables so that probability
over large number of random variables can be factorized into smaller
tractable problems using domain knowledge. Without using factorizable CRF, the
authors have not used any of the useful theorems that have been established in
the field of graphical models.

However, the authors in \cite{krahenbuhl2012efficient} invent a new term
called \emph{fully connected pairwise CRF model} and without any explanation 
introduce the following energy function.

\begin{align}
  E(\mathbf{x}) = \sum_i \psi_u(x_i) + \sum_{i < j} \psi_p(x_i, x_j)
\end{align}

Clearly this is a linear approximation of energy function. The energy function
is assumed to weighted sum of pairwise energies over different variable
states. How well the energy function can be approximated depends on the energy
function itself. For comparison we present \ref{fig:compare} a 2D Gaussian compared with an
approximation of Gaussian that is generated by sum of two 1D Gaussians.
\begin{figure}
  \includegraphics[width=0.5\columnwidth]{graphics/gaussian2D.png}%
  \includegraphics[width=0.5\columnwidth]{graphics/gaussianLinear1D.png}%
  \caption{Comparison of a 2D Gaussian (left) compared with an
    approximation of Gaussian (right) that is generated by sum of two 1D
  Gaussians.}
  \label{fig:compare}
\end{figure}

Intuitively, the approximation of a 2D Gaussian using sum of 1D Gaussians is
like approximating 2D Euclidean distance by using linear combination of 1D
distance only which is commonly known as L1 or manhattan distance. Note that
the deviation of approximation is minimal around the center of the Gaussian
and around the axes and becomes more prominent as the distance increases.

There are a few open questions here:
\begin{enumerate}
  \item How good is this approximation?  What are the error bounds of the
approximation? Can I check an energy function for error bounds?
\item Is this better than the sparse CRFs? (at least in gaussian kernel pairwise
energies)
\item What lessons can we take from empirical success of dense CRFs and how can
we make sparse CRFs better or vice versa?

\end{enumerate}

% In the dense CRF paper, the authors constrain the energy over the graph to be
% only pairwise energy. The pairwise energies are modeled in the paper as
% Gaussian distance between the feature vectors and positions of the points.
% However, if we consider higher order terms the energies could have been more
% complex

{\small
\bibliographystyle{ieee}
\bibliography{densecrf}
}

\end{document}

### 2014-10-09 Notes/model.tex
First commit to the umich git repository.

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{verbatim} % for comment environment
% \usepackage{soul} % for \hl highlighting
% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
%\setcounter{page}{4321}
%\DeclareMathSymbol{\Tangent}
\DeclareMathOperator{\sech}{sech}
\DeclareMathOperator{\poly}{poly}

\begin{document}
\title{Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.}
\author{Vikas Dhiman\\
{\tt\small vdhiman@nec-labs.com}
\and
Manmohan Chandraker\\
{\tt\small manu@nec-labs.com}
}
\maketitle

%%%%%%%%% ABSTRACT
\begin{abstract}
  The long term goal of this project is to identify and represent commonly 
  occurring potentially dangerous road situations where driver can be warned 
  about the situations. Such kind of driver assistance requires understanding
  the state of various road scene elements. We broadly categorize the elements
  in the scene as traffic participants (TP) and as other "scene elements" (like
  lanes, intersections etc). 
\end{abstract}

\section{Introduction}
  NEC has already developed a monocular camera based structure from motion
  system which is accurate for requirements of road scene understanding. So we
  assume that egomotion is given as an observed variable in our graphical
  model. And we have following features to our disposal for estimating the 3D
  poses (position + orientation) of traffic participants:
  \begin{description}
    \item[Ground plane] We assume that all the traffic participants lie on a common ground
      plane. This is not particularly true for the cars that are parked off the
      road. However, for autonomous driver assistance applications we can
      ignore those cars.
    \item[Detections] We assume that 2D car detections are available with tracking informations.
    \item[Point tracks] We assume that 2D point tracks are available.
    \item[GPS and Map information] We assume that GPS information is available
      and we use openstreetmaps.org for pulling out local map for the current
      car's position.
    \item[Lane Information] We assume the lane detection works well and lane
      information is available.
    \item[Size prior] The distribution of size of cars follows gaussian distribution.
    \item[Collision] A reasonable output of the system donot has any overlapping cars.
  \end{description}

\section{Notation}
% 3D pose of the cars and ego motion
\newcommand{\pos}[2]{\mathbf{p}^{(#1)}(#2)}
\newcommand{\ori}[2]{\mathbf{\omega}^{(#1)}(#2)}
\newcommand{\state}[2]{\mathbf{s}^{#1}(#2)}

% ego pose
\newcommand{\egop}[1][t]{\pos{c}{#1}}
\newcommand{\egoo}[1][t]{\ori{c}{#1}}
\newcommand{\egos}[1][t]{\state{c}{#1}}

% relative pose between camera and car $i$
\newcommand{\relp}[2]{\Omega^{#1}(#2)}
\newcommand{\relpz}[2]{\Omega_z^{#1}(#2)}

% 3D tracks on car $i$ in its own coordinate frame
\newcommand{\tracklets}{\mathbf{X}^{(i)}_o}
\newcommand{\tracklet}[1]{\mathbf{x}^{(i)}_{#1}}
% track projections on camera
\newcommand{\trackp}[1]{\mathbf{u}^{(i)}(#1)}
\newcommand{\trackpj}[1]{\mathbf{u}_j(#1)}
% Unclassified track point projected on camera
\newcommand{\ucTrackp}{\mathbf{u}(t)}

% dimensions of car $i$
\newcommand{\dimsn}[1]{\mathbf{B}^{#1}}
\newcommand{\expDimsn}{\hat{\mathbf{B}}}

% projection function
\newcommand{\projectionOf}[1]{\pi_{\relp{i}{t}}(#1)}
\newcommand{\centerProj}{\bar{\pi}_{\relp{i}{t}}(\dimsn{i})}
\newcommand{\cornerProj}[1]{\pi^{#1}_{\relp{i}{t}}(\dimsn{i})}
\newcommand{\triangleProj}[1]{\triangle^{#1}_{\relp{i}{t}}(\dimsn{i})}

% bounding box corners on image
\newcommand{\bb}[1]{\mathbf{d}^{#1}(t)}

\newcommand{\Energy}[1]{\mathcal{E}^{it}_{\text{#1}}}
\newcommand{\pEnergy}[1]{\mathcal{E}^{ijt}_{\text{#1}}}
% Weighted energy
\newcommand{\WEnergy}[1]{\lambda_{\text{#1}}\Energy{#1}}
\newcommand{\EnergyCol}{\mathcal{E}^{ijt}_{\text{col}}}
\newcommand{\WEnergyCol}{\lambda_{\text{col}}\EnergyCol}

\newcommand{\occFreeProj}[1]{\Pi_{\relp{i}{t}}(#1)}

\begin{table}[h]
  \begin{tabular}{|l|l|}
    \hline
    Symbol & Meaning \\
    \hline
    $\pos{i}{t}$ & Position of $i$th car at time $t$\\
    $\ori{i}{t}$ & Orientation of $i$th car at time $t$\\
     $\dimsn{i}$ & 3D bounding box of the car (dimensions)\\
    $\state{i}{t}$ & State of car $=\{\pos{i}{t}, \ori{i}{t}, \dimsn{i}\}$\\
    $\egop$ & Position of camera at time $t$\\
    $\egoo$ & Orientation of camera at time $t$\\
    $\relp{i}{t}$ & Relative car pose w.r.t. camera \\
    $\tracklets$ & 3D points tracked on car $i$ in its own frame\\
    $\trackp{t}$ & Projection of $\tracklets$ in camera\\
    $\projectionOf{.}$ & Projection function for pose $\relp{i}{t}$\\
    $\bb{i}$ & 2D bounding box of the car in image\\
    \hline
  \end{tabular}
\end{table}

%%%%%%%%% BODY TEXT
\section{The Model}

The objective is to find the most likely traffic participant state given various
evidences $\mathbb{E} = \{\{\trackp{t}\}, \{\bb{i}\}, \text{lane det.}, \text{map},
\text{GPS}\}$.

Mathematically, find:
\begin{align}
  \{\state{i}{t}\}^* &= \arg \max P(\{\state{i}{t}\} | \mathbb{E})
\end{align}

Bayes rule
\begin{align}
  P(\{\state{i}{t}\} | \mathbb{E}) &=
  \frac{1}{Z}P( \mathbb{E} | \{\state{i}{t}\})P(\{\state{i}{t}\})
\end{align}

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{graphics/graphicalModelFrom61ConstVars.pdf}
  \caption{Graphical model. The six numbered black circles represent the
    unknown state variables of each car. All other nodes in the graphical model
    are assumed
    observed variables. Consider each energy in the model one by one. (1)
    Bounding box energy: The bounding box energy without occlusion modeling is
    a unary term, but with occlusion it becomes a higher order term that
    affects the state of occluder as well. In this graphical model we assume
    that the scene is being observed from left to right, hence "2" occludes "6"
    and "5" and "5" occludes "1". The bounding box detection is represented by
  $\mathbf{d}_{bb}^i(t)$ and the statistical dependencies are represented by
  red lines. (2) Point tracks ($\Energy{track}$): Since occlusion is also
  included in modeling point tracks energy we have similar interdependencies
  for point tracks energy. The available point tracks are modeled by
  $\mathbf{u}(t)$. (3) Collision ($\Energy{coll}$) : The collision energy
  mathematically is a dense graph between all the TP but here we represent
  collision among only those TP that are near enough to have a significant
collision energy. (4) Orientation from detection ($\Energy{ori}$) (5) Orientation from lane (and map) information ($\Energy{lane}$)}
  \label{fig:graphmodel}
\end{figure}

Assume conditional independence according to graphical model in
\ref{fig:graphmodel}.

\begin{multline}
  P(\{\state{i}{t}\} | \mathbb{E}) =
  \frac{1}{Z}
  \prod_{t=s_i}^{e_i}\prod_{i,j: i \ne j}(P(\state{i}{t}, \state{j}{t}))\\
%
  \prod_{i=1}^{N}
  \prod_{t=s_i}^{e_i}
  P(\bb{i} | \state{i}{t})
  P(\trackp{t} | \state{i}{t})\\
  P(\state{i}{t} | L_m(t))
  P(\state{i}{t} | \state{i}{t-1})
  P(\state{i}{t})
\end{multline}

We can formulate similar objective function in negative log domain:
\footnote{TODO:Resolve inconsistency in summation absorption in energy terms.}
\begin{multline}
  -\log{P(\{\state{i}{t}\} | \mathbb{E})} = 
  Z' + \sum_{i,j:i\ne j} \sum_{t=s_i}^{e_i}  \WEnergyCol \\
  + \sum_{i=1}^N \sum_{t=s_i}^{e_i}
    \WEnergy{box}
  + \WEnergy{track}\\
  + \WEnergy{lane}
  + \WEnergy{dyn}
  + \WEnergy{prior}
\end{multline}

\subsection{Collision energy}

Bhattacharya coefficient $\int_a^b\sqrt{p(x)q(x)}dx$ is a measure of similarity of two
distributions $p(x)$ and $q(x)$. If we represent traffic participants as
gaussians in BEV, then similarity is a measure of collision. Exactly
overlapping distribution results in coefficient as 1. The analytical form of
Bhattacharya coefficient has been taken from
\url{http://like.silk.to/studymemo/PropertiesOfMultivariateGaussianFunction.pdf}

\begin{align}
  \label{eq:collisionEnergyHellingerDistance}
  \EnergyCol &=
  \frac{|\Sigma_i|^\frac{1}{4}|\Sigma_j|^\frac{1}{4}}
  {|P|^\frac{1}{2}}
  e^{-\frac{1}{8}
    \left(\pos{i}{t} - \pos{j}{t}\right)^\top
    P^{-1}
    \left(\pos{i}{t} - \pos{j}{t}\right)
    }
\end{align}
where 
\begin{align}
  P &= \frac{1}{2}\Sigma_i + \frac{1}{2}\Sigma_j\\
\Sigma_i^{-1} &= R^\top_{\ori{i}{t}} \begin{bmatrix} 2/l^i & 0 \\ 0 & 2/w^i \end{bmatrix}
R_{\ori{i}{t}}
\end{align}

\begin{comment}
  \subsection{Bounding box energy}
  \label{sec:totalBBoxEnergy}
  With abuse of notation we represent the four sides of hypothesized bounding
  box by $\projectionOf{\dimsn{i}}$ and detected bounding box by $\bb{i}$.
  Suppose the bounding box $i$ is occluded by bounding box $i$ then the
  bounding box energy becomes a pairwise term.

  \begin{multline}
    \pEnergy{occ}(\relp{i}{t}, \dimsn{i}, \relp{j}{t}, \dimsn{j}) = \\
    \sum_s \rho^{ijs}(t)\projectionOf{\dimsn{i}}_s - \bb{i}_s
               %\sum_{i=1}^N \sum_{t=s_i}^{e_i}
    %\sum_kp_{ik}^{\text{track}}(\projectionOf{\dimsn{i}} - \bb{k})^\top \pmb{\rho}(i,j,t)
  \end{multline}
  where $\rho^{ijs}(t)$ is the visibility fraction of the side $s$ of the
  bounding box. We need to compute visibility fraction we need to compute the
  occlusion mask which is explained in next few sections.

  \subsubsection{Visible faces from bounding boxes}

  \begin{figure}[h]
    \includegraphics[width=\columnwidth]{graphics/maxFacesVisible.pdf}
    \caption{Only three faces can be visible out of six faces of a bounding
    box.}
  \end{figure}

  \newcommand{\minx}{x_{\text{min}}}
  \newcommand{\miny}{y_{\text{min}}}
  \newcommand{\maxx}{x_{\text{max}}}
  \newcommand{\maxy}{y_{\text{max}}}
  \newcommand{\frontface}{F^i_\text{FF}(t)}
  Each bounding box has 6 faces of which only 3 can be visible.
  Sort the vertices in increasing order of depth. The closest vertex has three
  neighboring faces. All the faces that are visible must be a subset of these
  three. Use first three vertices to
  define the front face (say $\frontface$). Also identify the four 3D points
  that correspond to min/max in x and y direction in the image. If all min-max 4
  points are same as vertices of $\frontface$, then we have only one plane
  visible. If $\{\minx, \maxx\} \not\subset \frontface \land \{\miny, \maxy\}
  \not\subset \frontface$ then we have 3 planes visible. Otherwise we have just
  two planes visible. Let number of planes visible be $n_F$.

  \begin{align}
    n_F &= \begin{cases}
    1 & \text{if }\{\minx, \maxx, \miny, \maxy\} =
    \frontface\\
    2 & \text{else if }\{x_{\text{min}}, x_{\text{max}}\} \subset \frontface \lor
    \{y_{\text{min}}, y_{\text{max}}\} \subset \frontface
    \\
    3 & \text{else if }\{x_{\text{min}}, x_{\text{max}}\} \not\subset \frontface \land
    \{y_{\text{min}}, y_{\text{max}}\} \not\subset \frontface
    \end{cases}
    \label{eq:nfaces}
  \end{align}

  First vertex restrict possible visible faces to three faces. If $n_F = 3$,
  then all three of these faces are visible. If $n_F = 2$, use second closest
  vertex to restrict visible faces to just two. If $n_F = 3$, then front face 
  $\frontface$ is the only visible face.
\end{comment}

\newcommand{\occ}[1]{o({#1})}
\newcommand{\face}{F^i_k(t)}
\begin{comment}
  \subsubsection{Occlusion mask}
  % Initialize empty mask polygon $\occ{0}$ at depth $d=0$.
  % \begin{itemize}
  %   \item Sort all cars in increasing order of depth
  %   \item for each car $i$ in the sorted list
  %     \begin{itemize}
  %       \item Update mask polygon: \\
  %         $\occ{\relpz{i}{t}} = \occ{d} \cup \projectionOf{\dimsn{i}}$
  %       \item $d = \relpz{i}{t}$
  %     \end{itemize}
  % \end{itemize}

  % Sort all planes in increasing order of depth.  This yields a cumulative
  % occlusion mask function
  Occlusion mask is a function that takes the relative depth $d$ from the car
  camera and returns a binary mask that represents occlusions untill that depth.
  Near to the camera occlusion mask is all empty (all zeros) and more occlusions
  get added to the mask with distance.

  \begin{align}
    \occ{d} &= \begin{cases}
    \phi & \text{if } 0 < d \le \relpz{1}{t}\\
    \cup_{i=1}^j \projectionOf{F^i} & \text{if } \relpz{1}{t} < d \le \relpz{j+1}{t}
    \end{cases}
    \label{eq:occlusionmask}
  \end{align}

  where $\relpz{j}{t}$ is the depth of the $j$th traffic participant when sorted
  by increasing depth.

  \subsubsection{Algorithm to get faces based occlusion mask}
  \label{sec:occlusionMaskFromOptVector}

  This is an algorithm to compute occlusion mask Eq.\eqref{eq:occlusionmask}. We
  represent the occlusion mask as a set of polygons.

  Initialize empty mask polygon $\occ{0}$ at depth $d=0$.
  \begin{enumerate}
    \item Collect visible faces using Eq.\eqref{eq:nfaces} for all cars
    %\item for each face get its closest and farthest vertex to the camera.
    \item Create a sorted list of faces
    % \item Create a sorted binary tree of
    %   faces indexed by closed vertices.
    \item Loop over list of sorted visible faces
      \begin{enumerate}
        \item Get the face(s) $\{\face\}$ closer to camera than this face
        \item Add the faces to mask polygon (if not already added): \\
          $\occ{\relpz{i}{t}} = \occ{d} \cup \projectionOf{\face}$
        \item $d = \relpz{i}{t}$
      \end{enumerate}
  \end{enumerate}

  To get the occlusion mask for a face use the farthest vertex of the face to
  query $\occ{.}$.

  \subsubsection{Visibility fraction of a side}
  Let the center of the projected hypothesized bounding box be $\centerProj$ and
  the four corners be $\{\cornerProj{k}\}_{k=1}^{4}$ . Each side and the center
  of the bounding box form a triangle, for example $\triangleProj{1,2} =
  \{\cornerProj{1}, \cornerProj{2}, \centerProj\}$. We take the visibility of
  this triangle as a visibility of the side $s = (1,2)$. Hence the visibility
  fraction of side is given by
  \begin{align}
    \rho^{ijs}(t) = \frac{\|\triangleProj{s} \setminus \occ{\relpz{i}{t}}\|}
                         {\|\triangleProj{s}\|}
     \label{eq:bboxEnergyFromOccMask}
  \end{align}
\end{comment}

\begin{comment}
  \subsection{Occlusion free projection}
  Occlusion free projection can be obtained by applying the precomputed occlusion
  mask to the face projection.
  \begin{align}
    \occFreeProj{\face} &= \projectionOf{\face} \setminus
    \occ{\relpz{i}{t}}
  \end{align}

  \subsection{Perspective-visibility fraction}

  Apart from occlusion, we want to account for the perspective affects. When an 
  objects perspective projection is too small, detection and all related
  evidences deteriorate. One way of this is to find out the projection ratio. In
  fact, we can consolidate projection ratio and occlusion ratio in one term if
  we consider the projection of 3D bounding box planes instead of the entire
  bounding box.

  \begin{align}
    \rho^i_t &= \sum_{k=1}^{n_F}\frac{\relpz{i}{t}^2\|\occFreeProj{F^i_k(t)}\|}{f^2\|F^i_k(t)\|}
  \end{align}

  where $\occFreeProj{.}$ again means occlusion free projection. $f$ is the
  focal length of the camera so that $\frac{f^2}{\relpz{i}{t}^2}\|F^i_k(t)\|$ is
  the area of projected plane if there were no perspective effects.
\end{comment}

\subsection{Continous Point tracks energy with occlusion}
\label{sec:totalContPtTracksEnergy}
We want continuous modeling of occlusion. We model occlusion as a opacity
term. Based on the dimensions $\dimsn{i}$, we can
compute the covariance matrix $\Sigma_i$ as shown in Sec. 
\ref{sec:sigmacomputation}

So far we have modeled our point tracks energy in a non-smooth way:
\newcommand{\invProjectionOf}[1]{\pi^{-1}_{\relp{i}{t-1}}(#1)}
\begin{multline}
  \Energy{traci}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \\
    \sum_{i=1}^{N} 
    %\sum_{t = s_i}^{e_i}
    \sum_{j = 1}^{M}
    \int_1^\infty a_j^i(\lambda)\|\trackpj{t} - \projectionOf{\invProjectionOf{\trackpj{t-1}}}\|^2 d\lambda
\end{multline}

The tricky part here is inverse projection $\invProjectionOf{.}$ . When we
project an image point back to 3D we get a ray $\lambda K^{-1}\trackpj{t-1}$
which is ambiguous up to a scale factor $\lambda$. Using our hypothesized 3D
layout of the scene we can estimate this scale factor, we
can compute a distribution over the $\lambda$. 
\subsubsection{Occupancy function}
Assuming occupancy to be a
probability distribution over 3D space. For each traffic participant the
occupancy is modeled as a logistic function 
\newcommand{\occf}{f^i_{occ}(\mathbf{x})}
\begin{align}
   \occf = L(\mathbf{x}; \pos{i}{t}, \Sigma_i)
\end{align}
where $L(.)$ is the logistic function defined by
\begin{align}
  L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i) = \frac{1}{
    1 + e^{-k(1 - d(\mathbf{x},\pos{i}{t-1}))}
    }
\end{align}
where $d(\mathbf{x},\pos{i}{t-1}) =
(\mathbf{x}-\pos{i}{t-1})^\top\Sigma_i(\mathbf{x}-\pos{i}{t-1})$ and $k =
10\ln{49}$. $k$ is chosen such that $L(.) = 0.98$ when $d(.) =
0.9$

We model the probability of a point being projected to a camera is dependent
up two factors, (1) reflection and (2) transmission through intermediate
space. 
\subsubsection{Reflection probability}
For lambertian reflection we replace the surface normal with the
gradient of occupancy.
\begin{align}
  P_{\text{reflection}} = \sum_i (\max \{0, \nabla \occf^\top
  \hat{\mathbf{r}_j}\})^2
\end{align}
where $\hat{\mathbf{r}_j} =
\frac{K^{-1}\trackpj{t-1}}{\|K^{-1}\trackpj{t-1}\|}$ is unit vector in the
direction of ray. The gradient in the direction opposite to ray yields -ve
probability which needs to be clipped off. Squaring the function keep it
smooth near zero.

\subsubsection{Transmission probability}
A model for transmission of light through a material of thickness $x$,
density $\rho$ and opacity $k_o$ is given by Beer-Lambert law 
\begin{align}
  I(x) = I_0e^{-k_o\rho x}
\end{align}

Since both opacity and density are represented by our occupancy function
$\occf$, and also the domain of our $\occf$ is $[0, 1]$ instead of $[0,
\infty]$ as in case of $k_o$; we replace $e^{-k_o\rho}$ by our transparency
function $1 - \occf$. So the transmission probability over a small distance
$d\lambda$ is given by
\begin{align}
  P_{\text{transmission}}(\lambda + d\lambda) =
  P_{\text{transmission}}(\lambda) (1-\occf)^{d\lambda}
\end{align}
\newcommand{\ray}{\hat{\mathbf{r}}_j}
\newcommand{\occfray}{f_{occ}(\lambda\ray)}

For our given ray $\mathbf{x}_j = \lambda \ray$, the probability that the point
$\trackpj{t-1}$ is reflected from a distance $\lambda$ is given by

\newcommand{\lambdadist}{f_{\lambda}(\trackpj{t-1}, \lambda)}
\begin{align}
  \lambdadist &= P_{\text{reflection}}
  \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} %\\
  %= \max \{ 0, (\nabla f_{occ}&(\lambda \ray)^\top \ray) \}
  %\prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
\end{align}
where $\prod_{0}^{\lambda}$ represents the \emph{product integral} from $0$ to
$\lambda$. A product integral is a simple integral in log domain
\begin{align}
  \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} =
  e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
\end{align}

% Once we have our distribution over $\lambda$, $\lambdadist$ we can compute the
% reprojection of $\trackpj{t-1}$ over image in time $t$ as a function of
% $\lambda$. Let

\subsubsection{Reprojection error}

\begin{align}
  f^{i}_{reproj}&(\trackpj{t-1}, \lambda) =
  \projectionOf{\invProjectionOf{\trackpj{t-1}}}\\
  %&= K(R^i_t ((R^i_{t-1})^\top\lambda \ray - (R^i_{t-1})^\top T_{t-1}) + T_{t})\\
  &= \frac
  {p_{1:2}\lambda + q_{1:2}}
  {p_{3}\lambda + q_{3}}
\end{align}
where $p_{1:3} = KR^i_t(R^i_{t-1})^\top\ray$ and
$q_{1:3} = KR^i_t(R^i_{t-1})^\top T_{t-1} + KT_t$

Now that we have an association from TP $i$ to point track $j$ through
$\lambda$, we can come up with an association probability
\newcommand{\occfxi}{L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i)}
\newcommand{\occfi}{L(\lambda \ray; \pos{i}{t-1}, \Sigma_i)}
\newcommand{\assocP}{a^{i}_{j,t-1}(\lambda)}
\begin{align}
   \assocP &= \frac{(\max \{ 0, \nabla \occf^\top
\ray \})^2 }{P_{\text{reflection}}}\lambdadist\\
&=(\max \{ 0, \nabla \occf^\top \ray \})^2
  \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
\end{align}

Now coming back to our point track energy, the distribution over $\lambda$
becomes our association function which instead of associating each point track
with a traffic participant, associates it with a depth ($\lambda$). Hence our
summation over $N$ traffic participants is replaced by an integral over the
entire ray.
\begin{multline}
  \Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i,\{ \dimsn{i} \}_i) = \\
    \sum_{i = 1}^N
    \sum_{j = 1}^{M}
    \int_1^{\infty}
    a^i_{j,t-1}(\lambda) 
    \|\trackpj{t} - f^i_{reproj}(\trackpj{t-1}, \lambda)\|^2
    d\lambda
\end{multline}

\subsubsection{Approximations}
\newcommand{\Ptrans}{P_{\text{transmission}}}
\newcommand{\Prefl}{P^i_{\text{reflection}}}
\newcommand{\dishort}{d_i(\mathbf{x})}

Reflection probability of $i$th traffic participant is easy to compute
analytically 
\begin{multline}
  \Prefl =
  (\max \{ 0, \nabla \occf^\top \ray \})^2 \\
  = (\max \{ 0, \nabla \occfxi^\top\ray \})^2
  \label{eq:analytic-prefl}
\end{multline}
where 
\begin{multline}
  \nabla \occfxi^\top\ray \\=
  \nabla k\dishort \sech^2\left(\frac{k}{2}\dishort\right)
\end{multline}
where $\dishort = 1-d(\mathbf{x}, \pos{i}{t-1})$ is a signed distance measure
from the contour of the ellipsoid where $d(\mathbf{x}, \pos{i}{t-1})$ is 1.

However, the transmission probability needs to be approximated.  
%
% \subsubsection{Computing $\Prefl$ and $\Ptrans$}
% Focusing on  $\nabla \occfxi$ 
% 
% \begin{multline}
%   \nabla \occfxi =\\
%   \frac{-k\nabla d(\mathbf{x}, \pos{i}{t-1})e^{-k(1-d(\mathbf{x}, \pos{i}{t-1}))}}{
%     (1 + e^{-k(1-d(\mathbf{x}, \pos{i}{t-1}))})^2
%   } \\ 
%   = -k\nabla d(\mathbf{x}, \pos{i}{t-1})\sech^2\left(\frac{k}{2}(1-d(\mathbf{x},
%   \pos{i}{t-1}))\right)
%   \\
%   = \nabla k\dishort \sech^2\left(\frac{k}{2}\dishort\right)
% \end{multline}
% where $\dishort = 1-d(\mathbf{x}, \pos{i}{t-1})$ is a signed distance measure
% from the contour of the ellipsoid where $d(\mathbf{x}, \pos{i}{t-1})$ is 1.
% Focusing on $\nabla d(.)$
% 
% \begin{align}
%   \nabla d(\mathbf{x}, \pos{i}{t-1}) = 2\Sigma_i(\mathbf{x} - \pos{i}{t-1})
% \end{align}
% Back to \eqref{eq:analytic-prefl}
% 
% \begin{multline}
%   (\max \{ 0, \nabla \occf^\top \ray \})^2 = \\
%   \sech^4\left(\frac{k}{2}\dishort\right) 
%   (\max \{ 0 , \nabla k\dishort^\top\ray\})^2
% \end{multline}
% 
% The probability is simply $\sech^2(.)$ scaled by gradient of ellipsoid
% $\nabla k\dishort$ projected in the ray direction $\ray$.
% 
% \begin{align}
%   \Ptrans = 
%   e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
% \end{align}
% \begin{multline}
% \int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}
% =  \\
% \int_{1}^{\lambda} \ln{\left(1 - \sum_i \occfi\right)}{d\lambda}
% \end{multline}
% 
% The above integral is very difficult to approximate or compute analytically.
So based on intuition, we approximate the $\Ptrans$ by following function
\begin{align}
\label{eq:evalCumulativePtrans}
  \Ptrans &= \prod_i L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)L_{\lambda}(\lambda; \mu^i_d)\\
  L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u) &= \frac{1}{
    1 + e^{-k_u(1 - (\mathbf{u} - \mu^i_u)^\top\Sigma^i_u(\mathbf{u} -
    \mu^i_u))}
  }
  \\
  L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d) &= \frac{1}{
  1 + e^{-k_d(\lambda - \mu^i_d(\mathbf{u}))}
}
\end{align}
where 
\begin{align}
  \mu_u^i &= \projectionOf{\pos{i}{t-1}} \\
  \Sigma_u^i &= \projectionOf{\Sigma_i}\\
  \mu^i_d(\mathbf{u}) &= \relp{i}{t}\\
  k_u &= 10\log(49)\\
  k_d &= \frac{\log(49)}{\sqrt{h^2 + l^2 + w^2}}
  \label{eq:ptransmissionInit}
\end{align}
is the distance of the centre of the traffic participant from the camera.

% $\mu^i_d(\mathbf{u}) = \min_{\lambda} d^2_i(\lambda K^{-1}\mathbf{u})$.
% $\mu^i_d(\mathbf{u})$ is the closest point to the unit contour of ellipsoid.
% If there are multiple such points, the point closest to the camera is taken as
% $\mu^i_d(\mathbf{u})$

The association probability becomes

\newcommand{\Lu}{L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)}
\newcommand{\Llambda}{L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d)}
\begin{multline}
  \assocP = 
    \sech^4\left(\frac{k}{2}\dishort\right)
    (\max \{ 0, \nabla k\dishort^\top\ray \})^2\\
  \prod_i \Lu
    \Llambda \\
    \label{eq:assocCoeffEval}
\end{multline}

So the energy becomes

\begin{multline}
  \label{eq:integrand}
  \Energy{track}(.) = 
    \sum_{i = 1}^N
    \sum_{j = 1}^{M}
    \int_1^{\infty}
    \assocP
    E^i_{\text{reproj}}(\lambda)
    d\lambda
\end{multline}
where $x = \lambda \ray$ and $E^i_{\text{reproj}}(\lambda) = \|\trackpj{t} -
f^i_{reproj}(\trackpj{t-1}, \lambda)\|^2$ is reprojection error which is a
quadratic in $\lambda$

The integral in the above expression is computed numerically.

\begin{comment}
  %%%%%%%%%%%%%%%% Analytical attempt to integration %%%%%%%%%%%%%%%%%%%%%
  \begin{align}

    E^i_{\text{reproj}}(\lambda) &= \left\|\trackpj{t} - \frac{p_{1:2}\lambda +
  q_{1:2}}{p_3\lambda + q_3}\right\|^2\\
  &= \frac{(p_1\lambda + q_1 - u_{j1}(t))^2 + (p_2\lambda + q_2 - u_{j2}(t))^2}
  {(p_3\lambda + q_3)^2}\\
  &= \frac{a\lambda^2 + b\lambda + c}{(p_3\lambda + q_3)^2}
  \end{align}
  where $a = p_1^2 + p_2^2$, $b = 2p_1(q_1 - u_{j1}(t)) + 2p_2(q_2 - u_{j2}(t))$
  and $c = (q_1 - u_{j1}(t))^2 + (q_2 - u_{j2}(t))^2$

  So, in terms of $\lambda$ we have the integrand as
  \begin{multline}
    \int_1^\infty
    \prod_i (1 +
    \tanh(\poly^{(1)}_{ij1}(\lambda)))\sech^4(\poly^{(2)}_{ij2}(\lambda))\\
    (\max\{ 0, \poly^{(2)}_{ij3}(\lambda) \})^2
    \frac{\poly^{(2)}_{ij4}(\lambda)}{(\poly^{(1)}_{ij5}(\lambda))^2}d\lambda
  \end{multline}
  where $\poly^{(n)}_{ijk}$ denotes a polynomial $k$ of order $n$ dependent upon $i$th
  traffic participant and $j$th point. This integrand is still too difficult to
  be solved or approximated analytically.

  We approximate the expression,

  \begin{multline}
    \prod_i \Llambda
  \sech^4\left(\frac{k}{2}\dishort\right)(\max\{ 0, \nabla k\dishort^\top\ray \})^2
  \end{multline}

  with a
  gaussian with mean at $\mu^{ij}_{\lambda} : d_i(\mu^{ij}_{\lambda}\ray) = 0$
  standard deviation as $\sigma^{ij}_{\lambda} =
  \frac{\pi}{2\sqrt{3}kd(\mu^{ij}_{\lambda}\ray, \pos{i}{t-1})}$  and magnitude as the
  expression computed at mean. An integrand of the form
  \begin{align}
    \frac{\poly^{(2)}_{ij4}(\lambda)}{(\poly^{(1)}_{ij5})^2}
      e^{\frac{- (\lambda -
  \mu^{ij}_{\lambda})^2}{\sigma^{ij}_{\lambda}}}
  \end{align}
   is integrable analytically by parts.

   \newcommand{\muijl}{\mu^{ij}_{\lambda}}
   \newcommand{\sigmaijl}{\sigma^{ij}_{\lambda}}
   \begin{align}
   \int_1^\infty \frac{a\lambda^2 + b\lambda + c}{(p_3\lambda + q_3)^2}e^{\frac{- (\lambda -
  \mu^{ij}_{\lambda})^2}{\sigma^{ij}_{\lambda}}}d\lambda
   \end{align}
   Substituting $y = \frac{\lambda - \mu^{ij}_{\lambda}}{\sigma^{ij}_{\lambda}}$

   \begin{align}
     \int_1^\infty \frac{a_y y^2 + b_yy + c_y}
     {(p_{3y}y + q_{3y})^2}e^{-y^2}dy
   \end{align}
   where $a_y = a(\sigmaijl)^3$, $b_y = (2a\muijl + b)(\sigmaijl)^2$ and $c_y =
   (2a(\muijl)^2 + b\muijl + c)\sigmaijl$ and $p_{3y} = \sigmaijl p_3$ and
   $q_{3y} = p_3\muijl + q_3$

  % \subsubsection{Sandwich of ellipsoids model}
  % 
  % \begin{enumerate}
  %   \item Model $\occf$ as
  %     sigmoid over ellipse instead of a gaussian.
  %     \begin{align}
  %       \occf = \frac{1}{
  %       1 + e^{-(\mathbf{x} - \pos{i}{t})^\top
  %         \Sigma_i (\mathbf{x} - \pos{i}{t}))}}
  %     \end{align}
  %   \item To get the intuition of this occupancy function imagine the traffic
  %     participant as layered ellipsoid. The innermost ellipsoid has very high
  %     probability (approx 1) of being occupied. The outermost ellipsoid has very
  %     low probability (approx 0) of being occupied. We will just consider the
  %     occupancy interplay within these two ellipsoids.
  %   \item Project outer ellipsoids of all TP's on the image.
  %   \item Consider the ellipses that bound the track point $\trackpj{t-1}$.
  %   \item For each ellipse do
  %     \begin{itemize}
  %       \item Case 1: The ray intersects inner ellipse
  %         Now the ray intersects both inner and outer ellipse
  %         Compute the intersection points on both the ellipses
  %         Compute the gradient function $\nabla\occf^\top \ray$ at
  %         the mid point of the two intersections. Use this as the magnitude of
  %         gaussian mixture component centered at the mid point of intersections
  %         and spread such that 97 percentile of probability mass of guassian is
  %         within the intersection points. With the same parameters model the
  %         transimission probability with product of logistic function $L(.)$.
  %       \item Case 2: The ray do not intersects inner ellipse.
  %         The ray just passes through the outer ellipse. Find the point on the
  %         ray closest to the center of the ellipse. Compute gradient function
  %         at the closest point, which will be again used as the magnitude of
  %         gaussian mixture component centered at the closest point and spread
  %         such that 97 percentile of probabiltiy mass of gaussian is within the
  %         two intersection points of the ellipse. With the same parameters model
  %         the transimission probability with product of sigmoids.
  %     \end{itemize}
  %   \item Now this approximated $\lambdadist = \sum N(.) \prod (1 - L(.))$ can
  %     be used in integrating the error over $\lambda$.
  % \end{enumerate}
  \newpage

  \clearpage
  %%%%%%%%%%%%%%%% Analytical attempt to integration %%%%%%%%%%%%%%%%%%%%%
\end{comment}

\subsubsection{Sigma of ellipsoid}
\label{sec:sigmacomputation}

\newcommand{\Sigmait}{\Sigma^i_t}
\newcommand{\muit}{\mu^i_t}
\begin{align}
  \muit &= \begin{bmatrix}
  0& 0& \frac{h}{2}
  \end{bmatrix}^\top\\
  \Sigmait &= \begin{bmatrix}
    \frac{4}{l^2} & 0 & 0 \\
    0 & \frac{4}{w^2} & 0 \\
    0 & 0 & \frac{4}{h^2}
  \end{bmatrix}
\end{align}

In tracklet coordinates the equation of ellipsoid is 
\newcommand{\xt}{\mathbf{x}_t}
\newcommand{\xc}{\mathbf{x}_c}
\begin{align}
  (\xt - \muit)^\top \Sigmait (\xt - \muit) = 1
\end{align}

Moving to camera coordinates
\newcommand{\Rctot}{R}
\newcommand{\tctot}{t}
\begin{align}
  (\Rctot \xc + \tctot - \muit)^\top \Sigmait (\Rctot \xc + \tctot - \muit) = 1
\end{align}

\newcommand{\tcmut}{t'}
Let $\tcmut = \tctot - \muit$
\begin{align}
  (\Rctot \xc + \tcmut)^\top \Sigmait (\Rctot \xc + \tcmut) = 1
\end{align}
\begin{align}
  \xc^\top \Rctot^\top \Sigmait \Rctot \xc + 2 (\Rctot^\top \tcmut)^\top  \Rctot^\top\Sigmait \Rctot \xc
  + \tcmut^\top \Sigmait \tcmut = 1
\end{align}
\newcommand{\Sigmaic}{\Sigma'^i_c}
\newcommand{\muic}{{\mu^i_c}}
Let $\Sigmaic = \Rctot^\top \Sigmait \Rctot$ and $\muic = - \Rctot^\top
\tcmut$
\begin{align}
  (\xc - \muic)^\top\Sigmaic(\xc - \muic) - \muic^\top\Sigmaic\muic +
  \tcmut^\top \Sigmait \tcmut = 1
\end{align}
\newcommand{\Sigmaicf}{\Sigma^i_c}
Let $\Sigmaicf = \frac{\Sigmaic}{1 - \tcmut^\top \Sigmait \tcmut +
\muic^\top\Sigmaic\muic}$
\begin{align}
(\xc - \muic)^\top\Sigmaicf(\xc - \muic) = 1
\end{align}

Hence, we have following expression for mean and sigma of ellipsoid:
\begin{align}
  \label{eq:ellipsoidMeanSigma}
  \muic &= - \Rctot^\top \tcmut \\
  \Sigmaicf &= \frac{\Sigmaic}
{1 - \tcmut^\top \Sigmait \tcmut + \muic^\top\Sigmaic\muic}
\end{align}

% \subsection{Object detection score}
% \begin{align}
% \Energy{det}(\relp{i}{t}, \dimsn{i}) = 
%              \frac{1}{S_t^2(\projectionOf{\dimsn{i}})}
% \end{align}

% \subsection{Object 2D bounding box with occlusion}
% Reproduced from \cite{song2014eccv} section 4.3
% 
% \begin{multline}
%   \Energy{box}(\relp{i}{t}, \dimsn{i}) =
%              %\sum_{i=1}^N \sum_{t=s_i}^{e_i}
%              \rho^i_t \|\projectionOf{\dimsn{i}} -
%              \bb{i}\|^2
% \end{multline}
% 
% where $S_t(.)$ is the function to approximate the detection scores using
% mixture of Gaussian model and $\rho^i_t$ is the visibility fraction. 
% 
% % It can be
% % computed by using polygon intersection algorithms.
% % \begin{align}
% %   v^i_t &= \frac{\|\occFreeProj{\dimsn{i}}\|}
% %                 {\|\projectionOf{\dimsn{i}}\|}
% % \end{align}
% % where $\|.\|$ represents the norm or the area of the polygon.
% 
% Another approach is to just consider the corner points in the occlusion free
% area.  Say $\projectionOf{\dimsn{i}} = [b^i_1, \dots, b^i_4]$.
% \begin{multline}
%   \Energy{box}(\relp{i}{t}, \dimsn{i}) =
%              %\sum_{i=1}^N \sum_{t=s_i}^{e_i}
%              %S_t^2(\projectionOf{\dimsn{i}})
%              \sum_{{b^i_j} \in \occFreeProj{\dimsn{i}}}
%              \|b^i_j - d^i_j\|^2
% \end{multline}
% 
% In the opinion of this author, the second approach is better because the
% visibility is an area based measure while the error metric is point to point
% distance based measure. If we use bounding overlap instead of corner to corner
% distance, the use of visibility fraction makes much more sense. However, one
% can argue that even detection score is an area based measure. 
% 
% Hence a third approach can be 
% \begin{multline}
%   \Energy{box}(\relp{i}{t}, \dimsn{i}) =
%              %\sum_{i=1}^N \sum_{t=s_i}^{e_i}
%   \rho^i_t \|\projectionOf{\dimsn{i}} \ominus \bb{i}\|
% \end{multline}
% where $A \ominus B$ represents the symmetric difference between set $A$ and set
% $B$ and is given by $A \ominus B = (A \cup B) \setminus (A \cap B)$.
% One may argue that we can take the intersection of occlusion free projection 
% and get rid of the visibility fraction, but that would be a little off the 
% detection bounding box is usually more close to the projection of full car
% instead of the just the visible portion.
% 
% 
% \subsection{Orientation cues}
% There are two orientation cues (1) orientation from detection (2) orientation
% from appearance map \cite{yao2012describing}.
% 
% \begin{align}
%   \Energy{ori} &= 
%   %S_t^2(\projectionOf{\dimsn{i}})
%   \rho^i_t(1 - \cos({\omega}^i_{\text{det}} - \ori{i}{t})
% \end{align}
% 
% Appearance map is a shape prior that requires \emph{Scene labeling} input.

\section{Continuous object detection score energy with occlusion}

To start with we have hypothesized 3D bounding boxes $\{ \dimsn{i} \}_i$
over all traffic participants and we have object detection scores modeled as
mixture of Gaussians over four dimensional space of bounding box boundaries.
Let the detection score function over the detection $\bb{i}$ be 
%
\begin{align}
  S(\bb{i}) = \sum_j A_j \exp((\bb{i}-\mu^{(d)}_j)^\top \Sigma^{(d)-1}_j
  (\bb{i}-\mu^{(d)}_j))
\end{align}
%

\subsection{Soft occlusion regions}
Let the projections of hypothesized soft ellipsoids be
$\projectionOf{\dimsn{i}}$ with some mean $\mu_i$ and variance $\Sigma_i$
(assuming that projection of ellipsoids can be approximated by ellipses on
image plane). We take the occlusion (intersection of two ellipses) to be
modelled by product of the respective Gaussians.
%
\begin{align}
  O_{ij}(x; \mu_{Oij}, \Sigma_{Oij}) = N(x; \mu_i, \Sigma_i)N(x; \mu_j,
  \Sigma_j)
\end{align}
%
The product of Gaussian can be computed analytically.

\subsection{Merging occlusion regions with detection score}
But what does detection score function represents? It is a measure of
correlation of trained object features and the features in the candidate
bounding box. If the detection scores are indeed Gaussians around the mean
bounding box $\mu_j$, the $\Sigma_j^{-1}$ represents the variance (and
covariance) around the mean bounding box. But when the candidate objects seem
to be occluded we have additional information available. In such a case, we
can say that the occluded object might have unexpected effect on the detection
scores. However, the uncertainty in the detection score in loop sided. The
mean detection bounding box must have picked up correct boundaries on the
un-occluded sides but we cannot say the same about occluded boundaries. The
effect on detection score depends a lot on the features of the occluder. Given
this understanding we want to decrease our confidence on the mean detection
boundaries around the occluded boundaries. One of the simplest ways will be to
scale the appropriate diagonal element of $\Sigma_j$ by an appropriate scaling
factor.

We observe that the soft occlusion regions are 2D while the detection scores
are 4D. But that should not be a problem because the detection scores are
modeled as $[x_{\text{min}}, y_{\text{min}}, x_{\text{max}},
y_{\text{max}}]^\top$, we can stack the vectors in the soft occlusion region
domain as the regions are independent of min or max variation. The parameters
of 4D occlusion distribution are given by

\begin{align}
  \mu'_{Oij} = [\mu_{Oij}^\top \mu_{Oij}^\top]^\top
  \Sigma'_{Oij} = \begin{bmatrix}
    \Sigma_{Oij} & \Sigma_{Oij} \\
\Sigma_{Oij} & \Sigma_{Oij}
  \end{bmatrix}
\end{align}

With our
discussion so far, the function $O_{ij}(.)$ gives an additional measure of
uncertainty associated with each point in the space. To finally re-model our
detection scores scaled by continuous occlusion we sample $O_{ij}(.)$ at the
mean detection boundaries from GMM $S(.)$ and we scale the detection boundary
variance by $\mathcal{P}_{ij} = \rho_{ij}\rho_{ij}^\top$ where $\rho_{ij} =
\mathbf{1} + O_{ij}(\mu^{(d)}_j; \mu'_{Oij}, \Sigma'_{Oij})$. The new variance
in detection score is given by 
%
\begin{align}
  \Sigma'^{(d)}_j = \prod_{k \in \text{occluders}} \mathcal{P}_{kj}
  \Sigma^{(d)}_j
  \prod_{k \in \text{occluders}} \mathcal{P}^\top_{kj}
\end{align}
%
The detection scores GMM with occlusion is given by replacing the covariance
matrix
\begin{align}
  S'(\bb{i}) = \sum_j A_j \exp((\bb{i}-\mu^{(d)}_j)^\top \Sigma'^{(d)-1}_j
  (\bb{i}-\mu^{(d)}_j))
\end{align}

\newcommand{\Beizer}{B\'eizer }
\subsection{Lane energy}
\label{sec:laneEnergy}
 The lanes be are modeled as splines. The lanes geometry information can be
 obtained from camera input as well as from the available maps localized by
 GPS. We need to combine information in a different framework to lead to a
more accurate solution by using both the sources. In a probablistic framework
it is always useful to compute uncertainty along the estimated values.
Here we assume that the confidence in lane detection is inversely proportional
to the squre of distance of of the specific point on the lane to the camera
\newcommand{\LaneUncertainty}[1]{\Sigma_{L_m}(#1)}
$\Sigma_{L_m}({x}_{L_m}) = \frac{1}{\|\mathbf{x}_{L_m} - \egop\|^2}$.

A lane is modeled by four control points of a \Beizer curve $L_j = \{l_0, l_1,
l_2, l_3\}$. The parametric curve is given by $L_j(k) = \sum_{i=0}^3 {}^3C_i
(1-t)^{3-i}t^i l_i$. \Beizer are double differentiable so one can find
tangents ($L'_j(k)$) and normals $R_{\frac{\pi}{2}}L'_j(k)$ where 
$R_{\frac{\pi}{2}} = \begin{bmatrix} 0 & -1 \\ 1 & 0 \end{bmatrix}$ is
$90^\circ$ rotation matrix.

\newcommand{\projOnLane}[1]{\pi_{L_m(k)}(#1)}
Now, there are some algorithms \cite{ma2003point, chen2007improved} to
approximate the closest point on a \Beizer curve $k_x = \projOnLane{x}$.
Consequently one can get solutions for shortest distance $s =
\text{DIST}(L_j(k), x)$ and orientation at a closest point on the lane
$\mathbf{t} = \text{TAN}(L_j(k), x)$.

% \subsubsection{Position in lane}
%
% \begin{align}
%   \Energy{plane} &=
%   \min_{j = 0}^{n_l} \text{DIST}(L_j(k), \pos{i}{t})
% \end{align}
%
 % 
 % We normalize it with the confidence in lane positions.
 % 
 % \begin{align}
 %   \Energy{plane} &=
 %   \min_{m = 0}^{n_l} \text{DIST}(L_m(k), \pos{i}{t})
 %   \LaneUncertainty{\pos{i}{t}}
 % \end{align}

\subsubsection{Orientation within lane}
\begin{itemize}
  \item We can find the tangent to a lane
  \item The energy is given by the dot product between car orientation
    and tangent to the lane at that point.
\end{itemize}

% \begin{align}
%   \Energy{olane} &= 1 - \text{TAN}(L_l(k),  \pos{i}{t})
%   \cdot
%   \ori{i}{t}
% \end{align}
% 
% 
% 
% This model needs to be scaled by uncertainty. For example, if we want to say
% that the farther the lane is from the camera we are less sure about lane
% orientation and hence this evidence term we scale it by say square of distance
% of the car position from camera.

% \begin{align}
%   \Energy{olane} &= 
%   (1 - \ori{i}{t} \cdot \text{TAN}(L_{m^*}(k),  \pos{i}{t}) )
%   
% \end{align}
% where $m^* = \arg \min_m \text{DIST}(L_m(k), \pos{i}{t})$

\begin{align}
  \label{eq:laneOrientationEnergy}
  \Energy{lane} &= 
  \sum_{m \in M_{\text{close}}}
  (1 - \ori{i}{t} \cdot \text{TAN}(L_{m}(k), \pos{i}{t}) )
\LaneUncertainty{\pos{i}{t}}
\end{align}
where $M_{\text{close}} = \{m : \text{DIST}(L_{m}(k), \pos{i}{t}) < 50\} $ is
the set of nearby lanes and 
\begin{align}
\LaneUncertainty{\pos{i}{t}} = 
  \frac{1}{1 + exp(-q(w_{\text{road}} - \text{DIST}(L_{m}(k), \pos{i}{t})))}
\end{align}
for some constant $w_{\text{road}}$ that represents the width of the road.

\begin{comment}

\subsection{Collisions}

The collision constraint among traffic participants can be modelled by
pairwise distance based constraints. But having constraints between each pair
of participants is bound to create cycles and computational inefficient.
Among game developers it is common to use spatial hashing to find collision
candidates and use pairwise constraints only among those. While this will
enable us to speed up collision checking, we will still end up inducing cycles
in the model. There are two ways to break these cycles, 1) disable the cross
lane collision checking 2) created a weighted graph among collision
candidates weighted by distance and then find a minimum spanning
tree to break cycles. (1) is too strong of an assumption hence we focus on the
second approach.

There are two possible approaches to find collision among candidates (1)
polygon intersection methods (2) soft ellipse intersection method. Boost
provides scan line based approach to find intersections of polygons. Since our
polygons are simple rectangles, this approach can be very fast. Other approach
is to approximate rectangles with ellipses and finding if the ellipses
intersect.  This intersection can be computed analytically.

\begin{align}
  \EnergyCol &= \begin{cases}
  \infty &\text{if INTERSECTS}(\pos{i}{t}, \dimsn{i}, \pos{j}{t},
  \dimsn{j})\\
  0 &\text{otherwise}
  \end{cases}
\end{align}

%For smoother collision probability see Section \ref{sec:smoothercollision}.

\subsubsection{Ellipse-ellipse intersection}
\label{sec:ellipseintersection}
A rectangle with sides $2a$ and $2b$ can be approximated by an ellipse with
equation $\frac{x^2}{a^2} + \frac{y^2}{b^2} = 1$. But this ellipse is inside
the rectangle. To enclose the rectangle, scale the ellipse by a factor of
$\sqrt{2}$. The equation becomes, $\frac{x^2}{2a^2} + \frac{y^2}{2b^2} = 1$.
For rotation $\psi$ and center $\pos{i}{t}$, the equation of ellipse can be
re-written as:
\begin{align}
  (\mathbf{x} - \pos{i}{t})^\top\Sigma_i^{-1}(\mathbf{x} - \pos{i}{t}) &= 1
\end{align}
where
\begin{align}
  \Sigma_i^{-1} &= \begin{bmatrix}
    \frac{\cos^2{\psi}}{2a^2} + \frac{\sin^2{\psi}}{2b^2} &
    \frac{\cos{\psi}\sin{\psi}}{2}(\frac{1}{b^2} - \frac{1}{a^2})\\
    \frac{\cos{\psi}\sin{\psi}}{2}(\frac{1}{b^2} - \frac{1}{a^2}) &
    \frac{\sin^2{\psi}}{2a^2} + \frac{\cos^2{\psi}}{2b^2} \\
  \end{bmatrix}
\end{align}

% A point $\mathbf{x}$ is inside both ellipse $i$, $j$ if and only if
% \begin{multline}
%   (\mathbf{x} - \pos{i}{t})^\top\Sigma_i^{-1}(\mathbf{x} - \pos{i}{t}) +\\
% (\mathbf{x} - \pos{j}{t})^\top\Sigma_j^{-1}(\mathbf{x} - \pos{j}{t})
%   \le 2
% \end{multline}
% which is equivalent to
% \begin{multline}
%   (\mathbf{x} - \mu_c)^\top\Sigma_c^{-1}(\mathbf{x} - \mu_c)
%   + \pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t}\\
%   + \pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t}
%   - \mu_c^\top\Sigma_c^{-1}\mu_c
%   \le 2
% \end{multline}
% where $\Sigma_c = (\Sigma_i^{-1} + \Sigma_j^{-1})^{-1}$ and $\mu_c =
% \Sigma_c(\Sigma_i^{-1}\pos{i}{t} + \Sigma_j^{-1}\pos{j}{t})$.
% 
% There is at least one point inside both ellipse if 
% \begin{align}
%   \pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t}
%   + \pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t}
%   - \mu_c^\top\Sigma_c^{-1}\mu_c
%   &\le 2
% \end{align}
% 
% The left hand side can be interpreted as distance between two ellipses, which
% is 2 when the two ellipses collide and $0$ when two ellipse completely
% overlap.

\subsubsection{Smoother collision probability}
\label{sec:smoothercollision}
%The above mentioned ellipse-ellipse intersection formulation gives us an
%insight: the distance between two oriented ellipse boundaries can be again
%formulated as a distance metric\footnote{TODO:proof}.
Instead of using Gaussians to model
collision constraints as done by \cite{milan2013continuous}, we use a more
steeper sigmoid function.
\begin{multline}
  \EnergyCol = \frac{1}{1 +
\exp(-k(\pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t})-1)}\\
\frac{1}{1 +
\exp(-k(\pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t})-1)}
\end{multline}
where $k$ is steepness parameter.
%$d(.)$ is the distance metric defined as:
%\begin{multline}
%  d(\pos{i}{t}, \dimsn{i}, \pos{j}{t}, \dimsn{j})
%  =
%  \pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t} \\
%  + \pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t}
%  - \mu_c^\top\Sigma_c^{-1}\mu_c
%\end{multline}

\end{comment}

\subsection{Transition probability}
Dynamics constraints should not only enforce smooth trajectories, but also the
holonomic constraints.

The following equation adds a penalty if the change in
position is not in direction of previous orientation.

\begin{align}
  \label{eq:totalPosTransitionEnergy}
  \Energy{dyn-hol} = 1 - \ori{i}{t-1} \cdot (\pos{i}{t} - \pos{i}{t-1})
\end{align}

The following equation adds a penalty for change in position and orientation
but a penalty for change in velocity is much better approximation. However, in
a Markovian setting that would mean extending the state space of the car to
include velocity.

\begin{align}
  \Energy{dyn-ori} &= \|\ori{i}{t} - \ori{i}{t-1}\|^2\\
  \Energy{dyn-vel} &= \|(\pos{i}{t} - 2\pos{i}{t-1}) + \pos{i}{t-2}\|^2
\end{align}

As a result the dynamics are modeled by weighted combination of holonomic
constraint and smoothness constraints.

\begin{align}
  \WEnergy{dyn} &= \WEnergy{dyn-hol} + \WEnergy{dyn-ori} + \WEnergy{dyn-vel}
\end{align}

\subsection{Size Prior}

Prior can include among many other things the size prior on the car.

\begin{align}
  \label{eq:totalSizeEnergy}
  \Energy{prior} &= (\dimsn{i} - \expDimsn)^\top\Sigma_{\expDimsn}^{-1}(\dimsn{i} -
  \expDimsn)
\end{align}

where $\expDimsn$ is the mean traffic participant dimensions and
$\Sigma_{\expDimsn}$ is the correspondence covariance matrix.

\begin{table*}
  \begin{tabular}{|l|r|r|l|}
    \hline
    func            & equation                      & ms per 6 frames &
    comment \\
    \hline
    totalBBoxEnergy & Sec \ref{sec:totalBBoxEnergy} & 268 & \\
    laneEnergy      & Sec \ref{sec:laneEnergy}      & 163 & \\
    laneOrientationEnergy & Eq \eqref{eq:laneOrientationEnergy} & 155 & The
    equation summed up for all 6 tracklets\\
    collisionEnergyHellingerDistance & Eq 
    \eqref{eq:collisionEnergyHellingerDistance} & 93  & \\
    totalPosTransitionEnergy & Eq \eqref{eq:totalPosTransitionEnergy} & 15 & \\
    totalSizeEnergy & Eq \eqref{eq:totalSizeEnergy} & 0.9 & \\

    \hline
    occlusionMaskFromOptVector & Sec \ref{sec:occlusionMaskFromOptVector} &
    123 &
    \\
    bboxEnergyFromOccMask & Eq \eqref{eq:bboxEnergyFromOccMask} & 140 &  \\
    vis\_area\_from\_triangle & $\|\triangleProj{s} \setminus
    \occ{\relpz{i}{t}}\|$ & 76 & \\
    \hline
    distance2curve & $\text{DIST}(L_j(k), x)$ & 74 & Called 2 times per
    tracklet \\
    filterMapWaysByDistance & $M_{\text{close}} = \{m : \text{DIST}(.) < 50\} $ & 52 & \\
    area\_of\_triangle & $\|\triangleProj{s}\|$ & 48 & called 4 times per
    tracklet \\
    occlusionMask & Step 3 of Sec \ref{sec:occlusionMaskFromOptVector} & 46 &
    \\
    \hline
  \end{tabular}

  \begin{tabular}{|l|r|r|l|}
    \hline
    func            & equation                      & ms per 6 frames &
    comment \\
    \hline
    totalContPtTracksEnergy & Sec \ref{sec:totalContPtTracksEnergy} & 25000 &
    \\
    integrand & Eq \eqref{eq:integrand} & 23000 & \\
    repmat & & 5000 & \\
    assocCoeffEval & Eq \eqref{eq:assocCoeffEval} & 4000 & \\
    evalPreflection & Eq \eqref{eq:analytic-prefl} & 3000 & \\
    gradfocci & $\nabla \occf^\top \ray$ & 2040 & \\
    associationCoefficientInit & Eq
    \eqref{eq:ptransmissionInit}\eqref{eq:ellipsoidMeanSigma} & 1706 & \\
    projectToImage & $\frac{Ku}{Ku(3)}$ & 4000 & Called ~8 times per edge\\
    evalCumulativePtrans & \eqref{eq:evalCumulativePtrans} & 1178 & \\
    ptransmissionApproxInit & \eqref{eq:ptransmissionInit} & 1000 & \\
    ellipsoidCentreDist & $(x-\mu)^\top \Sigma (x-\mu)$ & 1000 & \\
    squeeze & & 951 &\\
    trackletToCamTransform & $R_{\ori{i}{t}}, t$ & 786 & \\
    ellipsoidMeanSigma & Eq \eqref{eq:ellipsoidMeanSigma} & 812 & \\
    \hline
  \end{tabular}
\end{table*}

{\small
\bibliographystyle{ieee}
\bibliography{model}
}
\end{document}
%\documentclass[11pt]{report}
%\usepackage{tikz}
%\usetikzlibrary{fit,positioning}
%\begin{document}
%\begin{figure}
%\centering
%\begin{tikzpicture}
%\tikzstyle{main}=[circle, minimum size = 10mm, thick, draw =black!80, node distance = 16mm]
%\tikzstyle{connect}=[-latex, thick]
%\tikzstyle{box}=[rectangle, draw=black!100]
%  \node[main, fill = white!100] at (cit)  {$c_i^t$ };
%  \node[main] at +(2.0cm, 1.0cm) (detect)  { $b$ };
%  \node[main] at +(2.0cm, -1.0cm) (sfm)    { $t$ };
%  \node[main] (lane)   [below=of cit] { $L$ };
%  \path (cit) edge [connect] (detect)
%        (cit) edge [connect] (sfm)
%        (cit) edge [connect] (lane);
%        \node[box, inner sep=4mm, fit=(cit) (detect) (lane),label=below right:N] {};
%  \node[main, fill = white!100] at (cit-1)  {$c_i^{t-1}$ };
%  \node[main] at +(2.0cm, 1.0cm) (detect)  { $b$ };
%  \node[main] at +(2.0cm, -1.0cm) (sfm)    { $t$ };
%  \node[main] (lane)   [below=of cit] { $L$ };
%  \path (cit) edge [connect] (detect)
%        (cit) edge [connect] (sfm)
%        (cit) edge [connect] (lane);
%        \node[box, inner sep=4mm, fit=(cit) (detect) (lane),label=below right:N] {};
%
%  %\node[rectangle, inner sep=4.4mm,draw=black!100, fit= (z) (w)] {};
%  %\node[rectangle, inner sep=4.6mm, fit= (z) (w),label=below right:M, xshift=12.5mm] {};
%  %\node[rectangle, inner sep=9mm, draw=black!100, fit = (theta) (z) (w)] {};
%\end{tikzpicture}
%\end{figure}
%\end{document}
%note - compiled with pdflatex

### 2014-10-09 Code/compSpline.m

@@ -1,0 +1,106 @@
+function [output_points, tangent] = compSpline(control_points, h)
+% compSpline evaluates a Bezier spline with the specified degree
+%
+% INPUTS
+% ------
+% control_points    - input 3 or 4 points in a 3x2 or 4x2 matrix [xs, ys]
+% h                 - the interval to use for evaluation, default = 0.05
+%
+% OUTPUTS
+% -------
+% output_points - n x 2 matrix of output points [xs; ys]
+% tangent       - the tangent at the two end-points [t0; t1]
+%
+% EXAMPLE
+% -------
+% [p, t] = compSpline(sp, 0.1);
+
+
+if nargin < 2
+    h = 0.05; 
+end
+
+% Get the degree
+degree = size(control_points, 1) - 1;
+
+% Compute number of return points
+n = floor(1/h) + 1;
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+%Quadratic Bezier curve
+%%%%%%%%%%%%%%%%%%%%%%%%
+if degree == 2
+    M =	[1, -2, 1; -2, 2, 0; 1,	0, 0];
+    
+    % Compute constants [a, b, c]
+    abcd = M * control_points;
+    a = abcd(1,:);
+    b = abcd(2,:);
+    c = abcd(3,:);
+    
+    % Compute at time 0
+    P = c;
+    dP = b * h + a * h^2;
+    ddP = 2*a*h^2;
+    
+    % Loop
+    output_points = zeros(n, size(control_points,2));
+    output_points(1,:) = P;
+    for i = 2:n
+	% Calculate new point
+	P = P + dP;
+	% Update steps
+	dP = dP + ddP;
+	% Put back
+	output_points(i,:) = P;
+    end;
+    
+    % Tangent: t0 = b
+    t0 = b;
+    % Tangent: t1 = 2a + b
+    t1 = 2*a + b;
+
+    
+%%%%%%%%%%%%%%%%%%%%%%%%
+%Cubic Bezier curve
+%%%%%%%%%%%%%%%%%%%%%%%%
+elseif degree == 3
+    
+    M =	[-1, 3,	-3, 1; 3, -6, 3, 0; -3,	3, 0, 0; 1, 0, 0, 0];
+    
+    % Compute constants [a, b, c, d]
+    abcd = M * control_points;
+    a = abcd(1,:);
+    b = abcd(2,:);
+    c = abcd(3,:);
[…]

### 2014-10-09 Code/visualizeLanes.m

@@ -1,0 +1,127 @@
+function out2 = visualizeLanes()
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Visualization for the annotated lanes
+%% (Hit any key to move to next image)
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% The directories with the images and the annotation output
+kitti_raw_dir = '/net/acadia/data/3DReconstBenchmarks/KITTI_RAW';
+sfm_out_dir = '/net/acadia/data/SFM_Outputs';
+%img_dir = '/home/ma/vdhiman/wrk/sceneunderstanding/KITTI_RAW/city/2011_09_26/2011_09_26_drive_0001_sync/image_02/data';
+%annotation_dir = '/home/ma/vdhiman/wrk/sceneunderstanding/SFM_Outputs/OtherLanes/Data/City/2011_09_26_drive_0001';
+img_dir = [kitti_raw_dir, '/', '%s/2011_09_26/2011_09_26_drive_%04d_sync/image_02/data'];
+annotation_dir = [sfm_out_dir, '/', 'OtherLanes/Data/%s/2011_09_26_drive_%04d'];
+
+% Load an annotation mat-file
+annotation_file = [annotation_dir, '/', 'otherlanes.mat'];
+
+egolanes_file = [sfm_out_dir, '/', 'EgoLanes/Data/%s/2011_09_26_drive_%04d/egolanes.mat'];
+
+for ktype={'Road', 'City', 'Residential'}
+	for count=1:110
+		if ~exist(sprintf(annotation_file, ktype{1}, count), 'file') 
+			%disp([sprintf(annotation_file, ktype{1}, count), ' do not exists']);
+		elseif ~exist(sprintf(img_dir, lower(ktype{1}), count), 'file')
+			disp([sprintf(img_dir, lower(ktype{1}), count), ' do not exists']);
+		else
+			if exist(sprintf(egolanes_file, ktype{1}, count), 'file')
+				disp(['showing egolanes ', ktype{1}, ' ', num2str(count)]);
+				showFrames(sprintf(img_dir, lower(ktype{1}), count), sprintf(egolanes_file, ktype{1}, count));
+			end
+
+			disp(['showing otherlanes ', ktype{1}, ' ', num2str(count)]);
[…]

### 2014-10-09 Notes/plot_linear_and_real_gaussian.py

@@ -1,0 +1,45 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D # for projection='3d' to work
+import sys
+
+
+def gaussianLinear1D(xx, yy, filename):
+    # plot linear low dimensional approximation of guassian
+    # this is like taking manhattan distance as approximation for euclidean
+    phi_xx = np.exp(-xx**2/0.4)
+    phi_yy = np.exp(-yy**2/0.9)
+    fig = plt.figure()
+    #ax = fig.add_subplot(111, projection='3d')
+    #ax.plot_wireframe(xx, yy, phi_xx + phi_yy, colors='r')
+    fig.add_subplot(111).matshow(phi_xx + phi_yy)
+    fig.savefig(filename)
+
+def gaussian2D(xx, yy, filename):
+    # plot real gaussian
+    #ax.plot_wireframe(xx, yy, np.exp(-(xx**2/0.4 + yy**2/0.9)), colors='g')
+    fig2 = plt.figure()
+    fig2.add_subplot(111).matshow(np.exp(-(xx**2/0.4 + yy**2/0.9)))
+    fig2.savefig(filename)
+
+########################
+# main
+#######################
+
+filename = sys.argv[1]
+
+
+x = np.linspace(-1, 1, num=20)
+y = np.linspace(-1, 1, num=20)
+xx, yy = np.meshgrid(x, y)
+
+if 'gaussianLinear1D' in filename:
+    gaussianLinear1D(xx, yy, filename)
+elif 'gaussian2D' in filename:
+    gaussian2D(xx, yy, filename)
+else:
+    raise ValueError("Don't understand plot type from filename %s" %
+                       filename)
+
+# show
+#plt.show()

### 2014-10-10 Notes/model.tex
Added some notes about numerical integration and actually computing association probability using both hypothesis and reprojection.

@@
 \DeclareMathOperator{\poly}{poly}
+\DeclareMathOperator*{\argmin}{\arg\min}
 
@@
 \newcommand{\assocP}{a^{i}_{j,t-1}(\lambda)}
+\newcommand{\assocPk}{a^{i}_{j,t-1}(\lambda_k)}
 \begin{align}
@@
 
-Now coming back to our point track energy, the distribution over $\lambda$
-becomes our association function which instead of associating each point track
-with a traffic participant, associates it with a depth ($\lambda$). Hence our
-summation over $N$ traffic participants is replaced by an integral over the
-entire ray.
+Note that this fraction although called association probability does not
+capture the entire information that we have available for compute association
+of points to tracks. This above fraction is the association probability given 
+the hypothesized parameters of traffic participant model. Given that a point is
+observed on the image the sum of probability marginalized over other parameters
+must be one i.e.
+\begin{align}
+    \sum_{i = 1}^N
+    \int_1^{\infty}
+    \assocP d\lambda = 1
+\end{align}
+
+To compute the association probability between traffic participant $i$ and
+point track $j$ we must use re-projection error as well. When the association
+$i$ and $j$ is right and the point of reflection is at depth $\lambda$ the
+re-projection error must be zero, otherwise the error becomes a measure of
+distance from the true solution:
+
+\newcommand{\Ereproj}{E^{(ij)}_{\text{reproj}}}
+\begin{align}
+  \Ereproj(\lambda) = \|\trackpj{t} - f^i_{reproj}(\trackpj{t-1}, \lambda)\|^2
+\end{align}
+
+The error terms can be converted to probability domain by considering the error
+term as negative log of probablity
+
+\begin{align}
+  P^{(ij)}_{\text{assoc by reproj}}(\lambda) = \frac{1}{\sqrt{2\pi}}\exp(-\Ereproj(\lambda))
+\end{align}
+
+Using both the evidence terms we can write probability of association as
+\begin{align}
+  P^{(ij)}_{\text{assoc}} \propto \int_0^{\infty} \assocP \frac{1}{\sqrt{2\pi}}\exp(-\Ereproj(\lambda))d\lambda
+  \label{eq:prob-assoc}
+\end{align}
+
+However, for estimating the overall energy we just need to compute the expected
+value of the re-projection error for given parameters, i.e.
+
 \begin{multline}
@@
 \end{multline}
+
+If the aim is to find the best possible association, it is easier as we need to
+to compute the association that minimizes the expected re-projection error for
+point $j$. It remains to be seen that how the minima of following expression relates to minima of \eqref{eq:prob-assoc}
+
+\begin{align}
+  i^* = \argmin_{i=1}^N \int_0^\infty \assocP \Ereproj(\lambda) d\lambda
+\end{align}
+
+Since the computation of $\assocP$ entirely depends on hypothesized parameters,
+it severely limits the applicability of this method outside this kind of
+parameterized model.
 
@@
     \assocP
-    E^i_{\text{reproj}}(\lambda)
+    \Ereproj(\lambda)
     d\lambda
 \end{multline}
-where $x = \lambda \ray$ and $E^i_{\text{reproj}}(\lambda) = \|\trackpj{t} -
+where $x = \lambda \ray$ and $\Ereproj(\lambda) = \|\trackpj{t} -
 f^i_{reproj}(\trackpj{t-1}, \lambda)\|^2$ is reprojection error which is a
@@
 The integral in the above expression is computed numerically.
+
+\subsection{Numerical integration}
+Numerical integration is possible by computed by sampling. Samples need to be
+generated from the association probability $\assocP$ for a given $j$. We take
+proposal distribution to be a GMM with modes around probable reflection points.
+The weights of all Gaussians in the mixture are proportional to the distance of
+the point $j$ from projection of ellipsoid centre i.e. $\|\trackpj{t} - \projectionOf{\relp{i}{t}}\|$ . The range of Gaussian $G_i$
+must be in the interval $[\|\relp{i}{t}\|, \|\relp{i}{t}\| +
+\sqrt{3}\max(\dimsn{i})]$. Hence we take the mean as $\|\relp{i}{t}\| +
+\frac{\sqrt{3}}{2}\max(\dimsn{i})$ and variance as
+$\frac{1}{3}\max(\dimsn{i})^2$. The distribution from which we sample is 
+\newcommand{\Gauss}{\mathcal{N}}
+\newcommand{\PropDist}{\mathcal{W}}
+\begin{align}
+  \PropDist(\lambda) = \sum_i A_i \Gauss(\lambda; \|\relp{i}{t}\| +
+  \frac{\sqrt{3}}{2}\max(\dimsn{i}), \frac{1}{\sqrt{3}}\max(\dimsn{i}))
+\end{align}
+And the numerical integral with $K$ samples is computed by
+\begin{align}
+    \int_1^{\infty}
+    \assocP
+    \Ereproj(\lambda)
+    d\lambda
+    =
+    \frac{1}{K}\sum_k \Ereproj \frac{\assocPk}{\PropDist(\lambda_k)}
+\end{align}
+where $\lambda_k$ is the $k$th sample drawn from $\PropDist(\lambda)$.
 

### 2014-10-11 Notes/model.tex
Added writeup about association probability computation and importance sampling.

@@
 \begin{align}
-  \mu_u^i &= \projectionOf{\pos{i}{t-1}} \\
-  \Sigma_u^i &= \projectionOf{\Sigma_i}\\
+  \mu_u^i &= \projectionOf{\pos{i}{t-1}} \label{eq:muiudef}\\
+  \Sigma_u^i &= \projectionOf{\Sigma_i} \label{eq:sigmauidef}\\
   \mu^i_d(\mathbf{u}) &= \relp{i}{t}\\
@@
 The weights of all Gaussians in the mixture are proportional to the distance of
-the point $j$ from projection of ellipsoid centre i.e. $\|\trackpj{t} - \projectionOf{\relp{i}{t}}\|$ . The range of Gaussian $G_i$
-must be in the interval $[\|\relp{i}{t}\|, \|\relp{i}{t}\| +
-\sqrt{3}\max(\dimsn{i})]$. Hence we take the mean as $\|\relp{i}{t}\| +
+the point $j$ from projection of ellipsoid centre i.e. 
+\begin{align}
+  A_{ij} = \frac{1}{Z_j}\exp(-(\trackpj{t} - \mu^i_u)^\top\Sigma_u^i(\trackpj{t} - \mu^i_u))
+\end{align}
+where $Z_j = \sum_{i=1}^N A_{ij}$ and $\mu^i_u$ and $\Sigma_u^i$ are described in \eqref{eq:muiudef} and \eqref{eq:sigmauidef} respectively.
+The range of Gaussian $G_i$
+must be in the interval $[\|\relp{i}{t}\|, \|\relp{i}{t}\| -
+\sqrt{3}\max(\dimsn{i})]$. Hence we take the mean as $\|\relp{i}{t}\| -
 \frac{\sqrt{3}}{2}\max(\dimsn{i})$ and variance as
@@
 \newcommand{\Gauss}{\mathcal{N}}
-\newcommand{\PropDist}{\mathcal{W}}
-\begin{align}
-  \PropDist(\lambda) = \sum_i A_i \Gauss(\lambda; \|\relp{i}{t}\| +
+\newcommand{\PropDist}{\mathcal{W}_j}
+\begin{align}
+  \PropDist(\lambda) = \sum_i A_{ij} \Gauss(\lambda; \|\relp{i}{t}\| -
   \frac{\sqrt{3}}{2}\max(\dimsn{i}), \frac{1}{\sqrt{3}}\max(\dimsn{i}))

### 2014-10-14 Notes/model.tex
Added a theoretical (mis-)explanation for adding up covariance matrices.

@@
 \subsection{Soft occlusion regions}
-Let the projections of hypothesized soft ellipsoids be
-$\projectionOf{\dimsn{i}}$ with some mean $\mu_i$ and variance $\Sigma_i$
-(assuming that projection of ellipsoids can be approximated by ellipses on
-image plane). We take the occlusion (intersection of two ellipses) to be
-modelled by product of the respective Gaussians.
-%
-\begin{align}
-  O_{ij}(x; \mu_{Oij}, \Sigma_{Oij}) = N(x; \mu_i, \Sigma_i)N(x; \mu_j,
-  \Sigma_j)
-\end{align}
-%
-The product of Gaussian can be computed analytically.
+The soft occlusion regions is exactly the $\Ptrans$
+%
+\begin{align}
+  O_{j}(x; \mu_{Oj}, \Sigma_{Oj}) = 1 - \Ptrans
+\end{align}
+%
 
 \subsection{Merging occlusion regions with detection score}
-But what does detection score function represents? It is a measure of
+What does detection score function represents? It is a measure of
 correlation of trained object features and the features in the candidate
@@
 scale the appropriate diagonal element of $\Sigma_j$ by an appropriate scaling
-factor.
+factor. But how does occlusion affects the non diagonal terms. Consider that we
+have a set of measurements whose mean and variance are known $\mu = E(x)$ and $\Sigma = E ((x - \mu_x)(x - \mu_x)^\top)$. We want to know the
+affect of uncertainty on mean and variance of existing observations. On adding
+noise $[\Delta x, \Delta y]^\top$ with zero mean and covariance $\Delta
+\Sigma = E(\Delta x \Delta x^\top)$ the covariance of new data is given by
+\begin{multline}
+  E((x + \Delta x)(x+\Delta x)^\top) = E(xx^\top) + E(x \Delta x^\top) \\
+  + E(\Delta x x^\top) + E(\Delta x \Delta x^\top)
+\end{multline}
+where the terms $E(x \Delta x^\top)$ denote the correlation between the data
+vector and the uncertainty in the data. Although we understand that in our case
+the data is the appearance based detection score and uncertainty because of
+occlusion is closely related to the appearance and hence detection score, we
+assume independence between $x$ and $\Delta x$. Hence our resultant covariance
+matrix $ E((x + \Delta x)(x+\Delta x)^\top) = \Sigma + \Delta \Sigma$
 
@@
 mean detection boundaries from GMM $S(.)$ and we scale the detection boundary
-variance by $\mathcal{P}_{ij} = \rho_{ij}\rho_{ij}^\top$ where $\rho_{ij} =
-\mathbf{1} + O_{ij}(\mu^{(d)}_j; \mu'_{Oij}, \Sigma'_{Oij})$. The new variance
+variance by $\mathcal{P}_{j} = \rho_{j}\rho_{j}^\top$ where $\rho_{j} =
+O_{j}(\mu^{(d)}_i; \mu'_{Oj}, \Sigma'_{Oj})$. The new variance
 in detection score is given by 
@@
 \begin{align}
-  \Sigma'^{(d)}_j = \prod_{k \in \text{occluders}} \mathcal{P}_{kj}
-  \Sigma^{(d)}_j
-  \prod_{k \in \text{occluders}} \mathcal{P}^\top_{kj}
+  \Sigma'^{(d)}_j = \mathcal{P}_{j}
+  + \Sigma^{(d)}_j
 \end{align}

### 2014-11-07 Paper/model.tex
Renamed Notes to paper folder.

--- 2014-10-14 Notes/model.tex
@@
 \author{Vikas Dhiman\\
-{\tt\small vdhiman@nec-labs.com}
-\and
+{\tt\small dhiman@umich.edu}
 Manmohan Chandraker\\
 {\tt\small manu@nec-labs.com}
+\and
+Jason J Corso\\
+{\tt\small jjcorso@eecs.umich.edu}
 }
@@
 \begin{abstract}
-  The long term goal of this project is to identify and represent commonly 
-  occurring potentially dangerous road situations where driver can be warned 
-  about the situations. Such kind of driver assistance requires understanding
-  the state of various road scene elements. We broadly categorize the elements
-  in the scene as traffic participants (TP) and as other "scene elements" (like
-  lanes, intersections etc). 
+  TODO: Write abstract
 \end{abstract}

### 2014-11-07 Paper/presentation.tex
Renamed Notes to paper folder.

\documentclass{beamer} % "Beamer" is a word used in Germany to mean video projector.

\usetheme{default} % Search online for beamer themes to find your favorite or use the Berkeley theme as in this file.

\usepackage{color} % It may be necessary to set PCTeX or whatever program you are using to output a .pdf instead of a .dvi file in order to see color on your screen.
\usepackage{graphicx} % This package is needed if you wish to include external image files.
\usepackage{tikz}

\title{3D Road Scene understanding with soft continuous occlusion modeling}
\author{Vikas Dhiman} 
\institute{NEC Laboratories America}
%\date{January 6, 2012}

% 3D pose of the cars and ego motion
\newcommand{\pos}[2]{\mathbf{p}^{(#1)}(#2)}
\newcommand{\ori}[2]{\mathbf{\omega}^{(#1)}(#2)}
\newcommand{\state}[2]{\mathbf{s}^{#1}(#2)}

% ego pose
\newcommand{\egop}[1][t]{\pos{c}{#1}}
\newcommand{\egoo}[1][t]{\ori{c}{#1}}
\newcommand{\egos}[1][t]{\state{c}{#1}}

% relative pose between camera and car $i$
\newcommand{\relp}[2]{\Omega^{#1}(#2)}
\newcommand{\relpz}[2]{\Omega_z^{#1}(#2)}

% 3D tracks on car $i$ in its own coordinate frame
\newcommand{\tracklets}{\mathbf{X}^{(i)}_o}
\newcommand{\tracklet}[1]{\mathbf{x}^{(i)}_{#1}}
% track projections on camera
\newcommand{\trackp}[1]{u_{j}(#1)}
% Unclassified track point projected on camera
\newcommand{\ucTrackp}{\mathbf{u}(t)}

% projection function
\newcommand{\projectionOfi}[2]{\pi_{\relp{#1}{t}}(#2)}
\newcommand{\projectionOf}[1]{\projectionOfi{i}{#1}}
\newcommand{\invProjectionOf}[1]{\pi^{-1}_{\relp{i}{t-1}}(#1)}

% dimensions of car $i$
\newcommand{\dimsn}[1]{\mathbf{B}^{#1}}
\newcommand{\expDimsn}[1]{\hat{\mathbf{B}^{#1}}}

% bounding box corners on image
\newcommand{\bb}[1]{\mathbf{d}^{#1}(t)}

\newcommand{\Energy}[1]{\mathcal{E}^{it}_{\text{#1}}}
\newcommand{\pEnergy}[1]{\mathcal{E}^{ijt}_{\text{#1}}}
% Weighted energy
\newcommand{\WEnergy}[1]{\lambda_{\text{#1}}\Energy{#1}}
\newcommand{\EnergyCol}{\mathcal{E}^{ijt}_{\text{col}}}
\newcommand{\WEnergyCol}{\lambda_{\text{col}}\EnergyCol}

\begin{document}

\begin{frame} 
\titlepage
\end{frame}

\begin{frame}
  \frametitle{Aim of the project}
\begin{itemize}
  \item Use output of various sub-systems
    \begin{itemize}
      \item Ego motion
      \item Detection bounding boxes
      \item Detection orientation
      \item Maps, GPS
      \item Point tracks on objects
    \end{itemize}
    \pause
  \item along with heuristics like size prior, cars usually align with lanes
    etc
    \pause
  \item Output the most likely configuration of scene that best fits the
    output of various sub-systems and our heuristic knowledge
\end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Before}
  \includegraphics[width=\textwidth]{graphics/Video000061.jpg}
\end{frame}

\begin{frame}
  \frametitle{After}
  \includegraphics[width=\textwidth]{graphics/61.png}
\end{frame}

\begin{frame}
  \includegraphics[width=\textwidth]{graphics/61WithGraphicalModel.pdf}
\end{frame}

\begin{frame}
  \centering{
    \includegraphics[width=0.5\textwidth]{graphics/graphicalModelFrom61.pdf}
  }
  \pause
  % Collision energy
  %\begin{multline}
  %  \EnergyCol = \frac{1}{1 +
  %\exp(-k(\pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t})-1)}\\
  %\frac{1}{1 +
  %\exp(-k(\pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t})-1)}
  %\end{multline}
  %where $k$ is steepness parameter.
  % Bounding box energy occlusion energy

  \begin{align}
    \EnergyCol &=
    \frac{|\Sigma_i|^\frac{1}{4}|\Sigma_j|^\frac{1}{4}}
    {|\frac{1}{2}\Sigma_i + \frac{1}{2}\Sigma_j|^\frac{1}{2}}
    e^{-\frac{1}{8}
      \left(\pos{i}{t} - \pos{i}{t}\right)^\top
      \left(\frac{1}{2}\Sigma_i + \frac{1}{2}\Sigma_j\right)^{-1}
      \left(\pos{i}{t} - \pos{i}{t}\right)
      }
  \end{align}
\end{frame}

\begin{frame}
  \begin{multline}
    \pEnergy{occ}(\relp{i}{t}, \dimsn{i}, \relp{j}{t}, \dimsn{j}) =
               %\sum_{i=1}^N \sum_{t=s_i}^{e_i}
    \sum_kp_{ik}^{\text{track}}(\projectionOf{\dimsn{i}} - \bb{k})^\top \pmb{\rho}(i,j,t)
  \end{multline}
  where $p_{ik}^{\text{track}}$ is the probability of $k$th detection being the
  right track for $i$ hypothesis. (to be computed from tracklet score)
\end{frame}

\begin{frame}
  \centering{
  \includegraphics[width=0.5\textwidth]{graphics/graphicalModelFrom61ConstVars.pdf}
}
  \begin{align}
    \Energy{ori} &= 
    %S_t^2(\projectionOf{\dimsn{i}})
    (1 - \cos({\omega}^i_{\text{det}} - \ori{i}{t})
  \end{align}
  \pause
  \begin{multline}
    \Energy{track}(\{ \relp{k}{t} \}_k, \{ \relp{k}{t-1} \}_k, \dimsn{i},
    \dimsn{j}, ) = \\
    \sum_{i=1}^{N} 
    %\sum_{t = s_i}^{e_i}
    \sum_{j = 1}^{M}
    a_j^i(t)\|\trackp{t} - \projectionOf{\invProjectionOf{\trackp{t-1}}}\|^2
  \end{multline}
  where $a_j^i(t)$ is the probability of association of $\trackp{t}$ with
  tracklet $i$.
\end{frame}

\begin{frame}
  $a_j^i(t)$ is soft occlusion dependent probability. Assume the projection of
  tracklet is given by 2D bounding box $[u^i_l, v^i_t, u^i_r, v^i_b] =
\projectionOf{\dimsn{i}}$. Approximate bounding box by ellipse
\begin{align}
\mu_i &= \frac{1}{2}\begin{bmatrix}u^i_l + u^i_r\\v^i_t + v^i_b
\end{bmatrix}\\
\Sigma_i &= \begin{bmatrix} 
\frac{2}{(u^i_l - u^i_r)^2} & 0 \\
0 & \frac{2}{(v^i_t - v^i_b)^2} 
\end{bmatrix}
\end{align}

\end{frame}
\begin{frame}
  \frametitle{The occlusion function}
  Following \cite{milan2013continuous} we model occlusion as soft continuous
  probablistic function that varies with distance from camera and distance of
  the center of projection of the object.
  \begin{align}
    f^i_{\text{occ}}(u, v, \lambda) &= \frac{N(u,v; \mu_i, \Sigma_i)}
    {1 + e^{-\frac{\lambda - \mu^{(d)}_i}{\beta}}}
    \text{where} &\\
    \beta &= \frac{\dimsn{i}_z}{2\log(49)}\\
    \mu_d &= \relp{i}{t}_z
  \end{align}
\end{frame}

\begin{frame}
  Soft occlusion modeling using can be viewed as if the traffic
  participant are being viewed as translucent objects with the probability of
  reflection as $P_{\text{reflection}} = f^i_{\text{occ}}$ . Given a point
  $(u,v)$ on the image, the probability of its association to the $i$ tracklet
  is given by
  \begin{align}
    a^i_j(t) = f^i_{\text{occ}}(u, v, \mu^{(d)}_i)\prod_{k : {\mu^{(d)}_k < \mu^{(d)}_i}}(1 -
    f^k_{\text{occ}}(u, v, \mu^{(d)}_i))
  \end{align}
  where the second term determines the probability of ray being \emph{not
  occluded} by the $k$ objects in front of the $i$th object and the first term
  is the probability of the ray being finally \emph{occluded} by the $i$
  object.
\end{frame}

\begin{frame}
  Since our occlusion function $f^i_{\text{occ}}$ is dependent upon depth as
  well, we can remove the explicit condition over $k:{\mu^{(d)}_k < \mu^{(d)}_i}$.
  \begin{align}
    a^i_j(t) = f^i_{\text{occ}}(u, v, \mu^{(d)}_i)\prod_{k}(1 - f^k_{\text{occ}}(u, v, \mu^{(d)}_i))
  \end{align}
  Also, in practice we compute this association only for the tracklets that
  have overlapping 2D bounding boxes.
  \begin{align}
    a^i_j(t) &= \begin{cases}
    f^i_{\text{occ}}
    \prod\limits_{k : (u,v) \in \projectionOfi{k}{\dimsn{k}}}
    (1 - f^k_{\text{occ}})
    & \text{if } i : (u,v) \in \projectionOf{\dimsn{i}} \\
    0 & \text{otherwise}
    \end{cases}
  \end{align}
\end{frame}

\begin{frame}
  \centering{
  \includegraphics[width=0.5\textwidth]{graphics/graphicalModelFrom61ConstVars.pdf}
}

  \begin{align}
    \Energy{lane} &= 
    \sum_{m : \text{DIST}(L_{m}(k), \pos{i}{t}) < 50}\frac{1 - \ori{i}{t} \cdot \text{TAN}(L_{m}(k),
    \pos{i}{t}) }
    {1 + exp(-q(w_{\text{road}} - \text{DIST}(L_{m}(k), \pos{i}{t})))}
  \end{align}
\end{frame}

\begin{frame}
  \centering{
  \includegraphics[width=0.6\textwidth]{graphics/graphicalModelFrom61withConstNodes.pdf}
}
\begin{align}
  \Energy{dyn-hol} &= 1 - \ori{i}{t-1} \cdot (\pos{i}{t} - \pos{i}{t-1})\\
  \Energy{dyn-ori} &= \|\ori{i}{t} - \ori{i}{t-1}\|^2\\
  \Energy{dyn-vel} &= \|(\pos{i}{t} - 2\pos{i}{t-1}) + \pos{i}{t-2}\|^2
\end{align}
\end{frame}

\begin{frame}
  \frametitle{Inference}
  \begin{itemize}
    \item Most previous works use MCMC which is slow
      \pause
    \item The number of edges $\approx$ 10-20 per frame $\approx$ 500-1000 for
      50 frame sequence
      \pause
    \item The described graph is mostly trees with a few loops
      \pause
    \item Variants of Belief propagation with damping seems a good bet.
      \pause
    \item However, traditional version of inference algorithms including BP,
      TRW-S, Dual decomposition discrete state space.
      \pause
    \item We will need simpler smooth analytical approximation of messages for
      continuous state spaces.
      \pause
    \item The approximation will need to be done for each message passing step
  \end{itemize}
\end{frame}

\begin{frame}
\begin{center}
\begin{tikzpicture}
  \node (img1) {\includegraphics[width=\textwidth]{graphics/61.png}};
  \node (img2) at (-2.5, 1.8) {\includegraphics[height=0.3\textwidth]{graphics/graphicalModelFrom61withConstNodesDirections.pdf}};
\end{tikzpicture}
\end{center}
\end{frame}

\bibliographystyle{plannat}
\bibliography{model}
\end{document}

### 2014-11-08 Paper/model.tex
Cleaned up the model.pdf to make it look more like a paper.

--- 2014-10-11 Notes/model.tex
@@
 \usepackage{amssymb}
+%%%%%%%%%%% CVPR template packages end %%%%%%%%%%%%%%
 \usepackage{verbatim} % for comment environment
@@
 % run, let it finish, and you should be clear).
-\usepackage[breaklinks=true,bookmarks=false]{hyperref}
-
-\cvprfinalcopy % *** Uncomment this line for the final submission
-
-\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
+\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+
+%\cvprfinalcopy % *** Uncomment this line for the final submission
+
+\def\cvprPaperID{489} % *** Enter the CVPR Paper ID here
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
 
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-%\ifcvprfinal\pagestyle{empty}\fi
-%\setcounter{page}{4321}
-%\DeclareMathSymbol{\Tangent}
-\DeclareMathOperator{\sech}{sech}
-\DeclareMathOperator{\poly}{poly}
-\DeclareMathOperator*{\argmin}{\arg\min}
-
-\begin{document}
-\title{Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.}
-\author{Vikas Dhiman\\
-{\tt\small vdhiman@nec-labs.com}
-\and
-Manmohan Chandraker\\
-{\tt\small manu@nec-labs.com}
-}
-\maketitle
-
-%%%%%%%%% ABSTRACT
-\begin{abstract}
-  The long term goal of this project is to identify and represent commonly 
-  occurring potentially dangerous road situations where driver can be warned 
-  about the situations. Such kind of driver assistance requires understanding
-  the state of various road scene elements. We broadly categorize the elements
-  in the scene as traffic participants (TP) and as other "scene elements" (like
-  lanes, intersections etc). 
-\end{abstract}
-
-\section{Introduction}
-  NEC has already developed a monocular camera based structure from motion
-  system which is accurate for requirements of road scene understanding. So we
-  assume that egomotion is given as an observed variable in our graphical
-  model. And we have following features to our disposal for estimating the 3D
-  poses (position + orientation) of traffic participants:
-  \begin{description}
-    \item[Ground plane] We assume that all the traffic participants lie on a common ground
-      plane. This is not particularly true for the cars that are parked off the
-      road. However, for autonomous driver assistance applications we can
-      ignore those cars.
-    \item[Detections] We assume that 2D car detections are available with tracking informations.
-    \item[Point tracks] We assume that 2D point tracks are available.
-    \item[GPS and Map information] We assume that GPS information is available
-      and we use openstreetmaps.org for pulling out local map for the current
-      car's position.
-    \item[Lane Information] We assume the lane detection works well and lane
-      information is available.
-    \item[Size prior] The distribution of size of cars follows gaussian distribution.
-    \item[Collision] A reasonable output of the system donot has any overlapping cars.
-  \end{description}
-
-\section{Notation}
 % 3D pose of the cars and ego motion
@@
 % projection function
-\newcommand{\projectionOf}[1]{\pi_{\relp{i}{t}}(#1)}
+\newcommand{\projectionOf}[1]{\pi_{\relp{i}{t}}\left(#1\right)}
+\newcommand{\projectionOft}[1]{\pi_{\relp{i}{t+1}}\left(#1\right)}
 \newcommand{\centerProj}{\bar{\pi}_{\relp{i}{t}}(\dimsn{i})}
@@
 \newcommand{\occFreeProj}[1]{\Pi_{\relp{i}{t}}(#1)}
-
-\begin{table}[h]
-  \begin{tabular}{|l|l|}
-    \hline
-    Symbol & Meaning \\
-    \hline
-    $\pos{i}{t}$ & Position of $i$th car at time $t$\\
-    $\ori{i}{t}$ & Orientation of $i$th car at time $t$\\
-     $\dimsn{i}$ & 3D bounding box of the car (dimensions)\\
-    $\state{i}{t}$ & State of car $=\{\pos{i}{t}, \ori{i}{t}, \dimsn{i}\}$\\
-    $\egop$ & Position of camera at time $t$\\
-    $\egoo$ & Orientation of camera at time $t$\\
-    $\relp{i}{t}$ & Relative car pose w.r.t. camera \\
-    $\tracklets$ & 3D points tracked on car $i$ in its own frame\\
-    $\trackp{t}$ & Projection of $\tracklets$ in camera\\
-    $\projectionOf{.}$ & Projection function for pose $\relp{i}{t}$\\
-    $\bb{i}$ & 2D bounding box of the car in image\\
-    \hline
-  \end{tabular}
-\end{table}
-
-%%%%%%%%% BODY TEXT
-\section{The Model}
-
-The objective is to find the most likely traffic participant state given various
-evidences $\mathbb{E} = \{\{\trackp{t}\}, \{\bb{i}\}, \text{lane det.}, \text{map},
-\text{GPS}\}$.
-
-Mathematically, find:
-\begin{align}
-  \{\state{i}{t}\}^* &= \arg \max P(\{\state{i}{t}\} | \mathbb{E})
-\end{align}
-
-Bayes rule
-\begin{align}
-  P(\{\state{i}{t}\} | \mathbb{E}) &=
-  \frac{1}{Z}P( \mathbb{E} | \{\state{i}{t}\})P(\{\state{i}{t}\})
-\end{align}
-
+\newcommand{\minx}{x_{\text{min}}}
+\newcommand{\miny}{y_{\text{min}}}
+\newcommand{\maxx}{x_{\text{max}}}
+\newcommand{\maxy}{y_{\text{max}}}
+\newcommand{\frontface}{F^i_\text{FF}(t)}
+
+\newcommand{\occ}[1]{o({#1})}
+\newcommand{\face}{F^i_k(t)}
+
+\newcommand{\invProjectionOf}[1]{\pi^{-1}_{\relp{i}{t}}\left(#1\right)}
+\newcommand{\occf}{f^i_{occ}(\mathbf{x}_j)}
+\newcommand{\occftot}{f_{occ}(\mathbf{x}_j)}
+\newcommand{\occft}[1]{f_{occ}(#1)}
+
+\newcommand{\ray}{\hat{\mathbf{r}}_j}
+\newcommand{\occfray}{f_{occ}(\lambda\ray)}
+\newcommand{\lambdadist}{f_{\lambda}(\trackpj{t-1}, \lambda)}
+
+\newcommand{\occfxi}{L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i)}
+\newcommand{\occfi}{L(\lambda \ray; \pos{i}{t-1}, \Sigma_i)}
+\newcommand{\assocP}{a^{(ij)}(\lambda)}
+\newcommand{\assocPk}{a^{(ij)}(\lambda_k)}
+
+\newcommand{\Ereproj}{E^{(ij)}_{\text{reproj}}}
+\newcommand{\Ptrans}{P^{(j)}_{\text{transmission}}(\lambda)}
+\newcommand{\Ptransmud}{P^{(j)}_{\text{transmission}}(\mu^{(i)}_d)}
+\newcommand{\Prefl}{P^{(ij)}_{\text{reflection}}(\lambda)}
+\newcommand{\dishort}{d_i(\mathbf{x})}
+
+\newcommand{\Lu}{L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)}
+\newcommand{\Llambda}{L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d)}
+
+\newcommand{\Gauss}{\mathcal{N}}
+\newcommand{\PropDist}{\mathcal{W}_j}
+
+\newcommand{\muijl}{\mu^{(ij)}_{\lambda}}
+\newcommand{\sigmaijl}{\sigma^{ij}_{\lambda}}
+
+\newcommand{\Sigmait}{\Sigma^{(i)^{-1}}_t}
+
+\newcommand{\muit}{\mu^(i)_t}
+\newcommand{\Sigmaic}{\Sigma'^{(i)^{-1}}_c}
+
+\newcommand{\muic}{{\mu^(i)_c}}
+\newcommand{\Sigmaicf}{\Sigma^{(i)^{-1}}_c}
+
+\newcommand{\muiu}{\mu^{(i)}_t}
+\newcommand{\Sigmaiu}{\Sigma^{(i)^{-1}}_u}
+
+\newcommand{\xt}{\mathbf{x}_t}
+\newcommand{\xc}{\mathbf{x}_c}
+
+\newcommand{\Rctot}{R}
+\newcommand{\tctot}{t}
+
+\newcommand{\tcmut}{t'}
+
+\newcommand{\Beizer}{B\'eizer }
+
+\newcommand{\LaneUncertainty}[1]{\Sigma_{L_m}(#1)}
+\newcommand{\projOnLane}[1]{\pi_{L_m(k)}(#1)}
+
+% Pages are numbered in submission mode, and unnumbered in camera-ready
+%\ifcvprfinal\pagestyle{empty}\fi
+%\setcounter{page}{4321}
+%\DeclareMathSymbol{\Tangent}
+\DeclareMathOperator{\sech}{sech}
+\DeclareMathOperator{\poly}{poly}
+\DeclareMathOperator*{\argmin}{\arg\min}
+
+\begin{document}
+\title{Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.}
+\author{Vikas Dhiman\\
+  University of Michigan\\
+  Ann Arbor, MI, USA\\
+{\tt\small dhiman@umich.edu}
+\and
+Manmohan Chandraker\\
+NEC Laboratories America, Inc.\\
+Cupertino, CA, USA\\
+{\tt\small manu@nec-labs.com}
+\and
+Jason J Corso\\
+  University of Michigan\\
+  Ann Arbor, MI, USA\\
+{\tt\small jjcorso@eecs.umich.edu}
+}
+\maketitle
+
+%%%%%%%%% ABSTRACT
+\begin{abstract}
+  TODO: Write abstract
+  \vspace{4cm}
+\end{abstract}
+
+\section{Introduction}
+
+\begin{itemize}
+  \item Introduce the problem
+  \item Describe our approach
+  \item Contrast with Milan's work
+  \item Contrast with Andreas Geiger's work
+  \item Highlight the contributions
+\end{itemize}
+\vspace{10cm}
 \begin{figure}[t]
@@
 
+\section{Related Work}
+TODO:
+\vfill
+\pagebreak
+Related work continued
+\vspace{15cm}
+
+\section{Problem Definition}
+TODO:
+\vspace{4cm}
+
+\section{Notation}
+
+\begin{table}[h]
+  \begin{tabular}{|l|l|}
+    \hline
+    Symbol & Meaning \\
+    \hline
+    $\pos{i}{t}$ & Position of $i$th car at time $t$\\
+    $\ori{i}{t}$ & Orientation of $i$th car at time $t$\\
+     $\dimsn{i}$ & 3D bounding box of the car (dimensions)\\
+    $\state{i}{t}$ & State of car $=\{\pos{i}{t}, \ori{i}{t}, \dimsn{i}\}$\\
+    $\egop$ & Position of camera at time $t$\\
+    $\egoo$ & Orientation of camera at time $t$\\
+    $\relp{i}{t}$ & Relative car pose w.r.t. camera \\
+    $\tracklets$ & 3D points tracked on car $i$ in its own frame\\
+    $\trackp{t}$ & Projection of $\tracklets$ in camera\\
+    $\projectionOf{.}$ & Projection function for pose $\relp{i}{t}$\\
+    $\bb{i}$ & 2D bounding box of the car in image\\
+    \hline
+  \end{tabular}
+\end{table}
+
+%%%%%%%%% BODY TEXT
+\section{The Model}
+
+The objective is to find the most likely traffic participant (TP) state given
+various evidences $\mathbb{E} = \{\{\trackp{t}\}, \{\bb{i}\}, \text{lane det.},
+\text{map}, \text{GPS}\}$.
+
+Mathematically, find:
+\begin{align}
+  \{\state{i}{t}\}^* &= \arg \max P(\{\state{i}{t}\} | \mathbb{E})
+\end{align}
+
+Bayes rule
+\begin{align}
+  P(\{\state{i}{t}\} | \mathbb{E}) &=
+  \frac{1}{Z}P( \mathbb{E} | \{\state{i}{t}\})P(\{\state{i}{t}\})
+\end{align}
+
 Assume conditional independence according to graphical model in
@@
 
-\subsection{Collision energy}
-
-Bhattacharya coefficient $\int_a^b\sqrt{p(x)q(x)}dx$ is a measure of similarity of two
-distributions $p(x)$ and $q(x)$. If we represent traffic participants as
-gaussians in BEV, then similarity is a measure of collision. Exactly
-overlapping distribution results in coefficient as 1. The analytical form of
-Bhattacharya coefficient has been taken from
-\url{http://like.silk.to/studymemo/PropertiesOfMultivariateGaussianFunction.pdf}
-
-\begin{align}
-  \label{eq:collisionEnergyHellingerDistance}
-  \EnergyCol &=
-  \frac{|\Sigma_i|^\frac{1}{4}|\Sigma_j|^\frac{1}{4}}
-  {|P|^\frac{1}{2}}
-  e^{-\frac{1}{8}
-    \left(\pos{i}{t} - \pos{j}{t}\right)^\top
-    P^{-1}
-    \left(\pos{i}{t} - \pos{j}{t}\right)
-    }
-\end{align}
-where 
-\begin{align}
-  P &= \frac{1}{2}\Sigma_i + \frac{1}{2}\Sigma_j\\
-\Sigma_i^{-1} &= R^\top_{\ori{i}{t}} \begin{bmatrix} 2/l^i & 0 \\ 0 & 2/w^i \end{bmatrix}
-R_{\ori{i}{t}}
-\end{align}
-
-\begin{comment}
-  \subsection{Bounding box energy}
-  \label{sec:totalBBoxEnergy}
-  With abuse of notation we represent the four sides of hypothesized bounding
-  box by $\projectionOf{\dimsn{i}}$ and detected bounding box by $\bb{i}$.
-  Suppose the bounding box $i$ is occluded by bounding box $i$ then the
-  bounding box energy becomes a pairwise term.
-
-  \begin{multline}
-    \pEnergy{occ}(\relp{i}{t}, \dimsn{i}, \relp{j}{t}, \dimsn{j}) = \\
-    \sum_s \rho^{ijs}(t)\projectionOf{\dimsn{i}}_s - \bb{i}_s
-               %\sum_{i=1}^N \sum_{t=s_i}^{e_i}
-    %\sum_kp_{ik}^{\text{track}}(\projectionOf{\dimsn{i}} - \bb{k})^\top \pmb{\rho}(i,j,t)
-  \end{multline}
-  where $\rho^{ijs}(t)$ is the visibility fraction of the side $s$ of the
-  bounding box. We need to compute visibility fraction we need to compute the
-  occlusion mask which is explained in next few sections.
-
-  \subsubsection{Visible faces from bounding boxes}
-
-  \begin{figure}[h]
-    \includegraphics[width=\columnwidth]{graphics/maxFacesVisible.pdf}
-    \caption{Only three faces can be visible out of six faces of a bounding
-    box.}
-  \end{figure}
-
-  \newcommand{\minx}{x_{\text{min}}}
-  \newcommand{\miny}{y_{\text{min}}}
-  \newcommand{\maxx}{x_{\text{max}}}
-  \newcommand{\maxy}{y_{\text{max}}}
-  \newcommand{\frontface}{F^i_\text{FF}(t)}
-  Each bounding box has 6 faces of which only 3 can be visible.
-  Sort the vertices in increasing order of depth. The closest vertex has three
-  neighboring faces. All the faces that are visible must be a subset of these
-  three. Use first three vertices to
-  define the front face (say $\frontface$). Also identify the four 3D points
-  that correspond to min/max in x and y direction in the image. If all min-max 4
-  points are same as vertices of $\frontface$, then we have only one plane
-  visible. If $\{\minx, \maxx\} \not\subset \frontface \land \{\miny, \maxy\}
-  \not\subset \frontface$ then we have 3 planes visible. Otherwise we have just
-  two planes visible. Let number of planes visible be $n_F$.
-
-  \begin{align}
-    n_F &= \begin{cases}
-    1 & \text{if }\{\minx, \maxx, \miny, \maxy\} =
-    \frontface\\
-    2 & \text{else if }\{x_{\text{min}}, x_{\text{max}}\} \subset \frontface \lor
-    \{y_{\text{min}}, y_{\text{max}}\} \subset \frontface
+\section{Modeling traffic participants}
+\label{sec:TPmodel}
+Following standard model of occupancy in 3D reconstruction community, we model
+the TP's as high occupancy regions in space. We model the
+uncertainty in occupancy equivalent of transparency i.e. the regions that are
+more certain to be occupied are viewed as relatively more opaque then other
+regions. Based on this intuition we model TP's translucent
+ellipsoids whose opacity is maximum at the center and drops off away from the
+center. More specifically we model, the occupancy of a TP as a
+logistic function,
+
+\begin{align}
+   \occf = L(\mathbf{x}; \pos{i}{t}, \Sigma_i)
+\end{align}
+where $L(.)$ is the logistic function defined by
+\begin{align}
+  L(\mathbf{x}; \pos{i}{t}, \Sigma_i) = \frac{1}{
+    1 + e^{-k(1 - d(\mathbf{x},\pos{i}{t}))}
+    }
+\end{align}
+where $d(\mathbf{x},\pos{i}{t}) =
+(\mathbf{x}-\pos{i}{t})^\top\Sigma_i(\mathbf{x}-\pos{i}{t})$ and $k =
+10\ln{49}$. $k$ is chosen such that $L(.) = 0.98$ when $d(.) =
+0.9$. $\Sigma_i$ determines the spread of the ellipsoid and depends on the
+dimensions of the TP. Please refer to supplementary material 
+for computation of $\Sigma_i$ from TP's dimensions.
+
+We model the probability of a point $\mathbf{x}_j$ on a object $i$ getting successfully
+observed in a camera image at point $\trackpj{t}$ is dependent up two factors,
+(1) reflection and (2) transmission through intermediate space. The reflection
+part ensures that there is an object to reflect a point at a certain region in
+the 3D space while transmission part models occlusion.
+\begin{align}
+  P^{(ij)}_{\text{observation}} = P^{(ij)}_{\text{reflection}}P^{(j)}_{\text{transmission}}
+\end{align}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Reflection probability}
+For Lambertian reflection we replace the surface normal with the
+gradient of occupancy.
+%
+\begin{align}
+  \Prefl = (\max \{0, \nabla \occf^\top
+  \hat{\mathbf{r}_j}\})^2
+\end{align}
+%
+where $\ray =
+\frac{K^{-1}\trackpj{t}}{\|K^{-1}\trackpj{t}\|}$ is unit vector in the
+direction of ray. The gradient in the direction opposite to ray yields -ve
+probability which needs to be clipped off. Squaring the function keep it
+smooth near zero.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Transmission probability}
+A model for transmission of light through a material of thickness $x$,
+density $\rho$ and opacity $k_o$ is given by Beer-Lambert law 
+%
+\begin{align}
+  I(x) = I_0e^{-k_o\rho x}
+\end{align}
+%
+
+Since both opacity and density are represented by the occupancy function
+$\occftot = \sum_i \occf$, and also the domain of our $\occftot$ is $[0, 1]$ instead of $[0,
+\infty]$ as in case of $k_o$; we replace $e^{-k_o\rho}$ by the transparency
+function $1 - \occftot$. So the transmission probability over a small distance
+$d\lambda$ is given by
+%
+\begin{align}
+  P_{\text{transmission}}(\lambda + d\lambda) =
+  P_{\text{transmission}}(\lambda) (1-\occftot)^{d\lambda}
+\end{align}
+%
+
+For a given 3D point $\mathbf{x}_j = \lambda \ray$, the probability that the
+point $\trackpj{t}$ is reflected from a distance $\lambda$ is given by
+
+\begin{align}
+  %P^{(j)}_{\text{observation}}(\lambda) &= P_{\text{reflection}}
+  \Ptrans &=
+  \prod_{0}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda} %\\
+  %= \max \{ 0, (\nabla f_{occ}&(\lambda \ray)^\top \ray) \}
+  %\prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
+  \label{eq:ptrans-integral}
+\end{align}
+where $\prod_{0}^{\lambda}$ represents the \emph{product integral} from $0$ to
+$\lambda$.
+
+In practice, the integral for transmission probability
+\eqref{eq:ptrans-integral} is difficult to compute even numerically. So we
+choose a product of sigmoid function that approximates the behaviour of
+transmission probability,
+%
+\begin{align}
+\label{eq:evalCumulativePtrans}
+  \Ptrans &= \prod_i L_u(\trackp{t}; \muiu,\Sigmaiu)L_{\lambda}(\lambda; \mu^i_d)
+\end{align}
+%
+where $L_u(.)$ is sigmoid in image domain with $\mu^i_u$ and $\Sigma^i_u$
+representing the elliptical projection of $i^{th}$ TP.
+$L_{\lambda}(.)$ is sigmoid in the depth domain with $\mu^i_d$ as the mean
+depth of the $i^{th}$ TP.
+%
+\begin{align}
+  L_u(\mathbf{u}; \muiu,\Sigmaiu) &= \frac{1}{
+    1 + e^{-k_u(1 - (\mathbf{u} - \muiu)^\top\Sigmaiu(\mathbf{u} -
+    \muiu))}
+  }
   \\
-    3 & \text{else if }\{x_{\text{min}}, x_{\text{max}}\} \not\subset \frontface \land
-    \{y_{\text{min}}, y_{\text{max}}\} \not\subset \frontface
-    \end{cases}
-    \label{eq:nfaces}
-  \end{align}
-
-  First vertex restrict possible visible faces to three faces. If $n_F = 3$,
-  then all three of these faces are visible. If $n_F = 2$, use second closest
-  vertex to restrict visible faces to just two. If $n_F = 3$, then front face 
-  $\frontface$ is the only visible face.
-\end{comment}
-
-\newcommand{\occ}[1]{o({#1})}
-\newcommand{\face}{F^i_k(t)}
-\begin{comment}
-  \subsubsection{Occlusion mask}
-  % Initialize empty mask polygon $\occ{0}$ at depth $d=0$.
-  % \begin{itemize}
-  %   \item Sort all cars in increasing order of depth
-  %   \item for each car $i$ in the sorted list
-  %     \begin{itemize}
-  %       \item Update mask polygon: \\
-  %         $\occ{\relpz{i}{t}} = \occ{d} \cup \projectionOf{\dimsn{i}}$
-  %       \item $d = \relpz{i}{t}$
-  %     \end{itemize}
-  % \end{itemize}
-
-  % Sort all planes in increasing order of depth.  This yields a cumulative
-  % occlusion mask function
-  Occlusion mask is a function that takes the relative depth $d$ from the car
-  camera and returns a binary mask that represents occlusions untill that depth.
-  Near to the camera occlusion mask is all empty (all zeros) and more occlusions
-  get added to the mask with distance.
-
-  \begin{align}
-    \occ{d} &= \begin{cases}
-    \phi & \text{if } 0 < d \le \relpz{1}{t}\\
-    \cup_{i=1}^j \projectionOf{F^i} & \text{if } \relpz{1}{t} < d \le \relpz{j+1}{t}
-    \end{cases}
-    \label{eq:occlusionmask}
-  \end{align}
-
-  where $\relpz{j}{t}$ is the depth of the $j$th traffic participant when sorted
-  by increasing depth.
-
-  \subsubsection{Algorithm to get faces based occlusion mask}
-  \label{sec:occlusionMaskFromOptVector}
-
-  This is an algorithm to compute occlusion mask Eq.\eqref{eq:occlusionmask}. We
-  represent the occlusion mask as a set of polygons.
-
-  Initialize empty mask polygon $\occ{0}$ at depth $d=0$.
-  \begin{enumerate}
-    \item Collect visible faces using Eq.\eqref{eq:nfaces} for all cars
-    %\item for each face get its closest and farthest vertex to the camera.
-    \item Create a sorted list of faces
-    % \item Create a sorted binary tree of
-    %   faces indexed by closed vertices.
-    \item Loop over list of sorted visible faces
-      \begin{enumerate}
-        \item Get the face(s) $\{\face\}$ closer to camera than this face
-        \item Add the faces to mask polygon (if not already added): \\
-          $\occ{\relpz{i}{t}} = \occ{d} \cup \projectionOf{\face}$
-        \item $d = \relpz{i}{t}$
-      \end{enumerate}
-  \end{enumerate}
-
-  To get the occlusion mask for a face use the farthest vertex of the face to
-  query $\occ{.}$.
-
-  \subsubsection{Visibility fraction of a side}
-  Let the center of the projected hypothesized bounding box be $\centerProj$ and
-  the four corners be $\{\cornerProj{k}\}_{k=1}^{4}$ . Each side and the center
-  of the bounding box form a triangle, for example $\triangleProj{1,2} =
-  \{\cornerProj{1}, \cornerProj{2}, \centerProj\}$. We take the visibility of
-  this triangle as a visibility of the side $s = (1,2)$. Hence the visibility
-  fraction of side is given by
-  \begin{align}
-    \rho^{ijs}(t) = \frac{\|\triangleProj{s} \setminus \occ{\relpz{i}{t}}\|}
-                         {\|\triangleProj{s}\|}
-     \label{eq:bboxEnergyFromOccMask}
-  \end{align}
-\end{comment}
-
-\begin{comment}
-  \subsection{Occlusion free projection}
-  Occlusion free projection can be obtained by applying the precomputed occlusion
-  mask to the face projection.
-  \begin{align}
-    \occFreeProj{\face} &= \projectionOf{\face} \setminus
-    \occ{\relpz{i}{t}}
-  \end{align}
-
-  \subsection{Perspective-visibility fraction}
-
-  Apart from occlusion, we want to account for the perspective affects. When an 
-  objects perspective projection is too small, detection and all related
-  evidences deteriorate. One way of this is to find out the projection ratio. In
-  fact, we can consolidate projection ratio and occlusion ratio in one term if
-  we consider the projection of 3D bounding box planes instead of the entire
-  bounding box.
-
-  \begin{align}
-    \rho^i_t &= \sum_{k=1}^{n_F}\frac{\relpz{i}{t}^2\|\occFreeProj{F^i_k(t)}\|}{f^2\|F^i_k(t)\|}
-  \end{align}
-
-  where $\occFreeProj{.}$ again means occlusion free projection. $f$ is the
-  focal length of the camera so that $\frac{f^2}{\relpz{i}{t}^2}\|F^i_k(t)\|$ is
-  the area of projected plane if there were no perspective effects.
-\end{comment}
-
-\subsection{Continous Point tracks energy with occlusion}
+  L_{\lambda}(\lambda; \mu^i_d) &= \frac{1}{
+    1 + e^{-k_d(\lambda - \mu^i_d)}
+}
+\end{align}
+%
+
+\begin{comment}%% Comment
+  A product integral is a simple integral in log domain
+  \begin{align}
+    \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} =
+    e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
+  \end{align}
+\end{comment}%% Comment
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Energies}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+We explain energies in this section
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Point tracks energy with occlusion}
 \label{sec:totalContPtTracksEnergy}
-We want continuous modeling of occlusion. We model occlusion as a opacity
-term. Based on the dimensions $\dimsn{i}$, we can
-compute the covariance matrix $\Sigma_i$ as shown in Sec. 
-\ref{sec:sigmacomputation}
-
-So far we have modeled our point tracks energy in a non-smooth way:
-\newcommand{\invProjectionOf}[1]{\pi^{-1}_{\relp{i}{t-1}}(#1)}
+We model continuous point tracks energy with explicit occlusion reasoning as
+the expected re-projection error over the association probability,
+
 \begin{multline}
@@
     \sum_{j = 1}^{M}
-    \int_1^\infty a_j^i(\lambda)\|\trackpj{t} - \projectionOf{\invProjectionOf{\trackpj{t-1}}}\|^2 d\lambda
-\end{multline}
-
-The tricky part here is inverse projection $\invProjectionOf{.}$ . When we
-project an image point back to 3D we get a ray $\lambda K^{-1}\trackpj{t-1}$
-which is ambiguous up to a scale factor $\lambda$. Using our hypothesized 3D
-layout of the scene we can estimate this scale factor, we
-can compute a distribution over the $\lambda$. 
+    \int_1^\infty \assocP\Ereproj(\lambda) d\lambda
+\end{multline}
+where $\assocP$ is the association probability of
+$j$\textsuperscript{th} point with $i$\textsuperscript{th} TP at depth $\lambda$
+and $\Ereproj(\lambda)$ is the re-projection error given by
+%
+\begin{align}
+  \assocP &= \Prefl\Ptrans\\
+  \Ereproj(\lambda) &= \left\|\trackpj{t+1} - \projectionOft{\invProjectionOf{\trackpj{t}, \lambda}}\right\|^2 .
+  \label{eq:reprojerror}
+\end{align}
+
+The  $\projectionOf{.}$ and $\invProjectionOf{.}$ denote the projection and
+inverse projection functions that project 3D point to camera image and vice
+versa. Note that inverse projection $\invProjectionOf{.}$ depend on both the
+point $\trackp{t}$ and the unknown depth $\lambda$. Also note that the inverse projection is dependent on TP pose at time $t$ while the projection depends on pose at time $t+1$ which can be different.
+
+\begin{comment}
   \subsubsection{Occupancy function}
   Assuming occupancy to be a
-probability distribution over 3D space. For each traffic participant the
+  probability distribution over 3D space. For each TP the
   occupancy is modeled as a logistic function 
-\newcommand{\occf}{f^i_{occ}(\mathbf{x})}
   \begin{align}
@@
   0.9$
-
-We model the probability of a point being projected to a camera is dependent
-up two factors, (1) reflection and (2) transmission through intermediate
-space. 
-\subsubsection{Reflection probability}
-For lambertian reflection we replace the surface normal with the
-gradient of occupancy.
-\begin{align}
-  P_{\text{reflection}} = \sum_i (\max \{0, \nabla \occf^\top
-  \hat{\mathbf{r}_j}\})^2
-\end{align}
-where $\hat{\mathbf{r}_j} =
-\frac{K^{-1}\trackpj{t-1}}{\|K^{-1}\trackpj{t-1}\|}$ is unit vector in the
-direction of ray. The gradient in the direction opposite to ray yields -ve
-probability which needs to be clipped off. Squaring the function keep it
-smooth near zero.
-
-\subsubsection{Transmission probability}
-A model for transmission of light through a material of thickness $x$,
-density $\rho$ and opacity $k_o$ is given by Beer-Lambert law 
-\begin{align}
-  I(x) = I_0e^{-k_o\rho x}
-\end{align}
-
-Since both opacity and density are represented by our occupancy function
-$\occf$, and also the domain of our $\occf$ is $[0, 1]$ instead of $[0,
-\infty]$ as in case of $k_o$; we replace $e^{-k_o\rho}$ by our transparency
-function $1 - \occf$. So the transmission probability over a small distance
-$d\lambda$ is given by
-\begin{align}
-  P_{\text{transmission}}(\lambda + d\lambda) =
-  P_{\text{transmission}}(\lambda) (1-\occf)^{d\lambda}
-\end{align}
-\newcommand{\ray}{\hat{\mathbf{r}}_j}
-\newcommand{\occfray}{f_{occ}(\lambda\ray)}
-
-For our given ray $\mathbf{x}_j = \lambda \ray$, the probability that the point
-$\trackpj{t-1}$ is reflected from a distance $\lambda$ is given by
-
-\newcommand{\lambdadist}{f_{\lambda}(\trackpj{t-1}, \lambda)}
-\begin{align}
-  \lambdadist &= P_{\text{reflection}}
-  \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} %\\
-  %= \max \{ 0, (\nabla f_{occ}&(\lambda \ray)^\top \ray) \}
-  %\prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
-\end{align}
-where $\prod_{0}^{\lambda}$ represents the \emph{product integral} from $0$ to
-$\lambda$. A product integral is a simple integral in log domain
-\begin{align}
-  \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} =
-  e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
-\end{align}
-
   % Once we have our distribution over $\lambda$, $\lambdadist$ we can compute the
@@
   % $\lambda$. Let
-
-\subsubsection{Reprojection error}
-
-\begin{align}
-  f^{i}_{reproj}&(\trackpj{t-1}, \lambda) =
-  \projectionOf{\invProjectionOf{\trackpj{t-1}}}\\
-  %&= K(R^i_t ((R^i_{t-1})^\top\lambda \ray - (R^i_{t-1})^\top T_{t-1}) + T_{t})\\
-  &= \frac
-  {p_{1:2}\lambda + q_{1:2}}
-  {p_{3}\lambda + q_{3}}
-\end{align}
-where $p_{1:3} = KR^i_t(R^i_{t-1})^\top\ray$ and
-$q_{1:3} = KR^i_t(R^i_{t-1})^\top T_{t-1} + KT_t$
-
-Now that we have an association from TP $i$ to point track $j$ through
-$\lambda$, we can come up with an association probability
-\newcommand{\occfxi}{L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i)}
-\newcommand{\occfi}{L(\lambda \ray; \pos{i}{t-1}, \Sigma_i)}
-\newcommand{\assocP}{a^{i}_{j,t-1}(\lambda)}
-\newcommand{\assocPk}{a^{i}_{j,t-1}(\lambda_k)}
-\begin{align}
-   \assocP &= \frac{(\max \{ 0, \nabla \occf^\top
-\ray \})^2 }{P_{\text{reflection}}}\lambdadist\\
-&=(\max \{ 0, \nabla \occf^\top \ray \})^2
-  \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
-\end{align}
-
-Note that this fraction although called association probability does not
-capture the entire information that we have available for compute association
-of points to tracks. This above fraction is the association probability given 
-the hypothesized parameters of traffic participant model. Given that a point is
-observed on the image the sum of probability marginalized over other parameters
-must be one i.e.
-\begin{align}
-    \sum_{i = 1}^N
-    \int_1^{\infty}
-    \assocP d\lambda = 1
-\end{align}
-
-To compute the association probability between traffic participant $i$ and
-point track $j$ we must use re-projection error as well. When the association
-$i$ and $j$ is right and the point of reflection is at depth $\lambda$ the
-re-projection error must be zero, otherwise the error becomes a measure of
-distance from the true solution:
-
-\newcommand{\Ereproj}{E^{(ij)}_{\text{reproj}}}
-\begin{align}
-  \Ereproj(\lambda) = \|\trackpj{t} - f^i_{reproj}(\trackpj{t-1}, \lambda)\|^2
-\end{align}
-
-The error terms can be converted to probability domain by considering the error
-term as negative log of probablity
-
-\begin{align}
-  P^{(ij)}_{\text{assoc by reproj}}(\lambda) = \frac{1}{\sqrt{2\pi}}\exp(-\Ereproj(\lambda))
-\end{align}
-
-Using both the evidence terms we can write probability of association as
-\begin{align}
-  P^{(ij)}_{\text{assoc}} \propto \int_0^{\infty} \assocP \frac{1}{\sqrt{2\pi}}\exp(-\Ereproj(\lambda))d\lambda
-  \label{eq:prob-assoc}
-\end{align}
-
-However, for estimating the overall energy we just need to compute the expected
-value of the re-projection error for given parameters, i.e.
-
-\begin{multline}
-  \Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i,\{ \dimsn{i} \}_i) = \\
-    \sum_{i = 1}^N
-    \sum_{j = 1}^{M}
-    \int_1^{\infty}
-    a^i_{j,t-1}(\lambda) 
-    \|\trackpj{t} - f^i_{reproj}(\trackpj{t-1}, \lambda)\|^2
-    d\lambda
-\end{multline}
-
-If the aim is to find the best possible association, it is easier as we need to
-to compute the association that minimizes the expected re-projection error for
-point $j$. It remains to be seen that how the minima of following expression relates to minima of \eqref{eq:prob-assoc}
-
-\begin{align}
-  i^* = \argmin_{i=1}^N \int_0^\infty \assocP \Ereproj(\lambda) d\lambda
-\end{align}
-
-Since the computation of $\assocP$ entirely depends on hypothesized parameters,
-it severely limits the applicability of this method outside this kind of
-parameterized model.
-
+\end{comment}
+
+\begin{comment}
   \subsubsection{Approximations}
-\newcommand{\Ptrans}{P_{\text{transmission}}}
-\newcommand{\Prefl}{P^i_{\text{reflection}}}
-\newcommand{\dishort}{d_i(\mathbf{x})}
-
-Reflection probability of $i$th traffic participant is easy to compute
+  Reflection probability of $i$th TP is easy to compute
   analytically 
@@
   \end{align}
-is the distance of the centre of the traffic participant from the camera.
+  is the distance of the centre of the TP from the camera.
 
@@
 
-\newcommand{\Lu}{L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)}
-\newcommand{\Llambda}{L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d)}
   \begin{multline}
@@
   The integral in the above expression is computed numerically.
-
-\subsection{Numerical integration}
-Numerical integration is possible by computed by sampling. Samples need to be
-generated from the association probability $\assocP$ for a given $j$. We take
-proposal distribution to be a GMM with modes around probable reflection points.
-The weights of all Gaussians in the mixture are proportional to the distance of
-the point $j$ from projection of ellipsoid centre i.e. 
-\begin{align}
-  A_{ij} = \frac{1}{Z_j}\exp(-(\trackpj{t} - \mu^i_u)^\top\Sigma_u^i(\trackpj{t} - \mu^i_u))
-\end{align}
-where $Z_j = \sum_{i=1}^N A_{ij}$ and $\mu^i_u$ and $\Sigma_u^i$ are described in \eqref{eq:muiudef} and \eqref{eq:sigmauidef} respectively.
-The range of Gaussian $G_i$
-must be in the interval $[\|\relp{i}{t}\|, \|\relp{i}{t}\| -
-\sqrt{3}\max(\dimsn{i})]$. Hence we take the mean as $\|\relp{i}{t}\| -
-\frac{\sqrt{3}}{2}\max(\dimsn{i})$ and variance as
-$\frac{1}{3}\max(\dimsn{i})^2$. The distribution from which we sample is 
-\newcommand{\Gauss}{\mathcal{N}}
-\newcommand{\PropDist}{\mathcal{W}_j}
-\begin{align}
-  \PropDist(\lambda) = \sum_i A_{ij} \Gauss(\lambda; \|\relp{i}{t}\| -
-  \frac{\sqrt{3}}{2}\max(\dimsn{i}), \frac{1}{\sqrt{3}}\max(\dimsn{i}))
-\end{align}
-And the numerical integral with $K$ samples is computed by
-\begin{align}
-    \int_1^{\infty}
-    \assocP
-    \Ereproj(\lambda)
-    d\lambda
-    =
-    \frac{1}{K}\sum_k \Ereproj \frac{\assocPk}{\PropDist(\lambda_k)}
-\end{align}
-where $\lambda_k$ is the $k$th sample drawn from $\PropDist(\lambda)$.
-
-\begin{comment}
-  %%%%%%%%%%%%%%%% Analytical attempt to integration %%%%%%%%%%%%%%%%%%%%%
-  \begin{align}
-
-    E^i_{\text{reproj}}(\lambda) &= \left\|\trackpj{t} - \frac{p_{1:2}\lambda +
-  q_{1:2}}{p_3\lambda + q_3}\right\|^2\\
-  &= \frac{(p_1\lambda + q_1 - u_{j1}(t))^2 + (p_2\lambda + q_2 - u_{j2}(t))^2}
-  {(p_3\lambda + q_3)^2}\\
-  &= \frac{a\lambda^2 + b\lambda + c}{(p_3\lambda + q_3)^2}
-  \end{align}
-  where $a = p_1^2 + p_2^2$, $b = 2p_1(q_1 - u_{j1}(t)) + 2p_2(q_2 - u_{j2}(t))$
-  and $c = (q_1 - u_{j1}(t))^2 + (q_2 - u_{j2}(t))^2$
-
-  So, in terms of $\lambda$ we have the integrand as
-  \begin{multline}
-    \int_1^\infty
-    \prod_i (1 +
-    \tanh(\poly^{(1)}_{ij1}(\lambda)))\sech^4(\poly^{(2)}_{ij2}(\lambda))\\
-    (\max\{ 0, \poly^{(2)}_{ij3}(\lambda) \})^2
-    \frac{\poly^{(2)}_{ij4}(\lambda)}{(\poly^{(1)}_{ij5}(\lambda))^2}d\lambda
-  \end{multline}
-  where $\poly^{(n)}_{ijk}$ denotes a polynomial $k$ of order $n$ dependent upon $i$th
-  traffic participant and $j$th point. This integrand is still too difficult to
-  be solved or approximated analytically.
-
-  We approximate the expression,
-
-  \begin{multline}
-    \prod_i \Llambda
-  \sech^4\left(\frac{k}{2}\dishort\right)(\max\{ 0, \nabla k\dishort^\top\ray \})^2
-  \end{multline}
-
-  with a
-  gaussian with mean at $\mu^{ij}_{\lambda} : d_i(\mu^{ij}_{\lambda}\ray) = 0$
-  standard deviation as $\sigma^{ij}_{\lambda} =
-  \frac{\pi}{2\sqrt{3}kd(\mu^{ij}_{\lambda}\ray, \pos{i}{t-1})}$  and magnitude as the
-  expression computed at mean. An integrand of the form
-  \begin{align}
-    \frac{\poly^{(2)}_{ij4}(\lambda)}{(\poly^{(1)}_{ij5})^2}
-      e^{\frac{- (\lambda -
-  \mu^{ij}_{\lambda})^2}{\sigma^{ij}_{\lambda}}}
-  \end{align}
-   is integrable analytically by parts.
-
-   \newcommand{\muijl}{\mu^{ij}_{\lambda}}
-   \newcommand{\sigmaijl}{\sigma^{ij}_{\lambda}}
-   \begin{align}
-   \int_1^\infty \frac{a\lambda^2 + b\lambda + c}{(p_3\lambda + q_3)^2}e^{\frac{- (\lambda -
-  \mu^{ij}_{\lambda})^2}{\sigma^{ij}_{\lambda}}}d\lambda
-   \end{align}
-   Substituting $y = \frac{\lambda - \mu^{ij}_{\lambda}}{\sigma^{ij}_{\lambda}}$
-
-   \begin{align}
-     \int_1^\infty \frac{a_y y^2 + b_yy + c_y}
-     {(p_{3y}y + q_{3y})^2}e^{-y^2}dy
-   \end{align}
-   where $a_y = a(\sigmaijl)^3$, $b_y = (2a\muijl + b)(\sigmaijl)^2$ and $c_y =
-   (2a(\muijl)^2 + b\muijl + c)\sigmaijl$ and $p_{3y} = \sigmaijl p_3$ and
-   $q_{3y} = p_3\muijl + q_3$
-
-  % \subsubsection{Sandwich of ellipsoids model}
-  % 
-  % \begin{enumerate}
-  %   \item Model $\occf$ as
-  %     sigmoid over ellipse instead of a gaussian.
-  %     \begin{align}
-  %       \occf = \frac{1}{
-  %       1 + e^{-(\mathbf{x} - \pos{i}{t})^\top
-  %         \Sigma_i (\mathbf{x} - \pos{i}{t}))}}
-  %     \end{align}
-  %   \item To get the intuition of this occupancy function imagine the traffic
-  %     participant as layered ellipsoid. The innermost ellipsoid has very high
-  %     probability (approx 1) of being occupied. The outermost ellipsoid has very
-  %     low probability (approx 0) of being occupied. We will just consider the
-  %     occupancy interplay within these two ellipsoids.
-  %   \item Project outer ellipsoids of all TP's on the image.
-  %   \item Consider the ellipses that bound the track point $\trackpj{t-1}$.
-  %   \item For each ellipse do
-  %     \begin{itemize}
-  %       \item Case 1: The ray intersects inner ellipse
-  %         Now the ray intersects both inner and outer ellipse
-  %         Compute the intersection points on both the ellipses
-  %         Compute the gradient function $\nabla\occf^\top \ray$ at
-  %         the mid point of the two intersections. Use this as the magnitude of
-  %         gaussian mixture component centered at the mid point of intersections
-  %         and spread such that 97 percentile of probability mass of guassian is
-  %         within the intersection points. With the same parameters model the
-  %         transimission probability with product of logistic function $L(.)$.
-  %       \item Case 2: The ray do not intersects inner ellipse.
-  %         The ray just passes through the outer ellipse. Find the point on the
-  %         ray closest to the center of the ellipse. Compute gradient function
-  %         at the closest point, which will be again used as the magnitude of
-  %         gaussian mixture component centered at the closest point and spread
-  %         such that 97 percentile of probabiltiy mass of gaussian is within the
-  %         two intersection points of the ellipse. With the same parameters model
-  %         the transimission probability with product of sigmoids.
-  %     \end{itemize}
-  %   \item Now this approximated $\lambdadist = \sum N(.) \prod (1 - L(.))$ can
-  %     be used in integrating the error over $\lambda$.
-  % \end{enumerate}
-  \newpage
-
-  \clearpage
-  %%%%%%%%%%%%%%%% Analytical attempt to integration %%%%%%%%%%%%%%%%%%%%%
 \end{comment}
 
-\subsubsection{Sigma of ellipsoid}
-\label{sec:sigmacomputation}
-
-\newcommand{\Sigmait}{\Sigma^i_t}
-\newcommand{\muit}{\mu^i_t}
-\begin{align}
-  \muit &= \begin{bmatrix}
-  0& 0& \frac{h}{2}
-  \end{bmatrix}^\top\\
-  \Sigmait &= \begin{bmatrix}
-    \frac{4}{l^2} & 0 & 0 \\
-    0 & \frac{4}{w^2} & 0 \\
-    0 & 0 & \frac{4}{h^2}
-  \end{bmatrix}
-\end{align}
-
-In tracklet coordinates the equation of ellipsoid is 
-\newcommand{\xt}{\mathbf{x}_t}
-\newcommand{\xc}{\mathbf{x}_c}
-\begin{align}
-  (\xt - \muit)^\top \Sigmait (\xt - \muit) = 1
-\end{align}
-
-Moving to camera coordinates
-\newcommand{\Rctot}{R}
-\newcommand{\tctot}{t}
-\begin{align}
-  (\Rctot \xc + \tctot - \muit)^\top \Sigmait (\Rctot \xc + \tctot - \muit) = 1
-\end{align}
-
-\newcommand{\tcmut}{t'}
-Let $\tcmut = \tctot - \muit$
-\begin{align}
-  (\Rctot \xc + \tcmut)^\top \Sigmait (\Rctot \xc + \tcmut) = 1
-\end{align}
-\begin{align}
-  \xc^\top \Rctot^\top \Sigmait \Rctot \xc + 2 (\Rctot^\top \tcmut)^\top  \Rctot^\top\Sigmait \Rctot \xc
-  + \tcmut^\top \Sigmait \tcmut = 1
-\end{align}
-\newcommand{\Sigmaic}{\Sigma'^i_c}
-\newcommand{\muic}{{\mu^i_c}}
-Let $\Sigmaic = \Rctot^\top \Sigmait \Rctot$ and $\muic = - \Rctot^\top
-\tcmut$
-\begin{align}
-  (\xc - \muic)^\top\Sigmaic(\xc - \muic) - \muic^\top\Sigmaic\muic +
-  \tcmut^\top \Sigmait \tcmut = 1
-\end{align}
-\newcommand{\Sigmaicf}{\Sigma^i_c}
-Let $\Sigmaicf = \frac{\Sigmaic}{1 - \tcmut^\top \Sigmait \tcmut +
-\muic^\top\Sigmaic\muic}$
-\begin{align}
-(\xc - \muic)^\top\Sigmaicf(\xc - \muic) = 1
-\end{align}
-
-Hence, we have following expression for mean and sigma of ellipsoid:
-\begin{align}
-  \label{eq:ellipsoidMeanSigma}
-  \muic &= - \Rctot^\top \tcmut \\
-  \Sigmaicf &= \frac{\Sigmaic}
-{1 - \tcmut^\top \Sigmait \tcmut + \muic^\top\Sigmaic\muic}
-\end{align}
-
-% \subsection{Object detection score}
-% \begin{align}
-% \Energy{det}(\relp{i}{t}, \dimsn{i}) = 
-%              \frac{1}{S_t^2(\projectionOf{\dimsn{i}})}
-% \end{align}
-
-% \subsection{Object 2D bounding box with occlusion}
-% Reproduced from \cite{song2014eccv} section 4.3
-% 
-% \begin{multline}
-%   \Energy{box}(\relp{i}{t}, \dimsn{i}) =
-%              %\sum_{i=1}^N \sum_{t=s_i}^{e_i}
-%              \rho^i_t \|\projectionOf{\dimsn{i}} -
-%              \bb{i}\|^2
-% \end{multline}
-% 
-% where $S_t(.)$ is the function to approximate the detection scores using
-% mixture of Gaussian model and $\rho^i_t$ is the visibility fraction. 
-% 
-% % It can be
-% % computed by using polygon intersection algorithms.
-% % \begin{align}
-% %   v^i_t &= \frac{\|\occFreeProj{\dimsn{i}}\|}
-% %                 {\|\projectionOf{\dimsn{i}}\|}
-% % \end{align}
-% % where $\|.\|$ represents the norm or the area of the polygon.
-% 
-% Another approach is to just consider the corner points in the occlusion free
-% area.  Say $\projectionOf{\dimsn{i}} = [b^i_1, \dots, b^i_4]$.
-% \begin{multline}
-%   \Energy{box}(\relp{i}{t}, \dimsn{i}) =
-%              %\sum_{i=1}^N \sum_{t=s_i}^{e_i}
-%              %S_t^2(\projectionOf{\dimsn{i}})
-%              \sum_{{b^i_j} \in \occFreeProj{\dimsn{i}}}
-%              \|b^i_j - d^i_j\|^2
-% \end{multline}
-% 
-% In the opinion of this author, the second approach is better because the
-% visibility is an area based measure while the error metric is point to point
-% distance based measure. If we use bounding overlap instead of corner to corner
-% distance, the use of visibility fraction makes much more sense. However, one
-% can argue that even detection score is an area based measure. 
-% 
-% Hence a third approach can be 
-% \begin{multline}
-%   \Energy{box}(\relp{i}{t}, \dimsn{i}) =
-%              %\sum_{i=1}^N \sum_{t=s_i}^{e_i}
-%   \rho^i_t \|\projectionOf{\dimsn{i}} \ominus \bb{i}\|
-% \end{multline}
-% where $A \ominus B$ represents the symmetric difference between set $A$ and set
-% $B$ and is given by $A \ominus B = (A \cup B) \setminus (A \cap B)$.
-% One may argue that we can take the intersection of occlusion free projection 
-% and get rid of the visibility fraction, but that would be a little off the 
-% detection bounding box is usually more close to the projection of full car
-% instead of the just the visible portion.
-% 
-% 
-% \subsection{Orientation cues}
-% There are two orientation cues (1) orientation from detection (2) orientation
-% from appearance map \cite{yao2012describing}.
-% 
-% \begin{align}
-%   \Energy{ori} &= 
-%   %S_t^2(\projectionOf{\dimsn{i}})
-%   \rho^i_t(1 - \cos({\omega}^i_{\text{det}} - \ori{i}{t})
-% \end{align}
-% 
-% Appearance map is a shape prior that requires \emph{Scene labeling} input.
-
-\section{Continuous object detection score energy with occlusion}
-
-To start with we have hypothesized 3D bounding boxes $\{ \dimsn{i} \}_i$
-over all traffic participants and we have object detection scores modeled as
-mixture of Gaussians over four dimensional space of bounding box boundaries.
-Let the detection score function over the detection $\bb{i}$ be 
-%
-\begin{align}
-  S(\bb{i}) = \sum_j A_j \exp((\bb{i}-\mu^{(d)}_j)^\top \Sigma^{(d)-1}_j
-  (\bb{i}-\mu^{(d)}_j))
-\end{align}
-%
-
-\subsection{Soft occlusion regions}
-Let the projections of hypothesized soft ellipsoids be
-$\projectionOf{\dimsn{i}}$ with some mean $\mu_i$ and variance $\Sigma_i$
-(assuming that projection of ellipsoids can be approximated by ellipses on
-image plane). We take the occlusion (intersection of two ellipses) to be
-modelled by product of the respective Gaussians.
-%
-\begin{align}
-  O_{ij}(x; \mu_{Oij}, \Sigma_{Oij}) = N(x; \mu_i, \Sigma_i)N(x; \mu_j,
-  \Sigma_j)
-\end{align}
-%
-The product of Gaussian can be computed analytically.
-
-\subsection{Merging occlusion regions with detection score}
-But what does detection score function represents? It is a measure of
-correlation of trained object features and the features in the candidate
-bounding box. If the detection scores are indeed Gaussians around the mean
-bounding box $\mu_j$, the $\Sigma_j^{-1}$ represents the variance (and
-covariance) around the mean bounding box. But when the candidate objects seem
-to be occluded we have additional information available. In such a case, we
-can say that the occluded object might have unexpected effect on the detection
-scores. However, the uncertainty in the detection score in loop sided. The
-mean detection bounding box must have picked up correct boundaries on the
-un-occluded sides but we cannot say the same about occluded boundaries. The
-effect on detection score depends a lot on the features of the occluder. Given
-this understanding we want to decrease our confidence on the mean detection
-boundaries around the occluded boundaries. One of the simplest ways will be to
-scale the appropriate diagonal element of $\Sigma_j$ by an appropriate scaling
-factor.
-
-We observe that the soft occlusion regions are 2D while the detection scores
-are 4D. But that should not be a problem because the detection scores are
-modeled as $[x_{\text{min}}, y_{\text{min}}, x_{\text{max}},
-y_{\text{max}}]^\top$, we can stack the vectors in the soft occlusion region
-domain as the regions are independent of min or max variation. The parameters
-of 4D occlusion distribution are given by
-
-\begin{align}
-  \mu'_{Oij} = [\mu_{Oij}^\top \mu_{Oij}^\top]^\top
-  \Sigma'_{Oij} = \begin{bmatrix}
-    \Sigma_{Oij} & \Sigma_{Oij} \\
-\Sigma_{Oij} & \Sigma_{Oij}
-  \end{bmatrix}
-\end{align}
-
-With our
-discussion so far, the function $O_{ij}(.)$ gives an additional measure of
-uncertainty associated with each point in the space. To finally re-model our
-detection scores scaled by continuous occlusion we sample $O_{ij}(.)$ at the
-mean detection boundaries from GMM $S(.)$ and we scale the detection boundary
-variance by $\mathcal{P}_{ij} = \rho_{ij}\rho_{ij}^\top$ where $\rho_{ij} =
-\mathbf{1} + O_{ij}(\mu^{(d)}_j; \mu'_{Oij}, \Sigma'_{Oij})$. The new variance
-in detection score is given by 
-%
-\begin{align}
-  \Sigma'^{(d)}_j = \prod_{k \in \text{occluders}} \mathcal{P}_{kj}
-  \Sigma^{(d)}_j
-  \prod_{k \in \text{occluders}} \mathcal{P}^\top_{kj}
+\subsection{Object detection energy with occlusion}
+
+Object detection is usually followed by non-maximal suppression that results in
+discarding similar bounding boxes. When we are jointly optimizing detections
+with other cues, it is not usually desirable to go with a single bounding box.
+Hence, we keep all the bounding box detections by approximating them with
+multi-modal sum of Gaussian like logistic functions. We fit the parametric function of the form 
+%
+\begin{align}
+  S(\bb{i}) = \sum_k A_k \exp(-(\bb{i}-\mu^{(d)}_k)^\top \Sigma^{(d)-1}_k
+  (\bb{i}-\mu^{(d)}_k))
+\end{align}
+%
+to detection scores, by non-linear error minimization with initialization from
+non-maximal suppressed outputs. Here $\mu^{(d)}_j$ is one of the $k$ modes as a
+4D vector representing a single bounding box as $[\minx, \miny, \maxx,
+\maxy]^\top$. The optimization is constrained with symmetry and positive
+definiteness of $\Sigma^{(d)-1}_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
+
+\subsubsection{Detection scores with occlusion reasoning} 
+With our model of $\Ptrans$ described in Section \ref{sec:TPmodel}, we can
+compute the probability of a point $\mathbf{u}$ on image be occluded assuming
+the point is on TP $i$ with mean depth $\mu^{(i)}_d$ as
+\begin{align}
+  O_{i}(\mathbf{u}, \mu^{(i)}_d) = 1 - \Ptransmud \enspace .
+\end{align}
+
+If we a portion of our proposed detection bounding box is known to be occluded,
+then we would like to decrease the confidence in the detection score about the
+localization of that end of the object. Assuming that the occlusion is often on
+the boundary of detection bounding boxes, we want to decrease our confidence on
+the mean detection boundaries around the occluded boundaries. 
+One of the simplest ways will be to scale the appropriate diagonal element of
+$\Sigma_j$ by an appropriate scaling factor proportional to occlusion. But this
+does not model appropriate how does occlusion affects the non diagonal terms.
+Hence, we choose a covariance addition model where we compute a occlusion
+covariance matrix, that provides a measure of occlusion in each direction.
+
+To re-model our detection scores scaled by continuous occlusion we sample
+$O_{i}(\mathbf{u}, \mu^{(i)}_d)$ at the hypothesized detection boundaries from
+GMM $S(.)$ and we augment the detection boundary covariance matrix by
+$\mathcal{P}_{j} = \rho_{j}\rho_{j}^\top$ where $\rho_{j} = O_{j}(\mathbf{u},
+\mu^{(i)}_d)$. The new covariance matrix in detection score is given by 
+%
+\begin{align}
+  \Sigma'^{(d)}_j = \mathcal{P}_{j} + \Sigma^{(d)}_j
 \end{align}
@@
 matrix
-\begin{align}
-  S'(\bb{i}) = \sum_j A_j \exp((\bb{i}-\mu^{(d)}_j)^\top \Sigma'^{(d)-1}_j
+%
+\begin{multline}
+  S'(\bb{i}) =\\
+  \sum_j A_j \exp(-(\bb{i}-\mu^{(d)}_j)^\top \Sigma'^{(d)-1}_j
   (\bb{i}-\mu^{(d)}_j))
-\end{align}
-
-\newcommand{\Beizer}{B\'eizer }
+\end{multline}
+
+The energy of detection scores is simply take to be the inverse of the detection score.
+\begin{align}
+  \Energy{detect}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}
+\end{align}
+
 \subsection{Lane energy}
 \label{sec:laneEnergy}
- The lanes be are modeled as splines. The lanes geometry information can be
- obtained from camera input as well as from the available maps localized by
- GPS. We need to combine information in a different framework to lead to a
-more accurate solution by using both the sources. In a probablistic framework
-it is always useful to compute uncertainty along the estimated values.
-Here we assume that the confidence in lane detection is inversely proportional
-to the squre of distance of of the specific point on the lane to the camera
-\newcommand{\LaneUncertainty}[1]{\Sigma_{L_m}(#1)}
-$\Sigma_{L_m}({x}_{L_m}) = \frac{1}{\|\mathbf{x}_{L_m} - \egop\|^2}$.
-
-A lane is modeled by four control points of a \Beizer curve $L_j = \{l_0, l_1,
-l_2, l_3\}$. The parametric curve is given by $L_j(k) = \sum_{i=0}^3 {}^3C_i
-(1-t)^{3-i}t^i l_i$. \Beizer are double differentiable so one can find
-tangents ($L'_j(k)$) and normals $R_{\frac{\pi}{2}}L'_j(k)$ where 
-$R_{\frac{\pi}{2}} = \begin{bmatrix} 0 & -1 \\ 1 & 0 \end{bmatrix}$ is
-$90^\circ$ rotation matrix.
-
-\newcommand{\projOnLane}[1]{\pi_{L_m(k)}(#1)}
-Now, there are some algorithms \cite{ma2003point, chen2007improved} to
-approximate the closest point on a \Beizer curve $k_x = \projOnLane{x}$.
-Consequently one can get solutions for shortest distance $s =
-\text{DIST}(L_j(k), x)$ and orientation at a closest point on the lane
-$\mathbf{t} = \text{TAN}(L_j(k), x)$.
-
-% \subsubsection{Position in lane}
-%
-% \begin{align}
-%   \Energy{plane} &=
-%   \min_{j = 0}^{n_l} \text{DIST}(L_j(k), \pos{i}{t})
-% \end{align}
-%
- % 
- % We normalize it with the confidence in lane positions.
- % 
- % \begin{align}
- %   \Energy{plane} &=
- %   \min_{m = 0}^{n_l} \text{DIST}(L_m(k), \pos{i}{t})
- %   \LaneUncertainty{\pos{i}{t}}
- % \end{align}
-
-\subsubsection{Orientation within lane}
-\begin{itemize}
-  \item We can find the tangent to a lane
-  \item The energy is given by the dot product between car orientation
-    and tangent to the lane at that point.
-\end{itemize}
-
-% \begin{align}
-%   \Energy{olane} &= 1 - \text{TAN}(L_l(k),  \pos{i}{t})
-%   \cdot
-%   \ori{i}{t}
-% \end{align}
-% 
-% 
-% 
-% This model needs to be scaled by uncertainty. For example, if we want to say
-% that the farther the lane is from the camera we are less sure about lane
-% orientation and hence this evidence term we scale it by say square of distance
-% of the car position from camera.
-
-% \begin{align}
-%   \Energy{olane} &= 
-%   (1 - \ori{i}{t} \cdot \text{TAN}(L_{m^*}(k),  \pos{i}{t}) )
-%   
-% \end{align}
-% where $m^* = \arg \min_m \text{DIST}(L_m(k), \pos{i}{t})$
-
-\begin{align}
+ The lanes are modeled as splines. Here we assume that the confidence in lane
+ detection is decreases as the distance from the lane center increases.  The
+ energy is given by the dot product between car orientation and tangent to the
+ lane at that point.
+
+\begin{multline}
   \label{eq:laneOrientationEnergy}
-  \Energy{lane} &= 
+  \Energy{lane} = \\
   \sum_{m \in M_{\text{close}}}
@@
 \LaneUncertainty{\pos{i}{t}}
-\end{align}
+\end{multline}
 where $M_{\text{close}} = \{m : \text{DIST}(L_{m}(k), \pos{i}{t}) < 50\} $ is
 the set of nearby lanes and 
-\begin{align}
-\LaneUncertainty{\pos{i}{t}} = 
+\begin{multline}
+\LaneUncertainty{\pos{i}{t}} = \\
   \frac{1}{1 + exp(-q(w_{\text{road}} - \text{DIST}(L_{m}(k), \pos{i}{t})))}
-\end{align}
+\end{multline}
 for some constant $w_{\text{road}}$ that represents the width of the road.
-
-\begin{comment}
-
-\subsection{Collisions}
-
-The collision constraint among traffic participants can be modelled by
-pairwise distance based constraints. But having constraints between each pair
-of participants is bound to create cycles and computational inefficient.
-Among game developers it is common to use spatial hashing to find collision
-candidates and use pairwise constraints only among those. While this will
-enable us to speed up collision checking, we will still end up inducing cycles
-in the model. There are two ways to break these cycles, 1) disable the cross
-lane collision checking 2) created a weighted graph among collision
-candidates weighted by distance and then find a minimum spanning
-tree to break cycles. (1) is too strong of an assumption hence we focus on the
-second approach.
-
-There are two possible approaches to find collision among candidates (1)
-polygon intersection methods (2) soft ellipse intersection method. Boost
-provides scan line based approach to find intersections of polygons. Since our
-polygons are simple rectangles, this approach can be very fast. Other approach
-is to approximate rectangles with ellipses and finding if the ellipses
-intersect.  This intersection can be computed analytically.
-
-\begin{align}
-  \EnergyCol &= \begin{cases}
-  \infty &\text{if INTERSECTS}(\pos{i}{t}, \dimsn{i}, \pos{j}{t},
-  \dimsn{j})\\
-  0 &\text{otherwise}
-  \end{cases}
-\end{align}
-
-%For smoother collision probability see Section \ref{sec:smoothercollision}.
-
-\subsubsection{Ellipse-ellipse intersection}
-\label{sec:ellipseintersection}
-A rectangle with sides $2a$ and $2b$ can be approximated by an ellipse with
-equation $\frac{x^2}{a^2} + \frac{y^2}{b^2} = 1$. But this ellipse is inside
-the rectangle. To enclose the rectangle, scale the ellipse by a factor of
-$\sqrt{2}$. The equation becomes, $\frac{x^2}{2a^2} + \frac{y^2}{2b^2} = 1$.
-For rotation $\psi$ and center $\pos{i}{t}$, the equation of ellipse can be
-re-written as:
-\begin{align}
-  (\mathbf{x} - \pos{i}{t})^\top\Sigma_i^{-1}(\mathbf{x} - \pos{i}{t}) &= 1
-\end{align}
-where
-\begin{align}
-  \Sigma_i^{-1} &= \begin{bmatrix}
-    \frac{\cos^2{\psi}}{2a^2} + \frac{\sin^2{\psi}}{2b^2} &
-    \frac{\cos{\psi}\sin{\psi}}{2}(\frac{1}{b^2} - \frac{1}{a^2})\\
-    \frac{\cos{\psi}\sin{\psi}}{2}(\frac{1}{b^2} - \frac{1}{a^2}) &
-    \frac{\sin^2{\psi}}{2a^2} + \frac{\cos^2{\psi}}{2b^2} \\
-  \end{bmatrix}
-\end{align}
-
-% A point $\mathbf{x}$ is inside both ellipse $i$, $j$ if and only if
-% \begin{multline}
-%   (\mathbf{x} - \pos{i}{t})^\top\Sigma_i^{-1}(\mathbf{x} - \pos{i}{t}) +\\
-% (\mathbf{x} - \pos{j}{t})^\top\Sigma_j^{-1}(\mathbf{x} - \pos{j}{t})
-%   \le 2
-% \end{multline}
-% which is equivalent to
-% \begin{multline}
-%   (\mathbf{x} - \mu_c)^\top\Sigma_c^{-1}(\mathbf{x} - \mu_c)
-%   + \pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t}\\
-%   + \pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t}
-%   - \mu_c^\top\Sigma_c^{-1}\mu_c
-%   \le 2
-% \end{multline}
-% where $\Sigma_c = (\Sigma_i^{-1} + \Sigma_j^{-1})^{-1}$ and $\mu_c =
-% \Sigma_c(\Sigma_i^{-1}\pos{i}{t} + \Sigma_j^{-1}\pos{j}{t})$.
-% 
-% There is at least one point inside both ellipse if 
-% \begin{align}
-%   \pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t}
-%   + \pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t}
-%   - \mu_c^\top\Sigma_c^{-1}\mu_c
-%   &\le 2
-% \end{align}
-% 
-% The left hand side can be interpreted as distance between two ellipses, which
-% is 2 when the two ellipses collide and $0$ when two ellipse completely
-% overlap.
-
-\subsubsection{Smoother collision probability}
-\label{sec:smoothercollision}
-%The above mentioned ellipse-ellipse intersection formulation gives us an
-%insight: the distance between two oriented ellipse boundaries can be again
-%formulated as a distance metric\footnote{TODO:proof}.
-Instead of using Gaussians to model
-collision constraints as done by \cite{milan2013continuous}, we use a more
-steeper sigmoid function.
-\begin{multline}
-  \EnergyCol = \frac{1}{1 +
-\exp(-k(\pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t})-1)}\\
-\frac{1}{1 +
-\exp(-k(\pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t})-1)}
-\end{multline}
-where $k$ is steepness parameter.
-%$d(.)$ is the distance metric defined as:
-%\begin{multline}
-%  d(\pos{i}{t}, \dimsn{i}, \pos{j}{t}, \dimsn{j})
-%  =
-%  \pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t} \\
-%  + \pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t}
-%  - \mu_c^\top\Sigma_c^{-1}\mu_c
-%\end{multline}
-
-\end{comment}
 
@@
 Dynamics constraints should not only enforce smooth trajectories, but also the
-holonomic constraints.
-
-The following equation adds a penalty if the change in
+holonomic constraints.  The following energy adds a penalty if the change in
 position is not in direction of previous orientation.
@@
 
-The following equation adds a penalty for change in position and orientation
+The following energy adds a penalty for change in position and orientation
 but a penalty for change in velocity is much better approximation. However, in
@@
 
+\subsection{Collision energy}
+
+Bhattacharya coefficient $\int_a^b\sqrt{p(x)q(x)}dx$ is a measure of similarity
+of two distributions $p(x)$ and $q(x)$. If we represent TPs as gaussians in
+Birds eye view (BEV), then similarity is a measure of collision. Exactly
+overlapping distribution results in coefficient as 1. 
+%The analytical form of
+%Bhattacharya coefficient has been taken from
+%\url{http://like.silk.to/studymemo/PropertiesOfMultivariateGaussianFunction.pdf}
+
+\begin{multline}
+  \label{eq:collisionEnergyHellingerDistance}
+  \EnergyCol =\\ -\log\left(
+  A_{ij}
+  e^{-\frac{1}{8}
+    \left(\pos{i}{t} - \pos{j}{t}\right)^\top
+    P^{-1}
+    \left(\pos{i}{t} - \pos{j}{t}\right)
+    }
+    \right)
+\end{multline}
+where 
+\begin{align}
+  A_{ij} &= \frac{|\Sigma_i|^\frac{1}{4}|\Sigma_j|^\frac{1}{4}}
+  {|P|^\frac{1}{2}}\\
+  P &= \frac{1}{2}\Sigma_i + \frac{1}{2}\Sigma_j\\
+\Sigma_i^{-1} &= R^\top_{\ori{i}{t}} \begin{bmatrix} 2/l_i & 0 \\ 0 & 2/w_i \end{bmatrix}
+R_{\ori{i}{t}}
+\end{align}
+
 \subsection{Size Prior}
@@
 
-where $\expDimsn$ is the mean traffic participant dimensions and
+where $\expDimsn$ is the mean TP dimensions and
 $\Sigma_{\expDimsn}$ is the correspondence covariance matrix.
 
-\begin{table*}
-  \begin{tabular}{|l|r|r|l|}
-    \hline
-    func            & equation                      & ms per 6 frames &
-    comment \\
-    \hline
-    totalBBoxEnergy & Sec \ref{sec:totalBBoxEnergy} & 268 & \\
-    laneEnergy      & Sec \ref{sec:laneEnergy}      & 163 & \\
-    laneOrientationEnergy & Eq \eqref{eq:laneOrientationEnergy} & 155 & The
-    equation summed up for all 6 tracklets\\
-    collisionEnergyHellingerDistance & Eq 
-    \eqref{eq:collisionEnergyHellingerDistance} & 93  & \\
-    totalPosTransitionEnergy & Eq \eqref{eq:totalPosTransitionEnergy} & 15 & \\
-    totalSizeEnergy & Eq \eqref{eq:totalSizeEnergy} & 0.9 & \\
-
-    \hline
-    occlusionMaskFromOptVector & Sec \ref{sec:occlusionMaskFromOptVector} &
-    123 &
-    \\
-    bboxEnergyFromOccMask & Eq \eqref{eq:bboxEnergyFromOccMask} & 140 &  \\
-    vis\_area\_from\_triangle & $\|\triangleProj{s} \setminus
-    \occ{\relpz{i}{t}}\|$ & 76 & \\
-    \hline
-    distance2curve & $\text{DIST}(L_j(k), x)$ & 74 & Called 2 times per
-    tracklet \\
-    filterMapWaysByDistance & $M_{\text{close}} = \{m : \text{DIST}(.) < 50\} $ & 52 & \\
-    area\_of\_triangle & $\|\triangleProj{s}\|$ & 48 & called 4 times per
-    tracklet \\
-    occlusionMask & Step 3 of Sec \ref{sec:occlusionMaskFromOptVector} & 46 &
-    \\
-    \hline
-  \end{tabular}
-
-  \begin{tabular}{|l|r|r|l|}
-    \hline
-    func            & equation                      & ms per 6 frames &
-    comment \\
-    \hline
-    totalContPtTracksEnergy & Sec \ref{sec:totalContPtTracksEnergy} & 25000 &
-    \\
-    integrand & Eq \eqref{eq:integrand} & 23000 & \\
-    repmat & & 5000 & \\
-    assocCoeffEval & Eq \eqref{eq:assocCoeffEval} & 4000 & \\
-    evalPreflection & Eq \eqref{eq:analytic-prefl} & 3000 & \\
-    gradfocci & $\nabla \occf^\top \ray$ & 2040 & \\
-    associationCoefficientInit & Eq
-    \eqref{eq:ptransmissionInit}\eqref{eq:ellipsoidMeanSigma} & 1706 & \\
-    projectToImage & $\frac{Ku}{Ku(3)}$ & 4000 & Called ~8 times per edge\\
-    evalCumulativePtrans & \eqref{eq:evalCumulativePtrans} & 1178 & \\
-    ptransmissionApproxInit & \eqref{eq:ptransmissionInit} & 1000 & \\
-    ellipsoidCentreDist & $(x-\mu)^\top \Sigma (x-\mu)$ & 1000 & \\
-    squeeze & & 951 &\\
-    trackletToCamTransform & $R_{\ori{i}{t}}, t$ & 786 & \\
-    ellipsoidMeanSigma & Eq \eqref{eq:ellipsoidMeanSigma} & 812 & \\
-    \hline
-  \end{tabular}
-\end{table*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Association error evaluation}
+
+To verify the correctness of our association probability $\assocP$ we perform
+association error experiment that compare the accuracy of point track
+association with TPs with that of bounding box baseline method.
+
+% \begin{align}
+%   f^{i}_{reproj}&(\trackpj{t-1}, \lambda) =
+%   \projectionOf{\invProjectionOf{\trackpj{t-1}}}\\
+%   %&= K(R^i_t ((R^i_{t-1})^\top\lambda \ray - (R^i_{t-1})^\top T_{t-1}) + T_{t})\\
+%   &= \frac
+%   {p_{1:2}\lambda + q_{1:2}}
+%   {p_{3}\lambda + q_{3}}
+% \end{align}
+% where $p_{1:3} = KR^i_t(R^i_{t-1})^\top\ray$ and
+% $q_{1:3} = KR^i_t(R^i_{t-1})^\top T_{t-1} + KT_t$
+% 
+% Now that we have an association from TP $i$ to point track $j$ through
+% $\lambda$, we can come up with an association probability
+% \begin{align}
+%    \assocP &= \frac{(\max \{ 0, \nabla \occf^\top
+% \ray \})^2 }{P_{\text{reflection}}}\lambdadist\\
+% &=(\max \{ 0, \nabla \occf^\top \ray \})^2
+%   \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
+% \end{align}
+
+Note that the fraction $\assocP$ although called association probability does
+not capture the entire information that we have available for compute
+association of points to tracks. This above fraction is the association
+probability given the hypothesized parameters of TP model.
+
+To compute the association probability between TP $i$ and
+point track $j$ we must use re-projection error as well. When the association
+$i$ and $j$ is right and the point of reflection is at depth $\lambda$ the
+re-projection error must be zero \eqref{eq:reprojerror}, otherwise the error
+becomes a measure of distance from the true solution.
+The error terms can be converted to probability domain by considering the error
+term as negative log of probability
+
+\begin{align}
+  P^{(ij)}_{\text{assoc by reproj}}(\lambda) = \frac{1}{Z}\exp(-\Ereproj(\lambda))
+\end{align}
+
+Using both the evidence terms we can write probability of association as
+\begin{align}
+  P^{(ij)}_{\text{assoc}} = \frac{1}{Z'}\int_0^{\infty} \assocP \frac{1}{\sqrt{2\pi}}\exp(-\Ereproj(\lambda))d\lambda
+  \label{eq:prob-assoc}
+\end{align}
+
+Once we have the probability of association we can compute the best possible
+assignment of TP for each point. The points having very small association
+probability are assigned to the background,
+\begin{align}
+  i^*_{j} = \argmin_{i} \int_0^\infty \assocP \Ereproj(\lambda) d\lambda
+\end{align}
+
+We use bounding box based assignment of point tracks to TPs as the baseline.
+For the regions where the bounding boxes overlap, we assign the points to the
+TP that has smaller mean depth then the competing bounding box.
 
@@
 \end{document}
-%\documentclass[11pt]{report}
-%\usepackage{tikz}
-%\usetikzlibrary{fit,positioning}
-%\begin{document}
-%\begin{figure}
-%\centering
-%\begin{tikzpicture}
-%\tikzstyle{main}=[circle, minimum size = 10mm, thick, draw =black!80, node distance = 16mm]
-%\tikzstyle{connect}=[-latex, thick]
-%\tikzstyle{box}=[rectangle, draw=black!100]
-%  \node[main, fill = white!100] at (cit)  {$c_i^t$ };
-%  \node[main] at +(2.0cm, 1.0cm) (detect)  { $b$ };
-%  \node[main] at +(2.0cm, -1.0cm) (sfm)    { $t$ };
-%  \node[main] (lane)   [below=of cit] { $L$ };
-%  \path (cit) edge [connect] (detect)
-%        (cit) edge [connect] (sfm)
-%        (cit) edge [connect] (lane);
-%        \node[box, inner sep=4mm, fit=(cit) (detect) (lane),label=below right:N] {};
-%  \node[main, fill = white!100] at (cit-1)  {$c_i^{t-1}$ };
-%  \node[main] at +(2.0cm, 1.0cm) (detect)  { $b$ };
-%  \node[main] at +(2.0cm, -1.0cm) (sfm)    { $t$ };
-%  \node[main] (lane)   [below=of cit] { $L$ };
-%  \path (cit) edge [connect] (detect)
-%        (cit) edge [connect] (sfm)
-%        (cit) edge [connect] (lane);
-%        \node[box, inner sep=4mm, fit=(cit) (detect) (lane),label=below right:N] {};
-%
-%  %\node[rectangle, inner sep=4.4mm,draw=black!100, fit= (z) (w)] {};
-%  %\node[rectangle, inner sep=4.6mm, fit= (z) (w),label=below right:M, xshift=12.5mm] {};
-%  %\node[rectangle, inner sep=9mm, draw=black!100, fit = (theta) (z) (w)] {};
-%\end{tikzpicture}
-%\end{figure}
-%\end{document}
-%note - compiled with pdflatex

### 2014-11-08 Paper/supplementary.tex
Cleaned up the model.pdf to make it look more like a paper.

--- 2014-10-14 Notes/model.tex
@@
 \newcommand{\occFreeProj}[1]{\Pi_{\relp{i}{t}}(#1)}
-
-\begin{table}[h]
-  \begin{tabular}{|l|l|}
-    \hline
-    Symbol & Meaning \\
-    \hline
-    $\pos{i}{t}$ & Position of $i$th car at time $t$\\
-    $\ori{i}{t}$ & Orientation of $i$th car at time $t$\\
-     $\dimsn{i}$ & 3D bounding box of the car (dimensions)\\
-    $\state{i}{t}$ & State of car $=\{\pos{i}{t}, \ori{i}{t}, \dimsn{i}\}$\\
-    $\egop$ & Position of camera at time $t$\\
-    $\egoo$ & Orientation of camera at time $t$\\
-    $\relp{i}{t}$ & Relative car pose w.r.t. camera \\
-    $\tracklets$ & 3D points tracked on car $i$ in its own frame\\
-    $\trackp{t}$ & Projection of $\tracklets$ in camera\\
-    $\projectionOf{.}$ & Projection function for pose $\relp{i}{t}$\\
-    $\bb{i}$ & 2D bounding box of the car in image\\
-    \hline
-  \end{tabular}
-\end{table}
-
-%%%%%%%%% BODY TEXT
-\section{The Model}
-
-The objective is to find the most likely traffic participant state given various
-evidences $\mathbb{E} = \{\{\trackp{t}\}, \{\bb{i}\}, \text{lane det.}, \text{map},
-\text{GPS}\}$.
-
-Mathematically, find:
-\begin{align}
-  \{\state{i}{t}\}^* &= \arg \max P(\{\state{i}{t}\} | \mathbb{E})
-\end{align}
-
-Bayes rule
-\begin{align}
-  P(\{\state{i}{t}\} | \mathbb{E}) &=
-  \frac{1}{Z}P( \mathbb{E} | \{\state{i}{t}\})P(\{\state{i}{t}\})
-\end{align}
-
-\begin{figure}[t]
-  \includegraphics[width=\columnwidth]{graphics/graphicalModelFrom61ConstVars.pdf}
-  \caption{Graphical model. The six numbered black circles represent the
-    unknown state variables of each car. All other nodes in the graphical model
-    are assumed
-    observed variables. Consider each energy in the model one by one. (1)
-    Bounding box energy: The bounding box energy without occlusion modeling is
-    a unary term, but with occlusion it becomes a higher order term that
-    affects the state of occluder as well. In this graphical model we assume
-    that the scene is being observed from left to right, hence "2" occludes "6"
-    and "5" and "5" occludes "1". The bounding box detection is represented by
-  $\mathbf{d}_{bb}^i(t)$ and the statistical dependencies are represented by
-  red lines. (2) Point tracks ($\Energy{track}$): Since occlusion is also
-  included in modeling point tracks energy we have similar interdependencies
-  for point tracks energy. The available point tracks are modeled by
-  $\mathbf{u}(t)$. (3) Collision ($\Energy{coll}$) : The collision energy
-  mathematically is a dense graph between all the TP but here we represent
-  collision among only those TP that are near enough to have a significant
-collision energy. (4) Orientation from detection ($\Energy{ori}$) (5) Orientation from lane (and map) information ($\Energy{lane}$)}
-  \label{fig:graphmodel}
-\end{figure}
-
-Assume conditional independence according to graphical model in
-\ref{fig:graphmodel}.
-
-\begin{multline}
-  P(\{\state{i}{t}\} | \mathbb{E}) =
-  \frac{1}{Z}
-  \prod_{t=s_i}^{e_i}\prod_{i,j: i \ne j}(P(\state{i}{t}, \state{j}{t}))\\
-%
-  \prod_{i=1}^{N}
-  \prod_{t=s_i}^{e_i}
-  P(\bb{i} | \state{i}{t})
-  P(\trackp{t} | \state{i}{t})\\
-  P(\state{i}{t} | L_m(t))
-  P(\state{i}{t} | \state{i}{t-1})
-  P(\state{i}{t})
-\end{multline}
-
-We can formulate similar objective function in negative log domain:
-\footnote{TODO:Resolve inconsistency in summation absorption in energy terms.}
-\begin{multline}
-  -\log{P(\{\state{i}{t}\} | \mathbb{E})} = 
-  Z' + \sum_{i,j:i\ne j} \sum_{t=s_i}^{e_i}  \WEnergyCol \\
-  + \sum_{i=1}^N \sum_{t=s_i}^{e_i}
-    \WEnergy{box}
-  + \WEnergy{track}\\
-  + \WEnergy{lane}
-  + \WEnergy{dyn}
-  + \WEnergy{prior}
-\end{multline}
-
-\subsection{Collision energy}
-
-Bhattacharya coefficient $\int_a^b\sqrt{p(x)q(x)}dx$ is a measure of similarity of two
-distributions $p(x)$ and $q(x)$. If we represent traffic participants as
-gaussians in BEV, then similarity is a measure of collision. Exactly
-overlapping distribution results in coefficient as 1. The analytical form of
-Bhattacharya coefficient has been taken from
-\url{http://like.silk.to/studymemo/PropertiesOfMultivariateGaussianFunction.pdf}
-
-\begin{align}
-  \label{eq:collisionEnergyHellingerDistance}
-  \EnergyCol &=
-  \frac{|\Sigma_i|^\frac{1}{4}|\Sigma_j|^\frac{1}{4}}
-  {|P|^\frac{1}{2}}
-  e^{-\frac{1}{8}
-    \left(\pos{i}{t} - \pos{j}{t}\right)^\top
-    P^{-1}
-    \left(\pos{i}{t} - \pos{j}{t}\right)
+\newcommand{\minx}{x_{\text{min}}}
+\newcommand{\miny}{y_{\text{min}}}
+\newcommand{\maxx}{x_{\text{max}}}
+\newcommand{\maxy}{y_{\text{max}}}
+\newcommand{\frontface}{F^i_\text{FF}(t)}
+
+\newcommand{\occ}[1]{o({#1})}
+\newcommand{\face}{F^i_k(t)}
+
+\newcommand{\invProjectionOf}[1]{\pi^{-1}_{\relp{i}{t}}\left(#1\right)}
+\newcommand{\occf}{f^i_{occ}(\mathbf{x}_j)}
+\newcommand{\occftot}{f_{occ}(\mathbf{x}_j)}
+\newcommand{\occft}[1]{f_{occ}(#1)}
+
+\newcommand{\ray}{\hat{\mathbf{r}}_j}
+\newcommand{\occfray}{f_{occ}(\lambda\ray)}
+\newcommand{\lambdadist}{f_{\lambda}(\trackpj{t-1}, \lambda)}
+
+\newcommand{\occfxi}{L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i)}
+\newcommand{\occfi}{L(\lambda \ray; \pos{i}{t-1}, \Sigma_i)}
+\newcommand{\assocP}{a^{(ij)}(\lambda)}
+\newcommand{\assocPk}{a^{(ij)}(\lambda_k)}
+
+\newcommand{\Ereproj}{E^{(ij)}_{\text{reproj}}}
+\newcommand{\Ptrans}{P^{(j)}_{\text{transmission}}(\lambda)}
+\newcommand{\Ptransmud}{P^{(j)}_{\text{transmission}}(\mu^{(i)}_d)}
+\newcommand{\Prefl}{P^{(ij)}_{\text{reflection}}(\lambda)}
+\newcommand{\dishort}{d_i(\mathbf{x})}
+
+\newcommand{\Lu}{L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)}
+\newcommand{\Llambda}{L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d)}
+
+\newcommand{\Gauss}{\mathcal{N}}
+\newcommand{\PropDist}{\mathcal{W}_j}
+
+\newcommand{\muijl}{\mu^{(ij)}_{\lambda}}
+\newcommand{\sigmaijl}{\sigma^{ij}_{\lambda}}
+
+\newcommand{\Sigmait}{\Sigma^{(i)^{-1}}_t}
+
+\newcommand{\muit}{\mu^(i)_t}
+\newcommand{\Sigmaic}{\Sigma'^{(i)^{-1}}_c}
+
+\newcommand{\muic}{{\mu^(i)_c}}
+\newcommand{\Sigmaicf}{\Sigma^{(i)^{-1}}_c}
+
+\newcommand{\muiu}{\mu^{(i)}_t}
+\newcommand{\Sigmaiu}{\Sigma^{(i)^{-1}}_u}
+
+\newcommand{\xt}{\mathbf{x}_t}
+\newcommand{\xc}{\mathbf{x}_c}
+
+\newcommand{\Rctot}{R}
+\newcommand{\tctot}{t}
+
+\newcommand{\tcmut}{t'}
+
+\newcommand{\Beizer}{B\'eizer }
+
+\newcommand{\LaneUncertainty}[1]{\Sigma_{L_m}(#1)}
+\newcommand{\projOnLane}[1]{\pi_{L_m(k)}(#1)}
+
+% Pages are numbered in submission mode, and unnumbered in camera-ready
+%\ifcvprfinal\pagestyle{empty}\fi
+%\setcounter{page}{4321}
+%\DeclareMathSymbol{\Tangent}
+\DeclareMathOperator{\sech}{sech}
+\DeclareMathOperator{\poly}{poly}
+\DeclareMathOperator*{\argmin}{\arg\min}
+
+\begin{document}
+\title{Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.}
+\author{Vikas Dhiman\\
+  University of Michigan\\
+  Ann Arbor, MI, USA\\
+{\tt\small dhiman@umich.edu}
+\and
+Manmohan Chandraker\\
+NEC Laboratories America, Inc.\\
+Cupertino, CA, USA\\
+{\tt\small manu@nec-labs.com}
+\and
+Jason J Corso\\
+  University of Michigan\\
+  Ann Arbor, MI, USA\\
+{\tt\small jjcorso@eecs.umich.edu}
 }
-\end{align}
-where 
-\begin{align}
-  P &= \frac{1}{2}\Sigma_i + \frac{1}{2}\Sigma_j\\
-\Sigma_i^{-1} &= R^\top_{\ori{i}{t}} \begin{bmatrix} 2/l^i & 0 \\ 0 & 2/w^i \end{bmatrix}
-R_{\ori{i}{t}}
+\maketitle
+
+\section{Supplementary Material}
+
+\subsection{Numerical integration}
+Numerical integration is possible by computed by sampling. Samples need to be
+generated from the association probability $\assocP$ for a given $j$. We take
+proposal distribution to be a GMM with modes around probable reflection points.
+The weights of all Gaussians in the mixture are proportional to the distance of
+the point $j$ from projection of ellipsoid centre i.e. 
+\begin{align}
+  A_{ij} = \frac{1}{Z_j}\exp(-(\trackpj{t} - \mu^i_u)^\top\Sigma_u^i(\trackpj{t} - \mu^i_u))
+\end{align}
+where $Z_j = \sum_{i=1}^N A_{ij}$ and $\mu^i_u$ and $\Sigma_u^i$ are described in \eqref{eq:muiudef} and \eqref{eq:sigmauidef} respectively.
+The range of Gaussian $G_i$
+must be in the interval $[\|\relp{i}{t}\|, \|\relp{i}{t}\| -
+\sqrt{3}\max(\dimsn{i})]$. Hence we take the mean as $\|\relp{i}{t}\| -
+\frac{\sqrt{3}}{2}\max(\dimsn{i})$ and variance as
+$\frac{1}{3}\max(\dimsn{i})^2$. The distribution from which we sample is 
+\begin{align}
+  \PropDist(\lambda) = \sum_i A_{ij} \Gauss(\lambda; \|\relp{i}{t}\| -
+  \frac{\sqrt{3}}{2}\max(\dimsn{i}), \frac{1}{\sqrt{3}}\max(\dimsn{i}))
+\end{align}
+And the numerical integral with $K$ samples is computed by
+\begin{align}
+    \int_1^{\infty}
+    \assocP
+    \Ereproj(\lambda)
+    d\lambda
+    =
+    \frac{1}{K}\sum_k \Ereproj \frac{\assocPk}{\PropDist(\lambda_k)}
+\end{align}
+where $\lambda_k$ is the $k$th sample drawn from $\PropDist(\lambda)$.
+
+\subsection{Sigma of ellipsoid}
+\label{sec:sigmacomputation}
+
+\begin{align}
+  \muit &= \begin{bmatrix}
+  0& 0& \frac{h}{2}
+  \end{bmatrix}^\top\\
+  \Sigmait &= \begin{bmatrix}
+    \frac{4}{l^2} & 0 & 0 \\
+    0 & \frac{4}{w^2} & 0 \\
+    0 & 0 & \frac{4}{h^2}
+  \end{bmatrix}
+\end{align}
+
+In tracklet coordinates the equation of ellipsoid is 
+\begin{align}
+  (\xt - \muit)^\top \Sigmait (\xt - \muit) = 1
+\end{align}
+
+Moving to camera coordinates
+\begin{align}
+  (\Rctot \xc + \tctot - \muit)^\top \Sigmait (\Rctot \xc + \tctot - \muit) = 1
+\end{align}
+
+Let $\tcmut = \tctot - \muit$
+\begin{align}
+  (\Rctot \xc + \tcmut)^\top \Sigmait (\Rctot \xc + \tcmut) = 1
+\end{align}
+\begin{align}
+  \xc^\top \Rctot^\top \Sigmait \Rctot \xc + 2 (\Rctot^\top \tcmut)^\top  \Rctot^\top\Sigmait \Rctot \xc
+  + \tcmut^\top \Sigmait \tcmut = 1
+\end{align}
+Let $\Sigmaic = \Rctot^\top \Sigmait \Rctot$ and $\muic = - \Rctot^\top
+\tcmut$
+\begin{align}
+  (\xc - \muic)^\top\Sigmaic(\xc - \muic) - \muic^\top\Sigmaic\muic +
+  \tcmut^\top \Sigmait \tcmut = 1
+\end{align}
+Let $\Sigmaicf = \frac{\Sigmaic}{1 - \tcmut^\top \Sigmait \tcmut +
+\muic^\top\Sigmaic\muic}$
+\begin{align}
+(\xc - \muic)^\top\Sigmaicf(\xc - \muic) = 1
+\end{align}
+
+Hence, we have following expression for mean and sigma of ellipsoid:
+\begin{align}
+  \label{eq:ellipsoidMeanSigma}
+  \muic &= - \Rctot^\top \tcmut \\
+  \Sigmaicf &= \frac{\Sigmaic}
+{1 - \tcmut^\top \Sigmait \tcmut + \muic^\top\Sigmaic\muic}
+\end{align}
+
+\subsection{Projection of ellipsoid to image}
+\newcommand{\mubar}{\bar{\mu}_i}
+The perspective projection of an ellipsoid in general is not an ellipsoid in
+general. We approximate the projection of ellipsoid by projecting a slice
+through the ellipsoid. We choose the slice as the plane perpendicular to the
+line joining the center of ellipsoid to the optical center of camera. Let
+$\muic$ and $\Sigmaicf$ be the parameters of ellipsoid describing the ellipsoid
+in camera coordinates. The any point $x$ on the plane satisfies
+$x^\top\frac{\muic}{\|\muic\|} = \|\muic\|$. We introduce 
+$\mubar = \frac{\muic}{\|\muic\|^2}$ for notational simplicity. Hence, we want
+to project the points that satisfy both the equation of chosen plane and the 
+ellipsoid i.e.
+\begin{align}
+  \mubar^\top x = x^\top\mubar &= 1\\ 
+  (x-\muic)^\top\Sigmaicf(x-\muic) &= 1 \enspace.
+\end{align}
+We rewrite $\muic = \muic\mubar^\top x$, and $1 = x^\top\mubar \mubar^\top x$
+\begin{align}
+  (x-\muic\mubar^\top x)^\top\Sigmaicf(x-\muic\mubar^\top x) &= x^\top\mubar \mubar^\top x \enspace,
+\end{align}
+which is equivalent to 
+\begin{align}
+  x^\top\left((I-\muic\mubar^\top)^\top\Sigmaicf(I-\muic\mubar^\top) - \mubar \mubar^\top\right)x &= 0\enspace.
+\end{align}
+
+Note that if $u$ is a projection of $x$ to camera with intrinsic parameters
+$K$, then $x = K^{-1}u$ where $u$ is in homgeneous coordinates. Hence the above equation can be re-written as
+\newcommand{\Sproj}{\Sigma^{-1}_{\text{proj }i}}
+\newcommand{\Sperpcut}{\Sigma^{-1}_{\text{perpcut }i}}
+\begin{align}
+  u^\top\Sproj u &= 0\enspace, 
+\end{align}
+where $\Sproj = K^{-\top}\Sperpcut K^{-1}$ and 
+\begin{align}
+  \Sperpcut = (I-\muic\mubar^\top)^\top\Sigmaicf(I-\muic\mubar^\top) - \mubar \mubar^\top \enspace.
 \end{align}
@@
 
-  \newcommand{\minx}{x_{\text{min}}}
-  \newcommand{\miny}{y_{\text{min}}}
-  \newcommand{\maxx}{x_{\text{max}}}
-  \newcommand{\maxy}{y_{\text{max}}}
-  \newcommand{\frontface}{F^i_\text{FF}(t)}
   Each bounding box has 6 faces of which only 3 can be visible.
@@
 
-\newcommand{\occ}[1]{o({#1})}
-\newcommand{\face}{F^i_k(t)}
 \begin{comment}
@@
 
-  where $\relpz{j}{t}$ is the depth of the $j$th traffic participant when sorted
+  where $\relpz{j}{t}$ is the depth of the $j$th TPs participant when sorted
   by increasing depth.
@@
 
-\subsection{Continous Point tracks energy with occlusion}
-\label{sec:totalContPtTracksEnergy}
-We want continuous modeling of occlusion. We model occlusion as a opacity
-term. Based on the dimensions $\dimsn{i}$, we can
-compute the covariance matrix $\Sigma_i$ as shown in Sec. 
-\ref{sec:sigmacomputation}
-
-So far we have modeled our point tracks energy in a non-smooth way:
-\newcommand{\invProjectionOf}[1]{\pi^{-1}_{\relp{i}{t-1}}(#1)}
+\begin{comment}
+
+\begin{table*}
+  \begin{tabular}{|l|r|r|l|}
+    \hline
+    func            & equation                      & ms per 6 frames &
+    comment \\
+    \hline
+    totalBBoxEnergy & Sec \ref{sec:totalBBoxEnergy} & 268 & \\
+    laneEnergy      & Sec \ref{sec:laneEnergy}      & 163 & \\
+    laneOrientationEnergy & Eq \eqref{eq:laneOrientationEnergy} & 155 & The
+    equation summed up for all 6 tracklets\\
+    collisionEnergyHellingerDistance & Eq 
+    \eqref{eq:collisionEnergyHellingerDistance} & 93  & \\
+    totalPosTransitionEnergy & Eq \eqref{eq:totalPosTransitionEnergy} & 15 & \\
+    totalSizeEnergy & Eq \eqref{eq:totalSizeEnergy} & 0.9 & \\
+
+    \hline
+    occlusionMaskFromOptVector & Sec \ref{sec:occlusionMaskFromOptVector} &
+    123 &
+    \\
+    bboxEnergyFromOccMask & Eq \eqref{eq:bboxEnergyFromOccMask} & 140 &  \\
+    vis\_area\_from\_triangle & $\|\triangleProj{s} \setminus
+    \occ{\relpz{i}{t}}\|$ & 76 & \\
+    \hline
+    distance2curve & $\text{DIST}(L_j(k), x)$ & 74 & Called 2 times per
+    tracklet \\
+    filterMapWaysByDistance & $M_{\text{close}} = \{m : \text{DIST}(.) < 50\} $ & 52 & \\
+    area\_of\_triangle & $\|\triangleProj{s}\|$ & 48 & called 4 times per
+    tracklet \\
+    occlusionMask & Step 3 of Sec \ref{sec:occlusionMaskFromOptVector} & 46 &
+    \\
+    \hline
+  \end{tabular}
+
+  \begin{tabular}{|l|r|r|l|}
+    \hline
+    func            & equation                      & ms per 6 frames &
+    comment \\
+    \hline
+    totalContPtTracksEnergy & Sec \ref{sec:totalContPtTracksEnergy} & 25000 &
+    \\
+    integrand & Eq \eqref{eq:integrand} & 23000 & \\
+    repmat & & 5000 & \\
+    assocCoeffEval & Eq \eqref{eq:assocCoeffEval} & 4000 & \\
+    evalPreflection & Eq \eqref{eq:analytic-prefl} & 3000 & \\
+    gradfocci & $\nabla \occf^\top \ray$ & 2040 & \\
+    associationCoefficientInit & Eq
+    \eqref{eq:ptransmissionInit}\eqref{eq:ellipsoidMeanSigma} & 1706 & \\
+    projectToImage & $\frac{Ku}{Ku(3)}$ & 4000 & Called ~8 times per edge\\
+    evalCumulativePtrans & \eqref{eq:evalCumulativePtrans} & 1178 & \\
+    ptransmissionApproxInit & \eqref{eq:ptransmissionInit} & 1000 & \\
+    ellipsoidCentreDist & $(x-\mu)^\top \Sigma (x-\mu)$ & 1000 & \\
+    squeeze & & 951 &\\
+    trackletToCamTransform & $R_{\ori{i}{t}}, t$ & 786 & \\
+    ellipsoidMeanSigma & Eq \eqref{eq:ellipsoidMeanSigma} & 812 & \\
+    \hline
+  \end{tabular}
+\end{table*}
+
+\end{comment}
+
+\begin{comment}%%%%%%%%%%%%% May or may not use %%%%%%%%%%%
+TODO: Write Introduction
+  NEC has already developed a monocular camera based structure from motion
+  system which is accurate for requirements of road scene understanding. So we
+  assume that egomotion is given as an observed variable in our graphical
+  model. And we have following features to our disposal for estimating the 3D
+  poses (position + orientation) of traffic participants (TPs):
+  \begin{description}
+    \item[Ground plane] We assume that all the TPs lie on a common ground
+      plane. This is not particularly true for the cars that are parked off the
+      road. However, for autonomous driver assistance applications we can
+      ignore those cars.
+    \item[Detections] We assume that 2D car detections are available with tracking informations.
+    \item[Point tracks] We assume that 2D point tracks are available.
+    \item[GPS and Map information] We assume that GPS information is available
+      and we use openstreetmaps.org for pulling out local map for the current
+      car's position.
+    \item[Lane Information] We assume the lane detection works well and lane
+      information is available.
+    \item[Size prior] The distribution of size of cars follows gaussian distribution.
+    \item[Collision] A reasonable output of the system donot has any overlapping cars.
+  \end{description}
+\end{comment}
+
+\begin{comment}
+  Consider that we have a set of measurements whose mean and variance are known $\mu = E(x)$ and $\Sigma = E ((x - \mu_x)(x - \mu_x)^\top)$. We want to know the
+  affect of uncertainty on mean and variance of existing observations. On adding
+  noise $[\Delta x, \Delta y]^\top$ with zero mean and covariance $\Delta
+  \Sigma = E(\Delta x \Delta x^\top)$ the covariance of new data is given by
   \begin{multline}
-  \Energy{traci}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \\
-    \sum_{i=1}^{N} 
-    %\sum_{t = s_i}^{e_i}
-    \sum_{j = 1}^{M}
-    \int_1^\infty a_j^i(\lambda)\|\trackpj{t} - \projectionOf{\invProjectionOf{\trackpj{t-1}}}\|^2 d\lambda
+    E((x + \Delta x)(x+\Delta x)^\top) = E(xx^\top) + E(x \Delta x^\top) \\
+    + E(\Delta x x^\top) + E(\Delta x \Delta x^\top)
   \end{multline}
-
-The tricky part here is inverse projection $\invProjectionOf{.}$ . When we
-project an image point back to 3D we get a ray $\lambda K^{-1}\trackpj{t-1}$
-which is ambiguous up to a scale factor $\lambda$. Using our hypothesized 3D
-layout of the scene we can estimate this scale factor, we
-can compute a distribution over the $\lambda$. 
-\subsubsection{Occupancy function}
-Assuming occupancy to be a
-probability distribution over 3D space. For each traffic participant the
-occupancy is modeled as a logistic function 
-\newcommand{\occf}{f^i_{occ}(\mathbf{x})}
-\begin{align}
-   \occf = L(\mathbf{x}; \pos{i}{t}, \Sigma_i)
-\end{align}
-where $L(.)$ is the logistic function defined by
-\begin{align}
-  L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i) = \frac{1}{
-    1 + e^{-k(1 - d(\mathbf{x},\pos{i}{t-1}))}
-    }
-\end{align}
-where $d(\mathbf{x},\pos{i}{t-1}) =
-(\mathbf{x}-\pos{i}{t-1})^\top\Sigma_i(\mathbf{x}-\pos{i}{t-1})$ and $k =
-10\ln{49}$. $k$ is chosen such that $L(.) = 0.98$ when $d(.) =
-0.9$
-
-We model the probability of a point being projected to a camera is dependent
-up two factors, (1) reflection and (2) transmission through intermediate
-space. 
-\subsubsection{Reflection probability}
-For lambertian reflection we replace the surface normal with the
-gradient of occupancy.
-\begin{align}
-  P_{\text{reflection}} = \sum_i (\max \{0, \nabla \occf^\top
-  \hat{\mathbf{r}_j}\})^2
-\end{align}
-where $\hat{\mathbf{r}_j} =
-\frac{K^{-1}\trackpj{t-1}}{\|K^{-1}\trackpj{t-1}\|}$ is unit vector in the
-direction of ray. The gradient in the direction opposite to ray yields -ve
-probability which needs to be clipped off. Squaring the function keep it
-smooth near zero.
-
-\subsubsection{Transmission probability}
-A model for transmission of light through a material of thickness $x$,
-density $\rho$ and opacity $k_o$ is given by Beer-Lambert law 
-\begin{align}
-  I(x) = I_0e^{-k_o\rho x}
-\end{align}
-
-Since both opacity and density are represented by our occupancy function
-$\occf$, and also the domain of our $\occf$ is $[0, 1]$ instead of $[0,
-\infty]$ as in case of $k_o$; we replace $e^{-k_o\rho}$ by our transparency
-function $1 - \occf$. So the transmission probability over a small distance
-$d\lambda$ is given by
-\begin{align}
-  P_{\text{transmission}}(\lambda + d\lambda) =
-  P_{\text{transmission}}(\lambda) (1-\occf)^{d\lambda}
-\end{align}
-\newcommand{\ray}{\hat{\mathbf{r}}_j}
-\newcommand{\occfray}{f_{occ}(\lambda\ray)}
-
-For our given ray $\mathbf{x}_j = \lambda \ray$, the probability that the point
-$\trackpj{t-1}$ is reflected from a distance $\lambda$ is given by
-
-\newcommand{\lambdadist}{f_{\lambda}(\trackpj{t-1}, \lambda)}
-\begin{align}
-  \lambdadist &= P_{\text{reflection}}
-  \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} %\\
-  %= \max \{ 0, (\nabla f_{occ}&(\lambda \ray)^\top \ray) \}
-  %\prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
-\end{align}
-where $\prod_{0}^{\lambda}$ represents the \emph{product integral} from $0$ to
-$\lambda$. A product integral is a simple integral in log domain
-\begin{align}
-  \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} =
-  e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
-\end{align}
-
-% Once we have our distribution over $\lambda$, $\lambdadist$ we can compute the
-% reprojection of $\trackpj{t-1}$ over image in time $t$ as a function of
-% $\lambda$. Let
-
-\subsubsection{Reprojection error}
-
-\begin{align}
-  f^{i}_{reproj}&(\trackpj{t-1}, \lambda) =
-  \projectionOf{\invProjectionOf{\trackpj{t-1}}}\\
-  %&= K(R^i_t ((R^i_{t-1})^\top\lambda \ray - (R^i_{t-1})^\top T_{t-1}) + T_{t})\\
-  &= \frac
-  {p_{1:2}\lambda + q_{1:2}}
-  {p_{3}\lambda + q_{3}}
-\end{align}
-where $p_{1:3} = KR^i_t(R^i_{t-1})^\top\ray$ and
-$q_{1:3} = KR^i_t(R^i_{t-1})^\top T_{t-1} + KT_t$
-
-Now that we have an association from TP $i$ to point track $j$ through
-$\lambda$, we can come up with an association probability
-\newcommand{\occfxi}{L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i)}
-\newcommand{\occfi}{L(\lambda \ray; \pos{i}{t-1}, \Sigma_i)}
-\newcommand{\assocP}{a^{i}_{j,t-1}(\lambda)}
-\newcommand{\assocPk}{a^{i}_{j,t-1}(\lambda_k)}
-\begin{align}
-   \assocP &= \frac{(\max \{ 0, \nabla \occf^\top
-\ray \})^2 }{P_{\text{reflection}}}\lambdadist\\
-&=(\max \{ 0, \nabla \occf^\top \ray \})^2
-  \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
-\end{align}
-
-Note that this fraction although called association probability does not
-capture the entire information that we have available for compute association
-of points to tracks. This above fraction is the association probability given 
-the hypothesized parameters of traffic participant model. Given that a point is
-observed on the image the sum of probability marginalized over other parameters
-must be one i.e.
-\begin{align}
-    \sum_{i = 1}^N
-    \int_1^{\infty}
-    \assocP d\lambda = 1
-\end{align}
-
-To compute the association probability between traffic participant $i$ and
-point track $j$ we must use re-projection error as well. When the association
-$i$ and $j$ is right and the point of reflection is at depth $\lambda$ the
-re-projection error must be zero, otherwise the error becomes a measure of
-distance from the true solution:
-
-\newcommand{\Ereproj}{E^{(ij)}_{\text{reproj}}}
-\begin{align}
-  \Ereproj(\lambda) = \|\trackpj{t} - f^i_{reproj}(\trackpj{t-1}, \lambda)\|^2
-\end{align}
-
-The error terms can be converted to probability domain by considering the error
-term as negative log of probablity
-
-\begin{align}
-  P^{(ij)}_{\text{assoc by reproj}}(\lambda) = \frac{1}{\sqrt{2\pi}}\exp(-\Ereproj(\lambda))
-\end{align}
-
-Using both the evidence terms we can write probability of association as
-\begin{align}
-  P^{(ij)}_{\text{assoc}} \propto \int_0^{\infty} \assocP \frac{1}{\sqrt{2\pi}}\exp(-\Ereproj(\lambda))d\lambda
-  \label{eq:prob-assoc}
-\end{align}
-
-However, for estimating the overall energy we just need to compute the expected
-value of the re-projection error for given parameters, i.e.
-
+  where the terms $E(x \Delta x^\top)$ denote the correlation between the data
+  vector and the uncertainty in the data. Although we understand that in our case
+  the data is the appearance based detection score and uncertainty because of
+  occlusion is closely related to the appearance and hence detection score, we
+  assume independence between $x$ and $\Delta x$. Hence our resultant covariance
+  matrix $ E((x + \Delta x)(x+\Delta x)^\top) = \Sigma + \Delta \Sigma$
+  are 4D. But that should not be a problem because the detection scores are
+  modeled as $[x_{\text{min}}, y_{\text{min}}, x_{\text{max}},
+  y_{\text{max}}]^\top$, we can stack the vectors in the soft occlusion region
+  domain as the regions are independent of min or max variation. The parameters
+  of 4D occlusion distribution are given by
+
+  \begin{align}
+    \mu'_{Oij} = [\mu_{Oij}^\top \mu_{Oij}^\top]^\top
+    \Sigma'_{Oij} = \begin{bmatrix}
+      \Sigma_{Oij} & \Sigma_{Oij} \\
+  \Sigma_{Oij} & \Sigma_{Oij}
+    \end{bmatrix}
+  \end{align}
+
+  With our
+  discussion so far, the function $O_{ij}(.)$ gives an additional measure of
+  uncertainty associated with each point in the space.
+\end{comment}
+
+% Explanation of Beizer curves is not needed %%%%%%%%%%%%%%%%%%%
+% A lane is modeled by four control points of a \Beizer curve $L_j = \{l_0, l_1,
+% l_2, l_3\}$. The parametric curve is given by $L_j(k) = \sum_{i=0}^3 {}^3C_i
+% (1-t)^{3-i}t^i l_i$. \Beizer are double differentiable so one can find
+% tangents ($L'_j(k)$) and normals $R_{\frac{\pi}{2}}L'_j(k)$ where 
+% $R_{\frac{\pi}{2}} = \begin{bmatrix} 0 & -1 \\ 1 & 0 \end{bmatrix}$ is
+% $90^\circ$ rotation matrix.
+
+%Using standard algorithms \cite{ma2003point, chen2007improved}, we 
+%approximate the closest point on a \Beizer curve $k_x = \projOnLane{x}$.
+%Consequently one can get solutions for shortest distance $s =
+%\text{DIST}(L_j(k), x)$ and orientation at a closest point on the lane
+%$\mathbf{t} = \text{TAN}(L_j(k), x)$.
+
+% \subsubsection{Position in lane}
+%
+% \begin{align}
+%   \Energy{plane} &=
+%   \min_{j = 0}^{n_l} \text{DIST}(L_j(k), \pos{i}{t})
+% \end{align}
+%
+ % 
+ % We normalize it with the confidence in lane positions.
+ % 
+ % \begin{align}
+ %   \Energy{plane} &=
+ %   \min_{m = 0}^{n_l} \text{DIST}(L_m(k), \pos{i}{t})
+ %   \LaneUncertainty{\pos{i}{t}}
+ % \end{align}
+
+%\subsubsection{Orientation within lane}
+%\begin{itemize}
+%\end{itemize}
+
+% \begin{align}
+%   \Energy{olane} &= 1 - \text{TAN}(L_l(k),  \pos{i}{t})
+%   \cdot
+%   \ori{i}{t}
+% \end{align}
+% 
+% 
+% 
+% This model needs to be scaled by uncertainty. For example, if we want to say
+% that the farther the lane is from the camera we are less sure about lane
+% orientation and hence this evidence term we scale it by say square of distance
+% of the car position from camera.
+
+% \begin{align}
+%   \Energy{olane} &= 
+%   (1 - \ori{i}{t} \cdot \text{TAN}(L_{m^*}(k),  \pos{i}{t}) )
+%   
+% \end{align}
+% where $m^* = \arg \min_m \text{DIST}(L_m(k), \pos{i}{t})$
+
+\begin{comment}
+
+\subsection{Collisions}
+
+The collision constraint among TPs can be modelled by
+pairwise distance based constraints. But having constraints between each pair
+of participants is bound to create cycles and computational inefficient.
+Among game developers it is common to use spatial hashing to find collision
+candidates and use pairwise constraints only among those. While this will
+enable us to speed up collision checking, we will still end up inducing cycles
+in the model. There are two ways to break these cycles, 1) disable the cross
+lane collision checking 2) created a weighted graph among collision
+candidates weighted by distance and then find a minimum spanning
+tree to break cycles. (1) is too strong of an assumption hence we focus on the
+second approach.
+
+There are two possible approaches to find collision among candidates (1)
+polygon intersection methods (2) soft ellipse intersection method. Boost
+provides scan line based approach to find intersections of polygons. Since our
+polygons are simple rectangles, this approach can be very fast. Other approach
+is to approximate rectangles with ellipses and finding if the ellipses
+intersect.  This intersection can be computed analytically.
+
+\begin{align}
+  \EnergyCol &= \begin{cases}
+  \infty &\text{if INTERSECTS}(\pos{i}{t}, \dimsn{i}, \pos{j}{t},
+  \dimsn{j})\\
+  0 &\text{otherwise}
+  \end{cases}
+\end{align}
+
+%For smoother collision probability see Section \ref{sec:smoothercollision}.
+
+\subsubsection{Ellipse-ellipse intersection}
+\label{sec:ellipseintersection}
+A rectangle with sides $2a$ and $2b$ can be approximated by an ellipse with
+equation $\frac{x^2}{a^2} + \frac{y^2}{b^2} = 1$. But this ellipse is inside
+the rectangle. To enclose the rectangle, scale the ellipse by a factor of
+$\sqrt{2}$. The equation becomes, $\frac{x^2}{2a^2} + \frac{y^2}{2b^2} = 1$.
+For rotation $\psi$ and center $\pos{i}{t}$, the equation of ellipse can be
+re-written as:
+\begin{align}
+  (\mathbf{x} - \pos{i}{t})^\top\Sigma_i^{-1}(\mathbf{x} - \pos{i}{t}) &= 1
+\end{align}
+where
+\begin{align}
+  \Sigma_i^{-1} &= \begin{bmatrix}
+    \frac{\cos^2{\psi}}{2a^2} + \frac{\sin^2{\psi}}{2b^2} &
+    \frac{\cos{\psi}\sin{\psi}}{2}(\frac{1}{b^2} - \frac{1}{a^2})\\
+    \frac{\cos{\psi}\sin{\psi}}{2}(\frac{1}{b^2} - \frac{1}{a^2}) &
+    \frac{\sin^2{\psi}}{2a^2} + \frac{\cos^2{\psi}}{2b^2} \\
+  \end{bmatrix}
+\end{align}
+
+% A point $\mathbf{x}$ is inside both ellipse $i$, $j$ if and only if
+% \begin{multline}
+%   (\mathbf{x} - \pos{i}{t})^\top\Sigma_i^{-1}(\mathbf{x} - \pos{i}{t}) +\\
+% (\mathbf{x} - \pos{j}{t})^\top\Sigma_j^{-1}(\mathbf{x} - \pos{j}{t})
+%   \le 2
+% \end{multline}
+% which is equivalent to
+% \begin{multline}
+%   (\mathbf{x} - \mu_c)^\top\Sigma_c^{-1}(\mathbf{x} - \mu_c)
+%   + \pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t}\\
+%   + \pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t}
+%   - \mu_c^\top\Sigma_c^{-1}\mu_c
+%   \le 2
+% \end{multline}
+% where $\Sigma_c = (\Sigma_i^{-1} + \Sigma_j^{-1})^{-1}$ and $\mu_c =
+% \Sigma_c(\Sigma_i^{-1}\pos{i}{t} + \Sigma_j^{-1}\pos{j}{t})$.
+% 
+% There is at least one point inside both ellipse if 
+% \begin{align}
+%   \pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t}
+%   + \pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t}
+%   - \mu_c^\top\Sigma_c^{-1}\mu_c
+%   &\le 2
+% \end{align}
+% 
+% The left hand side can be interpreted as distance between two ellipses, which
+% is 2 when the two ellipses collide and $0$ when two ellipse completely
+% overlap.
+
+\subsubsection{Smoother collision probability}
+\label{sec:smoothercollision}
+%The above mentioned ellipse-ellipse intersection formulation gives us an
+%insight: the distance between two oriented ellipse boundaries can be again
+%formulated as a distance metric\footnote{TODO:proof}.
+Instead of using Gaussians to model
+collision constraints as done by \cite{milan2013continuous}, we use a more
+steeper sigmoid function.
 \begin{multline}
-  \Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i,\{ \dimsn{i} \}_i) = \\
-    \sum_{i = 1}^N
-    \sum_{j = 1}^{M}
-    \int_1^{\infty}
-    a^i_{j,t-1}(\lambda) 
-    \|\trackpj{t} - f^i_{reproj}(\trackpj{t-1}, \lambda)\|^2
-    d\lambda
+  \EnergyCol = \frac{1}{1 +
+\exp(-k(\pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t})-1)}\\
+\frac{1}{1 +
+\exp(-k(\pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t})-1)}
 \end{multline}
-
-If the aim is to find the best possible association, it is easier as we need to
-to compute the association that minimizes the expected re-projection error for
-point $j$. It remains to be seen that how the minima of following expression relates to minima of \eqref{eq:prob-assoc}
-
-\begin{align}
-  i^* = \argmin_{i=1}^N \int_0^\infty \assocP \Ereproj(\lambda) d\lambda
-\end{align}
-
-Since the computation of $\assocP$ entirely depends on hypothesized parameters,
-it severely limits the applicability of this method outside this kind of
-parameterized model.
-
-\subsubsection{Approximations}
-\newcommand{\Ptrans}{P_{\text{transmission}}}
-\newcommand{\Prefl}{P^i_{\text{reflection}}}
-\newcommand{\dishort}{d_i(\mathbf{x})}
-
-Reflection probability of $i$th traffic participant is easy to compute
-analytically 
-\begin{multline}
-  \Prefl =
-  (\max \{ 0, \nabla \occf^\top \ray \})^2 \\
-  = (\max \{ 0, \nabla \occfxi^\top\ray \})^2
-  \label{eq:analytic-prefl}
-\end{multline}
-where 
-\begin{multline}
-  \nabla \occfxi^\top\ray \\=
-  \nabla k\dishort \sech^2\left(\frac{k}{2}\dishort\right)
-\end{multline}
-where $\dishort = 1-d(\mathbf{x}, \pos{i}{t-1})$ is a signed distance measure
-from the contour of the ellipsoid where $d(\mathbf{x}, \pos{i}{t-1})$ is 1.
-
-However, the transmission probability needs to be approximated.  
-%
-% \subsubsection{Computing $\Prefl$ and $\Ptrans$}
-% Focusing on  $\nabla \occfxi$ 
-% 
-% \begin{multline}
-%   \nabla \occfxi =\\
-%   \frac{-k\nabla d(\mathbf{x}, \pos{i}{t-1})e^{-k(1-d(\mathbf{x}, \pos{i}{t-1}))}}{
-%     (1 + e^{-k(1-d(\mathbf{x}, \pos{i}{t-1}))})^2
-%   } \\ 
-%   = -k\nabla d(\mathbf{x}, \pos{i}{t-1})\sech^2\left(\frac{k}{2}(1-d(\mathbf{x},
-%   \pos{i}{t-1}))\right)
-%   \\
-%   = \nabla k\dishort \sech^2\left(\frac{k}{2}\dishort\right)
-% \end{multline}
-% where $\dishort = 1-d(\mathbf{x}, \pos{i}{t-1})$ is a signed distance measure
-% from the contour of the ellipsoid where $d(\mathbf{x}, \pos{i}{t-1})$ is 1.
-% Focusing on $\nabla d(.)$
-% 
-% \begin{align}
-%   \nabla d(\mathbf{x}, \pos{i}{t-1}) = 2\Sigma_i(\mathbf{x} - \pos{i}{t-1})
-% \end{align}
-% Back to \eqref{eq:analytic-prefl}
-% 
-% \begin{multline}
-%   (\max \{ 0, \nabla \occf^\top \ray \})^2 = \\
-%   \sech^4\left(\frac{k}{2}\dishort\right) 
-%   (\max \{ 0 , \nabla k\dishort^\top\ray\})^2
-% \end{multline}
-% 
-% The probability is simply $\sech^2(.)$ scaled by gradient of ellipsoid
-% $\nabla k\dishort$ projected in the ray direction $\ray$.
-% 
-% \begin{align}
-%   \Ptrans = 
-%   e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
-% \end{align}
-% \begin{multline}
-% \int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}
-% =  \\
-% \int_{1}^{\lambda} \ln{\left(1 - \sum_i \occfi\right)}{d\lambda}
-% \end{multline}
-% 
-% The above integral is very difficult to approximate or compute analytically.
-So based on intuition, we approximate the $\Ptrans$ by following function
-\begin{align}
-\label{eq:evalCumulativePtrans}
-  \Ptrans &= \prod_i L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)L_{\lambda}(\lambda; \mu^i_d)\\
-  L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u) &= \frac{1}{
-    1 + e^{-k_u(1 - (\mathbf{u} - \mu^i_u)^\top\Sigma^i_u(\mathbf{u} -
-    \mu^i_u))}
-  }
-  \\
-  L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d) &= \frac{1}{
-  1 + e^{-k_d(\lambda - \mu^i_d(\mathbf{u}))}
-}
-\end{align}
-where 
-\begin{align}
-  \mu_u^i &= \projectionOf{\pos{i}{t-1}} \label{eq:muiudef}\\
-  \Sigma_u^i &= \projectionOf{\Sigma_i} \label{eq:sigmauidef}\\
-  \mu^i_d(\mathbf{u}) &= \relp{i}{t}\\
-  k_u &= 10\log(49)\\
-  k_d &= \frac{\log(49)}{\sqrt{h^2 + l^2 + w^2}}
-  \label{eq:ptransmissionInit}
-\end{align}
-is the distance of the centre of the traffic participant from the camera.
-
-% $\mu^i_d(\mathbf{u}) = \min_{\lambda} d^2_i(\lambda K^{-1}\mathbf{u})$.
-% $\mu^i_d(\mathbf{u})$ is the closest point to the unit contour of ellipsoid.
-% If there are multiple such points, the point closest to the camera is taken as
-% $\mu^i_d(\mathbf{u})$
-
-The association probability becomes
-
-\newcommand{\Lu}{L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)}
-\newcommand{\Llambda}{L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d)}
-\begin{multline}
-  \assocP = 
-    \sech^4\left(\frac{k}{2}\dishort\right)
-    (\max \{ 0, \nabla k\dishort^\top\ray \})^2\\
-  \prod_i \Lu
-    \Llambda \\
-    \label{eq:assocCoeffEval}
-\end{multline}
-
-So the energy becomes
-
-\begin{multline}
-  \label{eq:integrand}
-  \Energy{track}(.) = 
-    \sum_{i = 1}^N
-    \sum_{j = 1}^{M}
-    \int_1^{\infty}
-    \assocP
-    \Ereproj(\lambda)
-    d\lambda
-\end{multline}
-where $x = \lambda \ray$ and $\Ereproj(\lambda) = \|\trackpj{t} -
-f^i_{reproj}(\trackpj{t-1}, \lambda)\|^2$ is reprojection error which is a
-quadratic in $\lambda$
-
-The integral in the above expression is computed numerically.
-
-\subsection{Numerical integration}
-Numerical integration is possible by computed by sampling. Samples need to be
-generated from the association probability $\assocP$ for a given $j$. We take
-proposal distribution to be a GMM with modes around probable reflection points.
-The weights of all Gaussians in the mixture are proportional to the distance of
-the point $j$ from projection of ellipsoid centre i.e. 
-\begin{align}
-  A_{ij} = \frac{1}{Z_j}\exp(-(\trackpj{t} - \mu^i_u)^\top\Sigma_u^i(\trackpj{t} - \mu^i_u))
-\end{align}
-where $Z_j = \sum_{i=1}^N A_{ij}$ and $\mu^i_u$ and $\Sigma_u^i$ are described in \eqref{eq:muiudef} and \eqref{eq:sigmauidef} respectively.
-The range of Gaussian $G_i$
-must be in the interval $[\|\relp{i}{t}\|, \|\relp{i}{t}\| -
-\sqrt{3}\max(\dimsn{i})]$. Hence we take the mean as $\|\relp{i}{t}\| -
-\frac{\sqrt{3}}{2}\max(\dimsn{i})$ and variance as
-$\frac{1}{3}\max(\dimsn{i})^2$. The distribution from which we sample is 
-\newcommand{\Gauss}{\mathcal{N}}
-\newcommand{\PropDist}{\mathcal{W}_j}
-\begin{align}
-  \PropDist(\lambda) = \sum_i A_{ij} \Gauss(\lambda; \|\relp{i}{t}\| -
-  \frac{\sqrt{3}}{2}\max(\dimsn{i}), \frac{1}{\sqrt{3}}\max(\dimsn{i}))
-\end{align}
-And the numerical integral with $K$ samples is computed by
-\begin{align}
-    \int_1^{\infty}
-    \assocP
-    \Ereproj(\lambda)
-    d\lambda
-    =
-    \frac{1}{K}\sum_k \Ereproj \frac{\assocPk}{\PropDist(\lambda_k)}
-\end{align}
-where $\lambda_k$ is the $k$th sample drawn from $\PropDist(\lambda)$.
+where $k$ is steepness parameter.
+%$d(.)$ is the distance metric defined as:
+%\begin{multline}
+%  d(\pos{i}{t}, \dimsn{i}, \pos{j}{t}, \dimsn{j})
+%  =
+%  \pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t} \\
+%  + \pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t}
+%  - \mu_c^\top\Sigma_c^{-1}\mu_c
+%\end{multline}
+
+\end{comment}
 
 \begin{comment}
+
   %%%%%%%%%%%%%%%% Analytical attempt to integration %%%%%%%%%%%%%%%%%%%%%
@@
   where $\poly^{(n)}_{ijk}$ denotes a polynomial $k$ of order $n$ dependent upon $i$th
-  traffic participant and $j$th point. This integrand is still too difficult to
+  TP and $j$th point. This integrand is still too difficult to
   be solved or approximated analytically.
@@
 
-   \newcommand{\muijl}{\mu^{ij}_{\lambda}}
-   \newcommand{\sigmaijl}{\sigma^{ij}_{\lambda}}
    \begin{align}
@@
 
-\subsubsection{Sigma of ellipsoid}
-\label{sec:sigmacomputation}
-
-\newcommand{\Sigmait}{\Sigma^i_t}
-\newcommand{\muit}{\mu^i_t}
-\begin{align}
-  \muit &= \begin{bmatrix}
-  0& 0& \frac{h}{2}
-  \end{bmatrix}^\top\\
-  \Sigmait &= \begin{bmatrix}
-    \frac{4}{l^2} & 0 & 0 \\
-    0 & \frac{4}{w^2} & 0 \\
-    0 & 0 & \frac{4}{h^2}
-  \end{bmatrix}
-\end{align}
-
-In tracklet coordinates the equation of ellipsoid is 
-\newcommand{\xt}{\mathbf{x}_t}
-\newcommand{\xc}{\mathbf{x}_c}
-\begin{align}
-  (\xt - \muit)^\top \Sigmait (\xt - \muit) = 1
-\end{align}
-
-Moving to camera coordinates
-\newcommand{\Rctot}{R}
-\newcommand{\tctot}{t}
-\begin{align}
-  (\Rctot \xc + \tctot - \muit)^\top \Sigmait (\Rctot \xc + \tctot - \muit) = 1
-\end{align}
-
-\newcommand{\tcmut}{t'}
-Let $\tcmut = \tctot - \muit$
-\begin{align}
-  (\Rctot \xc + \tcmut)^\top \Sigmait (\Rctot \xc + \tcmut) = 1
-\end{align}
-\begin{align}
-  \xc^\top \Rctot^\top \Sigmait \Rctot \xc + 2 (\Rctot^\top \tcmut)^\top  \Rctot^\top\Sigmait \Rctot \xc
-  + \tcmut^\top \Sigmait \tcmut = 1
-\end{align}
-\newcommand{\Sigmaic}{\Sigma'^i_c}
-\newcommand{\muic}{{\mu^i_c}}
-Let $\Sigmaic = \Rctot^\top \Sigmait \Rctot$ and $\muic = - \Rctot^\top
-\tcmut$
-\begin{align}
-  (\xc - \muic)^\top\Sigmaic(\xc - \muic) - \muic^\top\Sigmaic\muic +
-  \tcmut^\top \Sigmait \tcmut = 1
-\end{align}
-\newcommand{\Sigmaicf}{\Sigma^i_c}
-Let $\Sigmaicf = \frac{\Sigmaic}{1 - \tcmut^\top \Sigmait \tcmut +
-\muic^\top\Sigmaic\muic}$
-\begin{align}
-(\xc - \muic)^\top\Sigmaicf(\xc - \muic) = 1
-\end{align}
-
-Hence, we have following expression for mean and sigma of ellipsoid:
-\begin{align}
-  \label{eq:ellipsoidMeanSigma}
-  \muic &= - \Rctot^\top \tcmut \\
-  \Sigmaicf &= \frac{\Sigmaic}
-{1 - \tcmut^\top \Sigmait \tcmut + \muic^\top\Sigmaic\muic}
-\end{align}
-
 % \subsection{Object detection score}
@@
 % Appearance map is a shape prior that requires \emph{Scene labeling} input.
-
-\section{Continuous object detection score energy with occlusion}
-
-To start with we have hypothesized 3D bounding boxes $\{ \dimsn{i} \}_i$
-over all traffic participants and we have object detection scores modeled as
-mixture of Gaussians over four dimensional space of bounding box boundaries.
-Let the detection score function over the detection $\bb{i}$ be 
-%
-\begin{align}
-  S(\bb{i}) = \sum_j A_j \exp((\bb{i}-\mu^{(d)}_j)^\top \Sigma^{(d)-1}_j
-  (\bb{i}-\mu^{(d)}_j))
-\end{align}
-%
-
-\subsection{Soft occlusion regions}
-The soft occlusion regions is exactly the $\Ptrans$
-%
-\begin{align}
-  O_{j}(x; \mu_{Oj}, \Sigma_{Oj}) = 1 - \Ptrans
-\end{align}
-%
-
-\subsection{Merging occlusion regions with detection score}
-What does detection score function represents? It is a measure of
-correlation of trained object features and the features in the candidate
-bounding box. If the detection scores are indeed Gaussians around the mean
-bounding box $\mu_j$, the $\Sigma_j^{-1}$ represents the variance (and
-covariance) around the mean bounding box. But when the candidate objects seem
-to be occluded we have additional information available. In such a case, we
-can say that the occluded object might have unexpected effect on the detection
-scores. However, the uncertainty in the detection score in loop sided. The
-mean detection bounding box must have picked up correct boundaries on the
-un-occluded sides but we cannot say the same about occluded boundaries. The
-effect on detection score depends a lot on the features of the occluder. Given
-this understanding we want to decrease our confidence on the mean detection
-boundaries around the occluded boundaries. One of the simplest ways will be to
-scale the appropriate diagonal element of $\Sigma_j$ by an appropriate scaling
-factor. But how does occlusion affects the non diagonal terms. Consider that we
-have a set of measurements whose mean and variance are known $\mu = E(x)$ and $\Sigma = E ((x - \mu_x)(x - \mu_x)^\top)$. We want to know the
-affect of uncertainty on mean and variance of existing observations. On adding
-noise $[\Delta x, \Delta y]^\top$ with zero mean and covariance $\Delta
-\Sigma = E(\Delta x \Delta x^\top)$ the covariance of new data is given by
-\begin{multline}
-  E((x + \Delta x)(x+\Delta x)^\top) = E(xx^\top) + E(x \Delta x^\top) \\
-  + E(\Delta x x^\top) + E(\Delta x \Delta x^\top)
-\end{multline}
-where the terms $E(x \Delta x^\top)$ denote the correlation between the data
-vector and the uncertainty in the data. Although we understand that in our case
-the data is the appearance based detection score and uncertainty because of
-occlusion is closely related to the appearance and hence detection score, we
-assume independence between $x$ and $\Delta x$. Hence our resultant covariance
-matrix $ E((x + \Delta x)(x+\Delta x)^\top) = \Sigma + \Delta \Sigma$
-
-We observe that the soft occlusion regions are 2D while the detection scores
-are 4D. But that should not be a problem because the detection scores are
-modeled as $[x_{\text{min}}, y_{\text{min}}, x_{\text{max}},
-y_{\text{max}}]^\top$, we can stack the vectors in the soft occlusion region
-domain as the regions are independent of min or max variation. The parameters
-of 4D occlusion distribution are given by
-
-\begin{align}
-  \mu'_{Oij} = [\mu_{Oij}^\top \mu_{Oij}^\top]^\top
-  \Sigma'_{Oij} = \begin{bmatrix}
-    \Sigma_{Oij} & \Sigma_{Oij} \\
-\Sigma_{Oij} & \Sigma_{Oij}
-  \end{bmatrix}
-\end{align}
-
-With our
-discussion so far, the function $O_{ij}(.)$ gives an additional measure of
-uncertainty associated with each point in the space. To finally re-model our
-detection scores scaled by continuous occlusion we sample $O_{ij}(.)$ at the
-mean detection boundaries from GMM $S(.)$ and we scale the detection boundary
-variance by $\mathcal{P}_{j} = \rho_{j}\rho_{j}^\top$ where $\rho_{j} =
-O_{j}(\mu^{(d)}_i; \mu'_{Oj}, \Sigma'_{Oj})$. The new variance
-in detection score is given by 
-%
-\begin{align}
-  \Sigma'^{(d)}_j = \mathcal{P}_{j}
-  + \Sigma^{(d)}_j
-\end{align}
-%
-The detection scores GMM with occlusion is given by replacing the covariance
-matrix
-\begin{align}
-  S'(\bb{i}) = \sum_j A_j \exp((\bb{i}-\mu^{(d)}_j)^\top \Sigma'^{(d)-1}_j
-  (\bb{i}-\mu^{(d)}_j))
-\end{align}
-
-\newcommand{\Beizer}{B\'eizer }
-\subsection{Lane energy}
-\label{sec:laneEnergy}
- The lanes be are modeled as splines. The lanes geometry information can be
- obtained from camera input as well as from the available maps localized by
- GPS. We need to combine information in a different framework to lead to a
-more accurate solution by using both the sources. In a probablistic framework
-it is always useful to compute uncertainty along the estimated values.
-Here we assume that the confidence in lane detection is inversely proportional
-to the squre of distance of of the specific point on the lane to the camera
-\newcommand{\LaneUncertainty}[1]{\Sigma_{L_m}(#1)}
-$\Sigma_{L_m}({x}_{L_m}) = \frac{1}{\|\mathbf{x}_{L_m} - \egop\|^2}$.
-
-A lane is modeled by four control points of a \Beizer curve $L_j = \{l_0, l_1,
-l_2, l_3\}$. The parametric curve is given by $L_j(k) = \sum_{i=0}^3 {}^3C_i
-(1-t)^{3-i}t^i l_i$. \Beizer are double differentiable so one can find
-tangents ($L'_j(k)$) and normals $R_{\frac{\pi}{2}}L'_j(k)$ where 
-$R_{\frac{\pi}{2}} = \begin{bmatrix} 0 & -1 \\ 1 & 0 \end{bmatrix}$ is
-$90^\circ$ rotation matrix.
-
-\newcommand{\projOnLane}[1]{\pi_{L_m(k)}(#1)}
-Now, there are some algorithms \cite{ma2003point, chen2007improved} to
-approximate the closest point on a \Beizer curve $k_x = \projOnLane{x}$.
-Consequently one can get solutions for shortest distance $s =
-\text{DIST}(L_j(k), x)$ and orientation at a closest point on the lane
-$\mathbf{t} = \text{TAN}(L_j(k), x)$.
-
-% \subsubsection{Position in lane}
-%
-% \begin{align}
-%   \Energy{plane} &=
-%   \min_{j = 0}^{n_l} \text{DIST}(L_j(k), \pos{i}{t})
-% \end{align}
-%
- % 
- % We normalize it with the confidence in lane positions.
- % 
- % \begin{align}
- %   \Energy{plane} &=
- %   \min_{m = 0}^{n_l} \text{DIST}(L_m(k), \pos{i}{t})
- %   \LaneUncertainty{\pos{i}{t}}
- % \end{align}
-
-\subsubsection{Orientation within lane}
-\begin{itemize}
-  \item We can find the tangent to a lane
-  \item The energy is given by the dot product between car orientation
-    and tangent to the lane at that point.
-\end{itemize}
-
-% \begin{align}
-%   \Energy{olane} &= 1 - \text{TAN}(L_l(k),  \pos{i}{t})
-%   \cdot
-%   \ori{i}{t}
-% \end{align}
-% 
-% 
-% 
-% This model needs to be scaled by uncertainty. For example, if we want to say
-% that the farther the lane is from the camera we are less sure about lane
-% orientation and hence this evidence term we scale it by say square of distance
-% of the car position from camera.
-
-% \begin{align}
-%   \Energy{olane} &= 
-%   (1 - \ori{i}{t} \cdot \text{TAN}(L_{m^*}(k),  \pos{i}{t}) )
-%   
-% \end{align}
-% where $m^* = \arg \min_m \text{DIST}(L_m(k), \pos{i}{t})$
-
-\begin{align}
-  \label{eq:laneOrientationEnergy}
-  \Energy{lane} &= 
-  \sum_{m \in M_{\text{close}}}
-  (1 - \ori{i}{t} \cdot \text{TAN}(L_{m}(k), \pos{i}{t}) )
-\LaneUncertainty{\pos{i}{t}}
-\end{align}
-where $M_{\text{close}} = \{m : \text{DIST}(L_{m}(k), \pos{i}{t}) < 50\} $ is
-the set of nearby lanes and 
-\begin{align}
-\LaneUncertainty{\pos{i}{t}} = 
-  \frac{1}{1 + exp(-q(w_{\text{road}} - \text{DIST}(L_{m}(k), \pos{i}{t})))}
-\end{align}
-for some constant $w_{\text{road}}$ that represents the width of the road.
-
-\begin{comment}
-
-\subsection{Collisions}
-
-The collision constraint among traffic participants can be modelled by
-pairwise distance based constraints. But having constraints between each pair
-of participants is bound to create cycles and computational inefficient.
-Among game developers it is common to use spatial hashing to find collision
-candidates and use pairwise constraints only among those. While this will
-enable us to speed up collision checking, we will still end up inducing cycles
-in the model. There are two ways to break these cycles, 1) disable the cross
-lane collision checking 2) created a weighted graph among collision
-candidates weighted by distance and then find a minimum spanning
-tree to break cycles. (1) is too strong of an assumption hence we focus on the
-second approach.
-
-There are two possible approaches to find collision among candidates (1)
-polygon intersection methods (2) soft ellipse intersection method. Boost
-provides scan line based approach to find intersections of polygons. Since our
-polygons are simple rectangles, this approach can be very fast. Other approach
-is to approximate rectangles with ellipses and finding if the ellipses
-intersect.  This intersection can be computed analytically.
-
-\begin{align}
-  \EnergyCol &= \begin{cases}
-  \infty &\text{if INTERSECTS}(\pos{i}{t}, \dimsn{i}, \pos{j}{t},
-  \dimsn{j})\\
-  0 &\text{otherwise}
-  \end{cases}
-\end{align}
-
-%For smoother collision probability see Section \ref{sec:smoothercollision}.
-
-\subsubsection{Ellipse-ellipse intersection}
-\label{sec:ellipseintersection}
-A rectangle with sides $2a$ and $2b$ can be approximated by an ellipse with
-equation $\frac{x^2}{a^2} + \frac{y^2}{b^2} = 1$. But this ellipse is inside
-the rectangle. To enclose the rectangle, scale the ellipse by a factor of
-$\sqrt{2}$. The equation becomes, $\frac{x^2}{2a^2} + \frac{y^2}{2b^2} = 1$.
-For rotation $\psi$ and center $\pos{i}{t}$, the equation of ellipse can be
-re-written as:
-\begin{align}
-  (\mathbf{x} - \pos{i}{t})^\top\Sigma_i^{-1}(\mathbf{x} - \pos{i}{t}) &= 1
-\end{align}
-where
-\begin{align}
-  \Sigma_i^{-1} &= \begin{bmatrix}
-    \frac{\cos^2{\psi}}{2a^2} + \frac{\sin^2{\psi}}{2b^2} &
-    \frac{\cos{\psi}\sin{\psi}}{2}(\frac{1}{b^2} - \frac{1}{a^2})\\
-    \frac{\cos{\psi}\sin{\psi}}{2}(\frac{1}{b^2} - \frac{1}{a^2}) &
-    \frac{\sin^2{\psi}}{2a^2} + \frac{\cos^2{\psi}}{2b^2} \\
-  \end{bmatrix}
-\end{align}
-
-% A point $\mathbf{x}$ is inside both ellipse $i$, $j$ if and only if
-% \begin{multline}
-%   (\mathbf{x} - \pos{i}{t})^\top\Sigma_i^{-1}(\mathbf{x} - \pos{i}{t}) +\\
-% (\mathbf{x} - \pos{j}{t})^\top\Sigma_j^{-1}(\mathbf{x} - \pos{j}{t})
-%   \le 2
-% \end{multline}
-% which is equivalent to
-% \begin{multline}
-%   (\mathbf{x} - \mu_c)^\top\Sigma_c^{-1}(\mathbf{x} - \mu_c)
-%   + \pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t}\\
-%   + \pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t}
-%   - \mu_c^\top\Sigma_c^{-1}\mu_c
-%   \le 2
-% \end{multline}
-% where $\Sigma_c = (\Sigma_i^{-1} + \Sigma_j^{-1})^{-1}$ and $\mu_c =
-% \Sigma_c(\Sigma_i^{-1}\pos{i}{t} + \Sigma_j^{-1}\pos{j}{t})$.
-% 
-% There is at least one point inside both ellipse if 
-% \begin{align}
-%   \pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t}
-%   + \pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t}
-%   - \mu_c^\top\Sigma_c^{-1}\mu_c
-%   &\le 2
-% \end{align}
-% 
-% The left hand side can be interpreted as distance between two ellipses, which
-% is 2 when the two ellipses collide and $0$ when two ellipse completely
-% overlap.
-
-\subsubsection{Smoother collision probability}
-\label{sec:smoothercollision}
-%The above mentioned ellipse-ellipse intersection formulation gives us an
-%insight: the distance between two oriented ellipse boundaries can be again
-%formulated as a distance metric\footnote{TODO:proof}.
-Instead of using Gaussians to model
-collision constraints as done by \cite{milan2013continuous}, we use a more
-steeper sigmoid function.
-\begin{multline}
-  \EnergyCol = \frac{1}{1 +
-\exp(-k(\pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t})-1)}\\
-\frac{1}{1 +
-\exp(-k(\pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t})-1)}
-\end{multline}
-where $k$ is steepness parameter.
-%$d(.)$ is the distance metric defined as:
-%\begin{multline}
-%  d(\pos{i}{t}, \dimsn{i}, \pos{j}{t}, \dimsn{j})
-%  =
-%  \pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t} \\
-%  + \pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t}
-%  - \mu_c^\top\Sigma_c^{-1}\mu_c
-%\end{multline}
-
-\end{comment}
-
-\subsection{Transition probability}
-Dynamics constraints should not only enforce smooth trajectories, but also the
-holonomic constraints.
-
-The following equation adds a penalty if the change in
-position is not in direction of previous orientation.
-
-\begin{align}
-  \label{eq:totalPosTransitionEnergy}
-  \Energy{dyn-hol} = 1 - \ori{i}{t-1} \cdot (\pos{i}{t} - \pos{i}{t-1})
-\end{align}
-
-The following equation adds a penalty for change in position and orientation
-but a penalty for change in velocity is much better approximation. However, in
-a Markovian setting that would mean extending the state space of the car to
-include velocity.
-
-\begin{align}
-  \Energy{dyn-ori} &= \|\ori{i}{t} - \ori{i}{t-1}\|^2\\
-  \Energy{dyn-vel} &= \|(\pos{i}{t} - 2\pos{i}{t-1}) + \pos{i}{t-2}\|^2
-\end{align}
-
-As a result the dynamics are modeled by weighted combination of holonomic
-constraint and smoothness constraints.
-
-\begin{align}
-  \WEnergy{dyn} &= \WEnergy{dyn-hol} + \WEnergy{dyn-ori} + \WEnergy{dyn-vel}
-\end{align}
-
-\subsection{Size Prior}
-
-Prior can include among many other things the size prior on the car.
-
-\begin{align}
-  \label{eq:totalSizeEnergy}
-  \Energy{prior} &= (\dimsn{i} - \expDimsn)^\top\Sigma_{\expDimsn}^{-1}(\dimsn{i} -
-  \expDimsn)
-\end{align}
-
-where $\expDimsn$ is the mean traffic participant dimensions and
-$\Sigma_{\expDimsn}$ is the correspondence covariance matrix.
-
-\begin{table*}
-  \begin{tabular}{|l|r|r|l|}
-    \hline
-    func            & equation                      & ms per 6 frames &
-    comment \\
-    \hline
-    totalBBoxEnergy & Sec \ref{sec:totalBBoxEnergy} & 268 & \\
-    laneEnergy      & Sec \ref{sec:laneEnergy}      & 163 & \\
-    laneOrientationEnergy & Eq \eqref{eq:laneOrientationEnergy} & 155 & The
-    equation summed up for all 6 tracklets\\
-    collisionEnergyHellingerDistance & Eq 
-    \eqref{eq:collisionEnergyHellingerDistance} & 93  & \\
-    totalPosTransitionEnergy & Eq \eqref{eq:totalPosTransitionEnergy} & 15 & \\
-    totalSizeEnergy & Eq \eqref{eq:totalSizeEnergy} & 0.9 & \\
-
-    \hline
-    occlusionMaskFromOptVector & Sec \ref{sec:occlusionMaskFromOptVector} &
-    123 &
-    \\
-    bboxEnergyFromOccMask & Eq \eqref{eq:bboxEnergyFromOccMask} & 140 &  \\
-    vis\_area\_from\_triangle & $\|\triangleProj{s} \setminus
-    \occ{\relpz{i}{t}}\|$ & 76 & \\
-    \hline
-    distance2curve & $\text{DIST}(L_j(k), x)$ & 74 & Called 2 times per
-    tracklet \\
-    filterMapWaysByDistance & $M_{\text{close}} = \{m : \text{DIST}(.) < 50\} $ & 52 & \\
-    area\_of\_triangle & $\|\triangleProj{s}\|$ & 48 & called 4 times per
-    tracklet \\
-    occlusionMask & Step 3 of Sec \ref{sec:occlusionMaskFromOptVector} & 46 &
-    \\
-    \hline
-  \end{tabular}
-
-  \begin{tabular}{|l|r|r|l|}
-    \hline
-    func            & equation                      & ms per 6 frames &
-    comment \\
-    \hline
-    totalContPtTracksEnergy & Sec \ref{sec:totalContPtTracksEnergy} & 25000 &
-    \\
-    integrand & Eq \eqref{eq:integrand} & 23000 & \\
-    repmat & & 5000 & \\
-    assocCoeffEval & Eq \eqref{eq:assocCoeffEval} & 4000 & \\
-    evalPreflection & Eq \eqref{eq:analytic-prefl} & 3000 & \\
-    gradfocci & $\nabla \occf^\top \ray$ & 2040 & \\
-    associationCoefficientInit & Eq
-    \eqref{eq:ptransmissionInit}\eqref{eq:ellipsoidMeanSigma} & 1706 & \\
-    projectToImage & $\frac{Ku}{Ku(3)}$ & 4000 & Called ~8 times per edge\\
-    evalCumulativePtrans & \eqref{eq:evalCumulativePtrans} & 1178 & \\
-    ptransmissionApproxInit & \eqref{eq:ptransmissionInit} & 1000 & \\
-    ellipsoidCentreDist & $(x-\mu)^\top \Sigma (x-\mu)$ & 1000 & \\
-    squeeze & & 951 &\\
-    trackletToCamTransform & $R_{\ori{i}{t}}, t$ & 786 & \\
-    ellipsoidMeanSigma & Eq \eqref{eq:ellipsoidMeanSigma} & 812 & \\
-    \hline
-  \end{tabular}
-\end{table*}
-
-{\small
-\bibliographystyle{ieee}
-\bibliography{model}
-}
 \end{document}
-%\documentclass[11pt]{report}
-%\usepackage{tikz}
-%\usetikzlibrary{fit,positioning}
-%\begin{document}
-%\begin{figure}
-%\centering
-%\begin{tikzpicture}
-%\tikzstyle{main}=[circle, minimum size = 10mm, thick, draw =black!80, node distance = 16mm]
-%\tikzstyle{connect}=[-latex, thick]
-%\tikzstyle{box}=[rectangle, draw=black!100]
-%  \node[main, fill = white!100] at (cit)  {$c_i^t$ };
-%  \node[main] at +(2.0cm, 1.0cm) (detect)  { $b$ };
-%  \node[main] at +(2.0cm, -1.0cm) (sfm)    { $t$ };
-%  \node[main] (lane)   [below=of cit] { $L$ };
-%  \path (cit) edge [connect] (detect)
-%        (cit) edge [connect] (sfm)
-%        (cit) edge [connect] (lane);
-%        \node[box, inner sep=4mm, fit=(cit) (detect) (lane),label=below right:N] {};
-%  \node[main, fill = white!100] at (cit-1)  {$c_i^{t-1}$ };
-%  \node[main] at +(2.0cm, 1.0cm) (detect)  { $b$ };
-%  \node[main] at +(2.0cm, -1.0cm) (sfm)    { $t$ };
-%  \node[main] (lane)   [below=of cit] { $L$ };
-%  \path (cit) edge [connect] (detect)
-%        (cit) edge [connect] (sfm)
-%        (cit) edge [connect] (lane);
-%        \node[box, inner sep=4mm, fit=(cit) (detect) (lane),label=below right:N] {};
-%
-%  %\node[rectangle, inner sep=4.4mm,draw=black!100, fit= (z) (w)] {};
-%  %\node[rectangle, inner sep=4.6mm, fit= (z) (w),label=below right:M, xshift=12.5mm] {};
-%  %\node[rectangle, inner sep=9mm, draw=black!100, fit = (theta) (z) (w)] {};
-%\end{tikzpicture}
-%\end{figure}
-%\end{document}
-%note - compiled with pdflatex

### 2014-11-10 CVPR/Source/abstract.tex
Reorganized paper tex files

--- 2014-11-08 Paper/model.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
-
-\usepackage{cvpr}
-\usepackage{times}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-%%%%%%%%%%% CVPR template packages end %%%%%%%%%%%%%%
-\usepackage{verbatim} % for comment environment
-% \usepackage{soul} % for \hl highlighting
-% Include other packages here, before hyperref.
-
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-
-%\cvprfinalcopy % *** Uncomment this line for the final submission
-
-\def\cvprPaperID{489} % *** Enter the CVPR Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-% 3D pose of the cars and ego motion
-\newcommand{\pos}[2]{\mathbf{p}^{(#1)}(#2)}
-\newcommand{\ori}[2]{\mathbf{\omega}^{(#1)}(#2)}
-\newcommand{\state}[2]{\mathbf{s}^{#1}(#2)}
-
-% ego pose
-\newcommand{\egop}[1][t]{\pos{c}{#1}}
-\newcommand{\egoo}[1][t]{\ori{c}{#1}}
-\newcommand{\egos}[1][t]{\state{c}{#1}}
-
-% relative pose between camera and car $i$
-\newcommand{\relp}[2]{\Omega^{#1}(#2)}
-\newcommand{\relpz}[2]{\Omega_z^{#1}(#2)}
-
-% 3D tracks on car $i$ in its own coordinate frame
-\newcommand{\tracklets}{\mathbf{X}^{(i)}_o}
-\newcommand{\tracklet}[1]{\mathbf{x}^{(i)}_{#1}}
-% track projections on camera
-\newcommand{\trackp}[1]{\mathbf{u}^{(i)}(#1)}
-\newcommand{\trackpj}[1]{\mathbf{u}_j(#1)}
-% Unclassified track point projected on camera
-\newcommand{\ucTrackp}{\mathbf{u}(t)}
-
-% dimensions of car $i$
-\newcommand{\dimsn}[1]{\mathbf{B}^{#1}}
-\newcommand{\expDimsn}{\hat{\mathbf{B}}}
-
-% projection function
-\newcommand{\projectionOf}[1]{\pi_{\relp{i}{t}}\left(#1\right)}
-\newcommand{\projectionOft}[1]{\pi_{\relp{i}{t+1}}\left(#1\right)}
-\newcommand{\centerProj}{\bar{\pi}_{\relp{i}{t}}(\dimsn{i})}
-\newcommand{\cornerProj}[1]{\pi^{#1}_{\relp{i}{t}}(\dimsn{i})}
-\newcommand{\triangleProj}[1]{\triangle^{#1}_{\relp{i}{t}}(\dimsn{i})}
-
-% bounding box corners on image
-\newcommand{\bb}[1]{\mathbf{d}^{#1}(t)}
-
-\newcommand{\Energy}[1]{\mathcal{E}^{it}_{\text{#1}}}
-\newcommand{\pEnergy}[1]{\mathcal{E}^{ijt}_{\text{#1}}}
-% Weighted energy
-\newcommand{\WEnergy}[1]{\lambda_{\text{#1}}\Energy{#1}}
-\newcommand{\EnergyCol}{\mathcal{E}^{ijt}_{\text{col}}}
-\newcommand{\WEnergyCol}{\lambda_{\text{col}}\EnergyCol}
-
-\newcommand{\occFreeProj}[1]{\Pi_{\relp{i}{t}}(#1)}
-\newcommand{\minx}{x_{\text{min}}}
-\newcommand{\miny}{y_{\text{min}}}
-\newcommand{\maxx}{x_{\text{max}}}
-\newcommand{\maxy}{y_{\text{max}}}
-\newcommand{\frontface}{F^i_\text{FF}(t)}
-
-\newcommand{\occ}[1]{o({#1})}
-\newcommand{\face}{F^i_k(t)}
-
-\newcommand{\invProjectionOf}[1]{\pi^{-1}_{\relp{i}{t}}\left(#1\right)}
-\newcommand{\occf}{f^i_{occ}(\mathbf{x}_j)}
-\newcommand{\occftot}{f_{occ}(\mathbf{x}_j)}
-\newcommand{\occft}[1]{f_{occ}(#1)}
-
-\newcommand{\ray}{\hat{\mathbf{r}}_j}
-\newcommand{\occfray}{f_{occ}(\lambda\ray)}
-\newcommand{\lambdadist}{f_{\lambda}(\trackpj{t-1}, \lambda)}
-
-\newcommand{\occfxi}{L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i)}
-\newcommand{\occfi}{L(\lambda \ray; \pos{i}{t-1}, \Sigma_i)}
-\newcommand{\assocP}{a^{(ij)}(\lambda)}
-\newcommand{\assocPk}{a^{(ij)}(\lambda_k)}
-
-\newcommand{\Ereproj}{E^{(ij)}_{\text{reproj}}}
-\newcommand{\Ptrans}{P^{(j)}_{\text{transmission}}(\lambda)}
-\newcommand{\Ptransmud}{P^{(j)}_{\text{transmission}}(\mu^{(i)}_d)}
-\newcommand{\Prefl}{P^{(ij)}_{\text{reflection}}(\lambda)}
-\newcommand{\dishort}{d_i(\mathbf{x})}
-
-\newcommand{\Lu}{L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)}
-\newcommand{\Llambda}{L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d)}
-
-\newcommand{\Gauss}{\mathcal{N}}
-\newcommand{\PropDist}{\mathcal{W}_j}
-
-\newcommand{\muijl}{\mu^{(ij)}_{\lambda}}
-\newcommand{\sigmaijl}{\sigma^{ij}_{\lambda}}
-
-\newcommand{\Sigmait}{\Sigma^{(i)^{-1}}_t}
-
-\newcommand{\muit}{\mu^(i)_t}
-\newcommand{\Sigmaic}{\Sigma'^{(i)^{-1}}_c}
-
-\newcommand{\muic}{{\mu^(i)_c}}
-\newcommand{\Sigmaicf}{\Sigma^{(i)^{-1}}_c}
-
-\newcommand{\muiu}{\mu^{(i)}_t}
-\newcommand{\Sigmaiu}{\Sigma^{(i)^{-1}}_u}
-
-\newcommand{\xt}{\mathbf{x}_t}
-\newcommand{\xc}{\mathbf{x}_c}
-
-\newcommand{\Rctot}{R}
-\newcommand{\tctot}{t}
-
-\newcommand{\tcmut}{t'}
-
-\newcommand{\Beizer}{B\'eizer }
-
-\newcommand{\LaneUncertainty}[1]{\Sigma_{L_m}(#1)}
-\newcommand{\projOnLane}[1]{\pi_{L_m(k)}(#1)}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-%\ifcvprfinal\pagestyle{empty}\fi
-%\setcounter{page}{4321}
-%\DeclareMathSymbol{\Tangent}
-\DeclareMathOperator{\sech}{sech}
-\DeclareMathOperator{\poly}{poly}
-\DeclareMathOperator*{\argmin}{\arg\min}
-
-\begin{document}
-\title{Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.}
-\author{Vikas Dhiman\\
-  University of Michigan\\
-  Ann Arbor, MI, USA\\
-{\tt\small dhiman@umich.edu}
-\and
-Manmohan Chandraker\\
-NEC Laboratories America, Inc.\\
-Cupertino, CA, USA\\
-{\tt\small manu@nec-labs.com}
-\and
-Jason J Corso\\
-  University of Michigan\\
-  Ann Arbor, MI, USA\\
-{\tt\small jjcorso@eecs.umich.edu}
-}
-\maketitle
-
-%%%%%%%%% ABSTRACT
 \begin{abstract}
@@
 \end{abstract}
-
-\section{Introduction}
-
-\begin{itemize}
-  \item Introduce the problem
-  \item Describe our approach
-  \item Contrast with Milan's work
-  \item Contrast with Andreas Geiger's work
-  \item Highlight the contributions
-\end{itemize}
-\vspace{10cm}
-\begin{figure}[t]
-  \includegraphics[width=\columnwidth]{graphics/graphicalModelFrom61ConstVars.pdf}
-  \caption{Graphical model. The six numbered black circles represent the
-    unknown state variables of each car. All other nodes in the graphical model
-    are assumed
-    observed variables. Consider each energy in the model one by one. (1)
-    Bounding box energy: The bounding box energy without occlusion modeling is
-    a unary term, but with occlusion it becomes a higher order term that
-    affects the state of occluder as well. In this graphical model we assume
-    that the scene is being observed from left to right, hence "2" occludes "6"
-    and "5" and "5" occludes "1". The bounding box detection is represented by
-  $\mathbf{d}_{bb}^i(t)$ and the statistical dependencies are represented by
-  red lines. (2) Point tracks ($\Energy{track}$): Since occlusion is also
-  included in modeling point tracks energy we have similar interdependencies
-  for point tracks energy. The available point tracks are modeled by
-  $\mathbf{u}(t)$. (3) Collision ($\Energy{coll}$) : The collision energy
-  mathematically is a dense graph between all the TP but here we represent
-  collision among only those TP that are near enough to have a significant
-collision energy. (4) Orientation from detection ($\Energy{ori}$) (5) Orientation from lane (and map) information ($\Energy{lane}$)}
-  \label{fig:graphmodel}
-\end{figure}
-
-\section{Related Work}
-TODO:
-\vfill
-\pagebreak
-Related work continued
-\vspace{15cm}
-
-\section{Problem Definition}
-TODO:
-\vspace{4cm}
-
-\section{Notation}
-
-\begin{table}[h]
-  \begin{tabular}{|l|l|}
-    \hline
-    Symbol & Meaning \\
-    \hline
-    $\pos{i}{t}$ & Position of $i$th car at time $t$\\
-    $\ori{i}{t}$ & Orientation of $i$th car at time $t$\\
-     $\dimsn{i}$ & 3D bounding box of the car (dimensions)\\
-    $\state{i}{t}$ & State of car $=\{\pos{i}{t}, \ori{i}{t}, \dimsn{i}\}$\\
-    $\egop$ & Position of camera at time $t$\\
-    $\egoo$ & Orientation of camera at time $t$\\
-    $\relp{i}{t}$ & Relative car pose w.r.t. camera \\
-    $\tracklets$ & 3D points tracked on car $i$ in its own frame\\
-    $\trackp{t}$ & Projection of $\tracklets$ in camera\\
-    $\projectionOf{.}$ & Projection function for pose $\relp{i}{t}$\\
-    $\bb{i}$ & 2D bounding box of the car in image\\
-    \hline
-  \end{tabular}
-\end{table}
-
-%%%%%%%%% BODY TEXT
-\section{The Model}
-
-The objective is to find the most likely traffic participant (TP) state given
-various evidences $\mathbb{E} = \{\{\trackp{t}\}, \{\bb{i}\}, \text{lane det.},
-\text{map}, \text{GPS}\}$.
-
-Mathematically, find:
-\begin{align}
-  \{\state{i}{t}\}^* &= \arg \max P(\{\state{i}{t}\} | \mathbb{E})
-\end{align}
-
-Bayes rule
-\begin{align}
-  P(\{\state{i}{t}\} | \mathbb{E}) &=
-  \frac{1}{Z}P( \mathbb{E} | \{\state{i}{t}\})P(\{\state{i}{t}\})
-\end{align}
-
-Assume conditional independence according to graphical model in
-\ref{fig:graphmodel}.
-
-\begin{multline}
-  P(\{\state{i}{t}\} | \mathbb{E}) =
-  \frac{1}{Z}
-  \prod_{t=s_i}^{e_i}\prod_{i,j: i \ne j}(P(\state{i}{t}, \state{j}{t}))\\
-%
-  \prod_{i=1}^{N}
-  \prod_{t=s_i}^{e_i}
-  P(\bb{i} | \state{i}{t})
-  P(\trackp{t} | \state{i}{t})\\
-  P(\state{i}{t} | L_m(t))
-  P(\state{i}{t} | \state{i}{t-1})
-  P(\state{i}{t})
-\end{multline}
-
-We can formulate similar objective function in negative log domain:
-\footnote{TODO:Resolve inconsistency in summation absorption in energy terms.}
-\begin{multline}
-  -\log{P(\{\state{i}{t}\} | \mathbb{E})} = 
-  Z' + \sum_{i,j:i\ne j} \sum_{t=s_i}^{e_i}  \WEnergyCol \\
-  + \sum_{i=1}^N \sum_{t=s_i}^{e_i}
-    \WEnergy{box}
-  + \WEnergy{track}\\
-  + \WEnergy{lane}
-  + \WEnergy{dyn}
-  + \WEnergy{prior}
-\end{multline}
-
-\section{Modeling traffic participants}
-\label{sec:TPmodel}
-Following standard model of occupancy in 3D reconstruction community, we model
-the TP's as high occupancy regions in space. We model the
-uncertainty in occupancy equivalent of transparency i.e. the regions that are
-more certain to be occupied are viewed as relatively more opaque then other
-regions. Based on this intuition we model TP's translucent
-ellipsoids whose opacity is maximum at the center and drops off away from the
-center. More specifically we model, the occupancy of a TP as a
-logistic function,
-
-\begin{align}
-   \occf = L(\mathbf{x}; \pos{i}{t}, \Sigma_i)
-\end{align}
-where $L(.)$ is the logistic function defined by
-\begin{align}
-  L(\mathbf{x}; \pos{i}{t}, \Sigma_i) = \frac{1}{
-    1 + e^{-k(1 - d(\mathbf{x},\pos{i}{t}))}
-    }
-\end{align}
-where $d(\mathbf{x},\pos{i}{t}) =
-(\mathbf{x}-\pos{i}{t})^\top\Sigma_i(\mathbf{x}-\pos{i}{t})$ and $k =
-10\ln{49}$. $k$ is chosen such that $L(.) = 0.98$ when $d(.) =
-0.9$. $\Sigma_i$ determines the spread of the ellipsoid and depends on the
-dimensions of the TP. Please refer to supplementary material 
-for computation of $\Sigma_i$ from TP's dimensions.
-
-We model the probability of a point $\mathbf{x}_j$ on a object $i$ getting successfully
-observed in a camera image at point $\trackpj{t}$ is dependent up two factors,
-(1) reflection and (2) transmission through intermediate space. The reflection
-part ensures that there is an object to reflect a point at a certain region in
-the 3D space while transmission part models occlusion.
-\begin{align}
-  P^{(ij)}_{\text{observation}} = P^{(ij)}_{\text{reflection}}P^{(j)}_{\text{transmission}}
-\end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Reflection probability}
-For Lambertian reflection we replace the surface normal with the
-gradient of occupancy.
-%
-\begin{align}
-  \Prefl = (\max \{0, \nabla \occf^\top
-  \hat{\mathbf{r}_j}\})^2
-\end{align}
-%
-where $\ray =
-\frac{K^{-1}\trackpj{t}}{\|K^{-1}\trackpj{t}\|}$ is unit vector in the
-direction of ray. The gradient in the direction opposite to ray yields -ve
-probability which needs to be clipped off. Squaring the function keep it
-smooth near zero.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Transmission probability}
-A model for transmission of light through a material of thickness $x$,
-density $\rho$ and opacity $k_o$ is given by Beer-Lambert law 
-%
-\begin{align}
-  I(x) = I_0e^{-k_o\rho x}
-\end{align}
-%
-
-Since both opacity and density are represented by the occupancy function
-$\occftot = \sum_i \occf$, and also the domain of our $\occftot$ is $[0, 1]$ instead of $[0,
-\infty]$ as in case of $k_o$; we replace $e^{-k_o\rho}$ by the transparency
-function $1 - \occftot$. So the transmission probability over a small distance
-$d\lambda$ is given by
-%
-\begin{align}
-  P_{\text{transmission}}(\lambda + d\lambda) =
-  P_{\text{transmission}}(\lambda) (1-\occftot)^{d\lambda}
-\end{align}
-%
-
-For a given 3D point $\mathbf{x}_j = \lambda \ray$, the probability that the
-point $\trackpj{t}$ is reflected from a distance $\lambda$ is given by
-
-\begin{align}
-  %P^{(j)}_{\text{observation}}(\lambda) &= P_{\text{reflection}}
-  \Ptrans &=
-  \prod_{0}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda} %\\
-  %= \max \{ 0, (\nabla f_{occ}&(\lambda \ray)^\top \ray) \}
-  %\prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
-  \label{eq:ptrans-integral}
-\end{align}
-where $\prod_{0}^{\lambda}$ represents the \emph{product integral} from $0$ to
-$\lambda$.
-
-In practice, the integral for transmission probability
-\eqref{eq:ptrans-integral} is difficult to compute even numerically. So we
-choose a product of sigmoid function that approximates the behaviour of
-transmission probability,
-%
-\begin{align}
-\label{eq:evalCumulativePtrans}
-  \Ptrans &= \prod_i L_u(\trackp{t}; \muiu,\Sigmaiu)L_{\lambda}(\lambda; \mu^i_d)
-\end{align}
-%
-where $L_u(.)$ is sigmoid in image domain with $\mu^i_u$ and $\Sigma^i_u$
-representing the elliptical projection of $i^{th}$ TP.
-$L_{\lambda}(.)$ is sigmoid in the depth domain with $\mu^i_d$ as the mean
-depth of the $i^{th}$ TP.
-%
-\begin{align}
-  L_u(\mathbf{u}; \muiu,\Sigmaiu) &= \frac{1}{
-    1 + e^{-k_u(1 - (\mathbf{u} - \muiu)^\top\Sigmaiu(\mathbf{u} -
-    \muiu))}
-  }
-  \\
-  L_{\lambda}(\lambda; \mu^i_d) &= \frac{1}{
-    1 + e^{-k_d(\lambda - \mu^i_d)}
-}
-\end{align}
-%
-
-\begin{comment}%% Comment
-  A product integral is a simple integral in log domain
-  \begin{align}
-    \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} =
-    e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
-  \end{align}
-\end{comment}%% Comment
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Energies}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We explain energies in this section
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Point tracks energy with occlusion}
-\label{sec:totalContPtTracksEnergy}
-We model continuous point tracks energy with explicit occlusion reasoning as
-the expected re-projection error over the association probability,
-
-\begin{multline}
-  \Energy{traci}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \\
-    \sum_{i=1}^{N} 
-    %\sum_{t = s_i}^{e_i}
-    \sum_{j = 1}^{M}
-    \int_1^\infty \assocP\Ereproj(\lambda) d\lambda
-\end{multline}
-where $\assocP$ is the association probability of
-$j$\textsuperscript{th} point with $i$\textsuperscript{th} TP at depth $\lambda$
-and $\Ereproj(\lambda)$ is the re-projection error given by
-%
-\begin{align}
-  \assocP &= \Prefl\Ptrans\\
-  \Ereproj(\lambda) &= \left\|\trackpj{t+1} - \projectionOft{\invProjectionOf{\trackpj{t}, \lambda}}\right\|^2 .
-  \label{eq:reprojerror}
-\end{align}
-
-The  $\projectionOf{.}$ and $\invProjectionOf{.}$ denote the projection and
-inverse projection functions that project 3D point to camera image and vice
-versa. Note that inverse projection $\invProjectionOf{.}$ depend on both the
-point $\trackp{t}$ and the unknown depth $\lambda$. Also note that the inverse projection is dependent on TP pose at time $t$ while the projection depends on pose at time $t+1$ which can be different.
-
-\begin{comment}
-  \subsubsection{Occupancy function}
-  Assuming occupancy to be a
-  probability distribution over 3D space. For each TP the
-  occupancy is modeled as a logistic function 
-  \begin{align}
-     \occf = L(\mathbf{x}; \pos{i}{t}, \Sigma_i)
-  \end{align}
-  where $L(.)$ is the logistic function defined by
-  \begin{align}
-    L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i) = \frac{1}{
-      1 + e^{-k(1 - d(\mathbf{x},\pos{i}{t-1}))}
-      }
-  \end{align}
-  where $d(\mathbf{x},\pos{i}{t-1}) =
-  (\mathbf{x}-\pos{i}{t-1})^\top\Sigma_i(\mathbf{x}-\pos{i}{t-1})$ and $k =
-  10\ln{49}$. $k$ is chosen such that $L(.) = 0.98$ when $d(.) =
-  0.9$
-  % Once we have our distribution over $\lambda$, $\lambdadist$ we can compute the
-  % reprojection of $\trackpj{t-1}$ over image in time $t$ as a function of
-  % $\lambda$. Let
-\end{comment}
-
-\begin{comment}
-  \subsubsection{Approximations}
-  Reflection probability of $i$th TP is easy to compute
-  analytically 
-  \begin{multline}
-    \Prefl =
-    (\max \{ 0, \nabla \occf^\top \ray \})^2 \\
-    = (\max \{ 0, \nabla \occfxi^\top\ray \})^2
-    \label{eq:analytic-prefl}
-  \end{multline}
-  where 
-  \begin{multline}
-    \nabla \occfxi^\top\ray \\=
-    \nabla k\dishort \sech^2\left(\frac{k}{2}\dishort\right)
-  \end{multline}
-  where $\dishort = 1-d(\mathbf{x}, \pos{i}{t-1})$ is a signed distance measure
-  from the contour of the ellipsoid where $d(\mathbf{x}, \pos{i}{t-1})$ is 1.
-
-  However, the transmission probability needs to be approximated.  
-  %
-  % \subsubsection{Computing $\Prefl$ and $\Ptrans$}
-  % Focusing on  $\nabla \occfxi$ 
-  % 
-  % \begin{multline}
-  %   \nabla \occfxi =\\
-  %   \frac{-k\nabla d(\mathbf{x}, \pos{i}{t-1})e^{-k(1-d(\mathbf{x}, \pos{i}{t-1}))}}{
-  %     (1 + e^{-k(1-d(\mathbf{x}, \pos{i}{t-1}))})^2
-  %   } \\ 
-  %   = -k\nabla d(\mathbf{x}, \pos{i}{t-1})\sech^2\left(\frac{k}{2}(1-d(\mathbf{x},
-  %   \pos{i}{t-1}))\right)
-  %   \\
-  %   = \nabla k\dishort \sech^2\left(\frac{k}{2}\dishort\right)
-  % \end{multline}
-  % where $\dishort = 1-d(\mathbf{x}, \pos{i}{t-1})$ is a signed distance measure
-  % from the contour of the ellipsoid where $d(\mathbf{x}, \pos{i}{t-1})$ is 1.
-  % Focusing on $\nabla d(.)$
-  % 
-  % \begin{align}
-  %   \nabla d(\mathbf{x}, \pos{i}{t-1}) = 2\Sigma_i(\mathbf{x} - \pos{i}{t-1})
-  % \end{align}
-  % Back to \eqref{eq:analytic-prefl}
-  % 
-  % \begin{multline}
-  %   (\max \{ 0, \nabla \occf^\top \ray \})^2 = \\
-  %   \sech^4\left(\frac{k}{2}\dishort\right) 
-  %   (\max \{ 0 , \nabla k\dishort^\top\ray\})^2
-  % \end{multline}
-  % 
-  % The probability is simply $\sech^2(.)$ scaled by gradient of ellipsoid
-  % $\nabla k\dishort$ projected in the ray direction $\ray$.
-  % 
-  % \begin{align}
-  %   \Ptrans = 
-  %   e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
-  % \end{align}
-  % \begin{multline}
-  % \int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}
-  % =  \\
-  % \int_{1}^{\lambda} \ln{\left(1 - \sum_i \occfi\right)}{d\lambda}
-  % \end{multline}
-  % 
-  % The above integral is very difficult to approximate or compute analytically.
-  So based on intuition, we approximate the $\Ptrans$ by following function
-  \begin{align}
-  \label{eq:evalCumulativePtrans}
-    \Ptrans &= \prod_i L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)L_{\lambda}(\lambda; \mu^i_d)\\
-    L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u) &= \frac{1}{
-      1 + e^{-k_u(1 - (\mathbf{u} - \mu^i_u)^\top\Sigma^i_u(\mathbf{u} -
-      \mu^i_u))}
-    }
-    \\
-    L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d) &= \frac{1}{
-    1 + e^{-k_d(\lambda - \mu^i_d(\mathbf{u}))}
-  }
-  \end{align}
-  where 
-  \begin{align}
-    \mu_u^i &= \projectionOf{\pos{i}{t-1}} \label{eq:muiudef}\\
-    \Sigma_u^i &= \projectionOf{\Sigma_i} \label{eq:sigmauidef}\\
-    \mu^i_d(\mathbf{u}) &= \relp{i}{t}\\
-    k_u &= 10\log(49)\\
-    k_d &= \frac{\log(49)}{\sqrt{h^2 + l^2 + w^2}}
-    \label{eq:ptransmissionInit}
-  \end{align}
-  is the distance of the centre of the TP from the camera.
-
-  % $\mu^i_d(\mathbf{u}) = \min_{\lambda} d^2_i(\lambda K^{-1}\mathbf{u})$.
-  % $\mu^i_d(\mathbf{u})$ is the closest point to the unit contour of ellipsoid.
-  % If there are multiple such points, the point closest to the camera is taken as
-  % $\mu^i_d(\mathbf{u})$
-
-  The association probability becomes
-
-  \begin{multline}
-    \assocP = 
-      \sech^4\left(\frac{k}{2}\dishort\right)
-      (\max \{ 0, \nabla k\dishort^\top\ray \})^2\\
-    \prod_i \Lu
-      \Llambda \\
-      \label{eq:assocCoeffEval}
-  \end{multline}
-
-  So the energy becomes
-
-  \begin{multline}
-    \label{eq:integrand}
-    \Energy{track}(.) = 
-      \sum_{i = 1}^N
-      \sum_{j = 1}^{M}
-      \int_1^{\infty}
-      \assocP
-      \Ereproj(\lambda)
-      d\lambda
-  \end{multline}
-  where $x = \lambda \ray$ and $\Ereproj(\lambda) = \|\trackpj{t} -
-  f^i_{reproj}(\trackpj{t-1}, \lambda)\|^2$ is reprojection error which is a
-  quadratic in $\lambda$
-
-  The integral in the above expression is computed numerically.
-\end{comment}
-
-\subsection{Object detection energy with occlusion}
-
-Object detection is usually followed by non-maximal suppression that results in
-discarding similar bounding boxes. When we are jointly optimizing detections
-with other cues, it is not usually desirable to go with a single bounding box.
-Hence, we keep all the bounding box detections by approximating them with
-multi-modal sum of Gaussian like logistic functions. We fit the parametric function of the form 
-%
-\begin{align}
-  S(\bb{i}) = \sum_k A_k \exp(-(\bb{i}-\mu^{(d)}_k)^\top \Sigma^{(d)-1}_k
-  (\bb{i}-\mu^{(d)}_k))
-\end{align}
-%
-to detection scores, by non-linear error minimization with initialization from
-non-maximal suppressed outputs. Here $\mu^{(d)}_j$ is one of the $k$ modes as a
-4D vector representing a single bounding box as $[\minx, \miny, \maxx,
-\maxy]^\top$. The optimization is constrained with symmetry and positive
-definiteness of $\Sigma^{(d)-1}_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
-
-\subsubsection{Detection scores with occlusion reasoning} 
-With our model of $\Ptrans$ described in Section \ref{sec:TPmodel}, we can
-compute the probability of a point $\mathbf{u}$ on image be occluded assuming
-the point is on TP $i$ with mean depth $\mu^{(i)}_d$ as
-\begin{align}
-  O_{i}(\mathbf{u}, \mu^{(i)}_d) = 1 - \Ptransmud \enspace .
-\end{align}
-
-If we a portion of our proposed detection bounding box is known to be occluded,
-then we would like to decrease the confidence in the detection score about the
-localization of that end of the object. Assuming that the occlusion is often on
-the boundary of detection bounding boxes, we want to decrease our confidence on
-the mean detection boundaries around the occluded boundaries. 
-One of the simplest ways will be to scale the appropriate diagonal element of
-$\Sigma_j$ by an appropriate scaling factor proportional to occlusion. But this
-does not model appropriate how does occlusion affects the non diagonal terms.
-Hence, we choose a covariance addition model where we compute a occlusion
-covariance matrix, that provides a measure of occlusion in each direction.
-
-To re-model our detection scores scaled by continuous occlusion we sample
-$O_{i}(\mathbf{u}, \mu^{(i)}_d)$ at the hypothesized detection boundaries from
-GMM $S(.)$ and we augment the detection boundary covariance matrix by
-$\mathcal{P}_{j} = \rho_{j}\rho_{j}^\top$ where $\rho_{j} = O_{j}(\mathbf{u},
-\mu^{(i)}_d)$. The new covariance matrix in detection score is given by 
-%
-\begin{align}
-  \Sigma'^{(d)}_j = \mathcal{P}_{j} + \Sigma^{(d)}_j
-\end{align}
-%
-The detection scores GMM with occlusion is given by replacing the covariance
-matrix
-%
-\begin{multline}
-  S'(\bb{i}) =\\
-  \sum_j A_j \exp(-(\bb{i}-\mu^{(d)}_j)^\top \Sigma'^{(d)-1}_j
-  (\bb{i}-\mu^{(d)}_j))
-\end{multline}
-
-The energy of detection scores is simply take to be the inverse of the detection score.
-\begin{align}
-  \Energy{detect}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}
-\end{align}
-
-\subsection{Lane energy}
-\label{sec:laneEnergy}
- The lanes are modeled as splines. Here we assume that the confidence in lane
- detection is decreases as the distance from the lane center increases.  The
- energy is given by the dot product between car orientation and tangent to the
- lane at that point.
-
-\begin{multline}
-  \label{eq:laneOrientationEnergy}
-  \Energy{lane} = \\
-  \sum_{m \in M_{\text{close}}}
-  (1 - \ori{i}{t} \cdot \text{TAN}(L_{m}(k), \pos{i}{t}) )
-\LaneUncertainty{\pos{i}{t}}
-\end{multline}
-where $M_{\text{close}} = \{m : \text{DIST}(L_{m}(k), \pos{i}{t}) < 50\} $ is
-the set of nearby lanes and 
-\begin{multline}
-\LaneUncertainty{\pos{i}{t}} = \\
-  \frac{1}{1 + exp(-q(w_{\text{road}} - \text{DIST}(L_{m}(k), \pos{i}{t})))}
-\end{multline}
-for some constant $w_{\text{road}}$ that represents the width of the road.
-
-\subsection{Transition probability}
-Dynamics constraints should not only enforce smooth trajectories, but also the
-holonomic constraints.  The following energy adds a penalty if the change in
-position is not in direction of previous orientation.
-
-\begin{align}
-  \label{eq:totalPosTransitionEnergy}
-  \Energy{dyn-hol} = 1 - \ori{i}{t-1} \cdot (\pos{i}{t} - \pos{i}{t-1})
-\end{align}
-
-The following energy adds a penalty for change in position and orientation
-but a penalty for change in velocity is much better approximation. However, in
-a Markovian setting that would mean extending the state space of the car to
-include velocity.
-
-\begin{align}
-  \Energy{dyn-ori} &= \|\ori{i}{t} - \ori{i}{t-1}\|^2\\
-  \Energy{dyn-vel} &= \|(\pos{i}{t} - 2\pos{i}{t-1}) + \pos{i}{t-2}\|^2
-\end{align}
-
-As a result the dynamics are modeled by weighted combination of holonomic
-constraint and smoothness constraints.
-
-\begin{align}
-  \WEnergy{dyn} &= \WEnergy{dyn-hol} + \WEnergy{dyn-ori} + \WEnergy{dyn-vel}
-\end{align}
-
-\subsection{Collision energy}
-
-Bhattacharya coefficient $\int_a^b\sqrt{p(x)q(x)}dx$ is a measure of similarity
-of two distributions $p(x)$ and $q(x)$. If we represent TPs as gaussians in
-Birds eye view (BEV), then similarity is a measure of collision. Exactly
-overlapping distribution results in coefficient as 1. 
-%The analytical form of
-%Bhattacharya coefficient has been taken from
-%\url{http://like.silk.to/studymemo/PropertiesOfMultivariateGaussianFunction.pdf}
-
-\begin{multline}
-  \label{eq:collisionEnergyHellingerDistance}
-  \EnergyCol =\\ -\log\left(
-  A_{ij}
-  e^{-\frac{1}{8}
-    \left(\pos{i}{t} - \pos{j}{t}\right)^\top
-    P^{-1}
-    \left(\pos{i}{t} - \pos{j}{t}\right)
-    }
-    \right)
-\end{multline}
-where 
-\begin{align}
-  A_{ij} &= \frac{|\Sigma_i|^\frac{1}{4}|\Sigma_j|^\frac{1}{4}}
-  {|P|^\frac{1}{2}}\\
-  P &= \frac{1}{2}\Sigma_i + \frac{1}{2}\Sigma_j\\
-\Sigma_i^{-1} &= R^\top_{\ori{i}{t}} \begin{bmatrix} 2/l_i & 0 \\ 0 & 2/w_i \end{bmatrix}
-R_{\ori{i}{t}}
-\end{align}
-
-\subsection{Size Prior}
-
-Prior can include among many other things the size prior on the car.
-
-\begin{align}
-  \label{eq:totalSizeEnergy}
-  \Energy{prior} &= (\dimsn{i} - \expDimsn)^\top\Sigma_{\expDimsn}^{-1}(\dimsn{i} -
-  \expDimsn)
-\end{align}
-
-where $\expDimsn$ is the mean TP dimensions and
-$\Sigma_{\expDimsn}$ is the correspondence covariance matrix.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Association error evaluation}
-
-To verify the correctness of our association probability $\assocP$ we perform
-association error experiment that compare the accuracy of point track
-association with TPs with that of bounding box baseline method.
-
-% \begin{align}
-%   f^{i}_{reproj}&(\trackpj{t-1}, \lambda) =
-%   \projectionOf{\invProjectionOf{\trackpj{t-1}}}\\
-%   %&= K(R^i_t ((R^i_{t-1})^\top\lambda \ray - (R^i_{t-1})^\top T_{t-1}) + T_{t})\\
-%   &= \frac
-%   {p_{1:2}\lambda + q_{1:2}}
-%   {p_{3}\lambda + q_{3}}
-% \end{align}
-% where $p_{1:3} = KR^i_t(R^i_{t-1})^\top\ray$ and
-% $q_{1:3} = KR^i_t(R^i_{t-1})^\top T_{t-1} + KT_t$
-% 
-% Now that we have an association from TP $i$ to point track $j$ through
-% $\lambda$, we can come up with an association probability
-% \begin{align}
-%    \assocP &= \frac{(\max \{ 0, \nabla \occf^\top
-% \ray \})^2 }{P_{\text{reflection}}}\lambdadist\\
-% &=(\max \{ 0, \nabla \occf^\top \ray \})^2
-%   \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
-% \end{align}
-
-Note that the fraction $\assocP$ although called association probability does
-not capture the entire information that we have available for compute
-association of points to tracks. This above fraction is the association
-probability given the hypothesized parameters of TP model.
-
-To compute the association probability between TP $i$ and
-point track $j$ we must use re-projection error as well. When the association
-$i$ and $j$ is right and the point of reflection is at depth $\lambda$ the
-re-projection error must be zero \eqref{eq:reprojerror}, otherwise the error
-becomes a measure of distance from the true solution.
-The error terms can be converted to probability domain by considering the error
-term as negative log of probability
-
-\begin{align}
-  P^{(ij)}_{\text{assoc by reproj}}(\lambda) = \frac{1}{Z}\exp(-\Ereproj(\lambda))
-\end{align}
-
-Using both the evidence terms we can write probability of association as
-\begin{align}
-  P^{(ij)}_{\text{assoc}} = \frac{1}{Z'}\int_0^{\infty} \assocP \frac{1}{\sqrt{2\pi}}\exp(-\Ereproj(\lambda))d\lambda
-  \label{eq:prob-assoc}
-\end{align}
-
-Once we have the probability of association we can compute the best possible
-assignment of TP for each point. The points having very small association
-probability are assigned to the background,
-\begin{align}
-  i^*_{j} = \argmin_{i} \int_0^\infty \assocP \Ereproj(\lambda) d\lambda
-\end{align}
-
-We use bounding box based assignment of point tracks to TPs as the baseline.
-For the regions where the bounding boxes overlap, we assign the points to the
-TP that has smaller mean depth then the competing bounding box.
-
-{\small
-\bibliographystyle{ieee}
-\bibliography{model}
-}
-\end{document}

### 2014-11-10 CVPR/Source/experiments.tex
Reorganized paper tex files

--- 2014-11-08 Paper/model.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
+\section{Experiments}
+\label{sec:experiments}
 
-\usepackage{cvpr}
-\usepackage{times}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-%%%%%%%%%%% CVPR template packages end %%%%%%%%%%%%%%
-\usepackage{verbatim} % for comment environment
-% \usepackage{soul} % for \hl highlighting
-% Include other packages here, before hyperref.
-
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-
-%\cvprfinalcopy % *** Uncomment this line for the final submission
-
-\def\cvprPaperID{489} % *** Enter the CVPR Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-% 3D pose of the cars and ego motion
-\newcommand{\pos}[2]{\mathbf{p}^{(#1)}(#2)}
-\newcommand{\ori}[2]{\mathbf{\omega}^{(#1)}(#2)}
-\newcommand{\state}[2]{\mathbf{s}^{#1}(#2)}
-
-% ego pose
-\newcommand{\egop}[1][t]{\pos{c}{#1}}
-\newcommand{\egoo}[1][t]{\ori{c}{#1}}
-\newcommand{\egos}[1][t]{\state{c}{#1}}
-
-% relative pose between camera and car $i$
-\newcommand{\relp}[2]{\Omega^{#1}(#2)}
-\newcommand{\relpz}[2]{\Omega_z^{#1}(#2)}
-
-% 3D tracks on car $i$ in its own coordinate frame
-\newcommand{\tracklets}{\mathbf{X}^{(i)}_o}
-\newcommand{\tracklet}[1]{\mathbf{x}^{(i)}_{#1}}
-% track projections on camera
-\newcommand{\trackp}[1]{\mathbf{u}^{(i)}(#1)}
-\newcommand{\trackpj}[1]{\mathbf{u}_j(#1)}
-% Unclassified track point projected on camera
-\newcommand{\ucTrackp}{\mathbf{u}(t)}
-
-% dimensions of car $i$
-\newcommand{\dimsn}[1]{\mathbf{B}^{#1}}
-\newcommand{\expDimsn}{\hat{\mathbf{B}}}
-
-% projection function
-\newcommand{\projectionOf}[1]{\pi_{\relp{i}{t}}\left(#1\right)}
-\newcommand{\projectionOft}[1]{\pi_{\relp{i}{t+1}}\left(#1\right)}
-\newcommand{\centerProj}{\bar{\pi}_{\relp{i}{t}}(\dimsn{i})}
-\newcommand{\cornerProj}[1]{\pi^{#1}_{\relp{i}{t}}(\dimsn{i})}
-\newcommand{\triangleProj}[1]{\triangle^{#1}_{\relp{i}{t}}(\dimsn{i})}
-
-% bounding box corners on image
-\newcommand{\bb}[1]{\mathbf{d}^{#1}(t)}
-
-\newcommand{\Energy}[1]{\mathcal{E}^{it}_{\text{#1}}}
-\newcommand{\pEnergy}[1]{\mathcal{E}^{ijt}_{\text{#1}}}
-% Weighted energy
-\newcommand{\WEnergy}[1]{\lambda_{\text{#1}}\Energy{#1}}
-\newcommand{\EnergyCol}{\mathcal{E}^{ijt}_{\text{col}}}
-\newcommand{\WEnergyCol}{\lambda_{\text{col}}\EnergyCol}
-
-\newcommand{\occFreeProj}[1]{\Pi_{\relp{i}{t}}(#1)}
-\newcommand{\minx}{x_{\text{min}}}
-\newcommand{\miny}{y_{\text{min}}}
-\newcommand{\maxx}{x_{\text{max}}}
-\newcommand{\maxy}{y_{\text{max}}}
-\newcommand{\frontface}{F^i_\text{FF}(t)}
-
-\newcommand{\occ}[1]{o({#1})}
-\newcommand{\face}{F^i_k(t)}
-
-\newcommand{\invProjectionOf}[1]{\pi^{-1}_{\relp{i}{t}}\left(#1\right)}
-\newcommand{\occf}{f^i_{occ}(\mathbf{x}_j)}
-\newcommand{\occftot}{f_{occ}(\mathbf{x}_j)}
-\newcommand{\occft}[1]{f_{occ}(#1)}
-
-\newcommand{\ray}{\hat{\mathbf{r}}_j}
-\newcommand{\occfray}{f_{occ}(\lambda\ray)}
-\newcommand{\lambdadist}{f_{\lambda}(\trackpj{t-1}, \lambda)}
-
-\newcommand{\occfxi}{L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i)}
-\newcommand{\occfi}{L(\lambda \ray; \pos{i}{t-1}, \Sigma_i)}
-\newcommand{\assocP}{a^{(ij)}(\lambda)}
-\newcommand{\assocPk}{a^{(ij)}(\lambda_k)}
-
-\newcommand{\Ereproj}{E^{(ij)}_{\text{reproj}}}
-\newcommand{\Ptrans}{P^{(j)}_{\text{transmission}}(\lambda)}
-\newcommand{\Ptransmud}{P^{(j)}_{\text{transmission}}(\mu^{(i)}_d)}
-\newcommand{\Prefl}{P^{(ij)}_{\text{reflection}}(\lambda)}
-\newcommand{\dishort}{d_i(\mathbf{x})}
-
-\newcommand{\Lu}{L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)}
-\newcommand{\Llambda}{L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d)}
-
-\newcommand{\Gauss}{\mathcal{N}}
-\newcommand{\PropDist}{\mathcal{W}_j}
-
-\newcommand{\muijl}{\mu^{(ij)}_{\lambda}}
-\newcommand{\sigmaijl}{\sigma^{ij}_{\lambda}}
-
-\newcommand{\Sigmait}{\Sigma^{(i)^{-1}}_t}
-
-\newcommand{\muit}{\mu^(i)_t}
-\newcommand{\Sigmaic}{\Sigma'^{(i)^{-1}}_c}
-
-\newcommand{\muic}{{\mu^(i)_c}}
-\newcommand{\Sigmaicf}{\Sigma^{(i)^{-1}}_c}
-
-\newcommand{\muiu}{\mu^{(i)}_t}
-\newcommand{\Sigmaiu}{\Sigma^{(i)^{-1}}_u}
-
-\newcommand{\xt}{\mathbf{x}_t}
-\newcommand{\xc}{\mathbf{x}_c}
-
-\newcommand{\Rctot}{R}
-\newcommand{\tctot}{t}
-
-\newcommand{\tcmut}{t'}
-
-\newcommand{\Beizer}{B\'eizer }
-
-\newcommand{\LaneUncertainty}[1]{\Sigma_{L_m}(#1)}
-\newcommand{\projOnLane}[1]{\pi_{L_m(k)}(#1)}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-%\ifcvprfinal\pagestyle{empty}\fi
-%\setcounter{page}{4321}
-%\DeclareMathSymbol{\Tangent}
-\DeclareMathOperator{\sech}{sech}
-\DeclareMathOperator{\poly}{poly}
-\DeclareMathOperator*{\argmin}{\arg\min}
-
-\begin{document}
-\title{Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.}
-\author{Vikas Dhiman\\
-  University of Michigan\\
-  Ann Arbor, MI, USA\\
-{\tt\small dhiman@umich.edu}
-\and
-Manmohan Chandraker\\
-NEC Laboratories America, Inc.\\
-Cupertino, CA, USA\\
-{\tt\small manu@nec-labs.com}
-\and
-Jason J Corso\\
-  University of Michigan\\
-  Ann Arbor, MI, USA\\
-{\tt\small jjcorso@eecs.umich.edu}
-}
-\maketitle
-
-%%%%%%%%% ABSTRACT
-\begin{abstract}
-  TODO: Write abstract
-  \vspace{4cm}
-\end{abstract}
-
-\section{Introduction}
-
-\begin{itemize}
-  \item Introduce the problem
-  \item Describe our approach
-  \item Contrast with Milan's work
-  \item Contrast with Andreas Geiger's work
-  \item Highlight the contributions
-\end{itemize}
-\vspace{10cm}
-\begin{figure}[t]
-  \includegraphics[width=\columnwidth]{graphics/graphicalModelFrom61ConstVars.pdf}
-  \caption{Graphical model. The six numbered black circles represent the
-    unknown state variables of each car. All other nodes in the graphical model
-    are assumed
-    observed variables. Consider each energy in the model one by one. (1)
-    Bounding box energy: The bounding box energy without occlusion modeling is
-    a unary term, but with occlusion it becomes a higher order term that
-    affects the state of occluder as well. In this graphical model we assume
-    that the scene is being observed from left to right, hence "2" occludes "6"
-    and "5" and "5" occludes "1". The bounding box detection is represented by
-  $\mathbf{d}_{bb}^i(t)$ and the statistical dependencies are represented by
-  red lines. (2) Point tracks ($\Energy{track}$): Since occlusion is also
-  included in modeling point tracks energy we have similar interdependencies
-  for point tracks energy. The available point tracks are modeled by
-  $\mathbf{u}(t)$. (3) Collision ($\Energy{coll}$) : The collision energy
-  mathematically is a dense graph between all the TP but here we represent
-  collision among only those TP that are near enough to have a significant
-collision energy. (4) Orientation from detection ($\Energy{ori}$) (5) Orientation from lane (and map) information ($\Energy{lane}$)}
-  \label{fig:graphmodel}
-\end{figure}
-
-\section{Related Work}
-TODO:
-\vfill
-\pagebreak
-Related work continued
-\vspace{15cm}
-
-\section{Problem Definition}
-TODO:
-\vspace{4cm}
-
-\section{Notation}
-
-\begin{table}[h]
-  \begin{tabular}{|l|l|}
-    \hline
-    Symbol & Meaning \\
-    \hline
-    $\pos{i}{t}$ & Position of $i$th car at time $t$\\
-    $\ori{i}{t}$ & Orientation of $i$th car at time $t$\\
-     $\dimsn{i}$ & 3D bounding box of the car (dimensions)\\
-    $\state{i}{t}$ & State of car $=\{\pos{i}{t}, \ori{i}{t}, \dimsn{i}\}$\\
-    $\egop$ & Position of camera at time $t$\\
-    $\egoo$ & Orientation of camera at time $t$\\
-    $\relp{i}{t}$ & Relative car pose w.r.t. camera \\
-    $\tracklets$ & 3D points tracked on car $i$ in its own frame\\
-    $\trackp{t}$ & Projection of $\tracklets$ in camera\\
-    $\projectionOf{.}$ & Projection function for pose $\relp{i}{t}$\\
-    $\bb{i}$ & 2D bounding box of the car in image\\
-    \hline
-  \end{tabular}
-\end{table}
-
-%%%%%%%%% BODY TEXT
-\section{The Model}
-
-The objective is to find the most likely traffic participant (TP) state given
-various evidences $\mathbb{E} = \{\{\trackp{t}\}, \{\bb{i}\}, \text{lane det.},
-\text{map}, \text{GPS}\}$.
-
-Mathematically, find:
-\begin{align}
-  \{\state{i}{t}\}^* &= \arg \max P(\{\state{i}{t}\} | \mathbb{E})
-\end{align}
-
-Bayes rule
-\begin{align}
-  P(\{\state{i}{t}\} | \mathbb{E}) &=
-  \frac{1}{Z}P( \mathbb{E} | \{\state{i}{t}\})P(\{\state{i}{t}\})
-\end{align}
-
-Assume conditional independence according to graphical model in
-\ref{fig:graphmodel}.
-
-\begin{multline}
-  P(\{\state{i}{t}\} | \mathbb{E}) =
-  \frac{1}{Z}
-  \prod_{t=s_i}^{e_i}\prod_{i,j: i \ne j}(P(\state{i}{t}, \state{j}{t}))\\
-%
-  \prod_{i=1}^{N}
-  \prod_{t=s_i}^{e_i}
-  P(\bb{i} | \state{i}{t})
-  P(\trackp{t} | \state{i}{t})\\
-  P(\state{i}{t} | L_m(t))
-  P(\state{i}{t} | \state{i}{t-1})
-  P(\state{i}{t})
-\end{multline}
-
-We can formulate similar objective function in negative log domain:
-\footnote{TODO:Resolve inconsistency in summation absorption in energy terms.}
-\begin{multline}
-  -\log{P(\{\state{i}{t}\} | \mathbb{E})} = 
-  Z' + \sum_{i,j:i\ne j} \sum_{t=s_i}^{e_i}  \WEnergyCol \\
-  + \sum_{i=1}^N \sum_{t=s_i}^{e_i}
-    \WEnergy{box}
-  + \WEnergy{track}\\
-  + \WEnergy{lane}
-  + \WEnergy{dyn}
-  + \WEnergy{prior}
-\end{multline}
-
-\section{Modeling traffic participants}
-\label{sec:TPmodel}
-Following standard model of occupancy in 3D reconstruction community, we model
-the TP's as high occupancy regions in space. We model the
-uncertainty in occupancy equivalent of transparency i.e. the regions that are
-more certain to be occupied are viewed as relatively more opaque then other
-regions. Based on this intuition we model TP's translucent
-ellipsoids whose opacity is maximum at the center and drops off away from the
-center. More specifically we model, the occupancy of a TP as a
-logistic function,
-
-\begin{align}
-   \occf = L(\mathbf{x}; \pos{i}{t}, \Sigma_i)
-\end{align}
-where $L(.)$ is the logistic function defined by
-\begin{align}
-  L(\mathbf{x}; \pos{i}{t}, \Sigma_i) = \frac{1}{
-    1 + e^{-k(1 - d(\mathbf{x},\pos{i}{t}))}
-    }
-\end{align}
-where $d(\mathbf{x},\pos{i}{t}) =
-(\mathbf{x}-\pos{i}{t})^\top\Sigma_i(\mathbf{x}-\pos{i}{t})$ and $k =
-10\ln{49}$. $k$ is chosen such that $L(.) = 0.98$ when $d(.) =
-0.9$. $\Sigma_i$ determines the spread of the ellipsoid and depends on the
-dimensions of the TP. Please refer to supplementary material 
-for computation of $\Sigma_i$ from TP's dimensions.
-
-We model the probability of a point $\mathbf{x}_j$ on a object $i$ getting successfully
-observed in a camera image at point $\trackpj{t}$ is dependent up two factors,
-(1) reflection and (2) transmission through intermediate space. The reflection
-part ensures that there is an object to reflect a point at a certain region in
-the 3D space while transmission part models occlusion.
-\begin{align}
-  P^{(ij)}_{\text{observation}} = P^{(ij)}_{\text{reflection}}P^{(j)}_{\text{transmission}}
-\end{align}
+\paragraph{Dataset}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Reflection probability}
-For Lambertian reflection we replace the surface normal with the
-gradient of occupancy.
-%
-\begin{align}
-  \Prefl = (\max \{0, \nabla \occf^\top
-  \hat{\mathbf{r}_j}\})^2
-\end{align}
-%
-where $\ray =
-\frac{K^{-1}\trackpj{t}}{\|K^{-1}\trackpj{t}\|}$ is unit vector in the
-direction of ray. The gradient in the direction opposite to ray yields -ve
-probability which needs to be clipped off. Squaring the function keep it
-smooth near zero.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Transmission probability}
-A model for transmission of light through a material of thickness $x$,
-density $\rho$ and opacity $k_o$ is given by Beer-Lambert law 
-%
-\begin{align}
-  I(x) = I_0e^{-k_o\rho x}
-\end{align}
-%
-
-Since both opacity and density are represented by the occupancy function
-$\occftot = \sum_i \occf$, and also the domain of our $\occftot$ is $[0, 1]$ instead of $[0,
-\infty]$ as in case of $k_o$; we replace $e^{-k_o\rho}$ by the transparency
-function $1 - \occftot$. So the transmission probability over a small distance
-$d\lambda$ is given by
-%
-\begin{align}
-  P_{\text{transmission}}(\lambda + d\lambda) =
-  P_{\text{transmission}}(\lambda) (1-\occftot)^{d\lambda}
-\end{align}
-%
-
-For a given 3D point $\mathbf{x}_j = \lambda \ray$, the probability that the
-point $\trackpj{t}$ is reflected from a distance $\lambda$ is given by
-
-\begin{align}
-  %P^{(j)}_{\text{observation}}(\lambda) &= P_{\text{reflection}}
-  \Ptrans &=
-  \prod_{0}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda} %\\
-  %= \max \{ 0, (\nabla f_{occ}&(\lambda \ray)^\top \ray) \}
-  %\prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
-  \label{eq:ptrans-integral}
-\end{align}
-where $\prod_{0}^{\lambda}$ represents the \emph{product integral} from $0$ to
-$\lambda$.
-
-In practice, the integral for transmission probability
-\eqref{eq:ptrans-integral} is difficult to compute even numerically. So we
-choose a product of sigmoid function that approximates the behaviour of
-transmission probability,
-%
-\begin{align}
-\label{eq:evalCumulativePtrans}
-  \Ptrans &= \prod_i L_u(\trackp{t}; \muiu,\Sigmaiu)L_{\lambda}(\lambda; \mu^i_d)
-\end{align}
-%
-where $L_u(.)$ is sigmoid in image domain with $\mu^i_u$ and $\Sigma^i_u$
-representing the elliptical projection of $i^{th}$ TP.
-$L_{\lambda}(.)$ is sigmoid in the depth domain with $\mu^i_d$ as the mean
-depth of the $i^{th}$ TP.
-%
-\begin{align}
-  L_u(\mathbf{u}; \muiu,\Sigmaiu) &= \frac{1}{
-    1 + e^{-k_u(1 - (\mathbf{u} - \muiu)^\top\Sigmaiu(\mathbf{u} -
-    \muiu))}
-  }
-  \\
-  L_{\lambda}(\lambda; \mu^i_d) &= \frac{1}{
-    1 + e^{-k_d(\lambda - \mu^i_d)}
-}
-\end{align}
-%
-
-\begin{comment}%% Comment
-  A product integral is a simple integral in log domain
-  \begin{align}
-    \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} =
-    e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
-  \end{align}
-\end{comment}%% Comment
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Energies}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We explain energies in this section
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Point tracks energy with occlusion}
-\label{sec:totalContPtTracksEnergy}
-We model continuous point tracks energy with explicit occlusion reasoning as
-the expected re-projection error over the association probability,
-
-\begin{multline}
-  \Energy{traci}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \\
-    \sum_{i=1}^{N} 
-    %\sum_{t = s_i}^{e_i}
-    \sum_{j = 1}^{M}
-    \int_1^\infty \assocP\Ereproj(\lambda) d\lambda
-\end{multline}
-where $\assocP$ is the association probability of
-$j$\textsuperscript{th} point with $i$\textsuperscript{th} TP at depth $\lambda$
-and $\Ereproj(\lambda)$ is the re-projection error given by
-%
-\begin{align}
-  \assocP &= \Prefl\Ptrans\\
-  \Ereproj(\lambda) &= \left\|\trackpj{t+1} - \projectionOft{\invProjectionOf{\trackpj{t}, \lambda}}\right\|^2 .
-  \label{eq:reprojerror}
-\end{align}
-
-The  $\projectionOf{.}$ and $\invProjectionOf{.}$ denote the projection and
-inverse projection functions that project 3D point to camera image and vice
-versa. Note that inverse projection $\invProjectionOf{.}$ depend on both the
-point $\trackp{t}$ and the unknown depth $\lambda$. Also note that the inverse projection is dependent on TP pose at time $t$ while the projection depends on pose at time $t+1$ which can be different.
-
-\begin{comment}
-  \subsubsection{Occupancy function}
-  Assuming occupancy to be a
-  probability distribution over 3D space. For each TP the
-  occupancy is modeled as a logistic function 
-  \begin{align}
-     \occf = L(\mathbf{x}; \pos{i}{t}, \Sigma_i)
-  \end{align}
-  where $L(.)$ is the logistic function defined by
-  \begin{align}
-    L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i) = \frac{1}{
-      1 + e^{-k(1 - d(\mathbf{x},\pos{i}{t-1}))}
-      }
-  \end{align}
-  where $d(\mathbf{x},\pos{i}{t-1}) =
-  (\mathbf{x}-\pos{i}{t-1})^\top\Sigma_i(\mathbf{x}-\pos{i}{t-1})$ and $k =
-  10\ln{49}$. $k$ is chosen such that $L(.) = 0.98$ when $d(.) =
-  0.9$
-  % Once we have our distribution over $\lambda$, $\lambdadist$ we can compute the
-  % reprojection of $\trackpj{t-1}$ over image in time $t$ as a function of
-  % $\lambda$. Let
-\end{comment}
-
-\begin{comment}
-  \subsubsection{Approximations}
-  Reflection probability of $i$th TP is easy to compute
-  analytically 
-  \begin{multline}
-    \Prefl =
-    (\max \{ 0, \nabla \occf^\top \ray \})^2 \\
-    = (\max \{ 0, \nabla \occfxi^\top\ray \})^2
-    \label{eq:analytic-prefl}
-  \end{multline}
-  where 
-  \begin{multline}
-    \nabla \occfxi^\top\ray \\=
-    \nabla k\dishort \sech^2\left(\frac{k}{2}\dishort\right)
-  \end{multline}
-  where $\dishort = 1-d(\mathbf{x}, \pos{i}{t-1})$ is a signed distance measure
-  from the contour of the ellipsoid where $d(\mathbf{x}, \pos{i}{t-1})$ is 1.
-
-  However, the transmission probability needs to be approximated.  
-  %
-  % \subsubsection{Computing $\Prefl$ and $\Ptrans$}
-  % Focusing on  $\nabla \occfxi$ 
-  % 
-  % \begin{multline}
-  %   \nabla \occfxi =\\
-  %   \frac{-k\nabla d(\mathbf{x}, \pos{i}{t-1})e^{-k(1-d(\mathbf{x}, \pos{i}{t-1}))}}{
-  %     (1 + e^{-k(1-d(\mathbf{x}, \pos{i}{t-1}))})^2
-  %   } \\ 
-  %   = -k\nabla d(\mathbf{x}, \pos{i}{t-1})\sech^2\left(\frac{k}{2}(1-d(\mathbf{x},
-  %   \pos{i}{t-1}))\right)
-  %   \\
-  %   = \nabla k\dishort \sech^2\left(\frac{k}{2}\dishort\right)
-  % \end{multline}
-  % where $\dishort = 1-d(\mathbf{x}, \pos{i}{t-1})$ is a signed distance measure
-  % from the contour of the ellipsoid where $d(\mathbf{x}, \pos{i}{t-1})$ is 1.
-  % Focusing on $\nabla d(.)$
-  % 
-  % \begin{align}
-  %   \nabla d(\mathbf{x}, \pos{i}{t-1}) = 2\Sigma_i(\mathbf{x} - \pos{i}{t-1})
-  % \end{align}
-  % Back to \eqref{eq:analytic-prefl}
-  % 
-  % \begin{multline}
-  %   (\max \{ 0, \nabla \occf^\top \ray \})^2 = \\
-  %   \sech^4\left(\frac{k}{2}\dishort\right) 
-  %   (\max \{ 0 , \nabla k\dishort^\top\ray\})^2
-  % \end{multline}
-  % 
-  % The probability is simply $\sech^2(.)$ scaled by gradient of ellipsoid
-  % $\nabla k\dishort$ projected in the ray direction $\ray$.
-  % 
-  % \begin{align}
-  %   \Ptrans = 
-  %   e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
-  % \end{align}
-  % \begin{multline}
-  % \int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}
-  % =  \\
-  % \int_{1}^{\lambda} \ln{\left(1 - \sum_i \occfi\right)}{d\lambda}
-  % \end{multline}
-  % 
-  % The above integral is very difficult to approximate or compute analytically.
-  So based on intuition, we approximate the $\Ptrans$ by following function
-  \begin{align}
-  \label{eq:evalCumulativePtrans}
-    \Ptrans &= \prod_i L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)L_{\lambda}(\lambda; \mu^i_d)\\
-    L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u) &= \frac{1}{
-      1 + e^{-k_u(1 - (\mathbf{u} - \mu^i_u)^\top\Sigma^i_u(\mathbf{u} -
-      \mu^i_u))}
-    }
-    \\
-    L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d) &= \frac{1}{
-    1 + e^{-k_d(\lambda - \mu^i_d(\mathbf{u}))}
-  }
-  \end{align}
-  where 
-  \begin{align}
-    \mu_u^i &= \projectionOf{\pos{i}{t-1}} \label{eq:muiudef}\\
-    \Sigma_u^i &= \projectionOf{\Sigma_i} \label{eq:sigmauidef}\\
-    \mu^i_d(\mathbf{u}) &= \relp{i}{t}\\
-    k_u &= 10\log(49)\\
-    k_d &= \frac{\log(49)}{\sqrt{h^2 + l^2 + w^2}}
-    \label{eq:ptransmissionInit}
-  \end{align}
-  is the distance of the centre of the TP from the camera.
-
-  % $\mu^i_d(\mathbf{u}) = \min_{\lambda} d^2_i(\lambda K^{-1}\mathbf{u})$.
-  % $\mu^i_d(\mathbf{u})$ is the closest point to the unit contour of ellipsoid.
-  % If there are multiple such points, the point closest to the camera is taken as
-  % $\mu^i_d(\mathbf{u})$
-
-  The association probability becomes
-
-  \begin{multline}
-    \assocP = 
-      \sech^4\left(\frac{k}{2}\dishort\right)
-      (\max \{ 0, \nabla k\dishort^\top\ray \})^2\\
-    \prod_i \Lu
-      \Llambda \\
-      \label{eq:assocCoeffEval}
-  \end{multline}
-
-  So the energy becomes
-
-  \begin{multline}
-    \label{eq:integrand}
-    \Energy{track}(.) = 
-      \sum_{i = 1}^N
-      \sum_{j = 1}^{M}
-      \int_1^{\infty}
-      \assocP
-      \Ereproj(\lambda)
-      d\lambda
-  \end{multline}
-  where $x = \lambda \ray$ and $\Ereproj(\lambda) = \|\trackpj{t} -
-  f^i_{reproj}(\trackpj{t-1}, \lambda)\|^2$ is reprojection error which is a
-  quadratic in $\lambda$
-
-  The integral in the above expression is computed numerically.
-\end{comment}
-
-\subsection{Object detection energy with occlusion}
-
-Object detection is usually followed by non-maximal suppression that results in
-discarding similar bounding boxes. When we are jointly optimizing detections
-with other cues, it is not usually desirable to go with a single bounding box.
-Hence, we keep all the bounding box detections by approximating them with
-multi-modal sum of Gaussian like logistic functions. We fit the parametric function of the form 
-%
-\begin{align}
-  S(\bb{i}) = \sum_k A_k \exp(-(\bb{i}-\mu^{(d)}_k)^\top \Sigma^{(d)-1}_k
-  (\bb{i}-\mu^{(d)}_k))
-\end{align}
-%
-to detection scores, by non-linear error minimization with initialization from
-non-maximal suppressed outputs. Here $\mu^{(d)}_j$ is one of the $k$ modes as a
-4D vector representing a single bounding box as $[\minx, \miny, \maxx,
-\maxy]^\top$. The optimization is constrained with symmetry and positive
-definiteness of $\Sigma^{(d)-1}_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
-
-\subsubsection{Detection scores with occlusion reasoning} 
-With our model of $\Ptrans$ described in Section \ref{sec:TPmodel}, we can
-compute the probability of a point $\mathbf{u}$ on image be occluded assuming
-the point is on TP $i$ with mean depth $\mu^{(i)}_d$ as
-\begin{align}
-  O_{i}(\mathbf{u}, \mu^{(i)}_d) = 1 - \Ptransmud \enspace .
-\end{align}
-
-If we a portion of our proposed detection bounding box is known to be occluded,
-then we would like to decrease the confidence in the detection score about the
-localization of that end of the object. Assuming that the occlusion is often on
-the boundary of detection bounding boxes, we want to decrease our confidence on
-the mean detection boundaries around the occluded boundaries. 
-One of the simplest ways will be to scale the appropriate diagonal element of
-$\Sigma_j$ by an appropriate scaling factor proportional to occlusion. But this
-does not model appropriate how does occlusion affects the non diagonal terms.
-Hence, we choose a covariance addition model where we compute a occlusion
-covariance matrix, that provides a measure of occlusion in each direction.
-
-To re-model our detection scores scaled by continuous occlusion we sample
-$O_{i}(\mathbf{u}, \mu^{(i)}_d)$ at the hypothesized detection boundaries from
-GMM $S(.)$ and we augment the detection boundary covariance matrix by
-$\mathcal{P}_{j} = \rho_{j}\rho_{j}^\top$ where $\rho_{j} = O_{j}(\mathbf{u},
-\mu^{(i)}_d)$. The new covariance matrix in detection score is given by 
-%
-\begin{align}
-  \Sigma'^{(d)}_j = \mathcal{P}_{j} + \Sigma^{(d)}_j
-\end{align}
-%
-The detection scores GMM with occlusion is given by replacing the covariance
-matrix
-%
-\begin{multline}
-  S'(\bb{i}) =\\
-  \sum_j A_j \exp(-(\bb{i}-\mu^{(d)}_j)^\top \Sigma'^{(d)-1}_j
-  (\bb{i}-\mu^{(d)}_j))
-\end{multline}
-
-The energy of detection scores is simply take to be the inverse of the detection score.
-\begin{align}
-  \Energy{detect}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}
-\end{align}
-
-\subsection{Lane energy}
-\label{sec:laneEnergy}
- The lanes are modeled as splines. Here we assume that the confidence in lane
- detection is decreases as the distance from the lane center increases.  The
- energy is given by the dot product between car orientation and tangent to the
- lane at that point.
-
-\begin{multline}
-  \label{eq:laneOrientationEnergy}
-  \Energy{lane} = \\
-  \sum_{m \in M_{\text{close}}}
-  (1 - \ori{i}{t} \cdot \text{TAN}(L_{m}(k), \pos{i}{t}) )
-\LaneUncertainty{\pos{i}{t}}
-\end{multline}
-where $M_{\text{close}} = \{m : \text{DIST}(L_{m}(k), \pos{i}{t}) < 50\} $ is
-the set of nearby lanes and 
-\begin{multline}
-\LaneUncertainty{\pos{i}{t}} = \\
-  \frac{1}{1 + exp(-q(w_{\text{road}} - \text{DIST}(L_{m}(k), \pos{i}{t})))}
-\end{multline}
-for some constant $w_{\text{road}}$ that represents the width of the road.
-
-\subsection{Transition probability}
-Dynamics constraints should not only enforce smooth trajectories, but also the
-holonomic constraints.  The following energy adds a penalty if the change in
-position is not in direction of previous orientation.
-
-\begin{align}
-  \label{eq:totalPosTransitionEnergy}
-  \Energy{dyn-hol} = 1 - \ori{i}{t-1} \cdot (\pos{i}{t} - \pos{i}{t-1})
-\end{align}
-
-The following energy adds a penalty for change in position and orientation
-but a penalty for change in velocity is much better approximation. However, in
-a Markovian setting that would mean extending the state space of the car to
-include velocity.
-
-\begin{align}
-  \Energy{dyn-ori} &= \|\ori{i}{t} - \ori{i}{t-1}\|^2\\
-  \Energy{dyn-vel} &= \|(\pos{i}{t} - 2\pos{i}{t-1}) + \pos{i}{t-2}\|^2
-\end{align}
-
-As a result the dynamics are modeled by weighted combination of holonomic
-constraint and smoothness constraints.
-
-\begin{align}
-  \WEnergy{dyn} &= \WEnergy{dyn-hol} + \WEnergy{dyn-ori} + \WEnergy{dyn-vel}
-\end{align}
-
-\subsection{Collision energy}
-
-Bhattacharya coefficient $\int_a^b\sqrt{p(x)q(x)}dx$ is a measure of similarity
-of two distributions $p(x)$ and $q(x)$. If we represent TPs as gaussians in
-Birds eye view (BEV), then similarity is a measure of collision. Exactly
-overlapping distribution results in coefficient as 1. 
-%The analytical form of
-%Bhattacharya coefficient has been taken from
-%\url{http://like.silk.to/studymemo/PropertiesOfMultivariateGaussianFunction.pdf}
-
-\begin{multline}
-  \label{eq:collisionEnergyHellingerDistance}
-  \EnergyCol =\\ -\log\left(
-  A_{ij}
-  e^{-\frac{1}{8}
-    \left(\pos{i}{t} - \pos{j}{t}\right)^\top
-    P^{-1}
-    \left(\pos{i}{t} - \pos{j}{t}\right)
-    }
-    \right)
-\end{multline}
-where 
-\begin{align}
-  A_{ij} &= \frac{|\Sigma_i|^\frac{1}{4}|\Sigma_j|^\frac{1}{4}}
-  {|P|^\frac{1}{2}}\\
-  P &= \frac{1}{2}\Sigma_i + \frac{1}{2}\Sigma_j\\
-\Sigma_i^{-1} &= R^\top_{\ori{i}{t}} \begin{bmatrix} 2/l_i & 0 \\ 0 & 2/w_i \end{bmatrix}
-R_{\ori{i}{t}}
-\end{align}
-
-\subsection{Size Prior}
-
-Prior can include among many other things the size prior on the car.
-
-\begin{align}
-  \label{eq:totalSizeEnergy}
-  \Energy{prior} &= (\dimsn{i} - \expDimsn)^\top\Sigma_{\expDimsn}^{-1}(\dimsn{i} -
-  \expDimsn)
-\end{align}
-
-where $\expDimsn$ is the mean TP dimensions and
-$\Sigma_{\expDimsn}$ is the correspondence covariance matrix.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Association error evaluation}
+\paragraph{Association error evaluation}
 
@@
 TP that has smaller mean depth then the competing bounding box.
-
-{\small
-\bibliographystyle{ieee}
-\bibliography{model}
-}
-\end{document}

### 2014-11-10 CVPR/Source/intro.tex
Reorganized paper tex files

--- 2014-11-08 Paper/model.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
+\section{Introduction}
+\label{sec:intro}
 
-\usepackage{cvpr}
-\usepackage{times}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-%%%%%%%%%%% CVPR template packages end %%%%%%%%%%%%%%
-\usepackage{verbatim} % for comment environment
-% \usepackage{soul} % for \hl highlighting
-% Include other packages here, before hyperref.
-
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-
-%\cvprfinalcopy % *** Uncomment this line for the final submission
-
-\def\cvprPaperID{489} % *** Enter the CVPR Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-% 3D pose of the cars and ego motion
-\newcommand{\pos}[2]{\mathbf{p}^{(#1)}(#2)}
-\newcommand{\ori}[2]{\mathbf{\omega}^{(#1)}(#2)}
-\newcommand{\state}[2]{\mathbf{s}^{#1}(#2)}
-
-% ego pose
-\newcommand{\egop}[1][t]{\pos{c}{#1}}
-\newcommand{\egoo}[1][t]{\ori{c}{#1}}
-\newcommand{\egos}[1][t]{\state{c}{#1}}
-
-% relative pose between camera and car $i$
-\newcommand{\relp}[2]{\Omega^{#1}(#2)}
-\newcommand{\relpz}[2]{\Omega_z^{#1}(#2)}
-
-% 3D tracks on car $i$ in its own coordinate frame
-\newcommand{\tracklets}{\mathbf{X}^{(i)}_o}
-\newcommand{\tracklet}[1]{\mathbf{x}^{(i)}_{#1}}
-% track projections on camera
-\newcommand{\trackp}[1]{\mathbf{u}^{(i)}(#1)}
-\newcommand{\trackpj}[1]{\mathbf{u}_j(#1)}
-% Unclassified track point projected on camera
-\newcommand{\ucTrackp}{\mathbf{u}(t)}
-
-% dimensions of car $i$
-\newcommand{\dimsn}[1]{\mathbf{B}^{#1}}
-\newcommand{\expDimsn}{\hat{\mathbf{B}}}
-
-% projection function
-\newcommand{\projectionOf}[1]{\pi_{\relp{i}{t}}\left(#1\right)}
-\newcommand{\projectionOft}[1]{\pi_{\relp{i}{t+1}}\left(#1\right)}
-\newcommand{\centerProj}{\bar{\pi}_{\relp{i}{t}}(\dimsn{i})}
-\newcommand{\cornerProj}[1]{\pi^{#1}_{\relp{i}{t}}(\dimsn{i})}
-\newcommand{\triangleProj}[1]{\triangle^{#1}_{\relp{i}{t}}(\dimsn{i})}
-
-% bounding box corners on image
-\newcommand{\bb}[1]{\mathbf{d}^{#1}(t)}
-
-\newcommand{\Energy}[1]{\mathcal{E}^{it}_{\text{#1}}}
-\newcommand{\pEnergy}[1]{\mathcal{E}^{ijt}_{\text{#1}}}
-% Weighted energy
-\newcommand{\WEnergy}[1]{\lambda_{\text{#1}}\Energy{#1}}
-\newcommand{\EnergyCol}{\mathcal{E}^{ijt}_{\text{col}}}
-\newcommand{\WEnergyCol}{\lambda_{\text{col}}\EnergyCol}
-
-\newcommand{\occFreeProj}[1]{\Pi_{\relp{i}{t}}(#1)}
-\newcommand{\minx}{x_{\text{min}}}
-\newcommand{\miny}{y_{\text{min}}}
-\newcommand{\maxx}{x_{\text{max}}}
-\newcommand{\maxy}{y_{\text{max}}}
-\newcommand{\frontface}{F^i_\text{FF}(t)}
-
-\newcommand{\occ}[1]{o({#1})}
-\newcommand{\face}{F^i_k(t)}
-
-\newcommand{\invProjectionOf}[1]{\pi^{-1}_{\relp{i}{t}}\left(#1\right)}
-\newcommand{\occf}{f^i_{occ}(\mathbf{x}_j)}
-\newcommand{\occftot}{f_{occ}(\mathbf{x}_j)}
-\newcommand{\occft}[1]{f_{occ}(#1)}
-
-\newcommand{\ray}{\hat{\mathbf{r}}_j}
-\newcommand{\occfray}{f_{occ}(\lambda\ray)}
-\newcommand{\lambdadist}{f_{\lambda}(\trackpj{t-1}, \lambda)}
-
-\newcommand{\occfxi}{L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i)}
-\newcommand{\occfi}{L(\lambda \ray; \pos{i}{t-1}, \Sigma_i)}
-\newcommand{\assocP}{a^{(ij)}(\lambda)}
-\newcommand{\assocPk}{a^{(ij)}(\lambda_k)}
-
-\newcommand{\Ereproj}{E^{(ij)}_{\text{reproj}}}
-\newcommand{\Ptrans}{P^{(j)}_{\text{transmission}}(\lambda)}
-\newcommand{\Ptransmud}{P^{(j)}_{\text{transmission}}(\mu^{(i)}_d)}
-\newcommand{\Prefl}{P^{(ij)}_{\text{reflection}}(\lambda)}
-\newcommand{\dishort}{d_i(\mathbf{x})}
-
-\newcommand{\Lu}{L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)}
-\newcommand{\Llambda}{L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d)}
-
-\newcommand{\Gauss}{\mathcal{N}}
-\newcommand{\PropDist}{\mathcal{W}_j}
-
-\newcommand{\muijl}{\mu^{(ij)}_{\lambda}}
-\newcommand{\sigmaijl}{\sigma^{ij}_{\lambda}}
-
-\newcommand{\Sigmait}{\Sigma^{(i)^{-1}}_t}
-
-\newcommand{\muit}{\mu^(i)_t}
-\newcommand{\Sigmaic}{\Sigma'^{(i)^{-1}}_c}
-
-\newcommand{\muic}{{\mu^(i)_c}}
-\newcommand{\Sigmaicf}{\Sigma^{(i)^{-1}}_c}
-
-\newcommand{\muiu}{\mu^{(i)}_t}
-\newcommand{\Sigmaiu}{\Sigma^{(i)^{-1}}_u}
-
-\newcommand{\xt}{\mathbf{x}_t}
-\newcommand{\xc}{\mathbf{x}_c}
-
-\newcommand{\Rctot}{R}
-\newcommand{\tctot}{t}
-
-\newcommand{\tcmut}{t'}
-
-\newcommand{\Beizer}{B\'eizer }
-
-\newcommand{\LaneUncertainty}[1]{\Sigma_{L_m}(#1)}
-\newcommand{\projOnLane}[1]{\pi_{L_m(k)}(#1)}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-%\ifcvprfinal\pagestyle{empty}\fi
-%\setcounter{page}{4321}
-%\DeclareMathSymbol{\Tangent}
-\DeclareMathOperator{\sech}{sech}
-\DeclareMathOperator{\poly}{poly}
-\DeclareMathOperator*{\argmin}{\arg\min}
-
-\begin{document}
-\title{Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.}
-\author{Vikas Dhiman\\
-  University of Michigan\\
-  Ann Arbor, MI, USA\\
-{\tt\small dhiman@umich.edu}
-\and
-Manmohan Chandraker\\
-NEC Laboratories America, Inc.\\
-Cupertino, CA, USA\\
-{\tt\small manu@nec-labs.com}
-\and
-Jason J Corso\\
-  University of Michigan\\
-  Ann Arbor, MI, USA\\
-{\tt\small jjcorso@eecs.umich.edu}
-}
-\maketitle
-
-%%%%%%%%% ABSTRACT
-\begin{abstract}
-  TODO: Write abstract
-  \vspace{4cm}
-\end{abstract}
-
-\section{Introduction}
-
-\begin{itemize}
+\begin{tight_itemize}
   \item Introduce the problem
@@
   \item Highlight the contributions
-\end{itemize}
+\end{tight_itemize}
 \vspace{10cm}
-\begin{figure}[t]
-  \includegraphics[width=\columnwidth]{graphics/graphicalModelFrom61ConstVars.pdf}
+\begin{figure}[!!t]
+  \includegraphics[width=\columnwidth]{Figures/graphicalModelFrom61ConstVars.pdf}
   \caption{Graphical model. The six numbered black circles represent the
@@
 \end{figure}
-
-\section{Related Work}
-TODO:
-\vfill
-\pagebreak
-Related work continued
-\vspace{15cm}
-
-\section{Problem Definition}
-TODO:
-\vspace{4cm}
-
-\section{Notation}
-
-\begin{table}[h]
-  \begin{tabular}{|l|l|}
-    \hline
-    Symbol & Meaning \\
-    \hline
-    $\pos{i}{t}$ & Position of $i$th car at time $t$\\
-    $\ori{i}{t}$ & Orientation of $i$th car at time $t$\\
-     $\dimsn{i}$ & 3D bounding box of the car (dimensions)\\
-    $\state{i}{t}$ & State of car $=\{\pos{i}{t}, \ori{i}{t}, \dimsn{i}\}$\\
-    $\egop$ & Position of camera at time $t$\\
-    $\egoo$ & Orientation of camera at time $t$\\
-    $\relp{i}{t}$ & Relative car pose w.r.t. camera \\
-    $\tracklets$ & 3D points tracked on car $i$ in its own frame\\
-    $\trackp{t}$ & Projection of $\tracklets$ in camera\\
-    $\projectionOf{.}$ & Projection function for pose $\relp{i}{t}$\\
-    $\bb{i}$ & 2D bounding box of the car in image\\
-    \hline
-  \end{tabular}
-\end{table}
-
-%%%%%%%%% BODY TEXT
-\section{The Model}
-
-The objective is to find the most likely traffic participant (TP) state given
-various evidences $\mathbb{E} = \{\{\trackp{t}\}, \{\bb{i}\}, \text{lane det.},
-\text{map}, \text{GPS}\}$.
-
-Mathematically, find:
-\begin{align}
-  \{\state{i}{t}\}^* &= \arg \max P(\{\state{i}{t}\} | \mathbb{E})
-\end{align}
-
-Bayes rule
-\begin{align}
-  P(\{\state{i}{t}\} | \mathbb{E}) &=
-  \frac{1}{Z}P( \mathbb{E} | \{\state{i}{t}\})P(\{\state{i}{t}\})
-\end{align}
-
-Assume conditional independence according to graphical model in
-\ref{fig:graphmodel}.
-
-\begin{multline}
-  P(\{\state{i}{t}\} | \mathbb{E}) =
-  \frac{1}{Z}
-  \prod_{t=s_i}^{e_i}\prod_{i,j: i \ne j}(P(\state{i}{t}, \state{j}{t}))\\
-%
-  \prod_{i=1}^{N}
-  \prod_{t=s_i}^{e_i}
-  P(\bb{i} | \state{i}{t})
-  P(\trackp{t} | \state{i}{t})\\
-  P(\state{i}{t} | L_m(t))
-  P(\state{i}{t} | \state{i}{t-1})
-  P(\state{i}{t})
-\end{multline}
-
-We can formulate similar objective function in negative log domain:
-\footnote{TODO:Resolve inconsistency in summation absorption in energy terms.}
-\begin{multline}
-  -\log{P(\{\state{i}{t}\} | \mathbb{E})} = 
-  Z' + \sum_{i,j:i\ne j} \sum_{t=s_i}^{e_i}  \WEnergyCol \\
-  + \sum_{i=1}^N \sum_{t=s_i}^{e_i}
-    \WEnergy{box}
-  + \WEnergy{track}\\
-  + \WEnergy{lane}
-  + \WEnergy{dyn}
-  + \WEnergy{prior}
-\end{multline}
-
-\section{Modeling traffic participants}
-\label{sec:TPmodel}
-Following standard model of occupancy in 3D reconstruction community, we model
-the TP's as high occupancy regions in space. We model the
-uncertainty in occupancy equivalent of transparency i.e. the regions that are
-more certain to be occupied are viewed as relatively more opaque then other
-regions. Based on this intuition we model TP's translucent
-ellipsoids whose opacity is maximum at the center and drops off away from the
-center. More specifically we model, the occupancy of a TP as a
-logistic function,
-
-\begin{align}
-   \occf = L(\mathbf{x}; \pos{i}{t}, \Sigma_i)
-\end{align}
-where $L(.)$ is the logistic function defined by
-\begin{align}
-  L(\mathbf{x}; \pos{i}{t}, \Sigma_i) = \frac{1}{
-    1 + e^{-k(1 - d(\mathbf{x},\pos{i}{t}))}
-    }
-\end{align}
-where $d(\mathbf{x},\pos{i}{t}) =
-(\mathbf{x}-\pos{i}{t})^\top\Sigma_i(\mathbf{x}-\pos{i}{t})$ and $k =
-10\ln{49}$. $k$ is chosen such that $L(.) = 0.98$ when $d(.) =
-0.9$. $\Sigma_i$ determines the spread of the ellipsoid and depends on the
-dimensions of the TP. Please refer to supplementary material 
-for computation of $\Sigma_i$ from TP's dimensions.
-
-We model the probability of a point $\mathbf{x}_j$ on a object $i$ getting successfully
-observed in a camera image at point $\trackpj{t}$ is dependent up two factors,
-(1) reflection and (2) transmission through intermediate space. The reflection
-part ensures that there is an object to reflect a point at a certain region in
-the 3D space while transmission part models occlusion.
-\begin{align}
-  P^{(ij)}_{\text{observation}} = P^{(ij)}_{\text{reflection}}P^{(j)}_{\text{transmission}}
-\end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Reflection probability}
-For Lambertian reflection we replace the surface normal with the
-gradient of occupancy.
-%
-\begin{align}
-  \Prefl = (\max \{0, \nabla \occf^\top
-  \hat{\mathbf{r}_j}\})^2
-\end{align}
-%
-where $\ray =
-\frac{K^{-1}\trackpj{t}}{\|K^{-1}\trackpj{t}\|}$ is unit vector in the
-direction of ray. The gradient in the direction opposite to ray yields -ve
-probability which needs to be clipped off. Squaring the function keep it
-smooth near zero.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Transmission probability}
-A model for transmission of light through a material of thickness $x$,
-density $\rho$ and opacity $k_o$ is given by Beer-Lambert law 
-%
-\begin{align}
-  I(x) = I_0e^{-k_o\rho x}
-\end{align}
-%
-
-Since both opacity and density are represented by the occupancy function
-$\occftot = \sum_i \occf$, and also the domain of our $\occftot$ is $[0, 1]$ instead of $[0,
-\infty]$ as in case of $k_o$; we replace $e^{-k_o\rho}$ by the transparency
-function $1 - \occftot$. So the transmission probability over a small distance
-$d\lambda$ is given by
-%
-\begin{align}
-  P_{\text{transmission}}(\lambda + d\lambda) =
-  P_{\text{transmission}}(\lambda) (1-\occftot)^{d\lambda}
-\end{align}
-%
-
-For a given 3D point $\mathbf{x}_j = \lambda \ray$, the probability that the
-point $\trackpj{t}$ is reflected from a distance $\lambda$ is given by
-
-\begin{align}
-  %P^{(j)}_{\text{observation}}(\lambda) &= P_{\text{reflection}}
-  \Ptrans &=
-  \prod_{0}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda} %\\
-  %= \max \{ 0, (\nabla f_{occ}&(\lambda \ray)^\top \ray) \}
-  %\prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
-  \label{eq:ptrans-integral}
-\end{align}
-where $\prod_{0}^{\lambda}$ represents the \emph{product integral} from $0$ to
-$\lambda$.
-
-In practice, the integral for transmission probability
-\eqref{eq:ptrans-integral} is difficult to compute even numerically. So we
-choose a product of sigmoid function that approximates the behaviour of
-transmission probability,
-%
-\begin{align}
-\label{eq:evalCumulativePtrans}
-  \Ptrans &= \prod_i L_u(\trackp{t}; \muiu,\Sigmaiu)L_{\lambda}(\lambda; \mu^i_d)
-\end{align}
-%
-where $L_u(.)$ is sigmoid in image domain with $\mu^i_u$ and $\Sigma^i_u$
-representing the elliptical projection of $i^{th}$ TP.
-$L_{\lambda}(.)$ is sigmoid in the depth domain with $\mu^i_d$ as the mean
-depth of the $i^{th}$ TP.
-%
-\begin{align}
-  L_u(\mathbf{u}; \muiu,\Sigmaiu) &= \frac{1}{
-    1 + e^{-k_u(1 - (\mathbf{u} - \muiu)^\top\Sigmaiu(\mathbf{u} -
-    \muiu))}
-  }
-  \\
-  L_{\lambda}(\lambda; \mu^i_d) &= \frac{1}{
-    1 + e^{-k_d(\lambda - \mu^i_d)}
-}
-\end{align}
-%
-
-\begin{comment}%% Comment
-  A product integral is a simple integral in log domain
-  \begin{align}
-    \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} =
-    e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
-  \end{align}
-\end{comment}%% Comment
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Energies}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We explain energies in this section
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Point tracks energy with occlusion}
-\label{sec:totalContPtTracksEnergy}
-We model continuous point tracks energy with explicit occlusion reasoning as
-the expected re-projection error over the association probability,
-
-\begin{multline}
-  \Energy{traci}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \\
-    \sum_{i=1}^{N} 
-    %\sum_{t = s_i}^{e_i}
-    \sum_{j = 1}^{M}
-    \int_1^\infty \assocP\Ereproj(\lambda) d\lambda
-\end{multline}
-where $\assocP$ is the association probability of
-$j$\textsuperscript{th} point with $i$\textsuperscript{th} TP at depth $\lambda$
-and $\Ereproj(\lambda)$ is the re-projection error given by
-%
-\begin{align}
-  \assocP &= \Prefl\Ptrans\\
-  \Ereproj(\lambda) &= \left\|\trackpj{t+1} - \projectionOft{\invProjectionOf{\trackpj{t}, \lambda}}\right\|^2 .
-  \label{eq:reprojerror}
-\end{align}
-
-The  $\projectionOf{.}$ and $\invProjectionOf{.}$ denote the projection and
-inverse projection functions that project 3D point to camera image and vice
-versa. Note that inverse projection $\invProjectionOf{.}$ depend on both the
-point $\trackp{t}$ and the unknown depth $\lambda$. Also note that the inverse projection is dependent on TP pose at time $t$ while the projection depends on pose at time $t+1$ which can be different.
-
-\begin{comment}
-  \subsubsection{Occupancy function}
-  Assuming occupancy to be a
-  probability distribution over 3D space. For each TP the
-  occupancy is modeled as a logistic function 
-  \begin{align}
-     \occf = L(\mathbf{x}; \pos{i}{t}, \Sigma_i)
-  \end{align}
-  where $L(.)$ is the logistic function defined by
-  \begin{align}
-    L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i) = \frac{1}{
-      1 + e^{-k(1 - d(\mathbf{x},\pos{i}{t-1}))}
-      }
-  \end{align}
-  where $d(\mathbf{x},\pos{i}{t-1}) =
-  (\mathbf{x}-\pos{i}{t-1})^\top\Sigma_i(\mathbf{x}-\pos{i}{t-1})$ and $k =
-  10\ln{49}$. $k$ is chosen such that $L(.) = 0.98$ when $d(.) =
-  0.9$
-  % Once we have our distribution over $\lambda$, $\lambdadist$ we can compute the
-  % reprojection of $\trackpj{t-1}$ over image in time $t$ as a function of
-  % $\lambda$. Let
-\end{comment}
-
-\begin{comment}
-  \subsubsection{Approximations}
-  Reflection probability of $i$th TP is easy to compute
-  analytically 
-  \begin{multline}
-    \Prefl =
-    (\max \{ 0, \nabla \occf^\top \ray \})^2 \\
-    = (\max \{ 0, \nabla \occfxi^\top\ray \})^2
-    \label{eq:analytic-prefl}
-  \end{multline}
-  where 
-  \begin{multline}
-    \nabla \occfxi^\top\ray \\=
-    \nabla k\dishort \sech^2\left(\frac{k}{2}\dishort\right)
-  \end{multline}
-  where $\dishort = 1-d(\mathbf{x}, \pos{i}{t-1})$ is a signed distance measure
-  from the contour of the ellipsoid where $d(\mathbf{x}, \pos{i}{t-1})$ is 1.
-
-  However, the transmission probability needs to be approximated.  
-  %
-  % \subsubsection{Computing $\Prefl$ and $\Ptrans$}
-  % Focusing on  $\nabla \occfxi$ 
-  % 
-  % \begin{multline}
-  %   \nabla \occfxi =\\
-  %   \frac{-k\nabla d(\mathbf{x}, \pos{i}{t-1})e^{-k(1-d(\mathbf{x}, \pos{i}{t-1}))}}{
-  %     (1 + e^{-k(1-d(\mathbf{x}, \pos{i}{t-1}))})^2
-  %   } \\ 
-  %   = -k\nabla d(\mathbf{x}, \pos{i}{t-1})\sech^2\left(\frac{k}{2}(1-d(\mathbf{x},
-  %   \pos{i}{t-1}))\right)
-  %   \\
-  %   = \nabla k\dishort \sech^2\left(\frac{k}{2}\dishort\right)
-  % \end{multline}
-  % where $\dishort = 1-d(\mathbf{x}, \pos{i}{t-1})$ is a signed distance measure
-  % from the contour of the ellipsoid where $d(\mathbf{x}, \pos{i}{t-1})$ is 1.
-  % Focusing on $\nabla d(.)$
-  % 
-  % \begin{align}
-  %   \nabla d(\mathbf{x}, \pos{i}{t-1}) = 2\Sigma_i(\mathbf{x} - \pos{i}{t-1})
-  % \end{align}
-  % Back to \eqref{eq:analytic-prefl}
-  % 
-  % \begin{multline}
-  %   (\max \{ 0, \nabla \occf^\top \ray \})^2 = \\
-  %   \sech^4\left(\frac{k}{2}\dishort\right) 
-  %   (\max \{ 0 , \nabla k\dishort^\top\ray\})^2
-  % \end{multline}
-  % 
-  % The probability is simply $\sech^2(.)$ scaled by gradient of ellipsoid
-  % $\nabla k\dishort$ projected in the ray direction $\ray$.
-  % 
-  % \begin{align}
-  %   \Ptrans = 
-  %   e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
-  % \end{align}
-  % \begin{multline}
-  % \int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}
-  % =  \\
-  % \int_{1}^{\lambda} \ln{\left(1 - \sum_i \occfi\right)}{d\lambda}
-  % \end{multline}
-  % 
-  % The above integral is very difficult to approximate or compute analytically.
-  So based on intuition, we approximate the $\Ptrans$ by following function
-  \begin{align}
-  \label{eq:evalCumulativePtrans}
-    \Ptrans &= \prod_i L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)L_{\lambda}(\lambda; \mu^i_d)\\
-    L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u) &= \frac{1}{
-      1 + e^{-k_u(1 - (\mathbf{u} - \mu^i_u)^\top\Sigma^i_u(\mathbf{u} -
-      \mu^i_u))}
-    }
-    \\
-    L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d) &= \frac{1}{
-    1 + e^{-k_d(\lambda - \mu^i_d(\mathbf{u}))}
-  }
-  \end{align}
-  where 
-  \begin{align}
-    \mu_u^i &= \projectionOf{\pos{i}{t-1}} \label{eq:muiudef}\\
-    \Sigma_u^i &= \projectionOf{\Sigma_i} \label{eq:sigmauidef}\\
-    \mu^i_d(\mathbf{u}) &= \relp{i}{t}\\
-    k_u &= 10\log(49)\\
-    k_d &= \frac{\log(49)}{\sqrt{h^2 + l^2 + w^2}}
-    \label{eq:ptransmissionInit}
-  \end{align}
-  is the distance of the centre of the TP from the camera.
-
-  % $\mu^i_d(\mathbf{u}) = \min_{\lambda} d^2_i(\lambda K^{-1}\mathbf{u})$.
-  % $\mu^i_d(\mathbf{u})$ is the closest point to the unit contour of ellipsoid.
-  % If there are multiple such points, the point closest to the camera is taken as
-  % $\mu^i_d(\mathbf{u})$
-
-  The association probability becomes
-
-  \begin{multline}
-    \assocP = 
-      \sech^4\left(\frac{k}{2}\dishort\right)
-      (\max \{ 0, \nabla k\dishort^\top\ray \})^2\\
-    \prod_i \Lu
-      \Llambda \\
-      \label{eq:assocCoeffEval}
-  \end{multline}
-
-  So the energy becomes
-
-  \begin{multline}
-    \label{eq:integrand}
-    \Energy{track}(.) = 
-      \sum_{i = 1}^N
-      \sum_{j = 1}^{M}
-      \int_1^{\infty}
-      \assocP
-      \Ereproj(\lambda)
-      d\lambda
-  \end{multline}
-  where $x = \lambda \ray$ and $\Ereproj(\lambda) = \|\trackpj{t} -
-  f^i_{reproj}(\trackpj{t-1}, \lambda)\|^2$ is reprojection error which is a
-  quadratic in $\lambda$
-
-  The integral in the above expression is computed numerically.
-\end{comment}
-
-\subsection{Object detection energy with occlusion}
-
-Object detection is usually followed by non-maximal suppression that results in
-discarding similar bounding boxes. When we are jointly optimizing detections
-with other cues, it is not usually desirable to go with a single bounding box.
-Hence, we keep all the bounding box detections by approximating them with
-multi-modal sum of Gaussian like logistic functions. We fit the parametric function of the form 
-%
-\begin{align}
-  S(\bb{i}) = \sum_k A_k \exp(-(\bb{i}-\mu^{(d)}_k)^\top \Sigma^{(d)-1}_k
-  (\bb{i}-\mu^{(d)}_k))
-\end{align}
-%
-to detection scores, by non-linear error minimization with initialization from
-non-maximal suppressed outputs. Here $\mu^{(d)}_j$ is one of the $k$ modes as a
-4D vector representing a single bounding box as $[\minx, \miny, \maxx,
-\maxy]^\top$. The optimization is constrained with symmetry and positive
-definiteness of $\Sigma^{(d)-1}_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
-
-\subsubsection{Detection scores with occlusion reasoning} 
-With our model of $\Ptrans$ described in Section \ref{sec:TPmodel}, we can
-compute the probability of a point $\mathbf{u}$ on image be occluded assuming
-the point is on TP $i$ with mean depth $\mu^{(i)}_d$ as
-\begin{align}
-  O_{i}(\mathbf{u}, \mu^{(i)}_d) = 1 - \Ptransmud \enspace .
-\end{align}
-
-If we a portion of our proposed detection bounding box is known to be occluded,
-then we would like to decrease the confidence in the detection score about the
-localization of that end of the object. Assuming that the occlusion is often on
-the boundary of detection bounding boxes, we want to decrease our confidence on
-the mean detection boundaries around the occluded boundaries. 
-One of the simplest ways will be to scale the appropriate diagonal element of
-$\Sigma_j$ by an appropriate scaling factor proportional to occlusion. But this
-does not model appropriate how does occlusion affects the non diagonal terms.
-Hence, we choose a covariance addition model where we compute a occlusion
-covariance matrix, that provides a measure of occlusion in each direction.
-
-To re-model our detection scores scaled by continuous occlusion we sample
-$O_{i}(\mathbf{u}, \mu^{(i)}_d)$ at the hypothesized detection boundaries from
-GMM $S(.)$ and we augment the detection boundary covariance matrix by
-$\mathcal{P}_{j} = \rho_{j}\rho_{j}^\top$ where $\rho_{j} = O_{j}(\mathbf{u},
-\mu^{(i)}_d)$. The new covariance matrix in detection score is given by 
-%
-\begin{align}
-  \Sigma'^{(d)}_j = \mathcal{P}_{j} + \Sigma^{(d)}_j
-\end{align}
-%
-The detection scores GMM with occlusion is given by replacing the covariance
-matrix
-%
-\begin{multline}
-  S'(\bb{i}) =\\
-  \sum_j A_j \exp(-(\bb{i}-\mu^{(d)}_j)^\top \Sigma'^{(d)-1}_j
-  (\bb{i}-\mu^{(d)}_j))
-\end{multline}
-
-The energy of detection scores is simply take to be the inverse of the detection score.
-\begin{align}
-  \Energy{detect}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}
-\end{align}
-
-\subsection{Lane energy}
-\label{sec:laneEnergy}
- The lanes are modeled as splines. Here we assume that the confidence in lane
- detection is decreases as the distance from the lane center increases.  The
- energy is given by the dot product between car orientation and tangent to the
- lane at that point.
-
-\begin{multline}
-  \label{eq:laneOrientationEnergy}
-  \Energy{lane} = \\
-  \sum_{m \in M_{\text{close}}}
-  (1 - \ori{i}{t} \cdot \text{TAN}(L_{m}(k), \pos{i}{t}) )
-\LaneUncertainty{\pos{i}{t}}
-\end{multline}
-where $M_{\text{close}} = \{m : \text{DIST}(L_{m}(k), \pos{i}{t}) < 50\} $ is
-the set of nearby lanes and 
-\begin{multline}
-\LaneUncertainty{\pos{i}{t}} = \\
-  \frac{1}{1 + exp(-q(w_{\text{road}} - \text{DIST}(L_{m}(k), \pos{i}{t})))}
-\end{multline}
-for some constant $w_{\text{road}}$ that represents the width of the road.
-
-\subsection{Transition probability}
-Dynamics constraints should not only enforce smooth trajectories, but also the
-holonomic constraints.  The following energy adds a penalty if the change in
-position is not in direction of previous orientation.
-
-\begin{align}
-  \label{eq:totalPosTransitionEnergy}
-  \Energy{dyn-hol} = 1 - \ori{i}{t-1} \cdot (\pos{i}{t} - \pos{i}{t-1})
-\end{align}
-
-The following energy adds a penalty for change in position and orientation
-but a penalty for change in velocity is much better approximation. However, in
-a Markovian setting that would mean extending the state space of the car to
-include velocity.
-
-\begin{align}
-  \Energy{dyn-ori} &= \|\ori{i}{t} - \ori{i}{t-1}\|^2\\
-  \Energy{dyn-vel} &= \|(\pos{i}{t} - 2\pos{i}{t-1}) + \pos{i}{t-2}\|^2
-\end{align}
-
-As a result the dynamics are modeled by weighted combination of holonomic
-constraint and smoothness constraints.
-
-\begin{align}
-  \WEnergy{dyn} &= \WEnergy{dyn-hol} + \WEnergy{dyn-ori} + \WEnergy{dyn-vel}
-\end{align}
-
-\subsection{Collision energy}
-
-Bhattacharya coefficient $\int_a^b\sqrt{p(x)q(x)}dx$ is a measure of similarity
-of two distributions $p(x)$ and $q(x)$. If we represent TPs as gaussians in
-Birds eye view (BEV), then similarity is a measure of collision. Exactly
-overlapping distribution results in coefficient as 1. 
-%The analytical form of
-%Bhattacharya coefficient has been taken from
-%\url{http://like.silk.to/studymemo/PropertiesOfMultivariateGaussianFunction.pdf}
-
-\begin{multline}
-  \label{eq:collisionEnergyHellingerDistance}
-  \EnergyCol =\\ -\log\left(
-  A_{ij}
-  e^{-\frac{1}{8}
-    \left(\pos{i}{t} - \pos{j}{t}\right)^\top
-    P^{-1}
-    \left(\pos{i}{t} - \pos{j}{t}\right)
-    }
-    \right)
-\end{multline}
-where 
-\begin{align}
-  A_{ij} &= \frac{|\Sigma_i|^\frac{1}{4}|\Sigma_j|^\frac{1}{4}}
-  {|P|^\frac{1}{2}}\\
-  P &= \frac{1}{2}\Sigma_i + \frac{1}{2}\Sigma_j\\
-\Sigma_i^{-1} &= R^\top_{\ori{i}{t}} \begin{bmatrix} 2/l_i & 0 \\ 0 & 2/w_i \end{bmatrix}
-R_{\ori{i}{t}}
-\end{align}
-
-\subsection{Size Prior}
-
-Prior can include among many other things the size prior on the car.
-
-\begin{align}
-  \label{eq:totalSizeEnergy}
-  \Energy{prior} &= (\dimsn{i} - \expDimsn)^\top\Sigma_{\expDimsn}^{-1}(\dimsn{i} -
-  \expDimsn)
-\end{align}
-
-where $\expDimsn$ is the mean TP dimensions and
-$\Sigma_{\expDimsn}$ is the correspondence covariance matrix.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Association error evaluation}
-
-To verify the correctness of our association probability $\assocP$ we perform
-association error experiment that compare the accuracy of point track
-association with TPs with that of bounding box baseline method.
-
-% \begin{align}
-%   f^{i}_{reproj}&(\trackpj{t-1}, \lambda) =
-%   \projectionOf{\invProjectionOf{\trackpj{t-1}}}\\
-%   %&= K(R^i_t ((R^i_{t-1})^\top\lambda \ray - (R^i_{t-1})^\top T_{t-1}) + T_{t})\\
-%   &= \frac
-%   {p_{1:2}\lambda + q_{1:2}}
-%   {p_{3}\lambda + q_{3}}
-% \end{align}
-% where $p_{1:3} = KR^i_t(R^i_{t-1})^\top\ray$ and
-% $q_{1:3} = KR^i_t(R^i_{t-1})^\top T_{t-1} + KT_t$
-% 
-% Now that we have an association from TP $i$ to point track $j$ through
-% $\lambda$, we can come up with an association probability
-% \begin{align}
-%    \assocP &= \frac{(\max \{ 0, \nabla \occf^\top
-% \ray \})^2 }{P_{\text{reflection}}}\lambdadist\\
-% &=(\max \{ 0, \nabla \occf^\top \ray \})^2
-%   \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
-% \end{align}
-
-Note that the fraction $\assocP$ although called association probability does
-not capture the entire information that we have available for compute
-association of points to tracks. This above fraction is the association
-probability given the hypothesized parameters of TP model.
-
-To compute the association probability between TP $i$ and
-point track $j$ we must use re-projection error as well. When the association
-$i$ and $j$ is right and the point of reflection is at depth $\lambda$ the
-re-projection error must be zero \eqref{eq:reprojerror}, otherwise the error
-becomes a measure of distance from the true solution.
-The error terms can be converted to probability domain by considering the error
-term as negative log of probability
-
-\begin{align}
-  P^{(ij)}_{\text{assoc by reproj}}(\lambda) = \frac{1}{Z}\exp(-\Ereproj(\lambda))
-\end{align}
-
-Using both the evidence terms we can write probability of association as
-\begin{align}
-  P^{(ij)}_{\text{assoc}} = \frac{1}{Z'}\int_0^{\infty} \assocP \frac{1}{\sqrt{2\pi}}\exp(-\Ereproj(\lambda))d\lambda
-  \label{eq:prob-assoc}
-\end{align}
-
-Once we have the probability of association we can compute the best possible
-assignment of TP for each point. The points having very small association
-probability are assigned to the background,
-\begin{align}
-  i^*_{j} = \argmin_{i} \int_0^\infty \assocP \Ereproj(\lambda) d\lambda
-\end{align}
-
-We use bounding box based assignment of point tracks to TPs as the baseline.
-For the regions where the bounding boxes overlap, we assign the points to the
-TP that has smaller mean depth then the competing bounding box.
-
-{\small
-\bibliographystyle{ieee}
-\bibliography{model}
-}
-\end{document}

### 2014-11-10 CVPR/Source/localize.tex
Reorganized paper tex files

--- 2014-11-08 Paper/model.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
-
-\usepackage{cvpr}
-\usepackage{times}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-%%%%%%%%%%% CVPR template packages end %%%%%%%%%%%%%%
-\usepackage{verbatim} % for comment environment
-% \usepackage{soul} % for \hl highlighting
-% Include other packages here, before hyperref.
-
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-
-%\cvprfinalcopy % *** Uncomment this line for the final submission
-
-\def\cvprPaperID{489} % *** Enter the CVPR Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-% 3D pose of the cars and ego motion
-\newcommand{\pos}[2]{\mathbf{p}^{(#1)}(#2)}
-\newcommand{\ori}[2]{\mathbf{\omega}^{(#1)}(#2)}
-\newcommand{\state}[2]{\mathbf{s}^{#1}(#2)}
-
-% ego pose
-\newcommand{\egop}[1][t]{\pos{c}{#1}}
-\newcommand{\egoo}[1][t]{\ori{c}{#1}}
-\newcommand{\egos}[1][t]{\state{c}{#1}}
-
-% relative pose between camera and car $i$
-\newcommand{\relp}[2]{\Omega^{#1}(#2)}
-\newcommand{\relpz}[2]{\Omega_z^{#1}(#2)}
-
-% 3D tracks on car $i$ in its own coordinate frame
-\newcommand{\tracklets}{\mathbf{X}^{(i)}_o}
-\newcommand{\tracklet}[1]{\mathbf{x}^{(i)}_{#1}}
-% track projections on camera
-\newcommand{\trackp}[1]{\mathbf{u}^{(i)}(#1)}
-\newcommand{\trackpj}[1]{\mathbf{u}_j(#1)}
-% Unclassified track point projected on camera
-\newcommand{\ucTrackp}{\mathbf{u}(t)}
-
-% dimensions of car $i$
-\newcommand{\dimsn}[1]{\mathbf{B}^{#1}}
-\newcommand{\expDimsn}{\hat{\mathbf{B}}}
-
-% projection function
-\newcommand{\projectionOf}[1]{\pi_{\relp{i}{t}}\left(#1\right)}
-\newcommand{\projectionOft}[1]{\pi_{\relp{i}{t+1}}\left(#1\right)}
-\newcommand{\centerProj}{\bar{\pi}_{\relp{i}{t}}(\dimsn{i})}
-\newcommand{\cornerProj}[1]{\pi^{#1}_{\relp{i}{t}}(\dimsn{i})}
-\newcommand{\triangleProj}[1]{\triangle^{#1}_{\relp{i}{t}}(\dimsn{i})}
-
-% bounding box corners on image
-\newcommand{\bb}[1]{\mathbf{d}^{#1}(t)}
-
-\newcommand{\Energy}[1]{\mathcal{E}^{it}_{\text{#1}}}
-\newcommand{\pEnergy}[1]{\mathcal{E}^{ijt}_{\text{#1}}}
-% Weighted energy
-\newcommand{\WEnergy}[1]{\lambda_{\text{#1}}\Energy{#1}}
-\newcommand{\EnergyCol}{\mathcal{E}^{ijt}_{\text{col}}}
-\newcommand{\WEnergyCol}{\lambda_{\text{col}}\EnergyCol}
-
-\newcommand{\occFreeProj}[1]{\Pi_{\relp{i}{t}}(#1)}
-\newcommand{\minx}{x_{\text{min}}}
-\newcommand{\miny}{y_{\text{min}}}
-\newcommand{\maxx}{x_{\text{max}}}
-\newcommand{\maxy}{y_{\text{max}}}
-\newcommand{\frontface}{F^i_\text{FF}(t)}
-
-\newcommand{\occ}[1]{o({#1})}
-\newcommand{\face}{F^i_k(t)}
-
-\newcommand{\invProjectionOf}[1]{\pi^{-1}_{\relp{i}{t}}\left(#1\right)}
-\newcommand{\occf}{f^i_{occ}(\mathbf{x}_j)}
-\newcommand{\occftot}{f_{occ}(\mathbf{x}_j)}
-\newcommand{\occft}[1]{f_{occ}(#1)}
-
-\newcommand{\ray}{\hat{\mathbf{r}}_j}
-\newcommand{\occfray}{f_{occ}(\lambda\ray)}
-\newcommand{\lambdadist}{f_{\lambda}(\trackpj{t-1}, \lambda)}
-
-\newcommand{\occfxi}{L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i)}
-\newcommand{\occfi}{L(\lambda \ray; \pos{i}{t-1}, \Sigma_i)}
-\newcommand{\assocP}{a^{(ij)}(\lambda)}
-\newcommand{\assocPk}{a^{(ij)}(\lambda_k)}
-
-\newcommand{\Ereproj}{E^{(ij)}_{\text{reproj}}}
-\newcommand{\Ptrans}{P^{(j)}_{\text{transmission}}(\lambda)}
-\newcommand{\Ptransmud}{P^{(j)}_{\text{transmission}}(\mu^{(i)}_d)}
-\newcommand{\Prefl}{P^{(ij)}_{\text{reflection}}(\lambda)}
-\newcommand{\dishort}{d_i(\mathbf{x})}
-
-\newcommand{\Lu}{L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)}
-\newcommand{\Llambda}{L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d)}
-
-\newcommand{\Gauss}{\mathcal{N}}
-\newcommand{\PropDist}{\mathcal{W}_j}
-
-\newcommand{\muijl}{\mu^{(ij)}_{\lambda}}
-\newcommand{\sigmaijl}{\sigma^{ij}_{\lambda}}
-
-\newcommand{\Sigmait}{\Sigma^{(i)^{-1}}_t}
-
-\newcommand{\muit}{\mu^(i)_t}
-\newcommand{\Sigmaic}{\Sigma'^{(i)^{-1}}_c}
-
-\newcommand{\muic}{{\mu^(i)_c}}
-\newcommand{\Sigmaicf}{\Sigma^{(i)^{-1}}_c}
-
-\newcommand{\muiu}{\mu^{(i)}_t}
-\newcommand{\Sigmaiu}{\Sigma^{(i)^{-1}}_u}
-
-\newcommand{\xt}{\mathbf{x}_t}
-\newcommand{\xc}{\mathbf{x}_c}
-
-\newcommand{\Rctot}{R}
-\newcommand{\tctot}{t}
-
-\newcommand{\tcmut}{t'}
-
-\newcommand{\Beizer}{B\'eizer }
-
-\newcommand{\LaneUncertainty}[1]{\Sigma_{L_m}(#1)}
-\newcommand{\projOnLane}[1]{\pi_{L_m(k)}(#1)}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-%\ifcvprfinal\pagestyle{empty}\fi
-%\setcounter{page}{4321}
-%\DeclareMathSymbol{\Tangent}
-\DeclareMathOperator{\sech}{sech}
-\DeclareMathOperator{\poly}{poly}
-\DeclareMathOperator*{\argmin}{\arg\min}
-
-\begin{document}
-\title{Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.}
-\author{Vikas Dhiman\\
-  University of Michigan\\
-  Ann Arbor, MI, USA\\
-{\tt\small dhiman@umich.edu}
-\and
-Manmohan Chandraker\\
-NEC Laboratories America, Inc.\\
-Cupertino, CA, USA\\
-{\tt\small manu@nec-labs.com}
-\and
-Jason J Corso\\
-  University of Michigan\\
-  Ann Arbor, MI, USA\\
-{\tt\small jjcorso@eecs.umich.edu}
-}
-\maketitle
-
-%%%%%%%%% ABSTRACT
-\begin{abstract}
-  TODO: Write abstract
-  \vspace{4cm}
-\end{abstract}
-
-\section{Introduction}
-
-\begin{itemize}
-  \item Introduce the problem
-  \item Describe our approach
-  \item Contrast with Milan's work
-  \item Contrast with Andreas Geiger's work
-  \item Highlight the contributions
-\end{itemize}
-\vspace{10cm}
-\begin{figure}[t]
-  \includegraphics[width=\columnwidth]{graphics/graphicalModelFrom61ConstVars.pdf}
-  \caption{Graphical model. The six numbered black circles represent the
-    unknown state variables of each car. All other nodes in the graphical model
-    are assumed
-    observed variables. Consider each energy in the model one by one. (1)
-    Bounding box energy: The bounding box energy without occlusion modeling is
-    a unary term, but with occlusion it becomes a higher order term that
-    affects the state of occluder as well. In this graphical model we assume
-    that the scene is being observed from left to right, hence "2" occludes "6"
-    and "5" and "5" occludes "1". The bounding box detection is represented by
-  $\mathbf{d}_{bb}^i(t)$ and the statistical dependencies are represented by
-  red lines. (2) Point tracks ($\Energy{track}$): Since occlusion is also
-  included in modeling point tracks energy we have similar interdependencies
-  for point tracks energy. The available point tracks are modeled by
-  $\mathbf{u}(t)$. (3) Collision ($\Energy{coll}$) : The collision energy
-  mathematically is a dense graph between all the TP but here we represent
-  collision among only those TP that are near enough to have a significant
-collision energy. (4) Orientation from detection ($\Energy{ori}$) (5) Orientation from lane (and map) information ($\Energy{lane}$)}
-  \label{fig:graphmodel}
-\end{figure}
-
-\section{Related Work}
-TODO:
-\vfill
-\pagebreak
-Related work continued
-\vspace{15cm}
-
-\section{Problem Definition}
-TODO:
-\vspace{4cm}
-
-\section{Notation}
-
-\begin{table}[h]
-  \begin{tabular}{|l|l|}
-    \hline
-    Symbol & Meaning \\
-    \hline
-    $\pos{i}{t}$ & Position of $i$th car at time $t$\\
-    $\ori{i}{t}$ & Orientation of $i$th car at time $t$\\
-     $\dimsn{i}$ & 3D bounding box of the car (dimensions)\\
-    $\state{i}{t}$ & State of car $=\{\pos{i}{t}, \ori{i}{t}, \dimsn{i}\}$\\
-    $\egop$ & Position of camera at time $t$\\
-    $\egoo$ & Orientation of camera at time $t$\\
-    $\relp{i}{t}$ & Relative car pose w.r.t. camera \\
-    $\tracklets$ & 3D points tracked on car $i$ in its own frame\\
-    $\trackp{t}$ & Projection of $\tracklets$ in camera\\
-    $\projectionOf{.}$ & Projection function for pose $\relp{i}{t}$\\
-    $\bb{i}$ & 2D bounding box of the car in image\\
-    \hline
-  \end{tabular}
-\end{table}
-
-%%%%%%%%% BODY TEXT
-\section{The Model}
-
-The objective is to find the most likely traffic participant (TP) state given
-various evidences $\mathbb{E} = \{\{\trackp{t}\}, \{\bb{i}\}, \text{lane det.},
-\text{map}, \text{GPS}\}$.
-
-Mathematically, find:
-\begin{align}
-  \{\state{i}{t}\}^* &= \arg \max P(\{\state{i}{t}\} | \mathbb{E})
-\end{align}
-
-Bayes rule
-\begin{align}
-  P(\{\state{i}{t}\} | \mathbb{E}) &=
-  \frac{1}{Z}P( \mathbb{E} | \{\state{i}{t}\})P(\{\state{i}{t}\})
-\end{align}
-
-Assume conditional independence according to graphical model in
-\ref{fig:graphmodel}.
-
-\begin{multline}
-  P(\{\state{i}{t}\} | \mathbb{E}) =
-  \frac{1}{Z}
-  \prod_{t=s_i}^{e_i}\prod_{i,j: i \ne j}(P(\state{i}{t}, \state{j}{t}))\\
-%
-  \prod_{i=1}^{N}
-  \prod_{t=s_i}^{e_i}
-  P(\bb{i} | \state{i}{t})
-  P(\trackp{t} | \state{i}{t})\\
-  P(\state{i}{t} | L_m(t))
-  P(\state{i}{t} | \state{i}{t-1})
-  P(\state{i}{t})
-\end{multline}
-
-We can formulate similar objective function in negative log domain:
-\footnote{TODO:Resolve inconsistency in summation absorption in energy terms.}
-\begin{multline}
-  -\log{P(\{\state{i}{t}\} | \mathbb{E})} = 
-  Z' + \sum_{i,j:i\ne j} \sum_{t=s_i}^{e_i}  \WEnergyCol \\
-  + \sum_{i=1}^N \sum_{t=s_i}^{e_i}
-    \WEnergy{box}
-  + \WEnergy{track}\\
-  + \WEnergy{lane}
-  + \WEnergy{dyn}
-  + \WEnergy{prior}
-\end{multline}
-
-\section{Modeling traffic participants}
-\label{sec:TPmodel}
-Following standard model of occupancy in 3D reconstruction community, we model
-the TP's as high occupancy regions in space. We model the
-uncertainty in occupancy equivalent of transparency i.e. the regions that are
-more certain to be occupied are viewed as relatively more opaque then other
-regions. Based on this intuition we model TP's translucent
-ellipsoids whose opacity is maximum at the center and drops off away from the
-center. More specifically we model, the occupancy of a TP as a
-logistic function,
-
-\begin{align}
-   \occf = L(\mathbf{x}; \pos{i}{t}, \Sigma_i)
-\end{align}
-where $L(.)$ is the logistic function defined by
-\begin{align}
-  L(\mathbf{x}; \pos{i}{t}, \Sigma_i) = \frac{1}{
-    1 + e^{-k(1 - d(\mathbf{x},\pos{i}{t}))}
-    }
-\end{align}
-where $d(\mathbf{x},\pos{i}{t}) =
-(\mathbf{x}-\pos{i}{t})^\top\Sigma_i(\mathbf{x}-\pos{i}{t})$ and $k =
-10\ln{49}$. $k$ is chosen such that $L(.) = 0.98$ when $d(.) =
-0.9$. $\Sigma_i$ determines the spread of the ellipsoid and depends on the
-dimensions of the TP. Please refer to supplementary material 
-for computation of $\Sigma_i$ from TP's dimensions.
-
-We model the probability of a point $\mathbf{x}_j$ on a object $i$ getting successfully
-observed in a camera image at point $\trackpj{t}$ is dependent up two factors,
-(1) reflection and (2) transmission through intermediate space. The reflection
-part ensures that there is an object to reflect a point at a certain region in
-the 3D space while transmission part models occlusion.
-\begin{align}
-  P^{(ij)}_{\text{observation}} = P^{(ij)}_{\text{reflection}}P^{(j)}_{\text{transmission}}
-\end{align}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Reflection probability}
-For Lambertian reflection we replace the surface normal with the
-gradient of occupancy.
-%
-\begin{align}
-  \Prefl = (\max \{0, \nabla \occf^\top
-  \hat{\mathbf{r}_j}\})^2
-\end{align}
-%
-where $\ray =
-\frac{K^{-1}\trackpj{t}}{\|K^{-1}\trackpj{t}\|}$ is unit vector in the
-direction of ray. The gradient in the direction opposite to ray yields -ve
-probability which needs to be clipped off. Squaring the function keep it
-smooth near zero.
-
+\section{Continuous Energies for Object Localization}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Transmission probability}
-A model for transmission of light through a material of thickness $x$,
-density $\rho$ and opacity $k_o$ is given by Beer-Lambert law 
-%
-\begin{align}
-  I(x) = I_0e^{-k_o\rho x}
-\end{align}
-%
-
-Since both opacity and density are represented by the occupancy function
-$\occftot = \sum_i \occf$, and also the domain of our $\occftot$ is $[0, 1]$ instead of $[0,
-\infty]$ as in case of $k_o$; we replace $e^{-k_o\rho}$ by the transparency
-function $1 - \occftot$. So the transmission probability over a small distance
-$d\lambda$ is given by
-%
-\begin{align}
-  P_{\text{transmission}}(\lambda + d\lambda) =
-  P_{\text{transmission}}(\lambda) (1-\occftot)^{d\lambda}
-\end{align}
-%
-
-For a given 3D point $\mathbf{x}_j = \lambda \ray$, the probability that the
-point $\trackpj{t}$ is reflected from a distance $\lambda$ is given by
-
-\begin{align}
-  %P^{(j)}_{\text{observation}}(\lambda) &= P_{\text{reflection}}
-  \Ptrans &=
-  \prod_{0}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda} %\\
-  %= \max \{ 0, (\nabla f_{occ}&(\lambda \ray)^\top \ray) \}
-  %\prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
-  \label{eq:ptrans-integral}
-\end{align}
-where $\prod_{0}^{\lambda}$ represents the \emph{product integral} from $0$ to
-$\lambda$.
-
-In practice, the integral for transmission probability
-\eqref{eq:ptrans-integral} is difficult to compute even numerically. So we
-choose a product of sigmoid function that approximates the behaviour of
-transmission probability,
-%
-\begin{align}
-\label{eq:evalCumulativePtrans}
-  \Ptrans &= \prod_i L_u(\trackp{t}; \muiu,\Sigmaiu)L_{\lambda}(\lambda; \mu^i_d)
-\end{align}
-%
-where $L_u(.)$ is sigmoid in image domain with $\mu^i_u$ and $\Sigma^i_u$
-representing the elliptical projection of $i^{th}$ TP.
-$L_{\lambda}(.)$ is sigmoid in the depth domain with $\mu^i_d$ as the mean
-depth of the $i^{th}$ TP.
-%
-\begin{align}
-  L_u(\mathbf{u}; \muiu,\Sigmaiu) &= \frac{1}{
-    1 + e^{-k_u(1 - (\mathbf{u} - \muiu)^\top\Sigmaiu(\mathbf{u} -
-    \muiu))}
-  }
-  \\
-  L_{\lambda}(\lambda; \mu^i_d) &= \frac{1}{
-    1 + e^{-k_d(\lambda - \mu^i_d)}
-}
-\end{align}
-%
-
-\begin{comment}%% Comment
-  A product integral is a simple integral in log domain
-  \begin{align}
-    \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} =
-    e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
-  \end{align}
-\end{comment}%% Comment
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Energies}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We explain energies in this section
+We explain energies in this section.
 
@@
 $\Sigma_{\expDimsn}$ is the correspondence covariance matrix.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Association error evaluation}
-
-To verify the correctness of our association probability $\assocP$ we perform
-association error experiment that compare the accuracy of point track
-association with TPs with that of bounding box baseline method.
-
-% \begin{align}
-%   f^{i}_{reproj}&(\trackpj{t-1}, \lambda) =
-%   \projectionOf{\invProjectionOf{\trackpj{t-1}}}\\
-%   %&= K(R^i_t ((R^i_{t-1})^\top\lambda \ray - (R^i_{t-1})^\top T_{t-1}) + T_{t})\\
-%   &= \frac
-%   {p_{1:2}\lambda + q_{1:2}}
-%   {p_{3}\lambda + q_{3}}
-% \end{align}
-% where $p_{1:3} = KR^i_t(R^i_{t-1})^\top\ray$ and
-% $q_{1:3} = KR^i_t(R^i_{t-1})^\top T_{t-1} + KT_t$
-% 
-% Now that we have an association from TP $i$ to point track $j$ through
-% $\lambda$, we can come up with an association probability
-% \begin{align}
-%    \assocP &= \frac{(\max \{ 0, \nabla \occf^\top
-% \ray \})^2 }{P_{\text{reflection}}}\lambdadist\\
-% &=(\max \{ 0, \nabla \occf^\top \ray \})^2
-%   \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
-% \end{align}
-
-Note that the fraction $\assocP$ although called association probability does
-not capture the entire information that we have available for compute
-association of points to tracks. This above fraction is the association
-probability given the hypothesized parameters of TP model.
-
-To compute the association probability between TP $i$ and
-point track $j$ we must use re-projection error as well. When the association
-$i$ and $j$ is right and the point of reflection is at depth $\lambda$ the
-re-projection error must be zero \eqref{eq:reprojerror}, otherwise the error
-becomes a measure of distance from the true solution.
-The error terms can be converted to probability domain by considering the error
-term as negative log of probability
-
-\begin{align}
-  P^{(ij)}_{\text{assoc by reproj}}(\lambda) = \frac{1}{Z}\exp(-\Ereproj(\lambda))
-\end{align}
-
-Using both the evidence terms we can write probability of association as
-\begin{align}
-  P^{(ij)}_{\text{assoc}} = \frac{1}{Z'}\int_0^{\infty} \assocP \frac{1}{\sqrt{2\pi}}\exp(-\Ereproj(\lambda))d\lambda
-  \label{eq:prob-assoc}
-\end{align}
-
-Once we have the probability of association we can compute the best possible
-assignment of TP for each point. The points having very small association
-probability are assigned to the background,
-\begin{align}
-  i^*_{j} = \argmin_{i} \int_0^\infty \assocP \Ereproj(\lambda) d\lambda
-\end{align}
-
-We use bounding box based assignment of point tracks to TPs as the baseline.
-For the regions where the bounding boxes overlap, we assign the points to the
-TP that has smaller mean depth then the competing bounding box.
-
-{\small
-\bibliographystyle{ieee}
-\bibliography{model}
-}
-\end{document}

### 2014-11-10 CVPR/Source/occlusion.tex
Reorganized paper tex files

--- 2014-11-08 Paper/model.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
-
-\usepackage{cvpr}
-\usepackage{times}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-%%%%%%%%%%% CVPR template packages end %%%%%%%%%%%%%%
-\usepackage{verbatim} % for comment environment
-% \usepackage{soul} % for \hl highlighting
-% Include other packages here, before hyperref.
-
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-
-%\cvprfinalcopy % *** Uncomment this line for the final submission
-
-\def\cvprPaperID{489} % *** Enter the CVPR Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-% 3D pose of the cars and ego motion
-\newcommand{\pos}[2]{\mathbf{p}^{(#1)}(#2)}
-\newcommand{\ori}[2]{\mathbf{\omega}^{(#1)}(#2)}
-\newcommand{\state}[2]{\mathbf{s}^{#1}(#2)}
-
-% ego pose
-\newcommand{\egop}[1][t]{\pos{c}{#1}}
-\newcommand{\egoo}[1][t]{\ori{c}{#1}}
-\newcommand{\egos}[1][t]{\state{c}{#1}}
-
-% relative pose between camera and car $i$
-\newcommand{\relp}[2]{\Omega^{#1}(#2)}
-\newcommand{\relpz}[2]{\Omega_z^{#1}(#2)}
-
-% 3D tracks on car $i$ in its own coordinate frame
-\newcommand{\tracklets}{\mathbf{X}^{(i)}_o}
-\newcommand{\tracklet}[1]{\mathbf{x}^{(i)}_{#1}}
-% track projections on camera
-\newcommand{\trackp}[1]{\mathbf{u}^{(i)}(#1)}
-\newcommand{\trackpj}[1]{\mathbf{u}_j(#1)}
-% Unclassified track point projected on camera
-\newcommand{\ucTrackp}{\mathbf{u}(t)}
-
-% dimensions of car $i$
-\newcommand{\dimsn}[1]{\mathbf{B}^{#1}}
-\newcommand{\expDimsn}{\hat{\mathbf{B}}}
-
-% projection function
-\newcommand{\projectionOf}[1]{\pi_{\relp{i}{t}}\left(#1\right)}
-\newcommand{\projectionOft}[1]{\pi_{\relp{i}{t+1}}\left(#1\right)}
-\newcommand{\centerProj}{\bar{\pi}_{\relp{i}{t}}(\dimsn{i})}
-\newcommand{\cornerProj}[1]{\pi^{#1}_{\relp{i}{t}}(\dimsn{i})}
-\newcommand{\triangleProj}[1]{\triangle^{#1}_{\relp{i}{t}}(\dimsn{i})}
-
-% bounding box corners on image
-\newcommand{\bb}[1]{\mathbf{d}^{#1}(t)}
-
-\newcommand{\Energy}[1]{\mathcal{E}^{it}_{\text{#1}}}
-\newcommand{\pEnergy}[1]{\mathcal{E}^{ijt}_{\text{#1}}}
-% Weighted energy
-\newcommand{\WEnergy}[1]{\lambda_{\text{#1}}\Energy{#1}}
-\newcommand{\EnergyCol}{\mathcal{E}^{ijt}_{\text{col}}}
-\newcommand{\WEnergyCol}{\lambda_{\text{col}}\EnergyCol}
-
-\newcommand{\occFreeProj}[1]{\Pi_{\relp{i}{t}}(#1)}
-\newcommand{\minx}{x_{\text{min}}}
-\newcommand{\miny}{y_{\text{min}}}
-\newcommand{\maxx}{x_{\text{max}}}
-\newcommand{\maxy}{y_{\text{max}}}
-\newcommand{\frontface}{F^i_\text{FF}(t)}
-
-\newcommand{\occ}[1]{o({#1})}
-\newcommand{\face}{F^i_k(t)}
-
-\newcommand{\invProjectionOf}[1]{\pi^{-1}_{\relp{i}{t}}\left(#1\right)}
-\newcommand{\occf}{f^i_{occ}(\mathbf{x}_j)}
-\newcommand{\occftot}{f_{occ}(\mathbf{x}_j)}
-\newcommand{\occft}[1]{f_{occ}(#1)}
-
-\newcommand{\ray}{\hat{\mathbf{r}}_j}
-\newcommand{\occfray}{f_{occ}(\lambda\ray)}
-\newcommand{\lambdadist}{f_{\lambda}(\trackpj{t-1}, \lambda)}
-
-\newcommand{\occfxi}{L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i)}
-\newcommand{\occfi}{L(\lambda \ray; \pos{i}{t-1}, \Sigma_i)}
-\newcommand{\assocP}{a^{(ij)}(\lambda)}
-\newcommand{\assocPk}{a^{(ij)}(\lambda_k)}
-
-\newcommand{\Ereproj}{E^{(ij)}_{\text{reproj}}}
-\newcommand{\Ptrans}{P^{(j)}_{\text{transmission}}(\lambda)}
-\newcommand{\Ptransmud}{P^{(j)}_{\text{transmission}}(\mu^{(i)}_d)}
-\newcommand{\Prefl}{P^{(ij)}_{\text{reflection}}(\lambda)}
-\newcommand{\dishort}{d_i(\mathbf{x})}
-
-\newcommand{\Lu}{L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)}
-\newcommand{\Llambda}{L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d)}
-
-\newcommand{\Gauss}{\mathcal{N}}
-\newcommand{\PropDist}{\mathcal{W}_j}
-
-\newcommand{\muijl}{\mu^{(ij)}_{\lambda}}
-\newcommand{\sigmaijl}{\sigma^{ij}_{\lambda}}
-
-\newcommand{\Sigmait}{\Sigma^{(i)^{-1}}_t}
-
-\newcommand{\muit}{\mu^(i)_t}
-\newcommand{\Sigmaic}{\Sigma'^{(i)^{-1}}_c}
-
-\newcommand{\muic}{{\mu^(i)_c}}
-\newcommand{\Sigmaicf}{\Sigma^{(i)^{-1}}_c}
-
-\newcommand{\muiu}{\mu^{(i)}_t}
-\newcommand{\Sigmaiu}{\Sigma^{(i)^{-1}}_u}
-
-\newcommand{\xt}{\mathbf{x}_t}
-\newcommand{\xc}{\mathbf{x}_c}
-
-\newcommand{\Rctot}{R}
-\newcommand{\tctot}{t}
-
-\newcommand{\tcmut}{t'}
-
-\newcommand{\Beizer}{B\'eizer }
-
-\newcommand{\LaneUncertainty}[1]{\Sigma_{L_m}(#1)}
-\newcommand{\projOnLane}[1]{\pi_{L_m(k)}(#1)}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-%\ifcvprfinal\pagestyle{empty}\fi
-%\setcounter{page}{4321}
-%\DeclareMathSymbol{\Tangent}
-\DeclareMathOperator{\sech}{sech}
-\DeclareMathOperator{\poly}{poly}
-\DeclareMathOperator*{\argmin}{\arg\min}
-
-\begin{document}
-\title{Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.}
-\author{Vikas Dhiman\\
-  University of Michigan\\
-  Ann Arbor, MI, USA\\
-{\tt\small dhiman@umich.edu}
-\and
-Manmohan Chandraker\\
-NEC Laboratories America, Inc.\\
-Cupertino, CA, USA\\
-{\tt\small manu@nec-labs.com}
-\and
-Jason J Corso\\
-  University of Michigan\\
-  Ann Arbor, MI, USA\\
-{\tt\small jjcorso@eecs.umich.edu}
-}
-\maketitle
-
-%%%%%%%%% ABSTRACT
-\begin{abstract}
-  TODO: Write abstract
-  \vspace{4cm}
-\end{abstract}
-
-\section{Introduction}
-
-\begin{itemize}
-  \item Introduce the problem
-  \item Describe our approach
-  \item Contrast with Milan's work
-  \item Contrast with Andreas Geiger's work
-  \item Highlight the contributions
-\end{itemize}
-\vspace{10cm}
-\begin{figure}[t]
-  \includegraphics[width=\columnwidth]{graphics/graphicalModelFrom61ConstVars.pdf}
-  \caption{Graphical model. The six numbered black circles represent the
-    unknown state variables of each car. All other nodes in the graphical model
-    are assumed
-    observed variables. Consider each energy in the model one by one. (1)
-    Bounding box energy: The bounding box energy without occlusion modeling is
-    a unary term, but with occlusion it becomes a higher order term that
-    affects the state of occluder as well. In this graphical model we assume
-    that the scene is being observed from left to right, hence "2" occludes "6"
-    and "5" and "5" occludes "1". The bounding box detection is represented by
-  $\mathbf{d}_{bb}^i(t)$ and the statistical dependencies are represented by
-  red lines. (2) Point tracks ($\Energy{track}$): Since occlusion is also
-  included in modeling point tracks energy we have similar interdependencies
-  for point tracks energy. The available point tracks are modeled by
-  $\mathbf{u}(t)$. (3) Collision ($\Energy{coll}$) : The collision energy
-  mathematically is a dense graph between all the TP but here we represent
-  collision among only those TP that are near enough to have a significant
-collision energy. (4) Orientation from detection ($\Energy{ori}$) (5) Orientation from lane (and map) information ($\Energy{lane}$)}
-  \label{fig:graphmodel}
-\end{figure}
-
-\section{Related Work}
-TODO:
-\vfill
-\pagebreak
-Related work continued
-\vspace{15cm}
-
-\section{Problem Definition}
-TODO:
-\vspace{4cm}
-
-\section{Notation}
-
-\begin{table}[h]
-  \begin{tabular}{|l|l|}
-    \hline
-    Symbol & Meaning \\
-    \hline
-    $\pos{i}{t}$ & Position of $i$th car at time $t$\\
-    $\ori{i}{t}$ & Orientation of $i$th car at time $t$\\
-     $\dimsn{i}$ & 3D bounding box of the car (dimensions)\\
-    $\state{i}{t}$ & State of car $=\{\pos{i}{t}, \ori{i}{t}, \dimsn{i}\}$\\
-    $\egop$ & Position of camera at time $t$\\
-    $\egoo$ & Orientation of camera at time $t$\\
-    $\relp{i}{t}$ & Relative car pose w.r.t. camera \\
-    $\tracklets$ & 3D points tracked on car $i$ in its own frame\\
-    $\trackp{t}$ & Projection of $\tracklets$ in camera\\
-    $\projectionOf{.}$ & Projection function for pose $\relp{i}{t}$\\
-    $\bb{i}$ & 2D bounding box of the car in image\\
-    \hline
-  \end{tabular}
-\end{table}
-
-%%%%%%%%% BODY TEXT
-\section{The Model}
-
-The objective is to find the most likely traffic participant (TP) state given
-various evidences $\mathbb{E} = \{\{\trackp{t}\}, \{\bb{i}\}, \text{lane det.},
-\text{map}, \text{GPS}\}$.
-
-Mathematically, find:
-\begin{align}
-  \{\state{i}{t}\}^* &= \arg \max P(\{\state{i}{t}\} | \mathbb{E})
-\end{align}
-
-Bayes rule
-\begin{align}
-  P(\{\state{i}{t}\} | \mathbb{E}) &=
-  \frac{1}{Z}P( \mathbb{E} | \{\state{i}{t}\})P(\{\state{i}{t}\})
-\end{align}
-
-Assume conditional independence according to graphical model in
-\ref{fig:graphmodel}.
-
-\begin{multline}
-  P(\{\state{i}{t}\} | \mathbb{E}) =
-  \frac{1}{Z}
-  \prod_{t=s_i}^{e_i}\prod_{i,j: i \ne j}(P(\state{i}{t}, \state{j}{t}))\\
-%
-  \prod_{i=1}^{N}
-  \prod_{t=s_i}^{e_i}
-  P(\bb{i} | \state{i}{t})
-  P(\trackp{t} | \state{i}{t})\\
-  P(\state{i}{t} | L_m(t))
-  P(\state{i}{t} | \state{i}{t-1})
-  P(\state{i}{t})
-\end{multline}
-
-We can formulate similar objective function in negative log domain:
-\footnote{TODO:Resolve inconsistency in summation absorption in energy terms.}
-\begin{multline}
-  -\log{P(\{\state{i}{t}\} | \mathbb{E})} = 
-  Z' + \sum_{i,j:i\ne j} \sum_{t=s_i}^{e_i}  \WEnergyCol \\
-  + \sum_{i=1}^N \sum_{t=s_i}^{e_i}
-    \WEnergy{box}
-  + \WEnergy{track}\\
-  + \WEnergy{lane}
-  + \WEnergy{dyn}
-  + \WEnergy{prior}
-\end{multline}
-
 \section{Modeling traffic participants}
@@
 \end{comment}%% Comment
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Energies}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We explain energies in this section
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Point tracks energy with occlusion}
-\label{sec:totalContPtTracksEnergy}
-We model continuous point tracks energy with explicit occlusion reasoning as
-the expected re-projection error over the association probability,
-
-\begin{multline}
-  \Energy{traci}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \\
-    \sum_{i=1}^{N} 
-    %\sum_{t = s_i}^{e_i}
-    \sum_{j = 1}^{M}
-    \int_1^\infty \assocP\Ereproj(\lambda) d\lambda
-\end{multline}
-where $\assocP$ is the association probability of
-$j$\textsuperscript{th} point with $i$\textsuperscript{th} TP at depth $\lambda$
-and $\Ereproj(\lambda)$ is the re-projection error given by
-%
-\begin{align}
-  \assocP &= \Prefl\Ptrans\\
-  \Ereproj(\lambda) &= \left\|\trackpj{t+1} - \projectionOft{\invProjectionOf{\trackpj{t}, \lambda}}\right\|^2 .
-  \label{eq:reprojerror}
-\end{align}
-
-The  $\projectionOf{.}$ and $\invProjectionOf{.}$ denote the projection and
-inverse projection functions that project 3D point to camera image and vice
-versa. Note that inverse projection $\invProjectionOf{.}$ depend on both the
-point $\trackp{t}$ and the unknown depth $\lambda$. Also note that the inverse projection is dependent on TP pose at time $t$ while the projection depends on pose at time $t+1$ which can be different.
-
-\begin{comment}
-  \subsubsection{Occupancy function}
-  Assuming occupancy to be a
-  probability distribution over 3D space. For each TP the
-  occupancy is modeled as a logistic function 
-  \begin{align}
-     \occf = L(\mathbf{x}; \pos{i}{t}, \Sigma_i)
-  \end{align}
-  where $L(.)$ is the logistic function defined by
-  \begin{align}
-    L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i) = \frac{1}{
-      1 + e^{-k(1 - d(\mathbf{x},\pos{i}{t-1}))}
-      }
-  \end{align}
-  where $d(\mathbf{x},\pos{i}{t-1}) =
-  (\mathbf{x}-\pos{i}{t-1})^\top\Sigma_i(\mathbf{x}-\pos{i}{t-1})$ and $k =
-  10\ln{49}$. $k$ is chosen such that $L(.) = 0.98$ when $d(.) =
-  0.9$
-  % Once we have our distribution over $\lambda$, $\lambdadist$ we can compute the
-  % reprojection of $\trackpj{t-1}$ over image in time $t$ as a function of
-  % $\lambda$. Let
-\end{comment}
-
-\begin{comment}
-  \subsubsection{Approximations}
-  Reflection probability of $i$th TP is easy to compute
-  analytically 
-  \begin{multline}
-    \Prefl =
-    (\max \{ 0, \nabla \occf^\top \ray \})^2 \\
-    = (\max \{ 0, \nabla \occfxi^\top\ray \})^2
-    \label{eq:analytic-prefl}
-  \end{multline}
-  where 
-  \begin{multline}
-    \nabla \occfxi^\top\ray \\=
-    \nabla k\dishort \sech^2\left(\frac{k}{2}\dishort\right)
-  \end{multline}
-  where $\dishort = 1-d(\mathbf{x}, \pos{i}{t-1})$ is a signed distance measure
-  from the contour of the ellipsoid where $d(\mathbf{x}, \pos{i}{t-1})$ is 1.
-
-  However, the transmission probability needs to be approximated.  
-  %
-  % \subsubsection{Computing $\Prefl$ and $\Ptrans$}
-  % Focusing on  $\nabla \occfxi$ 
-  % 
-  % \begin{multline}
-  %   \nabla \occfxi =\\
-  %   \frac{-k\nabla d(\mathbf{x}, \pos{i}{t-1})e^{-k(1-d(\mathbf{x}, \pos{i}{t-1}))}}{
-  %     (1 + e^{-k(1-d(\mathbf{x}, \pos{i}{t-1}))})^2
-  %   } \\ 
-  %   = -k\nabla d(\mathbf{x}, \pos{i}{t-1})\sech^2\left(\frac{k}{2}(1-d(\mathbf{x},
-  %   \pos{i}{t-1}))\right)
-  %   \\
-  %   = \nabla k\dishort \sech^2\left(\frac{k}{2}\dishort\right)
-  % \end{multline}
-  % where $\dishort = 1-d(\mathbf{x}, \pos{i}{t-1})$ is a signed distance measure
-  % from the contour of the ellipsoid where $d(\mathbf{x}, \pos{i}{t-1})$ is 1.
-  % Focusing on $\nabla d(.)$
-  % 
-  % \begin{align}
-  %   \nabla d(\mathbf{x}, \pos{i}{t-1}) = 2\Sigma_i(\mathbf{x} - \pos{i}{t-1})
-  % \end{align}
-  % Back to \eqref{eq:analytic-prefl}
-  % 
-  % \begin{multline}
-  %   (\max \{ 0, \nabla \occf^\top \ray \})^2 = \\
-  %   \sech^4\left(\frac{k}{2}\dishort\right) 
-  %   (\max \{ 0 , \nabla k\dishort^\top\ray\})^2
-  % \end{multline}
-  % 
-  % The probability is simply $\sech^2(.)$ scaled by gradient of ellipsoid
-  % $\nabla k\dishort$ projected in the ray direction $\ray$.
-  % 
-  % \begin{align}
-  %   \Ptrans = 
-  %   e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
-  % \end{align}
-  % \begin{multline}
-  % \int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}
-  % =  \\
-  % \int_{1}^{\lambda} \ln{\left(1 - \sum_i \occfi\right)}{d\lambda}
-  % \end{multline}
-  % 
-  % The above integral is very difficult to approximate or compute analytically.
-  So based on intuition, we approximate the $\Ptrans$ by following function
-  \begin{align}
-  \label{eq:evalCumulativePtrans}
-    \Ptrans &= \prod_i L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)L_{\lambda}(\lambda; \mu^i_d)\\
-    L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u) &= \frac{1}{
-      1 + e^{-k_u(1 - (\mathbf{u} - \mu^i_u)^\top\Sigma^i_u(\mathbf{u} -
-      \mu^i_u))}
-    }
-    \\
-    L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d) &= \frac{1}{
-    1 + e^{-k_d(\lambda - \mu^i_d(\mathbf{u}))}
-  }
-  \end{align}
-  where 
-  \begin{align}
-    \mu_u^i &= \projectionOf{\pos{i}{t-1}} \label{eq:muiudef}\\
-    \Sigma_u^i &= \projectionOf{\Sigma_i} \label{eq:sigmauidef}\\
-    \mu^i_d(\mathbf{u}) &= \relp{i}{t}\\
-    k_u &= 10\log(49)\\
-    k_d &= \frac{\log(49)}{\sqrt{h^2 + l^2 + w^2}}
-    \label{eq:ptransmissionInit}
-  \end{align}
-  is the distance of the centre of the TP from the camera.
-
-  % $\mu^i_d(\mathbf{u}) = \min_{\lambda} d^2_i(\lambda K^{-1}\mathbf{u})$.
-  % $\mu^i_d(\mathbf{u})$ is the closest point to the unit contour of ellipsoid.
-  % If there are multiple such points, the point closest to the camera is taken as
-  % $\mu^i_d(\mathbf{u})$
-
-  The association probability becomes
-
-  \begin{multline}
-    \assocP = 
-      \sech^4\left(\frac{k}{2}\dishort\right)
-      (\max \{ 0, \nabla k\dishort^\top\ray \})^2\\
-    \prod_i \Lu
-      \Llambda \\
-      \label{eq:assocCoeffEval}
-  \end{multline}
-
-  So the energy becomes
-
-  \begin{multline}
-    \label{eq:integrand}
-    \Energy{track}(.) = 
-      \sum_{i = 1}^N
-      \sum_{j = 1}^{M}
-      \int_1^{\infty}
-      \assocP
-      \Ereproj(\lambda)
-      d\lambda
-  \end{multline}
-  where $x = \lambda \ray$ and $\Ereproj(\lambda) = \|\trackpj{t} -
-  f^i_{reproj}(\trackpj{t-1}, \lambda)\|^2$ is reprojection error which is a
-  quadratic in $\lambda$
-
-  The integral in the above expression is computed numerically.
-\end{comment}
-
-\subsection{Object detection energy with occlusion}
-
-Object detection is usually followed by non-maximal suppression that results in
-discarding similar bounding boxes. When we are jointly optimizing detections
-with other cues, it is not usually desirable to go with a single bounding box.
-Hence, we keep all the bounding box detections by approximating them with
-multi-modal sum of Gaussian like logistic functions. We fit the parametric function of the form 
-%
-\begin{align}
-  S(\bb{i}) = \sum_k A_k \exp(-(\bb{i}-\mu^{(d)}_k)^\top \Sigma^{(d)-1}_k
-  (\bb{i}-\mu^{(d)}_k))
-\end{align}
-%
-to detection scores, by non-linear error minimization with initialization from
-non-maximal suppressed outputs. Here $\mu^{(d)}_j$ is one of the $k$ modes as a
-4D vector representing a single bounding box as $[\minx, \miny, \maxx,
-\maxy]^\top$. The optimization is constrained with symmetry and positive
-definiteness of $\Sigma^{(d)-1}_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
-
-\subsubsection{Detection scores with occlusion reasoning} 
-With our model of $\Ptrans$ described in Section \ref{sec:TPmodel}, we can
-compute the probability of a point $\mathbf{u}$ on image be occluded assuming
-the point is on TP $i$ with mean depth $\mu^{(i)}_d$ as
-\begin{align}
-  O_{i}(\mathbf{u}, \mu^{(i)}_d) = 1 - \Ptransmud \enspace .
-\end{align}
-
-If we a portion of our proposed detection bounding box is known to be occluded,
-then we would like to decrease the confidence in the detection score about the
-localization of that end of the object. Assuming that the occlusion is often on
-the boundary of detection bounding boxes, we want to decrease our confidence on
-the mean detection boundaries around the occluded boundaries. 
-One of the simplest ways will be to scale the appropriate diagonal element of
-$\Sigma_j$ by an appropriate scaling factor proportional to occlusion. But this
-does not model appropriate how does occlusion affects the non diagonal terms.
-Hence, we choose a covariance addition model where we compute a occlusion
-covariance matrix, that provides a measure of occlusion in each direction.
-
-To re-model our detection scores scaled by continuous occlusion we sample
-$O_{i}(\mathbf{u}, \mu^{(i)}_d)$ at the hypothesized detection boundaries from
-GMM $S(.)$ and we augment the detection boundary covariance matrix by
-$\mathcal{P}_{j} = \rho_{j}\rho_{j}^\top$ where $\rho_{j} = O_{j}(\mathbf{u},
-\mu^{(i)}_d)$. The new covariance matrix in detection score is given by 
-%
-\begin{align}
-  \Sigma'^{(d)}_j = \mathcal{P}_{j} + \Sigma^{(d)}_j
-\end{align}
-%
-The detection scores GMM with occlusion is given by replacing the covariance
-matrix
-%
-\begin{multline}
-  S'(\bb{i}) =\\
-  \sum_j A_j \exp(-(\bb{i}-\mu^{(d)}_j)^\top \Sigma'^{(d)-1}_j
-  (\bb{i}-\mu^{(d)}_j))
-\end{multline}
-
-The energy of detection scores is simply take to be the inverse of the detection score.
-\begin{align}
-  \Energy{detect}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}
-\end{align}
-
-\subsection{Lane energy}
-\label{sec:laneEnergy}
- The lanes are modeled as splines. Here we assume that the confidence in lane
- detection is decreases as the distance from the lane center increases.  The
- energy is given by the dot product between car orientation and tangent to the
- lane at that point.
-
-\begin{multline}
-  \label{eq:laneOrientationEnergy}
-  \Energy{lane} = \\
-  \sum_{m \in M_{\text{close}}}
-  (1 - \ori{i}{t} \cdot \text{TAN}(L_{m}(k), \pos{i}{t}) )
-\LaneUncertainty{\pos{i}{t}}
-\end{multline}
-where $M_{\text{close}} = \{m : \text{DIST}(L_{m}(k), \pos{i}{t}) < 50\} $ is
-the set of nearby lanes and 
-\begin{multline}
-\LaneUncertainty{\pos{i}{t}} = \\
-  \frac{1}{1 + exp(-q(w_{\text{road}} - \text{DIST}(L_{m}(k), \pos{i}{t})))}
-\end{multline}
-for some constant $w_{\text{road}}$ that represents the width of the road.
-
-\subsection{Transition probability}
-Dynamics constraints should not only enforce smooth trajectories, but also the
-holonomic constraints.  The following energy adds a penalty if the change in
-position is not in direction of previous orientation.
-
-\begin{align}
-  \label{eq:totalPosTransitionEnergy}
-  \Energy{dyn-hol} = 1 - \ori{i}{t-1} \cdot (\pos{i}{t} - \pos{i}{t-1})
-\end{align}
-
-The following energy adds a penalty for change in position and orientation
-but a penalty for change in velocity is much better approximation. However, in
-a Markovian setting that would mean extending the state space of the car to
-include velocity.
-
-\begin{align}
-  \Energy{dyn-ori} &= \|\ori{i}{t} - \ori{i}{t-1}\|^2\\
-  \Energy{dyn-vel} &= \|(\pos{i}{t} - 2\pos{i}{t-1}) + \pos{i}{t-2}\|^2
-\end{align}
-
-As a result the dynamics are modeled by weighted combination of holonomic
-constraint and smoothness constraints.
-
-\begin{align}
-  \WEnergy{dyn} &= \WEnergy{dyn-hol} + \WEnergy{dyn-ori} + \WEnergy{dyn-vel}
-\end{align}
-
-\subsection{Collision energy}
-
-Bhattacharya coefficient $\int_a^b\sqrt{p(x)q(x)}dx$ is a measure of similarity
-of two distributions $p(x)$ and $q(x)$. If we represent TPs as gaussians in
-Birds eye view (BEV), then similarity is a measure of collision. Exactly
-overlapping distribution results in coefficient as 1. 
-%The analytical form of
-%Bhattacharya coefficient has been taken from
-%\url{http://like.silk.to/studymemo/PropertiesOfMultivariateGaussianFunction.pdf}
-
-\begin{multline}
-  \label{eq:collisionEnergyHellingerDistance}
-  \EnergyCol =\\ -\log\left(
-  A_{ij}
-  e^{-\frac{1}{8}
-    \left(\pos{i}{t} - \pos{j}{t}\right)^\top
-    P^{-1}
-    \left(\pos{i}{t} - \pos{j}{t}\right)
-    }
-    \right)
-\end{multline}
-where 
-\begin{align}
-  A_{ij} &= \frac{|\Sigma_i|^\frac{1}{4}|\Sigma_j|^\frac{1}{4}}
-  {|P|^\frac{1}{2}}\\
-  P &= \frac{1}{2}\Sigma_i + \frac{1}{2}\Sigma_j\\
-\Sigma_i^{-1} &= R^\top_{\ori{i}{t}} \begin{bmatrix} 2/l_i & 0 \\ 0 & 2/w_i \end{bmatrix}
-R_{\ori{i}{t}}
-\end{align}
-
-\subsection{Size Prior}
-
-Prior can include among many other things the size prior on the car.
-
-\begin{align}
-  \label{eq:totalSizeEnergy}
-  \Energy{prior} &= (\dimsn{i} - \expDimsn)^\top\Sigma_{\expDimsn}^{-1}(\dimsn{i} -
-  \expDimsn)
-\end{align}
-
-where $\expDimsn$ is the mean TP dimensions and
-$\Sigma_{\expDimsn}$ is the correspondence covariance matrix.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Association error evaluation}
-
-To verify the correctness of our association probability $\assocP$ we perform
-association error experiment that compare the accuracy of point track
-association with TPs with that of bounding box baseline method.
-
-% \begin{align}
-%   f^{i}_{reproj}&(\trackpj{t-1}, \lambda) =
-%   \projectionOf{\invProjectionOf{\trackpj{t-1}}}\\
-%   %&= K(R^i_t ((R^i_{t-1})^\top\lambda \ray - (R^i_{t-1})^\top T_{t-1}) + T_{t})\\
-%   &= \frac
-%   {p_{1:2}\lambda + q_{1:2}}
-%   {p_{3}\lambda + q_{3}}
-% \end{align}
-% where $p_{1:3} = KR^i_t(R^i_{t-1})^\top\ray$ and
-% $q_{1:3} = KR^i_t(R^i_{t-1})^\top T_{t-1} + KT_t$
-% 
-% Now that we have an association from TP $i$ to point track $j$ through
-% $\lambda$, we can come up with an association probability
-% \begin{align}
-%    \assocP &= \frac{(\max \{ 0, \nabla \occf^\top
-% \ray \})^2 }{P_{\text{reflection}}}\lambdadist\\
-% &=(\max \{ 0, \nabla \occf^\top \ray \})^2
-%   \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
-% \end{align}
-
-Note that the fraction $\assocP$ although called association probability does
-not capture the entire information that we have available for compute
-association of points to tracks. This above fraction is the association
-probability given the hypothesized parameters of TP model.
-
-To compute the association probability between TP $i$ and
-point track $j$ we must use re-projection error as well. When the association
-$i$ and $j$ is right and the point of reflection is at depth $\lambda$ the
-re-projection error must be zero \eqref{eq:reprojerror}, otherwise the error
-becomes a measure of distance from the true solution.
-The error terms can be converted to probability domain by considering the error
-term as negative log of probability
-
-\begin{align}
-  P^{(ij)}_{\text{assoc by reproj}}(\lambda) = \frac{1}{Z}\exp(-\Ereproj(\lambda))
-\end{align}
-
-Using both the evidence terms we can write probability of association as
-\begin{align}
-  P^{(ij)}_{\text{assoc}} = \frac{1}{Z'}\int_0^{\infty} \assocP \frac{1}{\sqrt{2\pi}}\exp(-\Ereproj(\lambda))d\lambda
-  \label{eq:prob-assoc}
-\end{align}
-
-Once we have the probability of association we can compute the best possible
-assignment of TP for each point. The points having very small association
-probability are assigned to the background,
-\begin{align}
-  i^*_{j} = \argmin_{i} \int_0^\infty \assocP \Ereproj(\lambda) d\lambda
-\end{align}
-
-We use bounding box based assignment of point tracks to TPs as the baseline.
-For the regions where the bounding boxes overlap, we assign the points to the
-TP that has smaller mean depth then the competing bounding box.
-
-{\small
-\bibliographystyle{ieee}
-\bibliography{model}
-}
-\end{document}

### 2014-11-10 CVPR/Source/related.tex
Reorganized paper tex files

--- 2014-11-08 Paper/model.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
+\section{Related Work}
+\label{sec:related}
 
-\usepackage{cvpr}
-\usepackage{times}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-%%%%%%%%%%% CVPR template packages end %%%%%%%%%%%%%%
-\usepackage{verbatim} % for comment environment
-% \usepackage{soul} % for \hl highlighting
-% Include other packages here, before hyperref.
-
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-
-%\cvprfinalcopy % *** Uncomment this line for the final submission
-
-\def\cvprPaperID{489} % *** Enter the CVPR Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-% 3D pose of the cars and ego motion
-\newcommand{\pos}[2]{\mathbf{p}^{(#1)}(#2)}
-\newcommand{\ori}[2]{\mathbf{\omega}^{(#1)}(#2)}
-\newcommand{\state}[2]{\mathbf{s}^{#1}(#2)}
-
-% ego pose
-\newcommand{\egop}[1][t]{\pos{c}{#1}}
-\newcommand{\egoo}[1][t]{\ori{c}{#1}}
-\newcommand{\egos}[1][t]{\state{c}{#1}}
-
-% relative pose between camera and car $i$
-\newcommand{\relp}[2]{\Omega^{#1}(#2)}
-\newcommand{\relpz}[2]{\Omega_z^{#1}(#2)}
-
-% 3D tracks on car $i$ in its own coordinate frame
-\newcommand{\tracklets}{\mathbf{X}^{(i)}_o}
-\newcommand{\tracklet}[1]{\mathbf{x}^{(i)}_{#1}}
-% track projections on camera
-\newcommand{\trackp}[1]{\mathbf{u}^{(i)}(#1)}
-\newcommand{\trackpj}[1]{\mathbf{u}_j(#1)}
-% Unclassified track point projected on camera
-\newcommand{\ucTrackp}{\mathbf{u}(t)}
-
-% dimensions of car $i$
-\newcommand{\dimsn}[1]{\mathbf{B}^{#1}}
-\newcommand{\expDimsn}{\hat{\mathbf{B}}}
-
-% projection function
-\newcommand{\projectionOf}[1]{\pi_{\relp{i}{t}}\left(#1\right)}
-\newcommand{\projectionOft}[1]{\pi_{\relp{i}{t+1}}\left(#1\right)}
-\newcommand{\centerProj}{\bar{\pi}_{\relp{i}{t}}(\dimsn{i})}
-\newcommand{\cornerProj}[1]{\pi^{#1}_{\relp{i}{t}}(\dimsn{i})}
-\newcommand{\triangleProj}[1]{\triangle^{#1}_{\relp{i}{t}}(\dimsn{i})}
-
-% bounding box corners on image
-\newcommand{\bb}[1]{\mathbf{d}^{#1}(t)}
-
-\newcommand{\Energy}[1]{\mathcal{E}^{it}_{\text{#1}}}
-\newcommand{\pEnergy}[1]{\mathcal{E}^{ijt}_{\text{#1}}}
-% Weighted energy
-\newcommand{\WEnergy}[1]{\lambda_{\text{#1}}\Energy{#1}}
-\newcommand{\EnergyCol}{\mathcal{E}^{ijt}_{\text{col}}}
-\newcommand{\WEnergyCol}{\lambda_{\text{col}}\EnergyCol}
-
-\newcommand{\occFreeProj}[1]{\Pi_{\relp{i}{t}}(#1)}
-\newcommand{\minx}{x_{\text{min}}}
-\newcommand{\miny}{y_{\text{min}}}
-\newcommand{\maxx}{x_{\text{max}}}
-\newcommand{\maxy}{y_{\text{max}}}
-\newcommand{\frontface}{F^i_\text{FF}(t)}
-
-\newcommand{\occ}[1]{o({#1})}
-\newcommand{\face}{F^i_k(t)}
-
-\newcommand{\invProjectionOf}[1]{\pi^{-1}_{\relp{i}{t}}\left(#1\right)}
-\newcommand{\occf}{f^i_{occ}(\mathbf{x}_j)}
-\newcommand{\occftot}{f_{occ}(\mathbf{x}_j)}
-\newcommand{\occft}[1]{f_{occ}(#1)}
-
-\newcommand{\ray}{\hat{\mathbf{r}}_j}
-\newcommand{\occfray}{f_{occ}(\lambda\ray)}
-\newcommand{\lambdadist}{f_{\lambda}(\trackpj{t-1}, \lambda)}
-
-\newcommand{\occfxi}{L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i)}
-\newcommand{\occfi}{L(\lambda \ray; \pos{i}{t-1}, \Sigma_i)}
-\newcommand{\assocP}{a^{(ij)}(\lambda)}
-\newcommand{\assocPk}{a^{(ij)}(\lambda_k)}
-
-\newcommand{\Ereproj}{E^{(ij)}_{\text{reproj}}}
-\newcommand{\Ptrans}{P^{(j)}_{\text{transmission}}(\lambda)}
-\newcommand{\Ptransmud}{P^{(j)}_{\text{transmission}}(\mu^{(i)}_d)}
-\newcommand{\Prefl}{P^{(ij)}_{\text{reflection}}(\lambda)}
-\newcommand{\dishort}{d_i(\mathbf{x})}
-
-\newcommand{\Lu}{L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)}
-\newcommand{\Llambda}{L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d)}
-
-\newcommand{\Gauss}{\mathcal{N}}
-\newcommand{\PropDist}{\mathcal{W}_j}
-
-\newcommand{\muijl}{\mu^{(ij)}_{\lambda}}
-\newcommand{\sigmaijl}{\sigma^{ij}_{\lambda}}
-
-\newcommand{\Sigmait}{\Sigma^{(i)^{-1}}_t}
-
-\newcommand{\muit}{\mu^(i)_t}
-\newcommand{\Sigmaic}{\Sigma'^{(i)^{-1}}_c}
-
-\newcommand{\muic}{{\mu^(i)_c}}
-\newcommand{\Sigmaicf}{\Sigma^{(i)^{-1}}_c}
-
-\newcommand{\muiu}{\mu^{(i)}_t}
-\newcommand{\Sigmaiu}{\Sigma^{(i)^{-1}}_u}
-
-\newcommand{\xt}{\mathbf{x}_t}
-\newcommand{\xc}{\mathbf{x}_c}
-
-\newcommand{\Rctot}{R}
-\newcommand{\tctot}{t}
-
-\newcommand{\tcmut}{t'}
-
-\newcommand{\Beizer}{B\'eizer }
-
-\newcommand{\LaneUncertainty}[1]{\Sigma_{L_m}(#1)}
-\newcommand{\projOnLane}[1]{\pi_{L_m(k)}(#1)}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-%\ifcvprfinal\pagestyle{empty}\fi
-%\setcounter{page}{4321}
-%\DeclareMathSymbol{\Tangent}
-\DeclareMathOperator{\sech}{sech}
-\DeclareMathOperator{\poly}{poly}
-\DeclareMathOperator*{\argmin}{\arg\min}
-
-\begin{document}
-\title{Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.}
-\author{Vikas Dhiman\\
-  University of Michigan\\
-  Ann Arbor, MI, USA\\
-{\tt\small dhiman@umich.edu}
-\and
-Manmohan Chandraker\\
-NEC Laboratories America, Inc.\\
-Cupertino, CA, USA\\
-{\tt\small manu@nec-labs.com}
-\and
-Jason J Corso\\
-  University of Michigan\\
-  Ann Arbor, MI, USA\\
-{\tt\small jjcorso@eecs.umich.edu}
-}
-\maketitle
-
-%%%%%%%%% ABSTRACT
-\begin{abstract}
-  TODO: Write abstract
-  \vspace{4cm}
-\end{abstract}
-
-\section{Introduction}
-
-\begin{itemize}
-  \item Introduce the problem
-  \item Describe our approach
-  \item Contrast with Milan's work
-  \item Contrast with Andreas Geiger's work
-  \item Highlight the contributions
-\end{itemize}
-\vspace{10cm}
-\begin{figure}[t]
-  \includegraphics[width=\columnwidth]{graphics/graphicalModelFrom61ConstVars.pdf}
-  \caption{Graphical model. The six numbered black circles represent the
-    unknown state variables of each car. All other nodes in the graphical model
-    are assumed
-    observed variables. Consider each energy in the model one by one. (1)
-    Bounding box energy: The bounding box energy without occlusion modeling is
-    a unary term, but with occlusion it becomes a higher order term that
-    affects the state of occluder as well. In this graphical model we assume
-    that the scene is being observed from left to right, hence "2" occludes "6"
-    and "5" and "5" occludes "1". The bounding box detection is represented by
-  $\mathbf{d}_{bb}^i(t)$ and the statistical dependencies are represented by
-  red lines. (2) Point tracks ($\Energy{track}$): Since occlusion is also
-  included in modeling point tracks energy we have similar interdependencies
-  for point tracks energy. The available point tracks are modeled by
-  $\mathbf{u}(t)$. (3) Collision ($\Energy{coll}$) : The collision energy
-  mathematically is a dense graph between all the TP but here we represent
-  collision among only those TP that are near enough to have a significant
-collision energy. (4) Orientation from detection ($\Energy{ori}$) (5) Orientation from lane (and map) information ($\Energy{lane}$)}
-  \label{fig:graphmodel}
-\end{figure}
-
-\section{Related Work}
 TODO:
@@
 \vspace{15cm}
-
-\section{Problem Definition}
-TODO:
-\vspace{4cm}
-
-\section{Notation}
-
-\begin{table}[h]
-  \begin{tabular}{|l|l|}
-    \hline
-    Symbol & Meaning \\
-    \hline
-    $\pos{i}{t}$ & Position of $i$th car at time $t$\\
-    $\ori{i}{t}$ & Orientation of $i$th car at time $t$\\
-     $\dimsn{i}$ & 3D bounding box of the car (dimensions)\\
-    $\state{i}{t}$ & State of car $=\{\pos{i}{t}, \ori{i}{t}, \dimsn{i}\}$\\
-    $\egop$ & Position of camera at time $t$\\
-    $\egoo$ & Orientation of camera at time $t$\\
-    $\relp{i}{t}$ & Relative car pose w.r.t. camera \\
-    $\tracklets$ & 3D points tracked on car $i$ in its own frame\\
-    $\trackp{t}$ & Projection of $\tracklets$ in camera\\
-    $\projectionOf{.}$ & Projection function for pose $\relp{i}{t}$\\
-    $\bb{i}$ & 2D bounding box of the car in image\\
-    \hline
-  \end{tabular}
-\end{table}
-
-%%%%%%%%% BODY TEXT
-\section{The Model}
-
-The objective is to find the most likely traffic participant (TP) state given
-various evidences $\mathbb{E} = \{\{\trackp{t}\}, \{\bb{i}\}, \text{lane det.},
-\text{map}, \text{GPS}\}$.
-
-Mathematically, find:
-\begin{align}
-  \{\state{i}{t}\}^* &= \arg \max P(\{\state{i}{t}\} | \mathbb{E})
-\end{align}
-
-Bayes rule
-\begin{align}
-  P(\{\state{i}{t}\} | \mathbb{E}) &=
-  \frac{1}{Z}P( \mathbb{E} | \{\state{i}{t}\})P(\{\state{i}{t}\})
-\end{align}
-
-Assume conditional independence according to graphical model in
-\ref{fig:graphmodel}.
-
-\begin{multline}
-  P(\{\state{i}{t}\} | \mathbb{E}) =
-  \frac{1}{Z}
-  \prod_{t=s_i}^{e_i}\prod_{i,j: i \ne j}(P(\state{i}{t}, \state{j}{t}))\\
-%
-  \prod_{i=1}^{N}
-  \prod_{t=s_i}^{e_i}
-  P(\bb{i} | \state{i}{t})
-  P(\trackp{t} | \state{i}{t})\\
-  P(\state{i}{t} | L_m(t))
-  P(\state{i}{t} | \state{i}{t-1})
-  P(\state{i}{t})
-\end{multline}
-
-We can formulate similar objective function in negative log domain:
-\footnote{TODO:Resolve inconsistency in summation absorption in energy terms.}
-\begin{multline}
-  -\log{P(\{\state{i}{t}\} | \mathbb{E})} = 
-  Z' + \sum_{i,j:i\ne j} \sum_{t=s_i}^{e_i}  \WEnergyCol \\
-  + \sum_{i=1}^N \sum_{t=s_i}^{e_i}
-    \WEnergy{box}
-  + \WEnergy{track}\\
-  + \WEnergy{lane}
-  + \WEnergy{dyn}
-  + \WEnergy{prior}
-\end{multline}
-
-\section{Modeling traffic participants}
-\label{sec:TPmodel}
-Following standard model of occupancy in 3D reconstruction community, we model
-the TP's as high occupancy regions in space. We model the
-uncertainty in occupancy equivalent of transparency i.e. the regions that are
-more certain to be occupied are viewed as relatively more opaque then other
-regions. Based on this intuition we model TP's translucent
-ellipsoids whose opacity is maximum at the center and drops off away from the
-center. More specifically we model, the occupancy of a TP as a
-logistic function,
-
-\begin{align}
-   \occf = L(\mathbf{x}; \pos{i}{t}, \Sigma_i)
-\end{align}
-where $L(.)$ is the logistic function defined by
-\begin{align}
-  L(\mathbf{x}; \pos{i}{t}, \Sigma_i) = \frac{1}{
-    1 + e^{-k(1 - d(\mathbf{x},\pos{i}{t}))}
-    }
-\end{align}
-where $d(\mathbf{x},\pos{i}{t}) =
-(\mathbf{x}-\pos{i}{t})^\top\Sigma_i(\mathbf{x}-\pos{i}{t})$ and $k =
-10\ln{49}$. $k$ is chosen such that $L(.) = 0.98$ when $d(.) =
-0.9$. $\Sigma_i$ determines the spread of the ellipsoid and depends on the
-dimensions of the TP. Please refer to supplementary material 
-for computation of $\Sigma_i$ from TP's dimensions.
-
-We model the probability of a point $\mathbf{x}_j$ on a object $i$ getting successfully
-observed in a camera image at point $\trackpj{t}$ is dependent up two factors,
-(1) reflection and (2) transmission through intermediate space. The reflection
-part ensures that there is an object to reflect a point at a certain region in
-the 3D space while transmission part models occlusion.
-\begin{align}
-  P^{(ij)}_{\text{observation}} = P^{(ij)}_{\text{reflection}}P^{(j)}_{\text{transmission}}
-\end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Reflection probability}
-For Lambertian reflection we replace the surface normal with the
-gradient of occupancy.
-%
-\begin{align}
-  \Prefl = (\max \{0, \nabla \occf^\top
-  \hat{\mathbf{r}_j}\})^2
-\end{align}
-%
-where $\ray =
-\frac{K^{-1}\trackpj{t}}{\|K^{-1}\trackpj{t}\|}$ is unit vector in the
-direction of ray. The gradient in the direction opposite to ray yields -ve
-probability which needs to be clipped off. Squaring the function keep it
-smooth near zero.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Transmission probability}
-A model for transmission of light through a material of thickness $x$,
-density $\rho$ and opacity $k_o$ is given by Beer-Lambert law 
-%
-\begin{align}
-  I(x) = I_0e^{-k_o\rho x}
-\end{align}
-%
-
-Since both opacity and density are represented by the occupancy function
-$\occftot = \sum_i \occf$, and also the domain of our $\occftot$ is $[0, 1]$ instead of $[0,
-\infty]$ as in case of $k_o$; we replace $e^{-k_o\rho}$ by the transparency
-function $1 - \occftot$. So the transmission probability over a small distance
-$d\lambda$ is given by
-%
-\begin{align}
-  P_{\text{transmission}}(\lambda + d\lambda) =
-  P_{\text{transmission}}(\lambda) (1-\occftot)^{d\lambda}
-\end{align}
-%
-
-For a given 3D point $\mathbf{x}_j = \lambda \ray$, the probability that the
-point $\trackpj{t}$ is reflected from a distance $\lambda$ is given by
-
-\begin{align}
-  %P^{(j)}_{\text{observation}}(\lambda) &= P_{\text{reflection}}
-  \Ptrans &=
-  \prod_{0}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda} %\\
-  %= \max \{ 0, (\nabla f_{occ}&(\lambda \ray)^\top \ray) \}
-  %\prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
-  \label{eq:ptrans-integral}
-\end{align}
-where $\prod_{0}^{\lambda}$ represents the \emph{product integral} from $0$ to
-$\lambda$.
-
-In practice, the integral for transmission probability
-\eqref{eq:ptrans-integral} is difficult to compute even numerically. So we
-choose a product of sigmoid function that approximates the behaviour of
-transmission probability,
-%
-\begin{align}
-\label{eq:evalCumulativePtrans}
-  \Ptrans &= \prod_i L_u(\trackp{t}; \muiu,\Sigmaiu)L_{\lambda}(\lambda; \mu^i_d)
-\end{align}
-%
-where $L_u(.)$ is sigmoid in image domain with $\mu^i_u$ and $\Sigma^i_u$
-representing the elliptical projection of $i^{th}$ TP.
-$L_{\lambda}(.)$ is sigmoid in the depth domain with $\mu^i_d$ as the mean
-depth of the $i^{th}$ TP.
-%
-\begin{align}
-  L_u(\mathbf{u}; \muiu,\Sigmaiu) &= \frac{1}{
-    1 + e^{-k_u(1 - (\mathbf{u} - \muiu)^\top\Sigmaiu(\mathbf{u} -
-    \muiu))}
-  }
-  \\
-  L_{\lambda}(\lambda; \mu^i_d) &= \frac{1}{
-    1 + e^{-k_d(\lambda - \mu^i_d)}
-}
-\end{align}
-%
-
-\begin{comment}%% Comment
-  A product integral is a simple integral in log domain
-  \begin{align}
-    \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} =
-    e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
-  \end{align}
-\end{comment}%% Comment
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Energies}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We explain energies in this section
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Point tracks energy with occlusion}
-\label{sec:totalContPtTracksEnergy}
-We model continuous point tracks energy with explicit occlusion reasoning as
-the expected re-projection error over the association probability,
-
-\begin{multline}
-  \Energy{traci}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \\
-    \sum_{i=1}^{N} 
-    %\sum_{t = s_i}^{e_i}
-    \sum_{j = 1}^{M}
-    \int_1^\infty \assocP\Ereproj(\lambda) d\lambda
-\end{multline}
-where $\assocP$ is the association probability of
-$j$\textsuperscript{th} point with $i$\textsuperscript{th} TP at depth $\lambda$
-and $\Ereproj(\lambda)$ is the re-projection error given by
-%
-\begin{align}
-  \assocP &= \Prefl\Ptrans\\
-  \Ereproj(\lambda) &= \left\|\trackpj{t+1} - \projectionOft{\invProjectionOf{\trackpj{t}, \lambda}}\right\|^2 .
-  \label{eq:reprojerror}
-\end{align}
-
-The  $\projectionOf{.}$ and $\invProjectionOf{.}$ denote the projection and
-inverse projection functions that project 3D point to camera image and vice
-versa. Note that inverse projection $\invProjectionOf{.}$ depend on both the
-point $\trackp{t}$ and the unknown depth $\lambda$. Also note that the inverse projection is dependent on TP pose at time $t$ while the projection depends on pose at time $t+1$ which can be different.
-
-\begin{comment}
-  \subsubsection{Occupancy function}
-  Assuming occupancy to be a
-  probability distribution over 3D space. For each TP the
-  occupancy is modeled as a logistic function 
-  \begin{align}
-     \occf = L(\mathbf{x}; \pos{i}{t}, \Sigma_i)
-  \end{align}
-  where $L(.)$ is the logistic function defined by
-  \begin{align}
-    L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i) = \frac{1}{
-      1 + e^{-k(1 - d(\mathbf{x},\pos{i}{t-1}))}
-      }
-  \end{align}
-  where $d(\mathbf{x},\pos{i}{t-1}) =
-  (\mathbf{x}-\pos{i}{t-1})^\top\Sigma_i(\mathbf{x}-\pos{i}{t-1})$ and $k =
-  10\ln{49}$. $k$ is chosen such that $L(.) = 0.98$ when $d(.) =
-  0.9$
-  % Once we have our distribution over $\lambda$, $\lambdadist$ we can compute the
-  % reprojection of $\trackpj{t-1}$ over image in time $t$ as a function of
-  % $\lambda$. Let
-\end{comment}
-
-\begin{comment}
-  \subsubsection{Approximations}
-  Reflection probability of $i$th TP is easy to compute
-  analytically 
-  \begin{multline}
-    \Prefl =
-    (\max \{ 0, \nabla \occf^\top \ray \})^2 \\
-    = (\max \{ 0, \nabla \occfxi^\top\ray \})^2
-    \label{eq:analytic-prefl}
-  \end{multline}
-  where 
-  \begin{multline}
-    \nabla \occfxi^\top\ray \\=
-    \nabla k\dishort \sech^2\left(\frac{k}{2}\dishort\right)
-  \end{multline}
-  where $\dishort = 1-d(\mathbf{x}, \pos{i}{t-1})$ is a signed distance measure
-  from the contour of the ellipsoid where $d(\mathbf{x}, \pos{i}{t-1})$ is 1.
-
-  However, the transmission probability needs to be approximated.  
-  %
-  % \subsubsection{Computing $\Prefl$ and $\Ptrans$}
-  % Focusing on  $\nabla \occfxi$ 
-  % 
-  % \begin{multline}
-  %   \nabla \occfxi =\\
-  %   \frac{-k\nabla d(\mathbf{x}, \pos{i}{t-1})e^{-k(1-d(\mathbf{x}, \pos{i}{t-1}))}}{
-  %     (1 + e^{-k(1-d(\mathbf{x}, \pos{i}{t-1}))})^2
-  %   } \\ 
-  %   = -k\nabla d(\mathbf{x}, \pos{i}{t-1})\sech^2\left(\frac{k}{2}(1-d(\mathbf{x},
-  %   \pos{i}{t-1}))\right)
-  %   \\
-  %   = \nabla k\dishort \sech^2\left(\frac{k}{2}\dishort\right)
-  % \end{multline}
-  % where $\dishort = 1-d(\mathbf{x}, \pos{i}{t-1})$ is a signed distance measure
-  % from the contour of the ellipsoid where $d(\mathbf{x}, \pos{i}{t-1})$ is 1.
-  % Focusing on $\nabla d(.)$
-  % 
-  % \begin{align}
-  %   \nabla d(\mathbf{x}, \pos{i}{t-1}) = 2\Sigma_i(\mathbf{x} - \pos{i}{t-1})
-  % \end{align}
-  % Back to \eqref{eq:analytic-prefl}
-  % 
-  % \begin{multline}
-  %   (\max \{ 0, \nabla \occf^\top \ray \})^2 = \\
-  %   \sech^4\left(\frac{k}{2}\dishort\right) 
-  %   (\max \{ 0 , \nabla k\dishort^\top\ray\})^2
-  % \end{multline}
-  % 
-  % The probability is simply $\sech^2(.)$ scaled by gradient of ellipsoid
-  % $\nabla k\dishort$ projected in the ray direction $\ray$.
-  % 
-  % \begin{align}
-  %   \Ptrans = 
-  %   e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
-  % \end{align}
-  % \begin{multline}
-  % \int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}
-  % =  \\
-  % \int_{1}^{\lambda} \ln{\left(1 - \sum_i \occfi\right)}{d\lambda}
-  % \end{multline}
-  % 
-  % The above integral is very difficult to approximate or compute analytically.
-  So based on intuition, we approximate the $\Ptrans$ by following function
-  \begin{align}
-  \label{eq:evalCumulativePtrans}
-    \Ptrans &= \prod_i L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)L_{\lambda}(\lambda; \mu^i_d)\\
-    L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u) &= \frac{1}{
-      1 + e^{-k_u(1 - (\mathbf{u} - \mu^i_u)^\top\Sigma^i_u(\mathbf{u} -
-      \mu^i_u))}
-    }
-    \\
-    L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d) &= \frac{1}{
-    1 + e^{-k_d(\lambda - \mu^i_d(\mathbf{u}))}
-  }
-  \end{align}
-  where 
-  \begin{align}
-    \mu_u^i &= \projectionOf{\pos{i}{t-1}} \label{eq:muiudef}\\
-    \Sigma_u^i &= \projectionOf{\Sigma_i} \label{eq:sigmauidef}\\
-    \mu^i_d(\mathbf{u}) &= \relp{i}{t}\\
-    k_u &= 10\log(49)\\
-    k_d &= \frac{\log(49)}{\sqrt{h^2 + l^2 + w^2}}
-    \label{eq:ptransmissionInit}
-  \end{align}
-  is the distance of the centre of the TP from the camera.
-
-  % $\mu^i_d(\mathbf{u}) = \min_{\lambda} d^2_i(\lambda K^{-1}\mathbf{u})$.
-  % $\mu^i_d(\mathbf{u})$ is the closest point to the unit contour of ellipsoid.
-  % If there are multiple such points, the point closest to the camera is taken as
-  % $\mu^i_d(\mathbf{u})$
-
-  The association probability becomes
-
-  \begin{multline}
-    \assocP = 
-      \sech^4\left(\frac{k}{2}\dishort\right)
-      (\max \{ 0, \nabla k\dishort^\top\ray \})^2\\
-    \prod_i \Lu
-      \Llambda \\
-      \label{eq:assocCoeffEval}
-  \end{multline}
-
-  So the energy becomes
-
-  \begin{multline}
-    \label{eq:integrand}
-    \Energy{track}(.) = 
-      \sum_{i = 1}^N
-      \sum_{j = 1}^{M}
-      \int_1^{\infty}
-      \assocP
-      \Ereproj(\lambda)
-      d\lambda
-  \end{multline}
-  where $x = \lambda \ray$ and $\Ereproj(\lambda) = \|\trackpj{t} -
-  f^i_{reproj}(\trackpj{t-1}, \lambda)\|^2$ is reprojection error which is a
-  quadratic in $\lambda$
-
-  The integral in the above expression is computed numerically.
-\end{comment}
-
-\subsection{Object detection energy with occlusion}
-
-Object detection is usually followed by non-maximal suppression that results in
-discarding similar bounding boxes. When we are jointly optimizing detections
-with other cues, it is not usually desirable to go with a single bounding box.
-Hence, we keep all the bounding box detections by approximating them with
-multi-modal sum of Gaussian like logistic functions. We fit the parametric function of the form 
-%
-\begin{align}
-  S(\bb{i}) = \sum_k A_k \exp(-(\bb{i}-\mu^{(d)}_k)^\top \Sigma^{(d)-1}_k
-  (\bb{i}-\mu^{(d)}_k))
-\end{align}
-%
-to detection scores, by non-linear error minimization with initialization from
-non-maximal suppressed outputs. Here $\mu^{(d)}_j$ is one of the $k$ modes as a
-4D vector representing a single bounding box as $[\minx, \miny, \maxx,
-\maxy]^\top$. The optimization is constrained with symmetry and positive
-definiteness of $\Sigma^{(d)-1}_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
-
-\subsubsection{Detection scores with occlusion reasoning} 
-With our model of $\Ptrans$ described in Section \ref{sec:TPmodel}, we can
-compute the probability of a point $\mathbf{u}$ on image be occluded assuming
-the point is on TP $i$ with mean depth $\mu^{(i)}_d$ as
-\begin{align}
-  O_{i}(\mathbf{u}, \mu^{(i)}_d) = 1 - \Ptransmud \enspace .
-\end{align}
-
-If we a portion of our proposed detection bounding box is known to be occluded,
-then we would like to decrease the confidence in the detection score about the
-localization of that end of the object. Assuming that the occlusion is often on
-the boundary of detection bounding boxes, we want to decrease our confidence on
-the mean detection boundaries around the occluded boundaries. 
-One of the simplest ways will be to scale the appropriate diagonal element of
-$\Sigma_j$ by an appropriate scaling factor proportional to occlusion. But this
-does not model appropriate how does occlusion affects the non diagonal terms.
-Hence, we choose a covariance addition model where we compute a occlusion
-covariance matrix, that provides a measure of occlusion in each direction.
-
-To re-model our detection scores scaled by continuous occlusion we sample
-$O_{i}(\mathbf{u}, \mu^{(i)}_d)$ at the hypothesized detection boundaries from
-GMM $S(.)$ and we augment the detection boundary covariance matrix by
-$\mathcal{P}_{j} = \rho_{j}\rho_{j}^\top$ where $\rho_{j} = O_{j}(\mathbf{u},
-\mu^{(i)}_d)$. The new covariance matrix in detection score is given by 
-%
-\begin{align}
-  \Sigma'^{(d)}_j = \mathcal{P}_{j} + \Sigma^{(d)}_j
-\end{align}
-%
-The detection scores GMM with occlusion is given by replacing the covariance
-matrix
-%
-\begin{multline}
-  S'(\bb{i}) =\\
-  \sum_j A_j \exp(-(\bb{i}-\mu^{(d)}_j)^\top \Sigma'^{(d)-1}_j
-  (\bb{i}-\mu^{(d)}_j))
-\end{multline}
-
-The energy of detection scores is simply take to be the inverse of the detection score.
-\begin{align}
-  \Energy{detect}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}
-\end{align}
-
-\subsection{Lane energy}
-\label{sec:laneEnergy}
- The lanes are modeled as splines. Here we assume that the confidence in lane
- detection is decreases as the distance from the lane center increases.  The
- energy is given by the dot product between car orientation and tangent to the
- lane at that point.
-
-\begin{multline}
-  \label{eq:laneOrientationEnergy}
-  \Energy{lane} = \\
-  \sum_{m \in M_{\text{close}}}
-  (1 - \ori{i}{t} \cdot \text{TAN}(L_{m}(k), \pos{i}{t}) )
-\LaneUncertainty{\pos{i}{t}}
-\end{multline}
-where $M_{\text{close}} = \{m : \text{DIST}(L_{m}(k), \pos{i}{t}) < 50\} $ is
-the set of nearby lanes and 
-\begin{multline}
-\LaneUncertainty{\pos{i}{t}} = \\
-  \frac{1}{1 + exp(-q(w_{\text{road}} - \text{DIST}(L_{m}(k), \pos{i}{t})))}
-\end{multline}
-for some constant $w_{\text{road}}$ that represents the width of the road.
-
-\subsection{Transition probability}
-Dynamics constraints should not only enforce smooth trajectories, but also the
-holonomic constraints.  The following energy adds a penalty if the change in
-position is not in direction of previous orientation.
-
-\begin{align}
-  \label{eq:totalPosTransitionEnergy}
-  \Energy{dyn-hol} = 1 - \ori{i}{t-1} \cdot (\pos{i}{t} - \pos{i}{t-1})
-\end{align}
-
-The following energy adds a penalty for change in position and orientation
-but a penalty for change in velocity is much better approximation. However, in
-a Markovian setting that would mean extending the state space of the car to
-include velocity.
-
-\begin{align}
-  \Energy{dyn-ori} &= \|\ori{i}{t} - \ori{i}{t-1}\|^2\\
-  \Energy{dyn-vel} &= \|(\pos{i}{t} - 2\pos{i}{t-1}) + \pos{i}{t-2}\|^2
-\end{align}
-
-As a result the dynamics are modeled by weighted combination of holonomic
-constraint and smoothness constraints.
-
-\begin{align}
-  \WEnergy{dyn} &= \WEnergy{dyn-hol} + \WEnergy{dyn-ori} + \WEnergy{dyn-vel}
-\end{align}
-
-\subsection{Collision energy}
-
-Bhattacharya coefficient $\int_a^b\sqrt{p(x)q(x)}dx$ is a measure of similarity
-of two distributions $p(x)$ and $q(x)$. If we represent TPs as gaussians in
-Birds eye view (BEV), then similarity is a measure of collision. Exactly
-overlapping distribution results in coefficient as 1. 
-%The analytical form of
-%Bhattacharya coefficient has been taken from
-%\url{http://like.silk.to/studymemo/PropertiesOfMultivariateGaussianFunction.pdf}
-
-\begin{multline}
-  \label{eq:collisionEnergyHellingerDistance}
-  \EnergyCol =\\ -\log\left(
-  A_{ij}
-  e^{-\frac{1}{8}
-    \left(\pos{i}{t} - \pos{j}{t}\right)^\top
-    P^{-1}
-    \left(\pos{i}{t} - \pos{j}{t}\right)
-    }
-    \right)
-\end{multline}
-where 
-\begin{align}
-  A_{ij} &= \frac{|\Sigma_i|^\frac{1}{4}|\Sigma_j|^\frac{1}{4}}
-  {|P|^\frac{1}{2}}\\
-  P &= \frac{1}{2}\Sigma_i + \frac{1}{2}\Sigma_j\\
-\Sigma_i^{-1} &= R^\top_{\ori{i}{t}} \begin{bmatrix} 2/l_i & 0 \\ 0 & 2/w_i \end{bmatrix}
-R_{\ori{i}{t}}
-\end{align}
-
-\subsection{Size Prior}
-
-Prior can include among many other things the size prior on the car.
-
-\begin{align}
-  \label{eq:totalSizeEnergy}
-  \Energy{prior} &= (\dimsn{i} - \expDimsn)^\top\Sigma_{\expDimsn}^{-1}(\dimsn{i} -
-  \expDimsn)
-\end{align}
-
-where $\expDimsn$ is the mean TP dimensions and
-$\Sigma_{\expDimsn}$ is the correspondence covariance matrix.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Association error evaluation}
-
-To verify the correctness of our association probability $\assocP$ we perform
-association error experiment that compare the accuracy of point track
-association with TPs with that of bounding box baseline method.
-
-% \begin{align}
-%   f^{i}_{reproj}&(\trackpj{t-1}, \lambda) =
-%   \projectionOf{\invProjectionOf{\trackpj{t-1}}}\\
-%   %&= K(R^i_t ((R^i_{t-1})^\top\lambda \ray - (R^i_{t-1})^\top T_{t-1}) + T_{t})\\
-%   &= \frac
-%   {p_{1:2}\lambda + q_{1:2}}
-%   {p_{3}\lambda + q_{3}}
-% \end{align}
-% where $p_{1:3} = KR^i_t(R^i_{t-1})^\top\ray$ and
-% $q_{1:3} = KR^i_t(R^i_{t-1})^\top T_{t-1} + KT_t$
-% 
-% Now that we have an association from TP $i$ to point track $j$ through
-% $\lambda$, we can come up with an association probability
-% \begin{align}
-%    \assocP &= \frac{(\max \{ 0, \nabla \occf^\top
-% \ray \})^2 }{P_{\text{reflection}}}\lambdadist\\
-% &=(\max \{ 0, \nabla \occf^\top \ray \})^2
-%   \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
-% \end{align}
-
-Note that the fraction $\assocP$ although called association probability does
-not capture the entire information that we have available for compute
-association of points to tracks. This above fraction is the association
-probability given the hypothesized parameters of TP model.
-
-To compute the association probability between TP $i$ and
-point track $j$ we must use re-projection error as well. When the association
-$i$ and $j$ is right and the point of reflection is at depth $\lambda$ the
-re-projection error must be zero \eqref{eq:reprojerror}, otherwise the error
-becomes a measure of distance from the true solution.
-The error terms can be converted to probability domain by considering the error
-term as negative log of probability
-
-\begin{align}
-  P^{(ij)}_{\text{assoc by reproj}}(\lambda) = \frac{1}{Z}\exp(-\Ereproj(\lambda))
-\end{align}
-
-Using both the evidence terms we can write probability of association as
-\begin{align}
-  P^{(ij)}_{\text{assoc}} = \frac{1}{Z'}\int_0^{\infty} \assocP \frac{1}{\sqrt{2\pi}}\exp(-\Ereproj(\lambda))d\lambda
-  \label{eq:prob-assoc}
-\end{align}
-
-Once we have the probability of association we can compute the best possible
-assignment of TP for each point. The points having very small association
-probability are assigned to the background,
-\begin{align}
-  i^*_{j} = \argmin_{i} \int_0^\infty \assocP \Ereproj(\lambda) d\lambda
-\end{align}
-
-We use bounding box based assignment of point tracks to TPs as the baseline.
-For the regions where the bounding boxes overlap, we assign the points to the
-TP that has smaller mean depth then the competing bounding box.
-
-{\small
-\bibliographystyle{ieee}
-\bibliography{model}
-}
-\end{document}

### 2014-11-10 CVPR/Source/setup.tex
Reorganized paper tex files

--- 2014-11-08 Paper/model.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
-
-\usepackage{cvpr}
-\usepackage{times}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-%%%%%%%%%%% CVPR template packages end %%%%%%%%%%%%%%
-\usepackage{verbatim} % for comment environment
-% \usepackage{soul} % for \hl highlighting
-% Include other packages here, before hyperref.
-
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-
-%\cvprfinalcopy % *** Uncomment this line for the final submission
-
-\def\cvprPaperID{489} % *** Enter the CVPR Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-% 3D pose of the cars and ego motion
-\newcommand{\pos}[2]{\mathbf{p}^{(#1)}(#2)}
-\newcommand{\ori}[2]{\mathbf{\omega}^{(#1)}(#2)}
-\newcommand{\state}[2]{\mathbf{s}^{#1}(#2)}
-
-% ego pose
-\newcommand{\egop}[1][t]{\pos{c}{#1}}
-\newcommand{\egoo}[1][t]{\ori{c}{#1}}
-\newcommand{\egos}[1][t]{\state{c}{#1}}
-
-% relative pose between camera and car $i$
-\newcommand{\relp}[2]{\Omega^{#1}(#2)}
-\newcommand{\relpz}[2]{\Omega_z^{#1}(#2)}
-
-% 3D tracks on car $i$ in its own coordinate frame
-\newcommand{\tracklets}{\mathbf{X}^{(i)}_o}
-\newcommand{\tracklet}[1]{\mathbf{x}^{(i)}_{#1}}
-% track projections on camera
-\newcommand{\trackp}[1]{\mathbf{u}^{(i)}(#1)}
-\newcommand{\trackpj}[1]{\mathbf{u}_j(#1)}
-% Unclassified track point projected on camera
-\newcommand{\ucTrackp}{\mathbf{u}(t)}
-
-% dimensions of car $i$
-\newcommand{\dimsn}[1]{\mathbf{B}^{#1}}
-\newcommand{\expDimsn}{\hat{\mathbf{B}}}
-
-% projection function
-\newcommand{\projectionOf}[1]{\pi_{\relp{i}{t}}\left(#1\right)}
-\newcommand{\projectionOft}[1]{\pi_{\relp{i}{t+1}}\left(#1\right)}
-\newcommand{\centerProj}{\bar{\pi}_{\relp{i}{t}}(\dimsn{i})}
-\newcommand{\cornerProj}[1]{\pi^{#1}_{\relp{i}{t}}(\dimsn{i})}
-\newcommand{\triangleProj}[1]{\triangle^{#1}_{\relp{i}{t}}(\dimsn{i})}
-
-% bounding box corners on image
-\newcommand{\bb}[1]{\mathbf{d}^{#1}(t)}
-
-\newcommand{\Energy}[1]{\mathcal{E}^{it}_{\text{#1}}}
-\newcommand{\pEnergy}[1]{\mathcal{E}^{ijt}_{\text{#1}}}
-% Weighted energy
-\newcommand{\WEnergy}[1]{\lambda_{\text{#1}}\Energy{#1}}
-\newcommand{\EnergyCol}{\mathcal{E}^{ijt}_{\text{col}}}
-\newcommand{\WEnergyCol}{\lambda_{\text{col}}\EnergyCol}
-
-\newcommand{\occFreeProj}[1]{\Pi_{\relp{i}{t}}(#1)}
-\newcommand{\minx}{x_{\text{min}}}
-\newcommand{\miny}{y_{\text{min}}}
-\newcommand{\maxx}{x_{\text{max}}}
-\newcommand{\maxy}{y_{\text{max}}}
-\newcommand{\frontface}{F^i_\text{FF}(t)}
-
-\newcommand{\occ}[1]{o({#1})}
-\newcommand{\face}{F^i_k(t)}
-
-\newcommand{\invProjectionOf}[1]{\pi^{-1}_{\relp{i}{t}}\left(#1\right)}
-\newcommand{\occf}{f^i_{occ}(\mathbf{x}_j)}
-\newcommand{\occftot}{f_{occ}(\mathbf{x}_j)}
-\newcommand{\occft}[1]{f_{occ}(#1)}
-
-\newcommand{\ray}{\hat{\mathbf{r}}_j}
-\newcommand{\occfray}{f_{occ}(\lambda\ray)}
-\newcommand{\lambdadist}{f_{\lambda}(\trackpj{t-1}, \lambda)}
-
-\newcommand{\occfxi}{L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i)}
-\newcommand{\occfi}{L(\lambda \ray; \pos{i}{t-1}, \Sigma_i)}
-\newcommand{\assocP}{a^{(ij)}(\lambda)}
-\newcommand{\assocPk}{a^{(ij)}(\lambda_k)}
-
-\newcommand{\Ereproj}{E^{(ij)}_{\text{reproj}}}
-\newcommand{\Ptrans}{P^{(j)}_{\text{transmission}}(\lambda)}
-\newcommand{\Ptransmud}{P^{(j)}_{\text{transmission}}(\mu^{(i)}_d)}
-\newcommand{\Prefl}{P^{(ij)}_{\text{reflection}}(\lambda)}
-\newcommand{\dishort}{d_i(\mathbf{x})}
-
-\newcommand{\Lu}{L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)}
-\newcommand{\Llambda}{L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d)}
-
-\newcommand{\Gauss}{\mathcal{N}}
-\newcommand{\PropDist}{\mathcal{W}_j}
-
-\newcommand{\muijl}{\mu^{(ij)}_{\lambda}}
-\newcommand{\sigmaijl}{\sigma^{ij}_{\lambda}}
-
-\newcommand{\Sigmait}{\Sigma^{(i)^{-1}}_t}
-
-\newcommand{\muit}{\mu^(i)_t}
-\newcommand{\Sigmaic}{\Sigma'^{(i)^{-1}}_c}
-
-\newcommand{\muic}{{\mu^(i)_c}}
-\newcommand{\Sigmaicf}{\Sigma^{(i)^{-1}}_c}
-
-\newcommand{\muiu}{\mu^{(i)}_t}
-\newcommand{\Sigmaiu}{\Sigma^{(i)^{-1}}_u}
-
-\newcommand{\xt}{\mathbf{x}_t}
-\newcommand{\xc}{\mathbf{x}_c}
-
-\newcommand{\Rctot}{R}
-\newcommand{\tctot}{t}
-
-\newcommand{\tcmut}{t'}
-
-\newcommand{\Beizer}{B\'eizer }
-
-\newcommand{\LaneUncertainty}[1]{\Sigma_{L_m}(#1)}
-\newcommand{\projOnLane}[1]{\pi_{L_m(k)}(#1)}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-%\ifcvprfinal\pagestyle{empty}\fi
-%\setcounter{page}{4321}
-%\DeclareMathSymbol{\Tangent}
-\DeclareMathOperator{\sech}{sech}
-\DeclareMathOperator{\poly}{poly}
-\DeclareMathOperator*{\argmin}{\arg\min}
-
-\begin{document}
-\title{Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.}
-\author{Vikas Dhiman\\
-  University of Michigan\\
-  Ann Arbor, MI, USA\\
-{\tt\small dhiman@umich.edu}
-\and
-Manmohan Chandraker\\
-NEC Laboratories America, Inc.\\
-Cupertino, CA, USA\\
-{\tt\small manu@nec-labs.com}
-\and
-Jason J Corso\\
-  University of Michigan\\
-  Ann Arbor, MI, USA\\
-{\tt\small jjcorso@eecs.umich.edu}
-}
-\maketitle
-
-%%%%%%%%% ABSTRACT
-\begin{abstract}
-  TODO: Write abstract
-  \vspace{4cm}
-\end{abstract}
-
-\section{Introduction}
-
-\begin{itemize}
-  \item Introduce the problem
-  \item Describe our approach
-  \item Contrast with Milan's work
-  \item Contrast with Andreas Geiger's work
-  \item Highlight the contributions
-\end{itemize}
-\vspace{10cm}
-\begin{figure}[t]
-  \includegraphics[width=\columnwidth]{graphics/graphicalModelFrom61ConstVars.pdf}
-  \caption{Graphical model. The six numbered black circles represent the
-    unknown state variables of each car. All other nodes in the graphical model
-    are assumed
-    observed variables. Consider each energy in the model one by one. (1)
-    Bounding box energy: The bounding box energy without occlusion modeling is
-    a unary term, but with occlusion it becomes a higher order term that
-    affects the state of occluder as well. In this graphical model we assume
-    that the scene is being observed from left to right, hence "2" occludes "6"
-    and "5" and "5" occludes "1". The bounding box detection is represented by
-  $\mathbf{d}_{bb}^i(t)$ and the statistical dependencies are represented by
-  red lines. (2) Point tracks ($\Energy{track}$): Since occlusion is also
-  included in modeling point tracks energy we have similar interdependencies
-  for point tracks energy. The available point tracks are modeled by
-  $\mathbf{u}(t)$. (3) Collision ($\Energy{coll}$) : The collision energy
-  mathematically is a dense graph between all the TP but here we represent
-  collision among only those TP that are near enough to have a significant
-collision energy. (4) Orientation from detection ($\Energy{ori}$) (5) Orientation from lane (and map) information ($\Energy{lane}$)}
-  \label{fig:graphmodel}
-\end{figure}
-
-\section{Related Work}
-TODO:
-\vfill
-\pagebreak
-Related work continued
-\vspace{15cm}
-
-\section{Problem Definition}
+\section{Overview of Problem and Our Approach}
 TODO:
@@
 
-\section{Notation}
+\paragraph{Notation}
 
@@
 %%%%%%%%% BODY TEXT
-\section{The Model}
+\paragraph{The Model}
 
@@
 \end{multline}
-
-\section{Modeling traffic participants}
-\label{sec:TPmodel}
-Following standard model of occupancy in 3D reconstruction community, we model
-the TP's as high occupancy regions in space. We model the
-uncertainty in occupancy equivalent of transparency i.e. the regions that are
-more certain to be occupied are viewed as relatively more opaque then other
-regions. Based on this intuition we model TP's translucent
-ellipsoids whose opacity is maximum at the center and drops off away from the
-center. More specifically we model, the occupancy of a TP as a
-logistic function,
-
-\begin{align}
-   \occf = L(\mathbf{x}; \pos{i}{t}, \Sigma_i)
-\end{align}
-where $L(.)$ is the logistic function defined by
-\begin{align}
-  L(\mathbf{x}; \pos{i}{t}, \Sigma_i) = \frac{1}{
-    1 + e^{-k(1 - d(\mathbf{x},\pos{i}{t}))}
-    }
-\end{align}
-where $d(\mathbf{x},\pos{i}{t}) =
-(\mathbf{x}-\pos{i}{t})^\top\Sigma_i(\mathbf{x}-\pos{i}{t})$ and $k =
-10\ln{49}$. $k$ is chosen such that $L(.) = 0.98$ when $d(.) =
-0.9$. $\Sigma_i$ determines the spread of the ellipsoid and depends on the
-dimensions of the TP. Please refer to supplementary material 
-for computation of $\Sigma_i$ from TP's dimensions.
-
-We model the probability of a point $\mathbf{x}_j$ on a object $i$ getting successfully
-observed in a camera image at point $\trackpj{t}$ is dependent up two factors,
-(1) reflection and (2) transmission through intermediate space. The reflection
-part ensures that there is an object to reflect a point at a certain region in
-the 3D space while transmission part models occlusion.
-\begin{align}
-  P^{(ij)}_{\text{observation}} = P^{(ij)}_{\text{reflection}}P^{(j)}_{\text{transmission}}
-\end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Reflection probability}
-For Lambertian reflection we replace the surface normal with the
-gradient of occupancy.
-%
-\begin{align}
-  \Prefl = (\max \{0, \nabla \occf^\top
-  \hat{\mathbf{r}_j}\})^2
-\end{align}
-%
-where $\ray =
-\frac{K^{-1}\trackpj{t}}{\|K^{-1}\trackpj{t}\|}$ is unit vector in the
-direction of ray. The gradient in the direction opposite to ray yields -ve
-probability which needs to be clipped off. Squaring the function keep it
-smooth near zero.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Transmission probability}
-A model for transmission of light through a material of thickness $x$,
-density $\rho$ and opacity $k_o$ is given by Beer-Lambert law 
-%
-\begin{align}
-  I(x) = I_0e^{-k_o\rho x}
-\end{align}
-%
-
-Since both opacity and density are represented by the occupancy function
-$\occftot = \sum_i \occf$, and also the domain of our $\occftot$ is $[0, 1]$ instead of $[0,
-\infty]$ as in case of $k_o$; we replace $e^{-k_o\rho}$ by the transparency
-function $1 - \occftot$. So the transmission probability over a small distance
-$d\lambda$ is given by
-%
-\begin{align}
-  P_{\text{transmission}}(\lambda + d\lambda) =
-  P_{\text{transmission}}(\lambda) (1-\occftot)^{d\lambda}
-\end{align}
-%
-
-For a given 3D point $\mathbf{x}_j = \lambda \ray$, the probability that the
-point $\trackpj{t}$ is reflected from a distance $\lambda$ is given by
-
-\begin{align}
-  %P^{(j)}_{\text{observation}}(\lambda) &= P_{\text{reflection}}
-  \Ptrans &=
-  \prod_{0}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda} %\\
-  %= \max \{ 0, (\nabla f_{occ}&(\lambda \ray)^\top \ray) \}
-  %\prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
-  \label{eq:ptrans-integral}
-\end{align}
-where $\prod_{0}^{\lambda}$ represents the \emph{product integral} from $0$ to
-$\lambda$.
-
-In practice, the integral for transmission probability
-\eqref{eq:ptrans-integral} is difficult to compute even numerically. So we
-choose a product of sigmoid function that approximates the behaviour of
-transmission probability,
-%
-\begin{align}
-\label{eq:evalCumulativePtrans}
-  \Ptrans &= \prod_i L_u(\trackp{t}; \muiu,\Sigmaiu)L_{\lambda}(\lambda; \mu^i_d)
-\end{align}
-%
-where $L_u(.)$ is sigmoid in image domain with $\mu^i_u$ and $\Sigma^i_u$
-representing the elliptical projection of $i^{th}$ TP.
-$L_{\lambda}(.)$ is sigmoid in the depth domain with $\mu^i_d$ as the mean
-depth of the $i^{th}$ TP.
-%
-\begin{align}
-  L_u(\mathbf{u}; \muiu,\Sigmaiu) &= \frac{1}{
-    1 + e^{-k_u(1 - (\mathbf{u} - \muiu)^\top\Sigmaiu(\mathbf{u} -
-    \muiu))}
-  }
-  \\
-  L_{\lambda}(\lambda; \mu^i_d) &= \frac{1}{
-    1 + e^{-k_d(\lambda - \mu^i_d)}
-}
-\end{align}
-%
-
-\begin{comment}%% Comment
-  A product integral is a simple integral in log domain
-  \begin{align}
-    \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} =
-    e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
-  \end{align}
-\end{comment}%% Comment
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Energies}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We explain energies in this section
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Point tracks energy with occlusion}
-\label{sec:totalContPtTracksEnergy}
-We model continuous point tracks energy with explicit occlusion reasoning as
-the expected re-projection error over the association probability,
-
-\begin{multline}
-  \Energy{traci}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \\
-    \sum_{i=1}^{N} 
-    %\sum_{t = s_i}^{e_i}
-    \sum_{j = 1}^{M}
-    \int_1^\infty \assocP\Ereproj(\lambda) d\lambda
-\end{multline}
-where $\assocP$ is the association probability of
-$j$\textsuperscript{th} point with $i$\textsuperscript{th} TP at depth $\lambda$
-and $\Ereproj(\lambda)$ is the re-projection error given by
-%
-\begin{align}
-  \assocP &= \Prefl\Ptrans\\
-  \Ereproj(\lambda) &= \left\|\trackpj{t+1} - \projectionOft{\invProjectionOf{\trackpj{t}, \lambda}}\right\|^2 .
-  \label{eq:reprojerror}
-\end{align}
-
-The  $\projectionOf{.}$ and $\invProjectionOf{.}$ denote the projection and
-inverse projection functions that project 3D point to camera image and vice
-versa. Note that inverse projection $\invProjectionOf{.}$ depend on both the
-point $\trackp{t}$ and the unknown depth $\lambda$. Also note that the inverse projection is dependent on TP pose at time $t$ while the projection depends on pose at time $t+1$ which can be different.
-
-\begin{comment}
-  \subsubsection{Occupancy function}
-  Assuming occupancy to be a
-  probability distribution over 3D space. For each TP the
-  occupancy is modeled as a logistic function 
-  \begin{align}
-     \occf = L(\mathbf{x}; \pos{i}{t}, \Sigma_i)
-  \end{align}
-  where $L(.)$ is the logistic function defined by
-  \begin{align}
-    L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i) = \frac{1}{
-      1 + e^{-k(1 - d(\mathbf{x},\pos{i}{t-1}))}
-      }
-  \end{align}
-  where $d(\mathbf{x},\pos{i}{t-1}) =
-  (\mathbf{x}-\pos{i}{t-1})^\top\Sigma_i(\mathbf{x}-\pos{i}{t-1})$ and $k =
-  10\ln{49}$. $k$ is chosen such that $L(.) = 0.98$ when $d(.) =
-  0.9$
-  % Once we have our distribution over $\lambda$, $\lambdadist$ we can compute the
-  % reprojection of $\trackpj{t-1}$ over image in time $t$ as a function of
-  % $\lambda$. Let
-\end{comment}
-
-\begin{comment}
-  \subsubsection{Approximations}
-  Reflection probability of $i$th TP is easy to compute
-  analytically 
-  \begin{multline}
-    \Prefl =
-    (\max \{ 0, \nabla \occf^\top \ray \})^2 \\
-    = (\max \{ 0, \nabla \occfxi^\top\ray \})^2
-    \label{eq:analytic-prefl}
-  \end{multline}
-  where 
-  \begin{multline}
-    \nabla \occfxi^\top\ray \\=
-    \nabla k\dishort \sech^2\left(\frac{k}{2}\dishort\right)
-  \end{multline}
-  where $\dishort = 1-d(\mathbf{x}, \pos{i}{t-1})$ is a signed distance measure
-  from the contour of the ellipsoid where $d(\mathbf{x}, \pos{i}{t-1})$ is 1.
-
-  However, the transmission probability needs to be approximated.  
-  %
-  % \subsubsection{Computing $\Prefl$ and $\Ptrans$}
-  % Focusing on  $\nabla \occfxi$ 
-  % 
-  % \begin{multline}
-  %   \nabla \occfxi =\\
-  %   \frac{-k\nabla d(\mathbf{x}, \pos{i}{t-1})e^{-k(1-d(\mathbf{x}, \pos{i}{t-1}))}}{
-  %     (1 + e^{-k(1-d(\mathbf{x}, \pos{i}{t-1}))})^2
-  %   } \\ 
-  %   = -k\nabla d(\mathbf{x}, \pos{i}{t-1})\sech^2\left(\frac{k}{2}(1-d(\mathbf{x},
-  %   \pos{i}{t-1}))\right)
-  %   \\
-  %   = \nabla k\dishort \sech^2\left(\frac{k}{2}\dishort\right)
-  % \end{multline}
-  % where $\dishort = 1-d(\mathbf{x}, \pos{i}{t-1})$ is a signed distance measure
-  % from the contour of the ellipsoid where $d(\mathbf{x}, \pos{i}{t-1})$ is 1.
-  % Focusing on $\nabla d(.)$
-  % 
-  % \begin{align}
-  %   \nabla d(\mathbf{x}, \pos{i}{t-1}) = 2\Sigma_i(\mathbf{x} - \pos{i}{t-1})
-  % \end{align}
-  % Back to \eqref{eq:analytic-prefl}
-  % 
-  % \begin{multline}
-  %   (\max \{ 0, \nabla \occf^\top \ray \})^2 = \\
-  %   \sech^4\left(\frac{k}{2}\dishort\right) 
-  %   (\max \{ 0 , \nabla k\dishort^\top\ray\})^2
-  % \end{multline}
-  % 
-  % The probability is simply $\sech^2(.)$ scaled by gradient of ellipsoid
-  % $\nabla k\dishort$ projected in the ray direction $\ray$.
-  % 
-  % \begin{align}
-  %   \Ptrans = 
-  %   e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
-  % \end{align}
-  % \begin{multline}
-  % \int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}
-  % =  \\
-  % \int_{1}^{\lambda} \ln{\left(1 - \sum_i \occfi\right)}{d\lambda}
-  % \end{multline}
-  % 
-  % The above integral is very difficult to approximate or compute analytically.
-  So based on intuition, we approximate the $\Ptrans$ by following function
-  \begin{align}
-  \label{eq:evalCumulativePtrans}
-    \Ptrans &= \prod_i L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)L_{\lambda}(\lambda; \mu^i_d)\\
-    L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u) &= \frac{1}{
-      1 + e^{-k_u(1 - (\mathbf{u} - \mu^i_u)^\top\Sigma^i_u(\mathbf{u} -
-      \mu^i_u))}
-    }
-    \\
-    L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d) &= \frac{1}{
-    1 + e^{-k_d(\lambda - \mu^i_d(\mathbf{u}))}
-  }
-  \end{align}
-  where 
-  \begin{align}
-    \mu_u^i &= \projectionOf{\pos{i}{t-1}} \label{eq:muiudef}\\
-    \Sigma_u^i &= \projectionOf{\Sigma_i} \label{eq:sigmauidef}\\
-    \mu^i_d(\mathbf{u}) &= \relp{i}{t}\\
-    k_u &= 10\log(49)\\
-    k_d &= \frac{\log(49)}{\sqrt{h^2 + l^2 + w^2}}
-    \label{eq:ptransmissionInit}
-  \end{align}
-  is the distance of the centre of the TP from the camera.
-
-  % $\mu^i_d(\mathbf{u}) = \min_{\lambda} d^2_i(\lambda K^{-1}\mathbf{u})$.
-  % $\mu^i_d(\mathbf{u})$ is the closest point to the unit contour of ellipsoid.
-  % If there are multiple such points, the point closest to the camera is taken as
-  % $\mu^i_d(\mathbf{u})$
-
-  The association probability becomes
-
-  \begin{multline}
-    \assocP = 
-      \sech^4\left(\frac{k}{2}\dishort\right)
-      (\max \{ 0, \nabla k\dishort^\top\ray \})^2\\
-    \prod_i \Lu
-      \Llambda \\
-      \label{eq:assocCoeffEval}
-  \end{multline}
-
-  So the energy becomes
-
-  \begin{multline}
-    \label{eq:integrand}
-    \Energy{track}(.) = 
-      \sum_{i = 1}^N
-      \sum_{j = 1}^{M}
-      \int_1^{\infty}
-      \assocP
-      \Ereproj(\lambda)
-      d\lambda
-  \end{multline}
-  where $x = \lambda \ray$ and $\Ereproj(\lambda) = \|\trackpj{t} -
-  f^i_{reproj}(\trackpj{t-1}, \lambda)\|^2$ is reprojection error which is a
-  quadratic in $\lambda$
-
-  The integral in the above expression is computed numerically.
-\end{comment}
-
-\subsection{Object detection energy with occlusion}
-
-Object detection is usually followed by non-maximal suppression that results in
-discarding similar bounding boxes. When we are jointly optimizing detections
-with other cues, it is not usually desirable to go with a single bounding box.
-Hence, we keep all the bounding box detections by approximating them with
-multi-modal sum of Gaussian like logistic functions. We fit the parametric function of the form 
-%
-\begin{align}
-  S(\bb{i}) = \sum_k A_k \exp(-(\bb{i}-\mu^{(d)}_k)^\top \Sigma^{(d)-1}_k
-  (\bb{i}-\mu^{(d)}_k))
-\end{align}
-%
-to detection scores, by non-linear error minimization with initialization from
-non-maximal suppressed outputs. Here $\mu^{(d)}_j$ is one of the $k$ modes as a
-4D vector representing a single bounding box as $[\minx, \miny, \maxx,
-\maxy]^\top$. The optimization is constrained with symmetry and positive
-definiteness of $\Sigma^{(d)-1}_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
-
-\subsubsection{Detection scores with occlusion reasoning} 
-With our model of $\Ptrans$ described in Section \ref{sec:TPmodel}, we can
-compute the probability of a point $\mathbf{u}$ on image be occluded assuming
-the point is on TP $i$ with mean depth $\mu^{(i)}_d$ as
-\begin{align}
-  O_{i}(\mathbf{u}, \mu^{(i)}_d) = 1 - \Ptransmud \enspace .
-\end{align}
-
-If we a portion of our proposed detection bounding box is known to be occluded,
-then we would like to decrease the confidence in the detection score about the
-localization of that end of the object. Assuming that the occlusion is often on
-the boundary of detection bounding boxes, we want to decrease our confidence on
-the mean detection boundaries around the occluded boundaries. 
-One of the simplest ways will be to scale the appropriate diagonal element of
-$\Sigma_j$ by an appropriate scaling factor proportional to occlusion. But this
-does not model appropriate how does occlusion affects the non diagonal terms.
-Hence, we choose a covariance addition model where we compute a occlusion
-covariance matrix, that provides a measure of occlusion in each direction.
-
-To re-model our detection scores scaled by continuous occlusion we sample
-$O_{i}(\mathbf{u}, \mu^{(i)}_d)$ at the hypothesized detection boundaries from
-GMM $S(.)$ and we augment the detection boundary covariance matrix by
-$\mathcal{P}_{j} = \rho_{j}\rho_{j}^\top$ where $\rho_{j} = O_{j}(\mathbf{u},
-\mu^{(i)}_d)$. The new covariance matrix in detection score is given by 
-%
-\begin{align}
-  \Sigma'^{(d)}_j = \mathcal{P}_{j} + \Sigma^{(d)}_j
-\end{align}
-%
-The detection scores GMM with occlusion is given by replacing the covariance
-matrix
-%
-\begin{multline}
-  S'(\bb{i}) =\\
-  \sum_j A_j \exp(-(\bb{i}-\mu^{(d)}_j)^\top \Sigma'^{(d)-1}_j
-  (\bb{i}-\mu^{(d)}_j))
-\end{multline}
-
-The energy of detection scores is simply take to be the inverse of the detection score.
-\begin{align}
-  \Energy{detect}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}
-\end{align}
-
-\subsection{Lane energy}
-\label{sec:laneEnergy}
- The lanes are modeled as splines. Here we assume that the confidence in lane
- detection is decreases as the distance from the lane center increases.  The
- energy is given by the dot product between car orientation and tangent to the
- lane at that point.
-
-\begin{multline}
-  \label{eq:laneOrientationEnergy}
-  \Energy{lane} = \\
-  \sum_{m \in M_{\text{close}}}
-  (1 - \ori{i}{t} \cdot \text{TAN}(L_{m}(k), \pos{i}{t}) )
-\LaneUncertainty{\pos{i}{t}}
-\end{multline}
-where $M_{\text{close}} = \{m : \text{DIST}(L_{m}(k), \pos{i}{t}) < 50\} $ is
-the set of nearby lanes and 
-\begin{multline}
-\LaneUncertainty{\pos{i}{t}} = \\
-  \frac{1}{1 + exp(-q(w_{\text{road}} - \text{DIST}(L_{m}(k), \pos{i}{t})))}
-\end{multline}
-for some constant $w_{\text{road}}$ that represents the width of the road.
-
-\subsection{Transition probability}
-Dynamics constraints should not only enforce smooth trajectories, but also the
-holonomic constraints.  The following energy adds a penalty if the change in
-position is not in direction of previous orientation.
-
-\begin{align}
-  \label{eq:totalPosTransitionEnergy}
-  \Energy{dyn-hol} = 1 - \ori{i}{t-1} \cdot (\pos{i}{t} - \pos{i}{t-1})
-\end{align}
-
-The following energy adds a penalty for change in position and orientation
-but a penalty for change in velocity is much better approximation. However, in
-a Markovian setting that would mean extending the state space of the car to
-include velocity.
-
-\begin{align}
-  \Energy{dyn-ori} &= \|\ori{i}{t} - \ori{i}{t-1}\|^2\\
-  \Energy{dyn-vel} &= \|(\pos{i}{t} - 2\pos{i}{t-1}) + \pos{i}{t-2}\|^2
-\end{align}
-
-As a result the dynamics are modeled by weighted combination of holonomic
-constraint and smoothness constraints.
-
-\begin{align}
-  \WEnergy{dyn} &= \WEnergy{dyn-hol} + \WEnergy{dyn-ori} + \WEnergy{dyn-vel}
-\end{align}
-
-\subsection{Collision energy}
-
-Bhattacharya coefficient $\int_a^b\sqrt{p(x)q(x)}dx$ is a measure of similarity
-of two distributions $p(x)$ and $q(x)$. If we represent TPs as gaussians in
-Birds eye view (BEV), then similarity is a measure of collision. Exactly
-overlapping distribution results in coefficient as 1. 
-%The analytical form of
-%Bhattacharya coefficient has been taken from
-%\url{http://like.silk.to/studymemo/PropertiesOfMultivariateGaussianFunction.pdf}
-
-\begin{multline}
-  \label{eq:collisionEnergyHellingerDistance}
-  \EnergyCol =\\ -\log\left(
-  A_{ij}
-  e^{-\frac{1}{8}
-    \left(\pos{i}{t} - \pos{j}{t}\right)^\top
-    P^{-1}
-    \left(\pos{i}{t} - \pos{j}{t}\right)
-    }
-    \right)
-\end{multline}
-where 
-\begin{align}
-  A_{ij} &= \frac{|\Sigma_i|^\frac{1}{4}|\Sigma_j|^\frac{1}{4}}
-  {|P|^\frac{1}{2}}\\
-  P &= \frac{1}{2}\Sigma_i + \frac{1}{2}\Sigma_j\\
-\Sigma_i^{-1} &= R^\top_{\ori{i}{t}} \begin{bmatrix} 2/l_i & 0 \\ 0 & 2/w_i \end{bmatrix}
-R_{\ori{i}{t}}
-\end{align}
-
-\subsection{Size Prior}
-
-Prior can include among many other things the size prior on the car.
-
-\begin{align}
-  \label{eq:totalSizeEnergy}
-  \Energy{prior} &= (\dimsn{i} - \expDimsn)^\top\Sigma_{\expDimsn}^{-1}(\dimsn{i} -
-  \expDimsn)
-\end{align}
-
-where $\expDimsn$ is the mean TP dimensions and
-$\Sigma_{\expDimsn}$ is the correspondence covariance matrix.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Association error evaluation}
-
-To verify the correctness of our association probability $\assocP$ we perform
-association error experiment that compare the accuracy of point track
-association with TPs with that of bounding box baseline method.
-
-% \begin{align}
-%   f^{i}_{reproj}&(\trackpj{t-1}, \lambda) =
-%   \projectionOf{\invProjectionOf{\trackpj{t-1}}}\\
-%   %&= K(R^i_t ((R^i_{t-1})^\top\lambda \ray - (R^i_{t-1})^\top T_{t-1}) + T_{t})\\
-%   &= \frac
-%   {p_{1:2}\lambda + q_{1:2}}
-%   {p_{3}\lambda + q_{3}}
-% \end{align}
-% where $p_{1:3} = KR^i_t(R^i_{t-1})^\top\ray$ and
-% $q_{1:3} = KR^i_t(R^i_{t-1})^\top T_{t-1} + KT_t$
-% 
-% Now that we have an association from TP $i$ to point track $j$ through
-% $\lambda$, we can come up with an association probability
-% \begin{align}
-%    \assocP &= \frac{(\max \{ 0, \nabla \occf^\top
-% \ray \})^2 }{P_{\text{reflection}}}\lambdadist\\
-% &=(\max \{ 0, \nabla \occf^\top \ray \})^2
-%   \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
-% \end{align}
-
-Note that the fraction $\assocP$ although called association probability does
-not capture the entire information that we have available for compute
-association of points to tracks. This above fraction is the association
-probability given the hypothesized parameters of TP model.
-
-To compute the association probability between TP $i$ and
-point track $j$ we must use re-projection error as well. When the association
-$i$ and $j$ is right and the point of reflection is at depth $\lambda$ the
-re-projection error must be zero \eqref{eq:reprojerror}, otherwise the error
-becomes a measure of distance from the true solution.
-The error terms can be converted to probability domain by considering the error
-term as negative log of probability
-
-\begin{align}
-  P^{(ij)}_{\text{assoc by reproj}}(\lambda) = \frac{1}{Z}\exp(-\Ereproj(\lambda))
-\end{align}
-
-Using both the evidence terms we can write probability of association as
-\begin{align}
-  P^{(ij)}_{\text{assoc}} = \frac{1}{Z'}\int_0^{\infty} \assocP \frac{1}{\sqrt{2\pi}}\exp(-\Ereproj(\lambda))d\lambda
-  \label{eq:prob-assoc}
-\end{align}
-
-Once we have the probability of association we can compute the best possible
-assignment of TP for each point. The points having very small association
-probability are assigned to the background,
-\begin{align}
-  i^*_{j} = \argmin_{i} \int_0^\infty \assocP \Ereproj(\lambda) d\lambda
-\end{align}
-
-We use bounding box based assignment of point tracks to TPs as the baseline.
-For the regions where the bounding boxes overlap, we assign the points to the
-TP that has smaller mean depth then the competing bounding box.
-
-{\small
-\bibliographystyle{ieee}
-\bibliography{model}
-}
-\end{document}

### 2014-11-10 CVPR/Source/occlusion.tex
Section on occlusion modeling

@@
-\section{Modeling traffic participants}
+\section{Occlusion-Aware 3D Object Modeling}
 \label{sec:TPmodel}
-Following standard model of occupancy in 3D reconstruction community, we model
-the TP's as high occupancy regions in space. We model the
-uncertainty in occupancy equivalent of transparency i.e. the regions that are
-more certain to be occupied are viewed as relatively more opaque then other
-regions. Based on this intuition we model TP's translucent
-ellipsoids whose opacity is maximum at the center and drops off away from the
-center. More specifically we model, the occupancy of a TP as a
-logistic function,
 
+In this section, we introduce our representation of 3D traffic participants and our modeling of object-object occlusion relationships.
+
+\paragraph{Occupancy model for traffic participants}
+Intuitively, we consider traffic participants to be regions of 3D space with a high probability of occupancy.
+We model the uncertainty in occupancy as a translucency function, with regions more likely to be occupied by an object considered more opaque, while regions more likely to be free space are more transparent.
+Based on this intuition, we model objects as translucent 3D ellipsoids whos opacity is maximum at the center and falls off towards the edges.
+In particular, we model the occupancy at location $\bx$ corresponding to a traffic participant $i$ centered at $\bp$ as:
 \begin{align}
-   \occf = L(\mathbf{x}; \pos{i}{t}, \Sigma_i)
+  \occft{\bx} = \cL(\bx; \bp, \bSigma)
 \end{align}
-where $L(.)$ is the logistic function defined by
+where $\cL(\cdot)$ is the logistic function given by
 \begin{align}
-  L(\mathbf{x}; \pos{i}{t}, \Sigma_i) = \frac{1}{
-    1 + e^{-k(1 - d(\mathbf{x},\pos{i}{t}))}
-    }
+  L(\bx; \bp, \bSigma) = \frac{1}{1 + e^{-k(1 - d(\mathbf{x},\bp))}},
 \end{align}
-where $d(\mathbf{x},\pos{i}{t}) =
-(\mathbf{x}-\pos{i}{t})^\top\Sigma_i(\mathbf{x}-\pos{i}{t})$ and $k =
-10\ln{49}$. $k$ is chosen such that $L(.) = 0.98$ when $d(.) =
-0.9$. $\Sigma_i$ determines the spread of the ellipsoid and depends on the
-dimensions of the TP. Please refer to supplementary material 
-for computation of $\Sigma_i$ from TP's dimensions.
+with $d(\bx, \bp) = (\bx-\bp)^\top\bSigma(\bx-\bp)$ being the Mahalanobis distance.
+We set $k = 10\ln{49}$ as the value that allows the logistic function $\cL$ to drop to $0.98$ at a distance $d = 0.9$ from the object center.
+The spread of the ellipsoid, determined by $\bSigma_i$, depends of the dimensions of the traffic participant.
+Please refer to the additional material for computation of $\bSigma$ from object dimensions.
 
-We model the probability of a point $\mathbf{x}_j$ on a object $i$ getting successfully
-observed in a camera image at point $\trackpj{t}$ is dependent up two factors,
-(1) reflection and (2) transmission through intermediate space. The reflection
-part ensures that there is an object to reflect a point at a certain region in
-the 3D space while transmission part models occlusion.
+\paragraph{Image formation}
+Given the above occupancy representation of the scene, a point on an object is observed in the camera when precisely two conditions are satisfied.
+First, the backprojected ray from the observed image pixel is transmitted through free space until it reaches the object.
+Second, the ray encounters an opaque enough object surface and is reflected.
+More formally, the probability of observation of a point $\bx_j$ on object $O_i$ is given by
 \begin{align}
-  P^{(ij)}_{\text{observation}} = P^{(ij)}_{\text{reflection}}P^{(j)}_{\text{transmission}}
+  P^{ij}_{\textit{observation}} = P^{ij}_{\textit{reflection}}P^{j}_{\textit{transmission}}
 \end{align}
+The reflection term ensures the presence of an object to constitute the observation, while the transmission probability allows us to model occlusions.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Reflection probability}
-For Lambertian reflection we replace the surface normal with the
-gradient of occupancy.
+\paragraph{Reflection probability}
+Consider a 3D point $\bx_j$ observed in the image at pixel $\bu_j$.
+Let $\ray = \displaystyle\frac{\bK^{-1}\bu_j}{\lVert \bK^{-1}\bu_j \rVert}$ be the corresponding unit vector along the backprojected ray from the camera center.
+Then, the probability of reflection at depth $\lambda$ along the ray $\ray$, by an object $O_i$, is determined by the object's gradient of the occupancy function $f_{occ}^i$:
+\begin{align}
+  P^{ij}_{\textit{reflection}} (\lambda) = (\max \{0, \nabla {f^i_{occ}}(\bx_j)^\top \ray \})^2
+\end{align}
+The $\max \{ \}$ ensures that the negative probability due to gradient in the direction opposite to ray is clipped off and squaring the function allows it to be smooth near zero.
+We note that in the extreme case of an object object, the above reverts to a (squared) Lambertian reflection.
+
+\paragraph{Transmission probability}
+A model for transmission of light through a material of thickness $\alpha$, density $\rho$ and opacity $\beta$ is given by the Beer-Lambert Law:
+\begin{align}
+I(x) = I_0 e^{-\beta\rho\alpha}.
+\end{align}
+%
+In our formulation of scene occupancy, both opacity and density at a scene point $\bx_j$ are encapsulated within the total occupancy function $\occftot = \sum_i \occf$.
+Further, the domain of our ocupancy function $\occftot$ is $[0, 1]$ instead of $[0, \infty)$ for opacity $\beta$.
+Thus, we replace $e^{-\beta\rho}$ by the transparency function $1 - \occftot$ and consequently, the transmission probability over a small distance $d\lambda$ is given by
 %
 \begin{align}
-  \Prefl = (\max \{0, \nabla \occf^\top
-  \hat{\mathbf{r}_j}\})^2
+  \!\!\!\! P_{\textit{transmission}}(\lambda + d\lambda) = P_{\textit{transmission}}(\lambda) (1-\occftot)^{d\lambda}.
 \end{align}
 %
-where $\ray =
-\frac{K^{-1}\trackpj{t}}{\|K^{-1}\trackpj{t}\|}$ is unit vector in the
-direction of ray. The gradient in the direction opposite to ray yields -ve
-probability which needs to be clipped off. Squaring the function keep it
-smooth near zero.
+For an image point $\bu_j$ to correspond to a 3D point $\bx_j$ at depth $\lambda$ along the backprojected ray $\ray$, the ray must be transmitted through space with the probability
+\begin{align}
+P^j_{\textit{transmission}}(\lambda) = \prod_{0}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda},
+\label{eq:ptrans-integral}
+\vspace{\eqs}
+\end{align}
+where $\displaystyle\prod_{0}^{\lambda}$ represents the \emph{product integral} from $0$ to $\lambda$.\footnote{A product integral is a simple integral in log domain: 
+\vspace{-0.2cm}
+\begin{equation}
+\prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} = e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}. \nonumber
+\end{equation}
+}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Transmission probability}
-A model for transmission of light through a material of thickness $x$,
-density $\rho$ and opacity $k_o$ is given by Beer-Lambert law 
+In practice, the integral for transmission probability \eqref{eq:ptrans-integral} is difficult to compute even numerically.
+So we choose a parameterization in the form of a product of sigmoid functions, which is a reasonable approximation to the behaviour of the transmission probability:
 %
 \begin{align}
-  I(x) = I_0e^{-k_o\rho x}
+P^j_{\textit{transmission}}(\lambda) = \prod_i \cL_u (\bu; \bmu_i, \bGamma_i^{-1}) \cL_{\lambda}(\lambda; \nu_i),
+\label{eq:evalCumulativePtrans}
+\end{align}
+%
+where $\cL_u(.)$ is sigmoid in image domain, with $\bmu^i_u$ and $\bGamma_i$ representing the elliptical projection of object $O_i$ in the image and $\cL_{\lambda}(.)$ is sigmoid in the depth domain with $\nu_i$ the mean depth of object $O_i$.
+That is,
+%
+\begin{align}
+\cL_u(\bu; \bmu_i, \bGamma_i^{-1}) &= \frac{1}{1 + e^{-k_u(1 - (\bu - \bmu_i)^\top \bGamma_i^{-1} (\bu - \bmu_i))}} \\
+\cL_{\lambda}(\lambda; \nu_i) &= \frac{1}{1 + e^{-k_d(\lambda - \nu_i)}}
 \end{align}
@@
 
-Since both opacity and density are represented by the occupancy function
-$\occftot = \sum_i \occf$, and also the domain of our $\occftot$ is $[0, 1]$ instead of $[0,
-\infty]$ as in case of $k_o$; we replace $e^{-k_o\rho}$ by the transparency
-function $1 - \occftot$. So the transmission probability over a small distance
-$d\lambda$ is given by
-%
-\begin{align}
-  P_{\text{transmission}}(\lambda + d\lambda) =
-  P_{\text{transmission}}(\lambda) (1-\occftot)^{d\lambda}
-\end{align}
-%
+Thus, we have modeled the transmission probability to effectively capture the effect of occlusion due to all traffic participants in a scene that lie along a particular ray.
+We reiterate that our reflection and transmission probabilities are continuous functions, which allows us to define continuous energy functions for association and 3D object localization, as described in the next section.
 
-For a given 3D point $\mathbf{x}_j = \lambda \ray$, the probability that the
-point $\trackpj{t}$ is reflected from a distance $\lambda$ is given by
+%% We model the probability of a point $\mathbf{x}_j$ on a object $i$ getting successfully
+%% observed in a camera image at point $\trackpj{t}$ is dependent up two factors,
+%% (1) reflection and (2) transmission through intermediate space. The reflection
+%% part ensures that there is an object to reflect a point at a certain region in
+%% the 3D space while transmission part models occlusion.
+%% \begin{align}
+%%   P^{(ij)}_{\text{observation}} = P^{(ij)}_{\text{reflection}}P^{(j)}_{\text{transmission}}
+%% \end{align}
 
-\begin{align}
-  %P^{(j)}_{\text{observation}}(\lambda) &= P_{\text{reflection}}
-  \Ptrans &=
-  \prod_{0}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda} %\\
-  %= \max \{ 0, (\nabla f_{occ}&(\lambda \ray)^\top \ray) \}
-  %\prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
-  \label{eq:ptrans-integral}
-\end{align}
-where $\prod_{0}^{\lambda}$ represents the \emph{product integral} from $0$ to
-$\lambda$.
+%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% \subsection{Reflection probability}
+%% For Lambertian reflection we replace the surface normal with the
+%% gradient of occupancy.
+%% %
+%% \begin{align}
+%%   \Prefl = (\max \{0, \nabla \occf^\top
+%%   \hat{\mathbf{r}_j}\})^2
+%% \end{align}
+%% %
+%% where $\ray =
+%% \frac{K^{-1}\trackpj{t}}{\|K^{-1}\trackpj{t}\|}$ is unit vector in the
+%% direction of ray. The gradient in the direction opposite to ray yields -ve
+%% probability which needs to be clipped off. Squaring the function keep it
+%% smooth near zero.
 
-In practice, the integral for transmission probability
-\eqref{eq:ptrans-integral} is difficult to compute even numerically. So we
-choose a product of sigmoid function that approximates the behaviour of
-transmission probability,
-%
-\begin{align}
-\label{eq:evalCumulativePtrans}
-  \Ptrans &= \prod_i L_u(\trackp{t}; \muiu,\Sigmaiu)L_{\lambda}(\lambda; \mu^i_d)
-\end{align}
-%
-where $L_u(.)$ is sigmoid in image domain with $\mu^i_u$ and $\Sigma^i_u$
-representing the elliptical projection of $i^{th}$ TP.
-$L_{\lambda}(.)$ is sigmoid in the depth domain with $\mu^i_d$ as the mean
-depth of the $i^{th}$ TP.
-%
-\begin{align}
-  L_u(\mathbf{u}; \muiu,\Sigmaiu) &= \frac{1}{
-    1 + e^{-k_u(1 - (\mathbf{u} - \muiu)^\top\Sigmaiu(\mathbf{u} -
-    \muiu))}
-  }
-  \\
-  L_{\lambda}(\lambda; \mu^i_d) &= \frac{1}{
-    1 + e^{-k_d(\lambda - \mu^i_d)}
-}
-\end{align}
-%
+%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% \subsection{Transmission probability}
+%% A model for transmission of light through a material of thickness $x$,
+%% density $\rho$ and opacity $k_o$ is given by Beer-Lambert law 
+%% %
+%% \begin{align}
+%%   I(x) = I_0e^{-k_o\rho x}
+%% \end{align}
+%% %
 
-\begin{comment}%% Comment
-  A product integral is a simple integral in log domain
-  \begin{align}
-    \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} =
-    e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
-  \end{align}
-\end{comment}%% Comment
+%% Since both opacity and density are represented by the occupancy function
+%% $\occftot = \sum_i \occf$, and also the domain of our $\occftot$ is $[0, 1]$ instead of $[0,
+%% \infty]$ as in case of $k_o$; we replace $e^{-k_o\rho}$ by the transparency
+%% function $1 - \occftot$. So the transmission probability over a small distance
+%% $d\lambda$ is given by
+%% %
+%% \begin{align}
+%%   P_{\text{transmission}}(\lambda + d\lambda) =
+%%   P_{\text{transmission}}(\lambda) (1-\occftot)^{d\lambda}
+%% \end{align}
+%% %
+
+%% For a given 3D point $\mathbf{x}_j = \lambda \ray$, the probability that the
+%% point $\trackpj{t}$ is reflected from a distance $\lambda$ is given by
+
+%% \begin{align}
+%%   %P^{(j)}_{\text{observation}}(\lambda) &= P_{\text{reflection}}
+%%   \Ptrans &=
+%%   \prod_{0}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda} %\\
+%%   %= \max \{ 0, (\nabla f_{occ}&(\lambda \ray)^\top \ray) \}
+%%   %\prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
+%%   \label{eq:ptrans-integral}
+%% \end{align}
+%% where $\prod_{0}^{\lambda}$ represents the \emph{product integral} from $0$ to
+%% $\lambda$.
+
+%% In practice, the integral for transmission probability
+%% \eqref{eq:ptrans-integral} is difficult to compute even numerically. So we
+%% choose a product of sigmoid function that approximates the behaviour of
+%% transmission probability,
+%% %
+%% \begin{align}
+%% \label{eq:evalCumulativePtrans}
+%%   \Ptrans &= \prod_i L_u(\trackp{t}; \muiu,\Sigmaiu)L_{\lambda}(\lambda; \mu^i_d)
+%% \end{align}
+%% %
+%% where $L_u(.)$ is sigmoid in image domain with $\mu^i_u$ and $\Sigma^i_u$
+%% representing the elliptical projection of $i^{th}$ TP.
+%% $L_{\lambda}(.)$ is sigmoid in the depth domain with $\mu^i_d$ as the mean
+%% depth of the $i^{th}$ TP.
+%% %
+%% \begin{align}
+%%   L_u(\mathbf{u}; \muiu,\Sigmaiu) &= \frac{1}{
+%%     1 + e^{-k_u(1 - (\mathbf{u} - \muiu)^\top\Sigmaiu(\mathbf{u} -
+%%     \muiu))}
+%%   }
+%%   \\
+%%   L_{\lambda}(\lambda; \mu^i_d) &= \frac{1}{
+%%     1 + e^{-k_d(\lambda - \mu^i_d)}
+%% }
+%% \end{align}
+%% %
+
+%% \begin{comment}%% Comment
+%%   A product integral is a simple integral in log domain
+%%   \begin{align}
+%%     \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} =
+%%     e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
+%%   \end{align}
+%% \end{comment}%% Comment

### 2014-11-10 CVPR/Source/occlusion.tex
Started related works section

@@
 In this section, we introduce our representation of 3D traffic participants and our modeling of object-object occlusion relationships.
+We refer the reader to Figure [[FIGURE]] for an illustration of the proposed concepts.
 
@@
 \begin{align}
-  P^{ij}_{\textit{observation}} = P^{ij}_{\textit{reflection}}P^{j}_{\textit{transmission}}
+P^{ij}_{\textit{observation}} = P^{ij}_{\textit{reflection}}P^{j}_{\textit{transmission}}.
+\label{eq:imgform}
 \end{align}
-The reflection term ensures the presence of an object to constitute the observation, while the transmission probability allows us to model occlusions.
+The reflection probability ensures the presence of an object to constitute the observation, while the transmission probability allows us to model occlusions.
+The forms of these two functions are described next.
 
@@
 \label{eq:ptrans-integral}
-\vspace{\eqs}
 \end{align}
@@
 We reiterate that our reflection and transmission probabilities are continuous functions, which allows us to define continuous energy functions for association and 3D object localization, as described in the next section.
+
+%\paragraph{Probabilistic occlusion levels}
+%With the above modeling and using \eqref{eq:imgform},
 

### 2014-11-10 CVPR/Source/related.tex
Started related works section

@@
 \label{sec:related}
+
+\paragraph{Occlusion handling}
+Several works in object detection consider occlusion by training a detector on visible parts of the object \cite{Gao_etal_2011,Wu_Nevatia_2007}.
+In recent years, object detectors have also considered occlusion reasoning using 3D cues, often learned from a dataset of CAD models \cite{Pepik_etal_2012,Pepik_etal_2013,Xiang_Savarese_2013}.
+By necessity, such frameworks are often a discrete representation of occlusion behavior, for example, in the form of a collection of occlusion masks derived from object configurations discretized over viewpoint.
+In constrast to these works, our occlusion modeling is also fully 3D, but allows for a continuous representation.
+Further, to derive 3D information, we do not use CAD models, rather we derive a probabilistic formulation based on physical insights.
+
+Occlusion handling in tracking \cite{Wu_Nevatia_2007,Milan_etal_2014}.
+
+\paragraph{3D localization and scene understanding}
+Occlusion handling in scene understanding \cite{Zia_etal_2013,Zia_etal_2014}.
+
+\paragraph{Multibody SFM}
+
+\paragraph{Motion segmentation}
 

### 2014-11-10 CVPR/Source/related.tex
Added bibliography items

@@
 Several works in object detection consider occlusion by training a detector on visible parts of the object \cite{Gao_etal_2011,Wu_Nevatia_2007}.
+Occlusion reasoning based on 2D image silhouettes is used to improve detection performance in \cite{Hsiao_Herbert_2012}.
 In recent years, object detectors have also considered occlusion reasoning using 3D cues, often learned from a dataset of CAD models \cite{Pepik_etal_2012,Pepik_etal_2013,Xiang_Savarese_2013}.
@@
 
-Occlusion handling in tracking \cite{Wu_Nevatia_2007,Milan_etal_2014}.
+Occlusion handling in tracking \cite{Kwak_etal_2012,Wu_Nevatia_2007,Milan_etal_2014}.
 
 \paragraph{3D localization and scene understanding}
-Occlusion handling in scene understanding \cite{Zia_etal_2013,Zia_etal_2014}.
+General \cite{Geiger2011, Geiger_etal_2014}.
+Occlusion handling in scene understanding works \cite{Wojek_etal_2013,Zia_etal_2013,Zia_etal_2014}.
 
-\paragraph{Multibody SFM}
+\paragraph{Motion segmentation and multibody SFM}
+\cite{Tron_Vidal_2007}
+\cite{Rao_etal_2010}
+\cite{Brox_Malik_2010}
+
+\cite{Schindler2006}
+\cite{Ozden_etal_2010}
+\cite{Namdev2012}
+\cite{Kundu_etal_2011}
 

### 2015-01-29 Paper/supplementary.tex
Added supplementary.tex

@@
 
-\begin{comment}
+  \section{Uncertainty addition in measurement}
   Consider that we have a set of measurements whose mean and variance are known $\mu = E(x)$ and $\Sigma = E ((x - \mu_x)(x - \mu_x)^\top)$. We want to know the
@@
   uncertainty associated with each point in the space.
-\end{comment}
 
@@
 
-\begin{comment}
-
+\section{Analytical attempt to integration}
   %%%%%%%%%%%%%%%% Analytical attempt to integration %%%%%%%%%%%%%%%%%%%%%
   \begin{align}
-
     E^i_{\text{reproj}}(\lambda) &= \left\|\trackpj{t} - \frac{p_{1:2}\lambda +
@@
   %%%%%%%%%%%%%%%% Analytical attempt to integration %%%%%%%%%%%%%%%%%%%%%
-\end{comment}
 

### 2015-01-29 CVPR/Source/related.tex

--- 2014-11-10 CVPR/Source/related.tex
@@
 
-\paragraph{Occlusion handling}
-Several works in object detection consider occlusion by training a detector on visible parts of the object \cite{Gao_etal_2011,Wu_Nevatia_2007}.
+\paragraph{Occlusion handling in detection}
+Several works in object detection consider occlusion by training a detector on visible parts of the object \cite{Gao_etal_2011}.
+Occlusion reasoning based on 2D image silhouettes is used to improve detection performance in \cite{Hsiao_Herbert_2012}.
+In contrast, our occlusion reasoning is based on 3D entities.
 In recent years, object detectors have also considered occlusion reasoning using 3D cues, often learned from a dataset of CAD models \cite{Pepik_etal_2012,Pepik_etal_2013,Xiang_Savarese_2013}.
@@
 
-Occlusion handling in tracking \cite{Wu_Nevatia_2007,Milan_etal_2014}.
+\paragraph{Occlusion handling in tracking}
+Occlusions have also been handled in tracking-by-detection frameworks by considering occluder patterns in the image \cite{Kwak_etal_2012,Wu_Nevatia_2007}.
+A notable exception is the work of Milan et al.~\cite{Milan_etal_2014} that explicits models occlusion in the continuous domain to determine a visibility for each object in multi-target tracking.
+However, the occlusion model in \cite{Milan_etal_2014} is essentially the overlap of image projections of a Gaussian representation of the object.
+Our occlusion modeling, however, is much more general in determining the probability of a point in space as belonging to an object.
+While it can also be used to determine a visibility ratio similar to \cite{Milan_etal_2014}, it can have far more general applications and can be quantitatively evaluated, as shown by our experiments on point track associations.
 
 \paragraph{3D localization and scene understanding}
-Occlusion handling in scene understanding \cite{Zia_etal_2013,Zia_etal_2014}.
+One of the central goals of 3D scene understanding is to localize the 3D positions and orientations of objects in complex scenes.
+For instance, using stereo imagery, several visual cues are combined in \cite{Geiger_etal_2014} to simultaneously determine object locations and a rough intersection topology.
+Similar to us, other works have also considered monocular frameworks.
+Notably, occlusions are explicitly handled in \cite{Wojek_etal_2013} by considering partial object detectors.
+A detailed part-based representation of objects based on annotated CAD models is used for monocular scene understanding in \cite{Zia_etal_2013,Zia_etal_2014}, which also allows reasoning about mutual occlusions between objects.
+In contrast to these works, our monocular framework uses a physical modeling of occlusion in continuous space, which makes it more general, extensible and amenable for continuous optimization.
 
-\paragraph{Multibody SFM}
-
-\paragraph{Motion segmentation}
+\paragraph{Motion segmentation and multibody SFM}
+An application for our occlusion modeling is to determine point track associations in scenes with multiple objects.
+For moving objects, this is within the purview of motion segmentation, which has been actively studied \cite{Tron_Vidal_2007,Rao_etal_2010}.
+This also motivates further applications such as object segmentation based on point trajectories \cite{Brox_Malik_2010}.
+Motion segmentation is also used within multibody structure from motion (SFM) frameworks \cite{Ozden_etal_2010,Kundu_etal_2011,Namdev2012}.
+In contrast to these works, our formulation does not distinguish between moving and static objects and also explicitly reasons about occlusions due to 3D object geometries for associating point tracks to individual objects.
 

### 2015-02-12 Paper/supplementary.tex
Added more description about fitting convex polyhedra to bounding box analytically.

@@
 
+\DeclareMathOperator{\diag}{diag}
+
 % 3D pose of the cars and ego motion
+\newcommand{\uv}[1]{\hat{\mathbf{#1}}}
 \newcommand{\pos}[2]{\mathbf{p}^{(#1)}(#2)}
@@
 
+\newcommand{\xymin}[1]{#1_{\text{min}}}
+\newcommand{\xymax}[1]{#1_{\text{max}}}
+\newcommand{\xmin}{\xymin{x}}
+\newcommand{\xmax}{\xymax{x}}
+\newcommand{\ymin}{\xymin{y}}
+\newcommand{\ymax}{\xymax{y}}
+\newcommand{\Tr}[3]{{}^{#1}{#2}_{#3}}
+
 % Pages are numbered in submission mode, and unnumbered in camera-ready
@@
 \begin{document}
-\title{Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.}
+%\title{Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.}
+\title{Fitting convex polyhedra to project 2D bounding box}
 \author{Vikas Dhiman\\
@@
 \section{Supplementary Material}
+\subsection{Analytic initialization}
+Problem: given detection bounding box and ground plane estimate the unknown parameters i.e.
+position, orientation and size of the car.
+This problem is under-determined.
+Given the bounding box, we just have four constraints while we have six unknowns.
+To reduce the number of unknowns we assume that detection also gives us an estimate of angle and we assume that length of car is 1.3 times the height.
+Now, we have 4 unknowns and 4 constraints and we can solve them analytically.
+
+\subsubsection{Necessary transforms}
+Let the ground plane be known with parameters $(\uv{n}, h)$.
+Let us take the ground plane to be the XY plane with Z axis pointing upwards and origin at the point of intersection of Y-axis with ground plane.
+The unit vector describing the ground plane is ambiguous by sign, we choose the sign of $\uv{n}$ such that $\hat{n}_2 > 0$, i.e.
+the unit vector is along the positive Y-axis of the camera based on the assumption that the camera axis are approximately aligned such that Y-axis points downwards and Z-axis to the front.
+
+\begin{align}
+  ^gR_c &= [\uv{i}, -\uv{n} \times \uv{i}, -\uv{n}]\\
+  ^gt_c &= [0, 0, h]^\top\\
+        \text{where} & \\
+ \uv{i} &= \frac{1}{\sqrt{\hat{n}^2_3, \hat{n}^2_2}}[0, \hat{n}_3, \hat{n}_2]^\top
+\end{align}
+
+In homogeneous coordinates, let the camera to ground transformation be
+represented by $^gT_c = \begin{bmatrix}^gR_c & ^gt_c\\ \mathbf{0} &
+1\end{bmatrix}$ and its inverse be represented by $^cT_g = {}^gT_c^{-1}$. Let
+the yaw of car be given as theta in camera coordinates. Assume it to be same as
+ground plane coordinates.
+
+\begin{align}
+  \Tr{g}{R}{t} &= \begin{bmatrix}
+  \cos(\theta) & \sin(\theta) & 0 \\
+ -\sin(\theta) & \cos(\theta) & 0 \\
+             0 & 0 & 1
+  \end{bmatrix}
+\end{align}
+
+\subsubsection{System of equations}
+Let the detected bounding box be represented by $[\xmin, \ymin, \xmax, \ymax]^T$. Let $^cT_t$ be the transformation from tracklet to camera.
+\newcommand{\Cu}{C_u}
+\newcommand{\Cc}{C_c}
+\begin{align}
+  \Cu &= \begin{bmatrix}
+    0.5 & 0.5 & 0\\
+    0.5 & -0.5 & 0\\
+    -0.5 & -0.5 & 0\\
+    -0.5 & 0.5 & 0\\
+    0.5 & 0.5 & 1\\
+    0.5 & -0.5 & 1\\
+    -0.5 & -0.5 & 1\\
+    -0.5 & 0.5 & 1
+  \end{bmatrix}\\
+  C_i &= \diag( C_{u\{i,:\}} ) \begin{bmatrix}3& 0\\0 & 1 \\1 & 0\end{bmatrix} 
+\end{align}
+
+\newcommand{\ttg}{\Tr{g}{\mathbf{t}}{t}}
+\newcommand{\tgc}{\Tr{c}{\mathbf{t}}{g}}
+\newcommand{\Rgc}{\Tr{c}{R}{g}}
+\newcommand{\Rtg}{\Tr{g}{R}{t}}
+\newcommand{\Rtc}{\Tr{c}{R}{t}}
+\newcommand{\Pgc}{\Tr{c}{P}{g}}
+\newcommand{\Ptc}{\Tr{c}{P}{t}}
+
+Consider the projection of i\textsuperscript{th} corner of the car.
+\begin{align}
+  \lambda_i \mathbf{u}_i &= K(\Rgc(\Rtg C_i[h, w]^\top + \ttg) + \tgc) & \text{ or }\\
+  \lambda_i \mathbf{u}_i &= K\Rtc C_i [h, w]^\top + K\Rgc \ttg + K \tgc
+  \label{eq:vectorproj}
+\end{align}
+where $\Rtc = \Rgc\Rtg$, $\ttg = [t_x, t_y, 0]^\top$ is unknown car position in
+ground coordinates, $h$ is unknown height, $w$ is unknown width of the car,
+$\lambda$ is unknown scale factor and $\mathbf{u}_i$ is the image projection of
+i\textsuperscript{th} corner of the car.
+
+Equation \eqref{eq:vectorproj} is a set of 3 equations, the third of which allows us to eliminate $\lambda$ as it gives the $\lambda$ and as a linear combination of $t_x$, $t_y$, $h$ and $w$.
+Let $\Ptc = K\Rtc$ and $\Pgc = K\Rgc$.
+\begin{align}
+  \lambda_i \mathbf{u}_i &=  \Ptc C_i [h, w]^\top + \Pgc \ttg + K \tgc\\
+  \lambda_i &= \lambda_{hi}  h + \lambda_{wi}  w + \lambda_{tx}  t_x + \lambda_{ty} * t_y + \lambda_c\\
+  \text{where} & \\
+  \lambda_{hi} &= \Ptc(3, :) C_i(:, 1)\\
+  \lambda_{wi} &= \Ptc(3, :) C_i(:, 2)\\
+  \lambda_{tx} &= \Pgc(3, 1)\\
+  \lambda_{ty} &= \Pgc(3, 2)\\
+   \lambda_{c} &= K(3, :) \tgc
+\end{align}
+
+\subsubsection{Approximate solution}
+Initial approximate solution can be obtained by assuming that $\ymax$ is the projection either of point 
+\begin{align}
+  \lambda_c \mathbf{u}_c &= \Ptc[0, 0, \frac{h}{2}]^\top + \Pgc \ttg + K\tgc
+\end{align}
+
+Assuming the height to be mean height, we can solve for approximate solution
+for $\ttg$. Using this approximate solution find out the corner points that
+correspond to the bounding box. Finally \eqref{eq:vectorproj} can be used for
+the projected points to solve for exact $[h, w, t_x, t_y]$.
+
+\subsubsection{Correspondence of bounding box limits to cuboid corners}
+The $\xmin$ of bounding can be projection of either of the 8 points of the
+cuboid. Once $\xmin$ is chosen the $\xmax$ can be limited to the remain 7
+points hence $8 \times 7= 56$ possibilities and similarly $\ymin$ and $\ymax$
+lead to 56 different possibilities. In this relatively unconstrained
+configuration we have around $56 \times 56 = 3136$ possibilities, which is not
+too big but with a little more analysis we can reduce the number. To this
+effect we can use the aspect graph of a cuboid to understand the topological
+changes by change in view points. Also out of 28 possible configurations in the
+aspect graph, we can rule out the configurations that put camera below the
+ground plane and directly above the observed car itself. This leaves us with 16
+possible topological configurations, which include the symmetrical
+configurations when the car is rotated by $180^\circ$. Considering $180^\circ$ symmetry we are only left with 8 possible topological configurations.
+
+A more general way of finding the subset of aspect graph configuration that
+need to be configured is to rewrite the bounding box inequalities,
+
+\begin{align}
+  \lambda_i \xmax &\ge \Ptc(1, :) C_i [h, w]^\top + \Pgc(1, :) \ttg + K \tgc\\
+  \label{eq:bbox-ineqst}
+  \lambda_i \xmin &\le \Ptc(1, :) C_i [h, w]^\top + \Pgc(1, :) \ttg + K \tgc\\
+  \lambda_i \ymax &\ge \Ptc(2, :) C_i [h, w]^\top + \Pgc(2, :) \ttg + K \tgc\\
+  \lambda_i \ymin &\le \Ptc(2, :) C_i [h, w]^\top + \Pgc(2, :) \ttg + K \tgc \enspace.
+  \label{eq:bbox-ineq}
+\end{align}
+Each of the above four equations is true for all 8 corners, hence there are 32 such inequalities.
+
+The aspect graph boundaries also called the view events, occur when the view
+point or the camera optical center crosses the faces of the cuboid object being
+viewed. The camera optical center $o_t$ in tracklet coordinate frame is given by.
+\begin{align}
+  \mathbf{0} &= \Rgc(\Rtg o_t + \ttg) + \tgc\\
+  o_t &= -\Rtg^\top \ttg -\Rtg^\top \Rgc^\top \tgc
+\end{align}
+
+The 6 faces of a cuboid are simple planes that can be written in terms of $h$
+and $g$. A view event occurs whenever we have $o_t$ satisfying equations of any
+one of the equations that represent the 6 faces. We have to find the number of
+distinct regions that satisfy all of Eq
+\eqref{eq:bbox-ineqst}-\eqref{eq:bbox-ineq}. Then for each distinct region we
+need to find out the topological configuration that limits the number of
+corners candidates for extrema. These can be sorted to create boundaries.
 

### 2015-04-13 CVPR/Source/abstract.tex
Updated abstract.

@@
 \begin{abstract}
-  TODO: Write abstract
-  \vspace{4cm}
+  %Problem:
+  3D localization in road scenes from monocular video is an important problem
+  for applications in autonomous driving. We propose a probabilistic graphical
+  model based framework to estimate 3D localization of traffic participants in
+  road scenes.  We use object detections, point tracks, egomotion, estimated
+  ground truth, GPS and map information as an input to our system.
+  Given this input we compute 6DOF 3D localization of traffic participants
+  along with their dimensions (height, width and length).
+  We also introduce a novel perspective to the soft occlusion models where a
+  region in space is viewed in terms of reflection and transmission
+  probability.
+  We test and train our model on KITTI dataset and show that our occlusion
+  model works better than the baseline method of bounding boxes. We also show
+  that our 3D localization results with monocular video input are comparable to
+  (Geiger 2014) which uses stereo input.
+
+  % Why monocular
+  % Since laser scanners are expensive, we focus on solving the problem through
+  % monocular video, GPS and maps as our input. Given the video we extract the 
+  % Methodology
+  % We formulate the problem of 3D localization in a probabilistic graphical
+  % model specifically a factor graph model. We use additional heuristic
+  % constraints like collision constraint,
+
 \end{abstract}

### 2015-04-13 CVPR/Source/grphicalmodelTP.tex
Added graphical model detailed for a single traffic participant.

  	  \usetikzlibrary{shadows,trees}
  	  \begin{tikzpicture}[grow cyclic,line width=1.2pt,
variablenode/.style={circle,circular drop shadow,draw=black,fill=green,thick,minimum width=1.2cm},
  	  factor/.style={rectangle,drop shadow,draw=black,fill=white,thick,minimum width=1.1cm},
      obs/.style={fill=gray!30},
      prev/.style={text=gray,draw=gray,fill=green!50}]
  	  \path

(0.6,2.8) node [variablenode,prev] (xt1) {$x_{t-2}$}
(2.6,2.8) node [variablenode,prev] (theta1) {$\theta_{t-2}$}

(-0.05,1.8) node [factor,draw=gray,text=gray] (fdynx) {$E_{d}$}
(1.95,1.8) node [factor,draw=gray,text=gray,minimum width=1cm] (fdynt) {$E_{d}$}

(.7,1.1) node[factor](fhol) {$E_{hol}$}

  	 (1, 0)  node[variablenode](theta){$\theta_t$}
   [counterclockwise from=-60,sibling angle=60]
     (2.5, 0) node [factor] (flane) {$E_{lane}$} 
    child { node [variablenode,obs] (l) { $L_t$ } }
    child { node [ variablenode,obs] (gps) {GPS}}
    child { node [ variablenode,obs] (gps) {Map}}
  	(-1, 0)  node[variablenode](xt){$\mathbf{x}_t$}

    [counterclockwise from=60,sibling angle=60]
  	(-2, 1.5) node[factor](fdet){$E_{det}$} 
  	           child {
  	             node[variablenode,obs](gp){$G_t$} 
  	  			}
	  	   		child {           node[variablenode,obs](Det){$D_t$}
  			  }

      (-2.0,-1.5) node[factor](fsize){$E_{size}$}
     (-3,0) node[variablenode](dim){$B$}
[counterclockwise from=-90]
 (0, -1.5) node[factor](fpt) {$E_{pt}$}
 child { node[variablenode,obs](pt){$u_t$} }

  	  ;
  	  \draw (xt) -- (fdet) -- (Det);
  	  \draw (xt) edge (fpt);
      \draw (fpt) -- (pt);
  	  \path  (fpt) edge (theta);
  	  \draw (fdet) -- (gp);
      \draw (fhol) -- (xt);
      \draw (fhol) -- (xt1);
      \draw (fhol) -- (theta);  	  
      \draw (dim) -- (fdet);
     \draw (xt) -- (fsize) -- (dim);
   \draw (theta) -- (flane);
   \draw (xt) -- (fdynx) -- (xt1);
   \draw (theta) -- (fdynt) -- (theta1);
	\end{tikzpicture}

### 2015-05-03 CVPR/Source/experiments.tex
Added poster and a lots of tikz figures.

@@
 
-\paragraph{Dataset}
+\paragraph{Dataset} We use KITTI dataset for our experiments.  \cite{geiger2013vision}
 
@@
 TP that has smaller mean depth then the competing bounding box.
+
+%\subsection{Qualitative Results}
+\begin{figure}
+        \includegraphics[width=\columnwidth]{results/Visualization/City/2011_09_26_drive_0009/single_window_contPtTracks_size_bboxOcc_yawTstepWiseInference/0000000061.png}
+\end{figure}
+\begin{figure}
+  \includegraphics[width=\columnwidth]{results/Visualization/City/2011_09_26_drive_0009/single_window_lane_size_bboxOcc_yawTstepWiseInference/0000000061.png}
+\end{figure}
+\begin{figure}
+  \includegraphics[width=\columnwidth]{results/Visualization/City/2011_09_26_drive_0009/single_window_contPtTracks_size_bboxOcc_yawTstepWiseInference/0000000063.png}
+\end{figure}
+
+%\subsection{Quantitative results}
+
+\begin{table}[h]
+    \begin{tabular}{|l|l|r|r|r|}
+      \hline
+      Energy & Metric & Occ & Unocc & Total\\
+      \hline
+\multirow{3}{*}{\pbox{3cm}{contPtTracks+size\\+bboxOcc+yawT}}  &t  &2.636&4.499&3.351\\
+                            &yaw&0.130&0.201&0.159\\
+                            &dim&0.971&1.042&1.005\\
+      \hline
+      \multirow{3}{*}{\pbox{3cm}{contPtTracksNoOcc\\+size+bbox+yawT}}&t  &2.648&4.488&3.355\\
+                            &yaw&0.126&0.197&0.156\\
+                            &dim&0.964&1.051&1.006\\
+      \hline
+      \multirow{3}{*}{size+bbox+yawT}&t  &2.616&4.501&3.349\\
+                            &yaw&0.125&0.231&0.166\\
+                            &dim&0.969&1.024&0.997\\
+      \hline
+\multirow{3}{*}{
+size+bboxOcc+yawT}&t  &2.615&4.505&3.350\\
+                            &yaw&0.125&0.231&0.166\\
+                            &dim&0.969&1.008&0.991\\
+      \hline
+\multirow{3}{*}{
+(Init only)}           &t  &2.583&4.486&3.321\\
+                            &yaw&0.113&0.181&0.143\\
+                            &dim&0.768&0.864&0.819\\
+      \hline
+
+    \end{tabular}
+  \end{table}

### 2015-05-03 CVPR/Source/intro.tex
More symmetrical placement of nodes.
Again wasted a lot of time on tikz graphical model.
Added poster and a lots of tikz figures.

@@
 
-\begin{tight_itemize}
-  \item Introduce the problem
-  \item Describe our approach
-  \item Contrast with Milan's work
-  \item Contrast with Andreas Geiger's work
-  \item Highlight the contributions
-\end{tight_itemize}
-\vspace{10cm}
+% \begin{tight_itemize}
+%   \item Introduce the problem
+%   \item Describe our approach
+%   \item Contrast with Milan's work
+%   \item Contrast with Andreas Geiger's work
+%   \item Highlight the contributions
+% \end{tight_itemize}
+% \vspace{10cm}
+
+        To accomplish fully or partial autonomous driving we need 3D
+        localization of traffic participants in the scene. 
+        Since laser scanners and stable wide--baseline stereo setups are
+        expensive, we focus on solving the problem using monocular video, GPS
+        and maps as our input. Given the video we extract detection bounding
+        boxes, ground plane and point tracks.
+        We formulate the problem of 3D localization in a probabilistic graphical
+        model specifically a factor graph model. We use additional heuristic
+        constraints like collision constraint, that leads to a global consistent solution.
+        Using these multiple sources of information that provide, possibly conflicting, evidence about
+        the location of traffic participant, a consistent meaningful solution must be estimated. 
+        We formulate the problem in factor graph
+        formalism and use off-the-shelf methods for inference.
+
+        Our work is quite similar to that of Milan et
+        al~\cite{Milan_etal_2014}, except that we provide a optics based
+        perspective to occlusion modeling and our modeling is more detailed
+        than that used in Milan et al. In terms of application we perform 3D
+        localization using monocular camera while \cite{Geiger_etal_2014} use
+        stereo for similar results.
+
 \begin{figure}[!!t]
-  \includegraphics[width=\columnwidth]{Figures/graphicalModelFrom61ConstVars.pdf}
+  %\includegraphics[width=\columnwidth]{Figures/graphicalModelFrom61ConstVars.pdf}
+  \begin{center}
+  \input{Source/graphical_model_multiple}
+  \end{center}
   \caption{Graphical model. The six numbered black circles represent the
@@
 \end{figure}
+\begin{figure}
+  \centering
+  \include{Source/graphicalmodelTP}
+\end{figure}

### 2015-05-03 poster/occgrid.tex
Added poster and a lots of tikz figures.

\documentclass[final]{beamer}
% The following are possible:
%\documentclass[landscape,a0b,final,a4resizeable]{egsposter2013}
%\documentclass[portrait,a0b,final,a4resizeable]{egsposter2013}
%\documentclass[portrait,a0b,final]{egsposter2013}

% Set font
% If this will not compile, try commenting this out temporarily
\usepackage{amsmath}
\usepackage{fontspec}
\setmainfont{Arial}

% The font sizes seem to be inconsistent between TeX and MS Powerpoint.
% These are corrected below for the TeX template.

% Graphics path
\usepackage{graphicx}
\graphicspath{{figs/}}

% Load the EGS style
%\usepackage{egsposter}
\usepackage[scale=1.24]{beamerposter}

% Some packages used for the template
\usepackage{multicol}
\usepackage{graphicx}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\vect}[1]{\mathbf{#1}}
\newcommand{\hvect}[1]{\bar{\vect{#1}}}
\newcommand{\uvect}[1]{\hat{\vect{#1}}}
\newcommand{\field}[1]{\mathbb{#1}}
\newcommand{\Real}[0]{\field{R}}

\newcommand{\map}{\vect{x}}
\newcommand{\meas}{z}
\newcommand{\measurements}{\vect{\meas}}
\newcommand{\pose}{g}
\newcommand{\poses}{\vect{\pose}}
\newcommand{\unaryminus}{\scalebox{0.5}[0.5]{\( - \)}}
\newcommand{\prevtime}{1:t\unaryminus1}
%\newcommand{\pastobs}{\sigma_{\prevtime}}
\newcommand{\pastobs}{\measurements_{1:t\unaryminus1}, \poses_{1:t\unaryminus1}}
\newcommand{\remaining}{\measurements_{\prevtime}, \poses_{\prevtime}}
\newcommand{\bpmsg}[4]{\mu^{#4}_{#1\rightarrow#2}(#3)}

\newcommand{\msg}[3]{\mu_{#1#2}(#3)}
\newcommand{\assign}{\leftarrow}
\newcommand{\Sx}{L_i}

\newcommand{\actz}{\bar{z}_f(\map_f, g_f)}

% Poster title
\newcommand{\postertitle}{Modern MAP inference methods for accurate and fast
occupancy grid mapping on higher order factor graphs}

% Poster authors
\newcommand{\authors}{
Vikas Dhiman\textsuperscript{1},
Abhijit Kundu\textsuperscript{2},
Frank Dallaert\textsuperscript{2},
Jason J. Corso\textsuperscript{1}}

% Authors' departments
\newcommand{\departments}{
\textsuperscript{1}Electrical Engineering and Computer Science, Univeristy of Michigan, MI, USA,
\textsuperscript{2}College of Computing, Georgia Tech, GA, USA}

\begin{document}

%\begin{poster}

  % Header
  \maketitle

  \begin{multicols}{3}

    % Add a section heading
    % -----------------------
    \sectionheading{Introduction}
    % -----------------------

    % Note the usage of 0.5in hspace between the minipages. This is required (see text below)
    \begin{minipage}[c]{0.4\columnwidth}
      Using the inverse sensor model has been popular in occupancy grid mapping
      which assumes independence cell assumption, weakening the model. In our
      work, we make use of modern MAP inference methods along with the forward
      sensor model. Our implementation and experimental results demonstrate
      that these modern inference methods deliver more accurate maps more
      efficiently than previously used methods.
    \end{minipage}
    \hspace{0.5in}
    \begin{minipage}[r]{\dimexpr0.6\columnwidth-0.5in\relax}
      \begin{center}
      \includegraphics[width=\columnwidth]{../../figures/factorgraph/factorgraph3.pdf}
      \captionof{figure}{Representation of occupancy grid mapping as factor graph}
      \label{fig:factor-graph}
      \end{center}
    \end{minipage}

    % -----------------------
    \sectionheading{Contributions}
    % -----------------------

    % The EGS template defined packedEnumerate and packedItemize for convenience
    \begin{packedEnumerate}
      \item We introduce factor graph and apply modern fast inference
        algorithms, such as loopy belief propagation
        \cite{kschischang2001factor} and dual decomposition
        \cite{sontag2011introduction} to the problem of occupancy grid mapping.

      \item We introduce a class of higher order factors for the factor graph
        approach for which it is possible to reduce the time complexity of algorithm to polynomial
        time from exponential in neighborhood size.

    \end{packedEnumerate}

    % -----------------------
    \sectionheading{Mapping with an inverse sensor model}
    % -----------------------

    Mapping with inverse sensor model assume that each grid cell is independent of all other map cells: 
    \begin{align}
      p(\map|\measurements, \poses) &= \prod_{1 \le i \le N} p(x_i|\measurements, \poses)
      \enspace. \\
      p(x_i|\measurements, \poses) &= \frac{1}{Z'p^{t-1}(x_i)}\prod_{1\le f \le t} p(x_i|\meas_f, \pose_f)\enspace.
    \end{align}

    % -----------------------
    \sectionheading{Mapping with a forward sensor model}
    % -----------------------

    In forward sensor model we instead assume that each sensor measurement is independent of each other. 
    \begin{align}
     p(\map | \measurements, \poses) &= \frac{1}{Z} \prod_{1 \le f \le t}
     p(z_f|\map_f, g_f)\enspace.
     \label{eq:modernmap}
    \end{align}

    % Add columnbreak
    \vfill\columnbreak

    % -----------------------
    \sectionheading{Efficient Belief propagation}
    % -----------------------
    Belief propagation works by message passing over factor graph edges

\begin{align}
  \bpmsg{f}{i}{l_i}{r+1} &= \sum_{\map_f \in \Omega_f: x_i = l_i}P_f(\map_f)\prod_{j \in n(f) \setminus i}\bpmsg{j}{f}{x_j}{r}
  \label{eq:factor2node}
  \\
  \bpmsg{i}{f}{l_i}{r+1} &= \prod_{h \in n(i) \setminus f}\bpmsg{h}{i}{l_i}{r}
  \enspace,
  \label{eq:node2factor}
\end{align}
    For efficiency we suggest a class of factors called
    \textit{Pattern based factors} 
    \begin{align}
      p(z_f|\map_f, g_f) = \begin{cases}
        \psi_{m} & \text{ if $\map_f \sim \vect{R}_m$} \,\,\, \forall 1 \le m \le M\\
        \psi_{\text{min}} & \text{ otherwise}
      \end{cases}
      \enspace,
      \label{eq:patternfunction}
    \end{align}
    \begin{align}
      p(\vect{x_f} \sim \vect{R}_m|x_i = l_i)
      = \begin{cases}
    0 & \text{if $i \in n^m_0(f)$ and $l_i \ne r^m_i$}\\
      \prod\limits_{j \in n^m_0(f) \setminus i}\bpmsg{j}{f}{r^m_j}{r} & \text{otherwise}
      \end{cases}.
    \end{align}
    \begin{align}
      \bpmsg{f}{i}{l_i}{r+1} =
      \sum_{m \le M} \psi_m p(\vect{x_f} \sim \vect{R}_m|x_i = l_i)
      + \psi_{\text{min}} p_{\text{otherwise}}
      \label{eq:efficientbp}
      \enspace.
    \end{align}
    where $p_{\text{otherwise}} = 1 - \sum_{m \le M}p(\vect{x_f} \sim \vect{R}_m|x_i = l_i)$.  The message update can be computed in $O(M|n(f)|)$ using
    \eqref{eq:efficientbp}, instead of $O(L_i^{|n(f)|})$ in the general case.

    % -----------------------
    \sectionheading{Results and Discussion}
    % -----------------------

    \begin{minipage}[c]{1.0\columnwidth}
      \begin{center}
       \includegraphics[height=0.20\columnwidth, angle=90]{../../figures/zoomAndShow/zoomAndShowTwoAssumptionAlg.pdf}%
       \includegraphics[height=0.20\columnwidth, angle=90]{../../figures/zoomAndShow/zoomAndShowSICKDDMCMC.pdf}%
       \includegraphics[height=0.20\columnwidth, angle=90]{../../figures/zoomAndShow/zoomAndShowSICKDDMCMC.pdf}%
       \includegraphics[height=0.20\columnwidth, angle=90]{../../figures/zoomAndShow/zoomAndShowBP.pdf}%
       \includegraphics[height=0.20\columnwidth, angle=90]{../../figures/zoomAndShow/zoomAndShowDD.pdf}%
       \captionof{figure}{Qualitative results with different algorithms (from
         left to right): 1) Ground truth with the trajectory of the robot 2)
         Inverse sensor model 3) Metropolis Hastings without heat map 4)
         Metropolis Hastings with heat map 5) Belief Propagation (BP) 6) Dual
       decomposition (DD)}
      \end{center}
    \end{minipage}
    \providecommand{\mysubfloatwidth}{0.33\columnwidth}
    \begin{minipage}[c]{1.0\columnwidth}
      \begin{center}
        \includegraphics[width=\mysubfloatwidth]{../../../Data/cave_player/plot-time-energy.pdf}%
        \includegraphics[width=\mysubfloatwidth]{../../../Data/hospital_section_player/plot-time-energy.pdf}%
        \includegraphics[width=\mysubfloatwidth]{../../../Data/albertb.sm/plot-time-energy.pdf}%
        \captionof{figure}{Comparison of convergence rate of different
        algorithms on occupancy grid mapping on three datasets. While sampling methods like
      Metropolis hastings converge quickly they stay far from optimum energy. }
      \end{center}
    \end{minipage}

    % Add columnbreak
    \vfill\columnbreak

    % -----------------------
    \sectionheading{Conclusion}
    % -----------------------

    \begin{packedEnumerate}
        \item Using forward sensor models is a better then using inverse sensor
          model for occupancy grid mapping.
        \item Belief propagation and dual decomposition are faster algorithms
          as compared to Metropolis Hastings and converge to lower minima.
        \item Pattern based factors can be formulated for efficient inference.
    \end{packedEnumerate}

    % -----------------------
    \sectionheading{Future work}
    % -----------------------
    \begin{packedEnumerate}
      \item Extend the forward sensor model approach for localization and mapping.
      \item A recent comparative study \cite{kappes2013comparative} provides
        several candidate methods that can be used with higher order factors.
    \end{packedEnumerate}

    % -----------------------
    \sectionheading{Acknowledgements}
    % -----------------------

    Vikas Dhiman and Jason J. Corso were partially supported by FHWA
    DTFH61-07-H-00023 and NSF CAREER IIS-0845282 and ARO YIP W911NF-11-1-0090.
    Frank Dellaert and Abhijit Kundu
    were partially supported by an ARO MURI W911NF-11-1-0046.
    We thank Stan
    Birchfield and Brian Peasley for discussions and early efforts in this
    work.

    % -----------------------
    \sectionheading{References}
    % -----------------------

    %\nocite{*}
    {\onehalfspacing\scriptsize
      \bibliographystyle{plain}
      \bibliography{../../icra2014/modern_map}}

    % Add the sponsors
    \addegssponsors

  \end{multicols}

%\end{poster}

\end{document}

### 2015-05-03 poster/poster.tex
Added poster and a lots of tikz figures.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LaTeX poster template
% Created by Nathaniel Johnston
% August 2009
% http://www.nathanieljohnston.com/2009/08/latex-poster-template/
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[final]{beamer}
\usepackage{beamerposter}
\usepackage{graphicx}			% allows us to import images

\usepackage{bm}
\usepackage{tikz}

\usetikzlibrary{trees,shadows}

\tikzset{/tikz/x=2.5cm}
\tikzset{/tikz/y=2.5cm}

%-----------------------------------------------------------
% Define the column width and poster size
% To set effective sepwid, onecolwid and twocolwid values, first choose how many columns you want and how much separation you want between columns
% The separation I chose is 0.024 and I want 4 columns
% Then set onecolwid to be (1-(4+1)*0.024)/4 = 0.22
% Set twocolwid to be 2*onecolwid + sepwid = 0.464
%-----------------------------------------------------------

\newlength{\sepwid}
\newlength{\onecolwid}
\newlength{\twocolwid}
\newlength{\threecolwid}
\setlength{\paperwidth}{48in}
\setlength{\paperheight}{36in}
\setlength{\sepwid}{0.024\paperwidth}
\setlength{\onecolwid}{0.22\paperwidth}
\setlength{\twocolwid}{0.464\paperwidth}
\setlength{\threecolwid}{0.708\paperwidth}
\setlength{\topmargin}{-0.5in}
\usetheme{confposter}
\usepackage{exscale}

\input{preamble}

%-----------------------------------------------------------
% The next part fixes a problem with figure numbering. Thanks Nishan!
% When including a figure in your poster, be sure that the commands are typed in the following order:
% \begin{figure}
% \includegraphics[...]{...}
% \caption{...}
% \end{figure}
% That is, put the \caption after the \includegraphics
%-----------------------------------------------------------

\usecaptiontemplate{
\small
\structure{\insertcaptionname~\insertcaptionnumber:}
\insertcaption}

%-----------------------------------------------------------
% Define colours (see beamerthemeconfposter.sty to change these colour definitions)
%-----------------------------------------------------------

% \setbeamercolor{block title}{fg=ngreen,bg=white}
% \setbeamercolor{block body}{fg=black,bg=white}
% \setbeamercolor{block alerted title}{fg=white,bg=dblue!70}
% \setbeamercolor{block alerted body}{fg=black,bg=dblue!10}

%-----------------------------------------------------------
% Name and authors of poster/paper/research
%-----------------------------------------------------------

\title{3D object localization in road scenes using graphical models}
\author{Vikas Dhiman \and Manmohan Chandrakar \and Jason J Corso}
\institute{University of Michigan}

%-----------------------------------------------------------
% Start the poster itself
%-----------------------------------------------------------

\begin{document}

\begin{frame}[t]
  \begin{columns}[t]												% the [t] option aligns the column's content at the top
  \begin{column}{\sepwid}\end{column}			% empty spacer column
    \begin{column}{\onecolwid}
      \begin{block}{Introduction}
        To accomplish fully or partial autonomous driving we need 3D
        localization of traffic participants in the scene. 
        Since laser scanners and stable wide--baseline stereo setups are
        expensive, we focus on solving the problem using monocular video, GPS
        and maps as our input. Given the video we extract detection bounding
        boxes, ground plane and point tracks.
        We formulate the problem of 3D localization in a probabilistic graphical
        model specifically a factor graph model. We use additional heuristic
        constraints like collision constraint, that leads to a global consistent solution.
        Using these multiple sources of information that provide, possibly conflicting, evidence about
        the location of traffic participant, a consistent meaningful solution must be estimated. 
        We formulate the problem in factor graph
        formalism and use off-the-shelf methods for inference.

        % Related work
        %One of the central goals of 3D scene understanding is to localize the 3D positions and orientations of objects in complex scenes.
        Using
        stereo imagery, several visual cues are combined in \cite{Geiger_etal_2014} to
        simultaneously determine object locations and a rough intersection topology.
        Similar to us, other works have also considered monocular frameworks. Notably,
        occlusions are explicitly handled in \cite{Wojek_etal_2013} by considering
        partial object detectors. A detailed part-based representation of objects based
        on annotated CAD models is used for monocular scene understanding in
        \cite{Zia_etal_2013,Zia_etal_2014}, which also allows reasoning about mutual
        occlusions between objects. In contrast to these works, our monocular framework
        uses a physical modeling of occlusion in continuous space, which makes it more
        general, extensible and amenable for continuous optimization.
      \end{block}

      \begin{block}{Modeling}
        \begin{figure}
          \centering
          \newcommand{\imagewidth}{\onecolwid}
          \input{Source/scenelayoutoverlayCity0961}
          \caption{A sample road scene with the unknowns of each car modeled as random variables. 
          The relating energies are shown in Figure~\ref{fig:graphmodel}}
        \end{figure}

        \begin{figure}
          \centering
          \input{Source/graphical_model_multiple}%
          \caption{Graphical model showing the factor nodes among different
            cars in the same frame. We assume occlusion relationships between
            different cars are known and hence the occlusion modeling can be done
            locally. In this example, the occlusion relationship affects the
            following pair of cars 6-2, 2-5, 5-1. Cars 3 and 4 are not occluded
            and hence affected by only unary terms within the frame. We also avoid 
            collision modeling between unoccluded cars to encourage sparsity.
          }
          \label{fig:graphmodel}
        \end{figure}

      \end{block}
    \end{column}

  \begin{column}{\sepwid}\end{column}			% empty spacer column

    \begin{column}{\onecolwid}
      %\begin{block}{}
        \begin{figure}
          \centering
          \input{Source/graphicalmodelTP}
          \caption{Graphical model showing the factorization of energies for a
            single car. The six state variables of the car can be divided into
            pose $\pos{i}{t}$ and dimensions $\dimsn{i}$. Different energies
          depend only on either of those.}
        \end{figure}
      %\end{block}

      \begin{block}{Energies}
        \begin{table}[h]
          \begin{tabular}{|l|l|}
            \hline
            Symbol & Meaning \\
            \hline
            $\pos{i}{t}$ & Position of $i$th car at time $t$\\
            $\ori{i}{t}$ & Orientation of $i$th car at time $t$\\
            $\dimsn{i}$ & 3D bounding box of the car (dimensions)\\
            $\state{i}{t}$ & State of car $=\{\pos{i}{t}, \ori{i}{t}, \dimsn{i}\}$\\
            $\egop$ & Position of camera at time $t$\\
            $\egoo$ & Orientation of camera at time $t$\\
            $\relp{i}{t}$ & Relative car pose w.r.t. camera \\
            $\tracklets$ & 3D points tracked on car $i$ in its own frame\\
            $\trackp{t}$ & Projection of $\tracklets$ in camera\\
            $\projectionOf{.}$ & Projection function for pose $\relp{i}{t}$\\
            $\bb{i}$ & 2D bounding box of the car in image\\
            \hline
          \end{tabular}
        \end{table}

        Assume conditional independence according to graphical model in
        Figure~\ref{fig:graphmodel}, the negative log likelihood of required
        random variables is given by
        \begin{multline}
          -\log{P(\{\state{i}{t}\} | \mathbb{E})} = 
          Z' + 
          \left(
            \sum_{i=1}^N \sum_{t=s_i}^{e_i}
            \WEnergy{lane} \right.\\
            \left.
            + \WEnergy{size}
            + \WEnergy{dyn}
            + \WEnergy{prior}
            \vphantom{ \sum_{i=1}^N \sum_{t=s_i}^{e_i} }
          \right)\\
          +
          \left(
            \sum_{i,j:i\ne j}^N \sum_{t=s_i}^{e_i}  \WEnergyCol
            + \WpEnergy{box}
            + \WpEnergy{track}
          \right)
          \enspace.
        \end{multline}
      \end{block}
      \begin{block}{Point tracks with occlusion}
        We model continuous point tracks energy with explicit occlusion reasoning as
        the expected re-projection error over the association probability,

        \begin{align}
          \pEnergy{track}(.) =
          %\sum_{t = s_i}^{e_i}
          \sum_{j = 1}^{M}
          \int_1^\infty \assocP\Ereproj(\lambda) d\lambda
        \end{align}
        where $\assocP$ is the association probability of
        $j$\textsuperscript{th} point with $i$\textsuperscript{th} TP at depth $\lambda$
        and $\Ereproj(\lambda)$ is the re-projection error given by
        %
        \begin{align}
          \assocP &= \Prefl\Ptrans\\
          \Ereproj(\lambda) &= \left\|\trackpj{t+1} - \projectionOft{\invProjectionOf{\trackpj{t}, \lambda}}\right\|^2 .
          \label{eq:reprojerror}
        \end{align}

      \end{block}

    \end{column}

  \begin{column}{\sepwid}\end{column}			% empty spacer column

    \begin{column}{\onecolwid}

      \begin{block}{Object detection with occlusion}
        To account for occlusion we weight the error along each side of the
        bounding box with a visibility fraction that is proportional to
        unoccluded area around that side:
        \begin{align}
          \pEnergy{occ}(.) =
          \bm{\rho}^{ij}(t)^\top\left|\projectionOf{\dimsn{i}} - \bb{i}\right|
          \enspace,
          %\sum_{i=1}^N \sum_{t=s_i}^{e_i}
          %\sum_kp_{ik}^{\text{track}}(\projectionOf{\dimsn{i}} - \bb{k})^\top \pmb{\rho}(i,j,t)
        \end{align}
        where $\bm{\rho}^{ij}(t)$ is the visibility fraction vector of the side
        of the bounding box.

      \end{block}

      %\begin{block}{Object detection with continuous occlusion}
      %  The detection scores GMM with occlusion is given by replacing the covariance
      %  matrix
      %  %
      %  \begin{multline}
      %    S'(\bb{i}) =\\
      %    \sum_j A_j \exp(-(\bb{i}-\mu^{(d)}_j)^\top \Sigma'^{(d)-1}_j
      %    (\bb{i}-\mu^{(d)}_j))
      %  \end{multline}

      %  The energy of detection scores is simply take to be the inverse of the detection score.
      %  \begin{align}
      %    \Energy{detect}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}
      %  \end{align}
      %\end{block}

      \begin{block}{Other Energies}
        \begin{description}
          \item[Lane energy]
            \begin{multline}
              \label{eq:laneOrientationEnergy}
              \Energy{lane} = 
              \sum_{m \in M_{\text{close}}}
              (1 - \ori{i}{t} \cdot \text{tan}(L_{m}(k), \pos{i}{t}) )
              \LaneUncertainty{\pos{i}{t}}
            \end{multline}
            where $M_{\text{close}} = \{m : \text{dist}(L_{m}(k), \pos{i}{t}) < 50\} $ is
            the set of nearby lanes and 
            \begin{multline}
              \LaneUncertainty{\pos{i}{t}} = 
              \frac{1}{1 + \exp{(-q(w_{\text{road}} - \text{dist}(L_{m}(k), \pos{i}{t})))}}
            \end{multline}
            for some constant $w_{\text{road}}$ that represents the width of the road.

          \item[Holonomic energy]
            \begin{align}
              \label{eq:totalPosTransitionEnergy}
              \Energy{dyn} = 1 - \ori{i}{t-1} \cdot (\pos{i}{t} - \pos{i}{t-1})
            \end{align}

            %\begin{align}
            %  \Energy{dyn-ori} &= \|\ori{i}{t} - \ori{i}{t-1}\|^2\\
            %  \Energy{dyn-vel} &= \|(\pos{i}{t} - 2\pos{i}{t-1}) + \pos{i}{t-2}\|^2
            %\end{align}

            %\begin{align}
            %  \WEnergy{dyn} &= \WEnergy{dyn-hol} + \WEnergy{dyn-ori} + \WEnergy{dyn-vel}
            %\end{align}

          %\item[Collision Energy]
          %  \begin{align}
          %    \label{eq:collisionEnergyHellingerDistance}
          %    \EnergyCol = -\log\left(
          %      A_{ij}
          %      e^{-\frac{1}{8}
          %        \left(\pos{i}{t} - \pos{j}{t}\right)^\top
          %        P^{-1}
          %        \left(\pos{i}{t} - \pos{j}{t}\right)
          %      }
          %    \right)
          %  \end{align}

          \item[Size Prior]
            \begin{align}
              \label{eq:totalSizeEnergy}
              \Energy{size} &= (\dimsn{i} - \expDimsn)^\top\Sigma_{\expDimsn}^{-1}(\dimsn{i} -
              \expDimsn)
            \end{align}

            where $\expDimsn$ is the mean TP dimensions and
            $\Sigma_{\expDimsn}$ is the correspondence covariance matrix.

        \end{description}
      \end{block}
      \begin{block}{Experiments and Results}
        We perform experiments on KITTI \cite{geiger2013vision} dataset.
        \includegraphics[width=\onecolwid]{results/Visualization/City/2011_09_26_drive_0009/single_window_contPtTracks_size_bboxOcc_yawTstepWiseInference/0000000061.png}\\
        \includegraphics[width=\onecolwid]{results/Visualization/City/2011_09_26_drive_0009/single_window_lane_size_bboxOcc_yawTstepWiseInference/0000000061.png}\\

      \end{block}
    \end{column}

  \begin{column}{\sepwid}\end{column}			% empty spacer column

    \begin{column}{\onecolwid}
      \begin{block}{}
        \includegraphics[width=\onecolwid]{results/Visualization/City/2011_09_26_drive_0009/single_window_contPtTracks_size_bboxOcc_yawTstepWiseInference/0000000063.png}
      \end{block}
      \begin{table}
        \begin{tabular}{|l|l|r|r|r|}
          \hline
          Energy & Metric & Occ & Unocc & Total\\
          \hline
contPtTracks+size+bboxOcc+yawT  &t  &2.636&4.499&3.351\\
                                &yaw&0.130&0.201&0.159\\
                                &dim&0.971&1.042&1.005\\
          \hline
contPtTracksNoOcc+size+bbox+yawT&t  &2.648&4.488&3.355\\
                                &yaw&0.126&0.197&0.156\\
                                &dim&0.964&1.051&1.006\\
          \hline
                  size+bbox+yawT&t  &2.616&4.501&3.349\\
                                &yaw&0.125&0.231&0.166\\
                                &dim&0.969&1.024&0.997\\
          \hline
               size+bboxOcc+yawT&t  &2.615&4.505&3.350\\
                                &yaw&0.125&0.231&0.166\\
                                &dim&0.969&1.008&0.991\\
          \hline
          (Init only)           &t  &2.583&4.486&3.321\\
                                &yaw&0.113&0.181&0.143\\
                                &dim&0.768&0.864&0.819\\
          \hline

        \end{tabular}
      \end{table}
      \begin{block}{Conclusion}
        We use Probablistic graphical models to deduce consistent solutions from multiple sources. The results do not match our expectations and hence need further investigation.
      \end{block}
      \begin{block}{References}
        {\small
          \bibliographystyle{ieee}
          \bibliography{continuousocclusion}
        }
      \end{block}
    \end{column}

  \begin{column}{\sepwid}\end{column}			% empty spacer column

  \end{columns}
\end{frame}
\end{document}

\setbeamercolor{block alerted title}{fg=black,bg=norange}	% frame color
\setbeamercolor{block alerted body}{fg=black,bg=white}		% body color
\begin{alertblock}{Alert Block Colours}
  You can similarly modify the colours for alert blocks (but try not to overdo it):\\
  \begin{semiverbatim}
  {\color{red}\\setbeamercolor}\{block title\}\newline \{fg=black,bg=norange\}
  \end{semiverbatim}
  \begin{semiverbatim}
  {\color{red}\\setbeamercolor}\{block  body\}\newline \{fg=black,bg=white\}
  \end{semiverbatim}
\end{alertblock}

### 2015-05-03 presentation/intro.tex
Added poster and a lots of tikz figures.

% \begin{frame}{Problem}
%   % Notes: Spend around 30 sec on this slide
%   \centering
%   \begin{figure}
%     \input{Source/problemdef.tex}
%   \end{figure}
% \end{frame}
% This slide doesn't make it clear what problem we are trying to solve?  May be
% the slide that Manmohan made with an example image with cars and detections
% is better

% Should we have introduction slide that highlights our contributions?
% but we should have contributions to highlight them. Contributions are perhaps
% better with positive results but still. I don't think we should have negative
% results as a surprise. (It won't as they would have read the report.)

\begin{frame}{Problem}
  % Need a flowchart that describes the input and desired output of the system
 \tikzset{/tikz/x=0.8cm,/tikz/y=0.8cm}
 \newlength{\units}
 \setlength{\units}{0.8cm}
  \scriptsize{
    \input{Source/problemflowchart.tex}
  }
\end{frame}

% \begin{frame}{Problem}
%   \visible<-1>{
%     \begin{tikzpicture}
%       \node[anchor=south west,inner sep=0] (image) at (0,0)
%       {\includegraphics[width=\textwidth]{graphics/0000000061_bevdown.png}};
%       \fill[color=white] (image.south west) rectangle (image.east);
%     \end{tikzpicture}
%   }
% \end{frame}
\begin{frame}{Problem}

  \def\arrow{
    (0,0) -- ++(1,0)
    -- ++(0,1) -- ++(0.3, 0)
    -- ++(-0.8, 1) -- ++(-0.8, -1) -- ++(0.3, 0) -- ++(0, -1) }

  \begin{tikzpicture}
    \node[anchor=south west,inner sep=0] (image) at (0,0)
    {\includegraphics[width=\textwidth]{graphics/0000000061_bevdown.png}};
    \begin{scope}[x={(image.south east)},y={(image.north west)}]
      \fill[color=red,scale=0.05,shift={(10,11)},rotate=180,]\arrow;
    \end{scope}
  \end{tikzpicture}
\end{frame}

### 2015-05-03 presentation/pointTrackEnergyWithOccFigure.tex
Added poster and a lots of tikz figures.

\begin{tikzpicture}[x=0.8cm,y=0.8cm,3d/perspective eye={4,4,-10},ptstyle/.style={fill=#1,draw,circle,inner sep=1.5pt}]
    \input{Source/twocuboids.tex}
    \draw [->, very thick, draw=blue] (pta4) --  +(90:1) node [anchor=south,align=center] {$a^1(\lambda) = 0$\\$a^2(\lambda) = 1$};
    \draw [->, very thick, draw=red!50!blue] (pta-8) --  +(170:1.4) node [anchor=south,align=center] {$a^1(\lambda) = 0.5$\\$a^2(\lambda) = 0.5$};
    \draw [->, very thick, draw=red] ($(ptb-8)+(.5,-.8)$) --  +(-60:.8) node [anchor=north,align=center] {$a^1(\lambda) = 1$\\$a^2(\lambda) = 0$};
   \begin{scope}[shift={(4,-2)}]
     \path [fill=blue!20,draw] (0,0) ellipse (1.2 and 0.7);
     \path [fill=green!20,draw] (3,0) ellipse (1.2 and 0.7);
     \coordinate (o) at (-2,-1);
     \draw(o) edge [->,very thick] node (xa) {} +(6, 0);
     \node at ($(xa) + (0, -0.2)$) {Depth from camera ($\lambda$)};
     \draw(o) edge [->,very thick] node (ya) {} +(0, 2);
     \node [rotate=90]at ($(ya) + (-0.2, 0)$) {$a^{(1j)}(\lambda)$};
\draw [thick,red] plot [smooth] coordinates {($(o)+(0,1.8)$) ($(o)+(0.2,1.8)$) ($(o) + (0.8, 1.7)$) ($(o)+(1.4,0.3)$) ($(o)+(3.8,0.2)$)($(o)+(4.4,0.1)$) ($(o)+(6.1,0.1)$)};
   \end{scope}
\end{tikzpicture}

### 2015-05-04 CVPR/Source/experiments.tex
Latest version of presentation.

--- 2014-11-10 CVPR/Source/experiments.tex
@@
 
-\paragraph{Dataset}
+\paragraph{Dataset} We use KITTI dataset for our experiments.
+\cite{geiger2013vision}.
+KITTI dataset is a labeled video sequence of road scenes under variety of driving conditions including highways and residential areas in Karlsruhe, Germany.
+It provides manually labelled ground truth data for localization of cars and also uses velodyne data provide metrically accurate estimates of cars location.
 
@@
 \begin{align}
-  P^{(ij)}_{\text{assoc}} = \frac{1}{Z'}\int_0^{\infty} \assocP \frac{1}{\sqrt{2\pi}}\exp(-\Ereproj(\lambda))d\lambda
+  P^{(ij)}_{\text{assoc}} = \frac{1}{Z'}\int_0^{\infty} \assocP \exp(-\Ereproj(\lambda))d\lambda
   \label{eq:prob-assoc}
@@
 TP that has smaller mean depth then the competing bounding box.
+
+\begin{table}
+  \centering
+  \begin{tabular}{lrrr}
+    \toprule
+    Algorithm & Total & Unoccluded cars & Occluded cars \\
+    \midrule
+    bounding box only & 0.21 & \textbf{0.03}  & 0.36\\
+    Using $P^{(ij)}_{\text{assoc}}$ & \textbf{0.21} & 0.08 & \textbf{0.32}\\
+    Using $\assocP{}$ & 0.23 & 0.09 & 0.34 \\
+    Using $P^{(ij)}_{\text{assoc by reproj}}$ & 0.23 & 0.08 & 0.34\\
+    \bottomrule
+  \end{tabular}
+  \caption{Association Experiment results. The error is in terms of fraction of points wrongly associated with objects, hence lower is better.}
+\end{table}
+
+\paragraph{Localization Experiment}
+Localization is the main goal of our project.
+We estimate the position, orientation and dimensions of the car with our framework and compute the error in birds eye view domain along the ground plane.
+We report error in three metrics translation error (t) in meters per car, yaw error (yaw) in radians per car and dimension error is again meters per car.
+
+% %\subsection{Qualitative Results}
+% \begin{figure}
+%         \includegraphics[width=\columnwidth]{results/Visualization/City/2011_09_26_drive_0009/single_window_contPtTracks_size_bboxOcc_yawTstepWiseInference/0000000061.png}
+% \end{figure}
+% \begin{figure}
+%   \includegraphics[width=\columnwidth]{results/Visualization/City/2011_09_26_drive_0009/single_window_lane_size_bboxOcc_yawTstepWiseInference/0000000061.png}
+% \end{figure}
+% \begin{figure}
+%   \includegraphics[width=\columnwidth]{results/Visualization/City/2011_09_26_drive_0009/single_window_contPtTracks_size_bboxOcc_yawTstepWiseInference/0000000063.png}
+% \end{figure}
+
+%\subsection{Quantitative results}
+
+\begin{table}
+  \centering
+  \begin{tabular}{lrrr}
+    \toprule
+    Energy & t & yaw & dim \\
+    \midrule
+    lane+contPtTracksNoOcc+size+bbox+posT   & 3.80 & 0.91 & 1.58 \\
+    lane+contPtTracks+size+bboxOcc+posT+col & \textbf{3.78} & 0.91 & 1.58 \\
+    lane+contPtTracks+size+bboxOcc+posT     & 3.81 & 0.92 & 1.59 \\
+    lane+size+bboxOcc+posT+col              & 3.92 & 0.91 & 1.15 \\
+    lane+size+bboxOcc+posT                  & 3.83 & 0.90 & 1.14 \\
+    lane+size+bbox+posT                     & 3.83 & 0.90 & \textbf{1.14} \\
+    initialization                          & 3.79 & \textbf{0.86} & 1.64 \\
+    \bottomrule
+  \end{tabular}
+  \caption{Localization experiment results with different combination of energies.
+We report error in three metrics translation error (t) in meters per car, yaw error (yaw) in radians per car and dimension error is again meters per car.}
+\end{table}

### 2015-05-04 CVPR/Source/localize.tex
Added poster and a lots of tikz figures.
Latest version of presentation.

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Continuous Energies for Object Localization}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We explain energies in this section.
+With the understanding of our occlusion aware 3D representation of objects, we are know in position to describe the energies that we defined in Chapter~\ref{sec:setup}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Point tracks energy with occlusion}
+\section{Point tracks energy with occlusion}
 \label{sec:totalContPtTracksEnergy}
@@
 
-\begin{multline}
-  \Energy{traci}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \\
+\begin{align}
+  \Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = 
     \sum_{i=1}^{N} 
@@
     \int_1^\infty \assocP\Ereproj(\lambda) d\lambda
-\end{multline}
+\end{align}
 where $\assocP$ is the association probability of
-$j$\textsuperscript{th} point with $i$\textsuperscript{th} TP at depth $\lambda$
+$j$\textsuperscript{th} point with $i$\textsuperscript{th} TP at depth $\lambda$, $\{ \relp{i}{t} \}_i$ are the poses of all occluding objects at time $t$, $ \{ \dimsn{i} \}_i$ are the dimensions of all objects that occlude $i$
 and $\Ereproj(\lambda)$ is the re-projection error given by
@@
   \assocP &= \Prefl\Ptrans\\
-  \Ereproj(\lambda) &= \left\|\trackpj{t+1} - \projectionOft{\invProjectionOf{\trackpj{t}, \lambda}}\right\|^2 .
+  \Ereproj(\lambda) &= \left\|\trackpj{t} - \projectionOf{\invProjectionOftm{\trackpj{t-1}, \lambda}}\right\|^2 .
   \label{eq:reprojerror}
@@
 
-The  $\projectionOf{.}$ and $\invProjectionOf{.}$ denote the projection and
+The  $\projectionOf{.}$ and $\invProjectionOftm{.}$ denote the projection and
 inverse projection functions that project 3D point to camera image and vice
 versa. Note that inverse projection $\invProjectionOf{.}$ depend on both the
-point $\trackp{t}$ and the unknown depth $\lambda$. Also note that the inverse projection is dependent on TP pose at time $t$ while the projection depends on pose at time $t+1$ which can be different.
+point $\trackp{t}$ and the unknown depth $\lambda$. Also note that the inverse projection is dependent on TP pose at time $t-1$ while the projection depends on pose at time $t$ which can be different.
 
 \begin{comment}
-  \subsubsection{Occupancy function}
+  \subsection{Occupancy function}
   Assuming occupancy to be a
@@
 \begin{comment}
-  \subsubsection{Approximations}
+  \subsection{Approximations}
   Reflection probability of $i$th TP is easy to compute
@@
   %
-  % \subsubsection{Computing $\Prefl$ and $\Ptrans$}
+  % \subsection{Computing $\Prefl$ and $\Ptrans$}
   % Focusing on  $\nabla \occfxi$ 
@@
 
-\subsection{Object detection energy with occlusion}
+\section{Object detection energy with occlusion}
 
@@
 
-\subsubsection{Detection scores with occlusion reasoning} 
+\subsection{Detection scores with occlusion reasoning} 
 With our model of $\Ptrans$ described in Section \ref{sec:TPmodel}, we can
@@
 
-If we a portion of our proposed detection bounding box is known to be occluded,
-then we would like to decrease the confidence in the detection score about the
-localization of that end of the object. Assuming that the occlusion is often on
-the boundary of detection bounding boxes, we want to decrease our confidence on
-the mean detection boundaries around the occluded boundaries. 
+If we know a portion of our proposed detection bounding box is known to be
+occluded, then we would like to decrease the confidence in the detection score
+about the localization of that end of the object. Assuming that the occlusion
+is often on the boundary of detection bounding boxes, we want to decrease our
+confidence on the mean detection boundaries around the occluded boundaries.
 One of the simplest ways will be to scale the appropriate diagonal element of
 $\Sigma_j$ by an appropriate scaling factor proportional to occlusion. But this
-does not model appropriate how does occlusion affects the non diagonal terms.
+does not model explain the affect of occlusion on the non diagonal terms.
 Hence, we choose a covariance addition model where we compute a occlusion
@@
 %
-\begin{multline}
-  S'(\bb{i}) =\\
+\begin{align}
+  S'(\bb{i}) =
   \sum_j A_j \exp(-(\bb{i}-\mu^{(d)}_j)^\top \Sigma'^{(d)-1}_j
   (\bb{i}-\mu^{(d)}_j))
-\end{multline}
+\end{align}
 
@@
 
-\subsection{Lane energy}
+\section{Lane energy}
 \label{sec:laneEnergy}
@@
 
-\begin{multline}
+\begin{align}
   \label{eq:laneOrientationEnergy}
-  \Energy{lane} = \\
+  \Energy{lane} = 
   \sum_{m \in M_{\text{close}}}
@@
 \LaneUncertainty{\pos{i}{t}}
-\end{multline}
-where $M_{\text{close}} = \{m : \text{DIST}(L_{m}(k), \pos{i}{t}) < 50\} $ is
-the set of nearby lanes and 
-\begin{multline}
-\LaneUncertainty{\pos{i}{t}} = \\
-  \frac{1}{1 + exp(-q(w_{\text{road}} - \text{DIST}(L_{m}(k), \pos{i}{t})))}
-\end{multline}
+\end{align}
+where $M_{\text{close}} = \{m : \text{DIST}(L_{m}(k), \pos{i}{t}) < d_{\text{thresh}}\} $ is
+the set of nearby lanes close to the object by a certain distance threshold $d_{\text{thresh}}$ and 
+\begin{align}
+\LaneUncertainty{\pos{i}{t}} = 
+  \frac{1}{1 + \exp(-q(w_{\text{road}} - \text{DIST}(L_{m}(k), \pos{i}{t})))}
+\end{align}
 for some constant $w_{\text{road}}$ that represents the width of the road.
 
-\subsection{Transition probability}
+\section{Transition probability}
 Dynamics constraints should not only enforce smooth trajectories, but also the
@@
 
-\subsection{Collision energy}
+\section{Collision energy}
 
@@
 
-\begin{multline}
+\begin{align}
   \label{eq:collisionEnergyHellingerDistance}
-  \EnergyCol =\\ -\log\left(
+  \EnergyCol =
+  -\log\left(
   A_{ij}
@@
     \right)
+\end{align}
+where 
+\begin{multline}
+  A_{ij} = \frac{|\Sigma_i|^\frac{1}{4}|\Sigma_j|^\frac{1}{4}}{|P|^\frac{1}{2}}, \hfill
+  P = \frac{1}{2}\Sigma_i + \frac{1}{2}\Sigma_j, \hfill
+\Sigma_i^{-1} = R^\top_{\ori{i}{t}} \begin{bmatrix} 2/l_i & 0 \\ 0 & 2/w_i \end{bmatrix}
+R_{\ori{i}{t}}
 \end{multline}
-where 
-\begin{align}
-  A_{ij} &= \frac{|\Sigma_i|^\frac{1}{4}|\Sigma_j|^\frac{1}{4}}
-  {|P|^\frac{1}{2}}\\
-  P &= \frac{1}{2}\Sigma_i + \frac{1}{2}\Sigma_j\\
-\Sigma_i^{-1} &= R^\top_{\ori{i}{t}} \begin{bmatrix} 2/l_i & 0 \\ 0 & 2/w_i \end{bmatrix}
-R_{\ori{i}{t}}
-\end{align}
 
-\subsection{Size Prior}
+\section{Size Prior}
 
@@
   \label{eq:totalSizeEnergy}
-  \Energy{prior} &= (\dimsn{i} - \expDimsn)^\top\Sigma_{\expDimsn}^{-1}(\dimsn{i} -
+  \Energy{size} &= (\dimsn{i} - \expDimsn)^\top\Sigma_{\expDimsn}^{-1}(\dimsn{i} -
   \expDimsn)

### 2015-05-04 CVPR/Source/occlusion.tex
Latest version of presentation.

@@
-\section{Occlusion-Aware 3D Object Modeling}
-\label{sec:TPmodel}
+In this section, we introduce our representation of 3D traffic participants and our modeling of object-object occlusion relationships.
+We refer the reader to Figure~\ref{fig:reflectiontransimission} for an illustration of the proposed concepts.
 
-In this section, we introduce our representation of 3D traffic participants and our modeling of object-object occlusion relationships.
-We refer the reader to Figure [[FIGURE]] for an illustration of the proposed concepts.
+\begin{figure}
+  \usetikzlibrary{calc}
+  \centering
+  \begin{tikzpicture}
+    \input{Source/reflectiontransmissiongraph.tex}
+  \end{tikzpicture}
+  \caption{We represent traffic participants as soft ellipsoids which lead to formulation of transmision and reflection probability.
+This figure shows the reflection probability for the first car which is highest around the camera facing face of the car.
+Also note that transmission probability is inversly proportional to occupancy.}
+  \label{fig:reflectiontransimission}
+\end{figure}
 
@@
 Based on this intuition, we model objects as translucent 3D ellipsoids whos opacity is maximum at the center and falls off towards the edges.
-In particular, we model the occupancy at location $\bx$ corresponding to a traffic participant $i$ centered at $\bp$ as:
+In particular, we model the occupancy at location $\bx$ corresponding to a traffic participant $i$ centered at $\pos{i}{t}$ as:
 \begin{align}
-  \occft{\bx} = \cL(\bx; \bp, \bSigma)
+  f_{\text{occ}}{\bx} = \cL(\bx; \pos{i}{t}, \bSigma_i)
 \end{align}
@@
 The spread of the ellipsoid, determined by $\bSigma_i$, depends of the dimensions of the traffic participant.
-Please refer to the additional material for computation of $\bSigma$ from object dimensions.
+Please refer to the Appendix~\ref{sec:appendix} for computation of $\bSigma$ from object dimensions.
 
@@
 Consider a 3D point $\bx_j$ observed in the image at pixel $\bu_j$.
-Let $\ray = \displaystyle\frac{\bK^{-1}\bu_j}{\lVert \bK^{-1}\bu_j \rVert}$ be the corresponding unit vector along the backprojected ray from the camera center.
+Let the image was formed using camera with intrinsic matrix $\bK$.
+Let $\ray = \frac{\bK^{-1}\bu_j}{\lVert \bK^{-1}\bu_j \rVert}$ be the corresponding unit vector along the backprojected ray from the camera center.
 Then, the probability of reflection at depth $\lambda$ along the ray $\ray$, by an object $O_i$, is determined by the object's gradient of the occupancy function $f_{occ}^i$:
@@
 The $\max \{ \}$ ensures that the negative probability due to gradient in the direction opposite to ray is clipped off and squaring the function allows it to be smooth near zero.
-We note that in the extreme case of an object object, the above reverts to a (squared) Lambertian reflection.
+We note that in the extreme case of an object being lambertial, the above reverts to a (squared) Lambertian reflection.
 
 \paragraph{Transmission probability}
+Since we are modeling occupancy as transparency, we look towards optics for modeling of translucent objects.
 A model for transmission of light through a material of thickness $\alpha$, density $\rho$ and opacity $\beta$ is given by the Beer-Lambert Law:
@@
 \begin{align}
-P^j_{\textit{transmission}}(\lambda) = \prod_{0}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda},
+P^j_{\textit{transmission}}(\lambda) = \prod_{f}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda},
 \label{eq:ptrans-integral}
 \end{align}
-where $\displaystyle\prod_{0}^{\lambda}$ represents the \emph{product integral} from $0$ to $\lambda$.\footnote{A product integral is a simple integral in log domain: 
+where $\displaystyle\prod_{f}^{\lambda}$ represents the \emph{product integral} from $f$ to $\lambda$ and $f$ is the position of camera screen which has been taken equivalent to focal length of the camera .\footnote{A product integral is a simple integral in log domain:
 \vspace{-0.2cm}
@@
 %% \end{comment}%% Comment
+
+% \paragraph{Notation}
+% We summarize the notation used in the report for quick reference.
+% \\
+% 
+% 
+%   \begin{tabular}{|l|l|}
+%     \hline
+%     Symbol & Meaning \\
+%     \hline
+%     $\pos{i}{t}$ & Position of $i$th car at time $t$\\
+%     $\ori{i}{t}$ & Orientation of $i$th car at time $t$\\
+%      $\dimsn{i}$ & 3D bounding box of the car (dimensions)\\
+%     $\state{i}{t}$ & State of car $=\{\pos{i}{t}, \ori{i}{t}, \dimsn{i}\}$\\
+%     $\egop$ & Position of camera at time $t$\\
+%     $\egoo$ & Orientation of camera at time $t$\\
+%     $\relp{i}{t}$ & Relative car pose w.r.t. camera \\
+%     $\tracklets$ & 3D points tracked on car $i$ in its own frame\\
+%     $\trackp{t}$ & Projection of $\tracklets$ in camera\\
+%     $\projectionOf{.}$ & Projection function for pose $\relp{i}{t}$\\
+%     $\bb{i}$ & 2D bounding box of the car in image\\
+%     \hline
+%   \end{tabular}

### 2015-05-04 CVPR/Source/setup.tex
Added poster and a lots of tikz figures.
Latest version of presentation.

@@
-\section{Overview of Problem and Our Approach}
-TODO:
-\vspace{4cm}
+We are given video feed from a front facing monocular camera.
+We assume that features like car detections, point tracks, lane detections, ground plane and ego-motion are already available.
+We also use GPS and Map as a given input to the system.
+With this available information our goal is to find position, orientation and dimensions different participants in the scene.
 
-\paragraph{Notation}
+We model this problem in factor graph formulation.
+Factor graphs are bipartite graphs containing factor node and variable nodes that describe the factorization of the joint probability over the random variables in the graph.
+Each factor node is connected to a variable node if and only if the corresponding function depends on the corresponding random variable node.
 
-\begin{table}[h]
-  \begin{tabular}{|l|l|}
-    \hline
-    Symbol & Meaning \\
-    \hline
-    $\pos{i}{t}$ & Position of $i$th car at time $t$\\
-    $\ori{i}{t}$ & Orientation of $i$th car at time $t$\\
-     $\dimsn{i}$ & 3D bounding box of the car (dimensions)\\
-    $\state{i}{t}$ & State of car $=\{\pos{i}{t}, \ori{i}{t}, \dimsn{i}\}$\\
-    $\egop$ & Position of camera at time $t$\\
-    $\egoo$ & Orientation of camera at time $t$\\
-    $\relp{i}{t}$ & Relative car pose w.r.t. camera \\
-    $\tracklets$ & 3D points tracked on car $i$ in its own frame\\
-    $\trackp{t}$ & Projection of $\tracklets$ in camera\\
-    $\projectionOf{.}$ & Projection function for pose $\relp{i}{t}$\\
-    $\bb{i}$ & 2D bounding box of the car in image\\
-    \hline
-  \end{tabular}
-\end{table}
+\begin{figure}
+  \centering
+  \newcommand{\imagewidth}{\textwidth}
+  \input{Source/scenelayoutoverlayCity0961}
+  \caption{A sample road scene with the unknowns of each car modeled as random variables. 
+  The relating energies are shown in Figure~\ref{fig:graphmodel}}
+\end{figure}
+\begin{figure}
+  %\includegraphics[width=\columnwidth]{Figures/graphicalModelFrom61ConstVars.pdf}
+    %\tikzset{/tikz/x=0.8cm,/tikz/y=0.8cm}
+  \begin{subfigure}[b]{0.55\textwidth}
+    \input{Source/graphical_model_multiple}
+    \caption{Graphical model for a single frame with state of car represented
+    as single node.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.45\textwidth}
+    \tikzset{/tikz/x=0.8cm,/tikz/y=0.8cm}
+    \include{Source/graphicalmodelTP}
+    \caption{Factor graph dependence split up by pose and dimension}
+  \end{subfigure}
+\caption{Graphical model.
+The six numbered nodes represent the unknown state variables of each car.
+The shaded nodes in the graphical model are observed variables.
+%(1) Bounding box energy: The bounding box energy ($\Energy{bbox}$) without occlusion modeling is a unary term, but with occlusion it becomes a higher order term that affects the state of occluder as well.
+The bounding box detection is represented by $\mathbf{d}_{bb}^i(t)$.
+We can see that the bounding box energy affects both occluder and the occluded.
+(2) Point tracks energy ($\Energy{track}$) also exhibits occluder-occluded dependency.
+The available point tracks are modeled by $\mathbf{u}(t)$.
+(3) Collision energy ($\Energy{coll}$) should ideally be globally dependent on all traffic participants but here we represent collision among only those TP that are near enough to have a significant collision energy.
+(4) Orientation from lane (and map) information ($\Energy{lane}$) depends only on single traffic participant hence show in the right subfigure.
+(5) Dynamic energies ($\Energy{dyn}$) also affect only one traffic participant at a time but over two frames.
+(6) Size prior ($\Energy{size}$) is used to enforce reasonable size of traffic participants.
+}
+  \label{fig:graphmodel}
+\end{figure}
+\begin{figure}
+  \centering
+\end{figure}
 
@@
 
-The objective is to find the most likely traffic participant (TP) state given
-various evidences $\mathbb{E} = \{\{\trackp{t}\}, \{\bb{i}\}, \text{lane det.},
-\text{map}, \text{GPS}\}$.
-
-Mathematically, find:
+The objective is to find the most likely traffic participant (TP) state $\state{i}{t}$ given
+various evidences $\mathbb{E} = \{\{\trackp{t}\}, \{\bb{i}\}, \{L_m\}\}$. This problem can be formulated as to find the states that maximize the conditional probability given the evidence,
+%
 \begin{align}
-  \{\state{i}{t}\}^* &= \arg \max P(\{\state{i}{t}\} | \mathbb{E})
+  \{\state{i}{t}\}^* &= \arg \max P(\{\state{i}{t}\} | \mathbb{E})\enspace.
 \end{align}
-
-Bayes rule
+%
+By applying Bayes rule we get
 \begin{align}
   P(\{\state{i}{t}\} | \mathbb{E}) &=
-  \frac{1}{Z}P( \mathbb{E} | \{\state{i}{t}\})P(\{\state{i}{t}\})
+  \frac{1}{Z}P( \mathbb{E} | \{\state{i}{t}\})P(\{\state{i}{t}\}).
 \end{align}
-
-Assume conditional independence according to graphical model in
-\ref{fig:graphmodel}.
-
+%
+Assume conditional independence according to graphical model in Figure~\ref{fig:graphmodel}, we get an equivalant factorization of the joint probability distribution
+%
 \begin{multline}
@@
   \frac{1}{Z}
-  \prod_{t=s_i}^{e_i}\prod_{i,j: i \ne j}(P(\state{i}{t}, \state{j}{t}))\\
-%
+  \prod_{t=s_i}^{e_i}
+  \left(
+  \prod_{i,j: i \ne j}
+  P(\state{i}{t}, \state{j}{t})
+  P(\bb{i} | \state{i}{t}, \state{j}{t})
+  P(\trackp{t} | \state{i}{t}, \state{j}{t})
+\right)
+\\
+\left(
   \prod_{i=1}^{N}
-  \prod_{t=s_i}^{e_i}
-  P(\bb{i} | \state{i}{t})
-  P(\trackp{t} | \state{i}{t})\\
-  P(\state{i}{t} | L_m(t))
+  P(L_m(t) | \state{i}{t})
   P(\state{i}{t} | \state{i}{t-1})
   P(\state{i}{t})
+\right)
+  \enspace ,
 \end{multline}
-
-We can formulate similar objective function in negative log domain:
-\footnote{TODO:Resolve inconsistency in summation absorption in energy terms.}
+where $\bb{i}$ are the car detections, $\trackp{t}$ are the point tracks, $L_m(t)$ is the lane information from lane detection or GPS and Map information.
+For computational reason it is common to work on factor graphs in log domain
+and for historical reasons the negative log of probability is also called the energy of the system. In energy domain our factorization simplifies to
+%
 \begin{multline}
   -\log{P(\{\state{i}{t}\} | \mathbb{E})} = 
-  Z' + \sum_{i,j:i\ne j} \sum_{t=s_i}^{e_i}  \WEnergyCol \\
-  + \sum_{i=1}^N \sum_{t=s_i}^{e_i}
-    \WEnergy{box}
-  + \WEnergy{track}\\
-  + \WEnergy{lane}
+  -Z' 
+  + \sum_{t=s_i}^{e_i}
+  \left(
+  \sum_{i,j:i\ne j}   
+  \WEnergyCol 
+   + \WpEnergy{bbox}
+   + \WpEnergy{track}
+\right)
+  \\
+  + \left(
+  \sum_{i=1}^N 
+  \WEnergy{lane}
   + \WEnergy{dyn}
-  + \WEnergy{prior}
+  + \WEnergy{size}
+\right)
+  \enspace.
 \end{multline}
+%
+Here $\WEnergyCol = -\log P(\state{i}{t}, \state{j}{t})$ is collision energy which penalizes localization of cars that are too close together, $\WpEnergy{bbox} = -\log P(\bb{i} | \state{i}{t}, \state{j}{t})$ is bounding box energy that encourages the alignment of projected bounding box with the detected bounding box, $\WpEnergy{track} = -\log P(\trackp{t} | \state{i}{t}, \state{j}{t})$ is the point tracks energy which encourages the alignment of re-projected point tracks with ones that are detected, $\WEnergy{lane} = - \log P(L_m(t) | \state{i}{t})$ is lane energy which encourages cars to be along the direction of lanes, $\WEnergy{dyn} = - \log P( \state{i}{t} | \state{i}{t-1} ) $ is dynamic energy which captures the motion model of the cars and finally $\WEnergy{size} = - \log P (\state{i}{t})$ is the size prior over the cars.
+$\lambda_{\text{\{col,bbox,track,lane,dyn,size\}}}$ are unknown parameters that weight different energies.
+For now we set them empirically, but eventually they need to be learned from the data.

### 2015-05-04 CVPR/quals2report.tex
Latest version of presentation.

\documentclass[10pt,letterpaper]{report}

\usepackage[margin=1in]{geometry}
%\usepackage{iccv}
\usepackage{booktabs}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{subcaption}

\usepackage{pbox}
\usepackage{verbatim}
\usepackage{bm}
\usepackage{microtype}
\usepackage{url}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{shadows,trees}

\newlength{\eqs}
\setlength{\eqs}{-0.04in}

\usepackage{enumitem}
\setitemize[0]{leftmargin=15pt}

\newenvironment{tight_itemize}{
\begin{itemize}[leftmargin=10pt]
  \setlength{\topsep}{0pt}
  \setlength{\itemsep}{0pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{itemize}}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%\newcommand{\bm}{\mathbf{}}
\input{preamble}
\DeclareMathOperator*{\argmin}{\arg\min}

\begin{document}

%%%%%%%%% TITLE
\title{Continous occlusion models and traffic scene understanding}
\author{Vikas Dhiman\\
  {\tt\small dhiman@umich.edu}
  \and
  Mentor: Manmohan Chandrakar\\
  {\tt\small manu@nec-labs.com}
  \and
  Advisor: Jason J Corso\\
  {\tt\small jjcorso@umich.edu}
}
\date{\parbox{\linewidth}{\centering%
  \today\endgraf\bigskip
  Quals 2 report}}
\maketitle
%%%%%%%%% ABSTRACT
\input{Source/abstract.tex}

\tableofcontents

\chapter{Introduction}
\label{sec:intro}
\input{Source/intro}

% % This work is a triple dip: 
% (1) PGM course (2) Qualifier project (3) ICCV submiission

% 
% % Message to be delivered 
% 1. To show the work done
% 2. Exemplify technical powress 
% 3. understanding of graphical models
% 4. Lessons learned: 
%   4.a) occlusion modeling doesn't help much
%   4.b) GPS/Map/Lane are useful
%   4.c) Particle Belief propagation has tough competition from fminunc

% % Course point of view (PGM)
% What is the graphical model that we used for the problem
% What inference method we used for the problem.
% How did the results match to naive realization

% What I did
% GPS/Map/lane orientatio
% Occlusion modeling
% Particle Belief propagation

% What did I learn
% GPS is much more accurate than we would like to think
% Occlusion modeling doesn't help much as we think
% PBP has a surprising competitor

% Outline
% Abstract
% 1 Introduction
% Figure explaining the pipeline?

% 1.5 Related work
\chapter{Related Work}
\label{sec:related}
\input{Source/related}

%
% 2 Modeling
\chapter{Overview of Problem and Our Approach}
\label{sec:setup}
\input{Source/setup}
% Figure explaining the model within a car
% Figure explaining the model within a frame
% Figure explaining the model multiples frames
% 2.1 GPS and Lane information
% 2.2 Occlusion modeling
\chapter{Occlusion-Aware 3D Object Modeling}
\label{sec:TPmodel}
\input{Source/occlusion}
% 2.3 Point tracks
% 2.4 Object detections
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Continuous Energies for Object Localization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{Source/localize}

%
% 3. Inference
% 3.1 fminunc
% 3.2 Particle belief propagation
% 3.3 MCMC
\chapter{Inference}
\input{Source/inference}

%
% 4. Experments and Results
% 4.1 Prove that PGM is useful
% 4.2 Prove that Adding GPS/Lane information is useful
% 4.3 Prove that Adding Point tracks energy is useful
% 4.4 Prove that Adding Occlusion model is useful/not useful
\chapter{Experiments}
\input{Source/experiments}
% 
% 5. Conclusion and Discussions
% 6. Pacify negative results
\chapter{Discussions}
\input{Source/discussions}

\chapter{Appendix}
\label{ref:appendix}
\input{../Paper/suplementarymaterial.tex}

{\small
  \bibliographystyle{ieee}
  \bibliography{continuousocclusion}
}
\end{document}

### 2015-05-04 Paper/suplementarymaterial.tex
Latest version of presentation.

--- 2015-02-12 Paper/supplementary.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
-
-\usepackage{cvpr}
-\usepackage{times}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-%%%%%%%%%%% CVPR template packages end %%%%%%%%%%%%%%
-\usepackage{verbatim} % for comment environment
-% \usepackage{soul} % for \hl highlighting
-% Include other packages here, before hyperref.
-
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-
-%\cvprfinalcopy % *** Uncomment this line for the final submission
-
-\def\cvprPaperID{489} % *** Enter the CVPR Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-\DeclareMathOperator{\diag}{diag}
-
-% 3D pose of the cars and ego motion
-\newcommand{\uv}[1]{\hat{\mathbf{#1}}}
-\newcommand{\pos}[2]{\mathbf{p}^{(#1)}(#2)}
-\newcommand{\ori}[2]{\mathbf{\omega}^{(#1)}(#2)}
-\newcommand{\state}[2]{\mathbf{s}^{#1}(#2)}
-
-% ego pose
-\newcommand{\egop}[1][t]{\pos{c}{#1}}
-\newcommand{\egoo}[1][t]{\ori{c}{#1}}
-\newcommand{\egos}[1][t]{\state{c}{#1}}
-
-% relative pose between camera and car $i$
-\newcommand{\relp}[2]{\Omega^{#1}(#2)}
-\newcommand{\relpz}[2]{\Omega_z^{#1}(#2)}
-
-% 3D tracks on car $i$ in its own coordinate frame
-\newcommand{\tracklets}{\mathbf{X}^{(i)}_o}
-\newcommand{\tracklet}[1]{\mathbf{x}^{(i)}_{#1}}
-% track projections on camera
-\newcommand{\trackp}[1]{\mathbf{u}^{(i)}(#1)}
-\newcommand{\trackpj}[1]{\mathbf{u}_j(#1)}
-% Unclassified track point projected on camera
-\newcommand{\ucTrackp}{\mathbf{u}(t)}
-
-% dimensions of car $i$
-\newcommand{\dimsn}[1]{\mathbf{B}^{#1}}
-\newcommand{\expDimsn}{\hat{\mathbf{B}}}
-
-% projection function
-\newcommand{\projectionOf}[1]{\pi_{\relp{i}{t}}\left(#1\right)}
-\newcommand{\projectionOft}[1]{\pi_{\relp{i}{t+1}}\left(#1\right)}
-\newcommand{\centerProj}{\bar{\pi}_{\relp{i}{t}}(\dimsn{i})}
-\newcommand{\cornerProj}[1]{\pi^{#1}_{\relp{i}{t}}(\dimsn{i})}
-\newcommand{\triangleProj}[1]{\triangle^{#1}_{\relp{i}{t}}(\dimsn{i})}
-
-% bounding box corners on image
-\newcommand{\bb}[1]{\mathbf{d}^{#1}(t)}
-
-\newcommand{\Energy}[1]{\mathcal{E}^{it}_{\text{#1}}}
-\newcommand{\pEnergy}[1]{\mathcal{E}^{ijt}_{\text{#1}}}
-% Weighted energy
-\newcommand{\WEnergy}[1]{\lambda_{\text{#1}}\Energy{#1}}
-\newcommand{\EnergyCol}{\mathcal{E}^{ijt}_{\text{col}}}
-\newcommand{\WEnergyCol}{\lambda_{\text{col}}\EnergyCol}
-
-\newcommand{\occFreeProj}[1]{\Pi_{\relp{i}{t}}(#1)}
-\newcommand{\minx}{x_{\text{min}}}
-\newcommand{\miny}{y_{\text{min}}}
-\newcommand{\maxx}{x_{\text{max}}}
-\newcommand{\maxy}{y_{\text{max}}}
-\newcommand{\frontface}{F^i_\text{FF}(t)}
-
-\newcommand{\occ}[1]{o({#1})}
-\newcommand{\face}{F^i_k(t)}
-
-\newcommand{\invProjectionOf}[1]{\pi^{-1}_{\relp{i}{t}}\left(#1\right)}
-\newcommand{\occf}{f^i_{occ}(\mathbf{x}_j)}
-\newcommand{\occftot}{f_{occ}(\mathbf{x}_j)}
-\newcommand{\occft}[1]{f_{occ}(#1)}
-
-\newcommand{\ray}{\hat{\mathbf{r}}_j}
-\newcommand{\occfray}{f_{occ}(\lambda\ray)}
-\newcommand{\lambdadist}{f_{\lambda}(\trackpj{t-1}, \lambda)}
-
-\newcommand{\occfxi}{L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i)}
-\newcommand{\occfi}{L(\lambda \ray; \pos{i}{t-1}, \Sigma_i)}
-\newcommand{\assocP}{a^{(ij)}(\lambda)}
-\newcommand{\assocPk}{a^{(ij)}(\lambda_k)}
-
-\newcommand{\Ereproj}{E^{(ij)}_{\text{reproj}}}
-\newcommand{\Ptrans}{P^{(j)}_{\text{transmission}}(\lambda)}
-\newcommand{\Ptransmud}{P^{(j)}_{\text{transmission}}(\mu^{(i)}_d)}
-\newcommand{\Prefl}{P^{(ij)}_{\text{reflection}}(\lambda)}
-\newcommand{\dishort}{d_i(\mathbf{x})}
-
-\newcommand{\Lu}{L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)}
-\newcommand{\Llambda}{L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d)}
-
-\newcommand{\Gauss}{\mathcal{N}}
-\newcommand{\PropDist}{\mathcal{W}_j}
-
-\newcommand{\muijl}{\mu^{(ij)}_{\lambda}}
-\newcommand{\sigmaijl}{\sigma^{ij}_{\lambda}}
-
-\newcommand{\Sigmait}{\Sigma^{(i)^{-1}}_t}
-
-\newcommand{\muit}{\mu^(i)_t}
-\newcommand{\Sigmaic}{\Sigma'^{(i)^{-1}}_c}
-
-\newcommand{\muic}{{\mu^(i)_c}}
-\newcommand{\Sigmaicf}{\Sigma^{(i)^{-1}}_c}
-
-\newcommand{\muiu}{\mu^{(i)}_t}
-\newcommand{\Sigmaiu}{\Sigma^{(i)^{-1}}_u}
-
-\newcommand{\xt}{\mathbf{x}_t}
-\newcommand{\xc}{\mathbf{x}_c}
-
-\newcommand{\Rctot}{R}
-\newcommand{\tctot}{t}
-
-\newcommand{\tcmut}{t'}
-
-\newcommand{\Beizer}{B\'eizer }
-
-\newcommand{\LaneUncertainty}[1]{\Sigma_{L_m}(#1)}
-\newcommand{\projOnLane}[1]{\pi_{L_m(k)}(#1)}
-
-\newcommand{\xymin}[1]{#1_{\text{min}}}
-\newcommand{\xymax}[1]{#1_{\text{max}}}
-\newcommand{\xmin}{\xymin{x}}
-\newcommand{\xmax}{\xymax{x}}
-\newcommand{\ymin}{\xymin{y}}
-\newcommand{\ymax}{\xymax{y}}
-\newcommand{\Tr}[3]{{}^{#1}{#2}_{#3}}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-%\ifcvprfinal\pagestyle{empty}\fi
-%\setcounter{page}{4321}
-%\DeclareMathSymbol{\Tangent}
-\DeclareMathOperator{\sech}{sech}
-\DeclareMathOperator{\poly}{poly}
-\DeclareMathOperator*{\argmin}{\arg\min}
-
-\begin{document}
-%\title{Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.}
-\title{Fitting convex polyhedra to project 2D bounding box}
-\author{Vikas Dhiman\\
-  University of Michigan\\
-  Ann Arbor, MI, USA\\
-{\tt\small dhiman@umich.edu}
-\and
-Manmohan Chandraker\\
-NEC Laboratories America, Inc.\\
-Cupertino, CA, USA\\
-{\tt\small manu@nec-labs.com}
-\and
-Jason J Corso\\
-  University of Michigan\\
-  Ann Arbor, MI, USA\\
-{\tt\small jjcorso@eecs.umich.edu}
-}
-\maketitle
-
-\section{Supplementary Material}
-\subsection{Analytic initialization}
+\section{Analytic initialization}
 Problem: given detection bounding box and ground plane estimate the unknown parameters i.e.
@@
 
-\subsubsection{Necessary transforms}
+\subsection{Necessary transforms}
 Let the ground plane be known with parameters $(\uv{n}, h)$.
@@
 
-\subsubsection{System of equations}
+\subsection{System of equations}
 Let the detected bounding box be represented by $[\xmin, \ymin, \xmax, \ymax]^T$. Let $^cT_t$ be the transformation from tracklet to camera.
@@
 
-\subsubsection{Approximate solution}
+\subsection{Approximate solution}
 Initial approximate solution can be obtained by assuming that $\ymax$ is the projection either of point 
@@
 
-\subsubsection{Correspondence of bounding box limits to cuboid corners}
+\subsection{Correspondence of bounding box limits to cuboid corners}
 The $\xmin$ of bounding can be projection of either of the 8 points of the
@@
 
-\subsection{Numerical integration}
+\section{Numerical integration}
 Numerical integration is possible by computed by sampling. Samples need to be
@@
 
-\subsection{Sigma of ellipsoid}
+\section{Sigma of ellipsoid}
 \label{sec:sigmacomputation}
@@
 
-\subsection{Projection of ellipsoid to image}
+\section{Projection of ellipsoid to image}
 \newcommand{\mubar}{\bar{\mu}_i}
@@
 \begin{comment}
-  \subsection{Bounding box energy}
+  \section{Bounding box energy}
   \label{sec:totalBBoxEnergy}
@@
 
-  \subsubsection{Visible faces from bounding boxes}
+  \subsection{Visible faces from bounding boxes}
 
@@
 \begin{comment}
-  \subsubsection{Occlusion mask}
+  \subsection{Occlusion mask}
   % Initialize empty mask polygon $\occ{0}$ at depth $d=0$.
@@
 
-  \subsubsection{Algorithm to get faces based occlusion mask}
+  \subsection{Algorithm to get faces based occlusion mask}
   \label{sec:occlusionMaskFromOptVector}
@@
 
-  \subsubsection{Visibility fraction of a side}
+  \subsection{Visibility fraction of a side}
   Let the center of the projected hypothesized bounding box be $\centerProj$ and
@@
 \begin{comment}
-  \subsection{Occlusion free projection}
+  \section{Occlusion free projection}
   Occlusion free projection can be obtained by applying the precomputed occlusion
@@
 
-  \subsection{Perspective-visibility fraction}
+  \section{Perspective-visibility fraction}
 
@@
   \Sigma = E(\Delta x \Delta x^\top)$ the covariance of new data is given by
-  \begin{multline}
-    E((x + \Delta x)(x+\Delta x)^\top) = E(xx^\top) + E(x \Delta x^\top) \\
+  \begin{align}
+    E((x + \Delta x)(x+\Delta x)^\top) = E(xx^\top) + E(x \Delta x^\top) %\\
     + E(\Delta x x^\top) + E(\Delta x \Delta x^\top)
-  \end{multline}
+  \end{align}
   where the terms $E(x \Delta x^\top)$ denote the correlation between the data
@@
 
-% \subsubsection{Position in lane}
+% \subsection{Position in lane}
 %
@@
 
-%\subsubsection{Orientation within lane}
+%\subsection{Orientation within lane}
 %\begin{itemize}
@@
 
-\subsection{Collisions}
+\section{Collisions}
 
@@
 
-\subsubsection{Ellipse-ellipse intersection}
+\subsection{Ellipse-ellipse intersection}
 \label{sec:ellipseintersection}
@@
 
-\subsubsection{Smoother collision probability}
+\subsection{Smoother collision probability}
 \label{sec:smoothercollision}
@@
 
+\begin{comment}
 \section{Analytical attempt to integration}
@@
 
-  % \subsubsection{Sandwich of ellipsoids model}
+\end{comment}
+
+  % \subsection{Sandwich of ellipsoids model}
   % 
@@
 
-% \subsection{Object detection score}
+% \section{Object detection score}
 % \begin{align}
@@
 
-% \subsection{Object 2D bounding box with occlusion}
+% \section{Object 2D bounding box with occlusion}
 % Reproduced from \cite{song2014eccv} section 4.3
@@
 % 
-% \subsection{Orientation cues}
+% \section{Orientation cues}
 % There are two orientation cues (1) orientation from detection (2) orientation
@@
 % Appearance map is a shape prior that requires \emph{Scene labeling} input.
-\end{document}

### 2015-05-04 Paper/supplementary.tex
Latest version of presentation.

--- 2014-11-08 Paper/supplementary.tex
@@
 \maketitle
+\section{Supplementary Material}
+\input{suplementarymaterial.tex}
 
-\section{Supplementary Material}
-
-\subsection{Numerical integration}
-Numerical integration is possible by computed by sampling. Samples need to be
-generated from the association probability $\assocP$ for a given $j$. We take
-proposal distribution to be a GMM with modes around probable reflection points.
-The weights of all Gaussians in the mixture are proportional to the distance of
-the point $j$ from projection of ellipsoid centre i.e. 
-\begin{align}
-  A_{ij} = \frac{1}{Z_j}\exp(-(\trackpj{t} - \mu^i_u)^\top\Sigma_u^i(\trackpj{t} - \mu^i_u))
-\end{align}
-where $Z_j = \sum_{i=1}^N A_{ij}$ and $\mu^i_u$ and $\Sigma_u^i$ are described in \eqref{eq:muiudef} and \eqref{eq:sigmauidef} respectively.
-The range of Gaussian $G_i$
-must be in the interval $[\|\relp{i}{t}\|, \|\relp{i}{t}\| -
-\sqrt{3}\max(\dimsn{i})]$. Hence we take the mean as $\|\relp{i}{t}\| -
-\frac{\sqrt{3}}{2}\max(\dimsn{i})$ and variance as
-$\frac{1}{3}\max(\dimsn{i})^2$. The distribution from which we sample is 
-\begin{align}
-  \PropDist(\lambda) = \sum_i A_{ij} \Gauss(\lambda; \|\relp{i}{t}\| -
-  \frac{\sqrt{3}}{2}\max(\dimsn{i}), \frac{1}{\sqrt{3}}\max(\dimsn{i}))
-\end{align}
-And the numerical integral with $K$ samples is computed by
-\begin{align}
-    \int_1^{\infty}
-    \assocP
-    \Ereproj(\lambda)
-    d\lambda
-    =
-    \frac{1}{K}\sum_k \Ereproj \frac{\assocPk}{\PropDist(\lambda_k)}
-\end{align}
-where $\lambda_k$ is the $k$th sample drawn from $\PropDist(\lambda)$.
-
-\subsection{Sigma of ellipsoid}
-\label{sec:sigmacomputation}
-
-\begin{align}
-  \muit &= \begin{bmatrix}
-  0& 0& \frac{h}{2}
-  \end{bmatrix}^\top\\
-  \Sigmait &= \begin{bmatrix}
-    \frac{4}{l^2} & 0 & 0 \\
-    0 & \frac{4}{w^2} & 0 \\
-    0 & 0 & \frac{4}{h^2}
-  \end{bmatrix}
-\end{align}
-
-In tracklet coordinates the equation of ellipsoid is 
-\begin{align}
-  (\xt - \muit)^\top \Sigmait (\xt - \muit) = 1
-\end{align}
-
-Moving to camera coordinates
-\begin{align}
-  (\Rctot \xc + \tctot - \muit)^\top \Sigmait (\Rctot \xc + \tctot - \muit) = 1
-\end{align}
-
-Let $\tcmut = \tctot - \muit$
-\begin{align}
-  (\Rctot \xc + \tcmut)^\top \Sigmait (\Rctot \xc + \tcmut) = 1
-\end{align}
-\begin{align}
-  \xc^\top \Rctot^\top \Sigmait \Rctot \xc + 2 (\Rctot^\top \tcmut)^\top  \Rctot^\top\Sigmait \Rctot \xc
-  + \tcmut^\top \Sigmait \tcmut = 1
-\end{align}
-Let $\Sigmaic = \Rctot^\top \Sigmait \Rctot$ and $\muic = - \Rctot^\top
-\tcmut$
-\begin{align}
-  (\xc - \muic)^\top\Sigmaic(\xc - \muic) - \muic^\top\Sigmaic\muic +
-  \tcmut^\top \Sigmait \tcmut = 1
-\end{align}
-Let $\Sigmaicf = \frac{\Sigmaic}{1 - \tcmut^\top \Sigmait \tcmut +
-\muic^\top\Sigmaic\muic}$
-\begin{align}
-(\xc - \muic)^\top\Sigmaicf(\xc - \muic) = 1
-\end{align}
-
-Hence, we have following expression for mean and sigma of ellipsoid:
-\begin{align}
-  \label{eq:ellipsoidMeanSigma}
-  \muic &= - \Rctot^\top \tcmut \\
-  \Sigmaicf &= \frac{\Sigmaic}
-{1 - \tcmut^\top \Sigmait \tcmut + \muic^\top\Sigmaic\muic}
-\end{align}
-
-\subsection{Projection of ellipsoid to image}
-\newcommand{\mubar}{\bar{\mu}_i}
-The perspective projection of an ellipsoid in general is not an ellipsoid in
-general. We approximate the projection of ellipsoid by projecting a slice
-through the ellipsoid. We choose the slice as the plane perpendicular to the
-line joining the center of ellipsoid to the optical center of camera. Let
-$\muic$ and $\Sigmaicf$ be the parameters of ellipsoid describing the ellipsoid
-in camera coordinates. The any point $x$ on the plane satisfies
-$x^\top\frac{\muic}{\|\muic\|} = \|\muic\|$. We introduce 
-$\mubar = \frac{\muic}{\|\muic\|^2}$ for notational simplicity. Hence, we want
-to project the points that satisfy both the equation of chosen plane and the 
-ellipsoid i.e.
-\begin{align}
-  \mubar^\top x = x^\top\mubar &= 1\\ 
-  (x-\muic)^\top\Sigmaicf(x-\muic) &= 1 \enspace.
-\end{align}
-We rewrite $\muic = \muic\mubar^\top x$, and $1 = x^\top\mubar \mubar^\top x$
-\begin{align}
-  (x-\muic\mubar^\top x)^\top\Sigmaicf(x-\muic\mubar^\top x) &= x^\top\mubar \mubar^\top x \enspace,
-\end{align}
-which is equivalent to 
-\begin{align}
-  x^\top\left((I-\muic\mubar^\top)^\top\Sigmaicf(I-\muic\mubar^\top) - \mubar \mubar^\top\right)x &= 0\enspace.
-\end{align}
-
-Note that if $u$ is a projection of $x$ to camera with intrinsic parameters
-$K$, then $x = K^{-1}u$ where $u$ is in homgeneous coordinates. Hence the above equation can be re-written as
-\newcommand{\Sproj}{\Sigma^{-1}_{\text{proj }i}}
-\newcommand{\Sperpcut}{\Sigma^{-1}_{\text{perpcut }i}}
-\begin{align}
-  u^\top\Sproj u &= 0\enspace, 
-\end{align}
-where $\Sproj = K^{-\top}\Sperpcut K^{-1}$ and 
-\begin{align}
-  \Sperpcut = (I-\muic\mubar^\top)^\top\Sigmaicf(I-\muic\mubar^\top) - \mubar \mubar^\top \enspace.
-\end{align}
-
-\begin{comment}
-  \subsection{Bounding box energy}
-  \label{sec:totalBBoxEnergy}
-  With abuse of notation we represent the four sides of hypothesized bounding
-  box by $\projectionOf{\dimsn{i}}$ and detected bounding box by $\bb{i}$.
-  Suppose the bounding box $i$ is occluded by bounding box $i$ then the
-  bounding box energy becomes a pairwise term.
-
-  \begin{multline}
-    \pEnergy{occ}(\relp{i}{t}, \dimsn{i}, \relp{j}{t}, \dimsn{j}) = \\
-    \sum_s \rho^{ijs}(t)\projectionOf{\dimsn{i}}_s - \bb{i}_s
-               %\sum_{i=1}^N \sum_{t=s_i}^{e_i}
-    %\sum_kp_{ik}^{\text{track}}(\projectionOf{\dimsn{i}} - \bb{k})^\top \pmb{\rho}(i,j,t)
-  \end{multline}
-  where $\rho^{ijs}(t)$ is the visibility fraction of the side $s$ of the
-  bounding box. We need to compute visibility fraction we need to compute the
-  occlusion mask which is explained in next few sections.
-
-  \subsubsection{Visible faces from bounding boxes}
-
-  \begin{figure}[h]
-    \includegraphics[width=\columnwidth]{graphics/maxFacesVisible.pdf}
-    \caption{Only three faces can be visible out of six faces of a bounding
-    box.}
-  \end{figure}
-
-  Each bounding box has 6 faces of which only 3 can be visible.
-  Sort the vertices in increasing order of depth. The closest vertex has three
-  neighboring faces. All the faces that are visible must be a subset of these
-  three. Use first three vertices to
-  define the front face (say $\frontface$). Also identify the four 3D points
-  that correspond to min/max in x and y direction in the image. If all min-max 4
-  points are same as vertices of $\frontface$, then we have only one plane
-  visible. If $\{\minx, \maxx\} \not\subset \frontface \land \{\miny, \maxy\}
-  \not\subset \frontface$ then we have 3 planes visible. Otherwise we have just
-  two planes visible. Let number of planes visible be $n_F$.
-
-  \begin{align}
-    n_F &= \begin{cases}
-    1 & \text{if }\{\minx, \maxx, \miny, \maxy\} =
-    \frontface\\
-    2 & \text{else if }\{x_{\text{min}}, x_{\text{max}}\} \subset \frontface \lor
-    \{y_{\text{min}}, y_{\text{max}}\} \subset \frontface
-    \\
-    3 & \text{else if }\{x_{\text{min}}, x_{\text{max}}\} \not\subset \frontface \land
-    \{y_{\text{min}}, y_{\text{max}}\} \not\subset \frontface
-    \end{cases}
-    \label{eq:nfaces}
-  \end{align}
-
-  First vertex restrict possible visible faces to three faces. If $n_F = 3$,
-  then all three of these faces are visible. If $n_F = 2$, use second closest
-  vertex to restrict visible faces to just two. If $n_F = 3$, then front face 
-  $\frontface$ is the only visible face.
-\end{comment}
-
-\begin{comment}
-  \subsubsection{Occlusion mask}
-  % Initialize empty mask polygon $\occ{0}$ at depth $d=0$.
-  % \begin{itemize}
-  %   \item Sort all cars in increasing order of depth
-  %   \item for each car $i$ in the sorted list
-  %     \begin{itemize}
-  %       \item Update mask polygon: \\
-  %         $\occ{\relpz{i}{t}} = \occ{d} \cup \projectionOf{\dimsn{i}}$
-  %       \item $d = \relpz{i}{t}$
-  %     \end{itemize}
-  % \end{itemize}
-
-  % Sort all planes in increasing order of depth.  This yields a cumulative
-  % occlusion mask function
-  Occlusion mask is a function that takes the relative depth $d$ from the car
-  camera and returns a binary mask that represents occlusions untill that depth.
-  Near to the camera occlusion mask is all empty (all zeros) and more occlusions
-  get added to the mask with distance.
-
-  \begin{align}
-    \occ{d} &= \begin{cases}
-    \phi & \text{if } 0 < d \le \relpz{1}{t}\\
-    \cup_{i=1}^j \projectionOf{F^i} & \text{if } \relpz{1}{t} < d \le \relpz{j+1}{t}
-    \end{cases}
-    \label{eq:occlusionmask}
-  \end{align}
-
-  where $\relpz{j}{t}$ is the depth of the $j$th TPs participant when sorted
-  by increasing depth.
-
-  \subsubsection{Algorithm to get faces based occlusion mask}
-  \label{sec:occlusionMaskFromOptVector}
-
-  This is an algorithm to compute occlusion mask Eq.\eqref{eq:occlusionmask}. We
-  represent the occlusion mask as a set of polygons.
-
-  Initialize empty mask polygon $\occ{0}$ at depth $d=0$.
-  \begin{enumerate}
-    \item Collect visible faces using Eq.\eqref{eq:nfaces} for all cars
-    %\item for each face get its closest and farthest vertex to the camera.
-    \item Create a sorted list of faces
-    % \item Create a sorted binary tree of
-    %   faces indexed by closed vertices.
-    \item Loop over list of sorted visible faces
-      \begin{enumerate}
-        \item Get the face(s) $\{\face\}$ closer to camera than this face
-        \item Add the faces to mask polygon (if not already added): \\
-          $\occ{\relpz{i}{t}} = \occ{d} \cup \projectionOf{\face}$
-        \item $d = \relpz{i}{t}$
-      \end{enumerate}
-  \end{enumerate}
-
-  To get the occlusion mask for a face use the farthest vertex of the face to
-  query $\occ{.}$.
-
-  \subsubsection{Visibility fraction of a side}
-  Let the center of the projected hypothesized bounding box be $\centerProj$ and
-  the four corners be $\{\cornerProj{k}\}_{k=1}^{4}$ . Each side and the center
-  of the bounding box form a triangle, for example $\triangleProj{1,2} =
-  \{\cornerProj{1}, \cornerProj{2}, \centerProj\}$. We take the visibility of
-  this triangle as a visibility of the side $s = (1,2)$. Hence the visibility
-  fraction of side is given by
-  \begin{align}
-    \rho^{ijs}(t) = \frac{\|\triangleProj{s} \setminus \occ{\relpz{i}{t}}\|}
-                         {\|\triangleProj{s}\|}
-     \label{eq:bboxEnergyFromOccMask}
-  \end{align}
-\end{comment}
-
-\begin{comment}
-  \subsection{Occlusion free projection}
-  Occlusion free projection can be obtained by applying the precomputed occlusion
-  mask to the face projection.
-  \begin{align}
-    \occFreeProj{\face} &= \projectionOf{\face} \setminus
-    \occ{\relpz{i}{t}}
-  \end{align}
-
-  \subsection{Perspective-visibility fraction}
-
-  Apart from occlusion, we want to account for the perspective affects. When an 
-  objects perspective projection is too small, detection and all related
-  evidences deteriorate. One way of this is to find out the projection ratio. In
-  fact, we can consolidate projection ratio and occlusion ratio in one term if
-  we consider the projection of 3D bounding box planes instead of the entire
-  bounding box.
-
-  \begin{align}
-    \rho^i_t &= \sum_{k=1}^{n_F}\frac{\relpz{i}{t}^2\|\occFreeProj{F^i_k(t)}\|}{f^2\|F^i_k(t)\|}
-  \end{align}
-
-  where $\occFreeProj{.}$ again means occlusion free projection. $f$ is the
-  focal length of the camera so that $\frac{f^2}{\relpz{i}{t}^2}\|F^i_k(t)\|$ is
-  the area of projected plane if there were no perspective effects.
-\end{comment}
-
-\begin{comment}
-
-\begin{table*}
-  \begin{tabular}{|l|r|r|l|}
-    \hline
-    func            & equation                      & ms per 6 frames &
-    comment \\
-    \hline
-    totalBBoxEnergy & Sec \ref{sec:totalBBoxEnergy} & 268 & \\
-    laneEnergy      & Sec \ref{sec:laneEnergy}      & 163 & \\
-    laneOrientationEnergy & Eq \eqref{eq:laneOrientationEnergy} & 155 & The
-    equation summed up for all 6 tracklets\\
-    collisionEnergyHellingerDistance & Eq 
-    \eqref{eq:collisionEnergyHellingerDistance} & 93  & \\
-    totalPosTransitionEnergy & Eq \eqref{eq:totalPosTransitionEnergy} & 15 & \\
-    totalSizeEnergy & Eq \eqref{eq:totalSizeEnergy} & 0.9 & \\
-
-    \hline
-    occlusionMaskFromOptVector & Sec \ref{sec:occlusionMaskFromOptVector} &
-    123 &
-    \\
-    bboxEnergyFromOccMask & Eq \eqref{eq:bboxEnergyFromOccMask} & 140 &  \\
-    vis\_area\_from\_triangle & $\|\triangleProj{s} \setminus
-    \occ{\relpz{i}{t}}\|$ & 76 & \\
-    \hline
-    distance2curve & $\text{DIST}(L_j(k), x)$ & 74 & Called 2 times per
-    tracklet \\
-    filterMapWaysByDistance & $M_{\text{close}} = \{m : \text{DIST}(.) < 50\} $ & 52 & \\
-    area\_of\_triangle & $\|\triangleProj{s}\|$ & 48 & called 4 times per
-    tracklet \\
-    occlusionMask & Step 3 of Sec \ref{sec:occlusionMaskFromOptVector} & 46 &
-    \\
-    \hline
-  \end{tabular}
-
-  \begin{tabular}{|l|r|r|l|}
-    \hline
-    func            & equation                      & ms per 6 frames &
-    comment \\
-    \hline
-    totalContPtTracksEnergy & Sec \ref{sec:totalContPtTracksEnergy} & 25000 &
-    \\
-    integrand & Eq \eqref{eq:integrand} & 23000 & \\
-    repmat & & 5000 & \\
-    assocCoeffEval & Eq \eqref{eq:assocCoeffEval} & 4000 & \\
-    evalPreflection & Eq \eqref{eq:analytic-prefl} & 3000 & \\
-    gradfocci & $\nabla \occf^\top \ray$ & 2040 & \\
-    associationCoefficientInit & Eq
-    \eqref{eq:ptransmissionInit}\eqref{eq:ellipsoidMeanSigma} & 1706 & \\
-    projectToImage & $\frac{Ku}{Ku(3)}$ & 4000 & Called ~8 times per edge\\
-    evalCumulativePtrans & \eqref{eq:evalCumulativePtrans} & 1178 & \\
-    ptransmissionApproxInit & \eqref{eq:ptransmissionInit} & 1000 & \\
-    ellipsoidCentreDist & $(x-\mu)^\top \Sigma (x-\mu)$ & 1000 & \\
-    squeeze & & 951 &\\
-    trackletToCamTransform & $R_{\ori{i}{t}}, t$ & 786 & \\
-    ellipsoidMeanSigma & Eq \eqref{eq:ellipsoidMeanSigma} & 812 & \\
-    \hline
-  \end{tabular}
-\end{table*}
-
-\end{comment}
-
-\begin{comment}%%%%%%%%%%%%% May or may not use %%%%%%%%%%%
-TODO: Write Introduction
-  NEC has already developed a monocular camera based structure from motion
-  system which is accurate for requirements of road scene understanding. So we
-  assume that egomotion is given as an observed variable in our graphical
-  model. And we have following features to our disposal for estimating the 3D
-  poses (position + orientation) of traffic participants (TPs):
-  \begin{description}
-    \item[Ground plane] We assume that all the TPs lie on a common ground
-      plane. This is not particularly true for the cars that are parked off the
-      road. However, for autonomous driver assistance applications we can
-      ignore those cars.
-    \item[Detections] We assume that 2D car detections are available with tracking informations.
-    \item[Point tracks] We assume that 2D point tracks are available.
-    \item[GPS and Map information] We assume that GPS information is available
-      and we use openstreetmaps.org for pulling out local map for the current
-      car's position.
-    \item[Lane Information] We assume the lane detection works well and lane
-      information is available.
-    \item[Size prior] The distribution of size of cars follows gaussian distribution.
-    \item[Collision] A reasonable output of the system donot has any overlapping cars.
-  \end{description}
-\end{comment}
-
-\begin{comment}
-  Consider that we have a set of measurements whose mean and variance are known $\mu = E(x)$ and $\Sigma = E ((x - \mu_x)(x - \mu_x)^\top)$. We want to know the
-  affect of uncertainty on mean and variance of existing observations. On adding
-  noise $[\Delta x, \Delta y]^\top$ with zero mean and covariance $\Delta
-  \Sigma = E(\Delta x \Delta x^\top)$ the covariance of new data is given by
-  \begin{multline}
-    E((x + \Delta x)(x+\Delta x)^\top) = E(xx^\top) + E(x \Delta x^\top) \\
-    + E(\Delta x x^\top) + E(\Delta x \Delta x^\top)
-  \end{multline}
-  where the terms $E(x \Delta x^\top)$ denote the correlation between the data
-  vector and the uncertainty in the data. Although we understand that in our case
-  the data is the appearance based detection score and uncertainty because of
-  occlusion is closely related to the appearance and hence detection score, we
-  assume independence between $x$ and $\Delta x$. Hence our resultant covariance
-  matrix $ E((x + \Delta x)(x+\Delta x)^\top) = \Sigma + \Delta \Sigma$
-  are 4D. But that should not be a problem because the detection scores are
-  modeled as $[x_{\text{min}}, y_{\text{min}}, x_{\text{max}},
-  y_{\text{max}}]^\top$, we can stack the vectors in the soft occlusion region
-  domain as the regions are independent of min or max variation. The parameters
-  of 4D occlusion distribution are given by
-
-  \begin{align}
-    \mu'_{Oij} = [\mu_{Oij}^\top \mu_{Oij}^\top]^\top
-    \Sigma'_{Oij} = \begin{bmatrix}
-      \Sigma_{Oij} & \Sigma_{Oij} \\
-  \Sigma_{Oij} & \Sigma_{Oij}
-    \end{bmatrix}
-  \end{align}
-
-  With our
-  discussion so far, the function $O_{ij}(.)$ gives an additional measure of
-  uncertainty associated with each point in the space.
-\end{comment}
-
-% Explanation of Beizer curves is not needed %%%%%%%%%%%%%%%%%%%
-% A lane is modeled by four control points of a \Beizer curve $L_j = \{l_0, l_1,
-% l_2, l_3\}$. The parametric curve is given by $L_j(k) = \sum_{i=0}^3 {}^3C_i
-% (1-t)^{3-i}t^i l_i$. \Beizer are double differentiable so one can find
-% tangents ($L'_j(k)$) and normals $R_{\frac{\pi}{2}}L'_j(k)$ where 
-% $R_{\frac{\pi}{2}} = \begin{bmatrix} 0 & -1 \\ 1 & 0 \end{bmatrix}$ is
-% $90^\circ$ rotation matrix.
-
-%Using standard algorithms \cite{ma2003point, chen2007improved}, we 
-%approximate the closest point on a \Beizer curve $k_x = \projOnLane{x}$.
-%Consequently one can get solutions for shortest distance $s =
-%\text{DIST}(L_j(k), x)$ and orientation at a closest point on the lane
-%$\mathbf{t} = \text{TAN}(L_j(k), x)$.
-
-% \subsubsection{Position in lane}
-%
-% \begin{align}
-%   \Energy{plane} &=
-%   \min_{j = 0}^{n_l} \text{DIST}(L_j(k), \pos{i}{t})
-% \end{align}
-%
- % 
- % We normalize it with the confidence in lane positions.
- % 
- % \begin{align}
- %   \Energy{plane} &=
- %   \min_{m = 0}^{n_l} \text{DIST}(L_m(k), \pos{i}{t})
- %   \LaneUncertainty{\pos{i}{t}}
- % \end{align}
-
-%\subsubsection{Orientation within lane}
-%\begin{itemize}
-%\end{itemize}
-
-% \begin{align}
-%   \Energy{olane} &= 1 - \text{TAN}(L_l(k),  \pos{i}{t})
-%   \cdot
-%   \ori{i}{t}
-% \end{align}
-% 
-% 
-% 
-% This model needs to be scaled by uncertainty. For example, if we want to say
-% that the farther the lane is from the camera we are less sure about lane
-% orientation and hence this evidence term we scale it by say square of distance
-% of the car position from camera.
-
-% \begin{align}
-%   \Energy{olane} &= 
-%   (1 - \ori{i}{t} \cdot \text{TAN}(L_{m^*}(k),  \pos{i}{t}) )
-%   
-% \end{align}
-% where $m^* = \arg \min_m \text{DIST}(L_m(k), \pos{i}{t})$
-
-\begin{comment}
-
-\subsection{Collisions}
-
-The collision constraint among TPs can be modelled by
-pairwise distance based constraints. But having constraints between each pair
-of participants is bound to create cycles and computational inefficient.
-Among game developers it is common to use spatial hashing to find collision
-candidates and use pairwise constraints only among those. While this will
-enable us to speed up collision checking, we will still end up inducing cycles
-in the model. There are two ways to break these cycles, 1) disable the cross
-lane collision checking 2) created a weighted graph among collision
-candidates weighted by distance and then find a minimum spanning
-tree to break cycles. (1) is too strong of an assumption hence we focus on the
-second approach.
-
-There are two possible approaches to find collision among candidates (1)
-polygon intersection methods (2) soft ellipse intersection method. Boost
-provides scan line based approach to find intersections of polygons. Since our
-polygons are simple rectangles, this approach can be very fast. Other approach
-is to approximate rectangles with ellipses and finding if the ellipses
-intersect.  This intersection can be computed analytically.
-
-\begin{align}
-  \EnergyCol &= \begin{cases}
-  \infty &\text{if INTERSECTS}(\pos{i}{t}, \dimsn{i}, \pos{j}{t},
-  \dimsn{j})\\
-  0 &\text{otherwise}
-  \end{cases}
-\end{align}
-
-%For smoother collision probability see Section \ref{sec:smoothercollision}.
-
-\subsubsection{Ellipse-ellipse intersection}
-\label{sec:ellipseintersection}
-A rectangle with sides $2a$ and $2b$ can be approximated by an ellipse with
-equation $\frac{x^2}{a^2} + \frac{y^2}{b^2} = 1$. But this ellipse is inside
-the rectangle. To enclose the rectangle, scale the ellipse by a factor of
-$\sqrt{2}$. The equation becomes, $\frac{x^2}{2a^2} + \frac{y^2}{2b^2} = 1$.
-For rotation $\psi$ and center $\pos{i}{t}$, the equation of ellipse can be
-re-written as:
-\begin{align}
-  (\mathbf{x} - \pos{i}{t})^\top\Sigma_i^{-1}(\mathbf{x} - \pos{i}{t}) &= 1
-\end{align}
-where
-\begin{align}
-  \Sigma_i^{-1} &= \begin{bmatrix}
-    \frac{\cos^2{\psi}}{2a^2} + \frac{\sin^2{\psi}}{2b^2} &
-    \frac{\cos{\psi}\sin{\psi}}{2}(\frac{1}{b^2} - \frac{1}{a^2})\\
-    \frac{\cos{\psi}\sin{\psi}}{2}(\frac{1}{b^2} - \frac{1}{a^2}) &
-    \frac{\sin^2{\psi}}{2a^2} + \frac{\cos^2{\psi}}{2b^2} \\
-  \end{bmatrix}
-\end{align}
-
-% A point $\mathbf{x}$ is inside both ellipse $i$, $j$ if and only if
-% \begin{multline}
-%   (\mathbf{x} - \pos{i}{t})^\top\Sigma_i^{-1}(\mathbf{x} - \pos{i}{t}) +\\
-% (\mathbf{x} - \pos{j}{t})^\top\Sigma_j^{-1}(\mathbf{x} - \pos{j}{t})
-%   \le 2
-% \end{multline}
-% which is equivalent to
-% \begin{multline}
-%   (\mathbf{x} - \mu_c)^\top\Sigma_c^{-1}(\mathbf{x} - \mu_c)
-%   + \pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t}\\
-%   + \pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t}
-%   - \mu_c^\top\Sigma_c^{-1}\mu_c
-%   \le 2
-% \end{multline}
-% where $\Sigma_c = (\Sigma_i^{-1} + \Sigma_j^{-1})^{-1}$ and $\mu_c =
-% \Sigma_c(\Sigma_i^{-1}\pos{i}{t} + \Sigma_j^{-1}\pos{j}{t})$.
-% 
-% There is at least one point inside both ellipse if 
-% \begin{align}
-%   \pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t}
-%   + \pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t}
-%   - \mu_c^\top\Sigma_c^{-1}\mu_c
-%   &\le 2
-% \end{align}
-% 
-% The left hand side can be interpreted as distance between two ellipses, which
-% is 2 when the two ellipses collide and $0$ when two ellipse completely
-% overlap.
-
-\subsubsection{Smoother collision probability}
-\label{sec:smoothercollision}
-%The above mentioned ellipse-ellipse intersection formulation gives us an
-%insight: the distance between two oriented ellipse boundaries can be again
-%formulated as a distance metric\footnote{TODO:proof}.
-Instead of using Gaussians to model
-collision constraints as done by \cite{milan2013continuous}, we use a more
-steeper sigmoid function.
-\begin{multline}
-  \EnergyCol = \frac{1}{1 +
-\exp(-k(\pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t})-1)}\\
-\frac{1}{1 +
-\exp(-k(\pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t})-1)}
-\end{multline}
-where $k$ is steepness parameter.
-%$d(.)$ is the distance metric defined as:
-%\begin{multline}
-%  d(\pos{i}{t}, \dimsn{i}, \pos{j}{t}, \dimsn{j})
-%  =
-%  \pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t} \\
-%  + \pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t}
-%  - \mu_c^\top\Sigma_c^{-1}\mu_c
-%\end{multline}
-
-\end{comment}
-
-\begin{comment}
-
-  %%%%%%%%%%%%%%%% Analytical attempt to integration %%%%%%%%%%%%%%%%%%%%%
-  \begin{align}
-
-    E^i_{\text{reproj}}(\lambda) &= \left\|\trackpj{t} - \frac{p_{1:2}\lambda +
-  q_{1:2}}{p_3\lambda + q_3}\right\|^2\\
-  &= \frac{(p_1\lambda + q_1 - u_{j1}(t))^2 + (p_2\lambda + q_2 - u_{j2}(t))^2}
-  {(p_3\lambda + q_3)^2}\\
-  &= \frac{a\lambda^2 + b\lambda + c}{(p_3\lambda + q_3)^2}
-  \end{align}
-  where $a = p_1^2 + p_2^2$, $b = 2p_1(q_1 - u_{j1}(t)) + 2p_2(q_2 - u_{j2}(t))$
-  and $c = (q_1 - u_{j1}(t))^2 + (q_2 - u_{j2}(t))^2$
-
-  So, in terms of $\lambda$ we have the integrand as
-  \begin{multline}
-    \int_1^\infty
-    \prod_i (1 +
-    \tanh(\poly^{(1)}_{ij1}(\lambda)))\sech^4(\poly^{(2)}_{ij2}(\lambda))\\
-    (\max\{ 0, \poly^{(2)}_{ij3}(\lambda) \})^2
-    \frac{\poly^{(2)}_{ij4}(\lambda)}{(\poly^{(1)}_{ij5}(\lambda))^2}d\lambda
-  \end{multline}
-  where $\poly^{(n)}_{ijk}$ denotes a polynomial $k$ of order $n$ dependent upon $i$th
-  TP and $j$th point. This integrand is still too difficult to
-  be solved or approximated analytically.
-
-  We approximate the expression,
-
-  \begin{multline}
-    \prod_i \Llambda
-  \sech^4\left(\frac{k}{2}\dishort\right)(\max\{ 0, \nabla k\dishort^\top\ray \})^2
-  \end{multline}
-
-  with a
-  gaussian with mean at $\mu^{ij}_{\lambda} : d_i(\mu^{ij}_{\lambda}\ray) = 0$
-  standard deviation as $\sigma^{ij}_{\lambda} =
-  \frac{\pi}{2\sqrt{3}kd(\mu^{ij}_{\lambda}\ray, \pos{i}{t-1})}$  and magnitude as the
-  expression computed at mean. An integrand of the form
-  \begin{align}
-    \frac{\poly^{(2)}_{ij4}(\lambda)}{(\poly^{(1)}_{ij5})^2}
-      e^{\frac{- (\lambda -
-  \mu^{ij}_{\lambda})^2}{\sigma^{ij}_{\lambda}}}
-  \end{align}
-   is integrable analytically by parts.
-
-   \begin{align}
-   \int_1^\infty \frac{a\lambda^2 + b\lambda + c}{(p_3\lambda + q_3)^2}e^{\frac{- (\lambda -
-  \mu^{ij}_{\lambda})^2}{\sigma^{ij}_{\lambda}}}d\lambda
-   \end{align}
-   Substituting $y = \frac{\lambda - \mu^{ij}_{\lambda}}{\sigma^{ij}_{\lambda}}$
-
-   \begin{align}
-     \int_1^\infty \frac{a_y y^2 + b_yy + c_y}
-     {(p_{3y}y + q_{3y})^2}e^{-y^2}dy
-   \end{align}
-   where $a_y = a(\sigmaijl)^3$, $b_y = (2a\muijl + b)(\sigmaijl)^2$ and $c_y =
-   (2a(\muijl)^2 + b\muijl + c)\sigmaijl$ and $p_{3y} = \sigmaijl p_3$ and
-   $q_{3y} = p_3\muijl + q_3$
-
-  % \subsubsection{Sandwich of ellipsoids model}
-  % 
-  % \begin{enumerate}
-  %   \item Model $\occf$ as
-  %     sigmoid over ellipse instead of a gaussian.
-  %     \begin{align}
-  %       \occf = \frac{1}{
-  %       1 + e^{-(\mathbf{x} - \pos{i}{t})^\top
-  %         \Sigma_i (\mathbf{x} - \pos{i}{t}))}}
-  %     \end{align}
-  %   \item To get the intuition of this occupancy function imagine the traffic
-  %     participant as layered ellipsoid. The innermost ellipsoid has very high
-  %     probability (approx 1) of being occupied. The outermost ellipsoid has very
-  %     low probability (approx 0) of being occupied. We will just consider the
-  %     occupancy interplay within these two ellipsoids.
-  %   \item Project outer ellipsoids of all TP's on the image.
-  %   \item Consider the ellipses that bound the track point $\trackpj{t-1}$.
-  %   \item For each ellipse do
-  %     \begin{itemize}
-  %       \item Case 1: The ray intersects inner ellipse
-  %         Now the ray intersects both inner and outer ellipse
-  %         Compute the intersection points on both the ellipses
-  %         Compute the gradient function $\nabla\occf^\top \ray$ at
-  %         the mid point of the two intersections. Use this as the magnitude of
-  %         gaussian mixture component centered at the mid point of intersections
-  %         and spread such that 97 percentile of probability mass of guassian is
-  %         within the intersection points. With the same parameters model the
-  %         transimission probability with product of logistic function $L(.)$.
-  %       \item Case 2: The ray do not intersects inner ellipse.
-  %         The ray just passes through the outer ellipse. Find the point on the
-  %         ray closest to the center of the ellipse. Compute gradient function
-  %         at the closest point, which will be again used as the magnitude of
-  %         gaussian mixture component centered at the closest point and spread
-  %         such that 97 percentile of probabiltiy mass of gaussian is within the
-  %         two intersection points of the ellipse. With the same parameters model
-  %         the transimission probability with product of sigmoids.
-  %     \end{itemize}
-  %   \item Now this approximated $\lambdadist = \sum N(.) \prod (1 - L(.))$ can
-  %     be used in integrating the error over $\lambda$.
-  % \end{enumerate}
-  \newpage
-
-  \clearpage
-  %%%%%%%%%%%%%%%% Analytical attempt to integration %%%%%%%%%%%%%%%%%%%%%
-\end{comment}
-
-% \subsection{Object detection score}
-% \begin{align}
-% \Energy{det}(\relp{i}{t}, \dimsn{i}) = 
-%              \frac{1}{S_t^2(\projectionOf{\dimsn{i}})}
-% \end{align}
-
-% \subsection{Object 2D bounding box with occlusion}
-% Reproduced from \cite{song2014eccv} section 4.3
-% 
-% \begin{multline}
-%   \Energy{box}(\relp{i}{t}, \dimsn{i}) =
-%              %\sum_{i=1}^N \sum_{t=s_i}^{e_i}
-%              \rho^i_t \|\projectionOf{\dimsn{i}} -
-%              \bb{i}\|^2
-% \end{multline}
-% 
-% where $S_t(.)$ is the function to approximate the detection scores using
-% mixture of Gaussian model and $\rho^i_t$ is the visibility fraction. 
-% 
-% % It can be
-% % computed by using polygon intersection algorithms.
-% % \begin{align}
-% %   v^i_t &= \frac{\|\occFreeProj{\dimsn{i}}\|}
-% %                 {\|\projectionOf{\dimsn{i}}\|}
-% % \end{align}
-% % where $\|.\|$ represents the norm or the area of the polygon.
-% 
-% Another approach is to just consider the corner points in the occlusion free
-% area.  Say $\projectionOf{\dimsn{i}} = [b^i_1, \dots, b^i_4]$.
-% \begin{multline}
-%   \Energy{box}(\relp{i}{t}, \dimsn{i}) =
-%              %\sum_{i=1}^N \sum_{t=s_i}^{e_i}
-%              %S_t^2(\projectionOf{\dimsn{i}})
-%              \sum_{{b^i_j} \in \occFreeProj{\dimsn{i}}}
-%              \|b^i_j - d^i_j\|^2
-% \end{multline}
-% 
-% In the opinion of this author, the second approach is better because the
-% visibility is an area based measure while the error metric is point to point
-% distance based measure. If we use bounding overlap instead of corner to corner
-% distance, the use of visibility fraction makes much more sense. However, one
-% can argue that even detection score is an area based measure. 
-% 
-% Hence a third approach can be 
-% \begin{multline}
-%   \Energy{box}(\relp{i}{t}, \dimsn{i}) =
-%              %\sum_{i=1}^N \sum_{t=s_i}^{e_i}
-%   \rho^i_t \|\projectionOf{\dimsn{i}} \ominus \bb{i}\|
-% \end{multline}
-% where $A \ominus B$ represents the symmetric difference between set $A$ and set
-% $B$ and is given by $A \ominus B = (A \cup B) \setminus (A \cap B)$.
-% One may argue that we can take the intersection of occlusion free projection 
-% and get rid of the visibility fraction, but that would be a little off the 
-% detection bounding box is usually more close to the projection of full car
-% instead of the just the visible portion.
-% 
-% 
-% \subsection{Orientation cues}
-% There are two orientation cues (1) orientation from detection (2) orientation
-% from appearance map \cite{yao2012describing}.
-% 
-% \begin{align}
-%   \Energy{ori} &= 
-%   %S_t^2(\projectionOf{\dimsn{i}})
-%   \rho^i_t(1 - \cos({\omega}^i_{\text{det}} - \ori{i}{t})
-% \end{align}
-% 
-% Appearance map is a shape prior that requires \emph{Scene labeling} input.
 \end{document}

### 2015-05-04 poster/plot_convergence.m

@@ -1,0 +1,11 @@
+filelist = {'results/mcmc_inference_cputime.txt', ...
+    'results/coordinateDescent_cputime.txt'};
+colors = 'rgb';
+for i=1:numel(filelist)
+    data = dlmread(filelist{i});
+    plot(data(:, 1), data(:, 2), colors(i));
+    hold on;
+end
+legend('MCMC', 'Coordinate Descent');
+xlabel('CPU time');
+ylabel('Energy');

### 2015-05-11 CVPR/quals2report.tex
Latest version of presentation. Could not add fading because it makes my latex to crash with segmentation fault.

@@
-\documentclass[10pt,letterpaper]{report}
+\documentclass[letterpaper]{report}
 
@@
 \DeclareMathOperator*{\argmin}{\arg\min}
+
+\newcommand{\EnergyBBox}{{\pEnergy{bbox}}}
+\newcommand{\EnergyTrack}{{ \pEnergy{track}}}
+\newcommand{\EnergyTrackNoOcc}{{\pEnergy{trackNoOcc}}}
+\newcommand{\EnergyLane}{{\Energy{lane}}}
+\newcommand{\EnergySize}{{\Energy{size}}}
+\newcommand{\EnergyDyn}{{\Energy{dyn}}}
+\newcommand{\EnergyDynHol}{{\Energy{dyn-hol}}}
+\newcommand{\EnergyDynOri}{{\Energy{dyn-ori}}}
+\newcommand{\EnergyDynVel}{{\Energy{dyn-vel}}}
+
+\newcommand{\xmin}{\xymin{x}}
+\newcommand{\xmax}{\xymax{x}}
+\newcommand{\ymin}{\xymin{y}}
+\newcommand{\ymax}{\xymax{y}}
 
@@
 
+\chapter{Future Work}
+
+We have come up with model of Object detection energy with occlusion, and our plan is evaluate it
+and integrate it with the model.
+
+\section{Object detection energy with occlusion}
+
+Object detection is usually followed by non-maximal suppression that results in
+discarding similar bounding boxes. When we are jointly optimizing detections
+with other cues, it is not usually desirable to go with a single bounding box.
+Hence, we keep all the bounding box detections by approximating them with
+multi-modal sum of Gaussian like logistic functions. We fit the parametric function of the form 
+%
+\begin{align}
+  S(\bb{i}) = \sum_k A_k \exp(-(\bb{i}-\mu^{(d)}_k)^\top \Sigma^{(d)-1}_k
+  (\bb{i}-\mu^{(d)}_k))
+\end{align}
+%
+to detection scores, by non-linear error minimization with initialization from
+non-maximal suppressed outputs. Here $\mu^{(d)}_j$ is one of the $k$ modes as a
+4D vector representing a single bounding box as $[\minx, \miny, \maxx,
+\maxy]^\top$. The optimization is constrained with symmetry and positive
+definiteness of $\Sigma^{(d)-1}_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
+
+\subsection{Detection scores with occlusion reasoning} 
+With our model of $\Ptrans$ described in Section \ref{sec:TPmodel}, we can
+compute the probability of a point $\mathbf{u}$ on image be occluded assuming
+the point is on TP $i$ with mean depth $\mu^{(i)}_d$ as
+\begin{align}
+  O_{i}(\mathbf{u}, \mu^{(i)}_d) = 1 - \Ptransmud \enspace .
+\end{align}
+
+If we know a portion of our proposed detection bounding box is known to be
+occluded, then we would like to decrease the confidence in the detection score
+about the localization of that end of the object. Assuming that the occlusion
+is often on the boundary of detection bounding boxes, we want to decrease our
+confidence on the mean detection boundaries around the occluded boundaries.
+%One of the simplest ways will be to scale the appropriate diagonal element of
+%$\Sigma_j$ by an appropriate scaling factor proportional to occlusion. But this
+%does not model explain the affect of occlusion on the non diagonal terms.
+%Hence, we choose a covariance addition model where we compute a occlusion
+%covariance matrix, that provides a measure of occlusion in each direction.
+To re-model our detection scores scaled by continuous occlusion we sample
+$O_{i}(\mathbf{u}, \mu^{(i)}_d)$ at the hypothesized detection boundaries from
+GMM $S(.)$ and we augment the detection boundary covariance matrix by
+$\mathcal{P}_{j} = \rho_{j}\rho_{j}^\top$ where $\rho_{j} = O_{j}(\mathbf{u},
+\mu^{(i)}_d)$. The new covariance matrix in detection score is given by 
+  $\Sigma'^{(d)}_j = \mathcal{P}_{j} + \Sigma^{(d)}_j$.
+%
+%\begin{align}
+%\end{align}
+%
+The detection scores GMM with occlusion is given by replacing the covariance
+matrix
+%
+\begin{align}
+  S'(\bb{i}) =
+  \sum_j A_j \exp(-(\bb{i}-\mu^{(d)}_j)^\top \Sigma'^{(d)-1}_j
+  (\bb{i}-\mu^{(d)}_j))
+\end{align}
+
+The energy of detection scores is simply take to be the inverse of the detection score.
+\begin{align}
+  \Energy{detect}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}
+\end{align}
+
 \chapter{Appendix}
-\label{ref:appendix}
+\label{sec:appendix}
 \input{../Paper/suplementarymaterial.tex}

### 2015-05-11 presentation/inference.tex
Latest version of presentation. Could not add fading because it makes my latex to crash with segmentation fault.

\begin{frame}{Inference}
  \begin{itemize}

    \item
      Metropolic Hastings Inference with Gaussian proposal density (MCMC)

    \item
      Block Coordinate Descent with two kinds of blocks
      \begin{itemize}
        \item
          Optimize pose variables only 
        \item
          Optimize dimension variables only 
      \end{itemize}
  \end{itemize}
  \includegraphics[width=0.5\textwidth, trim=4.5cm 7cm 4.5cm 7cm, clip]{graphics/mcmc_vs_coordinate_descent_60.pdf}
  \includegraphics[width=0.5\textwidth, trim=4.5cm 7cm 4.5cm 7cm, clip]{graphics/mcmc_vs_coordinate_descent_192.pdf}
\end{frame}

### 2015-05-11 presentation/intro.tex
Latest version of presentation.
Latest version of presentation. Could not add fading because it makes my latex to crash with segmentation fault.

@@
+\begin{frame}{Motivation: Google car}
+
+  \begin{tikzpicture}
+    \node [anchor=north west,inner sep=0] (img) at (0,0) 
+    {\includegraphics[width=0.42\textwidth, trim=4cm 00cm 1cm 0cm,clip]{graphics/google-laser-scan-cost.jpg}};
+    \begin{scope}[x=(img.north east),y=(img.south west)] 
+      \coordinate (velc) at (0.25, 0.10);
+      \draw [very thick,red] (velc) ellipse (0.25 and 0.10);
+      %\draw [->,red] (0,0) -- (1, 0) node {X};
+      %\draw [->,red] (0,0) -- (0, 1) node {Y};
+    \end{scope}
+  \end{tikzpicture}
+  \includegraphics[width=0.50\textwidth, trim=3cm 00cm 3cm 0cm,clip]{graphics/google-laser-scan.jpg}
+  \pause
+
+  But Velodyne costs \tikz[remember picture] \node [anchor=north,inner sep=0] (cost) at (0,0) {\$75k};
+\end{frame}
+
+\begin{frame}{Can we do it with cameras? Stereo or Monocular}
+  \begin{columns}
+    \begin{column}{0.48\textwidth}
+      \centering
+      Left Camera\\
+      \includemedia[label=stereoleft,
+        width=\textwidth,
+        activate=pageopen,
+        addresource=graphics/upto61_quat.mp4,
+        flashvars={
+          source=graphics/upto61_quat.mp4
+          &autoPlay=true
+          &loop=true             % loop video
+          &scaleMode=letterbox   % preserve aspect ratio while scaling the video
+        }
+      ]{\includegraphics{graphics/0000000061_raw.png}}{VPlayer.swf}
+    \end{column}
+    \begin{column}{0.48\textwidth}
+      \centering
+      Right Camera\\
+      \includemedia[label=stereoright,
+        width=\textwidth,
+        activate=pageopen,
+        addresource=graphics/upto61_quat_right.mp4,
+        flashvars={
+          source=graphics/upto61_quat_right.mp4
+          &autoPlay=true
+          &loop=true             % loop video
+          &scaleMode=letterbox   % preserve aspect ratio while scaling the video
+        }
+      ]{\includegraphics{graphics/0000000061_right.png}}{VPlayer.swf}
+    \end{column}
+  \end{columns}
+
+  Stereo cameras neeed to be recaliberated
+
+  And the depth range of stereo cameras are limited
+
+  So after certain depth stereo is same as monocular
+\end{frame}
+
 % \begin{frame}{Problem}
@@
 
-\begin{frame}{Problem}
+\begin{frame}{Sample input and output}
+  \def\arrow{
+    (0,0) -- ++(1,0)
+    -- ++(0,1) -- ++(0.3, 0)
+    -- ++(-0.8, 1) -- ++(-0.8, -1) -- ++(0.3, 0) -- ++(0, -1) }
+    \begin{tikzpicture}
+      \node[anchor=south west,inner sep=0] (image) at (0,0)
+      {
+        \includemedia[label=sampleinput,
+          width=\textwidth,
+          activate=pageopen,
+          addresource=graphics/initonly_half.mp4,
+          flashvars={
+            source=graphics/initonly_half.mp4
+            &autoPlay=true
+            &loop=true             % loop video
+            &scaleMode=letterbox   % preserve aspect ratio while scaling the video
+          }
+        ]{
+        \includegraphics[width=\textwidth]{graphics/0000000061_bevdown.png}    }{VPlayer.swf}
+      };
+      \begin{scope}[x={(image.south east)},y={(image.north west)}]
+        \fill[color=red,scale=0.05,shift={(10,11)},rotate=180,]\arrow;
+      \end{scope}
+    \end{tikzpicture}
+
+\end{frame}
+
+\begin{frame}{Intermediate inputs}
   % Need a flowchart that describes the input and desired output of the system
  \tikzset{/tikz/x=0.8cm,/tikz/y=0.8cm}
- \newlength{\units}
  \setlength{\units}{0.8cm}
   \scriptsize{
-    \input{Source/problemflowchart.tex}
+    \problemflowchart{}{}{}{}{}
   }
@@
 % \end{frame}
-\begin{frame}{Problem}
-
-  \def\arrow{
-    (0,0) -- ++(1,0)
-    -- ++(0,1) -- ++(0.3, 0)
-    -- ++(-0.8, 1) -- ++(-0.8, -1) -- ++(0.3, 0) -- ++(0, -1) }
-
-  \begin{tikzpicture}
-    \node[anchor=south west,inner sep=0] (image) at (0,0)
-    {\includegraphics[width=\textwidth]{graphics/0000000061_bevdown.png}};
-    \begin{scope}[x={(image.south east)},y={(image.north west)}]
-      \fill[color=red,scale=0.05,shift={(10,11)},rotate=180,]\arrow;
-    \end{scope}
-  \end{tikzpicture}
-\end{frame}

### 2015-05-11 presentation/pointTrackEnergyWithOccFigure.tex
Latest version of presentation. Could not add fading because it makes my latex to crash with segmentation fault.

@@
     \input{Source/twocuboids.tex}
-    \draw [->, very thick, draw=blue] (pta4) --  +(90:1) node [anchor=south,align=center] {$a^1(\lambda) = 0$\\$a^2(\lambda) = 1$};
-    \draw [->, very thick, draw=red!50!blue] (pta-8) --  +(170:1.4) node [anchor=south,align=center] {$a^1(\lambda) = 0.5$\\$a^2(\lambda) = 0.5$};
-    \draw [->, very thick, draw=red] ($(ptb-8)+(.5,-.8)$) --  +(-60:.8) node [anchor=north,align=center] {$a^1(\lambda) = 1$\\$a^2(\lambda) = 0$};
+    \draw [->, very thick, draw=blue] (pta4) --  +(90:1) node [anchor=south,align=center] {$a^{1j}(\lambda) = 0$\\$a^{2j}(\lambda) = 1$};
+    \draw [->, very thick, draw=red!50!blue] (pta-8) --  +(170:1.4) node [anchor=south,align=center] {$a^{1j}(\lambda) = 0.5$\\$a^{2j}(\lambda) = 0.5$};
+    \draw [->, very thick, draw=red] ($(ptb-8)+(.5,-.8)$) --  +(-60:.8) node [anchor=north,align=center] {$a^{1j}(\lambda) = 1$\\$a^{2j}(\lambda) = 0$};
    \begin{scope}[shift={(4,-2)}]

### 2015-05-11 poster/plot_convergence.m

@@ -1,11 +1,0 @@
-filelist = {'results/mcmc_inference_cputime.txt', ...
-    'results/coordinateDescent_cputime.txt'};
-colors = 'rgb';
-for i=1:numel(filelist)
-    data = dlmread(filelist{i});
-    plot(data(:, 1), data(:, 2), colors(i));
-    hold on;
-end
-legend('MCMC', 'Coordinate Descent');
-xlabel('CPU time');
-ylabel('Energy');

### 2015-05-12 presentation/bboxoccfigure.tex
Added bounding box energy with occlusion.

\usetikzlibrary{intersections}
\begin{tikzpicture}[3d/perspective eye={4,4,-10}]
  \begin{scope}[shift={(0.7,0.9)},scale={10/11},facestyle/.style={fill=green!10,draw=green,thick}]
    \acuboid

  \end{scope}

    \draw [draw=green!50!black,very thick] (b) rectangle (h);
   \path  [name path=gbbox] (b) |- (h);
    \draw [name path=cross1,draw=green!50!black,very thick] (b) -- (h) ;
    \draw [name path=cross2,draw=green!50!black,very thick] (d-| b) -- (b -| h) ;
   \coordinate (gh) at (h);
   \coordinate (gb) at (b);
   \coordinate (gdpb) at (d-|b);

  \begin{scope}[opacity=0.6,facestyle/.style={fill=blue!20,draw=blue!20,very thick}]
    \acuboid
  \end{scope}

    \draw [name path=bbbox,draw=blue!50!black,very thick] (b) rectangle (h) ;

   \path [name intersections={of=cross1 and bbbox,by=E}];
   \path [name intersections={of=gbbox and bbbox,by=F}];
   \path [name intersections={of=cross1 and cross2,by=C}];
   \node [anchor=north east] at (gh) {A};
   \node [anchor=north west] at (gdpb) {B};
   \node [anchor=south west] at (gb) {C};
   \node [anchor=south east] at (gb -| gh) {D};
   \node [anchor=south] at (C) {E};
   \fill [red!30] (gh) -- (E) -- (b) -- (F) -- cycle;
   \node [anchor=west] at ($(C) + (1,0)$) {$v_{AB} = \frac{\text{area(\tikz \node [rectangle,inner sep=0,fill=red!30,text=red!30] {0};)}}{\text{area}(\bigtriangleup ABE)}$};
\end{tikzpicture}

### 2015-09-28 Paper/supplementarymaterial.tex
Added explanation for computing better projection of 3D ellipsoid.

--- 2015-05-04 Paper/suplementarymaterial.tex
@@
 \subsection{System of equations}
-Let the detected bounding box be represented by $[\xmin, \ymin, \xmax, \ymax]^T$. Let $^cT_t$ be the transformation from tracklet to camera.
+Let the detected bounding box be represented by $B$. Let $^cT_t$ be the transformation from tracklet to camera.
 \newcommand{\Cu}{C_u}
@@
 \begin{align}
+  B &= [\xmin, \ymin, \xmax, \ymax]^T
+  \\
   \Cu &= \begin{bmatrix}
@@
 \end{align}
-where $Z_j = \sum_{i=1}^N A_{ij}$ and $\mu^i_u$ and $\Sigma_u^i$ are described in \eqref{eq:muiudef} and \eqref{eq:sigmauidef} respectively.
+where $Z_j = \sum_{i=1}^N A_{ij}$ and $\mu^i_u$ and $\Sigma_u^i$ are described in %\eqref{eq:muiudef} and \eqref{eq:sigmauidef} respectively.
 The range of Gaussian $G_i$
@@
 $\frac{1}{3}\max(\dimsn{i})^2$. The distribution from which we sample is 
-\begin{align}
-  \PropDist(\lambda) = \sum_i A_{ij} \Gauss(\lambda; \|\relp{i}{t}\| -
+\begin{multline}
+  \PropDist(\lambda) = \sum_i A_{ij} \\
+  \Gauss(\lambda; \|\relp{i}{t}\| -
   \frac{\sqrt{3}}{2}\max(\dimsn{i}), \frac{1}{\sqrt{3}}\max(\dimsn{i}))
-\end{align}
+\end{multline}
 And the numerical integral with $K$ samples is computed by
@@
 \section{Sigma of ellipsoid}
+How to compute the parameters of ellipsoid in the camera coordinate frame when center and dimensions of the ellipsoid are given in tracklet coordinate frame.
 \label{sec:sigmacomputation}
@@
 \end{align}
-\begin{align}
+\begin{multline}
   \xc^\top \Rctot^\top \Sigmait \Rctot \xc + 2 (\Rctot^\top \tcmut)^\top  \Rctot^\top\Sigmait \Rctot \xc
+  \\
   + \tcmut^\top \Sigmait \tcmut = 1
-\end{align}
+\end{multline}
 Let $\Sigmaic = \Rctot^\top \Sigmait \Rctot$ and $\muic = - \Rctot^\top
 \tcmut$
-\begin{align}
-  (\xc - \muic)^\top\Sigmaic(\xc - \muic) - \muic^\top\Sigmaic\muic +
-  \tcmut^\top \Sigmait \tcmut = 1
-\end{align}
+\begin{multline}
+  (\xc - \muic)^\top\Sigmaic(\xc - \muic) - \muic^\top\Sigmaic\muic 
+  \\
+  + \tcmut^\top \Sigmait \tcmut = 1
+\end{multline}
 Let $\Sigmaicf = \frac{\Sigmaic}{1 - \tcmut^\top \Sigmait \tcmut +
@@
 general. We approximate the projection of ellipsoid by projecting a slice
-through the ellipsoid. We choose the slice as the plane perpendicular to the
+through the ellipsoid.
+
+\subsection{Tangent planes method}
+\newcommand{\nx}{\hat{n}_x}
+We chose the slice as the plane passing through the four points that touch 
+the tangent planes through the origin.
+Let the normal to plane representing $\xmin$, $\xmax$ be $\nx = [\cot(\alpha),
+0, 1]^\top$. The tangent point lies on the plane, ellipsoid and at
+the tangent point the gradient of ellipsoid is parallel to the plane normal.
+%
+\begin{align}
+  x^\top \nx = \nx^\top x &= 0\\
+  (x-\muic)^\top\Sigmaicf(x-\muic) &= 1 \\
+  2\Sigmaicf (x - \muic) &= \lambda \nx \enspace .
+\end{align}%
+%
+Eliminating $x$ from the three equations we get,
+%
+\begin{align}
+  \frac{ \lambda^2 }{ 4 } \nx^\top \Sigmaicfinv \nx &= 1\\
+  \frac{ \lambda }{ 2 } \nx^\top \Sigmaicfinv \nx - \muic^\top \nx &= 0
+\end{align}%
+%
+Solving for $\lambda$ we get $\lambda = \frac{ 2 \muic^\top \nx }{ \nx^\top \Sigmaicfinv \nx }$ or
+%
+\begin{align}
+  \nx^\top \muic \muic^\top \nx &= \nx^\top \Sigmaicfinv \nx\\
+  \nx^\top (\Sigmaicfinv - \muic \muic^\top) \nx &= 0
+\end{align}%
+%
+Let $C := \Sigmaicfinv - \muic \muic^\top$ and the quadratic equation can be solved by
+%
+\begin{align}
+  \cot(\alpha) &= \frac{ - C_{13} \pm \sqrt{ C^2_{13} - C_{11}C_{33} } }{ C_{11}  }
+\end{align}%
+%
+Similarly for $\beta_y$
+
+\begin{align}
+  \cot(\beta) &= \frac{ - C_{23} \pm \sqrt{ C^2_{23} - C_{22}C_{33} } }{ C_{22}  }
+\end{align}%
+
+%
+\begin{align}
+  \lambda &= \frac{ 2 } { [\cot(\alpha), 0, 1] \muic}\\
+  x &= \frac{ 1 } { [\cot(\alpha), 0, 1] \muic } \Sigmaicfinv [\cot(\alpha), 0, 1]^\top + \muic
+\end{align}%
+%
+Once we have four such points $[x_1, x_2, x_3, x_4]$, we can solve for the plane which is given by the null space of $A = \begin{bmatrix}
+  x_1^\top & 1\\
+  x_2^\top & 1\\
+  x_3^\top & 1\\
+  x_4^\top & 1
+\end{bmatrix}$
+\newcommand{\np}{\hat{n}_p}
+Let $\np$ be the normal of the derived plane such that the equation of plane is $\np^\top x = 1$.
+
+\subsection{Perpendicular plane method}
+ We choose the slice as the plane perpendicular to the
 line joining the center of ellipsoid to the optical center of camera. Let
@@
 $x^\top\frac{\muic}{\|\muic\|} = \|\muic\|$. We introduce 
-$\mubar = \frac{\muic}{\|\muic\|^2}$ for notational simplicity. Hence, we want
+$\np = \mubar = \frac{\muic}{\|\muic\|^2}$ for notational simplicity. Hence, we want
 to project the points that satisfy both the equation of chosen plane and the 
 ellipsoid i.e.
+
+\subsection{Projection of the ellipsoid slice}
 \begin{align}
-  \mubar^\top x = x^\top\mubar &= 1\\ 
+  \np^\top x = x^\top\np &= 1\\ 
   (x-\muic)^\top\Sigmaicf(x-\muic) &= 1 \enspace.
 \end{align}
-We rewrite $\muic = \muic\mubar^\top x$, and $1 = x^\top\mubar \mubar^\top x$
+We rewrite $\muic = \muic\np^\top x$, and $1 = x^\top\np \np^\top x$
 \begin{align}
-  (x-\muic\mubar^\top x)^\top\Sigmaicf(x-\muic\mubar^\top x) &= x^\top\mubar \mubar^\top x \enspace,
+  (x-\muic\np^\top x)^\top\Sigmaicf(x-\muic\np^\top x) &= x^\top\np \np^\top x \enspace,
 \end{align}
@@
 \begin{align}
-  x^\top\left((I-\muic\mubar^\top)^\top\Sigmaicf(I-\muic\mubar^\top) - \mubar \mubar^\top\right)x &= 0\enspace.
+  x^\top\left((I-\muic\np^\top)^\top\Sigmaicf(I-\muic\np^\top) - \np \np^\top\right)x &= 0\enspace.
 \end{align}
@@
 \begin{align}
-  \Sperpcut = (I-\muic\mubar^\top)^\top\Sigmaicf(I-\muic\mubar^\top) - \mubar \mubar^\top \enspace.
+  \Sperpcut = (I-\muic\np^\top)^\top\Sigmaicf(I-\muic\np^\top) - \np \np^\top \enspace.
 \end{align}
+If $u = [v^\top, 1]^\top$, $A = \Sproj(1:2, 1:2)$, $b = \Sproj(1:2, 3)$, $b^\top = \Sproj(3, 1:2)$ and $d = \Sproj(3,3)$ the equation can be expanded as
+%
+\begin{align}
+[v^\top, 1]\begin{bmatrix} A & b\\ b^\top & d \end{bmatrix}[v^\top, 1]^\top &= 0\\
+v^\top A v + 2 b^\top v + d &= 0
+\end{align}
+\begin{multline}
+  v^\top A v + 2 b^\top A^{-\top} A v + b^\top A^{-\top} A A^{-1}b \\
+  = b^\top A^{-\top} b - d
+\end{multline}
+\begin{multline}
+  \left(v + A^{-1} b\right)^\top A \left( v + A^{-1} b\right) \\
+  = b^\top A^{-\top}b - d
+\end{multline}%
+%
+The mean and sigma of the projected ellipse can be computed by
+
+%
+\begin{align}
+  \mu_{\text{2D}} &= A^{-1} b\\
+  \Sigma^{-1}_{\text{2D}} &= \frac{1}{b^\top A^{-\top} b - d} A
+\end{align}%
+%
 
@@
   \Sigma = E(\Delta x \Delta x^\top)$ the covariance of new data is given by
-  \begin{align}
-    E((x + \Delta x)(x+\Delta x)^\top) = E(xx^\top) + E(x \Delta x^\top) %\\
+  \begin{multline}
+    E((x + \Delta x)(x+\Delta x)^\top) = E(xx^\top) + E(x \Delta x^\top) 
+    \\
     + E(\Delta x x^\top) + E(\Delta x \Delta x^\top)
-  \end{align}
+  \end{multline}
   where the terms $E(x \Delta x^\top)$ denote the correlation between the data

### 2015-11-02 CVPR16/Source/experiments.tex
Generated visualizations.

--- 2015-05-04 CVPR/Source/experiments.tex
@@
 
-\begin{table}
-  \centering
-  \begin{tabular}{lrrr}
-    \toprule
-    Algorithm & Total & Unoccluded cars & Occluded cars \\
-    \midrule
-    bounding box only & 0.21 & \textbf{0.03}  & 0.36\\
-    Using $P^{(ij)}_{\text{assoc}}$ & \textbf{0.21} & 0.08 & \textbf{0.32}\\
-    Using $\assocP{}$ & 0.23 & 0.09 & 0.34 \\
-    Using $P^{(ij)}_{\text{assoc by reproj}}$ & 0.23 & 0.08 & 0.34\\
-    \bottomrule
-  \end{tabular}
-  \caption{Association Experiment results. The error is in terms of fraction of points wrongly associated with objects, hence lower is better.}
-\end{table}
+% \begin{table}
+%   \centering
+%   \begin{tabular}{lrrr}
+%     \toprule
+%     Algorithm & Total & Unoccluded cars & Occluded cars \\
+%     \midrule
+%     bounding box only & 0.21 & \textbf{0.03}  & 0.36\\
+%     Using $P^{(ij)}_{\text{assoc}}$ & \textbf{0.21} & 0.08 & \textbf{0.32}\\
+%     Using $\assocP{}$ & 0.23 & 0.09 & 0.34 \\
+%     Using $P^{(ij)}_{\text{assoc by reproj}}$ & 0.23 & 0.08 & 0.34\\
+%     \bottomrule
+%   \end{tabular}
+%   \caption{Association Experiment results. The error is in terms of fraction of points wrongly associated with objects, hence lower is better.}
+% \end{table}
+
+%\begin{table}
+%  \centering
+%  \begin{tabular}{lccc}
+%    \toprule
+%    Algorithm & All & Unoccluded cars & Occluded cars \\
+%    \midrule
+%    bounding box only                         & $0.18\pm0.01$          & $\color{red}0.04\pm0.003$  & $0.41\pm0.04$\\
+%    Using $\assocP{}$                         & $0.18\pm0.01$          & $0.05\pm0.003$           & $0.39\pm0.04$ \\
+%    Using $P^{(ij)}_{\text{assoc by reproj}}$ & $0.18\pm0.01$          & $0.06\pm0.003$           & $0.39\pm0.04$\\
+%    Using $P^{(ij)}_{\text{assoc}}$           & $\color{red}0.17\pm0.01$ & $0.05\pm0.003$           & $\color{red}0.38\pm0.04$\\
+%    \bottomrule
+%  \end{tabular}
+%  \caption{Association Experiment results. The error is in terms of average fraction of foreground points incorrectly associated to objects per sequence. }
+%\end{table}
+\begin{figure*}
+  \includegraphics[width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence_occ_50.pdf}
+  \caption{Association Experiment results. The error is in terms of average fraction of foreground points incorrectly associated to objects per sequence. }
+  \label{fig:assoc-occ-results}
+\end{figure*}
 
@@
 
-\begin{table}
-  \centering
-  \begin{tabular}{lrrr}
-    \toprule
-    Energy & t & yaw & dim \\
-    \midrule
-    lane+contPtTracksNoOcc+size+bbox+posT   & 3.80 & 0.91 & 1.58 \\
-    lane+contPtTracks+size+bboxOcc+posT+col & \textbf{3.78} & 0.91 & 1.58 \\
-    lane+contPtTracks+size+bboxOcc+posT     & 3.81 & 0.92 & 1.59 \\
-    lane+size+bboxOcc+posT+col              & 3.92 & 0.91 & 1.15 \\
-    lane+size+bboxOcc+posT                  & 3.83 & 0.90 & 1.14 \\
-    lane+size+bbox+posT                     & 3.83 & 0.90 & \textbf{1.14} \\
-    initialization                          & 3.79 & \textbf{0.86} & 1.64 \\
-    \bottomrule
+% \begin{table}
+%   \centering
+%   \begin{tabular}{lrrr}
+%     \toprule
+%     Energy & t & yaw & dim \\
+%     \midrule
+%     initialization                                                                                  & 3.79 & \textbf{0.86} & 1.64 \\
+%     $\EnergyLane+\EnergySize+\EnergyBBox+\EnergyDyn                                       $ & 3.83 & 0.90 & \textbf{1.14} \\
+%     %$\EnergyLane+\EnergySize+\EnergyBBoxocc+\EnergyDyn                                    $ & 3.83 & 0.90 & 1.14 \\
+%     %$\EnergyLane+\EnergySize+\EnergyBBoxocc+\EnergyDyn+\EnergyCol                         $ & 3.92 & 0.91 & 1.15 \\
+%     %$\EnergyLane+\EnergyContpttracks+\EnergySize+\EnergyBBoxocc+\EnergyDyn             $ & 3.81 & 0.92 & 1.59 \\
+%     $\EnergyLane+\EnergyTrackNoOcc+\EnergySize+\EnergyBBox+\EnergyDyn+\EnergyCol $ & 3.80 & 0.91 & 1.58 \\
+%     $\EnergyLane+\EnergyTrack+\EnergySize+\EnergyBBox+\EnergyDyn+\EnergyCol   $ & \textbf{3.78} & 0.91 & 1.58 \\
+%     \bottomrule
+%   \end{tabular}
+%   \caption{Localization experiment results with different combination of energies.
+We report error in three metrics translation error (t) in meters per car, yaw error (yaw) in radians per car and dimension error is again meters per car.}
+% \end{table}
+
+\newpage
+\begin{table*}
+  \begin{tabular}{ccc}
+    & Assignments & Error in assignment\\
+    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=0.48\textwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png} &%
+    \includegraphics[width=0.48\textwidth]{results/0009_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
+    \rotatebox{90}{\hspace{05pt} Brox and Malik} & \includegraphics[width=0.48\textwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png} &%
+    \includegraphics[width=0.48\textwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
+    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=0.48\textwidth]{results/0009_0000000060_point_assign_contPtTracks-small.png} &%
+    \includegraphics[width=0.48\textwidth]{results/0009_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}\\
+    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=0.48\textwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png} &%
+    \includegraphics[width=0.48\textwidth]{results/0013_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
+    \rotatebox{90}{\hspace{05pt} Brox and Malik} & \includegraphics[width=0.48\textwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png} &%
+    \includegraphics[width=0.48\textwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
+    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=0.48\textwidth]{results/0013_0000000060_point_assign_contPtTracks-small.png} &%
+    \includegraphics[width=0.48\textwidth]{results/0013_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}
   \end{tabular}
-  \caption{Localization experiment results with different combination of energies.
-We report error in three metrics translation error (t) in meters per car, yaw error (yaw) in radians per car and dimension error is again meters per car.}
-\end{table}
+\end{table*}

### 2015-11-02 CVPR16/Source/occlusion.tex
Generated visualizations.

--- 2015-05-04 CVPR/Source/occlusion.tex
@@
 \begin{align}
-  f_{\text{occ}}{\bx} = \cL(\bx; \pos{i}{t}, \bSigma_i)
+  f_{\text{occ}}(\bx) = \cL(\bx; \pos{i}{t}, \bSigma_i)
 \end{align}
@@
 The spread of the ellipsoid, determined by $\bSigma_i$, depends of the dimensions of the traffic participant.
-Please refer to the Appendix~\ref{sec:appendix} for computation of $\bSigma$ from object dimensions.
+Please refer to the Chapter~\ref{sec:appendix} for computation of $\bSigma$ from object dimensions.
 
@@
 %
+%\newcommand{\Ptrans}{P_{\textit{transmission}}}%
 \begin{align}
-P^j_{\textit{transmission}}(\lambda) = \prod_i \cL_u (\bu; \bmu_i, \bGamma_i^{-1}) \cL_{\lambda}(\lambda; \nu_i),
+  \Ptrans^j(\lambda) = \prod_i (1 - \cL_u (\bu; \bmu_i, \bGamma_i^{-1}) \cL_{\lambda}(\lambda; \nu_i)),
 \label{eq:evalCumulativePtrans}
@@
 %
+We compare the exact and relative formulation of transmission probability in Fig~\ref{fig:compare:exact:approx:ptrans}.
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{results/plotPtransmission_exact_vs_approx.pdf}
+  \caption{Comparing the approximate $\Ptrans$ with exact version.
+The drop in approximate version of $\Ptrans$ is delayed because we assume drop at the center of the car rather than camera facing face of the car.}
+  \label{fig:compare:exact:approx:ptrans}
+\end{figure}
 

### 2015-11-02 CVPR16/Source/abstract.tex
Added visualizations for the RAS algorithm.

\begin{abstract}
  We present a method to augment motion segmentation by representation of
  objects like cars with soft ellipsoids that not only present a probablistic
  alternative to bounding boxes but also inherently model occlusion. We compare
  our approach against state of the art motion segmentation methods.
\end{abstract}

### 2015-11-02 CVPR16/Source/experiments.tex
Added visualizations for the RAS algorithm.

@@
 \begin{figure*}
+  \includegraphics[width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence_static_and_dynamic.pdf}\\
+  \includegraphics[width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence_occ_50.pdf}\\
+  \includegraphics[width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence_50.pdf}\\
   \includegraphics[width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence_occ_50.pdf}
-  \caption{Association Experiment results. The error is in terms of average fraction of foreground points incorrectly associated to objects per sequence. }
-  \label{fig:assoc-occ-results}
+  \caption{From top: (1)Association Experiment results on all points. %} \label{fig:assoc-results}
+    (2) Association Experiment results on occluded points. %} \label{fig:assoc-occ-results}
+    (3) Association Experiment results on dynamic points. %} \label{fig:assoc-dynamic-results}
+    (4) Association Experiment results on dynamic  and occluded points.
+The error is in terms of average fraction of foreground points incorrectly associated to objects per sequence.
+} \label{fig:assoc-occ-results}
 \end{figure*}
@@
 \newpage
+\newlength{\tblimgwidth}
+\setlength{\tblimgwidth}{0.40\textwidth}
 \begin{table*}
+  \centering
   \begin{tabular}{ccc}
     & Assignments & Error in assignment\\
-    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=0.48\textwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png} &%
-    \includegraphics[width=0.48\textwidth]{results/0009_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{05pt} Brox and Malik} & \includegraphics[width=0.48\textwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png} &%
-    \includegraphics[width=0.48\textwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=0.48\textwidth]{results/0009_0000000060_point_assign_contPtTracks-small.png} &%
-    \includegraphics[width=0.48\textwidth]{results/0009_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=0.48\textwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png} &%
-    \includegraphics[width=0.48\textwidth]{results/0013_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{05pt} Brox and Malik} & \includegraphics[width=0.48\textwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png} &%
-    \includegraphics[width=0.48\textwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=0.48\textwidth]{results/0013_0000000060_point_assign_contPtTracks-small.png} &%
-    \includegraphics[width=0.48\textwidth]{results/0013_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}
+    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png} &%
+    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
+    \rotatebox{90}{\hspace{2em} Brox} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png} &%
+    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
+    \rotatebox{90}{\hspace{2em} RAS} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_RAS-small.png} &%
+    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
+    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks-small.png} &%
+    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}\\
+    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png} &%
+    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
+    \rotatebox{90}{\hspace{2em} Brox} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png} &%
+    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
+    \rotatebox{90}{\hspace{2em} RAS} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_RAS-small.png} &%
+    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
+    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks-small.png} &%
+    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}
   \end{tabular}
+  \caption{Qualitative results for association experiment. The left column
+  shows the point tracks assignment to appropriate track. Each color represents
+a different track to which the point is associated to. Right column shows the
+probablistic error in association: red is low error and blue is high error.
+Note that our method changes smoothly at the boundary of the objects with
+intermediate probabilities, while the baseline methods have only 0-1 error.} 
 \end{table*}

### 2015-11-02 CVPR16/Source/intro.tex
Added visualizations for the RAS algorithm.

\section{Introduction}
The problem of segmenting points to objects often comes up in different
computer vision problems especially in multi-body 
reconstruction and localization. Given correspondence points on
consecutive frames, the problem becomes one of finding out which points belong
to which object following which one can use the consensus of segmented points
to reconstruct or localize the object more accurately. Without additional 
information this is very difficult problem as attempted by semantic segmentation 
and motion segmentation methods. However, in the problems like reconstruction and
localization on can use the hypothesis of the algorithm as the feedback. For

### 2015-11-02 CVPR16/Source/occlusion.tex
Added visualizations for the RAS algorithm.

@@
 The spread of the ellipsoid, determined by $\bSigma_i$, depends of the dimensions of the traffic participant.
-Please refer to the Chapter~\ref{sec:appendix} for computation of $\bSigma$ from object dimensions.
+Please refer to the supplementary material for computation of $\bSigma_i$ from object dimensions.
 
@@
 \begin{equation}
-\prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} = e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}. \nonumber
+\prod_{f}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} = e^{\int_{f}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}. \nonumber
 \end{equation}
@@
 %
-%\newcommand{\Ptrans}{P_{\textit{transmission}}}%
+\newcommand{\Ptransmission}{P_{\textit{transmission}}}%
 \begin{align}
-  \Ptrans^j(\lambda) = \prod_i (1 - \cL_u (\bu; \bmu_i, \bGamma_i^{-1}) \cL_{\lambda}(\lambda; \nu_i)),
+  \Ptransmission^j(\lambda) = \prod_i (1 - \cL_u (\bu; \bmu_i, \bGamma_i^{-1}) \cL_{\lambda}(\lambda; \nu_i)),
 \label{eq:evalCumulativePtrans}
@@
 %
-We compare the exact and relative formulation of transmission probability in Fig~\ref{fig:compare:exact:approx:ptrans}.
+We compare the exact and relative formulation of transmission probability in
+Fig~\ref{fig:compare:exact:approx:ptrans}. Note that the choice of mean depth
+of object causes deviation from the exact transmission probability. However,
+the computation of ray intersection with ellipsoid is expensive to compute for 
+every ray and the shift of transmission probability anywhere through the object 
+is a reasonable approximation as the occluded points can only lie outside the
+object.
 

### 2015-11-02 CVPR16/Source/related.tex
Added visualizations for the RAS algorithm.

--- 2015-01-29 CVPR/Source/related.tex
@@
 \section{Related Work}
-\label{sec:related}
-
-\paragraph{Occlusion handling in detection}
-Several works in object detection consider occlusion by training a detector on visible parts of the object \cite{Gao_etal_2011}.
-Occlusion reasoning based on 2D image silhouettes is used to improve detection performance in \cite{Hsiao_Herbert_2012}.
-In contrast, our occlusion reasoning is based on 3D entities.
-In recent years, object detectors have also considered occlusion reasoning using 3D cues, often learned from a dataset of CAD models \cite{Pepik_etal_2012,Pepik_etal_2013,Xiang_Savarese_2013}.
-By necessity, such frameworks are often a discrete representation of occlusion behavior, for example, in the form of a collection of occlusion masks derived from object configurations discretized over viewpoint.
-In constrast to these works, our occlusion modeling is also fully 3D, but allows for a continuous representation.
-Further, to derive 3D information, we do not use CAD models, rather we derive a probabilistic formulation based on physical insights.
-
 \paragraph{Occlusion handling in tracking}
@@
 However, the occlusion model in \cite{Milan_etal_2014} is essentially the overlap of image projections of a Gaussian representation of the object.
-Our occlusion modeling, however, is much more general in determining the probability of a point in space as belonging to an object.
+Our occlusion modeling is much more general in determining the probability of a point in space as belonging to an object.
 While it can also be used to determine a visibility ratio similar to \cite{Milan_etal_2014}, it can have far more general applications and can be quantitatively evaluated, as shown by our experiments on point track associations.
@@
 In contrast to these works, our formulation does not distinguish between moving and static objects and also explicitly reasons about occlusions due to 3D object geometries for associating point tracks to individual objects.
-
-TODO:
-\vfill
-\pagebreak
-Related work continued
-\vspace{15cm}

### 2015-11-03 CVPR16/Source/experiments.tex
Plotted RAS and Brox together by an inner join. Will plot with a outer join if time permitted.

@@
 \begin{figure*}
-  \includegraphics[width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence_static_and_dynamic.pdf}\\
-  \includegraphics[width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence_occ_50.pdf}\\
-  \includegraphics[width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence_50.pdf}\\
-  \includegraphics[width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence_occ_50.pdf}
+\includegraphics[trim=1.0in 0.2in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
   \caption{From top: (1)Association Experiment results on all points. %} \label{fig:assoc-results}
@@
   \begin{tabular}{ccc}
-    & Assignments & Error in assignment\\
+    & Associations & Error in association\\
     \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png} &%

### 2015-11-03 CVPR16/Source/abstract.tex
latest version

@@
 \begin{abstract}
-  We present a method to augment motion segmentation by representation of
-  objects like cars with soft ellipsoids that not only present a probablistic
-  alternative to bounding boxes but also inherently model occlusion. We compare
-  our approach against state of the art motion segmentation methods.
+We propose a model for representation of objects so that points can be
+probabilistically  associated to the tracklets while accounting for occlusion.
+We compare our approach against state of the art motion segmentation methods.
 \end{abstract}

### 2015-11-03 CVPR16/Source/experiments.tex
latest version

@@
 \includegraphics[trim=1.0in 0.2in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
-  \caption{From top: (1)Association Experiment results on all points. %} \label{fig:assoc-results}
+  \caption{From top: (1)Association Experiment results on dynamic and occluded tracks. %} \label{fig:assoc-results}
     (2) Association Experiment results on occluded points. %} \label{fig:assoc-occ-results}
     (3) Association Experiment results on dynamic points. %} \label{fig:assoc-dynamic-results}
-    (4) Association Experiment results on dynamic  and occluded points.
+    (4) Association Experiment results on all points.
 The error is in terms of average fraction of foreground points incorrectly associated to objects per sequence.
-} \label{fig:assoc-occ-results}
+Occluded points are chosen because our method is especially helpful in occlusion cases while dynamic points are chosen for fair comparison against motion segmentation methods.} \label{fig:assoc-occ-results}
 \end{figure*}

### 2015-11-03 CVPR16/Source/intro.tex
latest version

@@
 and motion segmentation methods. However, in the problems like reconstruction and
-localization on can use the hypothesis of the algorithm as the feedback. For
+localization on can use the hypothesis of the algorithm as the feedback.
+% What is the problem we are trying to solve, and why is it even important?
+
+% What did we do
+We propose a model for representation of objects in the scene so that points
+can be probabilistically  associated to the tracklets while accounting for occlusion.
+% Why is it novel
+Although our proposed modeling is inspired by Milan et
+al.\cite{Milan_etal_2014}, it is more detailed and more principled than their
+work. Milan et al. used soft ellipses and sigmoids to model pedestrians and
+their occlusion. We instead reason in 3D and use ellipsoids to model objects
+and reason about occupancy of the space to model occlusion.
+% Ok you proposed a model is it of any use
+% How does it compare to state of art
+We employ our model in the context of autonomous for problem of localization of
+cars in the road scene. We show that associate points to objects more
+accurately than other methods like bounding box based association, Brox and
+Malik's\cite{Brox_Malik_2010} segmentation method and Robust Algebraic
+Segmentation (RAS)\cite{Rao_etal_2010}.

### 2015-11-03 CVPR16/Source/experiments.tex
Added the localization graphical model and the energies and the results back to the paper.

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph{Association error evaluation}
+\subsection{Association error evaluation}
 
@@
 association with TPs with that of bounding box baseline method.
-
-% \begin{align}
-%   f^{i}_{reproj}&(\trackpj{t-1}, \lambda) =
-%   \projectionOf{\invProjectionOf{\trackpj{t-1}}}\\
-%   %&= K(R^i_t ((R^i_{t-1})^\top\lambda \ray - (R^i_{t-1})^\top T_{t-1}) + T_{t})\\
-%   &= \frac
-%   {p_{1:2}\lambda + q_{1:2}}
-%   {p_{3}\lambda + q_{3}}
-% \end{align}
-% where $p_{1:3} = KR^i_t(R^i_{t-1})^\top\ray$ and
-% $q_{1:3} = KR^i_t(R^i_{t-1})^\top T_{t-1} + KT_t$
-% 
-% Now that we have an association from TP $i$ to point track $j$ through
-% $\lambda$, we can come up with an association probability
-% \begin{align}
-%    \assocP &= \frac{(\max \{ 0, \nabla \occf^\top
-% \ray \})^2 }{P_{\text{reflection}}}\lambdadist\\
-% &=(\max \{ 0, \nabla \occf^\top \ray \})^2
-%   \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
-% \end{align}
 
@@
 
-% \begin{table}
-%   \centering
-%   \begin{tabular}{lrrr}
-%     \toprule
-%     Algorithm & Total & Unoccluded cars & Occluded cars \\
-%     \midrule
-%     bounding box only & 0.21 & \textbf{0.03}  & 0.36\\
-%     Using $P^{(ij)}_{\text{assoc}}$ & \textbf{0.21} & 0.08 & \textbf{0.32}\\
-%     Using $\assocP{}$ & 0.23 & 0.09 & 0.34 \\
-%     Using $P^{(ij)}_{\text{assoc by reproj}}$ & 0.23 & 0.08 & 0.34\\
-%     \bottomrule
-%   \end{tabular}
-%   \caption{Association Experiment results. The error is in terms of fraction of points wrongly associated with objects, hence lower is better.}
-% \end{table}
-
-%\begin{table}
-%  \centering
-%  \begin{tabular}{lccc}
-%    \toprule
-%    Algorithm & All & Unoccluded cars & Occluded cars \\
-%    \midrule
-%    bounding box only                         & $0.18\pm0.01$          & $\color{red}0.04\pm0.003$  & $0.41\pm0.04$\\
-%    Using $\assocP{}$                         & $0.18\pm0.01$          & $0.05\pm0.003$           & $0.39\pm0.04$ \\
-%    Using $P^{(ij)}_{\text{assoc by reproj}}$ & $0.18\pm0.01$          & $0.06\pm0.003$           & $0.39\pm0.04$\\
-%    Using $P^{(ij)}_{\text{assoc}}$           & $\color{red}0.17\pm0.01$ & $0.05\pm0.003$           & $\color{red}0.38\pm0.04$\\
-%    \bottomrule
-%  \end{tabular}
-%  \caption{Association Experiment results. The error is in terms of average fraction of foreground points incorrectly associated to objects per sequence. }
-%\end{table}
 \begin{figure*}
@@
 
-\paragraph{Localization Experiment}
-Localization is the main goal of our project.
-We estimate the position, orientation and dimensions of the car with our framework and compute the error in birds eye view domain along the ground plane.
-We report error in three metrics translation error (t) in meters per car, yaw error (yaw) in radians per car and dimension error is again meters per car.
-
-% %\subsection{Qualitative Results}
-% \begin{figure}
-%         \includegraphics[width=\columnwidth]{results/Visualization/City/2011_09_26_drive_0009/single_window_contPtTracks_size_bboxOcc_yawTstepWiseInference/0000000061.png}
-% \end{figure}
-% \begin{figure}
-%   \includegraphics[width=\columnwidth]{results/Visualization/City/2011_09_26_drive_0009/single_window_lane_size_bboxOcc_yawTstepWiseInference/0000000061.png}
-% \end{figure}
-% \begin{figure}
-%   \includegraphics[width=\columnwidth]{results/Visualization/City/2011_09_26_drive_0009/single_window_contPtTracks_size_bboxOcc_yawTstepWiseInference/0000000063.png}
-% \end{figure}
-
-%\subsection{Quantitative results}
-
-% \begin{table}
-%   \centering
-%   \begin{tabular}{lrrr}
-%     \toprule
-%     Energy & t & yaw & dim \\
-%     \midrule
-%     initialization                                                                                  & 3.79 & \textbf{0.86} & 1.64 \\
-%     $\EnergyLane+\EnergySize+\EnergyBBox+\EnergyDyn                                       $ & 3.83 & 0.90 & \textbf{1.14} \\
-%     %$\EnergyLane+\EnergySize+\EnergyBBoxocc+\EnergyDyn                                    $ & 3.83 & 0.90 & 1.14 \\
-%     %$\EnergyLane+\EnergySize+\EnergyBBoxocc+\EnergyDyn+\EnergyCol                         $ & 3.92 & 0.91 & 1.15 \\
-%     %$\EnergyLane+\EnergyContpttracks+\EnergySize+\EnergyBBoxocc+\EnergyDyn             $ & 3.81 & 0.92 & 1.59 \\
-%     $\EnergyLane+\EnergyTrackNoOcc+\EnergySize+\EnergyBBox+\EnergyDyn+\EnergyCol $ & 3.80 & 0.91 & 1.58 \\
-%     $\EnergyLane+\EnergyTrack+\EnergySize+\EnergyBBox+\EnergyDyn+\EnergyCol   $ & \textbf{3.78} & 0.91 & 1.58 \\
-%     \bottomrule
-%   \end{tabular}
-%   \caption{Localization experiment results with different combination of energies.
-We report error in three metrics translation error (t) in meters per car, yaw error (yaw) in radians per car and dimension error is again meters per car.}
-% \end{table}
-
-\newpage
 \newlength{\tblimgwidth}
@@
 \end{table*}
+
+\subsection{Localization Experiment}
+To prove the effectiveness of our method we apply it to the localization
+problem. We estimate the position, orientation and dimensions of the car with
+our framework and compute the error in birds eye view domain along the ground
+plane. We report error in three metrics translation error (t) in meters per
+car, yaw error (yaw) in radians per car and dimension error is again meters per
+car.
+
+We build the graphical model as shown in Fig~\ref{fig:graphmodel} that 
+allows us to factorize the intractable probability distribution into following form
+%
+\begin{multline}
+  -\log{P(\{\state{i}{t}\} | \mathbb{E})} = 
+  -Z' 
+  \\
+  + \sum_{t=s_i}^{e_i}
+  \left(
+  \sum_{i,j:i\ne j}   
+  \WEnergyCol 
+   + \WpEnergy{bbox}
+   + \WpEnergy{track}
+\right)
+  \\
+  + \left(
+  \sum_{i=1}^N 
+  \WEnergy{lane}
+  + \WEnergy{dyn}
+  + \WEnergy{size}
+\right)
+  \enspace.
+\end{multline}
+%
+We use the following energies in our graphical model.
+
+\subsubsection{Point tracks energy with occlusion}
+\label{sec:totalContPtTracksEnergy}
+We model continuous point tracks energy with explicit occlusion reasoning as
+the expected re-projection error over the association probability,
+
+\begin{multline}
+  \Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = 
+  \\
+    \sum_{i=1}^{N} 
+    %\sum_{t = s_i}^{e_i}
+    \sum_{j = 1}^{M}
+    \int_1^\infty \assocP\Ereproj(\lambda) d\lambda
+\end{multline}
+where $\assocP$ is the association probability of
+$j$\textsuperscript{th} point with $i$\textsuperscript{th} TP at depth $\lambda$, $\{ \relp{i}{t} \}_i$ are the poses of all occluding objects at time $t$, $ \{ \dimsn{i} \}_i$ are the dimensions of all objects that occlude $i$
+and $\Ereproj(\lambda)$ is the re-projection error given by
+%
+\begin{align}
+  \assocP &= \Prefl\Ptrans\\
+  \Ereproj(\lambda) &= \left\|\trackpj{t} - \projectionOf{\invProjectionOftm{\trackpj{t-1}, \lambda}}\right\|^2 .
+  \label{eq:reprojerror}
+\end{align}
+
+The  $\projectionOf{.}$ and $\invProjectionOftm{.}$ denote the projection and
+inverse projection functions that project 3D point to camera image and vice
+versa. Note that inverse projection $\invProjectionOf{.}$ depend on both the
+point $\trackp{t}$ and the unknown depth $\lambda$. Also note that the inverse projection is dependent on TP pose at time $t-1$ while the projection depends on pose at time $t$ which can be different.
+
+\subsubsection{Object detection energy}
+
+We model object detection energy as the norm of difference in the coordinates
+of the projected bounding box and detected bounding box. The detected bounding
+box is represented by the extrema along X and Y dimensions $\bb{i} = [\xmin,
+\ymin, \xmax, \ymax]^\top$. If $\dimsn{i} = [l, w, h]^\top$ represent the 3D
+then we can compute the eight corners of the cuboid model in the tracklet
+coordinate transform as
+
+With slight abuse of notation for projection operator we write this energy as
+\begin{align}
+  \EnergyBBox &= \left\| \projectionOf{\dimsn{i}} - \bb{i}\right\|^2_2 \enspace.
+\end{align}
+
+For object detections we use object detector by \cite{Felzenszwalb_etal_2010}
+which is detector by parts model and we use eight parts to train the car model 
+on half of the KITTI dataset \cite{geiger2013vision}. The trained modeled is 
+used to get detections for the other half of the dataset and vice versa.
+
+\subsubsection{Lane energy}
+\label{sec:laneEnergy}
+ The lanes are modeled as splines. Here we assume that the confidence in lane
+ detection is decreases as the distance from the lane center increases.  The
+ energy is given by the dot product between car orientation and tangent to the
+ lane at that point.
+
+\begin{align}
+  \label{eq:laneOrientationEnergy}
+  \Energy{lane} = 
+  \sum_{m \in M_{\text{close}}}
+  (1 - \ori{i}{t} \cdot \text{TAN}(L_{m}(k), \pos{i}{t}) )
+\LaneUncertainty{\pos{i}{t}}
+\end{align}
+where $M_{\text{close}} = \{m : \text{DIST}(L_{m}(k), \pos{i}{t}) < d_{\text{thresh}}\} $ is
+the set of nearby lanes close to the object by a certain distance threshold $d_{\text{thresh}}$ and 
+\begin{align}
+\LaneUncertainty{\pos{i}{t}} = 
+  \frac{1}{1 + \exp(-q(w_{\text{road}} - \text{DIST}(L_{m}(k), \pos{i}{t})))}
+\end{align}
+for some constant $w_{\text{road}}$ that represents the width of the road.
+
+\subsubsection{Transition probability}
+Dynamics constraints should not only enforce smooth trajectories, but also the
+holonomic constraints.  The following energy adds a penalty if the change in
+position is not in direction of previous orientation.
+
+\begin{align}
+  \label{eq:totalPosTransitionEnergy}
+  \Energy{dyn-hol} = 1 - \ori{i}{t-1} \cdot (\pos{i}{t} - \pos{i}{t-1})
+\end{align}
+
+The following energy adds a penalty for change in position and orientation
+but a penalty for change in velocity is much better approximation. However, in
+a Markovian setting that would mean extending the state space of the car to
+include velocity.
+
+\begin{align}
+  \Energy{dyn-ori} &= \|\ori{i}{t} - \ori{i}{t-1}\|^2\\
+  \Energy{dyn-vel} &= \|(\pos{i}{t} - 2\pos{i}{t-1}) + \pos{i}{t-2}\|^2
+\end{align}
+
+As a result the dynamics are modeled by weighted combination of holonomic
+constraint and smoothness constraints.
+
+\begin{align}
+  \WEnergy{dyn} &= \WEnergy{dyn-hol} + \WEnergy{dyn-ori} + \WEnergy{dyn-vel}
+\end{align}
+
+\subsubsection{Size Prior}
+
+Prior can include among many other things the size prior on the car.
+
+\begin{align}
+  \label{eq:totalSizeEnergy}
+  \Energy{size} &= (\dimsn{i} - \expDimsn)^\top\Sigma_{\expDimsn}^{-1}(\dimsn{i} -
+  \expDimsn)
+\end{align}
+
+where $\expDimsn$ is the mean TP dimensions and
+$\Sigma_{\expDimsn}$ is the correspondence covariance matrix.
+
+\begin{figure}
+  \centering
+  \newcommand{\imagewidth}{\columnwidth}
+  \input{Source/scenelayoutoverlayCity0961}
+  \caption{A sample road scene with the unknowns of each car modeled as random variables. 
+  The relating energies are shown in Figure~\ref{fig:graphmodel}}
+\end{figure}
+\begin{figure}
+    \input{Source/graphical_model_multiple}
+    \caption{Graphical model for a single frame with state of car represented
+    as single node.  The six numbered nodes represent the unknown state variables of each car. The shaded nodes in the graphical model are observed variables. }
+  \label{fig:graphmodel}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{results/0009_contPtTracks_size_bboxOcc_yawTstepWiseInference_0000000061.png}
+\end{figure}
+\begin{figure}
+  \includegraphics[width=\columnwidth]{results/0009_lane_size_bboxOcc_yawTstepWiseInference_0000000061.png}
+\end{figure}
+
+\begin{table}
+  \centering
+  \begin{tabular}{lrrr}
+    \toprule
+    Energy & t & yaw & dim \\
+    \midrule
+    initialization                                                                                  & 3.79 & \textbf{0.86} & 1.64 \\
+    $\EnergyLane+\EnergySize+\EnergyBBox+\EnergyDyn                                       $ & 3.83 & 0.90 & \textbf{1.14} \\
+    %$\EnergyLane+\EnergySize+\EnergyBBoxocc+\EnergyDyn                                    $ & 3.83 & 0.90 & 1.14 \\
+    %$\EnergyLane+\EnergySize+\EnergyBBoxocc+\EnergyDyn+\EnergyCol                         $ & 3.92 & 0.91 & 1.15 \\
+    %$\EnergyLane+\EnergyContpttracks+\EnergySize+\EnergyBBoxocc+\EnergyDyn             $ & 3.81 & 0.92 & 1.59 \\
+    % \EnergyBBox+\EnergyDyn+\EnergyCol $
+    $\EnergyTrackNoOcc+\EnergyCol + \EnergyLane + \dots$  & 3.80 & 0.91 & 1.58 \\
+    $\EnergyTrack+\EnergyCol + \EnergyLane + \dots$ & \textbf{3.78} & 0.91 & 1.58 \\
+    \bottomrule
+  \end{tabular}
+  \caption{Localization experiment results with different combination of energies.
+We report error in three metrics translation error (t) in meters per car, yaw error (yaw) in radians per car and dimension error is again meters per car.}
+\end{table}

### 2015-11-03 CVPR16/Source/experiments.tex
Added plot for mean error in the error plot.

@@
 \begin{figure*}
-\includegraphics[trim=1.0in 0.2in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
-  \caption{From top: (1)Association Experiment results on dynamic and occluded tracks. %} \label{fig:assoc-results}
-    (2) Association Experiment results on occluded points. %} \label{fig:assoc-occ-results}
-    (3) Association Experiment results on dynamic points. %} \label{fig:assoc-dynamic-results}
-    (4) Association Experiment results on all points.
-The error is in terms of average fraction of foreground points incorrectly associated to objects per sequence.
-Occluded points are chosen because our method is especially helpful in occlusion cases while dynamic points are chosen for fair comparison against motion segmentation methods.} \label{fig:assoc-occ-results}
+\includegraphics[trim=1.0in 0.4in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
+  \caption{Association error evaluation on different selection of tracks. The
+    numbers on y-axis represent the data sequence number in KITTI dataset. The
+    first set of bars in each plot correspond to the mean across all sequences.
+    The error is in terms of average fraction of foreground points incorrectly
+    associated to objects per sequence. Occluded points are chosen because our
+    method is especially helpful in occlusion cases while dynamic points are
+    chosen for fair comparison against motion segmentation methods.}
+\label{fig:assoc-occ-results}
 \end{figure*}

### 2015-11-03 CVPR16/Source/experiments.tex
Added continous bouding box energy. Moved all other energies to the supplementary material. Moved the qualitative results from localization experiment to supplementary material as well.

@@
 \subsection{Localization Experiment}
-To prove the effectiveness of our method we apply it to the localization
+To show the effectiveness of our method we apply it to the localization
 problem. We estimate the position, orientation and dimensions of the car with
@@
 car, yaw error (yaw) in radians per car and dimension error is again meters per
-car.
+car. The results are shown in Table~\ref{tab:localizationExperiment}.
 
@@
 
-\subsubsection{Point tracks energy with occlusion}
+\subsubsection{Continuous point tracks energy with occlusion}
 \label{sec:totalContPtTracksEnergy}
@@
 
-\subsubsection{Object detection energy}
+\subsubsection{Continuous bounding box energy with occlusion}
 
-We model object detection energy as the norm of difference in the coordinates
-of the projected bounding box and detected bounding box. The detected bounding
-box is represented by the extrema along X and Y dimensions $\bb{i} = [\xmin,
-\ymin, \xmax, \ymax]^\top$. If $\dimsn{i} = [l, w, h]^\top$ represent the 3D
-then we can compute the eight corners of the cuboid model in the tracklet
-coordinate transform as
+Object detection is usually followed by non-maximal suppression that results in
+discarding similar bounding boxes. When we are jointly optimizing detections
+with other cues, it is not usually desirable to go with a single bounding box.
+Hence, we keep all the bounding box detections by approximating them with
+multi-modal sum of Gaussian like logistic functions. We fit the parametric function of the form 
+%
+\begin{multline}
+  S(\bb{i}) = \\
+  \sum_k A_k \exp(-(\bb{i}-\mu^{(d)}_k)^\top \Sigma^{(d)-1}_k
+  (\bb{i}-\mu^{(d)}_k))
+\end{multline}
+%
+to detection scores, by non-linear error minimization with initialization from
+non-maximal suppressed outputs. Here $\mu^{(d)}_j$ is one of the $k$ modes as a
+4D vector representing a single bounding box as $[\minx, \miny, \maxx,
+\maxy]^\top$. The optimization is constrained with symmetry and positive
+definiteness of $\Sigma^{(d)-1}_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
 
-With slight abuse of notation for projection operator we write this energy as
+\paragraph{Detection scores with occlusion reasoning} 
+\def\u{\mathbf{u}}
+With our model of $\Ptrans$ described in Section \ref{sec:ptransmission}, we can
+compute the probability of a point $\u$ on image be occluded assuming
+the point is on traffic participant (TP) $i$ with mean depth $\mu^{(i)}_d$ as
 \begin{align}
-  \EnergyBBox &= \left\| \projectionOf{\dimsn{i}} - \bb{i}\right\|^2_2 \enspace.
+  O_{i}(\u, \mu^{(i)}_d) = 1 - \Ptransmission(\mu^{(i)}_d\u) \enspace .
+\end{align}
+
+If we know a portion of our proposed detection bounding box is known to be
+occluded, then we would like to decrease the confidence in the detection score
+about the localization of that end of the object. Assuming that the occlusion
+is often on the boundary of detection bounding boxes, we want to decrease our
+confidence on the mean detection boundaries around the occluded boundaries.
+To re-model our detection scores scaled by continuous occlusion we sample
+$O_{i}(\mathbf{u}, \mu^{(i)}_d)$ at the hypothesized detection boundaries from
+GMM $S(.)$ and we augment the detection boundary covariance matrix by
+$\mathcal{P}_{j} = \rho_{j}\rho_{j}^\top$ where $\rho_{j} = O_{j}(\mathbf{u},
+\mu^{(i)}_d)$. The new covariance matrix in detection score is given by 
+  $\Sigma'^{(d)}_j = \mathcal{P}_{j} + \Sigma^{(d)}_j$.
+The detection scores GMM with occlusion is given by replacing the covariance
+matrix
+%
+\begin{multline}
+  S'(\bb{i}) =
+  \\
+  \sum_j A_j \exp(-(\bb{i}-\mu^{(d)}_j)^\top \Sigma'^{(d)-1}_j
+  (\bb{i}-\mu^{(d)}_j))
+\end{multline}
+
+The energy of detection scores is simply take to be the inverse of the detection score.
+\begin{align}
+  \Energy{detect}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}
 \end{align}
@@
 
-\subsubsection{Lane energy}
-\label{sec:laneEnergy}
- The lanes are modeled as splines. Here we assume that the confidence in lane
- detection is decreases as the distance from the lane center increases.  The
- energy is given by the dot product between car orientation and tangent to the
- lane at that point.
-
-\begin{align}
-  \label{eq:laneOrientationEnergy}
-  \Energy{lane} = 
-  \sum_{m \in M_{\text{close}}}
-  (1 - \ori{i}{t} \cdot \text{TAN}(L_{m}(k), \pos{i}{t}) )
-\LaneUncertainty{\pos{i}{t}}
-\end{align}
-where $M_{\text{close}} = \{m : \text{DIST}(L_{m}(k), \pos{i}{t}) < d_{\text{thresh}}\} $ is
-the set of nearby lanes close to the object by a certain distance threshold $d_{\text{thresh}}$ and 
-\begin{align}
-\LaneUncertainty{\pos{i}{t}} = 
-  \frac{1}{1 + \exp(-q(w_{\text{road}} - \text{DIST}(L_{m}(k), \pos{i}{t})))}
-\end{align}
-for some constant $w_{\text{road}}$ that represents the width of the road.
-
-\subsubsection{Transition probability}
-Dynamics constraints should not only enforce smooth trajectories, but also the
-holonomic constraints.  The following energy adds a penalty if the change in
-position is not in direction of previous orientation.
-
-\begin{align}
-  \label{eq:totalPosTransitionEnergy}
-  \Energy{dyn-hol} = 1 - \ori{i}{t-1} \cdot (\pos{i}{t} - \pos{i}{t-1})
-\end{align}
-
-The following energy adds a penalty for change in position and orientation
-but a penalty for change in velocity is much better approximation. However, in
-a Markovian setting that would mean extending the state space of the car to
-include velocity.
-
-\begin{align}
-  \Energy{dyn-ori} &= \|\ori{i}{t} - \ori{i}{t-1}\|^2\\
-  \Energy{dyn-vel} &= \|(\pos{i}{t} - 2\pos{i}{t-1}) + \pos{i}{t-2}\|^2
-\end{align}
-
-As a result the dynamics are modeled by weighted combination of holonomic
-constraint and smoothness constraints.
-
-\begin{align}
-  \WEnergy{dyn} &= \WEnergy{dyn-hol} + \WEnergy{dyn-ori} + \WEnergy{dyn-vel}
-\end{align}
-
-\subsubsection{Size Prior}
-
-Prior can include among many other things the size prior on the car.
-
-\begin{align}
-  \label{eq:totalSizeEnergy}
-  \Energy{size} &= (\dimsn{i} - \expDimsn)^\top\Sigma_{\expDimsn}^{-1}(\dimsn{i} -
-  \expDimsn)
-\end{align}
-
-where $\expDimsn$ is the mean TP dimensions and
-$\Sigma_{\expDimsn}$ is the correspondence covariance matrix.
+\subsubsection{Other energies}
+Other energies we use are described in detail in the supplementary material. We briefly describe them here:
+\begin{description}
+  \item[Lane energy ($\Energy{lane}$)] This energy term constrains the
+    orientation of traffic participants to be parallel to the nearest detected
+    lane. The lanes are either detected visually or obtained from GPS and Map 
+    information.
+  \item[Transition probability ($\Energy{dyn}$)] We use these energies to
+    constrain the motion of cars to be smooth in linear motion and rotation
+    motion. We also constrain cars to move in the direction of heading.
+  \item[Size prior ($\EnergySize$)] We use size prior of cars by using the mean
+    of cars over the KITTI dataset.
+\end{description}
 
@@
   \label{fig:graphmodel}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{results/0009_contPtTracks_size_bboxOcc_yawTstepWiseInference_0000000061.png}
-\end{figure}
-\begin{figure}
-  \includegraphics[width=\columnwidth]{results/0009_lane_size_bboxOcc_yawTstepWiseInference_0000000061.png}
 \end{figure}
@@
 We report error in three metrics translation error (t) in meters per car, yaw error (yaw) in radians per car and dimension error is again meters per car.}
+  \label{tab:localizationExperiment}
 \end{table}

### 2015-11-04 CVPR16/Source/experiments.tex
Update Association Experiment

@@
 
-\paragraph{Dataset} We use KITTI dataset for our experiments.
+In this section, we first compare our continuous occlusion model for point-to-object association against the baseline method using detection bounding boxes and state-of-the-art methods for motion segmentation.
+We then show how the proposed model benefits the task of 3D localization in autonomous driving.
+
+For our experiments, we use the KITTI dataset~\cite{geiger2013vision}, which consists of video sequences of road scenes under a variety of driving conditions including highways and residential areas.
+It also provides ground truth data for different tasks such as segmentation, detection, tracking and 3D localization.
+
+%\paragraph{Dataset} We use KITTI dataset for our experiments.
 \cite{geiger2013vision}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Association error evaluation}
+\subsection{Association experiment}
 
-To verify the correctness of our association probability $\assocP$ we perform
-association error experiment that compare the accuracy of point track
-association with TPs with that of bounding box baseline method.
+We first perform the association experiment that compares the accuracy of point-to-object association using the proposed model against those of detection bounding box baseline method (BBox) and state-of-the-art motion segmentation methods, namely robust algebraic segmentation with hybrid perspective constraints (RAS)~\cite{Rao_etal_2010} and spectral clustering with point track spatial affinity (BM)~\cite{Brox_Malik_2010}.
 
-Note that the fraction $\assocP$ although called association probability does
-not capture the entire information that we have available for compute
-association of points to tracks. This above fraction is the association
-probability given the hypothesized parameters of TP model.
+%To verify the correctness of our association probability $\assocP$ we perform association error experiment that compare the accuracy of point track association with TPs with that of bounding box baseline method.
 
-To compute the association probability between TP $i$ and
-point track $j$ we must use re-projection error as well. When the association
-$i$ and $j$ is right and the point of reflection is at depth $\lambda$ the
-re-projection error must be zero \eqref{eq:reprojerror}, otherwise the error
-becomes a measure of distance from the true solution.
-The error terms can be converted to probability domain by considering the error
-term as negative log of probability
+\subsubsection{Association probability}
 
+Using our continuous occlusion model in Section~\ref{sec:setup}, the association probability $\assocP$ of $j$\textsuperscript{th} point track with $i$\textsuperscript{th} object at depth $\lambda$ can be defined as
+\begin{align}
+  \assocP = \Prefl\Ptrans,
+\end{align}
+where $\Prefl$ and $\Ptrans$ are from \ref{eq:evalPrefl} and \ref{eq:evalCumulativePtrans} respectively.
+Note that the fraction $\assocP$ although called association probability does not capture the entire information that we have available for computing association of point tracks to objects.
+This above fraction is the association probability given the hypothesized parameters of TPs.
+
+To compute the association probability $\assocP$ between point track $j$ and TP $i$ we must use re-projection error as well.
+When the association of $i$ and $j$ is correct and the point of reflection is at depth $\lambda$, the re-projection error must be zero \eqref{eq:reprojerror}, otherwise the error becomes a measure of distance from the true solution.
+The error terms can be converted to probability domain by considering the error term as negative log of probability
 \begin{align}
@@
 
-Using both the evidence terms we can write probability of association as
+Using both of the above evidence terms we can write the probability of association $P^{(ij)}_{\text{assoc}}$ as follows
 \begin{align}
@@
 
-Once we have the probability of association we can compute the best possible
-assignment of TP for each point. The points having very small association
-probability are assigned to the background,
+Once we have the probability of association $P^{(ij)}_{\text{assoc}}$ we can compute the best possible assignment of TP for each point track.
+The points having very small association probability are assigned to the background,
 \begin{align}
@@
 
-We use bounding box based assignment of point tracks to TPs as the baseline.
-For the regions where the bounding boxes overlap, we assign the points to the
-TP that has smaller mean depth then the competing bounding box.
+We use detection bounding box based assignment of point tracks to TPs as the baseline.
+For the regions where the bounding boxes overlap, we assign the point tracks to the TP that has smaller mean depth than the competing bounding box.
+
+\subsubsection{Association results}
+
+For each sequence of the KITTI dataset, the methods of \cite{} and \cite{} are used respectively for computing detection bounding boxes and object tracklets.
+We then apply \cite{} on object tracklets to extract point tracks.
+From these point tracks, we create four different sets of input point tracks, namely all point tracks, occluded point tracks, dynamic point tracks and dynamic and occluded point tracks, to examine various aspects of the methods (our method focuses on occlusion scenes while RAS and BM favor dynamic scenes).
+In addition to point tracks, the parameters of all TPs estimated by the method~\cite{Song_Chandraker_2014} are provided to our method (for computing association probablity) and the baseline method (for depth ordering).
+
+Figure~\ref{fig:assoc-occ-results} presents the association errors --- the percentages of point tracks incorrectly assigned to objects --- of all methods on four sets of input point tracks for each sequence as well as the mean results over all sequences of the KITTI dataset.
+From these results, our method consistently achieves the lowest mean errors, followed by the bounding box baseline method, which clearly shows the advantage of our continous occlusion model.
+The mean errors of BM and RAS are comparable and among the highest ones.
 
@@
 \includegraphics[trim=1.0in 0.4in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
-  \caption{Association error evaluation on different selection of tracks. The
+  \caption{Association errors on different sets of point tracks. The
     numbers on y-axis represent the data sequence number in KITTI dataset. The
@@
     The error is in terms of average fraction of foreground points incorrectly
-    associated to objects per sequence. Occluded points are chosen because our
-    method is especially helpful in occlusion cases while dynamic points are
-    chosen for fair comparison against motion segmentation methods.}
+    associated to objects per sequence.}
 \label{fig:assoc-occ-results}
@@
     & Associations & Error in association\\
-    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png} &%
+    \rotatebox{90}{\hspace{2em} Baseline} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png} &%
     \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{2em} Brox} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png} &%
+    \rotatebox{90}{\hspace{2em} BM} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png} &%
     \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
@@
     \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png} &%
+    \rotatebox{90}{\hspace{2em} Baseline} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png} &%
     \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{2em} Brox} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png} &%
+    \rotatebox{90}{\hspace{2em} BM} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png} &%
     \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
@@
   \caption{Qualitative results for association experiment. The left column
-  shows the point tracks assignment to appropriate track. Each color represents
+  shows the point tracks assignment to appropriate object. Each color represents
 a different track to which the point is associated to. Right column shows the
-probablistic error in association: red is low error and blue is high error.
+probablistic error in association: red is low error while blue is high error.
 Note that our method changes smoothly at the boundary of the objects with

### 2015-11-04 CVPR16/Source/experiments.tex
Update Association Experiment

@@
 We then apply \cite{} on object tracklets to extract point tracks.
-From these point tracks, we create four different sets of input point tracks, namely all point tracks, occluded point tracks, dynamic point tracks and dynamic and occluded point tracks, to examine various aspects of the methods (our method focuses on occlusion scenes while RAS and BM favor dynamic scenes).
-In addition to point tracks, the parameters of all TPs estimated by the method~\cite{Song_Chandraker_2014} are provided to our method (for computing association probablity) and the baseline method (for depth ordering).
+From these point tracks, we create four different sets of input point tracks, namely all point tracks, occluded point tracks, dynamic point tracks and dynamic and occluded point tracks, to examine various aspects of the methods (our method focuses on occlusion scenes while RAS and BM favour dynamic scenes).
+In addition to point tracks, the parameters of all TPs estimated by the method~\cite{Song_Chandraker_2014} are provided to our method (for computing association probability) and the baseline method (for depth ordering).
 
 Figure~\ref{fig:assoc-occ-results} presents the association errors --- the percentages of point tracks incorrectly assigned to objects --- of all methods on four sets of input point tracks for each sequence as well as the mean results over all sequences of the KITTI dataset.
-From these results, our method consistently achieves the lowest mean errors, followed by the bounding box baseline method, which clearly shows the advantage of our continous occlusion model.
-The mean errors of BM and RAS are comparable and among the highest ones.
+From the results, our method is usually the most accurate among all methods, leading to the best mean errors on all sets of input point tracks, which is followed by the bounding box baseline method.
+This clearly shows the advantage of our continuous occlusion model over the simple baseline method for resolving occlusions.
+Both RAS and BM often have the highest errors and hence the highest mean errors on all sets of input point tracks.
 

### 2015-11-04 CVPR16/Source/experiments.tex
fixed the plot and added a table for association results.

@@
 
-Figure~\ref{fig:assoc-occ-results} presents the association errors --- the percentages of point tracks incorrectly assigned to objects --- of all methods on four sets of input point tracks for each sequence as well as the mean results over all sequences of the KITTI dataset.
+Table~\ref{tab:meanAssoc} and Figure~\ref{fig:assoc-occ-results} present the association errors --- the percentages of point tracks incorrectly assigned to objects --- of all methods on four sets of input point tracks for each sequence as well as the mean results over all sequences of the KITTI dataset.
 From the results, our method is usually the most accurate among all methods, leading to the best mean errors on all sets of input point tracks, which is followed by the bounding box baseline method.
@@
 \end{figure*}
+\begin{table}
+\begin{tabular}{lrrrr}
+  \toprule
+  & Ours & BBox & BM & RAS\\
+  \midrule
+  Dyn. and occ. tracks        & \textbf{13.2} & 21.3 & 30.9 & 37.8 \\
+  Occluded tracks             & \textbf{15.7} & 19.8 & 39.5 & 29.3 \\
+  Dynamic tracks              & \textbf{06.6} & 11.4 & 15.3 & 21.5 \\
+  All tracks                  & \textbf{08.6} & 12.6 & 21.9 & 16.4 \\
+  \bottomrule
+\end{tabular}
+\caption{Mean association experiment results in error percentage calculated as percentage of points wrongly associated.}
+\label{tab:meanAssoc}
+\end{table}
 

### 2015-11-04 CVPR16/Source/experiments.tex
Swapped the RAS results for dynamic and static points.

@@
   \midrule
-  Dyn. and occ. tracks        & \textbf{13.2} & 21.3 & 30.9 & 37.8 \\
-  Occluded tracks             & \textbf{15.7} & 19.8 & 39.5 & 29.3 \\
-  Dynamic tracks              & \textbf{06.6} & 11.4 & 15.3 & 21.5 \\
-  All tracks                  & \textbf{08.6} & 12.6 & 21.9 & 16.4 \\
+  Dyn. and occ. tracks        & \textbf{13.2} & 21.3 & 30.9 & 29.3 \\
+  Occluded tracks             & \textbf{15.7} & 19.8 & 39.5 & 37.8 \\
+  Dynamic tracks              & \textbf{06.6} & 11.4 & 15.3 & 16.4 \\
+  All tracks                  & \textbf{08.6} & 12.6 & 21.9 & 21.5 \\
   \bottomrule

### 2015-11-04 CVPR16/Source/experiments.tex
Update Association Experiment and Improve Flow A Bit

@@
-\section{Experiments}
+\section{Experimental results}
 \label{sec:experiments}
 
-In this section, we first compare our continuous occlusion model for point-to-object association against the baseline method using detection bounding boxes and state-of-the-art methods for motion segmentation.
+In this section, we first benchmark our continuous occlusion model for point-to-object association against the baseline method using detection bounding boxes and state-of-the-art methods for motion segmentation.
 We then show how the proposed model benefits the task of 3D localization in autonomous driving.
-
 For our experiments, we use the KITTI dataset~\cite{geiger2013vision}, which consists of video sequences of road scenes under a variety of driving conditions including highways and residential areas.
@@
 
-We first perform the association experiment that compares the accuracy of point-to-object association using the proposed model against those of detection bounding box baseline method (BBox) and state-of-the-art motion segmentation methods, namely robust algebraic segmentation with hybrid perspective constraints (RAS)~\cite{Rao_etal_2010} and spectral clustering with point track spatial affinity (BM)~\cite{Brox_Malik_2010}.
+We first perform the association experiment that compares the accuracy of point-to-object association using the proposed model against those of the detection bounding box baseline method (BBox) and state-of-the-art motion segmentation methods, namely robust algebraic segmentation with hybrid perspective constraints (RAS)~\cite{Rao_etal_2010} and spectral clustering with point track spatial affinity (BM)~\cite{Brox_Malik_2010}.
 
@@
 
-Using our continuous occlusion model in Section~\ref{sec:setup}, the association probability $\assocP$ of $j$\textsuperscript{th} point track with $i$\textsuperscript{th} object at depth $\lambda$ can be defined as
+Based on our continuous occlusion model in Section~\ref{sec:setup}, the association probability $\assocP$ of $j$\textsuperscript{th} point track with $i$\textsuperscript{th} object at depth $\lambda$ can be defined as
 \begin{align}
@@
 \end{align}
-where $\Prefl$ and $\Ptrans$ are from \ref{eq:evalPrefl} and \ref{eq:evalCumulativePtrans} respectively.
+where $\Prefl$ and $\Ptrans$ are from \eqref{eq:evalPrefl} and \eqref{eq:evalCumulativePtrans} respectively.
 Note that the fraction $\assocP$ although called association probability does not capture the entire information that we have available for computing association of point tracks to objects.
-This above fraction is the association probability given the hypothesized parameters of TPs.
+This above fraction is the association probability given the hypothesized parameters of TPs in the scene.
 
-To compute the association probability $\assocP$ between point track $j$ and TP $i$ we must use re-projection error as well.
-When the association of $i$ and $j$ is correct and the point of reflection is at depth $\lambda$, the re-projection error must be zero \eqref{eq:reprojerror}, otherwise the error becomes a measure of distance from the true solution.
-The error terms can be converted to probability domain by considering the error term as negative log of probability
+To compute the association probability $\assocP$ between point track $j$ and TP $i$ we must use the reprojection error as well.
+When the association of $i$ and $j$ is correct and the point of reflection is at depth $\lambda$, the reprojection error must be zero \eqref{eq:reprojerror}, otherwise the error becomes a measure of distance from the true solution.
+The error term can be converted to probability domain by considering the error term as negative log of probability
 \begin{align}
@@
 
-We use detection bounding box based assignment of point tracks to TPs as the baseline.
-For the regions where the bounding boxes overlap, we assign the point tracks to the TP that has smaller mean depth than the competing bounding box.
+For the baseline method, the associations between point tracks and TPs are achieved by using detection bounding boxes, where point tracks within each bounding box are simply assigned to it.
+For the regions where the bounding boxes overlap, we assign the point tracks to the TP that has smaller mean depth than the competing bounding boxes.
 
@@
 
-For each sequence of the KITTI dataset, the methods of \cite{} and \cite{} are used respectively for computing detection bounding boxes and object tracklets.
-We then apply \cite{} on object tracklets to extract point tracks.
+For each sequence of the KITTI dataset, the methods of \cite{Felzenszwalb_etal_2010} and \cite{Choi_Savarese_2010} are used respectively for computing detection bounding boxes and object tracklets.
+We then apply \cite{Zach2007} on object tracklets to extract point tracks.
 From these point tracks, we create four different sets of input point tracks, namely all point tracks, occluded point tracks, dynamic point tracks and dynamic and occluded point tracks, to examine various aspects of the methods (our method focuses on occlusion scenes while RAS and BM favour dynamic scenes).
@@
 
-Table~\ref{tab:meanAssoc} and Figure~\ref{fig:assoc-occ-results} present the association errors --- the percentages of point tracks incorrectly assigned to objects --- of all methods on four sets of input point tracks for each sequence as well as the mean results over all sequences of the KITTI dataset.
-From the results, our method is usually the most accurate among all methods, leading to the best mean errors on all sets of input point tracks, which is followed by the bounding box baseline method.
+Figure~\ref{fig:assoc-occ-results} shows the association errors --- the percentages of point tracks incorrectly assigned to objects --- of all methods on four sets of input point tracks for each sequence of the KITTI dataset, while the mean results over all sequences are presented in Table~\ref{tab:meanAssoc}.
+From Figure~\ref{fig:assoc-occ-results}, our method is usually the most accurate among all methods, leading to the best mean errors on all sets of input point tracks in Table~\ref{tab:meanAssoc}, which is followed by the bounding box baseline method.
 This clearly shows the advantage of our continuous occlusion model over the simple baseline method for resolving occlusions.
-Both RAS and BM often have the highest errors and hence the highest mean errors on all sets of input point tracks.
+RAS and BM often have the highest errors in Figure~\ref{fig:assoc-occ-results}, and hence the highest mean errors on all sets of input point tracks in Table~\ref{tab:meanAssoc}.
+
+More importantly, both RAS and BM rely on motions of objects for clustering point tracks, therefore they cannot work well with static point tracks (e.g., point tracks belong to parked cars).
+This fact can be observed in Table~\ref{tab:meanAssoc}, where there are large differences in the mean errors of both methods on data containing static point tracks (i.e., rows 2 and 4) and data consisting of dynamic point tracks only (i.e., rows 1 and 3).
+In contrast, our method and the baseline method are relatively independent of object motions, resulting in smaller performance gaps.
 
@@
 \includegraphics[trim=1.0in 0.4in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
-  \caption{Association errors on different sets of point tracks. The
-    numbers on y-axis represent the data sequence number in KITTI dataset. The
-    first set of bars in each plot correspond to the mean across all sequences.
-    The error is in terms of average fraction of foreground points incorrectly
-    associated to objects per sequence.}
+  \caption{Association errors on different sets of input point tracks.
+Numbers on y-axis represent data sequence numbers in KITTI dataset.
+Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
 \label{fig:assoc-occ-results}
@@
 \end{tabular}
-\caption{Mean association experiment results in error percentage calculated as percentage of points wrongly associated.}
+\caption{Mean association errors on different sets of input point tracks over all sequences of KITTI dataset.
+Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
 \label{tab:meanAssoc}
@@
   \end{tabular}
-  \caption{Qualitative results for association experiment. The left column
-  shows the point tracks assignment to appropriate object. Each color represents
-a different track to which the point is associated to. Right column shows the
-probablistic error in association: red is low error while blue is high error.
-Note that our method changes smoothly at the boundary of the objects with
-intermediate probabilities, while the baseline methods have only 0-1 error.} 
+  \caption{Qualitative results of the association experiment. The left column
+  shows the point track assignments to appropriate objects. Each color represents
+a different object to which point tracks can be associated to. Right column shows the
+probabilistic error in association: low errors are in red while high errors are in blue.
+Note that our method changes smoothly at the object boundaries with
+intermediate probabilities, while the baseline method has merely 0-1 error.} 
 \end{table*}
 
-\subsection{Localization Experiment}
+\subsection{Localization experiment}
 To show the effectiveness of our method we apply it to the localization
@@
 We model continuous point tracks energy with explicit occlusion reasoning as
-the expected re-projection error over the association probability,
+the expected reprojection error over the association probability,
 
@@
 $j$\textsuperscript{th} point with $i$\textsuperscript{th} TP at depth $\lambda$, $\{ \relp{i}{t} \}_i$ are the poses of all occluding objects at time $t$, $ \{ \dimsn{i} \}_i$ are the dimensions of all objects that occlude $i$
-and $\Ereproj(\lambda)$ is the re-projection error given by
+and $\Ereproj(\lambda)$ is the reprojection error given by
 %

### 2015-11-04 CVPR16/Source/intro.tex
Update Association Experiment and Improve Flow A Bit

--- 2015-11-02 CVPR16/Source/intro.tex
@@
 consecutive frames, the problem becomes one of finding out which points belong
-to which object following which one can use the consensus of segmented points
+to which object, following which one can use the consensus of segmented points
 to reconstruct or localize the object more accurately. Without additional 
-information this is very difficult problem as attempted by semantic segmentation 
+information, this is a very difficult problem as attempted by semantic segmentation 
 and motion segmentation methods. However, in the problems like reconstruction and
-localization on can use the hypothesis of the algorithm as the feedback. For
+localization one can use the hypothesis of the algorithm as the feedback.
+% What is the problem we are trying to solve, and why is it even important?
+
+% What did we do
+We propose a novel model for representation of objects in the scene so that point tracks
+can be probabilistically associated with objects while accounting for object occlusions.
+% Why is it novel
+Although our proposed model is inspired by Milan et
+al.\cite{Milan_etal_2014}, it is more detailed and more principled than their
+work. Milan et al. used soft ellipses and sigmoids to model pedestrians and
+their occlusions. Our reasoning is instead in 3D. We use ellipsoids to model objects
+and reason about their occupancies of the space to model their occlusions.
+% Ok you proposed a model is it of any use
+% How does it compare to state of art
+We show that our continuous occlusion model achieves significantly lower point-to-object association errors compared to the baseline method using detection bounding boxes and other state-of-the-art methods for motion segmentation~\cite{Brox_Malik_2010, Rao_etal_2010}.
+As a consequence, our model benefits the task of 3D localization of traffic participants in autonomous driving.

### 2015-11-04 CVPR16/Source/setup.tex
Generated visualizations.
Update Association Experiment and Improve Flow A Bit

--- 2014-11-10 CVPR/Source/setup.tex
@@
-\section{Overview of Problem and Our Approach}
-TODO:
-\vspace{4cm}
-
-\paragraph{Notation}
-
-\begin{table}[h]
-  \begin{tabular}{|l|l|}
-    \hline
-    Symbol & Meaning \\
-    \hline
-    $\pos{i}{t}$ & Position of $i$th car at time $t$\\
-    $\ori{i}{t}$ & Orientation of $i$th car at time $t$\\
-     $\dimsn{i}$ & 3D bounding box of the car (dimensions)\\
-    $\state{i}{t}$ & State of car $=\{\pos{i}{t}, \ori{i}{t}, \dimsn{i}\}$\\
-    $\egop$ & Position of camera at time $t$\\
-    $\egoo$ & Orientation of camera at time $t$\\
-    $\relp{i}{t}$ & Relative car pose w.r.t. camera \\
-    $\tracklets$ & 3D points tracked on car $i$ in its own frame\\
-    $\trackp{t}$ & Projection of $\tracklets$ in camera\\
-    $\projectionOf{.}$ & Projection function for pose $\relp{i}{t}$\\
-    $\bb{i}$ & 2D bounding box of the car in image\\
-    \hline
-  \end{tabular}
-\end{table}
-
-%%%%%%%%% BODY TEXT
-\paragraph{The Model}
-
-The objective is to find the most likely traffic participant (TP) state given
-various evidences $\mathbb{E} = \{\{\trackp{t}\}, \{\bb{i}\}, \text{lane det.},
-\text{map}, \text{GPS}\}$.
-
-Mathematically, find:
-\begin{align}
-  \{\state{i}{t}\}^* &= \arg \max P(\{\state{i}{t}\} | \mathbb{E})
-\end{align}
-
-Bayes rule
-\begin{align}
-  P(\{\state{i}{t}\} | \mathbb{E}) &=
-  \frac{1}{Z}P( \mathbb{E} | \{\state{i}{t}\})P(\{\state{i}{t}\})
-\end{align}
-
-Assume conditional independence according to graphical model in
-\ref{fig:graphmodel}.
-
-\begin{multline}
-  P(\{\state{i}{t}\} | \mathbb{E}) =
-  \frac{1}{Z}
-  \prod_{t=s_i}^{e_i}\prod_{i,j: i \ne j}(P(\state{i}{t}, \state{j}{t}))\\
-%
-  \prod_{i=1}^{N}
-  \prod_{t=s_i}^{e_i}
-  P(\bb{i} | \state{i}{t})
-  P(\trackp{t} | \state{i}{t})\\
-  P(\state{i}{t} | L_m(t))
-  P(\state{i}{t} | \state{i}{t-1})
-  P(\state{i}{t})
-\end{multline}
-
-We can formulate similar objective function in negative log domain:
-\footnote{TODO:Resolve inconsistency in summation absorption in energy terms.}
-\begin{multline}
-  -\log{P(\{\state{i}{t}\} | \mathbb{E})} = 
-  Z' + \sum_{i,j:i\ne j} \sum_{t=s_i}^{e_i}  \WEnergyCol \\
-  + \sum_{i=1}^N \sum_{t=s_i}^{e_i}
-    \WEnergy{box}
-  + \WEnergy{track}\\
-  + \WEnergy{lane}
-  + \WEnergy{dyn}
-  + \WEnergy{prior}
-\end{multline}
+\section{Continuous Occlusion Model}
+\label{sec:setup}
+The problem of segmenting points to objects often comes up in different
+computer vision problems especially in multi-body 
+reconstruction and localization. Given correspondence points on
+consecutive frames, the problem becomes one of finding out which points belong
+to which object, following which one can use the consensus of segmented points
+to reconstruct or localize the object more accurately. Without additional 
+information, this is a very difficult problem as attempted by semantic segmentation 
+and motion segmentation methods. However, in the problems like reconstruction and
+localization one can use the hypothesis of the algorithm as the feedback. For
+example, in this work we use 3D localization hypotheses to fit ellipsoid
+models of objects that can aid in better association of points to objects and
+further leading to more accurate localization results.

### 2015-11-04 CVPR16/Source/experiments.tex
Updated RAS results with sequence 4 results.

--- 2015-11-04 CVPR16/Source/experiments.tex
@@
   \midrule
-  Dyn. and occ. tracks        & \textbf{13.2} & 21.3 & 30.9 & 29.3 \\
+  Dyn. and occ. tracks        & \textbf{13.2} & 21.3 & 30.9 & 30.1 \\
   Occluded tracks             & \textbf{15.7} & 19.8 & 39.5 & 37.8 \\
-  Dynamic tracks              & \textbf{06.6} & 11.4 & 15.3 & 16.4 \\
+  Dynamic tracks              & \textbf{06.6} & 11.4 & 15.3 & 17.7 \\
   All tracks                  & \textbf{08.6} & 12.6 & 21.9 & 21.5 \\

### 2015-11-04 CVPR16/Source/abstract.tex

@@
 \begin{abstract}
-We propose a model for representation of objects so that points can be
-probabilistically  associated to the tracklets while accounting for occlusion.
-We compare our approach against state of the art motion segmentation methods.
+We propose a novel model for representing objects so that point tracks can be
+probabilistically  associated with objects while accounting for object occlusions.
+We compare our approach against state-of-the-art motion segmentation methods.
 \end{abstract}

### 2015-11-04 CVPR16/Source/occlusion.tex
Added continous bouding box energy. Moved all other energies to the supplementary material. Moved the qualitative results from localization experiment to supplementary material as well.
Update Association Experiment and Improve Flow A Bit
Added a picture of chosen points for the ptransmission plot.

@@
   P^{ij}_{\textit{reflection}} (\lambda) = (\max \{0, \nabla {f^i_{occ}}(\bx_j)^\top \ray \})^2
+\label{eq:evalPrefl}
 \end{align}
@@
 \paragraph{Transmission probability}
+\label{sec:ptransmission}
 Since we are modeling occupancy as transparency, we look towards optics for modeling of translucent objects.
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{results/plotPtransmission_exact_vs_approx.pdf}
+  \includegraphics[width=\columnwidth]{results/plotPtransmission_exact_vs_approx_pt_vis-small.png}\\
+  \includegraphics[trim=0.0 0 0.3in 0, clip, width=\columnwidth]{results/plotPtransmission_exact_vs_approx.pdf}
   \caption{Comparing the approximate $\Ptrans$ with exact version.

### 2015-11-04 CVPR16/Source/experiments.tex
Changed the color of correct points to blue instead of red.

@@
     & Associations & Error in association\\
-    \rotatebox{90}{\hspace{2em} Baseline} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png} &%
+    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png} &%
     \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
@@
     \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{2em} Baseline} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png} &%
+    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png} &%
     \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
@@
 a different object to which point tracks can be associated to. Right column shows the
-probabilistic error in association: low errors are in red while high errors are in blue.
+probabilistic error in association: low error points are in blue while high error points are in red.
 Note that our method changes smoothly at the object boundaries with
@@
 %
-We use the following energies in our graphical model.
+Next, we explain the important energies used in our graphical model.
 
@@
 
+\subsection{Metropolis Hastings Inference}
+We use Metropolis Hastings' methods for graphical model inference. Since we are
+optimizing over continuous random variables, we use Gaussian distribution as
+the proposal distribution.
+
 \begin{figure}
@@
     initialization                                                                                  & 3.79 & \textbf{0.86} & 1.64 \\
-    $\EnergyLane+\EnergySize+\EnergyBBox+\EnergyDyn                                       $ & 3.83 & 0.90 & \textbf{1.14} \\
+    %$\EnergyLane+\EnergySize+\EnergyBBox+\EnergyDyn                                       $ & 3.83 & 0.90 & \textbf{1.14} \\
     %$\EnergyLane+\EnergySize+\EnergyBBoxocc+\EnergyDyn                                    $ & 3.83 & 0.90 & 1.14 \\

### 2015-11-04 CVPR16/Source/abstract.tex
Add Abstract"

--- 2015-11-03 CVPR16/Source/abstract.tex
@@
 \begin{abstract}
-We propose a model for representation of objects so that points can be
-probabilistically  associated to the tracklets while accounting for occlusion.
-We compare our approach against state of the art motion segmentation methods.
+This paper studies the problem of segmenting tracked feature points of multiple objects in a video sequence.
+We consider scenes that contain both dynamic and static objects which usually appear in the context of autonomous driving (e.g., moving and parked cars) and occlusions among objects.
+We propose a novel continuous model for representing objects so that point tracks can be probabilistically and accurately assigned to the corresponding object while accounting for object occlusions.
+Detailed experiments on the KITTI dataset show the superiority of the propose method over the baseline method which simply uses detection bounding boxes for resolving occlusions and other state-of-the-art motion segmentation methods which cannot cope well with static objects.
+As a notable application, we show how our continuous occlusion model benefits the task of 3D localization of traffic participants in autonomous driving.
 \end{abstract}

### 2015-11-04 CVPR16/Source/intro.tex
Add Abstract"

@@
 \section{Introduction}
+Motion segmentation is a fundamental problem in computer vision, which aims to separate the motions of multiple objects appearing in a video sequence.
+The input data is usually a set of points extracted on the surfaces of the objects, which are then tracked through the video sequence.
+Motion segmentation serves as an important preprocessing step for different applications such as 3D localization and reconstruction, where the point tracks associated with each individual object can be used to localize or reconstruct the object in the 3D space accurately.
+
+Previous work 
+Input assumption
+Contributions
+
 The problem of segmenting points to objects often comes up in different

### 2015-11-05 CVPR16/Source/occlusion.tex
Reviewed occlusion.tex

@@
 
-Thus, we have modeled the transmission probability to effectively capture the effect of occlusion due to all traffic participants in a scene that lie along a particular ray.
-We reiterate that our reflection and transmission probabilities are continuous functions, which allows us to define continuous energy functions for association and 3D object localization, as described in the next section.
-
-%\paragraph{Probabilistic occlusion levels}
-%With the above modeling and using \eqref{eq:imgform},
-
-%% We model the probability of a point $\mathbf{x}_j$ on a object $i$ getting successfully
-%% observed in a camera image at point $\trackpj{t}$ is dependent up two factors,
-%% (1) reflection and (2) transmission through intermediate space. The reflection
-%% part ensures that there is an object to reflect a point at a certain region in
-%% the 3D space while transmission part models occlusion.
-%% \begin{align}
-%%   P^{(ij)}_{\text{observation}} = P^{(ij)}_{\text{reflection}}P^{(j)}_{\text{transmission}}
-%% \end{align}
-
-%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% \subsection{Reflection probability}
-%% For Lambertian reflection we replace the surface normal with the
-%% gradient of occupancy.
-%% %
-%% \begin{align}
-%%   \Prefl = (\max \{0, \nabla \occf^\top
-%%   \hat{\mathbf{r}_j}\})^2
-%% \end{align}
-%% %
-%% where $\ray =
-%% \frac{K^{-1}\trackpj{t}}{\|K^{-1}\trackpj{t}\|}$ is unit vector in the
-%% direction of ray. The gradient in the direction opposite to ray yields -ve
-%% probability which needs to be clipped off. Squaring the function keep it
-%% smooth near zero.
-
-%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% \subsection{Transmission probability}
-%% A model for transmission of light through a material of thickness $x$,
-%% density $\rho$ and opacity $k_o$ is given by Beer-Lambert law 
-%% %
-%% \begin{align}
-%%   I(x) = I_0e^{-k_o\rho x}
-%% \end{align}
-%% %
-
-%% Since both opacity and density are represented by the occupancy function
-%% $\occftot = \sum_i \occf$, and also the domain of our $\occftot$ is $[0, 1]$ instead of $[0,
-%% \infty]$ as in case of $k_o$; we replace $e^{-k_o\rho}$ by the transparency
-%% function $1 - \occftot$. So the transmission probability over a small distance
-%% $d\lambda$ is given by
-%% %
-%% \begin{align}
-%%   P_{\text{transmission}}(\lambda + d\lambda) =
-%%   P_{\text{transmission}}(\lambda) (1-\occftot)^{d\lambda}
-%% \end{align}
-%% %
-
-%% For a given 3D point $\mathbf{x}_j = \lambda \ray$, the probability that the
-%% point $\trackpj{t}$ is reflected from a distance $\lambda$ is given by
-
-%% \begin{align}
-%%   %P^{(j)}_{\text{observation}}(\lambda) &= P_{\text{reflection}}
-%%   \Ptrans &=
-%%   \prod_{0}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda} %\\
-%%   %= \max \{ 0, (\nabla f_{occ}&(\lambda \ray)^\top \ray) \}
-%%   %\prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
-%%   \label{eq:ptrans-integral}
-%% \end{align}
-%% where $\prod_{0}^{\lambda}$ represents the \emph{product integral} from $0$ to
-%% $\lambda$.
-
-%% In practice, the integral for transmission probability
-%% \eqref{eq:ptrans-integral} is difficult to compute even numerically. So we
-%% choose a product of sigmoid function that approximates the behaviour of
-%% transmission probability,
-%% %
-%% \begin{align}
-%% \label{eq:evalCumulativePtrans}
-%%   \Ptrans &= \prod_i L_u(\trackp{t}; \muiu,\Sigmaiu)L_{\lambda}(\lambda; \mu^i_d)
-%% \end{align}
-%% %
-%% where $L_u(.)$ is sigmoid in image domain with $\mu^i_u$ and $\Sigma^i_u$
-%% representing the elliptical projection of $i^{th}$ TP.
-%% $L_{\lambda}(.)$ is sigmoid in the depth domain with $\mu^i_d$ as the mean
-%% depth of the $i^{th}$ TP.
-%% %
-%% \begin{align}
-%%   L_u(\mathbf{u}; \muiu,\Sigmaiu) &= \frac{1}{
-%%     1 + e^{-k_u(1 - (\mathbf{u} - \muiu)^\top\Sigmaiu(\mathbf{u} -
-%%     \muiu))}
-%%   }
-%%   \\
-%%   L_{\lambda}(\lambda; \mu^i_d) &= \frac{1}{
-%%     1 + e^{-k_d(\lambda - \mu^i_d)}
-%% }
-%% \end{align}
-%% %
-
-%% \begin{comment}%% Comment
-%%   A product integral is a simple integral in log domain
-%%   \begin{align}
-%%     \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} =
-%%     e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
-%%   \end{align}
-%% \end{comment}%% Comment
-
-% \paragraph{Notation}
-% We summarize the notation used in the report for quick reference.
-% \\
-% 
-% 
-%   \begin{tabular}{|l|l|}
-%     \hline
-%     Symbol & Meaning \\
-%     \hline
-%     $\pos{i}{t}$ & Position of $i$th car at time $t$\\
-%     $\ori{i}{t}$ & Orientation of $i$th car at time $t$\\
-%      $\dimsn{i}$ & 3D bounding box of the car (dimensions)\\
-%     $\state{i}{t}$ & State of car $=\{\pos{i}{t}, \ori{i}{t}, \dimsn{i}\}$\\
-%     $\egop$ & Position of camera at time $t$\\
-%     $\egoo$ & Orientation of camera at time $t$\\
-%     $\relp{i}{t}$ & Relative car pose w.r.t. camera \\
-%     $\tracklets$ & 3D points tracked on car $i$ in its own frame\\
-%     $\trackp{t}$ & Projection of $\tracklets$ in camera\\
-%     $\projectionOf{.}$ & Projection function for pose $\relp{i}{t}$\\
-%     $\bb{i}$ & 2D bounding box of the car in image\\
-%     \hline
-%   \end{tabular}
+Thus, we have modeled the transmission probability to effectively capture the
+effect of occlusion due to all traffic participants in a scene that lie along a
+particular ray. We reiterate that our reflection and transmission probabilities
+are continuous functions, which allows us to keep the problem formulation in
+continuous domain allowing for easier optimization.

### 2015-11-05 CVPR16/Source/abstract.tex
Update Intro

@@
 This paper studies the problem of segmenting tracked feature points of multiple objects in a video sequence.
-We consider scenes that contain both dynamic and static objects which usually appear in the context of autonomous driving (e.g., moving and parked cars) and occlusions among objects.
+We consider scenes that contain both dynamic and static objects, which usually appear in the context of autonomous driving (e.g., moving and parked cars), and occlusions among objects.
 We propose a novel continuous model for representing objects so that point tracks can be probabilistically and accurately assigned to the corresponding object while accounting for object occlusions.
 Detailed experiments on the KITTI dataset show the superiority of the propose method over the baseline method which simply uses detection bounding boxes for resolving occlusions and other state-of-the-art motion segmentation methods which cannot cope well with static objects.
-As a notable application, we show how our continuous occlusion model benefits the task of 3D localization of traffic participants in autonomous driving.
+As a notable application, we show how our continuous occlusion model benefits the task of 3D localization in autonomous driving.
 \end{abstract}

### 2015-11-05 CVPR16/Source/intro.tex
Update Intro

--- 2015-11-03 CVPR16/Source/intro.tex
@@
 \section{Introduction}
-The problem of segmenting points to objects often comes up in different
-computer vision problems especially in multi-body 
-reconstruction and localization. Given correspondence points on
-consecutive frames, the problem becomes one of finding out which points belong
-to which object following which one can use the consensus of segmented points
-to reconstruct or localize the object more accurately. Without additional 
-information this is very difficult problem as attempted by semantic segmentation 
-and motion segmentation methods. However, in the problems like reconstruction and
-localization on can use the hypothesis of the algorithm as the feedback.
+
+A fundamental problem in computer vision is to separate feature points of multiple objects which are tracked through a video sequence.
+The assignments of point tracks to objects can serve as an important preprocessing step for different applications such as 3D localization and reconstruction, where the point tracks associated with an individual object can be used to localize or reconstruct the object in 3D space accurately.
+In this paper, we focus on road scenes in autonomous driving applications which often include dynamic and static objects simultaneously.
+For example, some cars are parked near the curb while other cars are moving on the street.
+
+Motion segmentation approaches usually rely on object motions for clustering point tracks.
+Since point tracks of the same object possess similar motion patterns, these methods generally produce accurate point-to-object associations for dynamic objects.
+However, when there are static objects in the scene, their corresponding point tracks are often clustered together, which decreases the performances significantly and makes motion segmentation approaches unsuitable for road scenes with combinations of dynamic and static objects.
+Moreover, object occlusions are frequently involved in road scenes, where cars are relatively close to each other and move in the same directions, which makes the problem of point-to-object association for road scene understanding become more challenging.
+
+In this work, we first propose to represent objects as 3D ellipsoids.
+Motivated by image formulation theory in computer graphics, we then develop novel \emph{transmission} and \emph{reflection} models, which can explicitly reason about object occlusions.
+Leveraging on the success of object detection and tracking algorithms, we assume that detection bounding boxes and object tracklets are provided, thus we concentrate on segmenting point tracks that are only computed within object tracklets, which often contain both dynamic and static point tracks.
+As we will show later, the proposed method outperforms the baseline method which merely uses detection bounding boxes for resolving occlusions.
+Furthermore, our method is not based on object motions and hence does not suffer from static objects as other state-of-the-art methods for motion segmentation.
+
+%The problem of segmenting points to objects often comes up in different computer vision problems especially in multi-body reconstruction and localization.
+Given correspondence points on consecutive frames, the problem becomes one of finding out which points belong to which object, following which one can use the consensus of segmented points to reconstruct or localize the object more accurately.
+Without additional information, this is a very difficult problem as attempted by semantic segmentation and motion segmentation methods.
+However, in the problems like reconstruction and localization one can use the hypothesis of the algorithm as the feedback.
 % What is the problem we are trying to solve, and why is it even important?
 
-% What did we do
-We propose a model for representation of objects in the scene so that points
-can be probabilistically  associated to the tracklets while accounting for occlusion.
+% What did we do We propose a novel model for representation of objects in the scene so that point tracks can be probabilistically associated with objects while accounting for object occlusions.
 % Why is it novel
-Although our proposed modeling is inspired by Milan et
-al.\cite{Milan_etal_2014}, it is more detailed and more principled than their
-work. Milan et al. used soft ellipses and sigmoids to model pedestrians and
-their occlusion. We instead reason in 3D and use ellipsoids to model objects
-and reason about occupancy of the space to model occlusion.
+
+%Although our proposed model is inspired by Milan et al.\cite{Milan_etal_2014}, it is more detailed and more principled than their work.
+Milan et al.
+used soft ellipses and sigmoids to model pedestrians and their occlusions.
+Our reasoning is instead in 3D.
+We use ellipsoids to model objects and reason about their occupancies of the space to model their occlusions.
 % Ok you proposed a model is it of any use
 % How does it compare to state of art
-We employ our model in the context of autonomous for problem of localization of
-cars in the road scene. We show that associate points to objects more
-accurately than other methods like bounding box based association, Brox and
-Malik's\cite{Brox_Malik_2010} segmentation method and Robust Algebraic
-Segmentation (RAS)\cite{Rao_etal_2010}.
+% We show that our continuous occlusion model achieves significantly lower point-to-object association errors compared to the baseline method using detection bounding boxes and other state-of-the-art methods for motion segmentation~\cite{Brox_Malik_2010, Rao_etal_2010}.
+As a consequence, our model benefits the task of 3D localization of traffic participants in autonomous driving.

### 2015-11-05 CVPR16/Source/abstract.tex
Update Intro

@@
 We propose a novel continuous model for representing objects so that point tracks can be probabilistically and accurately assigned to the corresponding object while accounting for object occlusions.
-Detailed experiments on the KITTI dataset show the superiority of the propose method over the baseline method which simply uses detection bounding boxes for resolving occlusions and other state-of-the-art motion segmentation methods which cannot cope well with static objects.
+Detailed experiments on the KITTI dataset show the superiority of the proposed method over the baseline method which simply uses detection bounding boxes for resolving occlusions and other state-of-the-art motion segmentation methods which cannot cope well with static objects.
 As a notable application, we show how our continuous occlusion model benefits the task of 3D localization in autonomous driving.

### 2015-11-05 CVPR16/Source/intro.tex
Update Intro

@@
 
-In this work, we first propose to represent objects as 3D ellipsoids.
-Motivated by image formulation theory in computer graphics, we then develop novel \emph{transmission} and \emph{reflection} models, which can explicitly reason about object occlusions.
-Leveraging on the success of object detection and tracking algorithms, we assume that detection bounding boxes and object tracklets are provided, thus we concentrate on segmenting point tracks that are only computed within object tracklets, which often contain both dynamic and static point tracks.
-As we will show later, the proposed method outperforms the baseline method which merely uses detection bounding boxes for resolving occlusions.
+In this work, we first propose to model objects as 3D ellipsoids.
+Motivated by image formulation theory in computer graphics, we then develop novel continuous models for representing \emph{transmission} and \emph{reflection} probabilities, which can explicitly explain image observations and reason about object occlusions.
+Leveraging on the success of object detection and tracking algorithms, we assume that detection bounding boxes and object tracklets are provided, thus we concentrate on segmenting point tracks that are computed only within object tracklets.
+As we will show in the experiments, the proposed continuous occlusion modelling method outperforms the baseline method which merely uses bounding boxes for resolving occlusions.
 Furthermore, our method is not based on object motions and hence does not suffer from static objects as other state-of-the-art methods for motion segmentation.
+
+As an important contribution, we examine the applicability of the proposed model for 3D localization in autonomous driving.
+In contrast to the bounding box baseline method, which uses hard assignments of point tracks to objects (i.e., {0,1} probabilities), our continuous occlusion modelling method employs soft assignments (i.e., [0,1] probabilities).
+Consequently, it offers a unified continuous occlusion modelling for both point track and bounding box energies, which allows the use of effective optimization tools.
+As we will show later, the proposed model benefits the task of 3D localization in autonomous driving in terms of lower translation and dimension errors.
+
+The rest of the paper is organized as follows: Section~\ref{sec:related} discusses related work.
+Section~\ref{sec:setup} describes our continuous occlusion model for road scene understanding.
+Section~\ref{sec:experiments} presents experimental results for point-to-object association and 3D localization.
+Finally, we conclude in Section~\ref{}.
 

### 2015-11-05 CVPR16/Source/intro.tex
Finish Intro

@@
 
-Motion segmentation approaches usually rely on object motions for clustering point tracks.
-Since point tracks of the same object possess similar motion patterns, these methods generally produce accurate point-to-object associations for dynamic objects.
+Motion segmentation approaches~\cite{Rao_etal_2010,Brox_Malik_2010} usually rely on object motions for clustering point tracks.
+Since point tracks of the same object possess similar motion patterns, these methods generally produce accurate point-to-object associations for dynamic objects~\cite{Tron_Vidal_2007}.
 However, when there are static objects in the scene, their corresponding point tracks are often clustered together, which decreases the performances significantly and makes motion segmentation approaches unsuitable for road scenes with combinations of dynamic and static objects.
@@
 Motivated by image formulation theory in computer graphics, we then develop novel continuous models for representing \emph{transmission} and \emph{reflection} probabilities, which can explicitly explain image observations and reason about object occlusions.
-Leveraging on the success of object detection and tracking algorithms, we assume that detection bounding boxes and object tracklets are provided, thus we concentrate on segmenting point tracks that are computed only within object tracklets.
+Leveraging on the success of object detection and tracking algorithms~\cite{Felzenszwalb_etal_2010,Choi_Savarese_2010}, we assume that detection bounding boxes and object tracklets are provided, thus we concentrate on segmenting point tracks that are computed only within object tracklets~\cite{Zach2007}.
 As we will show in the experiments, the proposed continuous occlusion modelling method outperforms the baseline method which merely uses bounding boxes for resolving occlusions.
-Furthermore, our method is not based on object motions and hence does not suffer from static objects as other state-of-the-art methods for motion segmentation.
+Furthermore, our method is not based on object motions and hence does not suffer from static objects as other state-of-the-art motion segmentation methods~\cite{Rao_etal_2010,Brox_Malik_2010}.
 
 As an important contribution, we examine the applicability of the proposed model for 3D localization in autonomous driving.
-In contrast to the bounding box baseline method, which uses hard assignments of point tracks to objects (i.e., {0,1} probabilities), our continuous occlusion modelling method employs soft assignments (i.e., [0,1] probabilities).
+In contrast to the bounding box baseline method, which uses hard assignments of point tracks to objects (i.e., $\{0,1\}$ probabilities), our continuous occlusion modelling method employs soft assignments (i.e., [$0,1$] probabilities).
 Consequently, it offers a unified continuous occlusion modelling for both point track and bounding box energies, which allows the use of effective optimization tools.
-As we will show later, the proposed model benefits the task of 3D localization in autonomous driving in terms of lower translation and dimension errors.
+As we will show later, the proposed model benefits the task of 3D localization in autonomous driving in terms of lower translation and dimension errors compared to those of the baseline method~\cite{Song_Chandraker_2014} which employs the bounding box baseline method for point-to-object association.
 
 The rest of the paper is organized as follows: Section~\ref{sec:related} discusses related work.
-Section~\ref{sec:setup} describes our continuous occlusion model for road scene understanding.
-Section~\ref{sec:experiments} presents experimental results for point-to-object association and 3D localization.
+Section~\ref{sec:setup} describes the proposed continuous occlusion model for road scene understanding.
+Section~\ref{sec:experiments} presents detailed experiments for point-to-object association and 3D localization.
 Finally, we conclude in Section~\ref{}.

### 2015-11-05 CVPR16/Source/intro.tex
Finish Intro

@@
 Leveraging on the success of object detection and tracking algorithms~\cite{Felzenszwalb_etal_2010,Choi_Savarese_2010}, we assume that detection bounding boxes and object tracklets are provided, thus we concentrate on segmenting point tracks that are computed only within object tracklets~\cite{Zach2007}.
-As we will show in the experiments, the proposed continuous occlusion modelling method outperforms the baseline method which merely uses bounding boxes for resolving occlusions.
+As we will show later, the proposed continuous occlusion modelling method outperforms the baseline method which merely uses bounding boxes for tackling occlusions.
 Furthermore, our method is not based on object motions and hence does not suffer from static objects as other state-of-the-art motion segmentation methods~\cite{Rao_etal_2010,Brox_Malik_2010}.
@@
 Consequently, it offers a unified continuous occlusion modelling for both point track and bounding box energies, which allows the use of effective optimization tools.
-As we will show later, the proposed model benefits the task of 3D localization in autonomous driving in terms of lower translation and dimension errors compared to those of the baseline method~\cite{Song_Chandraker_2014} which employs the bounding box baseline method for point-to-object association.
+As we will show in the experiments, the proposed model benefits the task of 3D localization in autonomous driving in terms of lower translation and dimension errors compared to those of~\cite{Song_Chandraker_2014} which employs bounding boxes for point-to-object assignments.
 

### 2015-11-05 CVPR16/Source/applications.tex
Reorganize Section 4

--- 2015-11-04 CVPR16/Source/experiments.tex
@@
-\section{Experimental results}
-\label{sec:experiments}
+\section{Unified Occlusion Models}
+%\section{Occlusion-Aware Association and Localization}
 
-In this section, we first benchmark our continuous occlusion model for point-to-object association against the baseline method using detection bounding boxes and state-of-the-art methods for motion segmentation.
-We then show how the proposed model benefits the task of 3D localization in autonomous driving.
-For our experiments, we use the KITTI dataset~\cite{geiger2013vision}, which consists of video sequences of road scenes under a variety of driving conditions including highways and residential areas.
-It also provides ground truth data for different tasks such as segmentation, detection, tracking and 3D localization.
+In this section, we highlight the versatility of our occlusion modeling by demonstrating its unified application to two different problems: associating point tracks with objects and 3D object localization using object and point tracks.
 
-%\paragraph{Dataset} We use KITTI dataset for our experiments.
-\cite{geiger2013vision}.
-KITTI dataset is a labeled video sequence of road scenes under variety of driving conditions including highways and residential areas in Karlsruhe, Germany.
-It provides manually labelled ground truth data for localization of cars and also uses velodyne data provide metrically accurate estimates of cars location.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Association experiment}
-
-We first perform the association experiment that compares the accuracy of point-to-object association using the proposed model against those of the detection bounding box baseline method (BBox) and state-of-the-art motion segmentation methods, namely robust algebraic segmentation with hybrid perspective constraints (RAS)~\cite{Rao_etal_2010} and spectral clustering with point track spatial affinity (BM)~\cite{Brox_Malik_2010}.
-
-%To verify the correctness of our association probability $\assocP$ we perform association error experiment that compare the accuracy of point track association with TPs with that of bounding box baseline method.
-
-\subsubsection{Association probability}
-
-Based on our continuous occlusion model in Section~\ref{sec:setup}, the association probability $\assocP$ of $j$\textsuperscript{th} point track with $i$\textsuperscript{th} object at depth $\lambda$ can be defined as
+\subsection{Object-Point Association}
+Based on our continuous occlusion model in Section~\ref{sec:setup}, the association probability $\assocP$ of the $j$\textsuperscript{th} point track with $i$\textsuperscript{th} object at depth $\lambda$ can be defined as
 \begin{align}
@@
 Note that the fraction $\assocP$ although called association probability does not capture the entire information that we have available for computing association of point tracks to objects.
-This above fraction is the association probability given the hypothesized parameters of TPs in the scene.
+This above fraction is the association probability given the hypothesized parameters of objects in the scene.
 
-To compute the association probability $\assocP$ between point track $j$ and TP $i$ we must use the reprojection error as well.
+To compute the association probability $\assocP$ between point track $j$ and object $i$, we must use the reprojection error as well.
 When the association of $i$ and $j$ is correct and the point of reflection is at depth $\lambda$, the reprojection error must be zero \eqref{eq:reprojerror}, otherwise the error becomes a measure of distance from the true solution.
@@
 \end{align}
-
-Once we have the probability of association $P^{(ij)}_{\text{assoc}}$ we can compute the best possible assignment of TP for each point track.
+Once we have the probability of association $P^{(ij)}_{\text{assoc}}$ we can compute the best possible assignment of object for each point track.
 The points having very small association probability are assigned to the background,
 \begin{align}
-  i^*_{j} = \argmin_{i} \int_0^\infty \assocP \Ereproj(\lambda) d\lambda
+  i^*_{j} = \arg \min_{i} \int_0^\infty \assocP \Ereproj(\lambda) d\lambda
 \end{align}
 
-For the baseline method, the associations between point tracks and TPs are achieved by using detection bounding boxes, where point tracks within each bounding box are simply assigned to it.
+In contrast to the principled approach above, a heuristic baseline may simply assign a point to the detection bounding box enclosing it (and background if outside all bounding boxes).
+For regions where bounding boxes overlap, it may assign point tracks to the object that has smaller mean depth among the competing bounding boxes.
+As we will demonstrate in experiments, such heuristics are sub-optimal compared to using \eqref{eq:prob-assoc} inspired by our occlusion model.
+
+%For the baseline method, the associations between point tracks and TPs are achieved by using detection bounding boxes, where point tracks within each bounding box are simply assigned to it.
 For the regions where the bounding boxes overlap, we assign the point tracks to the TP that has smaller mean depth than the competing bounding boxes.
 
-\subsubsection{Association results}
-
-For each sequence of the KITTI dataset, the methods of \cite{Felzenszwalb_etal_2010} and \cite{Choi_Savarese_2010} are used respectively for computing detection bounding boxes and object tracklets.
-We then apply \cite{Zach2007} on object tracklets to extract point tracks.
-From these point tracks, we create four different sets of input point tracks, namely all point tracks, occluded point tracks, dynamic point tracks and dynamic and occluded point tracks, to examine various aspects of the methods (our method focuses on occlusion scenes while RAS and BM favour dynamic scenes).
-In addition to point tracks, the parameters of all TPs estimated by the method~\cite{Song_Chandraker_2014} are provided to our method (for computing association probability) and the baseline method (for depth ordering).
-
-Figure~\ref{fig:assoc-occ-results} shows the association errors --- the percentages of point tracks incorrectly assigned to objects --- of all methods on four sets of input point tracks for each sequence of the KITTI dataset, while the mean results over all sequences are presented in Table~\ref{tab:meanAssoc}.
-From Figure~\ref{fig:assoc-occ-results}, our method is usually the most accurate among all methods, leading to the best mean errors on all sets of input point tracks in Table~\ref{tab:meanAssoc}, which is followed by the bounding box baseline method.
-This clearly shows the advantage of our continuous occlusion model over the simple baseline method for resolving occlusions.
-RAS and BM often have the highest errors in Figure~\ref{fig:assoc-occ-results}, and hence the highest mean errors on all sets of input point tracks in Table~\ref{tab:meanAssoc}.
-
-More importantly, both RAS and BM rely on motions of objects for clustering point tracks, therefore they cannot work well with static point tracks (e.g., point tracks belong to parked cars).
-This fact can be observed in Table~\ref{tab:meanAssoc}, where there are large differences in the mean errors of both methods on data containing static point tracks (i.e., rows 2 and 4) and data consisting of dynamic point tracks only (i.e., rows 1 and 3).
-In contrast, our method and the baseline method are relatively independent of object motions, resulting in smaller performance gaps.
-
-\begin{figure*}
-\includegraphics[trim=1.0in 0.4in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
-  \caption{Association errors on different sets of input point tracks.
-Numbers on y-axis represent data sequence numbers in KITTI dataset.
-Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
-\label{fig:assoc-occ-results}
-\end{figure*}
-\begin{table}
-\begin{tabular}{lrrrr}
-  \toprule
-  & Ours & BBox & BM & RAS\\
-  \midrule
-  Dyn. and occ. tracks        & \textbf{13.2} & 21.3 & 30.9 & 30.1 \\
-  Occluded tracks             & \textbf{15.7} & 19.8 & 39.5 & 37.8 \\
-  Dynamic tracks              & \textbf{06.6} & 11.4 & 15.3 & 17.7 \\
-  All tracks                  & \textbf{08.6} & 12.6 & 21.9 & 21.5 \\
-  \bottomrule
-\end{tabular}
-\caption{Mean association errors on different sets of input point tracks over all sequences of KITTI dataset.
-Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
-\label{tab:meanAssoc}
-\end{table}
-
-\newlength{\tblimgwidth}
-\setlength{\tblimgwidth}{0.40\textwidth}
-\begin{table*}
-  \centering
-  \begin{tabular}{ccc}
-    & Associations & Error in association\\
-    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png} &%
-    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{2em} BM} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png} &%
-    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{2em} RAS} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_RAS-small.png} &%
-    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks-small.png} &%
-    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png} &%
-    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{2em} BM} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png} &%
-    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{2em} RAS} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_RAS-small.png} &%
-    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks-small.png} &%
-    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}
-  \end{tabular}
-  \caption{Qualitative results of the association experiment. The left column
-  shows the point track assignments to appropriate objects. Each color represents
-a different object to which point tracks can be associated to. Right column shows the
-probabilistic error in association: low error points are in blue while high error points are in red.
-Note that our method changes smoothly at the object boundaries with
-intermediate probabilities, while the baseline method has merely 0-1 error.} 
-\end{table*}
-
-\subsection{Localization experiment}
+\subsection{3D Object Localization}
 To show the effectiveness of our method we apply it to the localization
@@
 \end{figure}
-
-\begin{table}
-  \centering
-  \begin{tabular}{lrrr}
-    \toprule
-    Energy & t & yaw & dim \\
-    \midrule
-    initialization                                                                                  & 3.79 & \textbf{0.86} & 1.64 \\
-    %$\EnergyLane+\EnergySize+\EnergyBBox+\EnergyDyn                                       $ & 3.83 & 0.90 & \textbf{1.14} \\
-    %$\EnergyLane+\EnergySize+\EnergyBBoxocc+\EnergyDyn                                    $ & 3.83 & 0.90 & 1.14 \\
-    %$\EnergyLane+\EnergySize+\EnergyBBoxocc+\EnergyDyn+\EnergyCol                         $ & 3.92 & 0.91 & 1.15 \\
-    %$\EnergyLane+\EnergyContpttracks+\EnergySize+\EnergyBBoxocc+\EnergyDyn             $ & 3.81 & 0.92 & 1.59 \\
-    % \EnergyBBox+\EnergyDyn+\EnergyCol $
-    $\EnergyTrackNoOcc+\EnergyCol + \EnergyLane + \dots$  & 3.80 & 0.91 & 1.58 \\
-    $\EnergyTrack+\EnergyCol + \EnergyLane + \dots$ & \textbf{3.78} & 0.91 & 1.58 \\
-    \bottomrule
-  \end{tabular}
-  \caption{Localization experiment results with different combination of energies.
-We report error in three metrics translation error (t) in meters per car, yaw error (yaw) in radians per car and dimension error is again meters per car.}
-  \label{tab:localizationExperiment}
-\end{table}

### 2015-11-05 CVPR16/Source/experiments2.tex
Reorganize Section 4

--- 2015-11-04 CVPR16/Source/experiments.tex
@@
 %To verify the correctness of our association probability $\assocP$ we perform association error experiment that compare the accuracy of point track association with TPs with that of bounding box baseline method.
-
-\subsubsection{Association probability}
-
-Based on our continuous occlusion model in Section~\ref{sec:setup}, the association probability $\assocP$ of $j$\textsuperscript{th} point track with $i$\textsuperscript{th} object at depth $\lambda$ can be defined as
-\begin{align}
-  \assocP = \Prefl\Ptrans,
-\end{align}
-where $\Prefl$ and $\Ptrans$ are from \eqref{eq:evalPrefl} and \eqref{eq:evalCumulativePtrans} respectively.
-Note that the fraction $\assocP$ although called association probability does not capture the entire information that we have available for computing association of point tracks to objects.
-This above fraction is the association probability given the hypothesized parameters of TPs in the scene.
-
-To compute the association probability $\assocP$ between point track $j$ and TP $i$ we must use the reprojection error as well.
-When the association of $i$ and $j$ is correct and the point of reflection is at depth $\lambda$, the reprojection error must be zero \eqref{eq:reprojerror}, otherwise the error becomes a measure of distance from the true solution.
-The error term can be converted to probability domain by considering the error term as negative log of probability
-\begin{align}
-  P^{(ij)}_{\text{assoc by reproj}}(\lambda) = \frac{1}{Z}\exp(-\Ereproj(\lambda))
-\end{align}
-
-Using both of the above evidence terms we can write the probability of association $P^{(ij)}_{\text{assoc}}$ as follows
-\begin{align}
-  P^{(ij)}_{\text{assoc}} = \frac{1}{Z'}\int_0^{\infty} \assocP \exp(-\Ereproj(\lambda))d\lambda
-  \label{eq:prob-assoc}
-\end{align}
-
-Once we have the probability of association $P^{(ij)}_{\text{assoc}}$ we can compute the best possible assignment of TP for each point track.
-The points having very small association probability are assigned to the background,
-\begin{align}
-  i^*_{j} = \argmin_{i} \int_0^\infty \assocP \Ereproj(\lambda) d\lambda
-\end{align}
-
-For the baseline method, the associations between point tracks and TPs are achieved by using detection bounding boxes, where point tracks within each bounding box are simply assigned to it.
-For the regions where the bounding boxes overlap, we assign the point tracks to the TP that has smaller mean depth than the competing bounding boxes.
 
@@
 
-\subsection{Localization experiment}
-To show the effectiveness of our method we apply it to the localization
-problem. We estimate the position, orientation and dimensions of the car with
-our framework and compute the error in birds eye view domain along the ground
-plane. We report error in three metrics translation error (t) in meters per
-car, yaw error (yaw) in radians per car and dimension error is again meters per
-car. The results are shown in Table~\ref{tab:localizationExperiment}.
-
-We build the graphical model as shown in Fig~\ref{fig:graphmodel} that 
-allows us to factorize the intractable probability distribution into following form
-%
-\begin{multline}
-  -\log{P(\{\state{i}{t}\} | \mathbb{E})} = 
-  -Z' 
-  \\
-  + \sum_{t=s_i}^{e_i}
-  \left(
-  \sum_{i,j:i\ne j}   
-  \WEnergyCol 
-   + \WpEnergy{bbox}
-   + \WpEnergy{track}
-\right)
-  \\
-  + \left(
-  \sum_{i=1}^N 
-  \WEnergy{lane}
-  + \WEnergy{dyn}
-  + \WEnergy{size}
-\right)
-  \enspace.
-\end{multline}
-%
-Next, we explain the important energies used in our graphical model.
-
-\subsubsection{Continuous point tracks energy with occlusion}
-\label{sec:totalContPtTracksEnergy}
-We model continuous point tracks energy with explicit occlusion reasoning as
-the expected reprojection error over the association probability,
-
-\begin{multline}
-  \Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = 
-  \\
-    \sum_{i=1}^{N} 
-    %\sum_{t = s_i}^{e_i}
-    \sum_{j = 1}^{M}
-    \int_1^\infty \assocP\Ereproj(\lambda) d\lambda
-\end{multline}
-where $\assocP$ is the association probability of
-$j$\textsuperscript{th} point with $i$\textsuperscript{th} TP at depth $\lambda$, $\{ \relp{i}{t} \}_i$ are the poses of all occluding objects at time $t$, $ \{ \dimsn{i} \}_i$ are the dimensions of all objects that occlude $i$
-and $\Ereproj(\lambda)$ is the reprojection error given by
-%
-\begin{align}
-  \assocP &= \Prefl\Ptrans\\
-  \Ereproj(\lambda) &= \left\|\trackpj{t} - \projectionOf{\invProjectionOftm{\trackpj{t-1}, \lambda}}\right\|^2 .
-  \label{eq:reprojerror}
-\end{align}
-
-The  $\projectionOf{.}$ and $\invProjectionOftm{.}$ denote the projection and
-inverse projection functions that project 3D point to camera image and vice
-versa. Note that inverse projection $\invProjectionOf{.}$ depend on both the
-point $\trackp{t}$ and the unknown depth $\lambda$. Also note that the inverse projection is dependent on TP pose at time $t-1$ while the projection depends on pose at time $t$ which can be different.
-
-\subsubsection{Continuous bounding box energy with occlusion}
-
-Object detection is usually followed by non-maximal suppression that results in
-discarding similar bounding boxes. When we are jointly optimizing detections
-with other cues, it is not usually desirable to go with a single bounding box.
-Hence, we keep all the bounding box detections by approximating them with
-multi-modal sum of Gaussian like logistic functions. We fit the parametric function of the form 
-%
-\begin{multline}
-  S(\bb{i}) = \\
-  \sum_k A_k \exp(-(\bb{i}-\mu^{(d)}_k)^\top \Sigma^{(d)-1}_k
-  (\bb{i}-\mu^{(d)}_k))
-\end{multline}
-%
-to detection scores, by non-linear error minimization with initialization from
-non-maximal suppressed outputs. Here $\mu^{(d)}_j$ is one of the $k$ modes as a
-4D vector representing a single bounding box as $[\minx, \miny, \maxx,
-\maxy]^\top$. The optimization is constrained with symmetry and positive
-definiteness of $\Sigma^{(d)-1}_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
-
-\paragraph{Detection scores with occlusion reasoning} 
-\def\u{\mathbf{u}}
-With our model of $\Ptrans$ described in Section \ref{sec:ptransmission}, we can
-compute the probability of a point $\u$ on image be occluded assuming
-the point is on traffic participant (TP) $i$ with mean depth $\mu^{(i)}_d$ as
-\begin{align}
-  O_{i}(\u, \mu^{(i)}_d) = 1 - \Ptransmission(\mu^{(i)}_d\u) \enspace .
-\end{align}
-
-If we know a portion of our proposed detection bounding box is known to be
-occluded, then we would like to decrease the confidence in the detection score
-about the localization of that end of the object. Assuming that the occlusion
-is often on the boundary of detection bounding boxes, we want to decrease our
-confidence on the mean detection boundaries around the occluded boundaries.
-To re-model our detection scores scaled by continuous occlusion we sample
-$O_{i}(\mathbf{u}, \mu^{(i)}_d)$ at the hypothesized detection boundaries from
-GMM $S(.)$ and we augment the detection boundary covariance matrix by
-$\mathcal{P}_{j} = \rho_{j}\rho_{j}^\top$ where $\rho_{j} = O_{j}(\mathbf{u},
-\mu^{(i)}_d)$. The new covariance matrix in detection score is given by 
-  $\Sigma'^{(d)}_j = \mathcal{P}_{j} + \Sigma^{(d)}_j$.
-The detection scores GMM with occlusion is given by replacing the covariance
-matrix
-%
-\begin{multline}
-  S'(\bb{i}) =
-  \\
-  \sum_j A_j \exp(-(\bb{i}-\mu^{(d)}_j)^\top \Sigma'^{(d)-1}_j
-  (\bb{i}-\mu^{(d)}_j))
-\end{multline}
-
-The energy of detection scores is simply take to be the inverse of the detection score.
-\begin{align}
-  \Energy{detect}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}
-\end{align}
-
-For object detections we use object detector by \cite{Felzenszwalb_etal_2010}
-which is detector by parts model and we use eight parts to train the car model 
-on half of the KITTI dataset \cite{geiger2013vision}. The trained modeled is 
-used to get detections for the other half of the dataset and vice versa.
-
-\subsubsection{Other energies}
-Other energies we use are described in detail in the supplementary material. We briefly describe them here:
-\begin{description}
-  \item[Lane energy ($\Energy{lane}$)] This energy term constrains the
-    orientation of traffic participants to be parallel to the nearest detected
-    lane. The lanes are either detected visually or obtained from GPS and Map 
-    information.
-  \item[Transition probability ($\Energy{dyn}$)] We use these energies to
-    constrain the motion of cars to be smooth in linear motion and rotation
-    motion. We also constrain cars to move in the direction of heading.
-  \item[Size prior ($\EnergySize$)] We use size prior of cars by using the mean
-    of cars over the KITTI dataset.
-\end{description}
-
-\subsection{Metropolis Hastings Inference}
-We use Metropolis Hastings' methods for graphical model inference. Since we are
-optimizing over continuous random variables, we use Gaussian distribution as
-the proposal distribution.
-
-\begin{figure}
-  \centering
-  \newcommand{\imagewidth}{\columnwidth}
-  \input{Source/scenelayoutoverlayCity0961}
-  \caption{A sample road scene with the unknowns of each car modeled as random variables. 
-  The relating energies are shown in Figure~\ref{fig:graphmodel}}
-\end{figure}
-\begin{figure}
-    \input{Source/graphical_model_multiple}
-    \caption{Graphical model for a single frame with state of car represented
-    as single node.  The six numbered nodes represent the unknown state variables of each car. The shaded nodes in the graphical model are observed variables. }
-  \label{fig:graphmodel}
-\end{figure}
-
 \begin{table}

### 2015-11-05 CVPR16/Source/applications.tex
Reorganize Section 4

@@
 \assocP = \Prefl\Ptrans,
+\label{eq:defineassocP}
 \end{align}
@@
 \label{sec:totalContPtTracksEnergy}
-We model continuous point tracks energy with explicit occlusion reasoning as
-the expected reprojection error over the association probability,
 
+Let the pose of object $i$ at time $t$ be $\relp{i}{t}$.
+We denote $\projectionOf{.}$ and $\invProjectionOftm{.}$ for the projection and inverse projection functions that project a 3D point to the camera image and vice versa.
+Then, the reprojection error for the $j$\textsuperscript{th} 2D point, with hypothesized depth $\lambda$, is given by
+\begin{equation}
+\Ereproj(\lambda) = \left\|\trackpj{t} - \projectionOf{\invProjectionOftm{\trackpj{t-1}, \lambda}}\right\|^2.
+\label{eq:reprojerror}
+\end{equation}
+Note that inverse projection $\invProjectionOf{.}$ depends on both the 2D point $\trackp{t}$ and the unknown depth $\lambda$.
+Also note that the inverse projection is dependent on object pose at time $t-1$ while the forward projection depends on pose at time $t$ which can be different.
+
+For an object $i$, let $\{ \relp{i}{t} \}_i$ be the poses of all occluding objects at time $t$ and $ \{ \dimsn{i} \}_i$ be their dimensions.
+Then, we model the continuous point tracks energy with explicit occlusion reasoning as the expected reprojection error over the association probability:
 \begin{multline}
@@
 \end{multline}
-where $\assocP$ is the association probability of
-$j$\textsuperscript{th} point with $i$\textsuperscript{th} TP at depth $\lambda$, $\{ \relp{i}{t} \}_i$ are the poses of all occluding objects at time $t$, $ \{ \dimsn{i} \}_i$ are the dimensions of all objects that occlude $i$
-and $\Ereproj(\lambda)$ is the reprojection error given by
-%
-\begin{align}
-  \assocP &= \Prefl\Ptrans\\
-  \Ereproj(\lambda) &= \left\|\trackpj{t} - \projectionOf{\invProjectionOftm{\trackpj{t-1}, \lambda}}\right\|^2 .
-  \label{eq:reprojerror}
-\end{align}
+where $\assocP$ is the association probability of the $j$\textsuperscript{th} point with the $i$\textsuperscript{th} object at depth $\lambda$, given by \eqref{eq:defineassocP}.
 
-The  $\projectionOf{.}$ and $\invProjectionOftm{.}$ denote the projection and
-inverse projection functions that project 3D point to camera image and vice
-versa. Note that inverse projection $\invProjectionOf{.}$ depend on both the
-point $\trackp{t}$ and the unknown depth $\lambda$. Also note that the inverse projection is dependent on TP pose at time $t-1$ while the projection depends on pose at time $t$ which can be different.
+%\begin{align}
+%  \assocP &= \Prefl\Ptrans\\
+%  \Ereproj(\lambda) &= \left\|\trackpj{t} - \projectionOf{\invProjectionOftm{\trackpj{t-1}, \lambda}}\right\|^2 .
+%  \label{eq:reprojerror}
+%\end{align}
+
+%The $\projectionOf{.}$ and $\invProjectionOftm{.}$ denote the projection and inverse projection functions that project 3D point to camera image and vice versa.
+Note that inverse projection $\invProjectionOf{.}$ depend on both the point $\trackp{t}$ and the unknown depth $\lambda$.
+Also note that the inverse projection is dependent on TP pose at time $t-1$ while the projection depends on pose at time $t$ which can be different.
 

### 2015-11-05 CVPR16/Source/applications.tex

@@
 Let the pose of object $i$ at time $t$ be $\relp{i}{t}$.
-We denote $\projectionOf{.}$ and $\invProjectionOftm{.}$ for the projection and inverse projection functions that project a 3D point to the camera image and vice versa.
-Then, the reprojection error for the $j$\textsuperscript{th} 2D point, with hypothesized depth $\lambda$, is given by
+We denote $\projectionOf{.}$ and $\invProjectionOftm{.}$ for the forward and inverse projection functions that project a 3D point to the camera image and vice versa.
+Then, the reprojection error for the $j$\textsuperscript{th} 2D point, $\trackp{t}$, with hypothesized depth $\lambda$, is given by
 \begin{equation}
@@
 Note that inverse projection $\invProjectionOf{.}$ depends on both the 2D point $\trackp{t}$ and the unknown depth $\lambda$.
-Also note that the inverse projection is dependent on object pose at time $t-1$ while the forward projection depends on pose at time $t$ which can be different.
+Also note that the inverse projection is dependent on object pose at time $t-1$ while the forward projection depends on pose at time $t$, which can be different.
 
-For an object $i$, let $\{ \relp{i}{t} \}_i$ be the poses of all occluding objects at time $t$ and $ \{ \dimsn{i} \}_i$ be their dimensions.
+For an object $i$, let $\{ \Omega (t) \}_i$ be the poses of all occluding objects at time $t$ (inclusive of object $i$) and $ \{ \bB \}_i$ be their dimensions.
 Then, we model the continuous point tracks energy with explicit occlusion reasoning as the expected reprojection error over the association probability:
 \begin{multline}
-  \Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = 
+  %\!\!\!\! \Energy{track}(\relp{i}{t}, \relp{i}{t-1}, \dimsn{i}, \{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i ) 
+  %\Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = 
+  \Energy{track}(\{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i )
   \\
-    \sum_{i=1}^{N} 
+    = \sum_{i=1}^{N} 
     %\sum_{t = s_i}^{e_i}
@@
 
-Object detection is usually followed by non-maximal suppression that results in
-discarding similar bounding boxes. When we are jointly optimizing detections
-with other cues, it is not usually desirable to go with a single bounding box.
-Hence, we keep all the bounding box detections by approximating them with
-multi-modal sum of Gaussian like logistic functions. We fit the parametric function of the form 
-%
-\begin{multline}
-  S(\bb{i}) = \\
-  \sum_k A_k \exp(-(\bb{i}-\mu^{(d)}_k)^\top \Sigma^{(d)-1}_k
-  (\bb{i}-\mu^{(d)}_k))
-\end{multline}
-%
-to detection scores, by non-linear error minimization with initialization from
-non-maximal suppressed outputs. Here $\mu^{(d)}_j$ is one of the $k$ modes as a
-4D vector representing a single bounding box as $[\minx, \miny, \maxx,
-\maxy]^\top$. The optimization is constrained with symmetry and positive
-definiteness of $\Sigma^{(d)-1}_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
+Object detection is usually followed by non-maximal suppression that results in discarding similar bounding boxes.
+When we are jointly optimizing detections with other cues, it is not usually desirable to go with a single bounding box.
+To retain the entire detection output while maintaining the continuous form of our energies, we approximate the distribution of detection scores with a multi-modal sum of Gaussians-like logistic functions.
+In particular, let $\bb{i}$ be a detection bounding box for object $i$, parameterized as a 4D vector $[\minx, \miny, \maxx, \maxy]^\top$.
+We fit a parametric function to the detection scores, of the form
+\begin{equation}
+S(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{(i)}(t)^\top \Lambda_k^{-1} \bepsilon_k^{(i)}(t) \right)
+\end{equation}
+where $A_k$ is an amplitude and $\bepsilon_k^{(i)}(t) = \bb{i}-\mu^{(k)}_d$, with $\mu^{(k)}_d$ the mean and $\Lambda_k$ the covariance.
+%% %
+%% \begin{multline}
+%%   S(\bb{i}) = \\
+%%   \sum_k A_k \exp(-(\bb{i}-\mu^{(d)}_k)^\top \Sigma^{(d)-1}_k
+%%   (\bb{i}-\mu^{(d)}_k))
+%% \end{multline}
+%% %
+%% to detection scores, by 
+We use a non-linear solver to minimize the above, with initialization from non-maximal suppressed outputs.
+The optimization is constrained by the symmetry and positive definiteness of $\Lambda_k^{-1}$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
+%Here $\mu^{(d)}_j$ is one of the $k$ modes as a 4D vector representing a single bounding box as $[\minx, \miny, \maxx, \maxy]^\top$.
+The optimization is constrained with symmetry and positive definiteness of $\Sigma^{(d)-1}_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
 
@@
 With our model of $\Ptrans$ described in Section \ref{sec:ptransmission}, we can
-compute the probability of a point $\u$ on image be occluded assuming
-the point is on traffic participant (TP) $i$ with mean depth $\mu^{(i)}_d$ as
+compute the probability of a point $\u$ in the image to be occluded assuming
+the point is on object $i$ with mean depth $\mu^{(i)}_d$ as
 \begin{align}
@@
 
-If we know a portion of our proposed detection bounding box is known to be
+If a portion of our proposed detection bounding box is known to be
 occluded, then we would like to decrease the confidence in the detection score

### 2015-11-05 CVPR16/Source/intro.tex

@@
 Motivated by image formulation theory in computer graphics, we then develop novel continuous models for representing \emph{transmission} and \emph{reflection} probabilities, which can explicitly explain image observations and reason about object occlusions.
-Leveraging on the success of object detection and tracking algorithms~\cite{Felzenszwalb_etal_2010,Choi_Savarese_2010}, we assume that detection bounding boxes and object tracklets are provided, thus we concentrate on segmenting point tracks that are computed only within object tracklets~\cite{Zach2007}.
-As we will show later, the proposed continuous occlusion modelling method outperforms the baseline method which merely uses bounding boxes for tackling occlusions.
+Leveraging on the success of object detection and tracking algorithms~\cite{Felzenszwalb_etal_2010,Choi_Savarese_2010}, we assume that detection bounding boxes and object tracklets are provided, thus we concentrate on segmenting point tracks that are computed only within object tracklets~\cite{Zach2007}, including both dynamic and static point tracks.
+As we will show in the experiments, the proposed continuous occlusion modelling method outperforms the baseline method which merely uses bounding boxes for dealing with occlusions.
 Furthermore, our method is not based on object motions and hence does not suffer from static objects as other state-of-the-art motion segmentation methods~\cite{Rao_etal_2010,Brox_Malik_2010}.
 
-As an important contribution, we examine the applicability of the proposed model for 3D localization in autonomous driving.
+As another important contribution, we examine the applicability of the proposed model for 3D localization in autonomous driving.
 In contrast to the bounding box baseline method, which uses hard assignments of point tracks to objects (i.e., $\{0,1\}$ probabilities), our continuous occlusion modelling method employs soft assignments (i.e., [$0,1$] probabilities).
-Consequently, it offers a unified continuous occlusion modelling for both point track and bounding box energies, which allows the use of effective optimization tools.
-As we will show in the experiments, the proposed model benefits the task of 3D localization in autonomous driving in terms of lower translation and dimension errors compared to those of~\cite{Song_Chandraker_2014} which employs bounding boxes for point-to-object assignments.
+Consequently, it offers a \emph{unified} continuous occlusion modelling for both point track and bounding box energies, which allows the use of effective continuous optimization tools.
+As we will show later, the proposed model benefits the task of 3D localization in autonomous driving in terms of lower translation and dimension errors compared to those of~\cite{Song_Chandraker_2014}, which employs bounding boxes for point-to-object associations.
 

### 2015-11-05 CVPR16/Source/related.tex

@@
 \section{Related Work}
-\paragraph{Occlusion handling in tracking}
-Occlusions have also been handled in tracking-by-detection frameworks by considering occluder patterns in the image \cite{Kwak_etal_2012,Wu_Nevatia_2007}.
+\label{sec:related}
+
+%An application for our occlusion modeling is to determine point track associations in scenes with multiple objects.
+For moving objects, this is within the purview of motion segmentation, which has been actively studied \cite{Tron_Vidal_2007,Rao_etal_2010}.
+This also motivates further applications such as object segmentation based on point trajectories \cite{Brox_Malik_2010}.
+Motion segmentation is also used within multibody structure from motion (SFM) frameworks \cite{Ozden_etal_2010,Kundu_etal_2011,Namdev2012}.
+In contrast to these works, our formulation does not distinguish between moving and static objects and also explicitly reasons about occlusions due to 3D object geometries for associating point tracks to individual objects.
+
+\paragraph{Motion segmentation}
+Motion segmentation has actively been studied in the literature.
+Previous work can roughly be categorized into algebraic methods~\cite{}, statistical methods~\cite{} and clustering methods~\cite{}.
+Some recent efforts include robust algebraic segmentation with hybrid perspective constraints~\cite{} and spectral clustering with point track spatial affinity~\cite{}.
+The above methods usually exploit the fact that point tracks of a particular moving object tend to follow similar motion patterns.
+Therefore, they cannot segment static objects due to no motion cues.
+In contrast, our method is relatively independent of object motions and hence does not suffer from static objects.
+
+\paragraph{Occlusion handling}
+Occlusion handling plays an important role in many computer vision applications such as object detection and tracking.
+Methods that are capable of detecting occluded objects include~\cite{}, which trains different object part detectors, and~\cite{}, which learns 3D cues from a CAD database.
+These methods are either based on 2D cues~\cite{} or often a discrete representation of occlusion behavior~\cite{}.
+In contrast, our occlusion model is fully 3D and allows for a continuous representation.
+For object tracking, occlusions are often handled by a set of occluder patterns~\cite{}.
+A notable exception is~\cite{}, which explicitly models object occlusions in continuous domain to determine the visibility of each object.
+...
+
+%Occlusions have also been handled in tracking-by-detection frameworks by considering occluder patterns in the image \cite{Kwak_etal_2012,Wu_Nevatia_2007}.
 A notable exception is the work of Milan et al.~\cite{Milan_etal_2014} that explicits models occlusion in the continuous domain to determine a visibility for each object in multi-target tracking.
@@
 
-\paragraph{3D localization and scene understanding}
+\paragraph{3D localization}
 One of the central goals of 3D scene understanding is to localize the 3D positions and orientations of objects in complex scenes.
@@
 In contrast to these works, our monocular framework uses a physical modeling of occlusion in continuous space, which makes it more general, extensible and amenable for continuous optimization.
-
-\paragraph{Motion segmentation and multibody SFM}
-An application for our occlusion modeling is to determine point track associations in scenes with multiple objects.
-For moving objects, this is within the purview of motion segmentation, which has been actively studied \cite{Tron_Vidal_2007,Rao_etal_2010}.
-This also motivates further applications such as object segmentation based on point trajectories \cite{Brox_Malik_2010}.
-Motion segmentation is also used within multibody structure from motion (SFM) frameworks \cite{Ozden_etal_2010,Kundu_etal_2011,Namdev2012}.
-In contrast to these works, our formulation does not distinguish between moving and static objects and also explicitly reasons about occlusions due to 3D object geometries for associating point tracks to individual objects.

### 2015-11-05 CVPR16/Source/applications.tex
Moving some content from experiments.tex to application.tex and experiments2.tex

@@
 our framework and compute the error in birds eye view domain along the ground
-plane. We report error in three metrics translation error (t) in meters per
-car, yaw error (yaw) in radians per car and dimension error is again meters per
-car. The results are shown in Table~\ref{tab:localizationExperiment}.
-
+plane. 
+To estimate the localization of traffic participants (TPs) in a road scene we follow the graphical model approach.
 We build the graphical model as shown in Fig~\ref{fig:graphmodel} that 
@@
 optimizing over continuous random variables, we use Gaussian distribution as
-the proposal distribution.
+the proposal distribution. We choose Metropolis Hastings inference over
+block-coordinate descent which turns out to be slower than Metropolis Hastings
+in our experiments. Please refer to our supplementary material for the comparison
+of inference methods.
 

### 2015-11-05 CVPR16/Source/experiments.tex
Moving some content from experiments.tex to application.tex and experiments2.tex

@@
 
+To estimate the localization of traffic participants (TPs) in a road scene we follow the graphical model approach.
 We build the graphical model as shown in Fig~\ref{fig:graphmodel} that 
@@
 %
-Next, we explain the important energies used in our graphical model.
+Next, we explain the formulation of important energies used in our graphical
+model.
 
@@
 occluded, then we would like to decrease the confidence in the detection score
-about the localization of that end of the object. Assuming that the occlusion
+about the localization of that end of the object. Assuming that the occlusion of interest
 is often on the boundary of detection bounding boxes, we want to decrease our
@@
 optimizing over continuous random variables, we use Gaussian distribution as
-the proposal distribution.
+the proposal distribution. We choose Metropolis Hastings inference over
+block-coordinate descent which turns out to be slower than Metropolis Hastings
+in our experiments. Please refer to our supplementary material for the comparison
+of inference methods.
+
+\subsection{Observations}
+The results from our localization experiments are shown in Table~\ref{tab:localizationExperiment}. We compare four combinations of energies as shown in the table.
+The energy $\EnergyTrackNoOcc$ represents the point tracks energy modeled with 
+accounting for occlusion, i.e., we remove the term $\Ptransmission$ and model
+$\EnergyTrack$ in the absence of $\Ptransmission$. Similarly, $\EnergyBBoxNoOcc$ is the energy without the modification of $\bSigma$ that accounts for occlusion.
+The results show that use of continuous occlusion model 
+improves the localization accuracy in terms of all three metrics: translation,
+yaw and dimension error.
 

### 2015-11-05 CVPR16/Source/experiments2.tex
Moving some content from experiments.tex to application.tex and experiments2.tex

@@
 \end{table}
+
+\subsection{Localization Experiment and Results}
+We report error in three metrics translation error (t) in meters per car, yaw
+error (yaw) in radians per car and dimension error is again meters per car. The
+results are shown in Table~\ref{tab:localizationExperiment}.  We compare four
+combinations of energies as shown in the table.  The energy $\EnergyTrackNoOcc$
+represents the point tracks energy modeled with accounting for occlusion, i.e.,
+we remove the term $\Ptransmission$ and model $\EnergyTrack$ in the absence of
+$\Ptransmission$. Similarly, $\EnergyBBoxNoOcc$ is the energy without the
+modification of $\bSigma$ that accounts for occlusion.  The results show that
+use of continuous occlusion model improves the localization accuracy in terms
+of all three metrics: translation, yaw and dimension error.

### 2015-11-05 CVPR16/Source/abstract.tex
Added more comments about the experiments.

--- 2015-11-05 CVPR16/Source/abstract.tex
@@
 \begin{abstract}
-This paper studies the problem of segmenting tracked feature points of multiple objects in a video sequence.
+This paper studies the problem of segmenting tracked feature points on multiple objects in a video sequence.
 We consider scenes that contain both dynamic and static objects, which usually appear in the context of autonomous driving (e.g., moving and parked cars), and occlusions among objects.
-We propose a novel continuous model for representing objects so that point tracks can be probabilistically and accurately assigned to the corresponding object while accounting for object occlusions.
-Detailed experiments on the KITTI dataset show the superiority of the propose method over the baseline method which simply uses detection bounding boxes for resolving occlusions and other state-of-the-art motion segmentation methods which cannot cope well with static objects.
+We propose a novel continuous model for modeling objects so that point tracks can be probabilistically and accurately assigned to the corresponding object while accounting for object occlusions.
+Detailed experiments on the KITTI dataset show the superiority of the proposed method over the baseline method which simply uses detection bounding boxes for resolving occlusions and the state-of-the-art motion segmentation methods which cannot cope well with static objects.
 As a notable application, we show how our continuous occlusion model benefits the task of 3D localization in autonomous driving.

### 2015-11-05 CVPR16/Source/applications.tex
Added more comments about the experiments.

@@
 plane. 
-To estimate the localization of traffic participants (TPs) in a road scene we follow the graphical model approach.
+To estimate the localization of traffic participants (TPs) in a road scene we use the graphical model approach.
 We build the graphical model as shown in Fig~\ref{fig:graphmodel} that 
@@
 \subsection{Metropolis Hastings Inference}
-We use Metropolis Hastings' methods for graphical model inference. Since we are
+We use Metropolis Hastings' methods \cite{mackay1998introduction} for graphical model inference. Since we are
 optimizing over continuous random variables, we use Gaussian distribution as
@@
 block-coordinate descent which turns out to be slower than Metropolis Hastings
-in our experiments. Please refer to our supplementary material for the comparison
-of inference methods.
+in our experiments. Please refer to the supplementary material for the
+comparison of inference methods.
 

### 2015-11-05 CVPR16/Source/discussions.tex
Added more comments about the experiments.

\section{Discussion and Future Work}
\label{sec:conclusions}

Our experiments shows that our association probability produces more accurate
point to object associations when compared to bounding box based
association and state of art motion segmentation.
Also the localization experiment results show improvement by modeling occlusions, however, the average translation error of 5 meters is very high. Since the results are averaged over the entire KITTI dataset, there are various possible sources of error, including outliers in point tracks, outliers in detections results. 
One of the reasons of poor performance is that we set the parameters $\lambda_{\text{bbox,track,lane,dyn,size}}$ empirically which may be suboptimal. However, because of slow inference algorithms, which take about a day to run on 300 cores for the entire KITTI dataset, learning become infeasible.

We have several ideas for speeding up inference and thereby allowing learning
of weights to become feasible. One of them is to approximate the graph into a
tree using Chow-Liu's \cite{chow1968approximating} algorithm and then using
Belief Propagation which is linear in the number of edges of the tree.

### 2015-11-05 CVPR16/Source/related.tex
Added more comments about the experiments.

@@
 Previous work can roughly be categorized into algebraic methods~\cite{}, statistical methods~\cite{} and clustering methods~\cite{}.
-Some recent efforts include robust algebraic segmentation with hybrid perspective constraints~\cite{} and spectral clustering with point track spatial affinity~\cite{}.
+Some recent efforts include robust algebraic segmentation with hybrid perspective constraints~\cite{Rao_etal_2010} and spectral clustering with point track spatial affinity~\cite{Brox_Malik_2010}.
 The above methods usually exploit the fact that point tracks of a particular moving object tend to follow similar motion patterns.

### 2015-11-05 CVPR16/Source/applications.tex
Making notation more consistent.

@@
 \begin{equation}
-S(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{(i)}(t)^\top \Lambda_k^{-1} \bepsilon_k^{(i)}(t) \right)
+S(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{(i)}(t)^\top \Lambda_k^{'-1} \bepsilon_k^{(i)}(t) \right)
 \end{equation}
@@
 compute the probability of a point $\u$ in the image to be occluded assuming
-the point is on object $i$ with mean depth $\mu^{(i)}_d$ as
+the point is on object $i$ with mean depth $\meandepth{i}$ as
 \begin{align}
-  O_{i}(\u, \mu^{(i)}_d) = 1 - \Ptransmission(\mu^{(i)}_d\u) \enspace .
+  O_{i}(\u, \meandepth{i}) = 1 - \Ptransmission(\meandepth{i}, \u) \enspace .
 \end{align}
@@
 To re-model our detection scores scaled by continuous occlusion we sample
-$O_{i}(\mathbf{u}, \mu^{(i)}_d)$ at the hypothesized detection boundaries from
+$O_{i}(\mathbf{u}, \meandepth{i})$ at the hypothesized detection boundaries from
 GMM $S(.)$ and we augment the detection boundary covariance matrix by
-$\mathcal{P}_{j} = \rho_{j}\rho_{j}^\top$ where $\rho_{j} = O_{j}(\mathbf{u},
-\mu^{(i)}_d)$. The new covariance matrix in detection score is given by 
-  $\Sigma'^{(d)}_j = \mathcal{P}_{j} + \Sigma^{(d)}_j$.
+$\mathcal{P}_{i} = \rho_{i}\rho_{i}^\top$ where $\rho_{i} = O_{i}(\mathbf{u},
+\meandepth{i})$. The new covariance matrix in detection score is given by 
+  $\Lambda'_k = \mathcal{P}_{i} + \Lambda_k$ for all $k$.
 The detection scores GMM with occlusion is given by replacing the covariance
@@
 \begin{multline}
-  S'(\bb{i}) =
-  \\
-  \sum_j A_j \exp(-(\bb{i}-\mu^{(d)}_j)^\top \Sigma'^{(d)-1}_j
-  (\bb{i}-\mu^{(d)}_j))
+S'(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{(i)}(t)^\top \Lambda_k^{'-1} \bepsilon_k^{(i)}(t) \right)
 \end{multline}

### 2015-11-05 CVPR16/Source/occlusion.tex
Making notation more consistent.

@@
 \begin{align}
-  \Ptransmission^j(\lambda) = \prod_i (1 - \cL_u (\bu; \bmu_i, \bGamma_i^{-1}) \cL_{\lambda}(\lambda; \nu_i)),
+  \Ptransmission^j(\lambda) = \prod_i (1 - \cL_u (\bu; \bmu_i, \bGamma_i^{-1}) \cL_{\lambda}(\lambda; \meandepth{i})),
 \label{eq:evalCumulativePtrans}
@@
 %
-where $\cL_u(.)$ is sigmoid in image domain, with $\bmu^i_u$ and $\bGamma_i$ representing the elliptical projection of object $O_i$ in the image and $\cL_{\lambda}(.)$ is sigmoid in the depth domain with $\nu_i$ the mean depth of object $O_i$.
+where $\cL_u(.)$ is sigmoid in image domain, with $\bmu^i_u$ and $\bGamma_i$ representing the elliptical projection of object $O_i$ in the image and $\cL_{\lambda}(.)$ is sigmoid in the depth domain with $\meandepth{i}$ the mean depth of object $O_i$.
 That is,
@@
 \cL_u(\bu; \bmu_i, \bGamma_i^{-1}) &= \frac{1}{1 + e^{-k_u(1 - (\bu - \bmu_i)^\top \bGamma_i^{-1} (\bu - \bmu_i))}} \\
-\cL_{\lambda}(\lambda; \nu_i) &= \frac{1}{1 + e^{-k_d(\lambda - \nu_i)}}
+  \cL_{\lambda}(\lambda; \meandepth{i}) &= \frac{1}{1 + e^{-k_d(\lambda - \meandepth{i})}}
 \end{align}

### 2015-11-05 CVPR16/supplementarymaterial.tex
Renaming bbox -> detect. Adding supplementary material.

--- 2015-09-28 Paper/supplementarymaterial.tex
@@
-\section{Analytic initialization}
-Problem: given detection bounding box and ground plane estimate the unknown parameters i.e.
-position, orientation and size of the car.
-This problem is under-determined.
-Given the bounding box, we just have four constraints while we have six unknowns.
-To reduce the number of unknowns we assume that detection also gives us an estimate of angle and we assume that length of car is 1.3 times the height.
-Now, we have 4 unknowns and 4 constraints and we can solve them analytically.
+\documentclass[10pt,twocolumn,letterpaper]{article}
 
-\subsection{Necessary transforms}
-Let the ground plane be known with parameters $(\uv{n}, h)$.
-Let us take the ground plane to be the XY plane with Z axis pointing upwards and origin at the point of intersection of Y-axis with ground plane.
-The unit vector describing the ground plane is ambiguous by sign, we choose the sign of $\uv{n}$ such that $\hat{n}_2 > 0$, i.e.
-the unit vector is along the positive Y-axis of the camera based on the assumption that the camera axis are approximately aligned such that Y-axis points downwards and Z-axis to the front.
+\usepackage{cvpr}
+\usepackage{times}
+\usepackage{epsfig}
+\usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{tikz}
+\usepackage{pgfplots}
+\usetikzlibrary{shadows,trees}
 
-\begin{align}
-  ^gR_c &= [\uv{i}, -\uv{n} \times \uv{i}, -\uv{n}]\\
-  ^gt_c &= [0, 0, h]^\top\\
-        \text{where} & \\
- \uv{i} &= \frac{1}{\sqrt{\hat{n}^2_3, \hat{n}^2_2}}[0, \hat{n}_3, \hat{n}_2]^\top
-\end{align}
+\usepackage{verbatim}
+\usepackage{bm}
+\usepackage{microtype}
+\usepackage{url}
+\usepackage{multirow}
+\usepackage{subcaption}
+\usepackage{booktabs} % for better tables
 
-In homogeneous coordinates, let the camera to ground transformation be
-represented by $^gT_c = \begin{bmatrix}^gR_c & ^gt_c\\ \mathbf{0} &
-1\end{bmatrix}$ and its inverse be represented by $^cT_g = {}^gT_c^{-1}$. Let
-the yaw of car be given as theta in camera coordinates. Assume it to be same as
-ground plane coordinates.
+\newlength{\eqs}
+\setlength{\eqs}{-0.04in}
 
-\begin{align}
-  \Tr{g}{R}{t} &= \begin{bmatrix}
-  \cos(\theta) & \sin(\theta) & 0 \\
- -\sin(\theta) & \cos(\theta) & 0 \\
-             0 & 0 & 1
-  \end{bmatrix}
-\end{align}
+\usepackage{enumitem}
+\setitemize[0]{leftmargin=15pt}
 
-\subsection{System of equations}
-Let the detected bounding box be represented by $B$. Let $^cT_t$ be the transformation from tracklet to camera.
-\newcommand{\Cu}{C_u}
-\newcommand{\Cc}{C_c}
-\begin{align}
-  B &= [\xmin, \ymin, \xmax, \ymax]^T
-  \\
-  \Cu &= \begin{bmatrix}
-    0.5 & 0.5 & 0\\
-    0.5 & -0.5 & 0\\
-    -0.5 & -0.5 & 0\\
-    -0.5 & 0.5 & 0\\
-    0.5 & 0.5 & 1\\
-    0.5 & -0.5 & 1\\
-    -0.5 & -0.5 & 1\\
-    -0.5 & 0.5 & 1
-  \end{bmatrix}\\
-  C_i &= \diag( C_{u\{i,:\}} ) \begin{bmatrix}3& 0\\0 & 1 \\1 & 0\end{bmatrix} 
-\end{align}
+\newenvironment{tight_itemize}{
+\begin{itemize}[leftmargin=10pt]
+  \setlength{\topsep}{0pt}
+  \setlength{\itemsep}{0pt}
+  \setlength{\parskip}{0pt}
+  \setlength{\parsep}{0pt}
+}{\end{itemize}}
 
-\newcommand{\ttg}{\Tr{g}{\mathbf{t}}{t}}
-\newcommand{\tgc}{\Tr{c}{\mathbf{t}}{g}}
-\newcommand{\Rgc}{\Tr{c}{R}{g}}
-\newcommand{\Rtg}{\Tr{g}{R}{t}}
-\newcommand{\Rtc}{\Tr{c}{R}{t}}
-\newcommand{\Pgc}{\Tr{c}{P}{g}}
-\newcommand{\Ptc}{\Tr{c}{P}{t}}
+% If you comment hyperref and then uncomment it, you should delete
+% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
+% run, let it finish, and you should be clear).
+\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
 
-Consider the projection of i\textsuperscript{th} corner of the car.
-\begin{align}
-  \lambda_i \mathbf{u}_i &= K(\Rgc(\Rtg C_i[h, w]^\top + \ttg) + \tgc) & \text{ or }\\
-  \lambda_i \mathbf{u}_i &= K\Rtc C_i [h, w]^\top + K\Rgc \ttg + K \tgc
-  \label{eq:vectorproj}
-\end{align}
-where $\Rtc = \Rgc\Rtg$, $\ttg = [t_x, t_y, 0]^\top$ is unknown car position in
-ground coordinates, $h$ is unknown height, $w$ is unknown width of the car,
-$\lambda$ is unknown scale factor and $\mathbf{u}_i$ is the image projection of
-i\textsuperscript{th} corner of the car.
+\input{preamble}
+\newcommand{\xmin}{x_\text{min}}
+\newcommand{\ymin}{y_\text{min}}
+\newcommand{\xmax}{x_\text{max}}
+\newcommand{\ymax}{y_\text{max}}
+\DeclareMathOperator*{\argmin}{\arg\min}
 
-Equation \eqref{eq:vectorproj} is a set of 3 equations, the third of which allows us to eliminate $\lambda$ as it gives the $\lambda$ and as a linear combination of $t_x$, $t_y$, $h$ and $w$.
-Let $\Ptc = K\Rtc$ and $\Pgc = K\Rgc$.
-\begin{align}
-  \lambda_i \mathbf{u}_i &=  \Ptc C_i [h, w]^\top + \Pgc \ttg + K \tgc\\
-  \lambda_i &= \lambda_{hi}  h + \lambda_{wi}  w + \lambda_{tx}  t_x + \lambda_{ty} * t_y + \lambda_c\\
-  \text{where} & \\
-  \lambda_{hi} &= \Ptc(3, :) C_i(:, 1)\\
-  \lambda_{wi} &= \Ptc(3, :) C_i(:, 2)\\
-  \lambda_{tx} &= \Pgc(3, 1)\\
-  \lambda_{ty} &= \Pgc(3, 2)\\
-   \lambda_{c} &= K(3, :) \tgc
-\end{align}
+% Some diagrams have "visble" macro from beamer. Everything should be visible in paper mode.
+\makeatletter
+\def\visible<#1>#2{#2}
+\makeatother
 
-\subsection{Approximate solution}
-Initial approximate solution can be obtained by assuming that $\ymax$ is the projection either of point 
-\begin{align}
-  \lambda_c \mathbf{u}_c &= \Ptc[0, 0, \frac{h}{2}]^\top + \Pgc \ttg + K\tgc
-\end{align}
+%\cvprfinalcopy % *** Uncomment this line for the final submission
 
-Assuming the height to be mean height, we can solve for approximate solution
-for $\ttg$. Using this approximate solution find out the corner points that
-correspond to the bounding box. Finally \eqref{eq:vectorproj} can be used for
-the projected points to solve for exact $[h, w, t_x, t_y]$.
+\def\cvprPaperID{XXX} % *** Enter the CVPR Paper ID here
+\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
 
-\subsection{Correspondence of bounding box limits to cuboid corners}
-The $\xmin$ of bounding can be projection of either of the 8 points of the
-cuboid. Once $\xmin$ is chosen the $\xmax$ can be limited to the remain 7
-points hence $8 \times 7= 56$ possibilities and similarly $\ymin$ and $\ymax$
-lead to 56 different possibilities. In this relatively unconstrained
-configuration we have around $56 \times 56 = 3136$ possibilities, which is not
-too big but with a little more analysis we can reduce the number. To this
-effect we can use the aspect graph of a cuboid to understand the topological
-changes by change in view points. Also out of 28 possible configurations in the
-aspect graph, we can rule out the configurations that put camera below the
-ground plane and directly above the observed car itself. This leaves us with 16
-possible topological configurations, which include the symmetrical
-configurations when the car is rotated by $180^\circ$. Considering $180^\circ$ symmetry we are only left with 8 possible topological configurations.
+% Pages are numbered in submission mode, and unnumbered in camera-ready
+%\ifcvprfinal\pagestyle{empty}\fi
+%\setcounter{page}{4321}
 
-A more general way of finding the subset of aspect graph configuration that
-need to be configured is to rewrite the bounding box inequalities,
-
-\begin{align}
-  \lambda_i \xmax &\ge \Ptc(1, :) C_i [h, w]^\top + \Pgc(1, :) \ttg + K \tgc\\
-  \label{eq:bbox-ineqst}
-  \lambda_i \xmin &\le \Ptc(1, :) C_i [h, w]^\top + \Pgc(1, :) \ttg + K \tgc\\
-  \lambda_i \ymax &\ge \Ptc(2, :) C_i [h, w]^\top + \Pgc(2, :) \ttg + K \tgc\\
-  \lambda_i \ymin &\le \Ptc(2, :) C_i [h, w]^\top + \Pgc(2, :) \ttg + K \tgc \enspace.
-  \label{eq:bbox-ineq}
-\end{align}
-Each of the above four equations is true for all 8 corners, hence there are 32 such inequalities.
-
-The aspect graph boundaries also called the view events, occur when the view
-point or the camera optical center crosses the faces of the cuboid object being
-viewed. The camera optical center $o_t$ in tracklet coordinate frame is given by.
-\begin{align}
-  \mathbf{0} &= \Rgc(\Rtg o_t + \ttg) + \tgc\\
-  o_t &= -\Rtg^\top \ttg -\Rtg^\top \Rgc^\top \tgc
-\end{align}
-
-The 6 faces of a cuboid are simple planes that can be written in terms of $h$
-and $g$. A view event occurs whenever we have $o_t$ satisfying equations of any
-one of the equations that represent the 6 faces. We have to find the number of
-distinct regions that satisfy all of Eq
-\eqref{eq:bbox-ineqst}-\eqref{eq:bbox-ineq}. Then for each distinct region we
-need to find out the topological configuration that limits the number of
-corners candidates for extrema. These can be sorted to create boundaries.
-
-\section{Numerical integration}
-Numerical integration is possible by computed by sampling. Samples need to be
-generated from the association probability $\assocP$ for a given $j$. We take
-proposal distribution to be a GMM with modes around probable reflection points.
-The weights of all Gaussians in the mixture are proportional to the distance of
-the point $j$ from projection of ellipsoid centre i.e. 
-\begin{align}
-  A_{ij} = \frac{1}{Z_j}\exp(-(\trackpj{t} - \mu^i_u)^\top\Sigma_u^i(\trackpj{t} - \mu^i_u))
-\end{align}
-where $Z_j = \sum_{i=1}^N A_{ij}$ and $\mu^i_u$ and $\Sigma_u^i$ are described in %\eqref{eq:muiudef} and \eqref{eq:sigmauidef} respectively.
-The range of Gaussian $G_i$
-must be in the interval $[\|\relp{i}{t}\|, \|\relp{i}{t}\| -
-\sqrt{3}\max(\dimsn{i})]$. Hence we take the mean as $\|\relp{i}{t}\| -
-\frac{\sqrt{3}}{2}\max(\dimsn{i})$ and variance as
-$\frac{1}{3}\max(\dimsn{i})^2$. The distribution from which we sample is 
-\begin{multline}
-  \PropDist(\lambda) = \sum_i A_{ij} \\
-  \Gauss(\lambda; \|\relp{i}{t}\| -
-  \frac{\sqrt{3}}{2}\max(\dimsn{i}), \frac{1}{\sqrt{3}}\max(\dimsn{i}))
-\end{multline}
-And the numerical integral with $K$ samples is computed by
-\begin{align}
-    \int_1^{\infty}
-    \assocP
-    \Ereproj(\lambda)
-    d\lambda
-    =
-    \frac{1}{K}\sum_k \Ereproj \frac{\assocPk}{\PropDist(\lambda_k)}
-\end{align}
-where $\lambda_k$ is the $k$th sample drawn from $\PropDist(\lambda)$.
-
-\section{Sigma of ellipsoid}
+\begin{document}
+\section{Computation of ellipsoid parameters}
 How to compute the parameters of ellipsoid in the camera coordinate frame when center and dimensions of the ellipsoid are given in tracklet coordinate frame.
@@
 
-\begin{comment}
-  \section{Bounding box energy}
-  \label{sec:totalBBoxEnergy}
-  With abuse of notation we represent the four sides of hypothesized bounding
-  box by $\projectionOf{\dimsn{i}}$ and detected bounding box by $\bb{i}$.
-  Suppose the bounding box $i$ is occluded by bounding box $i$ then the
-  bounding box energy becomes a pairwise term.
+\section{Localization}
+\subsection{Other Energies}
+\subsubsection{Lane energy}
+\label{sec:laneEnergy}
+ The lanes are modeled as splines. Here we assume that the confidence in lane
+ detection is decreases as the distance from the lane center increases.  The
+ energy is given by the dot product between car orientation and tangent to the
+ lane at that point.
 
-  \begin{multline}
-    \pEnergy{occ}(\relp{i}{t}, \dimsn{i}, \relp{j}{t}, \dimsn{j}) = \\
-    \sum_s \rho^{ijs}(t)\projectionOf{\dimsn{i}}_s - \bb{i}_s
-               %\sum_{i=1}^N \sum_{t=s_i}^{e_i}
-    %\sum_kp_{ik}^{\text{track}}(\projectionOf{\dimsn{i}} - \bb{k})^\top \pmb{\rho}(i,j,t)
-  \end{multline}
-  where $\rho^{ijs}(t)$ is the visibility fraction of the side $s$ of the
-  bounding box. We need to compute visibility fraction we need to compute the
-  occlusion mask which is explained in next few sections.
+\begin{align}
+  \label{eq:laneOrientationEnergy}
+  \Energy{lane} = 
+  \sum_{m \in M_{\text{close}}}
+  (1 - \ori{i}{t} \cdot \text{TAN}(L_{m}(k), \pos{i}{t}) )
+\LaneUncertainty{\pos{i}{t}}
+\end{align}
+where $M_{\text{close}} = \{m : \text{DIST}(L_{m}(k), \pos{i}{t}) < d_{\text{thresh}}\} $ is
+the set of nearby lanes close to the object by a certain distance threshold $d_{\text{thresh}}$ and 
+\begin{align}
+\LaneUncertainty{\pos{i}{t}} = 
+  \frac{1}{1 + \exp(-q(w_{\text{road}} - \text{DIST}(L_{m}(k), \pos{i}{t})))}
+\end{align}
+for some constant $w_{\text{road}}$ that represents the width of the road.
 
-  \subsection{Visible faces from bounding boxes}
+\subsubsection{Transition probability}
+Dynamics constraints should not only enforce smooth trajectories, but also the
+holonomic constraints.  The following energy adds a penalty if the change in
+position is not in direction of previous orientation.
 
-  \begin{figure}[h]
-    \includegraphics[width=\columnwidth]{graphics/maxFacesVisible.pdf}
-    \caption{Only three faces can be visible out of six faces of a bounding
-    box.}
+\begin{align}
+  \label{eq:totalPosTransitionEnergy}
+  \Energy{dyn-hol} = 1 - \ori{i}{t-1} \cdot (\pos{i}{t} - \pos{i}{t-1})
+\end{align}
+
+The following energy adds a penalty for change in position and orientation
+but a penalty for change in velocity is much better approximation. However, in
+a Markovian setting that would mean extending the state space of the car to
+include velocity.
+
+\begin{align}
+  \Energy{dyn-ori} &= \|\ori{i}{t} - \ori{i}{t-1}\|^2\\
+  \Energy{dyn-vel} &= \|(\pos{i}{t} - 2\pos{i}{t-1}) + \pos{i}{t-2}\|^2
+\end{align}
+
+As a result the dynamics are modeled by weighted combination of holonomic
+constraint and smoothness constraints.
+
+\begin{align}
+  \WEnergy{dyn} &= \WEnergy{dyn-hol} + \WEnergy{dyn-ori} + \WEnergy{dyn-vel}
+\end{align}
+
+\subsubsection{Size Prior}
+
+Prior can include among many other things the size prior on the car.
+
+\begin{align}
+  \label{eq:totalSizeEnergy}
+  \Energy{size} &= (\dimsn{i} - \expDimsn)^\top\Sigma_{\expDimsn}^{-1}(\dimsn{i} -
+  \expDimsn)
+\end{align}
+
+where $\expDimsn$ is the mean TP dimensions and
+$\Sigma_{\expDimsn}$ is the correspondence covariance matrix.
+
+\section{Inference method Comparison}
+
+We use two methods for inference, Metropolic Hastings and block coordinate descent. We briefly describe the inference algorithms for completeness.
+
+\subsection{Metropolis Hastings}
+Metropolis Hastings requires a \emph{transition probability} $Q(\map'|
+\map^r)$, that depends on current sample $\map^r$ and guides
+the random walk in the high-dimensional space. We randomly sample a point
+$\map'$ from from $Q(.)$ and it is either accepted or rejected based on the
+\emph{acceptance probability} $a$:
+\begin{align}
+  a = \frac{P(\map')Q(\map^r| \map')}
+  {P(\map^r)Q(\map'| \map^r)}
+  \enspace,
+\end{align}
+where $P(\map)$ is joint probability of the model at point $\map$.
+
+If $a \ge 1$, then the new point $\map'$ is accepted otherwise it is accepted
+with probability $a$. Here acceptance means that the point in the next
+iteration is taken as the sampled point otherwise the earlier point is retained.
+
+\subsection{Block Coordinate Descent}
+
+We use block coordinate descent algorithm on our factor graph, by iteratively
+minimizing the energy with respect to only a subset (block) of random 
+variables. We choose to divide the blocks along the
+variable types like dimension, yaw and position.
+Hence we iteratively minimize the energies with respect to dimension variables, then with respect to yaw variables and then with respect to position variables.
+Since we know the dependence of parts of our energy on specific variables, thanks to factor graph formulation, we can minimize the energies corresponding to the given set of variables.
+
+  \begin{center}
+    \scalebox{0.5}{
+    \begin{tikzpicture}
+      \begin{axis}[xlabel=CPU time (sec),ylabel=Energy,
+          legend entries={Coordinate Descent,Metropolic Hastings},
+          legend columns=-1,
+          legend to name=convergencelegend,
+          legend style={draw=none,fill=none},
+          width=0.5\textwidth,
+          y post scale=0.8,
+        name=plot1]
+        \addplot table [x index=0,y index=1,header=false] {graphics/mcmc_inference_cputime_0000000060.txt};
+        \addplot table [x index=0,y index=1,header=false] {graphics/stepWiseInference_cputime_0000000060.txt};
+      \end{axis}
+      %\includegraphics[width=0.5\textwidth, trim=4.5cm 7cm 4.5cm 7cm, clip]{graphics/mcmc_vs_coordinate_descent_60.pdf}
+      \begin{axis}[at={(plot1.south east)},
+          xlabel=CPU time (sec),xshift=0.5cm,
+          width=0.5\textwidth,
+          y post scale=0.8,
+        ]
+        \addplot table [x index=0,y index=1,header=false] {graphics/mcmc_inference_cputime_0000000192.txt};
+        \addplot table [x index=0,y index=1,header=false] {graphics/stepWiseInference_cputime_0000000192.txt};
+      \end{axis}
+    \end{tikzpicture}
+    }
+    \ref{convergencelegend}
+  \end{center}
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{results/0009_contPtTracks_size_bboxOcc_yawTstepWiseInference_0000000061.png}
+  \includegraphics[width=\columnwidth]{results/0009_lane_size_bboxOcc_yawTstepWiseInference_0000000061.png}
+  \caption{Qualitative localization results}
+  \label{fig:qualLocalizationResults}
 \end{figure}
 
-  Each bounding box has 6 faces of which only 3 can be visible.
-  Sort the vertices in increasing order of depth. The closest vertex has three
-  neighboring faces. All the faces that are visible must be a subset of these
-  three. Use first three vertices to
-  define the front face (say $\frontface$). Also identify the four 3D points
-  that correspond to min/max in x and y direction in the image. If all min-max 4
-  points are same as vertices of $\frontface$, then we have only one plane
-  visible. If $\{\minx, \maxx\} \not\subset \frontface \land \{\miny, \maxy\}
-  \not\subset \frontface$ then we have 3 planes visible. Otherwise we have just
-  two planes visible. Let number of planes visible be $n_F$.
-
-  \begin{align}
-    n_F &= \begin{cases}
-    1 & \text{if }\{\minx, \maxx, \miny, \maxy\} =
-    \frontface\\
-    2 & \text{else if }\{x_{\text{min}}, x_{\text{max}}\} \subset \frontface \lor
-    \{y_{\text{min}}, y_{\text{max}}\} \subset \frontface
-    \\
-    3 & \text{else if }\{x_{\text{min}}, x_{\text{max}}\} \not\subset \frontface \land
-    \{y_{\text{min}}, y_{\text{max}}\} \not\subset \frontface
-    \end{cases}
-    \label{eq:nfaces}
-  \end{align}
-
-  First vertex restrict possible visible faces to three faces. If $n_F = 3$,
-  then all three of these faces are visible. If $n_F = 2$, use second closest
-  vertex to restrict visible faces to just two. If $n_F = 3$, then front face 
-  $\frontface$ is the only visible face.
-\end{comment}
-
-\begin{comment}
-  \subsection{Occlusion mask}
-  % Initialize empty mask polygon $\occ{0}$ at depth $d=0$.
-  % \begin{itemize}
-  %   \item Sort all cars in increasing order of depth
-  %   \item for each car $i$ in the sorted list
-  %     \begin{itemize}
-  %       \item Update mask polygon: \\
-  %         $\occ{\relpz{i}{t}} = \occ{d} \cup \projectionOf{\dimsn{i}}$
-  %       \item $d = \relpz{i}{t}$
-  %     \end{itemize}
-  % \end{itemize}
-
-  % Sort all planes in increasing order of depth.  This yields a cumulative
-  % occlusion mask function
-  Occlusion mask is a function that takes the relative depth $d$ from the car
-  camera and returns a binary mask that represents occlusions untill that depth.
-  Near to the camera occlusion mask is all empty (all zeros) and more occlusions
-  get added to the mask with distance.
-
-  \begin{align}
-    \occ{d} &= \begin{cases}
-    \phi & \text{if } 0 < d \le \relpz{1}{t}\\
-    \cup_{i=1}^j \projectionOf{F^i} & \text{if } \relpz{1}{t} < d \le \relpz{j+1}{t}
-    \end{cases}
-    \label{eq:occlusionmask}
-  \end{align}
-
-  where $\relpz{j}{t}$ is the depth of the $j$th TPs participant when sorted
-  by increasing depth.
-
-  \subsection{Algorithm to get faces based occlusion mask}
-  \label{sec:occlusionMaskFromOptVector}
-
-  This is an algorithm to compute occlusion mask Eq.\eqref{eq:occlusionmask}. We
-  represent the occlusion mask as a set of polygons.
-
-  Initialize empty mask polygon $\occ{0}$ at depth $d=0$.
-  \begin{enumerate}
-    \item Collect visible faces using Eq.\eqref{eq:nfaces} for all cars
-    %\item for each face get its closest and farthest vertex to the camera.
-    \item Create a sorted list of faces
-    % \item Create a sorted binary tree of
-    %   faces indexed by closed vertices.
-    \item Loop over list of sorted visible faces
-      \begin{enumerate}
-        \item Get the face(s) $\{\face\}$ closer to camera than this face
-        \item Add the faces to mask polygon (if not already added): \\
-          $\occ{\relpz{i}{t}} = \occ{d} \cup \projectionOf{\face}$
-        \item $d = \relpz{i}{t}$
-      \end{enumerate}
-  \end{enumerate}
-
-  To get the occlusion mask for a face use the farthest vertex of the face to
-  query $\occ{.}$.
-
-  \subsection{Visibility fraction of a side}
-  Let the center of the projected hypothesized bounding box be $\centerProj$ and
-  the four corners be $\{\cornerProj{k}\}_{k=1}^{4}$ . Each side and the center
-  of the bounding box form a triangle, for example $\triangleProj{1,2} =
-  \{\cornerProj{1}, \cornerProj{2}, \centerProj\}$. We take the visibility of
-  this triangle as a visibility of the side $s = (1,2)$. Hence the visibility
-  fraction of side is given by
-  \begin{align}
-    \rho^{ijs}(t) = \frac{\|\triangleProj{s} \setminus \occ{\relpz{i}{t}}\|}
-                         {\|\triangleProj{s}\|}
-     \label{eq:bboxEnergyFromOccMask}
-  \end{align}
-\end{comment}
-
-\begin{comment}
-  \section{Occlusion free projection}
-  Occlusion free projection can be obtained by applying the precomputed occlusion
-  mask to the face projection.
-  \begin{align}
-    \occFreeProj{\face} &= \projectionOf{\face} \setminus
-    \occ{\relpz{i}{t}}
-  \end{align}
-
-  \section{Perspective-visibility fraction}
-
-  Apart from occlusion, we want to account for the perspective affects. When an 
-  objects perspective projection is too small, detection and all related
-  evidences deteriorate. One way of this is to find out the projection ratio. In
-  fact, we can consolidate projection ratio and occlusion ratio in one term if
-  we consider the projection of 3D bounding box planes instead of the entire
-  bounding box.
-
-  \begin{align}
-    \rho^i_t &= \sum_{k=1}^{n_F}\frac{\relpz{i}{t}^2\|\occFreeProj{F^i_k(t)}\|}{f^2\|F^i_k(t)\|}
-  \end{align}
-
-  where $\occFreeProj{.}$ again means occlusion free projection. $f$ is the
-  focal length of the camera so that $\frac{f^2}{\relpz{i}{t}^2}\|F^i_k(t)\|$ is
-  the area of projected plane if there were no perspective effects.
-\end{comment}
-
-\begin{comment}
-
-\begin{table*}
-  \begin{tabular}{|l|r|r|l|}
-    \hline
-    func            & equation                      & ms per 6 frames &
-    comment \\
-    \hline
-    totalBBoxEnergy & Sec \ref{sec:totalBBoxEnergy} & 268 & \\
-    laneEnergy      & Sec \ref{sec:laneEnergy}      & 163 & \\
-    laneOrientationEnergy & Eq \eqref{eq:laneOrientationEnergy} & 155 & The
-    equation summed up for all 6 tracklets\\
-    collisionEnergyHellingerDistance & Eq 
-    \eqref{eq:collisionEnergyHellingerDistance} & 93  & \\
-    totalPosTransitionEnergy & Eq \eqref{eq:totalPosTransitionEnergy} & 15 & \\
-    totalSizeEnergy & Eq \eqref{eq:totalSizeEnergy} & 0.9 & \\
-
-    \hline
-    occlusionMaskFromOptVector & Sec \ref{sec:occlusionMaskFromOptVector} &
-    123 &
-    \\
-    bboxEnergyFromOccMask & Eq \eqref{eq:bboxEnergyFromOccMask} & 140 &  \\
-    vis\_area\_from\_triangle & $\|\triangleProj{s} \setminus
-    \occ{\relpz{i}{t}}\|$ & 76 & \\
-    \hline
-    distance2curve & $\text{DIST}(L_j(k), x)$ & 74 & Called 2 times per
-    tracklet \\
-    filterMapWaysByDistance & $M_{\text{close}} = \{m : \text{DIST}(.) < 50\} $ & 52 & \\
-    area\_of\_triangle & $\|\triangleProj{s}\|$ & 48 & called 4 times per
-    tracklet \\
-    occlusionMask & Step 3 of Sec \ref{sec:occlusionMaskFromOptVector} & 46 &
-    \\
-    \hline
-  \end{tabular}
-
-  \begin{tabular}{|l|r|r|l|}
-    \hline
-    func            & equation                      & ms per 6 frames &
-    comment \\
-    \hline
-    totalContPtTracksEnergy & Sec \ref{sec:totalContPtTracksEnergy} & 25000 &
-    \\
-    integrand & Eq \eqref{eq:integrand} & 23000 & \\
-    repmat & & 5000 & \\
-    assocCoeffEval & Eq \eqref{eq:assocCoeffEval} & 4000 & \\
-    evalPreflection & Eq \eqref{eq:analytic-prefl} & 3000 & \\
-    gradfocci & $\nabla \occf^\top \ray$ & 2040 & \\
-    associationCoefficientInit & Eq
-    \eqref{eq:ptransmissionInit}\eqref{eq:ellipsoidMeanSigma} & 1706 & \\
-    projectToImage & $\frac{Ku}{Ku(3)}$ & 4000 & Called ~8 times per edge\\
-    evalCumulativePtrans & \eqref{eq:evalCumulativePtrans} & 1178 & \\
-    ptransmissionApproxInit & \eqref{eq:ptransmissionInit} & 1000 & \\
-    ellipsoidCentreDist & $(x-\mu)^\top \Sigma (x-\mu)$ & 1000 & \\
-    squeeze & & 951 &\\
-    trackletToCamTransform & $R_{\ori{i}{t}}, t$ & 786 & \\
-    ellipsoidMeanSigma & Eq \eqref{eq:ellipsoidMeanSigma} & 812 & \\
-    \hline
-  \end{tabular}
-\end{table*}
-
-\end{comment}
-
-\begin{comment}%%%%%%%%%%%%% May or may not use %%%%%%%%%%%
-TODO: Write Introduction
-  NEC has already developed a monocular camera based structure from motion
-  system which is accurate for requirements of road scene understanding. So we
-  assume that egomotion is given as an observed variable in our graphical
-  model. And we have following features to our disposal for estimating the 3D
-  poses (position + orientation) of traffic participants (TPs):
-  \begin{description}
-    \item[Ground plane] We assume that all the TPs lie on a common ground
-      plane. This is not particularly true for the cars that are parked off the
-      road. However, for autonomous driver assistance applications we can
-      ignore those cars.
-    \item[Detections] We assume that 2D car detections are available with tracking informations.
-    \item[Point tracks] We assume that 2D point tracks are available.
-    \item[GPS and Map information] We assume that GPS information is available
-      and we use openstreetmaps.org for pulling out local map for the current
-      car's position.
-    \item[Lane Information] We assume the lane detection works well and lane
-      information is available.
-    \item[Size prior] The distribution of size of cars follows gaussian distribution.
-    \item[Collision] A reasonable output of the system donot has any overlapping cars.
-  \end{description}
-\end{comment}
-
-  \section{Uncertainty addition in measurement}
-  Consider that we have a set of measurements whose mean and variance are known $\mu = E(x)$ and $\Sigma = E ((x - \mu_x)(x - \mu_x)^\top)$. We want to know the
-  affect of uncertainty on mean and variance of existing observations. On adding
-  noise $[\Delta x, \Delta y]^\top$ with zero mean and covariance $\Delta
-  \Sigma = E(\Delta x \Delta x^\top)$ the covariance of new data is given by
-  \begin{multline}
-    E((x + \Delta x)(x+\Delta x)^\top) = E(xx^\top) + E(x \Delta x^\top) 
-    \\
-    + E(\Delta x x^\top) + E(\Delta x \Delta x^\top)
-  \end{multline}
-  where the terms $E(x \Delta x^\top)$ denote the correlation between the data
-  vector and the uncertainty in the data. Although we understand that in our case
-  the data is the appearance based detection score and uncertainty because of
-  occlusion is closely related to the appearance and hence detection score, we
-  assume independence between $x$ and $\Delta x$. Hence our resultant covariance
-  matrix $ E((x + \Delta x)(x+\Delta x)^\top) = \Sigma + \Delta \Sigma$
-  are 4D. But that should not be a problem because the detection scores are
-  modeled as $[x_{\text{min}}, y_{\text{min}}, x_{\text{max}},
-  y_{\text{max}}]^\top$, we can stack the vectors in the soft occlusion region
-  domain as the regions are independent of min or max variation. The parameters
-  of 4D occlusion distribution are given by
-
-  \begin{align}
-    \mu'_{Oij} = [\mu_{Oij}^\top \mu_{Oij}^\top]^\top
-    \Sigma'_{Oij} = \begin{bmatrix}
-      \Sigma_{Oij} & \Sigma_{Oij} \\
-  \Sigma_{Oij} & \Sigma_{Oij}
-    \end{bmatrix}
-  \end{align}
-
-  With our
-  discussion so far, the function $O_{ij}(.)$ gives an additional measure of
-  uncertainty associated with each point in the space.
-
-% Explanation of Beizer curves is not needed %%%%%%%%%%%%%%%%%%%
-% A lane is modeled by four control points of a \Beizer curve $L_j = \{l_0, l_1,
-% l_2, l_3\}$. The parametric curve is given by $L_j(k) = \sum_{i=0}^3 {}^3C_i
-% (1-t)^{3-i}t^i l_i$. \Beizer are double differentiable so one can find
-% tangents ($L'_j(k)$) and normals $R_{\frac{\pi}{2}}L'_j(k)$ where 
-% $R_{\frac{\pi}{2}} = \begin{bmatrix} 0 & -1 \\ 1 & 0 \end{bmatrix}$ is
-% $90^\circ$ rotation matrix.
-
-%Using standard algorithms \cite{ma2003point, chen2007improved}, we 
-%approximate the closest point on a \Beizer curve $k_x = \projOnLane{x}$.
-%Consequently one can get solutions for shortest distance $s =
-%\text{DIST}(L_j(k), x)$ and orientation at a closest point on the lane
-%$\mathbf{t} = \text{TAN}(L_j(k), x)$.
-
-% \subsection{Position in lane}
-%
-% \begin{align}
-%   \Energy{plane} &=
-%   \min_{j = 0}^{n_l} \text{DIST}(L_j(k), \pos{i}{t})
-% \end{align}
-%
- % 
- % We normalize it with the confidence in lane positions.
- % 
- % \begin{align}
- %   \Energy{plane} &=
- %   \min_{m = 0}^{n_l} \text{DIST}(L_m(k), \pos{i}{t})
- %   \LaneUncertainty{\pos{i}{t}}
- % \end{align}
-
-%\subsection{Orientation within lane}
-%\begin{itemize}
-%\end{itemize}
-
-% \begin{align}
-%   \Energy{olane} &= 1 - \text{TAN}(L_l(k),  \pos{i}{t})
-%   \cdot
-%   \ori{i}{t}
-% \end{align}
-% 
-% 
-% 
-% This model needs to be scaled by uncertainty. For example, if we want to say
-% that the farther the lane is from the camera we are less sure about lane
-% orientation and hence this evidence term we scale it by say square of distance
-% of the car position from camera.
-
-% \begin{align}
-%   \Energy{olane} &= 
-%   (1 - \ori{i}{t} \cdot \text{TAN}(L_{m^*}(k),  \pos{i}{t}) )
-%   
-% \end{align}
-% where $m^* = \arg \min_m \text{DIST}(L_m(k), \pos{i}{t})$
-
-\begin{comment}
-
-\section{Collisions}
-
-The collision constraint among TPs can be modelled by
-pairwise distance based constraints. But having constraints between each pair
-of participants is bound to create cycles and computational inefficient.
-Among game developers it is common to use spatial hashing to find collision
-candidates and use pairwise constraints only among those. While this will
-enable us to speed up collision checking, we will still end up inducing cycles
-in the model. There are two ways to break these cycles, 1) disable the cross
-lane collision checking 2) created a weighted graph among collision
-candidates weighted by distance and then find a minimum spanning
-tree to break cycles. (1) is too strong of an assumption hence we focus on the
-second approach.
-
-There are two possible approaches to find collision among candidates (1)
-polygon intersection methods (2) soft ellipse intersection method. Boost
-provides scan line based approach to find intersections of polygons. Since our
-polygons are simple rectangles, this approach can be very fast. Other approach
-is to approximate rectangles with ellipses and finding if the ellipses
-intersect.  This intersection can be computed analytically.
-
-\begin{align}
-  \EnergyCol &= \begin{cases}
-  \infty &\text{if INTERSECTS}(\pos{i}{t}, \dimsn{i}, \pos{j}{t},
-  \dimsn{j})\\
-  0 &\text{otherwise}
-  \end{cases}
-\end{align}
-
-%For smoother collision probability see Section \ref{sec:smoothercollision}.
-
-\subsection{Ellipse-ellipse intersection}
-\label{sec:ellipseintersection}
-A rectangle with sides $2a$ and $2b$ can be approximated by an ellipse with
-equation $\frac{x^2}{a^2} + \frac{y^2}{b^2} = 1$. But this ellipse is inside
-the rectangle. To enclose the rectangle, scale the ellipse by a factor of
-$\sqrt{2}$. The equation becomes, $\frac{x^2}{2a^2} + \frac{y^2}{2b^2} = 1$.
-For rotation $\psi$ and center $\pos{i}{t}$, the equation of ellipse can be
-re-written as:
-\begin{align}
-  (\mathbf{x} - \pos{i}{t})^\top\Sigma_i^{-1}(\mathbf{x} - \pos{i}{t}) &= 1
-\end{align}
-where
-\begin{align}
-  \Sigma_i^{-1} &= \begin{bmatrix}
-    \frac{\cos^2{\psi}}{2a^2} + \frac{\sin^2{\psi}}{2b^2} &
-    \frac{\cos{\psi}\sin{\psi}}{2}(\frac{1}{b^2} - \frac{1}{a^2})\\
-    \frac{\cos{\psi}\sin{\psi}}{2}(\frac{1}{b^2} - \frac{1}{a^2}) &
-    \frac{\sin^2{\psi}}{2a^2} + \frac{\cos^2{\psi}}{2b^2} \\
-  \end{bmatrix}
-\end{align}
-
-% A point $\mathbf{x}$ is inside both ellipse $i$, $j$ if and only if
-% \begin{multline}
-%   (\mathbf{x} - \pos{i}{t})^\top\Sigma_i^{-1}(\mathbf{x} - \pos{i}{t}) +\\
-% (\mathbf{x} - \pos{j}{t})^\top\Sigma_j^{-1}(\mathbf{x} - \pos{j}{t})
-%   \le 2
-% \end{multline}
-% which is equivalent to
-% \begin{multline}
-%   (\mathbf{x} - \mu_c)^\top\Sigma_c^{-1}(\mathbf{x} - \mu_c)
-%   + \pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t}\\
-%   + \pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t}
-%   - \mu_c^\top\Sigma_c^{-1}\mu_c
-%   \le 2
-% \end{multline}
-% where $\Sigma_c = (\Sigma_i^{-1} + \Sigma_j^{-1})^{-1}$ and $\mu_c =
-% \Sigma_c(\Sigma_i^{-1}\pos{i}{t} + \Sigma_j^{-1}\pos{j}{t})$.
-% 
-% There is at least one point inside both ellipse if 
-% \begin{align}
-%   \pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t}
-%   + \pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t}
-%   - \mu_c^\top\Sigma_c^{-1}\mu_c
-%   &\le 2
-% \end{align}
-% 
-% The left hand side can be interpreted as distance between two ellipses, which
-% is 2 when the two ellipses collide and $0$ when two ellipse completely
-% overlap.
-
-\subsection{Smoother collision probability}
-\label{sec:smoothercollision}
-%The above mentioned ellipse-ellipse intersection formulation gives us an
-%insight: the distance between two oriented ellipse boundaries can be again
-%formulated as a distance metric\footnote{TODO:proof}.
-Instead of using Gaussians to model
-collision constraints as done by \cite{milan2013continuous}, we use a more
-steeper sigmoid function.
-\begin{multline}
-  \EnergyCol = \frac{1}{1 +
-\exp(-k(\pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t})-1)}\\
-\frac{1}{1 +
-\exp(-k(\pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t})-1)}
-\end{multline}
-where $k$ is steepness parameter.
-%$d(.)$ is the distance metric defined as:
-%\begin{multline}
-%  d(\pos{i}{t}, \dimsn{i}, \pos{j}{t}, \dimsn{j})
-%  =
-%  \pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t} \\
-%  + \pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t}
-%  - \mu_c^\top\Sigma_c^{-1}\mu_c
-%\end{multline}
-
-\end{comment}
-
-\begin{comment}
-\section{Analytical attempt to integration}
-  %%%%%%%%%%%%%%%% Analytical attempt to integration %%%%%%%%%%%%%%%%%%%%%
-  \begin{align}
-    E^i_{\text{reproj}}(\lambda) &= \left\|\trackpj{t} - \frac{p_{1:2}\lambda +
-  q_{1:2}}{p_3\lambda + q_3}\right\|^2\\
-  &= \frac{(p_1\lambda + q_1 - u_{j1}(t))^2 + (p_2\lambda + q_2 - u_{j2}(t))^2}
-  {(p_3\lambda + q_3)^2}\\
-  &= \frac{a\lambda^2 + b\lambda + c}{(p_3\lambda + q_3)^2}
-  \end{align}
-  where $a = p_1^2 + p_2^2$, $b = 2p_1(q_1 - u_{j1}(t)) + 2p_2(q_2 - u_{j2}(t))$
-  and $c = (q_1 - u_{j1}(t))^2 + (q_2 - u_{j2}(t))^2$
-
-  So, in terms of $\lambda$ we have the integrand as
-  \begin{multline}
-    \int_1^\infty
-    \prod_i (1 +
-    \tanh(\poly^{(1)}_{ij1}(\lambda)))\sech^4(\poly^{(2)}_{ij2}(\lambda))\\
-    (\max\{ 0, \poly^{(2)}_{ij3}(\lambda) \})^2
-    \frac{\poly^{(2)}_{ij4}(\lambda)}{(\poly^{(1)}_{ij5}(\lambda))^2}d\lambda
-  \end{multline}
-  where $\poly^{(n)}_{ijk}$ denotes a polynomial $k$ of order $n$ dependent upon $i$th
-  TP and $j$th point. This integrand is still too difficult to
-  be solved or approximated analytically.
-
-  We approximate the expression,
-
-  \begin{multline}
-    \prod_i \Llambda
-  \sech^4\left(\frac{k}{2}\dishort\right)(\max\{ 0, \nabla k\dishort^\top\ray \})^2
-  \end{multline}
-
-  with a
-  gaussian with mean at $\mu^{ij}_{\lambda} : d_i(\mu^{ij}_{\lambda}\ray) = 0$
-  standard deviation as $\sigma^{ij}_{\lambda} =
-  \frac{\pi}{2\sqrt{3}kd(\mu^{ij}_{\lambda}\ray, \pos{i}{t-1})}$  and magnitude as the
-  expression computed at mean. An integrand of the form
-  \begin{align}
-    \frac{\poly^{(2)}_{ij4}(\lambda)}{(\poly^{(1)}_{ij5})^2}
-      e^{\frac{- (\lambda -
-  \mu^{ij}_{\lambda})^2}{\sigma^{ij}_{\lambda}}}
-  \end{align}
-   is integrable analytically by parts.
-
-   \begin{align}
-   \int_1^\infty \frac{a\lambda^2 + b\lambda + c}{(p_3\lambda + q_3)^2}e^{\frac{- (\lambda -
-  \mu^{ij}_{\lambda})^2}{\sigma^{ij}_{\lambda}}}d\lambda
-   \end{align}
-   Substituting $y = \frac{\lambda - \mu^{ij}_{\lambda}}{\sigma^{ij}_{\lambda}}$
-
-   \begin{align}
-     \int_1^\infty \frac{a_y y^2 + b_yy + c_y}
-     {(p_{3y}y + q_{3y})^2}e^{-y^2}dy
-   \end{align}
-   where $a_y = a(\sigmaijl)^3$, $b_y = (2a\muijl + b)(\sigmaijl)^2$ and $c_y =
-   (2a(\muijl)^2 + b\muijl + c)\sigmaijl$ and $p_{3y} = \sigmaijl p_3$ and
-   $q_{3y} = p_3\muijl + q_3$
-
-\end{comment}
-
-  % \subsection{Sandwich of ellipsoids model}
-  % 
-  % \begin{enumerate}
-  %   \item Model $\occf$ as
-  %     sigmoid over ellipse instead of a gaussian.
-  %     \begin{align}
-  %       \occf = \frac{1}{
-  %       1 + e^{-(\mathbf{x} - \pos{i}{t})^\top
-  %         \Sigma_i (\mathbf{x} - \pos{i}{t}))}}
-  %     \end{align}
-  %   \item To get the intuition of this occupancy function imagine the traffic
-  %     participant as layered ellipsoid. The innermost ellipsoid has very high
-  %     probability (approx 1) of being occupied. The outermost ellipsoid has very
-  %     low probability (approx 0) of being occupied. We will just consider the
-  %     occupancy interplay within these two ellipsoids.
-  %   \item Project outer ellipsoids of all TP's on the image.
-  %   \item Consider the ellipses that bound the track point $\trackpj{t-1}$.
-  %   \item For each ellipse do
-  %     \begin{itemize}
-  %       \item Case 1: The ray intersects inner ellipse
-  %         Now the ray intersects both inner and outer ellipse
-  %         Compute the intersection points on both the ellipses
-  %         Compute the gradient function $\nabla\occf^\top \ray$ at
-  %         the mid point of the two intersections. Use this as the magnitude of
-  %         gaussian mixture component centered at the mid point of intersections
-  %         and spread such that 97 percentile of probability mass of guassian is
-  %         within the intersection points. With the same parameters model the
-  %         transimission probability with product of logistic function $L(.)$.
-  %       \item Case 2: The ray do not intersects inner ellipse.
-  %         The ray just passes through the outer ellipse. Find the point on the
-  %         ray closest to the center of the ellipse. Compute gradient function
-  %         at the closest point, which will be again used as the magnitude of
-  %         gaussian mixture component centered at the closest point and spread
-  %         such that 97 percentile of probabiltiy mass of gaussian is within the
-  %         two intersection points of the ellipse. With the same parameters model
-  %         the transimission probability with product of sigmoids.
-  %     \end{itemize}
-  %   \item Now this approximated $\lambdadist = \sum N(.) \prod (1 - L(.))$ can
-  %     be used in integrating the error over $\lambda$.
-  % \end{enumerate}
-  \newpage
-
-  \clearpage
-  %%%%%%%%%%%%%%%% Analytical attempt to integration %%%%%%%%%%%%%%%%%%%%%
-
-% \section{Object detection score}
-% \begin{align}
-% \Energy{det}(\relp{i}{t}, \dimsn{i}) = 
-%              \frac{1}{S_t^2(\projectionOf{\dimsn{i}})}
-% \end{align}
-
-% \section{Object 2D bounding box with occlusion}
-% Reproduced from \cite{song2014eccv} section 4.3
-% 
-% \begin{multline}
-%   \Energy{box}(\relp{i}{t}, \dimsn{i}) =
-%              %\sum_{i=1}^N \sum_{t=s_i}^{e_i}
-%              \rho^i_t \|\projectionOf{\dimsn{i}} -
-%              \bb{i}\|^2
-% \end{multline}
-% 
-% where $S_t(.)$ is the function to approximate the detection scores using
-% mixture of Gaussian model and $\rho^i_t$ is the visibility fraction. 
-% 
-% % It can be
-% % computed by using polygon intersection algorithms.
-% % \begin{align}
-% %   v^i_t &= \frac{\|\occFreeProj{\dimsn{i}}\|}
-% %                 {\|\projectionOf{\dimsn{i}}\|}
-% % \end{align}
-% % where $\|.\|$ represents the norm or the area of the polygon.
-% 
-% Another approach is to just consider the corner points in the occlusion free
-% area.  Say $\projectionOf{\dimsn{i}} = [b^i_1, \dots, b^i_4]$.
-% \begin{multline}
-%   \Energy{box}(\relp{i}{t}, \dimsn{i}) =
-%              %\sum_{i=1}^N \sum_{t=s_i}^{e_i}
-%              %S_t^2(\projectionOf{\dimsn{i}})
-%              \sum_{{b^i_j} \in \occFreeProj{\dimsn{i}}}
-%              \|b^i_j - d^i_j\|^2
-% \end{multline}
-% 
-% In the opinion of this author, the second approach is better because the
-% visibility is an area based measure while the error metric is point to point
-% distance based measure. If we use bounding overlap instead of corner to corner
-% distance, the use of visibility fraction makes much more sense. However, one
-% can argue that even detection score is an area based measure. 
-% 
-% Hence a third approach can be 
-% \begin{multline}
-%   \Energy{box}(\relp{i}{t}, \dimsn{i}) =
-%              %\sum_{i=1}^N \sum_{t=s_i}^{e_i}
-%   \rho^i_t \|\projectionOf{\dimsn{i}} \ominus \bb{i}\|
-% \end{multline}
-% where $A \ominus B$ represents the symmetric difference between set $A$ and set
-% $B$ and is given by $A \ominus B = (A \cup B) \setminus (A \cap B)$.
-% One may argue that we can take the intersection of occlusion free projection 
-% and get rid of the visibility fraction, but that would be a little off the 
-% detection bounding box is usually more close to the projection of full car
-% instead of the just the visible portion.
-% 
-% 
-% \section{Orientation cues}
-% There are two orientation cues (1) orientation from detection (2) orientation
-% from appearance map \cite{yao2012describing}.
-% 
-% \begin{align}
-%   \Energy{ori} &= 
-%   %S_t^2(\projectionOf{\dimsn{i}})
-%   \rho^i_t(1 - \cos({\omega}^i_{\text{det}} - \ori{i}{t})
-% \end{align}
-% 
-% Appearance map is a shape prior that requires \emph{Scene labeling} input.
+\end{document}

### 2015-11-05 CVPR16/Source/related.tex
Related Work Complete

--- 2015-11-02 CVPR16/Source/related.tex
@@
 \section{Related Work}
-\paragraph{Occlusion handling in tracking}
-Occlusions have also been handled in tracking-by-detection frameworks by considering occluder patterns in the image \cite{Kwak_etal_2012,Wu_Nevatia_2007}.
-A notable exception is the work of Milan et al.~\cite{Milan_etal_2014} that explicits models occlusion in the continuous domain to determine a visibility for each object in multi-target tracking.
-However, the occlusion model in \cite{Milan_etal_2014} is essentially the overlap of image projections of a Gaussian representation of the object.
-Our occlusion modeling is much more general in determining the probability of a point in space as belonging to an object.
-While it can also be used to determine a visibility ratio similar to \cite{Milan_etal_2014}, it can have far more general applications and can be quantitatively evaluated, as shown by our experiments on point track associations.
+\label{sec:related}
 
-\paragraph{3D localization and scene understanding}
-One of the central goals of 3D scene understanding is to localize the 3D positions and orientations of objects in complex scenes.
+\paragraph{Occlusion handling} 
+Occlusion handling plays an important role in many computer vision applications such as object detection and tracking.
+Methods that are capable of detecting occluded objects include \cite{Gao_etal_2011}, which trains different detectors for detecting specific parts of the object, and \cite{Pepik_etal_2013,Xiang_Savarese_2013}, which use 3D cues that are learned from a CAD database.
+These methods are either based on 2D cues~\cite{Gao_etal_2011} or often a discrete representation of occlusion behaviors~\cite{Pepik_etal_2013,Xiang_Savarese_2013}, e.g., in terms of a set of occlusion masks.
+In contrast, our occlusion model is fully 3D and a continuous representation, which enables the use of various continuous optimization tools.
+For object tracking, occlusions are usually handled by a set of occluder patterns~\cite{Kwak_etal_2012,Wu_Nevatia_2007}, which is also a discrete representation.
+A notable exception is the work of Milan et al.~\cite{Milan_etal_2014}, which explicitly models object occlusions in continuous domain.
+However, their work is based on 2D ellipses while we use 3D ellipsoids, which are more principled and meaningful for tackling occlusions in 3D space.
+Moreover, our formulations have more general applications, especially 3D scene understanding such as 3D localization and reconstruction.
+
+\paragraph{Motion segmentation}
+Motion segmentation has actively been studied in the literature.
+Previous work can roughly be categorized into algebraic/factorization methods~\cite{Costeria98,Vidal03,Vidal04}, statistical methods~\cite{Kanatani01,Gruber04,Rao08} and clustering methods~\cite{Yan06,Goh07}.
+Some recent efforts include robust algebraic segmentation with hybrid perspective constraints~\cite{Rao_etal_2010} and spectral clustering with point track spatial affinity~\cite{Brox_Malik_2010}.
+The above methods usually exploit the fact that point tracks of a particular moving object tend to follow similar motion patterns.
+Therefore, they cannot segment static objects due to no motion cues.
+In contrast, our method for point-to-object association is relatively independent of object motions and hence does not suffer from static objects.
+
+\paragraph{3D localization}
+One of the vital goals of 3D scene understanding is to localize the 3D positions and orientations of objects in complex scenes.
 For instance, using stereo imagery, several visual cues are combined in \cite{Geiger_etal_2014} to simultaneously determine object locations and a rough intersection topology.
-Similar to us, other works have also considered monocular frameworks.
-Notably, occlusions are explicitly handled in \cite{Wojek_etal_2013} by considering partial object detectors.
-A detailed part-based representation of objects based on annotated CAD models is used for monocular scene understanding in \cite{Zia_etal_2013,Zia_etal_2014}, which also allows reasoning about mutual occlusions between objects.
-In contrast to these works, our monocular framework uses a physical modeling of occlusion in continuous space, which makes it more general, extensible and amenable for continuous optimization.
-
-\paragraph{Motion segmentation and multibody SFM}
-An application for our occlusion modeling is to determine point track associations in scenes with multiple objects.
-For moving objects, this is within the purview of motion segmentation, which has been actively studied \cite{Tron_Vidal_2007,Rao_etal_2010}.
-This also motivates further applications such as object segmentation based on point trajectories \cite{Brox_Malik_2010}.
-Motion segmentation is also used within multibody structure from motion (SFM) frameworks \cite{Ozden_etal_2010,Kundu_etal_2011,Namdev2012}.
-In contrast to these works, our formulation does not distinguish between moving and static objects and also explicitly reasons about occlusions due to 3D object geometries for associating point tracks to individual objects.
+Notable monocular frameworks for 3D localization include \cite{Wojek_etal_2013}, which uses partial object detectors for handling occlusions, and \cite{Zia_etal_2013,Zia_etal_2014}, which learn a detailed part-based representation of objects from annotated CAD models for reasoning about mutual occlusions.
+Generally speaking, the above methods are based on a discrete representation of occlusion behaviors.
+In contrast, leveraging on our occlusion model, we further develop unified formulations for both point track and bounding box energies, which are continuous and occlusion-aware, leading to an increase in 3D localization accuracy.

### 2015-11-05 CVPR16/Source/related.tex
Update related work

@@
 \paragraph{Occlusion handling} 
-Occlusion handling plays an important role in many computer vision applications such as object detection and tracking.
+Occlusion handling is an integral part of many computer vision applications such as object detection and tracking.
 Methods that are capable of detecting occluded objects include \cite{Gao_etal_2011}, which trains different detectors for detecting specific parts of the object, and \cite{Pepik_etal_2013,Xiang_Savarese_2013}, which use 3D cues that are learned from a CAD database.
@@
 Some recent efforts include robust algebraic segmentation with hybrid perspective constraints~\cite{Rao_etal_2010} and spectral clustering with point track spatial affinity~\cite{Brox_Malik_2010}.
-The above methods usually exploit the fact that point tracks of a particular moving object tend to follow similar motion patterns.
+The above methods usually exploit the fact that point tracks of a particular moving object tend to follow similar motion patterns (e.g., affine, epipolar and homography constraints).
 Therefore, they cannot segment static objects due to no motion cues.

### 2015-11-05 CVPR16/Source/applications.tex
Renaming bbox -> detect. Adding supplementary material.
New introduction

@@
 %\section{Occlusion-Aware Association and Localization}
+\label{sec:unified}
 
@@
 \subsection{Object-Point Association}
+\label{sec:association}
+
 Based on our continuous occlusion model in Section~\ref{sec:setup}, the association probability $\assocP$ of the $j$\textsuperscript{th} point track with $i$\textsuperscript{th} object at depth $\lambda$ can be defined as
@@
 \subsection{3D Object Localization}
+\label{sec:localization}
+
 To show the effectiveness of our method we apply it to the localization
@@
   \WEnergyCol 
-   + \WpEnergy{bbox}
+   + \WpEnergy{detect}
    + \WpEnergy{track}

### 2015-11-05 CVPR16/Source/intro.tex
Added more comments about the experiments.
New introduction

--- 2015-11-05 CVPR16/Source/intro.tex
@@
 
-A fundamental problem in computer vision is to separate feature points of multiple objects which are tracked through a video sequence.
+%Occlusions present a significant challenge to scene understanding.
+
+As a 2D projection of the 3D world, image formation is often associated with a loss of information.
+This is especially significant when objects in 3D space occlude each other with respect to the camera viewpoint.
+In recent years, we have seen remarkable progress in various fields that enable scene understanding, such as structure from motion and object detection.
+However, occlusions still present a difficult challenge, with the difficulty of physically modeling them being a major bottleneck.
+%Prior works have considered occlusions in 2D or through discrete occluder patterns
+
+Our main contribution is a novel theoretical model for occlusion handling that is continuous and fully 3D.
+Our model is motivated by insights from computer graphics, whereby we represent objects as translucent 3D ellipsoids.
+In Section \ref{sec:setup}, we develop novel continuous models for representing \emph{transmission} and \emph{reflection} probabilities for each ray emanating from the camera.
+This allows assigning probabilities for each point in space belonging to an object, which can explicitly explain image observations and reason about occlusions.
+This is in contrast to prior works that consider occlusions in 2D, or through discrete occluder patterns that are not physically interpretable.
+
+A key advantage afforded by our occlusion model is unification.
+While previous approaches to handling occlusion are application-dependent, ours is physically-inspired, thus, flexible enough to be used in a variety of scenarios.
+In this paper, we show that our theory can be used for modeling the association of 3D structure from motion points with static or dynamic objects (Section \ref{sec:association}), as well as modeling object detection scores in applications like 3D localization (Section \ref{sec:localization}).
+We demonstrate application of our formulations for road scenes from the KITTI dataset \cite{Geiger_etal_2012}.
+
+In particular, assigning 2D point tracks to independently moving, but potentially occluding, objects is a fundamental challenge in computer vision problems such as multibody SFM \cite{Ozden_etal_2010}.
+Recent works use motion segmentation \cite{Rao_etal_2010,Brox_Malik_2010} as a precursor to localizing moving objects, which often suffices for moving objects \cite{Tron_Vidal_2007} and has been considered for multibody SFM \cite{Kundu_etal_2011}.
+But motion-based segmentation is not always applicable in road scenes, due to static parked cars, or dynamic cars that move with similar velocities.
+Occlusions make the problem more severe since point tracks get clustered together for static objects and may frequently appear to change association among dynamic objects in 2D.
+%In contrast, we leverage the success of 
+Indeed, we show in Section \ref{sec:experiments} that our point track association outperforms state-of-the-art motion segmentation methods, as well as a baseline that uses detection bounding boxes but does not consider occlusions.
+
+Another potential application of our proposed model is towards 3D localization in road scenes.
+Prior works such as \cite{Song_Chandraker_2014} combine information from point tracks and detection bounding boxes, but do not consider occlusions for either.
+In contrast, our unified occlusion model allows a probabilistic soft assignment of point tracks to objects, as well as an occlusion-aware interpretation of object detection outputs.
+Our model is continuous, so remains amenable to the use of continuous optimization tools.
+
+To summarize, our main contributions are:
+\vspace{-0.2cm}
+\begin{tight_itemize}
+%\setlength\itemsep{0cm}
+\item A novel theoretical model for handling occlusions that is continuous and 3D.
+\item Unified occlusion handling in various applications, such as 3D points in SFM and bounding boxes in object detection.
+\item Application of our model to association of point tracks with both static and moving objects, improving over motion segmentation and occlusion-unaware baselines.
+\item Application of our unified formulation to 3D localization of traffic participants in road scenes.
+\end{tight_itemize}
+
+%A fundamental problem in computer vision is to separate feature points of multiple objects which are tracked through a video sequence.
 The assignments of point tracks to objects can serve as an important preprocessing step for different applications such as 3D localization and reconstruction, where the point tracks associated with an individual object can be used to localize or reconstruct the object in 3D space accurately.
@@
 
-Motion segmentation approaches~\cite{Rao_etal_2010,Brox_Malik_2010} usually rely on object motions for clustering point tracks.
+%Motion segmentation approaches~\cite{Rao_etal_2010,Brox_Malik_2010} usually rely on object motions for clustering point tracks.
 Since point tracks of the same object possess similar motion patterns, these methods generally produce accurate point-to-object associations for dynamic objects~\cite{Tron_Vidal_2007}.
@@
 
-In this work, we first propose to model objects as 3D ellipsoids.
+%In this work, we first propose to model objects as 3D ellipsoids.
 Motivated by image formulation theory in computer graphics, we then develop novel continuous models for representing \emph{transmission} and \emph{reflection} probabilities, which can explicitly explain image observations and reason about object occlusions.
-Leveraging on the success of object detection and tracking algorithms~\cite{Felzenszwalb_etal_2010,Choi_Savarese_2010}, we assume that detection bounding boxes and object tracklets are provided, thus we concentrate on segmenting point tracks that are computed only within object tracklets~\cite{Zach2007}.
-As we will show later, the proposed continuous occlusion modelling method outperforms the baseline method which merely uses bounding boxes for tackling occlusions.
+Leveraging on the success of object detection and tracking algorithms~\cite{Felzenszwalb_etal_2010,Choi_Savarese_2010}, we assume that detection bounding boxes and object tracklets are provided, thus we concentrate on segmenting point tracks that are computed only within object tracklets~\cite{Zach2007}, including both dynamic and static point tracks.
+As we will show in the experiments, the proposed continuous occlusion modelling method outperforms the baseline method which merely uses bounding boxes for dealing with occlusions.
 Furthermore, our method is not based on object motions and hence does not suffer from static objects as other state-of-the-art motion segmentation methods~\cite{Rao_etal_2010,Brox_Malik_2010}.
 
-As an important contribution, we examine the applicability of the proposed model for 3D localization in autonomous driving.
+%As another important contribution, we examine the applicability of the proposed model for 3D localization in autonomous driving.
 In contrast to the bounding box baseline method, which uses hard assignments of point tracks to objects (i.e., $\{0,1\}$ probabilities), our continuous occlusion modelling method employs soft assignments (i.e., [$0,1$] probabilities).
-Consequently, it offers a unified continuous occlusion modelling for both point track and bounding box energies, which allows the use of effective optimization tools.
-As we will show in the experiments, the proposed model benefits the task of 3D localization in autonomous driving in terms of lower translation and dimension errors compared to those of~\cite{Song_Chandraker_2014} which employs bounding boxes for point-to-object assignments.
+Consequently, it offers a \emph{unified} continuous occlusion modelling for both point track and bounding box energies, which allows the use of effective continuous optimization tools.
+As we will show later, the proposed model benefits the task of 3D localization in autonomous driving in terms of lower translation and dimension errors compared to those of~\cite{Song_Chandraker_2014}, which employs bounding boxes for point-to-object associations.
 
-The rest of the paper is organized as follows: Section~\ref{sec:related} discusses related work.
+%The rest of the paper is organized as follows: Section~\ref{sec:related} discusses related work.
 Section~\ref{sec:setup} describes the proposed continuous occlusion model for road scene understanding.
 Section~\ref{sec:experiments} presents detailed experiments for point-to-object association and 3D localization.
-Finally, we conclude in Section~\ref{}.
+Finally, we conclude in Section~\ref{sec:conclusions}.
 

### 2015-11-06 CVPR16/Source/related.tex
related work

--- 2015-11-05 CVPR16/Source/related.tex
@@
 
-\paragraph{Occlusion handling} 
-Occlusion handling plays an important role in many computer vision applications such as object detection and tracking.
-Methods that are capable of detecting occluded objects include \cite{Gao_etal_2011}, which trains different detectors for detecting specific parts of the object, and \cite{Pepik_etal_2013,Xiang_Savarese_2013}, which use 3D cues that are learned from a CAD database.
-These methods are either based on 2D cues~\cite{Gao_etal_2011} or often a discrete representation of occlusion behaviors~\cite{Pepik_etal_2013,Xiang_Savarese_2013}, e.g., in terms of a set of occlusion masks.
-In contrast, our occlusion model is fully 3D and a continuous representation, which enables the use of various continuous optimization tools.
+\paragraph{Occlusion handling in detection}
+Several works in object detection consider occlusion by training a detector on visible parts of the object \cite{Gao_etal_2011}.
+Occlusion reasoning based on 2D image silhouettes is used to improve detection performance in \cite{Hsiao_Herbert_2012}.
+In contrast, our occlusion reasoning is based on 3D entities.
+In recent years, object detectors have also considered occlusion reasoning using 3D cues, often learned from a dataset of CAD models \cite{Pepik_etal_2012,Pepik_etal_2013,Xiang_Savarese_2013}.
+By necessity, such frameworks are often a discrete representation of occlusion behavior, for example, in the form of a collection of occlusion masks derived from object configurations discretized over viewpoint.
+In constrast to these works, our occlusion modeling is also fully 3D, but allows for a continuous representation.
+Further, to derive 3D information, we do not use CAD models, rather we derive a probabilistic formulation based on physical insights.
+
+\vspace{-0.3cm}
+\paragraph{Occlusion handling in tracking}
+Occlusions have also been handled in tracking-by-detection frameworks by considering occluder patterns in the image \cite{Kwak_etal_2012,Wu_Nevatia_2007}.
+A notable exception is the work of Milan et al.~\cite{Milan_etal_2014} that explicits models occlusion in the continuous domain to determine a visibility for each object in multi-target tracking.
+However, the occlusion model in \cite{Milan_etal_2014} is essentially the overlap of image projections of a Gaussian representation of the object.
+Our occlusion modeling, on the other hand, is fully 3D, based on physical modeling of object-ray intersections and much more general in determining the probability of a point in space as belonging to an object.
+While our model can also be used to determine a visibility ratio similar to \cite{Milan_etal_2014}, it has far more general applications and can be quantitatively evaluated, as shown by our experiments on point track associations.
+
+%\paragraph{Occlusion handling} 
+%Occlusion handling is an integral part of many computer vision applications such as object detection and tracking.
+For instance, different detectors are trained for specific parts of the object in \cite{Gao_etal_2011} and 3D cues are learned from a CAD database in \cite{Pepik_etal_2013,Xiang_Savarese_2013}.
+Such prior approaches are application-dependent and either based on 2D cues~\cite{Gao_etal_2011} or offer a discrete representation of occlusion behaviors, for example, in terms of a set of occlusion masks \cite{Pepik_etal_2013,Xiang_Savarese_2013,Zia_etal_2014}.
+In contrast, our occlusion model is physically-inspired, fully 3D and a continuous representation, which makes it amenable to various applications and enables the use of continuous optimization tools.
 For object tracking, occlusions are usually handled by a set of occluder patterns~\cite{Kwak_etal_2012,Wu_Nevatia_2007}, which is also a discrete representation.
-A notable exception is the work of Milan et al.~\cite{Milan_etal_2014}, which explicitly models object occlusions in continuous domain.
+A notable exception is the work of Milan et al.~\cite{Milan_etal_2014}, which explicitly models object occlusions in the continuous domain.
 However, their work is based on 2D ellipses while we use 3D ellipsoids, which are more principled and meaningful for tackling occlusions in 3D space.
@@
 
-\paragraph{Motion segmentation}
-Motion segmentation has actively been studied in the literature.
+\vspace{-0.3cm}
+\paragraph{Motion segmentation and multibody SFM}
+An application for our occlusion modeling is to determine point track associations in scenes with multiple objects.
+For moving objects, this is within the purview of motion segmentation, which has been approached through algebraic factorization methods \cite{Costeria98,Vidal03,Vidal04}, statistical methods~\cite{Kanatani01,Gruber04,Rao08} and clustering methods~\cite{Yan06,Goh07}.
+Some recent efforts include robust algebraic segmentation with hybrid perspective constraints \cite{Rao_etal_2010} and spectral clustering with point track spatial affinities \cite{Brox_Malik_2010}.
+In contrast to our modeling, such methods cannot handle static objects, or dynamic objects with little relative motion.
+%\cite{Tron_Vidal_2007,Rao_etal_2010}. This also motivates further applications such as object segmentation based on point trajectories \cite{Brox_Malik_2010}. 
+Closer to our application, motion segmentation is also used within multibody structure from motion (SFM) frameworks \cite{Ozden_etal_2010,Kundu_etal_2011,Namdev2012}.
+In contrast to these works, our formulation does not distinguish between moving and static objects and also explicitly reasons about occlusions due to 3D object geometries for associating point tracks to individual objects.
+
+%\paragraph{Motion segmentation}
+%Motion segmentation has actively been studied in the literature.
 Previous work can roughly be categorized into algebraic/factorization methods~\cite{Costeria98,Vidal03,Vidal04}, statistical methods~\cite{Kanatani01,Gruber04,Rao08} and clustering methods~\cite{Yan06,Goh07}.
 Some recent efforts include robust algebraic segmentation with hybrid perspective constraints~\cite{Rao_etal_2010} and spectral clustering with point track spatial affinity~\cite{Brox_Malik_2010}.
-The above methods usually exploit the fact that point tracks of a particular moving object tend to follow similar motion patterns.
+The above methods usually exploit the fact that point tracks of a particular moving object tend to follow similar motion patterns (e.g., affine, epipolar and homography constraints).
 Therefore, they cannot segment static objects due to no motion cues.
@@
 
+\vspace{-0.3cm}
 \paragraph{3D localization}
-One of the vital goals of 3D scene understanding is to localize the 3D positions and orientations of objects in complex scenes.
-For instance, using stereo imagery, several visual cues are combined in \cite{Geiger_etal_2014} to simultaneously determine object locations and a rough intersection topology.
-Notable monocular frameworks for 3D localization include \cite{Wojek_etal_2013}, which uses partial object detectors for handling occlusions, and \cite{Zia_etal_2013,Zia_etal_2014}, which learn a detailed part-based representation of objects from annotated CAD models for reasoning about mutual occlusions.
+One of the vital goals of 3D scene understanding is to localize the 3D objects in complex scenes. 
+%For instance, using stereo imagery, several visual cues are combined in \cite{Geiger_etal_2014} to simultaneously determine object locations and a rough intersection topology. 
+Monocular frameworks like ours have also reasoned about occlusions, for instance, \cite{Wojek_etal_2013} consider partial object detectors.
+A detailed part-based representation of objects based on annotated CAD models is used for monocular scene understanding in \cite{Zia_etal_2013,Zia_etal_2014}, which also allows reasoning about mutual occlusions between objects.
+In contrast to these works, our monocular framework uses a physical modeling of occlusion in continuous space and derives unified representations for SFM points and object detection bounding boxes.
+This makes our model more general, extensible and amenable for continuous optimization.
+
+%Notable monocular frameworks for 3D localization include \cite{Wojek_etal_2013}, which uses partial object detectors for handling occlusions and \cite{Zia_etal_2013,Zia_etal_2014}, which learn a detailed part-based representation of objects from annotated CAD models for reasoning about mutual occlusions.
 Generally speaking, the above methods are based on a discrete representation of occlusion behaviors.
 In contrast, leveraging on our occlusion model, we further develop unified formulations for both point track and bounding box energies, which are continuous and occlusion-aware, leading to an increase in 3D localization accuracy.
+
+%One of the central goals of 3D scene understanding is to localize the 3D positions and orientations of objects in complex scenes.
+For instance, using stereo imagery, several visual cues are combined in \cite{Geiger_etal_2014} to simultaneously determine object locations and a rough intersection topology.
+Similar to us, other works have also considered monocular frameworks.
+Notably, occlusions are explicitly handled in \cite{Wojek_etal_2013} by considering partial object detectors.
+A detailed part-based representation of objects based on annotated CAD models is used for monocular scene understanding in \cite{Zia_etal_2013,Zia_etal_2014}, which also allows reasoning about mutual occlusions between objects.
+In contrast to these works, our monocular framework uses a physical modeling of occlusion in continuous space, which makes it more general, extensible and amenable for continuous optimization.

### 2015-11-06 CVPR16/Source/intro.tex
changes
small changes in Intro & Related Work

@@
 This is especially significant when objects in 3D space occlude each other with respect to the camera viewpoint.
-In recent years, we have seen remarkable progress in various fields that enable scene understanding, such as structure from motion and object detection.
+In recent years, we have seen remarkable progress in various fields that enable scene understanding, such as structure from motion (SFM) and object detection.
 However, occlusions still present a difficult challenge, with the difficulty of physically modeling them being a major bottleneck.
@@
 While previous approaches to handling occlusion are application-dependent, ours is physically-inspired, thus, flexible enough to be used in a variety of scenarios.
-In this paper, we show that our theory can be used for modeling the association of 3D structure from motion points with static or dynamic objects (Section \ref{sec:association}), as well as modeling object detection scores in applications like 3D localization (Section \ref{sec:localization}).
+In this paper, we show that our theory can be used for modeling the association of 3D SFM points with static or dynamic objects (Section \ref{sec:association}), as well as modeling object detection scores in applications like 3D localization (Section \ref{sec:localization}).
 We demonstrate application of our formulations for road scenes from the KITTI dataset \cite{Geiger_etal_2012}.
@@
 %\setlength\itemsep{0cm}
-\item A novel theoretical model for handling occlusions that is continuous and 3D.
+\item A novel theoretical model for handling occlusions that is continuous and formulated in 3D.
 \item Unified occlusion handling in various applications, such as 3D points in SFM and bounding boxes in object detection.

### 2015-11-06 CVPR16/Source/related.tex
small changes in Intro & Related Work

@@
 Occlusions have also been handled in tracking-by-detection frameworks by considering occluder patterns in the image \cite{Kwak_etal_2012,Wu_Nevatia_2007}.
-A notable exception is the work of Milan et al.~\cite{Milan_etal_2014} that explicits models occlusion in the continuous domain to determine a visibility for each object in multi-target tracking.
+A notable exception is the work of Milan et al.~\cite{Milan_etal_2014} that explicitly models occlusion in the continuous domain to determine a visibility for each object in multi-target tracking.
 However, the occlusion model in \cite{Milan_etal_2014} is essentially the overlap of image projections of a Gaussian representation of the object.
@@
 %\cite{Tron_Vidal_2007,Rao_etal_2010}. This also motivates further applications such as object segmentation based on point trajectories \cite{Brox_Malik_2010}. 
-Closer to our application, motion segmentation is also used within multibody structure from motion (SFM) frameworks \cite{Ozden_etal_2010,Kundu_etal_2011,Namdev2012}.
+Closer to our application, motion segmentation is also used within multibody SFM frameworks \cite{Ozden_etal_2010,Kundu_etal_2011,Namdev2012}.
 In contrast to these works, our formulation does not distinguish between moving and static objects and also explicitly reasons about occlusions due to 3D object geometries for associating point tracks to individual objects.
@@
 %For instance, using stereo imagery, several visual cues are combined in \cite{Geiger_etal_2014} to simultaneously determine object locations and a rough intersection topology. 
-Monocular frameworks like ours have also reasoned about occlusions, for instance, \cite{Wojek_etal_2013} consider partial object detectors.
+Monocular frameworks like ours have also reasoned about occlusions, for instance, \cite{Wojek_etal_2013} considers partial object detectors.
 A detailed part-based representation of objects based on annotated CAD models is used for monocular scene understanding in \cite{Zia_etal_2013,Zia_etal_2014}, which also allows reasoning about mutual occlusions between objects.

### 2015-11-06 CVPR16/Source/occlusion.tex
Section 3

@@
-In this section, we introduce our representation of 3D traffic participants and our modeling of object-object occlusion relationships.
+\section{Continuous Occlusion Model}
+\label{sec:setup}
+
+%We want to solve the problem of segmenting point tracks into object so that the consensus of points can be used draw inferences about the object.
+In particular given a set of correspondence points on consecutive frames $(\trackpj{t}, \trackpj{t-1})$, object localizations $\relp{i}{t}$ and object dimensions $\dimsn{i}$ we want to figure out which points belong to which object.
+We call this the association problem.
+Even if the pose of the object is not immediately available we propose the use of hypothesized pose of the object as we show in the localization estimation experiments.
+
+\def\TP{TP}
+A common parametric modeling for objects, especially traffic participants (TP) in road scene understanding, is as opaque cuboids.\footnote{Notable exceptions exist, such as \cite{Zia_etal_2014}, but we note that such models are expensive, application-specific and still discontinuous.} However such models introduce discontinuities in the problem formulation and do not adequately account for uncertainties in pose and dimensions.
+With this motivation, we introduce our representation of 3D objects and our modeling of object-object relationships, which lead to a continuous occlusion model that correctly accounts for uncertainties in position and dimensions.
+We refer the reader to Figure~\ref{fig:reflectiontransimission} for an illustration of the proposed concepts.
+
+%In this section, we introduce our representation of 3D objects and our modeling of object-object occlusion relationships.
 We refer the reader to Figure~\ref{fig:reflectiontransimission} for an illustration of the proposed concepts.
@@
 We model the uncertainty in occupancy as a translucency function, with regions more likely to be occupied by an object considered more opaque, while regions more likely to be free space are more transparent.
-Based on this intuition, we model objects as translucent 3D ellipsoids whos opacity is maximum at the center and falls off towards the edges.
-In particular, we model the occupancy at location $\bx$ corresponding to a traffic participant $i$ centered at $\pos{i}{t}$ as:
+Based on this intuition, we model objects as translucent 3D ellipsoids whose opacity is maximum at the center and falls off towards the edges.
+In particular, we model the occupancy at 3D location $\bx$ corresponding to an object $i$ centered at $\pos{i}{t}$ as:
 \begin{align}
@@
 We set $k = 10\ln{49}$ as the value that allows the logistic function $\cL$ to drop to $0.98$ at a distance $d = 0.9$ from the object center.
-The spread of the ellipsoid, determined by $\bSigma_i$, depends of the dimensions of the traffic participant.
-Please refer to the supplementary material for computation of $\bSigma_i$ from object dimensions.
+The spread of the ellipsoid, determined by $\bSigma_i$, depends of the dimensions of the object.
+Please refer to the supplementary material for the computation of $\bSigma_i$ from object dimensions.
 
@@
 Consider a 3D point $\bx_j$ observed in the image at pixel $\bu_j$.
-Let the image was formed using camera with intrinsic matrix $\bK$.
-Let $\ray = \frac{\bK^{-1}\bu_j}{\lVert \bK^{-1}\bu_j \rVert}$ be the corresponding unit vector along the backprojected ray from the camera center.
-Then, the probability of reflection at depth $\lambda$ along the ray $\ray$, by an object $O_i$, is determined by the object's gradient of the occupancy function $f_{occ}^i$:
+Let $\bK$ be the intrinsic calibration matrix for the camera and $\ray = \displaystyle\frac{\bK^{-1}\bu_j}{\lVert \bK^{-1}\bu_j \rVert}$ be the unit vector along the backprojected ray from the camera center passing through $\bu_j$.
+Then, the probability of reflection at depth $\lambda$ along the ray $\ray$, by an object $O_i$, is determined by the gradient of the object's occupancy function $f_{occ}^i$:
 \begin{align}
@@
 \end{align}
-The $\max \{ \}$ ensures that the negative probability due to gradient in the direction opposite to ray is clipped off and squaring the function allows it to be smooth near zero.
-We note that in the extreme case of an object being lambertial, the above reverts to a (squared) Lambertian reflection.
+The $\max \{ \}$ ensures that the negative probability due to gradient in the direction opposite to the ray is clipped off and squaring the function allows it to be smooth near zero.
+We note that in the extreme case of an object being Lambertian, the above reverts to a (squared) Lambertian reflection.
 
@@
 \label{sec:ptransmission}
-Since we are modeling occupancy as transparency, we look towards optics for modeling of translucent objects.
-A model for transmission of light through a material of thickness $\alpha$, density $\rho$ and opacity $\beta$ is given by the Beer-Lambert Law:
+Since we are modeling occupancy as transparency, we derive inspiration from optics for the modeling of translucent objects.
+A model for transmission of light across a distance $\alpha$, through a medium of density $\rho$ and opacity $\beta$ is given by the Beer-Lambert Law:
 \begin{align}
-I(x) = I_0 e^{-\beta\rho\alpha}.
+I(\alpha) = I_0 e^{-\beta\rho\alpha}.
 \end{align}
 %
-In our formulation of scene occupancy, both opacity and density at a scene point $\bx_j$ are encapsulated within the total occupancy function $\occftot = \sum_i \occf$.
+In our formulation of scene occupancy, both opacity and density at a scene point $\bx_j$ are encapsulated within the total occupancy function summer over all objects, $\occftot = \sum_i \occf$.
 Further, the domain of our ocupancy function $\occftot$ is $[0, 1]$ instead of $[0, \infty)$ for opacity $\beta$.
@@
 %
-For an image point $\bu_j$ to correspond to a 3D point $\bx_j$ at depth $\lambda$ along the backprojected ray $\ray$, the ray must be transmitted through space with the probability
+Thus, for an image point $\bu_j$ to correspond to a 3D point $\bx_j$ at depth $\lambda$ along the backprojected ray $\ray$, the ray must be transmitted through space with the probability
 \begin{align}
-P^j_{\textit{transmission}}(\lambda) = \prod_{f}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda},
+P^j_{\textit{transmission}}(\lambda) = \prod_{c}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda}.
 \label{eq:ptrans-integral}
 \end{align}
-where $\displaystyle\prod_{f}^{\lambda}$ represents the \emph{product integral} from $f$ to $\lambda$ and $f$ is the position of camera screen which has been taken equivalent to focal length of the camera .\footnote{A product integral is a simple integral in log domain:
+Here, $\prod_{c}^{\lambda}$ represents a \emph{product integral} from $c$ to $\lambda$, where $c$ is the position of camera screen, considered here to be equivalent to the focal length of the camera .\footnote{A product integral is a simple integral in the log domain:
 \vspace{-0.2cm}
 \begin{equation}
-\prod_{f}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} = e^{\int_{f}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}. \nonumber
+\prod_{c}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} = e^{\int_{c}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}. \nonumber
 \end{equation}
@@
 %
-where $\cL_u(.)$ is sigmoid in image domain, with $\bmu^i_u$ and $\bGamma_i$ representing the elliptical projection of object $O_i$ in the image and $\cL_{\lambda}(.)$ is sigmoid in the depth domain with $\meandepth{i}$ the mean depth of object $O_i$.
+where $\cL_u(.)$ is sigmoid in image domain, with $\bmu_i$ and $\bGamma_i$ representing the elliptical projection of object $O_i$ in the image and $\cL_{\lambda}(.)$ is sigmoid in the depth domain with $\meandepth{i}$ the mean depth of object $O_i$.
 That is,
@@
 %
-We compare the exact and relative formulation of transmission probability in
-Fig~\ref{fig:compare:exact:approx:ptrans}. Note that the choice of mean depth
-of object causes deviation from the exact transmission probability. However,
-the computation of ray intersection with ellipsoid is expensive to compute for 
-every ray and the shift of transmission probability anywhere through the object 
-is a reasonable approximation as the occluded points can only lie outside the
-object.
+In Figure \ref{fig:compare:exact:approx:ptrans}, we compare the exact and relative formulations of transmission probability given by \eqref{eq:ptrans-integral} and \eqref{eq:evalCumulativePtrans}, respectively.
+Note that the choice of mean depth of the object causes some deviation from the exact transmission probability.
+However, the shift of transmission probability anywhere through the object is still a reasonable approximation as occluded points can only lie outside the object.
+On the other hand, it yields significant computational savings since ray intersections with an ellipsoid are expensive to evaluate densely.
+
+%the computation of ray intersection with ellipsoid is expensive to compute for every ray and the shift of transmission probability anywhere through the object is a reasonable approximation as the occluded points can only lie outside the object.
 
@@
 
-Thus, we have modeled the transmission probability to effectively capture the
-effect of occlusion due to all traffic participants in a scene that lie along a
-particular ray. We reiterate that our reflection and transmission probabilities
-are continuous functions, which allows us to keep the problem formulation in
-continuous domain allowing for easier optimization.
+Thus, we have modeled the transmission probability to effectively capture the effect of occlusion due to all traffic participants in a scene that lie along a particular ray.
+We reiterate that our reflection and transmission probabilities are continuous functions, which allows us to keep the problem formulation in the continuous domain.
+% allowing for easier optimization.

### 2015-11-06 CVPR16/Source/applications.tex
Section 4 edits

@@
 \label{sec:association}
+
+Consider the problem of assigning 2D point tracks among several objects (including background), so that the consensus of points can be used draw inferences about the object.
+In particular given a set of corresponding 2D points $\trackpj{t-1}$ and $\trackpj{t}$ in consecutive frames, object poses $\relp{i}{t}$ and object dimensions $\dimsn{i}$, we wish to associate points with various objects.
+We call this the association problem.
+Even if the pose of the object is not immediately available, we propose the use of hypothesized pose of the object as we show in the localization estimation experiments.
 

### 2015-11-06 CVPR16/Source/applications.tex
Edit Section 4.1

@@
 
-Based on our continuous occlusion model in Section~\ref{sec:setup}, the association probability $\assocP$ of the $j$\textsuperscript{th} point track with $i$\textsuperscript{th} object at depth $\lambda$ can be defined as
+Based on our continuous occlusion model in Section~\ref{sec:setup}, the association probability $\assocP$ between point track $j$ and object $i$ at depth $\lambda$ can be defined as
 \begin{align}
@@
 To compute the association probability $\assocP$ between point track $j$ and object $i$, we must use the reprojection error as well.
-When the association of $i$ and $j$ is correct and the point of reflection is at depth $\lambda$, the reprojection error must be zero \eqref{eq:reprojerror}, otherwise the error becomes a measure of distance from the true solution.
+When the association of point track $j$ and object $i$ is correct and the point of reflection is at depth $\lambda$, the reprojection error must be zero \eqref{eq:reprojerror}, otherwise the error becomes a measure of distance from the true solution.
 The error term can be converted to probability domain by considering the error term as negative log of probability
 \begin{align}
-  P^{(ij)}_{\text{assoc by reproj}}(\lambda) = \frac{1}{Z}\exp(-\Ereproj(\lambda))
+  P^{ij}_{\text{assoc by reproj}}(\lambda) = \frac{1}{Z}\exp(-\Ereproj(\lambda))
 \end{align}
 
-Using both of the above evidence terms we can write the probability of association $P^{(ij)}_{\text{assoc}}$ as follows
+Using both of the above evidence terms we can define the new association probability $P^{ij}_{\text{assoc}}$ as follows
 \begin{align}
-  P^{(ij)}_{\text{assoc}} = \frac{1}{Z'}\int_0^{\infty} \assocP \exp(-\Ereproj(\lambda))d\lambda
+  P^{ij}_{\text{assoc}} = \frac{1}{Z'}\int_0^{\infty} \assocP \exp(-\Ereproj(\lambda))d\lambda
   \label{eq:prob-assoc}
 \end{align}
-Once we have the probability of association $P^{(ij)}_{\text{assoc}}$ we can compute the best possible assignment of object for each point track.
-The points having very small association probability are assigned to the background,
-\begin{align}
-  i^*_{j} = \arg \min_{i} \int_0^\infty \assocP \Ereproj(\lambda) d\lambda
-\end{align}
+Once we have the association probability $P^{ij}_{\text{assoc}}$ we can compute the best possible assignment of object for each point track.
+The points having very small association probabilities are assigned to the background.
 

### 2015-11-06 CVPR16/Source/applications.tex
Section 4 edits

--- 2015-11-06 CVPR16/Source/applications.tex
@@
 
-To show the effectiveness of our method we apply it to the localization
-problem. We estimate the position, orientation and dimensions of the car with
-our framework and compute the error in birds eye view domain along the ground
-plane. 
+%To show the effectiveness of our method we apply it to the localization problem.
+We estimate the position, orientation and dimensions of the car with our framework and compute the error in birds eye view domain along the ground plane.
 To estimate the localization of traffic participants (TPs) in a road scene we use the graphical model approach.
-We build the graphical model as shown in Fig~\ref{fig:graphmodel} that 
-allows us to factorize the intractable probability distribution into following form
+We build the graphical model as shown in Fig~\ref{fig:graphmodel} that allows us to factorize the intractable probability distribution into following form
+
+To show the effectiveness of our method we also apply it to the localization problem, where we must jointly solve for association and object poses, while considering occlusions.
+In road scenes, we estimate the position, orientation and dimensions traffic participants (cars) with our framework and compute the error in birds eye view along the ground plane.
+We propose a graphical model as shown in Figure \ref{fig:graphmodel} that allows a factorization of the intractable probability distribution into following form
 %
@@
 Next, we explain the important energies used in our graphical model.
+
+\begin{figure}
+  \centering
+  \begin{tabular}{c}
+    \newcommand{\imagewidth}{7cm}
+    \input{Source/scenelayoutoverlayCity0961} \\
+    \input{Source/graphical_model_multiple}
+  \end{tabular}
+  \caption{\small (Top) A sample road scene with occlusions, where the unknowns of each car are modeled as random variables.
+(Bottom) Graphical model for a single frame.
+The six numbered nodes represent the unknown state variables of each car.
+The shaded nodes in the graphical model are observed variables (detection bounding boxes and point tracks), while the colored squares represent various energies that capture object-object interactions.}
+  \label{fig:graphmodel}
+\end{figure}
 
@@
 
-\begin{figure}
-  \centering
-  \newcommand{\imagewidth}{\columnwidth}
-  \input{Source/scenelayoutoverlayCity0961}
-  \caption{A sample road scene with the unknowns of each car modeled as random variables. 
-  The relating energies are shown in Figure~\ref{fig:graphmodel}}
-\end{figure}
-\begin{figure}
-    \input{Source/graphical_model_multiple}
-    \caption{Graphical model for a single frame with state of car represented
-    as single node.  The six numbered nodes represent the unknown state variables of each car. The shaded nodes in the graphical model are observed variables. }
-  \label{fig:graphmodel}
-\end{figure}
+%% \begin{figure}
+%%   \centering
+%%   \newcommand{\imagewidth}{\columnwidth}
+%%   \input{Source/scenelayoutoverlayCity0961}
+%%   \caption{A sample road scene with the unknowns of each car modeled as random variables. 
+%%   The relating energies are shown in Figure~\ref{fig:graphmodel}}
+%% \end{figure}
+%% \begin{figure}
+%%     \input{Source/graphical_model_multiple}
+%%     \caption{Graphical model for a single frame with state of car represented
+%%     as single node.  The six numbered nodes represent the unknown state variables of each car. The shaded nodes in the graphical model are observed variables. }
+%%   \label{fig:graphmodel}
+%% \end{figure}

### 2015-11-06 CVPR16/Source/applications.tex
Section 4 edits
changes in Sec 3 and 4.1

@@
 
-In this section, we highlight the versatility of our occlusion modeling by demonstrating its unified application to two different problems: associating point tracks with objects and 3D object localization using object and point tracks.
+In this section, we highlight the versatility of our occlusion modeling by demonstrating its unified application to two different problems: associating point tracks with objects and 3D object localization using objects and point tracks.
 
@@
 
-Consider the problem of assigning 2D point tracks among several objects (including background), so that the consensus of points can be used draw inferences about the object.
-In particular given a set of corresponding 2D points $\trackpj{t-1}$ and $\trackpj{t}$ in consecutive frames, object poses $\relp{i}{t}$ and object dimensions $\dimsn{i}$, we wish to associate points with various objects.
+%Given a set of corresponding 2D points $\trackpj{t-1}$ and $\trackpj{t}$ in consecutive frames, object poses $\relp{i}{t}$ and object dimensions $\dimsn{i}$, we wish to associate points with various objects.
 We call this the association problem.
@@
 
-Based on our continuous occlusion model in Section~\ref{sec:setup}, the association probability $\assocP$ between point track $j$ and object $i$ at depth $\lambda$ can be defined as
+Given 2D image points $\bu_j$ which are tracked between consecutive frames and a set of objects $O_i$ appearing in the frames, we aim to associate $\bu_j$ with $O_i$.
+Based on our continuous occlusion model in Section~\ref{sec:setup}, the association probability $\assocP$ between point track $\bu_j$ and object $O_i$ at depth $\lambda$ can be defined as
 \begin{align}
@@
 Note that the fraction $\assocP$ although called association probability does not capture the entire information that we have available for computing association of point tracks to objects.
-This above fraction is the association probability given the hypothesized parameters of objects in the scene.
 
-To compute the association probability $\assocP$ between point track $j$ and object $i$, we must use the reprojection error as well.
-When the association of point track $j$ and object $i$ is correct and the point of reflection is at depth $\lambda$, the reprojection error must be zero \eqref{eq:reprojerror}, otherwise the error becomes a measure of distance from the true solution.
-The error term can be converted to probability domain by considering the error term as negative log of probability
+To compute the association probability between point track $\bu_j$ and object $O_i$, we should also use the reprojection error.
+When the association of point track $\bu_j$ and object $O_i$ is correct and the point of reflection is at depth $\lambda$, the corresponding reprojection error $\Ereproj(\lambda)$ must be zero \eqref{eq:reprojerror}, otherwise the error becomes a measure of distance from the true solution.
+The error $\Ereproj(\lambda)$ can be used for associating point tracks and objects by converting it to the probability domain as
 \begin{align}
-  P^{ij}_{\text{assoc by reproj}}(\lambda) = \frac{1}{Z}\exp(-\Ereproj(\lambda))
+  P^{ij}_{\text{reproj}}(\lambda) = \frac{1}{Z}\exp(-\Ereproj(\lambda)),
+\label{eq:Passocbyreproj}
 \end{align}
+where $Z$ is the normalization coefficient.
 
-Using both of the above evidence terms we can define the new association probability $P^{ij}_{\text{assoc}}$ as follows
+Using both of the evidence terms in \eqref{eq:defineassocP} and \eqref{eq:Passocbyreproj}, we can define the new association probability $P^{ij}_{\text{assoc}}$ as follows
 \begin{align}
-  P^{ij}_{\text{assoc}} = \frac{1}{Z'}\int_0^{\infty} \assocP \exp(-\Ereproj(\lambda))d\lambda
+  P^{ij}_{\text{assoc}} = \frac{1}{Z'}\int_0^{\infty} \assocP \exp(-\Ereproj(\lambda))d\lambda,
   \label{eq:prob-assoc}
 \end{align}
-Once we have the association probability $P^{ij}_{\text{assoc}}$ we can compute the best possible assignment of object for each point track.
-The points having very small association probabilities are assigned to the background.
+where $Z'$ is the new normalization coefficient.
 
-In contrast to the principled approach above, a heuristic baseline may simply assign a point to the detection bounding box enclosing it (and background if outside all bounding boxes).
-For regions where bounding boxes overlap, it may assign point tracks to the object that has smaller mean depth among the competing bounding boxes.
-As we will demonstrate in experiments, such heuristics are sub-optimal compared to using \eqref{eq:prob-assoc} inspired by our occlusion model.
+Once we have computed the association probability $P^{ij}_{\text{assoc}}$ for every pair of point tracks and objects, we can assign each point track to the object with the highest association probability.
+The point tracks having very small association probabilities are assigned to the background.
+
+In contrast to the principled approach above, a heuristic baseline may simply assign a point track to the detection bounding box enclosing it (and background if outside all bounding boxes).
+For regions where bounding boxes overlap, it may assign point tracks to the object that has the smallest mean depth among the competing bounding boxes.
+As we will demonstrate in the experiments, such heuristics are sub-optimal compared to using \eqref{eq:prob-assoc} inspired by our occlusion model.
 
@@
   \begin{tabular}{c}
-    \newcommand{\imagewidth}{7cm}
+    \newcommand{\imagewidth}{7.5cm}
     \input{Source/scenelayoutoverlayCity0961} \\

### 2015-11-06 CVPR16/Source/applications.tex
consistent symbols
Addressed Surens comments.

@@
 \begin{equation}
-S(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{(i)}(t)^\top \Lambda_k^{'-1} \bepsilon_k^{(i)}(t) \right)
+S(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \Lambda_k^{'-1} \bepsilon_k^{i}(t) \right)
 \end{equation}
-where $A_k$ is an amplitude and $\bepsilon_k^{(i)}(t) = \bb{i}-\mu^{(k)}_d$, with $\mu^{(k)}_d$ the mean and $\Lambda_k$ the covariance.
+where $A_k$ is an amplitude and $\bepsilon_k^{i}(t) = \bb{i}-\mu^{k}_d$, with $\mu^{k}_d$ the mean and $\Lambda_k$ the covariance.
 %% %
@@
 $O_{i}(\mathbf{u}, \meandepth{i})$ at the hypothesized detection boundaries from
-GMM $S(.)$ and we augment the detection boundary covariance matrix by
+detection score function $S(.)$ and we augment the detection boundary covariance matrix by
 $\mathcal{P}_{i} = \rho_{i}\rho_{i}^\top$ where $\rho_{i} = O_{i}(\mathbf{u},
@@
   $\Lambda'_k = \mathcal{P}_{i} + \Lambda_k$ for all $k$.
-The detection scores GMM with occlusion is given by replacing the covariance
+The detection scores function with occlusion is given by replacing the covariance
 matrix
@@
 \begin{multline}
-S'(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{(i)}(t)^\top \Lambda_k^{'-1} \bepsilon_k^{(i)}(t) \right)
+S'(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \Lambda_k^{'-1} \bepsilon_k^{i}(t) \right)
 \end{multline}
@@
 For object detections we use object detector by \cite{Felzenszwalb_etal_2010}
-which is detector by parts model and we use eight parts to train the car model 
-on half of the KITTI dataset \cite{geiger2013vision}. The trained modeled is 
+which uses a detector by parts model and we use eight parts to train the car model 
+on half of the KITTI dataset \cite{geiger2013vision}. The trained model is 
 used to get detections for the other half of the dataset and vice versa.

### 2015-11-06 CVPR16/Source/related.tex
Addressed Surens comments.

@@
 Occlusion reasoning based on 2D image silhouettes is used to improve detection performance in \cite{Hsiao_Herbert_2012}.
-In contrast, our occlusion reasoning is based on 3D entities.
+On the other hand our occlusion reasoning is based on 3D entities.
 In recent years, object detectors have also considered occlusion reasoning using 3D cues, often learned from a dataset of CAD models \cite{Pepik_etal_2012,Pepik_etal_2013,Xiang_Savarese_2013}.
 By necessity, such frameworks are often a discrete representation of occlusion behavior, for example, in the form of a collection of occlusion masks derived from object configurations discretized over viewpoint.
-In constrast to these works, our occlusion modeling is also fully 3D, but allows for a continuous representation.
+In contrast to these works, our occlusion modeling is also fully 3D, but allows for a continuous representation.
 Further, to derive 3D information, we do not use CAD models, rather we derive a probabilistic formulation based on physical insights.
@@
 Some recent efforts include robust algebraic segmentation with hybrid perspective constraints \cite{Rao_etal_2010} and spectral clustering with point track spatial affinities \cite{Brox_Malik_2010}.
-In contrast to our modeling, such methods cannot handle static objects, or dynamic objects with little relative motion.
+Unlike our work, such methods cannot handle static objects, or dynamic objects with little relative motion.
 %\cite{Tron_Vidal_2007,Rao_etal_2010}. This also motivates further applications such as object segmentation based on point trajectories \cite{Brox_Malik_2010}. 

### 2015-11-06 CVPR16/Source/applications.tex
edit Sec 4

--- 2015-11-06 CVPR16/Source/applications.tex
@@
 
-Given 2D image points $\bu_j$ which are tracked between consecutive frames and a set of objects $O_i$ appearing in the frames, we aim to associate $\bu_j$ with $O_i$.
+Given 2D image points $\{\bu_j\}$ which are tracked between consecutive frames and a set of objects $\{O_i\}$ appearing in the frames, we aim to associate $\bu_j$ with $O_i$.
 Based on our continuous occlusion model in Section~\ref{sec:setup}, the association probability $\assocP$ between point track $\bu_j$ and object $O_i$ at depth $\lambda$ can be defined as
@@
 
-To show the effectiveness of our method we also apply it to the localization problem, where we must jointly solve for association and object poses, while considering occlusions.
+%To show the effectiveness of our method we also apply it to the localization problem, where we must jointly solve for association and object poses, while considering occlusions.
 In road scenes, we estimate the position, orientation and dimensions traffic participants (cars) with our framework and compute the error in birds eye view along the ground plane.
 We propose a graphical model as shown in Figure \ref{fig:graphmodel} that allows a factorization of the intractable probability distribution into following form
+
+We exploit in this section the application of our continuous occlusion model to 3D localization in road scenes, which further demonstrates its versatility.
+Given a set of tracked feature points $\{\bu_j(t)\}$ and 2D detection bounding boxes $\{\bb{i}\}$ at frame $t$, the goal is to localize 3D traffic participants (TPs), in particular, for each TP, estimating its position $\bp^i(t)$ and orientation $\bomega^i(t)$ on the ground plane and its 3D dimensions $\bB^i(t)$.
+We build a graphical model for representing object relationships and decompose the negative log likelihood as follows
 %
 \begin{multline}
-  -\log{P(\{\state{i}{t}\} | \mathbb{E})} = 
-  -Z' 
+  -\log{P(\{ \bp^i(t) , \bomega^i(t) , \bB^i(t) \} | \{\bu_j(t)\} , \{\bb{i}\} )} = \\
+  -Z 
+   + \sum_{t=s_i}^{e_i} \WpEnergy{track}
   \\
-  + \sum_{t=s_i}^{e_i}
+  + 
+  \sum_{t=s_i}^{e_i}
+  \sum_{i=1}^N  
   \left( 
-  \sum_{i,j:i\ne j}   
-  \WEnergyCol 
-   + \WpEnergy{detect}
-   + \WpEnergy{track}
-\right)
-  \\
-  + \left(
-  \sum_{i=1}^N 
-  \WEnergy{lane}
+  \WEnergy{detect}
   + \WEnergy{dyn}
@@
 \right)
-  \enspace.
+  \enspace,
 \end{multline}
 %
-Next, we explain the important energies used in our graphical model.
+where $\pEnergy{track}$ and $\Energy{detect}$ reason about image observations such as point tracks and bounding boxes while $\Energy{dyn}$  and $\Energy{size}$ impose smoothness constraints and size priors respectively.
+Here, $\lambda_{track}$, $\lambda_{detect}$, $\lambda_{dyn}$, $\lambda_{size}$ are energy weights and $Z$ is the normalization coefficient.
+Figure~\ref{fig:graphmodel} illustrates an example of the graph and energies.
+Next, we present our unified continuous occlusion modelling for point track and bounding box energies; please refer to our supplementary material for the formulations of other energies.
 
@@
 
-Let the pose of object $i$ at time $t$ be $\relp{i}{t}$.
+Let $\relp{i}{t}$ be the pose of object $O_i$ with respect to the camera at time $t$.
 We denote $\projectionOf{.}$ and $\invProjectionOftm{.}$ for the forward and inverse projection functions that project a 3D point to the camera image and vice versa.
-Then, the reprojection error for the $j$\textsuperscript{th} 2D point, $\trackp{t}$, with hypothesized depth $\lambda$, is given by
+Then, the reprojection error for the 2D point $\trackp{t}$ with hypothesized depth $\lambda$, is given by
 \begin{equation}
@@
   %\Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = 
-  \Energy{track}(\{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i )
+  \pEnergy{track}(\{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i )
   \\
@@
 \end{multline}
-where $\assocP$ is the association probability of the $j$\textsuperscript{th} point with the $i$\textsuperscript{th} object at depth $\lambda$, given by \eqref{eq:defineassocP}.
+where $\assocP$ is the association probability of point $\trackp{t}$ with the object $O_i$ at depth $\lambda$, given by \eqref{eq:defineassocP}.
 
@@
 To retain the entire detection output while maintaining the continuous form of our energies, we approximate the distribution of detection scores with a multi-modal sum of Gaussians-like logistic functions.
-In particular, let $\bb{i}$ be a detection bounding box for object $i$, parameterized as a 4D vector $[\minx, \miny, \maxx, \maxy]^\top$.
+In particular, let $\bb{i}$ be parameterized as a 4D vector $[\minx, \miny, \maxx, \maxy]^\top$.
 We fit a parametric function to the detection scores, of the form
 \begin{equation}
-S(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{(i)}(t)^\top \Lambda_k^{'-1} \bepsilon_k^{(i)}(t) \right)
+S(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \Lambda_k^{'-1} \bepsilon_k^{i}(t) \right)
 \end{equation}
-where $A_k$ is an amplitude and $\bepsilon_k^{(i)}(t) = \bb{i}-\mu^{(k)}_d$, with $\mu^{(k)}_d$ the mean and $\Lambda_k$ the covariance.
+where $A_k$ is an amplitude and $\bepsilon_k^{i}(t) = \bb{i}-\mu^{k}_d$, with $\mu^{k}_d$ the mean and $\Lambda_k$ the covariance.
 %% %
@@
 
-For object detections we use object detector by \cite{Felzenszwalb_etal_2010}
-which is detector by parts model and we use eight parts to train the car model 
-on half of the KITTI dataset \cite{geiger2013vision}. The trained modeled is 
-used to get detections for the other half of the dataset and vice versa.
+%For object detections we use object detector by \cite{Felzenszwalb_etal_2010} which is detector by parts model and we use eight parts to train the car model on half of the KITTI dataset \cite{geiger2013vision}.
+The trained modeled is used to get detections for the other half of the dataset and vice versa.
 
-\subsubsection{Other energies}
-Other energies we use are described in detail in the supplementary material. We briefly describe them here:
-\begin{description}
-  \item[Lane energy ($\Energy{lane}$)] This energy term constrains the
-    orientation of traffic participants to be parallel to the nearest detected
-    lane. The lanes are either detected visually or obtained from GPS and Map 
-    information.
-  \item[Transition probability ($\Energy{dyn}$)] We use these energies to
-    constrain the motion of cars to be smooth in linear motion and rotation
-    motion. We also constrain cars to move in the direction of heading.
-  \item[Size prior ($\EnergySize$)] We use size prior of cars by using the mean
-    of cars over the KITTI dataset.
-\end{description}
+%\subsubsection{Other energies}
+%Other energies we use are described in detail in the supplementary material. We briefly describe them here:
+%\begin{description}
+  %\item[Lane energy ($\Energy{lane}$)] This energy term constrains the orientation of traffic participants to be parallel to the nearest detected lane.
+The lanes are either detected visually or obtained from GPS and Map information.
+  %\item[Transition probability ($\Energy{dyn}$)] We use these energies to constrain the motion of cars to be smooth in linear motion and rotation motion.
+We also constrain cars to move in the direction of heading.
+  % \item[Size prior ($\EnergySize$)] We use size prior of cars by using the mean of cars over the KITTI dataset.
+%\end{description}
 

### 2015-11-06 CVPR16/Source/abstract.tex
changes

@@
 \begin{abstract}
-This paper studies the problem of segmenting tracked feature points on multiple objects in a video sequence.
+
+We present a physically interpretable, continuous 3D model for handling occlusions with applications to road scene understanding.
+We probabilistically assign each point in space to an object with a theoretical modeling of the reflection and transmission probabilities for the corresponding camera ray.
+Our modeling is unified in handling occlusions across a variety of scenarios, such as associating structure from motion point tracks with potentially occluded objects or modeling object detection scores in applications such as 3D localization.
+For point track association, our model uniformly handles static and dynamic objects, which is an advantage over motion segmentation approaches traditionally used in multibody SFM.
+Detailed experiments on the KITTI dataset show the superiority of the proposed method over both state-of-the-art motion segmentation and a baseline that heuristically uses detection bounding boxes for resolving occlusions.
+We also demonstrate how our continuous occlusion model may be applied to the task of 3D localization in road scenes.
+
+%This paper studies the problem of segmenting tracked feature points on multiple objects in a video sequence.
 We consider scenes that contain both dynamic and static objects, which usually appear in the context of autonomous driving (e.g., moving and parked cars), and occlusions among objects.

### 2015-11-06 CVPR16/Source/experiments.tex
changes

@@
 
-In this section, we first benchmark our continuous occlusion model for point-to-object association against the baseline method using detection bounding boxes and state-of-the-art methods for motion segmentation.
+In this section, we first benchmark our continuous occlusion model for point-to-object association against the baseline method using detection bounding boxes and state-of-the-art methods for motion segmentation \cite{Rao_etal_2010,Brox_Malik_2010}.
 We then show how the proposed model benefits the task of 3D localization in autonomous driving.

### 2015-11-06 CVPR16/Source/abstract.tex
Addressed jasons comments.

--- 2015-11-05 CVPR16/Source/abstract.tex
@@
 We consider scenes that contain both dynamic and static objects, which usually appear in the context of autonomous driving (e.g., moving and parked cars), and occlusions among objects.
-We propose a novel continuous model for modeling objects so that point tracks can be probabilistically and accurately assigned to the corresponding object while accounting for object occlusions.
+We propose a novel continuous model for representing objects so that point tracks can be probabilistically and accurately assigned to the corresponding object while accounting for object occlusions.
 Detailed experiments on the KITTI dataset show the superiority of the proposed method over the baseline method which simply uses detection bounding boxes for resolving occlusions and the state-of-the-art motion segmentation methods which cannot cope well with static objects.
-As a notable application, we show how our continuous occlusion model benefits the task of 3D localization in autonomous driving.
+We apply our continuous occlusion model to task of 3D localization in autonomous driving and show improvements in results.
 \end{abstract}

### 2015-11-06 CVPR16/Source/experiments2.tex
Added more comments about the experiments.
Addressed jasons comments.

@@
 
-In this section, we first benchmark our continuous occlusion model for point-to-object association against the baseline method using detection bounding boxes and state-of-the-art methods for motion segmentation.
+In this section, we first benchmark our continuous occlusion model for point-to-object association against a baseline method that uses detection bounding boxes and state-of-the-art methods for motion segmentation.
 We then show how the proposed model benefits the task of 3D localization in autonomous driving.
@@
 $\Ptransmission$. Similarly, $\EnergyBBoxNoOcc$ is the energy without the
-modification of $\bSigma$ that accounts for occlusion.  The results show that
+modification of $\Sigma^{(d)}_j$ that accounts for occlusion.  The results show that
 use of continuous occlusion model improves the localization accuracy in terms

### 2015-11-06 CVPR16/Source/intro.tex
Addressed jasons comments.

@@
 This allows assigning probabilities for each point in space belonging to an object, which can explicitly explain image observations and reason about occlusions.
-This is in contrast to prior works that consider occlusions in 2D, or through discrete occluder patterns that are not physically interpretable.
+This is in contrast to prior works that consider occlusions in 2D, either through discrete occluder patterns or models that are not physically interpretable.
 

### 2015-11-06 CVPR16/Source/experiments.tex
changes

@@
 In this section, we first benchmark our continuous occlusion model for point-to-object association against the baseline method using detection bounding boxes and state-of-the-art methods for motion segmentation \cite{Rao_etal_2010,Brox_Malik_2010}.
-We then show how the proposed model benefits the task of 3D localization in autonomous driving.
-For our experiments, we use the KITTI dataset~\cite{geiger2013vision}, which consists of video sequences of road scenes under a variety of driving conditions including highways and residential areas.
-It also provides ground truth data for different tasks such as segmentation, detection, tracking and 3D localization.
+We then show how the proposed model may be applied for 3D localization in road scenes.
+For our experiments, we use the KITTI dataset~\cite{geiger2013vision}, which consists of video sequences of road scenes under a variety of driving conditions.
+%It also provides ground truth data for different tasks such as segmentation, detection, tracking and 3D localization.
 

### 2015-11-06 CVPR16/Source/experiments2.tex
changes

@@
-\section{Experimental results}
+\section{Experiments}
 \label{sec:experiments}
 
-In this section, we first benchmark our continuous occlusion model for point-to-object association against a baseline method that uses detection bounding boxes and state-of-the-art methods for motion segmentation.
-We then show how the proposed model benefits the task of 3D localization in autonomous driving.
-For our experiments, we use the KITTI dataset~\cite{geiger2013vision}, which consists of video sequences of road scenes under a variety of driving conditions including highways and residential areas.
-It also provides ground truth data for different tasks such as segmentation, detection, tracking and 3D localization.
+In this section, we benchmark our continuous occlusion model for point-to-object association against the baseline method using detection bounding boxes and state-of-the-art methods for motion segmentation \cite{Rao_etal_2010,Brox_Malik_2010}.
+We then show how the proposed model may be applied for 3D localization in road scenes.
+For our experiments, we use the KITTI dataset~\cite{geiger2013vision}, which consists of video sequences of road scenes under a variety of driving conditions.
+%It also provides ground truth data for different tasks such as segmentation, detection, tracking and 3D localization.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Association experiment}
 
-We first perform the association experiment that compares the accuracy of point-to-object association using the proposed model against those of the detection bounding box baseline method (BBox) and state-of-the-art motion segmentation methods, namely robust algebraic segmentation with hybrid perspective constraints (RAS)~\cite{Rao_etal_2010} and spectral clustering with point track spatial affinity (BM)~\cite{Brox_Malik_2010}.
+\subsection{Association Experiments}
+
+\vspace{-0.4cm}
+\paragraph{Setup}
+
+We first perform the association experiment that compares the accuracy of point-to-object association using our proposed model against a heuristic baseline and state-of-the-art motion segmentation methods.
+The detection bounding box baseline method (BBox) is as described at the end of Section \ref{sec:association}.
+For motion segmentation, we use robust algebraic segmentation with hybrid perspective constraints (RAS)~\cite{Rao_etal_2010} and spectral clustering with point track spatial affinity (BM)~\cite{Brox_Malik_2010}.
 
@@
 
-\subsubsection{Association results}
+For each sequence of the KITTI dataset, the methods of \cite{Felzenszwalb_etal_2010} and \cite{Choi_Savarese_2010} are used for computing detection bounding boxes and object tracklets, respectively.
+We then apply \cite{Zach2007} to extract point tracks.
+Note that our method can handle occlusions in both static and dynamic scenes, but motion segmentation focuses on dynamic scenes.
+For a complete evaluation, we create organize the point tracks into four sets: all point tracks, occluded point tracks, dynamic point tracks and dynamic as well as occluded point tracks.
+In addition to point tracks, the parameters of all objects (cars) estimated by the method of \cite{Song_Chandraker_2014} are provided to our method (for computing association probability) and the baseline BBox method (for depth ordering).
 
-For each sequence of the KITTI dataset, the methods of \cite{Felzenszwalb_etal_2010} and \cite{Choi_Savarese_2010} are used respectively for computing detection bounding boxes and object tracklets.
-We then apply \cite{Zach2007} on object tracklets to extract point tracks.
-From these point tracks, we create four different sets of input point tracks, namely all point tracks, occluded point tracks, dynamic point tracks and dynamic and occluded point tracks, to examine various aspects of the methods (our method focuses on occlusion scenes while RAS and BM favour dynamic scenes).
-In addition to point tracks, the parameters of all TPs estimated by the method~\cite{Song_Chandraker_2014} are provided to our method (for computing association probability) and the baseline method (for depth ordering).
+\vspace{-0.4cm}
+\paragraph{Results}
+Figure~\ref{fig:assoc-occ-results} shows the association errors -- the percentages of point tracks incorrectly assigned to objects -- for all methods on the four sets of input point tracks, for each sequence of the KITTI dataset.
+The mean results over all sequences are summarized in Table~\ref{tab:meanAssoc}.
+From Figure~\ref{fig:assoc-occ-results}, our method is usually the most accurate among all methods, leading to the best mean error on all sets of input point tracks in Table~\ref{tab:meanAssoc}, which is followed by the bounding box baseline method.
+This clearly shows the advantage of our continuous occlusion model over the simple baseline method for resolving occlusions.
+RAS and BM often have the highest errors in Figure~\ref{fig:assoc-occ-results}, thus, the highest mean errors on all sets of input point tracks in Table~\ref{tab:meanAssoc}.
 
-Figure~\ref{fig:assoc-occ-results} shows the association errors --- the percentages of point tracks incorrectly assigned to objects --- of all methods on four sets of input point tracks for each sequence of the KITTI dataset, while the mean results over all sequences are presented in Table~\ref{tab:meanAssoc}.
-From Figure~\ref{fig:assoc-occ-results}, our method is usually the most accurate among all methods, leading to the best mean errors on all sets of input point tracks in Table~\ref{tab:meanAssoc}, which is followed by the bounding box baseline method.
-This clearly shows the advantage of our continuous occlusion model over the simple baseline method for resolving occlusions.
-RAS and BM often have the highest errors in Figure~\ref{fig:assoc-occ-results}, and hence the highest mean errors on all sets of input point tracks in Table~\ref{tab:meanAssoc}.
+More importantly, both RAS and BM rely on motions of objects for clustering point tracks, therefore they cannot work well with static point tracks (for example, point tracks that belong to parked cars).
+This fact can be observed in Table~\ref{tab:meanAssoc}, where there are large differences in the mean errors of both methods on data containing static point tracks (rows 2 and 4) and data consisting of dynamic point tracks only (rows 1 and 3).
+In contrast, our method and the baseline method are relatively independent of object motions, resulting in smaller performance gaps.
+Further, our method also outperforms motion segmentation on dynamic objects (row 3), which shows the effect of detection bounding boxes and by a more significant margin when occlusions are present (row 1), which shows the effect of our occlusion modeling.
 
-More importantly, both RAS and BM rely on motions of objects for clustering point tracks, therefore they cannot work well with static point tracks (e.g., point tracks belong to parked cars).
-This fact can be observed in Table~\ref{tab:meanAssoc}, where there are large differences in the mean errors of both methods on data containing static point tracks (i.e., rows 2 and 4) and data consisting of dynamic point tracks only (i.e., rows 1 and 3).
-In contrast, our method and the baseline method are relatively independent of object motions, resulting in smaller performance gaps.
+Qualitative comparisons of point track associations from various methods are shown in Figure \ref{fig:qualitative}.
+We note the low errors using our occlusion model and the smooth transition of assignment across object boundaries.
 
@@
 \setlength{\tblimgwidth}{0.40\textwidth}
-\begin{table*}
+\begin{figure*}
   \centering
@@
   \end{tabular}
-  \caption{Qualitative results of the association experiment. The left column
+  \caption{\small Qualitative results of the association experiment. The left column
   shows the point track assignments to appropriate objects. Each color represents
@@
 intermediate probabilities, while the baseline method has merely 0-1 error.}
-\end{table*}
+\label{fig:qualitative}
+\end{figure*}
 

### 2015-11-06 CVPR16/Source/applications.tex
changes
Addressed jasons comments.
Added an option of enabling the square bounding box model.

@@
 
-\subsubsection{Continuous bounding box energy with occlusion}
-
-Object detection is usually followed by non-maximal suppression that results in discarding similar bounding boxes.
-When we are jointly optimizing detections with other cues, it is not usually desirable to go with a single bounding box.
-To retain the entire detection output while maintaining the continuous form of our energies, we approximate the distribution of detection scores with a multi-modal sum of Gaussians-like logistic functions.
-In particular, let $\bb{i}$ be parameterized as a 4D vector $[\minx, \miny, \maxx, \maxy]^\top$.
-We fit a parametric function to the detection scores, of the form
-\begin{equation}
-S(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \Lambda_k^{'-1} \bepsilon_k^{i}(t) \right)
-\end{equation}
-where $A_k$ is an amplitude and $\bepsilon_k^{i}(t) = \bb{i}-\mu^{k}_d$, with $\mu^{k}_d$ the mean and $\Lambda_k$ the covariance.
-%% %
-%% \begin{multline}
-%%   S(\bb{i}) = \\
-%%   \sum_k A_k \exp(-(\bb{i}-\mu^{(d)}_k)^\top \Sigma^{(d)-1}_k
-%%   (\bb{i}-\mu^{(d)}_k))
-%% \end{multline}
-%% %
-%% to detection scores, by 
-We use a non-linear solver to minimize the above, with initialization from non-maximal suppressed outputs.
-The optimization is constrained by the symmetry and positive definiteness of $\Lambda_k^{-1}$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
-%Here $\mu^{(d)}_j$ is one of the $k$ modes as a 4D vector representing a single bounding box as $[\minx, \miny, \maxx, \maxy]^\top$.
-The optimization is constrained with symmetry and positive definiteness of $\Sigma^{(d)-1}_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
-
-\paragraph{Detection scores with occlusion reasoning} 
-\def\u{\mathbf{u}}
-With our model of $\Ptrans$ described in Section \ref{sec:ptransmission}, we can
-compute the probability of a point $\u$ in the image to be occluded assuming
-the point is on object $i$ with mean depth $\meandepth{i}$ as
-\begin{align}
-  O_{i}(\u, \meandepth{i}) = 1 - \Ptransmission(\meandepth{i}, \u) \enspace .
-\end{align}
-
-If a portion of our proposed detection bounding box is known to be
-occluded, then we would like to decrease the confidence in the detection score
-about the localization of that end of the object. Assuming that the occlusion
-is often on the boundary of detection bounding boxes, we want to decrease our
-confidence on the mean detection boundaries around the occluded boundaries.
-To re-model our detection scores scaled by continuous occlusion we sample
-$O_{i}(\mathbf{u}, \meandepth{i})$ at the hypothesized detection boundaries from
-GMM $S(.)$ and we augment the detection boundary covariance matrix by
-$\mathcal{P}_{i} = \rho_{i}\rho_{i}^\top$ where $\rho_{i} = O_{i}(\mathbf{u},
-\meandepth{i})$. The new covariance matrix in detection score is given by 
-  $\Lambda'_k = \mathcal{P}_{i} + \Lambda_k$ for all $k$.
-The detection scores GMM with occlusion is given by replacing the covariance
-matrix
-%
-\begin{multline}
-S'(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \Lambda_k^{'-1} \bepsilon_k^{i}(t) \right)
-\end{multline}
-
-The energy of detection scores is simply take to be the inverse of the detection score.
-\begin{align}
-  \Energy{detect}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}
-\end{align}
-
-%For object detections we use object detector by \cite{Felzenszwalb_etal_2010} which is detector by parts model and we use eight parts to train the car model on half of the KITTI dataset \cite{geiger2013vision}.
-The trained modeled is used to get detections for the other half of the dataset and vice versa.
+\input{contBBoxModel.tex}
+%\input{Source/squareBBoxModel.tex}
 

### 2015-11-06 CVPR16/Source/contBBoxModel.tex
Added an option of enabling the square bounding box model.

\subsubsection{Continuous bounding box energy with occlusion}

Object detection is usually followed by non-maximal suppression that results in discarding similar bounding boxes. When we are jointly optimizing detections with other cues, it is not usually desirable to go with a single bounding box. To retain the entire detection output while maintaining the continuous form of our energies, we approximate the distribution of detection scores with a multi-modal sum of Gaussians-like logistic functions. In particular, let $\bb{i}$ be parameterized as a 4D vector $[\minx, \miny, \maxx, \maxy]^\top$. We fit a parametric function to the detection scores, of the form
\begin{equation}
S(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \Lambda_k^{'-1} \bepsilon_k^{i}(t) \right)
\end{equation}
where $A_k$ is an amplitude and $\bepsilon_k^{i}(t) = \bb{i}-\mu^{k}_d$, with $\mu^{k}_d$ the mean and $\Lambda_k$ the covariance.
%% %
%% \begin{multline}
%%   S(\bb{i}) = \\
%%   \sum_k A_k \exp(-(\bb{i}-\mu^{(d)}_k)^\top \Sigma^{(d)-1}_k
%%   (\bb{i}-\mu^{(d)}_k))
%% \end{multline}
%% %
%% to detection scores, by 
We use a non-linear solver to minimize the above, with initialization from non-maximal suppressed outputs. The optimization is constrained by the symmetry and positive definiteness of $\Lambda_k^{-1}$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
%Here $\mu^{(d)}_j$ is one of the $k$ modes as a 4D vector representing a single bounding box as $[\minx, \miny, \maxx, \maxy]^\top$. The optimization is constrained with symmetry and positive definiteness of $\Sigma^{(d)-1}_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.

\paragraph{Detection scores with occlusion reasoning} 
\def\u{\mathbf{u}}
With our model of $\Ptrans$ described in Section \ref{sec:ptransmission}, we can
compute the probability of a point $\u$ in the image to be occluded assuming
the point is on object $i$ with mean depth $\meandepth{i}$ as
\begin{align}
  O_{i}(\u, \meandepth{i}) = 1 - \Ptransmission(\meandepth{i}, \u) \enspace .
\end{align}

If a portion of our proposed detection bounding box is known to be
occluded, then we would like to decrease the confidence in the detection score
about the localization of that end of the object. Assuming that the occlusion
is often on the boundary of detection bounding boxes, we want to decrease our
confidence on the mean detection boundaries around the occluded boundaries.
To re-model our detection scores scaled by continuous occlusion we sample
$O_{i}(\mathbf{u}, \meandepth{i})$ at the hypothesized detection boundaries from
GMM $S(.)$ and we augment the detection boundary covariance matrix by
$\mathcal{P}_{i} = \rho_{i}\rho_{i}^\top$ where $\rho_{i} = O_{i}(\mathbf{u},
\meandepth{i})$. The new covariance matrix in detection score is given by 
  $\Lambda'_k = \mathcal{P}_{i} + \Lambda_k$ for all $k$.
The detection scores GMM with occlusion is given by replacing the covariance
matrix
%
\begin{multline}
S'(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \Lambda_k^{'-1} \bepsilon_k^{i}(t) \right)
\end{multline}

The energy of detection scores is simply take to be the inverse of the detection score.
\begin{align}
  \Energy{detect}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}
\end{align}

%For object detections we use object detector by \cite{Felzenszwalb_etal_2010} which is detector by parts model and we use eight parts to train the car model on half of the KITTI dataset \cite{geiger2013vision}. The trained modeled is used to get detections for the other half of the dataset and vice versa.

### 2015-11-06 CVPR16/Source/squareBBoxModel.tex
Added an option of enabling the square bounding box model.

\section{Object detection energy}

We model object detection energy as the norm of difference in the coordinates
of the projected bounding box and detected bounding box. The detected bounding
box is represented by the extrema along X and Y dimensions $\bb{i} = [\xmin,
\ymin, \xmax, \ymax]^\top$. If $\dimsn{i} = [l, w, h]^\top$ represent the 3D
dimensions of the traffic participant along the X, Y and Z dimensions then we 
can compute the projection of the bounding box in terms the dimensions $\dimsn{i}$
and object pose $\Omega_i(t)$. We model occlusion such that the confidence in
accuracy of the particular bounding box edge is reduced proportional to its
occlusion. We measure the extent of occlusion by the fraction of the area of 
the triangle corresponding to the occluded side and call it visibility fraction.
The visibility fraction stacked as a diagonal matrix gives us visibility matrix
$\mathcal{V}$ which can be used to scale the difference between projected bounding box
$\projectionOf{\dimsn{i}}$ and the detected bounding box $\bbt{i}{t}$. More precisely, for
the situation described in Fig~\ref{fig:bboxoccfigure}.
%
\begin{align}
  \mathcal{V} &= \text{diag}([v_{AB}, v_{BC}, v_{CD}, v_{DA}])\\
  \EnergyBBox &= \left\| \mathcal{V} \left(\projectionOf{\dimsn{i}}-\bbt{i}{t}\right) \right\|^2 
\end{align}
%
%
\begin{figure}
  \centering
  \input{bboxoccfigure}
  \caption{We model the occlusion of bounding by taking the corresponding
  triangle as a proxy for edge. The visibility fraction for the AD, $v_{AD}$ is given
by the fraction of the area of triangle $\bigtriangleup AED$ 
that is occluded.}
  \label{fig:bboxoccfigure}
\end{figure}

% \begin{align}
%   X^{(i)}_{\text{cuboid}} &= \dimsn{i}{}^\top C_u \\
%   \text{where} &\\
%   C_u &= 
%   \begin{bmatrix}
%   0.5 & 0.5 & -0.5 & -0.5 & 0.5 & 0.5 & -0.5 & -0.5 \\
%     0.5 & -0.5 & -0.5 & 0.5 & 0.5 & -0.5 & -0.5 & 0.5 \\
%     0 & 0 & 0 & 0 & 1  & 1 & 1 & 1
%   \end{bmatrix} \enspace .
% \end{align}
% These cuboid points can be projected to the camera image plane to get the projected bounding box,
% \newcommand{\ucub}{U^{(i)}(t)}
% \newcommand{\ucubx}{U_{(1,:)}^{(i)}(t)}
% \newcommand{\ucuby}{U_{(2,:)}^{(i)}(t)}
% \newcommand{\estbb}{\hat{\mathbf{d}}^{(i)}(t)}
% \begin{align}
%   \ucub &= \projectionOf{\dimsn{i}{}^\top C_u}\\
%   \estbb &= [\min \ucubx, \min \ucuby, \max \ucubx, \max \ucuby]^\top \enspace .
% \end{align}
% We take $\estbb$ as the projected bounding box. The object detection energy is
% taken to be the euclidean distance between projected and detected bounding box.
% \begin{align}
%   \EnergyBBox &= \| \estbb - \bb{i}\|^2_2
% \end{align}
% With slight abuse of notation for projection operator we write this energy as
% \begin{align}
%   \EnergyBBox &= \left\| \projectionOf{\dimsn{i}} - \bb{i}\right\|^2_2 \enspace.
% \end{align}

### 2015-11-06 CVPR16/Source/experiments2.tex

@@
 
-\subsection{Localization Experiment and Results}
+\subsection{Localization Experiments}
 We report error in three metrics translation error (t) in meters per car, yaw

### 2015-11-06 CVPR16/Source/discussions.tex

@@
 
-Our experiments shows that our association probability produces more accurate
+Our experiments show that our association probability produces more accurate
 point to object associations when compared to bounding box based
 association and state of art motion segmentation.
-Also the localization experiment results show improvement by modeling occlusions, however, the average translation error of 5 meters is very high.
+Also the localization experiment results show improvement in localization accuracy by modeling occlusions.
+However, the average translation error of 5 meters is very high.
 Since the results are averaged over the entire KITTI dataset, there are various possible sources of error, including outliers in point tracks, outliers in detections results.

### 2015-11-06 CVPR16/Source/experiments2.tex
Fixed the contBBoxModel.tex
Added results from continuous bounding box experiments.

@@
 
+%  seqName   seqNum    Energy_description                                                    windows         t      yaw             dim        
+%    City      1       contPtTracksNoOcc_ctBBoxNoOcc_size_posTmcmc_inference      9/18  5.811142 0.696358        1.961227        
+%    City      1       contPtTracksNoOcc_contBBoxOcc_size_posTmcmc_inference      8/18  4.501543 0.786599        2.375481        
+%    City      1       contPtTracks_ctBBoxNoOcc_size_posTmcmc_inference           8/18  3.932855 0.766397        2.222919        
+%    City      1       contPtTracks_contBBoxOcc_size_posTmcmc_inference           8/18  4.928155 0.806356        2.287911        
+% OccCity      1       contPtTracksNoOcc_ctBBoxNoOcc_size_posTmcmc_inference      9/18  3.953464 0.442196        1.720844        
+% OccCity      1       contPtTracksNoOcc_contBBoxOcc_size_posTmcmc_inference      8/18  4.815849 0.463034        2.159956        
+% OccCity      1       contPtTracks_ctBBoxNoOcc_size_posTmcmc_inference           8/18  4.058560 0.995495        1.593641        
+% OccCity      1       contPtTracks_contBBoxOcc_size_posTmcmc_inference           8/18  3.241853 0.631901        2.167446        
+% \begin{table}
+%   \centering
+%   \begin{tabular}{lrrr}
+%     \toprule
+%     Energy & t & yaw & dim \\
+%     \midrule
+%     $\EnergyTrackNoOcc + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$
+%     5.81 & 0.69 & 1.96 \\
+%     $\EnergyTrackNoOcc + \EnergyBBox +\EnergySize+\EnergyDyn$
+%     4.50 & 0.78 & 2.37 \\
+%     $\EnergyTrack + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$
+%     3.93 & 0.76 & 2.22 \\
+%     $\EnergyTrack + \EnergyBBox +\EnergySize+\EnergyDyn$
+%     4.92 & 0.80 & 2.28 \\
+%     \bottomrule
+%   \end{tabular}
+%   \caption{Localization experiment results with different combination of energies.
+We report error in three metrics translation error (t) in meters per car, yaw error (yaw) in radians per car and dimension error is again meters per car.}
+%   \label{tab:localizationExperimentNoOcc}
+% \end{table}
 \begin{table}
-  \centering
   \begin{tabular}{lrrr}
@@
     \midrule
-    initialization                                                                                  & 3.79 & \textbf{0.86} & 1.64 \\
-    %$\EnergyLane+\EnergySize+\EnergyBBox+\EnergyDyn                                       $ & 3.83 & 0.90 & \textbf{1.14} \\
-    %$\EnergyLane+\EnergySize+\EnergyBBoxocc+\EnergyDyn                                    $ & 3.83 & 0.90 & 1.14 \\
-    %$\EnergyLane+\EnergySize+\EnergyBBoxocc+\EnergyDyn+\EnergyCol                         $ & 3.92 & 0.91 & 1.15 \\
-    %$\EnergyLane+\EnergyContpttracks+\EnergySize+\EnergyBBoxocc+\EnergyDyn             $ & 3.81 & 0.92 & 1.59 \\
-    % \EnergyBBox+\EnergyDyn+\EnergyCol $
-    $\EnergyTrackNoOcc+\EnergyCol + \EnergyLane + \dots$  & 3.80 & 0.91 & 1.58 \\
-    $\EnergyTrack+\EnergyCol + \EnergyLane + \dots$ & \textbf{3.78} & 0.91 & 1.58 \\
+    $\EnergyTrackNoOcc + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$ 
+    & 3.95 & 0.44  & 1.72\\        
+    $\EnergyTrackNoOcc + \EnergyBBox +\EnergySize+\EnergyDyn$        
+    & 4.81 & 0.46  & 2.16\\        
+    $\EnergyTrack + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$      
+    & 4.05 & 0.99  & 1.59\\        
+    $\EnergyTrack + \EnergyBBox +\EnergySize+\EnergyDyn$             
+    & 3.24 & 0.63  & 2.16\\
     \bottomrule
@@
   \caption{Localization experiment results with different combination of energies.
-We report error in three metrics translation error (t) in meters per car, yaw error (yaw) in radians per car and dimension error is again meters per car.}
+We report error in three metrics translation error (t) in meters per car, yaw error (yaw) in radians per car and dimension error is again meters per car.
+The result provided here are only on occluded tracks}
   \label{tab:localizationExperiment}

### 2015-11-06 CVPR16/Source/experiments2.tex
changes

--- 2015-11-06 CVPR16/Source/experiments2.tex
@@
 
-\vspace{-0.4cm}
+\vspace{-0.2cm}
 \paragraph{Setup}
@@
 For a complete evaluation, we create organize the point tracks into four sets: all point tracks, occluded point tracks, dynamic point tracks and dynamic as well as occluded point tracks.
-In addition to point tracks, the parameters of all objects (cars) estimated by the method of \cite{Song_Chandraker_2014} are provided to our method (for computing association probability) and the baseline BBox method (for depth ordering).
+In addition to point tracks, the parameters of all objects (cars) estimated by the method of \cite{Song_Chandraker_2015} are provided to our method (for computing association probability) and the baseline BBox method (for depth ordering).
 
@@
 
+%  seqName   seqNum    Energy_description                                                    windows         t      yaw             dim        
+%    City      1       contPtTracksNoOcc_ctBBoxNoOcc_size_posTmcmc_inference      9/18  5.811142 0.696358        1.961227        
+%    City      1       contPtTracksNoOcc_contBBoxOcc_size_posTmcmc_inference      8/18  4.501543 0.786599        2.375481        
+%    City      1       contPtTracks_ctBBoxNoOcc_size_posTmcmc_inference           8/18  3.932855 0.766397        2.222919        
+%    City      1       contPtTracks_contBBoxOcc_size_posTmcmc_inference           8/18  4.928155 0.806356        2.287911        
+% OccCity      1       contPtTracksNoOcc_ctBBoxNoOcc_size_posTmcmc_inference      9/18  3.953464 0.442196        1.720844        
+% OccCity      1       contPtTracksNoOcc_contBBoxOcc_size_posTmcmc_inference      8/18  4.815849 0.463034        2.159956        
+% OccCity      1       contPtTracks_ctBBoxNoOcc_size_posTmcmc_inference           8/18  4.058560 0.995495        1.593641        
+% OccCity      1       contPtTracks_contBBoxOcc_size_posTmcmc_inference           8/18  3.241853 0.631901        2.167446        
 \begin{table}

### 2015-11-06 CVPR16/Source/intro.tex
Added Figure 1

--- 2015-11-06 CVPR16/Source/intro.tex
@@
 
-As a 2D projection of the 3D world, image formation is often associated with a loss of information.
+As a two-dimensional (2D) projection of the three-dimensional (3D) world, image formation is associated with a loss of information.
 This is especially significant when objects in 3D space occlude each other with respect to the camera viewpoint.
-In recent years, we have seen remarkable progress in various fields that enable scene understanding, such as structure from motion (SFM) and object detection.
-However, occlusions still present a difficult challenge, with the difficulty of physically modeling them being a major bottleneck.
+In recent years, we have seen remarkable progress in various aspects of scene understanding, such as structure from motion (SFM) and object detection.
+However, occlusions still present a challenge, with the difficulty of physically modeling them being a major bottleneck.
 %Prior works have considered occlusions in 2D or through discrete occluder patterns
+
+\begin{figure}[!!t]
+\begin{center}
+\includegraphics[width=\linewidth]{graphics/figure1.png}
+\end{center}
+\vspace{-0.6cm}
+\caption{\small We propose an occlusion model in 3D that is physically-inspired and continuous.
+Given object detection and SFM point tracks, our unified model probabilistically assigns point tracks to objects and reasons about object detection scores and bounding boxes.
+It uniformly handles static and dynamic objects, thus, outperforms motion segmentation for association problems.
+We also demonstrate occlusion-aware 3D localization in road scenes.}
+\label{fig:page1}
+\vspace{-0.4cm}
+\end{figure}
 
@@
 This allows assigning probabilities for each point in space belonging to an object, which can explicitly explain image observations and reason about occlusions.
-This is in contrast to prior works that consider occlusions in 2D, or through discrete occluder patterns that are not physically interpretable.
+This is in contrast to prior works that consider occlusions in 2D, or through discrete occluder patterns or models that are not physically interpretable \cite{Hsiao_Herbert_2012,Pepik_etal_2013,Xiang_Savarese_2013,Zia_etal_2013,Zia_etal_2014}.
 
@@
 While previous approaches to handling occlusion are application-dependent, ours is physically-inspired, thus, flexible enough to be used in a variety of scenarios.
-In this paper, we show that our theory can be used for modeling the association of 3D SFM points with static or dynamic objects (Section \ref{sec:association}), as well as modeling object detection scores in applications like 3D localization (Section \ref{sec:localization}).
+In this paper, we show that our theory can be used for uniformly modeling the association of SFM point tracks with static or dynamic objects (Section \ref{sec:association}), as well as modeling object detection scores in applications like 3D localization (Section \ref{sec:localization}).
 We demonstrate application of our formulations for road scenes from the KITTI dataset \cite{Geiger_etal_2012}.
 
-In particular, assigning 2D point tracks to independently moving, but potentially occluding, objects is a fundamental challenge in computer vision problems such as multibody SFM \cite{Ozden_etal_2010}.
-Recent works use motion segmentation \cite{Rao_etal_2010,Brox_Malik_2010} as a precursor to localizing moving objects, which often suffices for moving objects \cite{Tron_Vidal_2007} and has been considered for multibody SFM \cite{Kundu_etal_2011}.
+In particular, assigning 2D point tracks to independent, but potentially occluding, objects is a fundamental challenge in computer vision problems such as multibody SFM \cite{Ozden_etal_2010}.
+Recent works use motion segmentation \cite{Rao_etal_2010,Brox_Malik_2010} as a precursor to localizing objects, which often suffices for moving objects \cite{Tron_Vidal_2007} and has been considered for multibody SFM \cite{Kundu_etal_2011}.
 But motion-based segmentation is not always applicable in road scenes, due to static parked cars, or dynamic cars that move with similar velocities.
@@
 %In contrast, we leverage the success of 
-Indeed, we show in Section \ref{sec:experiments} that our point track association outperforms state-of-the-art motion segmentation methods, as well as a baseline that uses detection bounding boxes but does not consider occlusions.
+Indeed, we show in Section \ref{sec:experiments} that our point track association outperforms state-of-the-art motion segmentation, as well as a baseline that uses detection bounding boxes but does not consider occlusions.
 
 Another potential application of our proposed model is towards 3D localization in road scenes.
-Prior works such as \cite{Song_Chandraker_2014} combine information from point tracks and detection bounding boxes, but do not consider occlusions for either.
+Prior works such as \cite{Song_Chandraker_2015} combine information from point tracks and detection bounding boxes, but do not consider occlusions for either.
 In contrast, our unified occlusion model allows a probabilistic soft assignment of point tracks to objects, as well as an occlusion-aware interpretation of object detection outputs.

### 2015-11-06 CVPR16/Source/applications.tex
Fixed the contBBoxModel.tex
changes
edit Sec 4.2

@@
 
-We exploit in this section the application of our continuous occlusion model to 3D localization in road scenes, which further demonstrates its versatility.
+We exploit in this section the application of our continuous occlusion model to 3D localization in road scenes, which further demonstrates the versatility of the proposed model.
 Given a set of tracked feature points $\{\bu_j(t)\}$ and 2D detection bounding boxes $\{\bb{i}\}$ at frame $t$, the goal is to localize 3D traffic participants (TPs), in particular, for each TP, estimating its position $\bp^i(t)$ and orientation $\bomega^i(t)$ on the ground plane and its 3D dimensions $\bB^i(t)$.
@@
 where $\pEnergy{track}$ and $\Energy{detect}$ reason about image observations such as point tracks and bounding boxes while $\Energy{dyn}$  and $\Energy{size}$ impose smoothness constraints and size priors respectively.
-Here, $\lambda_{track}$, $\lambda_{detect}$, $\lambda_{dyn}$, $\lambda_{size}$ are energy weights and $Z$ is the normalization coefficient.
+Here, $\lambda_{track}$, $\lambda_{detect}$, $\lambda_{dyn}$, $\lambda_{size}$ are energy weights, $N$ is the number of objects in the sequence, $s_i$ and $t_i$ are respectively the starting and ending frames of object $O_i$, and $Z$ is the normalization coefficient.
 Figure~\ref{fig:graphmodel} illustrates an example of the graph and energies.
-Next, we present our unified continuous occlusion modelling for point track and bounding box energies; please refer to our supplementary material for the formulations of other energies.
+Next, we present our unified continuous occlusion modelling for both point track and bounding box energies.
+Due to space constraints, we present the details of other energies in the supplementary.
 
@@
     \newcommand{\imagewidth}{7.5cm}
+      \hspace{-0.8cm}
     \input{Source/scenelayoutoverlayCity0961} \\
+      \hspace{-0.8cm}
     \input{Source/graphical_model_multiple}
@@
 
-For an object $i$, let $\{ \Omega (t) \}_i$ be the poses of all occluding objects at time $t$ (inclusive of object $i$) and $ \{ \bB \}_i$ be their dimensions.
+For an object $O_i$, let $\{ \Omega (t) \}_i$ be the poses of all occluding objects at time $t$ (inclusive of object $i$) and $ \{ \bB \}_i$ be their corresponding 3D dimensions.
 Then, we model the continuous point tracks energy with explicit occlusion reasoning as the expected reprojection error over the association probability:
@@
 
-\input{contBBoxModel.tex}
+\input{Source/contBBoxModel}
 %\input{Source/squareBBoxModel.tex}
@@
 
-\subsection{Metropolis Hastings Inference}
+\subsubsection{Metropolis Hastings Inference}
 We use Metropolis Hastings' methods \cite{mackay1998introduction} for graphical model inference. Since we are

### 2015-11-06 CVPR16/Source/contBBoxModel.tex
edit Sec 4.2

@@
 To retain the entire detection output while maintaining the continuous form of our energies, we approximate the distribution of detection scores with a multi-modal sum of Gaussians-like logistic functions.
-In particular, let $\bb{i}$ be parameterized as a 4D vector $[\minx, \miny, \maxx, \maxy]^\top$.
+In particular, let the 2D bounding box $\bb{i}$ be parameterized as a 4D vector $[\minx, \miny, \maxx, \maxy]^\top$.
 We fit a parametric function to the detection scores, of the form
 \begin{equation}
-S(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \Lambda_k^{'-1} \bepsilon_k^{i}(t) \right)
+S(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \Lambda_k^{-1} \bepsilon_k^{i}(t) \right)
 \end{equation}
@@
 compute the probability of a point $\u$ in the image to be occluded assuming
-the point is on object $i$ with mean depth $\meandepth{i}$ as
+the point is on object $O_i$ with mean depth $\meandepth{i}$ as
 \begin{align}

### 2015-11-06 CVPR16/Source/contBBoxModel.tex
changes in 4.2

@@
 To retain the entire detection output while maintaining the continuous form of our energies, we approximate the distribution of detection scores with a multi-modal sum of Gaussians-like logistic functions.
-In particular, let the 2D bounding box $\bb{i}$ be parameterized as a 4D vector $[\minx, \miny, \maxx, \maxy]^\top$.
+In particular, let 2D bounding box $\bb{i}$ be parameterized as a 4D vector $[\minx, \miny, \maxx, \maxy]^\top$.
 We fit a parametric function to the detection scores, of the form
@@
 \begin{align}
-  O_{i}(\u, \meandepth{i}) = 1 - \Ptransmission(\meandepth{i}, \u) \enspace .
+  \Theta_{i}(\u, \meandepth{i}) = 1 - \Ptransmission(\meandepth{i}, \u) \enspace .
 \end{align}
@@
 To re-model our detection scores scaled by continuous occlusion we sample
-$O_{i}(\mathbf{u}, \meandepth{i})$ at the hypothesized detection boundaries from
-GMM $S(.)$ and we augment the detection boundary covariance matrix by
-$\mathcal{P}_{i} = \rho_{i}\rho_{i}^\top$ where $\rho_{i} = O_{i}(\mathbf{u},
+$\Theta_{i}(\mathbf{u}, \meandepth{i})$ at the hypothesized detection boundaries from
+Gaussian mixture model (GMM) $S(.)$ and we augment the detection boundary covariance matrix by
+$\mathcal{P}_{i} = \rho_{i}\rho_{i}^\top$ where $\rho_{i} = \Theta_{i}(\mathbf{u},
 \meandepth{i})$. The new covariance matrix in detection score is given by 

### 2015-11-06 CVPR16/Source/applications.tex

@@
 \end{multline}
-where $\assocP$ is the association probability of point $\trackp{t}$ with the object $O_i$ at depth $\lambda$, given by \eqref{eq:defineassocP}.
+where $N$ and $M$ are respectively the number of objects and points and $\assocP$ is the association probability of point $\trackp{t}$ with the object $O_i$ at depth $\lambda$, given by \eqref{eq:defineassocP}.
 
@@
 
-\subsubsection{Metropolis Hastings Inference}
-We use Metropolis Hastings' methods \cite{mackay1998introduction} for graphical model inference. Since we are
-optimizing over continuous random variables, we use Gaussian distribution as
-the proposal distribution. We choose Metropolis Hastings inference over
-block-coordinate descent which turns out to be slower than Metropolis Hastings
-in our experiments. Please refer to the supplementary material for the
-comparison of inference methods.
+\subsubsection{Inference on graphical model}
+We apply Metropolis Hastings' method~\cite{mackay1998introduction} for performing inference on graphical model. Since we are
+optimizing over continuous variables, we use Gaussian distribution as
+the proposal function. We choose Metropolis Hastings over
+Blocked Coordinate Descent which turns out to be slower than Metropolis Hastings
+in our experiments. Please refer to the supplementary material for our comparisons of inference methods.
 

### 2015-11-06 CVPR16/Source/intro.tex
changes
Squeezed plots fig 3 and fig 4.

@@
 In this paper, we show that our theory can be used for uniformly modeling the association of SFM point tracks with static or dynamic objects (Section \ref{sec:association}), as well as modeling object detection scores in applications like 3D localization (Section \ref{sec:localization}).
-We demonstrate application of our formulations for road scenes from the KITTI dataset \cite{Geiger_etal_2012}.
+We demonstrate the application of our formulations for road scenes from the KITTI dataset \cite{Geiger_etal_2012}.
 
@@
 \item A novel theoretical model for handling occlusions that is continuous and formulated in 3D.
-\item Unified occlusion handling in various applications, such as 3D points in SFM and bounding boxes in object detection.
+\item Unified occlusion handling for point tracks in SFM and bounding boxes and detection scores in object detection.
 \item Application of our model to association of point tracks with both static and moving objects, improving over motion segmentation and occlusion-unaware baselines.

### 2015-11-06 CVPR16/Source/experiments2.tex
changes

@@
 \end{figure*}
+
 \begin{table}
@@
 \end{tabular}
-\caption{Mean association errors on different sets of input point tracks over all sequences of KITTI dataset.
+\caption{\small Mean association errors on different sets of input point tracks over all sequences of KITTI dataset.
 Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
@@
 % \end{table}
+
+%% \begin{table}
+%% \small
+%%   \begin{tabular}{lrrr}
+%%     \toprule
+%%     Energy & t & yaw & dim \\
+%%     \midrule
+%%     $\EnergyTrackNoOcc + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$ 
+%%     & 3.95 & 0.44  & 1.72\\        
+%%     $\EnergyTrackNoOcc + \EnergyBBox +\EnergySize+\EnergyDyn$        
+%%     & 4.81 & 0.46  & 2.16\\        
+%%     $\EnergyTrack + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$      
+%%     & 4.05 & 0.99  & 1.59\\        
+%%     $\EnergyTrack + \EnergyBBox +\EnergySize+\EnergyDyn$             
+%%     & 3.24 & 0.63  & 2.16\\
+%%     \bottomrule
+%%   \end{tabular}
+%%   \caption{\small Localization experiment results with different combination of energies.
+We report error in three metrics translation error (t) in meters per car, yaw error (yaw) in radians per car and dimension error is again meters per car.
+The results provided here are only on occluded tracks.}
+%%   \label{tab:localizationExperiment}
+%% \end{table}
+
 \begin{table}
-  \begin{tabular}{lrrr}
+  \begin{tabular}{lrr}
     \toprule
-    Energy & t & yaw & dim \\
+    Energy & t & dim \\
     \midrule
     $\EnergyTrackNoOcc + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$ 
-    & 3.95 & 0.44  & 1.72\\        
+    & 3.95  & 1.72\\        
     $\EnergyTrackNoOcc + \EnergyBBox +\EnergySize+\EnergyDyn$        
-    & 4.81 & 0.46  & 2.16\\        
+    & 4.81  & 2.16\\        
     $\EnergyTrack + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$      
-    & 4.05 & 0.99  & 1.59\\        
+    & 4.05  & {\bf 1.59}\\        
     $\EnergyTrack + \EnergyBBox +\EnergySize+\EnergyDyn$             
-    & 3.24 & 0.63  & 2.16\\
+    & {\bf 3.24}  & 2.16\\
     \bottomrule
   \end{tabular}
-  \caption{Localization experiment results with different combination of energies.
-We report error in three metrics translation error (t) in meters per car, yaw error (yaw) in radians per car and dimension error is again meters per car.
-The result provided here are only on occluded tracks}
+  \caption{\small Localization experiment results with different combinations of energies.
+We report translation error (t) and dimension error (dim) in meters per car.
+Yaw angles for static objects are not optimized by our model.
+These experiments use the set of occluded tracks to demonstrate the effect of our modeling.}
   \label{tab:localizationExperiment}
@@
 \subsection{Localization Experiments}
-We report error in three metrics translation error (t) in meters per car, yaw
-error (yaw) in radians per car and dimension error is again meters per car. The
-results are shown in Table~\ref{tab:localizationExperiment}.  We compare four
-combinations of energies as shown in the table.  The energy $\EnergyTrackNoOcc$
-represents the point tracks energy modeled with accounting for occlusion, i.e.,
-we remove the term $\Ptransmission$ and model $\EnergyTrack$ in the absence of
-$\Ptransmission$. Similarly, $\EnergyBBoxNoOcc$ is the energy without the
-modification of $\Sigma^{(d)}_j$ that accounts for occlusion.  The results show that
-use of continuous occlusion model improves the localization accuracy in terms
-of all three metrics: translation, yaw and dimension error.
+We report errors in translation error and dimension estimates, measured in meters per car, in Table~\ref{tab:localizationExperiment}.
+We compare four combinations of energies.
+The energy $\EnergyTrackNoOcc$ represents the point tracks energy without accounting for occlusion, that is, we model $\EnergyTrack$ in the absence of $\Ptransmission$.
+Similarly, $\EnergyBBoxNoOcc$ is the energy without the modification of $\Lambda_k$ that accounts for occlusion.
+The results show that the use of continuous occlusion model improves the localization accuracy in terms of the translation error, which is he most significant metric affected by all cues.
+Occlusion modeling for detection improves localization, but penalizes dimension since we explicitly allow greater uncertainty in occluded edges of the bounding box.
+
+%of all three metrics: translation, yaw and dimension error.
+
+%We report error in three metrics translation error (t) in meters per car, yaw error (yaw) in radians per car and dimension error is again meters per car.
+The results are shown in Table~\ref{tab:localizationExperiment}.
+We compare four combinations of energies as shown in the table.
+The energy $\EnergyTrackNoOcc$ represents the point tracks energy modeled with accounting for occlusion, i.e., we remove the term $\Ptransmission$ and model $\EnergyTrack$ in the absence of $\Ptransmission$.
+Similarly, $\EnergyBBoxNoOcc$ is the energy without the modification of $\Sigma^{(d)}_j$ that accounts for occlusion.
+The results show that use of continuous occlusion model improves the localization accuracy in terms of all three metrics: translation, yaw and dimension error.

### 2015-11-06 CVPR16/Source/discussions.tex
changes

--- 2015-11-05 CVPR16/Source/discussions.tex
@@
-\section{Discussion and Future Work}
+\section{Conclusions and Future Work}
 \label{sec:conclusions}
 
-Our experiments shows that our association probability produces more accurate
-point to object associations when compared to bounding box based
-association and state of art motion segmentation.
-Also the localization experiment results show improvement by modeling occlusions, however, the average translation error of 5 meters is very high.
+We have presented a continuous model for occlusion modeling in 3D.
+A key advantage is its physically-inspired modeling that lends flexibility towards occlusion reasoning for various elements of scene understanding, such as point tracks, object detection bounding boxes and scores.
+We demonstrate unified modeling for different applications such as point tracks associations and 3D localization.
+Our occlusion model can uniformly handle static and dynamic objects, which is an advantage over motion segmentation methods for point-object association.
+A challenge is that inference for 3D localization is currently slow, requiring a few minutes per window of frames, which prevents exhaustive cross-validation for tuning of weights.
+Our future work will explore speeding up the inference, for example, by approximating the graph with a tree using the Chow-Liu method \cite{chow1968approximating}, allowing belief propagation for fast inference.
+
+%Our experiments show that our association probability produces more accurate point to object associations when compared to bounding box based association and state of art motion segmentation.
+Also the localization experiment results show improvement in localization accuracy by modeling occlusions.
+However, the average translation error of 5 meters is very high.
 Since the results are averaged over the entire KITTI dataset, there are various possible sources of error, including outliers in point tracks, outliers in detections results.
@@
 
-We have several ideas for speeding up inference and thereby allowing learning
-of weights to become feasible. One of them is to approximate the graph into a
-tree using Chow-Liu's \cite{chow1968approximating} algorithm and then using
-Belief Propagation which is linear in the number of edges of the tree.
+%We have several ideas for speeding up inference and thereby allowing learning of weights to become feasible.
+One of them is to approximate the graph into a tree using Chow-Liu's \cite{chow1968approximating} algorithm and then using Belief Propagation which is linear in the number of edges of the tree.

### 2015-11-06 CVPR16/Source/experiments2.tex
changes

@@
 The results show that the use of continuous occlusion model improves the localization accuracy in terms of the translation error, which is he most significant metric affected by all cues.
-Occlusion modeling for detection improves localization, but penalizes dimension since we explicitly allow greater uncertainty in occluded edges of the bounding box.
+Occlusion modeling for point tracks is always beneficial, while that for detection improves localization, but penalizes dimension since we explicitly allow greater uncertainty in occluded edges of the bounding box.
+Note that none of our energies optimize yaw angles for static objects, which can be handled in practice through either the detector orientation or external information such as lane geometry.
 

### 2015-11-06 CVPR16/Source/applications.tex
squeezed equation 14
changes

@@
 %
-\begin{multline}
+\begin{multline*}
   -\log{P(\{ \bp^i(t) , \bomega^i(t) , \bB^i(t) \} | \{\bu_j(t)\} , \{\bb{i}\} )} = \\
   -Z 
-   + \sum_{t=s_i}^{e_i} \WpEnergy{track}
-  \\
+   + \sum_{t=s_i}^{e_i} \lambda_t\EnergyTrack
   + 
@@
   \sum_{i=1}^N  
-  \left( 
-  \WEnergy{detect}
-  + \WEnergy{dyn}
-  + \WEnergy{size}
-\right)
+  %\sum_{\substack{i \in [1, \dots, N] \\t \in [s_i, \dots e_i]}}
+  \lambda_d\EnergyBBox
+  + \lambda_{\text{dyn}}\EnergyDyn
+  + \lambda_{\text{size}}\EnergySize
   \enspace,
-\end{multline}
+\end{multline*}
 %
@@
 
-\subsubsection{Inference on graphical model}
-We apply Metropolis Hastings' method~\cite{mackay1998introduction} for performing inference on graphical model. Since we are
-optimizing over continuous variables, we use Gaussian distribution as
-the proposal function. We choose Metropolis Hastings over
-Blocked Coordinate Descent which turns out to be slower than Metropolis Hastings
-in our experiments. Please refer to the supplementary material for our comparisons of inference methods.
+\vspace{-0.3cm}
+\paragraph{Inference on graphical model}
+We apply Metropolis Hastings method~\cite{mackay1998introduction} for performing inference on the graphical model.
+Since we are optimizing over continuous variables, we use Gaussian distribution as the proposal function.
+We choose this over alternatives such as blocked coordinate descent since they are slower in our experiments.
+
+%in our experiments. Please refer to the supplementary material for our comparisons of inference methods.
 

### 2015-11-06 CVPR16/Source/experiments2.tex
changes

@@
 \subsection{Association Experiments}
-
 \vspace{-0.2cm}
 \paragraph{Setup}
-
 We first perform the association experiment that compares the accuracy of point-to-object association using our proposed model against a heuristic baseline and state-of-the-art motion segmentation methods.
@@
 For motion segmentation, we use robust algebraic segmentation with hybrid perspective constraints (RAS)~\cite{Rao_etal_2010} and spectral clustering with point track spatial affinity (BM)~\cite{Brox_Malik_2010}.
+
+\begin{figure*}[!!t]
+\centering
+%\includegraphics[trim=1.0in 0.4in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
+\includegraphics[width=0.9\textwidth]{graphics/figure5.png}
+  \vspace{-0.3cm}
+  \caption{\small Association errors on different sets of input point tracks.
+Numbers on y-axis represent data sequence numbers in KITTI dataset.
+Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
+  \vspace{-0.3cm}
+  \label{fig:assoc-occ-results}
+\end{figure*}
+
+\begin{table}
+\begin{tabular}{lrrrr}
+  \toprule
+  & Ours & BBox & BM & RAS\\
+  \midrule
+  Dyn. and occ. tracks        & \textbf{13.2} & 21.3 & 30.9 & 30.1 \\
+  Occluded tracks             & \textbf{15.7} & 19.8 & 39.5 & 37.8 \\
+  Dynamic tracks              & \textbf{06.6} & 11.4 & 15.3 & 17.7 \\
+  All tracks                  & \textbf{08.6} & 12.6 & 21.9 & 21.5 \\
+  \bottomrule
+\end{tabular}
+\caption{\small Mean association errors on different sets of input point tracks over all sequences of KITTI dataset.
+Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
+\label{tab:meanAssoc}
+\end{table}
+
+\newlength{\tblimgwidth}
+\setlength{\tblimgwidth}{0.40\textwidth}
+\begin{figure*}[!!t]
+  \centering
+  \begin{tabular}{ccc}
+    & Associations & Error in association\\
+    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png} &%
+    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
+    \rotatebox{90}{\hspace{2em} BM} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png} &%
+    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
+    \rotatebox{90}{\hspace{2em} RAS} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_RAS-small.png} &%
+    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
+    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks-small.png} &%
+    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}\\
+    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png} &%
+    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
+    \rotatebox{90}{\hspace{2em} BM} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png} &%
+    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
+    \rotatebox{90}{\hspace{2em} RAS} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_RAS-small.png} &%
+    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
+    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks-small.png} &%
+    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}
+  \end{tabular}
+  \vspace{-0.3cm}
+  \caption{\small Qualitative results of the association experiment. The left column
+  shows the point track assignments to appropriate objects. Each color represents
+a different object to which point tracks can be associated to. Right column shows the
+probabilistic error in association: low error points are in blue while high error points are in red.
+Note that our method changes smoothly at the object boundaries with
+intermediate probabilities, while the baseline method has merely 0-1 error.}
+\label{fig:qualitative}
+\vspace{-0.3cm}
+\end{figure*}
 
@@
 We note the low errors using our occlusion model and the smooth transition of assignment across object boundaries.
-
-\begin{figure*}
-\includegraphics[trim=1.0in 0.4in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
-  \caption{Association errors on different sets of input point tracks.
-Numbers on y-axis represent data sequence numbers in KITTI dataset.
-Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
-\label{fig:assoc-occ-results}
-\end{figure*}
-
-\begin{table}
-\begin{tabular}{lrrrr}
-  \toprule
-  & Ours & BBox & BM & RAS\\
-  \midrule
-  Dyn. and occ. tracks        & \textbf{13.2} & 21.3 & 30.9 & 30.1 \\
-  Occluded tracks             & \textbf{15.7} & 19.8 & 39.5 & 37.8 \\
-  Dynamic tracks              & \textbf{06.6} & 11.4 & 15.3 & 17.7 \\
-  All tracks                  & \textbf{08.6} & 12.6 & 21.9 & 21.5 \\
-  \bottomrule
-\end{tabular}
-\caption{\small Mean association errors on different sets of input point tracks over all sequences of KITTI dataset.
-Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
-\label{tab:meanAssoc}
-\end{table}
-
-\newlength{\tblimgwidth}
-\setlength{\tblimgwidth}{0.40\textwidth}
-\begin{figure*}
-  \centering
-  \begin{tabular}{ccc}
-    & Associations & Error in association\\
-    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png} &%
-    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{2em} BM} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png} &%
-    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{2em} RAS} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_RAS-small.png} &%
-    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks-small.png} &%
-    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png} &%
-    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{2em} BM} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png} &%
-    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{2em} RAS} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_RAS-small.png} &%
-    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks-small.png} &%
-    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}
-  \end{tabular}
-  \caption{\small Qualitative results of the association experiment. The left column
-  shows the point track assignments to appropriate objects. Each color represents
-a different object to which point tracks can be associated to. Right column shows the
-probabilistic error in association: low error points are in blue while high error points are in red.
-Note that our method changes smoothly at the object boundaries with
-intermediate probabilities, while the baseline method has merely 0-1 error.}
-\label{fig:qualitative}
-\end{figure*}
 

### 2015-11-06 CVPR16/Source/occlusion.tex
changes in Sec 3 and 4.1
changes

@@
   \end{tikzpicture}
-  \caption{We represent traffic participants as soft ellipsoids which lead to formulation of transmision and reflection probability.
+  \vspace{-0.3cm}
+  \caption{\small We represent traffic participants as soft ellipsoids which lead to formulation of transmision and reflection probability.
 This figure shows the reflection probability for the first car which is highest around the camera facing face of the car.
@@
   \label{fig:reflectiontransimission}
+  \vspace{-0.3cm}
 \end{figure}
 
+\vspace{-0.3cm}
 \paragraph{Occupancy model for traffic participants}
@@
 Based on this intuition, we model objects as translucent 3D ellipsoids whose opacity is maximum at the center and falls off towards the edges.
-In particular, we model the occupancy at 3D location $\bx$ corresponding to an object $i$ centered at $\pos{i}{t}$ as:
+In particular, we model the occupancy at 3D location $\bx$ corresponding to an object $O_i$ centered at $\bp_i$ as:
 \begin{align}
-  f_{\text{occ}}(\bx) = \cL(\bx; \pos{i}{t}, \bSigma_i)
+  f^i_{\text{occ}}(\bx) = \cL(\bx; \bp_i, \bSigma_i)
 \end{align}
@@
 \begin{align}
-  L(\bx; \bp, \bSigma) = \frac{1}{1 + e^{-k(1 - d(\mathbf{x},\bp))}},
+  \cL(\bx; \bp, \bSigma) = \frac{1}{1 + e^{-k(1 - d(\mathbf{x},\bp))}},
 \end{align}
@@
 
+\vspace{-0.3cm}
 \paragraph{Image formation}
@@
 
+\vspace{-0.3cm}
 \paragraph{Reflection probability}
@@
 
+\vspace{-0.3cm}
 \paragraph{Transmission probability}
@@
 \begin{align}
-  \!\!\!\! P_{\textit{transmission}}(\lambda + d\lambda) = P_{\textit{transmission}}(\lambda) (1-\occftot)^{d\lambda}.
+  \!\!\!\! P^j_{\textit{transmission}}(\lambda + d\lambda) = P^j_{\textit{transmission}}(\lambda) (1-\occftot)^{d\lambda}.
 \end{align}
@@
 \begin{align}
-  \Ptransmission^j(\lambda) = \prod_i (1 - \cL_u (\bu; \bmu_i, \bGamma_i^{-1}) \cL_{\lambda}(\lambda; \meandepth{i})),
+  \Ptransmission^j(\lambda) = \prod_i (1 - \cL_u (\bu; \bmu_i, \bGamma_i) \cL_{\lambda}(\lambda; \meandepth{i})),
 \label{eq:evalCumulativePtrans}
@@
 \begin{align}
-\cL_u(\bu; \bmu_i, \bGamma_i^{-1}) &= \frac{1}{1 + e^{-k_u(1 - (\bu - \bmu_i)^\top \bGamma_i^{-1} (\bu - \bmu_i))}} \\
+\cL_u(\bu; \bmu_i, \bGamma_i) &= \frac{1}{1 + e^{-k_u(1 - (\bu - \bmu_i)^\top \bGamma_i (\bu - \bmu_i))}} \\
   \cL_{\lambda}(\lambda; \meandepth{i}) &= \frac{1}{1 + e^{-k_d(\lambda - \meandepth{i})}}
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{results/plotPtransmission_exact_vs_approx_pt_vis-small.png}\\
-  \includegraphics[trim=0.0 0 0.3in 0, clip, width=\columnwidth]{results/plotPtransmission_exact_vs_approx.pdf}
-  \caption{Comparing the approximate $\Ptrans$ with exact version.
+\centering
+  \includegraphics[width=0.9\columnwidth]{results/plotPtransmission_exact_vs_approx_pt_vis-small.png}\\
+  \includegraphics[trim=0.0 0 0.3in 0, clip, width=0.9\columnwidth]{results/plotPtransmission_exact_vs_approx.pdf}
+  \vspace{-0.3cm}
+  \caption{\small Comparing the approximate $\Ptrans$ with exact version.
 The drop in approximate version of $\Ptrans$ is delayed because we assume drop at the center of the car rather than camera facing face of the car.}
   \label{fig:compare:exact:approx:ptrans}
+  \vspace{-0.3cm}
 \end{figure}

### 2015-11-07 CVPR16/Source/applications.tex
changes

@@
 where $\Prefl$ and $\Ptrans$ are from \eqref{eq:evalPrefl} and \eqref{eq:evalCumulativePtrans} respectively.
-Note that the fraction $\assocP$ although called association probability does not capture the entire information that we have available for computing association of point tracks to objects.
+Note that the fraction $\assocP$, although called association probability, does not capture the entire information that we have available for computing the association of point tracks to objects.
 
-To compute the association probability between point track $\bu_j$ and object $O_i$, we should also use the reprojection error.
+Rather, to compute the association probability between point track $\bu_j$ and object $O_i$, we should also use the reprojection error.
 When the association of point track $\bu_j$ and object $O_i$ is correct and the point of reflection is at depth $\lambda$, the corresponding reprojection error $\Ereproj(\lambda)$ must be zero \eqref{eq:reprojerror}, otherwise the error becomes a measure of distance from the true solution.
@@
 For regions where bounding boxes overlap, it may assign point tracks to the object that has the smallest mean depth among the competing bounding boxes.
-As we will demonstrate in the experiments, such heuristics are sub-optimal compared to using \eqref{eq:prob-assoc} inspired by our occlusion model.
+As we demonstrate in our experiments, such heuristics are sub-optimal compared to using \eqref{eq:prob-assoc} from our occlusion model.
 
@@
 where $\pEnergy{track}$ and $\Energy{detect}$ reason about image observations such as point tracks and bounding boxes while $\Energy{dyn}$  and $\Energy{size}$ impose smoothness constraints and size priors respectively.
-Here, $\lambda_{track}$, $\lambda_{detect}$, $\lambda_{dyn}$, $\lambda_{size}$ are energy weights, $N$ is the number of objects in the sequence, $s_i$ and $t_i$ are respectively the starting and ending frames of object $O_i$, and $Z$ is the normalization coefficient.
+Here, $\lambda_{t}$, $\lambda_{d}$, $\lambda_{dyn}$, $\lambda_{size}$ are energy weights, $N$ is the number of objects in the sequence, $s_i$ and $t_i$ are respectively the starting and ending frames of object $O_i$ and $Z$ is the normalization coefficient.
 Figure~\ref{fig:graphmodel} illustrates an example of the graph and energies.
 Next, we present our unified continuous occlusion modelling for both point track and bounding box energies.
-Due to space constraints, we present the details of other energies in the supplementary.
+Due to space constraints, we present the details of other energies in the supplementary material.
 
@@
 
-\subsubsection{Continuous point tracks energy with occlusion}
-\label{sec:totalContPtTracksEnergy}
-
+\vspace{-0.3cm}
+\paragraph{Continuous point tracks energy with occlusion}
+%\label{sec:totalContPtTracksEnergy}
 Let $\relp{i}{t}$ be the pose of object $O_i$ with respect to the camera at time $t$.
@@
 Since we are optimizing over continuous variables, we use Gaussian distribution as the proposal function.
-We choose this over alternatives such as blocked coordinate descent since they are slower in our experiments.
+We choose this over alternatives such as block coordinate descent since they are slower in our experiments.
 

### 2015-11-07 CVPR16/Source/related.tex
changes

@@
 Occlusions have also been handled in tracking-by-detection frameworks by considering occluder patterns in the image \cite{Kwak_etal_2012,Wu_Nevatia_2007}.
-A notable exception is the work of Milan et al.~\cite{Milan_etal_2014} that explicitly models occlusion in the continuous domain to determine a visibility for each object in multi-target tracking.
+A notable exception is the work of Milan et al.~\cite{Milan_etal_2014} that explicitly models occlusions in the continuous domain to determine a visibility ratio for each object in multi-target tracking.
 However, the occlusion model in \cite{Milan_etal_2014} is essentially the overlap of image projections of a Gaussian representation of the object.

### 2015-11-11 CVPR16/supplementarymaterial.tex
clean up supp

@@
 \usepackage{multirow}
+\usepackage{caption}
 \usepackage{subcaption}
@@
 \begin{document}
-\section{Computation of ellipsoid parameters}
+\section{Computation of Ellipsoids}
 How to compute the parameters of ellipsoid in the camera coordinate frame when center and dimensions of the ellipsoid are given in tracklet coordinate frame.
@@
 
-\section{Projection of ellipsoid to image}
+\section{Projection of Ellipsoids to Image}
 \newcommand{\mubar}{\bar{\mu}_i}
@@
 
-\subsection{Tangent planes method}
+\subsection{Tangent plane method}
 \newcommand{\nx}{\hat{n}_x}
@@
 
-\subsection{Projection of the ellipsoid slice}
 \begin{align}
@@
 
-\section{Localization}
-\subsection{Other Energies}
+\section{Other Energies for 3D Object Localization}
+
+\begin{comment}
 \subsubsection{Lane energy}
@@
 for some constant $w_{\text{road}}$ that represents the width of the road.
+\end{comment}
 
-\subsubsection{Transition probability}
+\subsection{Dynamic energy}
 Dynamics constraints should not only enforce smooth trajectories, but also the
@@
 
-\subsubsection{Size Prior}
+\subsection{Size energy}
 
@@
 
+\begin{comment}
 \section{Inference method Comparison}
@@
 \end{figure}
+\end{comment}
 

### 2015-11-13 CVPR16/supplementarymaterial.tex
edit supp

@@
 \DeclareMathOperator*{\argmin}{\arg\min}
+\input{Source/drawingslib}
 
@@
 
-\def\cvprPaperID{XXX} % *** Enter the CVPR Paper ID here
+\def\cvprPaperID{2072} % *** Enter the CVPR Paper ID here
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
@@
 \begin{document}
+\title{A Continuous Occlusion Model for Road Scene Understanding}
+
+\author{Vikas Dhiman\\
+  University of Michigan\\
+  Ann Arbor, MI, USA\\
+{\tt\small dhiman@umich.edu}
+Quoc-Huy Tran\\
+NEC Laboratories America, Inc.\\
+Cupertino, CA, USA\\
+{\tt\small qhtran@nec-labs.com}
+\and
+Manmohan Chandraker\\
+NEC Laboratories America, Inc.\\
+Cupertino, CA, USA\\
+{\tt\small manu@nec-labs.com}
+\and
+Jason J Corso\\
+  University of Michigan\\
+  Ann Arbor, MI, USA\\
+{\tt\small jjcorso@eecs.umich.edu}
+}
+
+\maketitle
+
+\appendix
+
 \section{Computation of Ellipsoids}
-How to compute the parameters of ellipsoid in the camera coordinate frame when center and dimensions of the ellipsoid are given in tracklet coordinate frame.
 \label{sec:sigmacomputation}
+Here we present how to compute the parameters of ellipsoids representing the occupancy of traffic participants.
+For an object $O_i$, let $\bB^i = [l~w~h]$ be its 3D dimensions, where $l$, $w$ and $h$ are respectively its length, width, and height on the ground plane, we are interested in calculating the center $\muic$ and spread $\Sigmaicf$ of the ellipsoid representing the occupancy of $O_i$ with respect to the camera coordinate system $\cC$ of the current frame.
 
+Consider an object coordinate system $\cO$, which has the same orthonormal axes as the camera coordinate system and the origin at the projected point of the object center to the ground plane.
+For an object $O_i$, the center $\muit$ and spread $\Sigmait$ of the ellipsoid representing the occupancy of $O_i$ in the object coordinate system are expressed as
 \begin{align}
@@
   0& 0& \frac{h}{2}
-  \end{bmatrix}^\top\\
+  \end{bmatrix}^\top,\\
   \Sigmait &= \begin{bmatrix}
@@
     0 & 0 & \frac{4}{h^2}
-  \end{bmatrix}
+  \end{bmatrix}.
 \end{align}
 
-In tracklet coordinates the equation of ellipsoid is 
+In object coordinates, the ellipsoid equation is written as
 \begin{align}
-  (\xt - \muit)^\top \Sigmait (\xt - \muit) = 1
+  (\xt - \muit)^\top \Sigmait (\xt - \muit) = 1,
+\label{equ:ellipsoidobj}
 \end{align}
+where $\xt$ is a point in object coordinates.
+Given $\Omega^i$ as the pose of $O_i$ in camera coordinates, we can extract the rotation $\Rctot$ and translation $\tctot$ for converting points in camera coordinates to object coordinates and rewrite \eqref{equ:ellipsoidobj} as
+\begin{align}
+  (\Rctot \xc + \tctot - \muit)^\top \Sigmait (\Rctot \xc + \tctot - \muit) = 1,
+\label{equ:ellipsoidobj1}
+\end{align}
+where $\xc$ is a point in camera coordinates.
 
-Moving to camera coordinates
-\begin{align}
-  (\Rctot \xc + \tctot - \muit)^\top \Sigmait (\Rctot \xc + \tctot - \muit) = 1
-\end{align}
-
-Let $\tcmut = \tctot - \muit$
-\begin{align}
-  (\Rctot \xc + \tcmut)^\top \Sigmait (\Rctot \xc + \tcmut) = 1
-\end{align}
+Let $\tcmut = \tctot - \muit$, \eqref{equ:ellipsoidobj1} becomes
+%\begin{align}
+%  (\Rctot \xc + \tcmut)^\top \Sigmait (\Rctot \xc + \tcmut) = 1
+%\end{align}
 \begin{multline}
@@
   \\
-  + \tcmut^\top \Sigmait \tcmut = 1
+  + \tcmut^\top \Sigmait \tcmut = 1.
+\
+\label{equ:ellipsoidobj2}
 \end{multline}
-Let $\Sigmaic = \Rctot^\top \Sigmait \Rctot$ and $\muic = - \Rctot^\top
-\tcmut$
+Next, denote $\Sigmaic = \Rctot^\top \Sigmait \Rctot$ and $\muic = - \Rctot^\top
+\tcmut$, \eqref{equ:ellipsoidobj2} becomes
 \begin{multline}
@@
   \\
-  + \tcmut^\top \Sigmait \tcmut = 1
+  + \tcmut^\top \Sigmait \tcmut = 1.
 \end{multline}
-Let $\Sigmaicf = \frac{\Sigmaic}{1 - \tcmut^\top \Sigmait \tcmut +
-\muic^\top\Sigmaic\muic}$
+Finally, denote $\Sigmaicf = \frac{\Sigmaic}{1 - \tcmut^\top \Sigmait \tcmut +
+\muic^\top\Sigmaic\muic}$, we have the ellipsoid equation in camera coordinates
 \begin{align}
-(\xc - \muic)^\top\Sigmaicf(\xc - \muic) = 1
+(\xc - \muic)^\top\Sigmaicf(\xc - \muic) = 1.
+\label{equ:ellipsoidcam}
 \end{align}
 
-Hence, we have following expression for mean and sigma of ellipsoid:
+Therefore, the center $\muic$ and spread $\Sigmaicf$ of the ellipsoid representing the occupancy of $O_i$ in camera coordinates are expressed as
 \begin{align}
   \label{eq:ellipsoidMeanSigma}
-  \muic &= - \Rctot^\top \tcmut \\
+  \muic &= - \Rctot^\top \tcmut, \\
   \Sigmaicf &= \frac{\Sigmaic}
-{1 - \tcmut^\top \Sigmait \tcmut + \muic^\top\Sigmaic\muic}
+{1 - \tcmut^\top \Sigmait \tcmut + \muic^\top\Sigmaic\muic},
 \end{align}
+where $\Rctot$, $\tcmut$, $\Sigmaic$, $\Sigmait$ are derived as above.
 
+\begin{comment}
 \section{Projection of Ellipsoids to Image}
 \newcommand{\mubar}{\bar{\mu}_i}
-The perspective projection of an ellipsoid in general is not an ellipsoid in
-general. We approximate the projection of ellipsoid by projecting a slice
-through the ellipsoid.
+In general, the perspective projection of an ellipsoid to the image plane is not an ellipse.
+We describe below two reasonable approximate methods which project a slice of the ellipsoid to the image such that the projection is always an ellipse.
 
@@
 %
+\end{comment}
 
 \section{Other Energies for 3D Object Localization}
+We present in this section the details of other energies, namely dynamic and size energies (in addition to point track and detection bounding box energies), that are used in our localization experiment.
 
@@
 \subsection{Dynamic energy}
-Dynamics constraints should not only enforce smooth trajectories, but also the
-holonomic constraints.  The following energy adds a penalty if the change in
-position is not in direction of previous orientation.
-
+Dynamic energy imposes both temporal smoothness and holonomic constraints.
+In particular, holonomic constraints penalize changes in object position that are not in the direction of object orientation at the previous time step as
 \begin{align}
   \label{eq:totalPosTransitionEnergy}
-  \Energy{dyn-hol} = 1 - \ori{i}{t-1} \cdot (\pos{i}{t} - \pos{i}{t-1})
+  \Energy{dyn-hol} = 1 - \ori{i}{t-1} \cdot (\pos{i}{t} - \pos{i}{t-1}),
 \end{align}
-
-The following energy adds a penalty for change in position and orientation
-but a penalty for change in velocity is much better approximation. However, in
-a Markovian setting that would mean extending the state space of the car to
-include velocity.
-
+while temporal smoothness constraints add a penalty for unsmooth changes in object orientation and velocity over consecutive time steps as
 \begin{align}
-  \Energy{dyn-ori} &= \|\ori{i}{t} - \ori{i}{t-1}\|^2\\
-  \Energy{dyn-vel} &= \|(\pos{i}{t} - 2\pos{i}{t-1}) + \pos{i}{t-2}\|^2
+  \Energy{dyn-ori} &= \|\ori{i}{t} - \ori{i}{t-1}\|^2,\\
+  \Energy{dyn-vel} &= \|(\pos{i}{t} - 2\pos{i}{t-1}) + \pos{i}{t-2}\|^2.
 \end{align}
-
-As a result the dynamics are modeled by weighted combination of holonomic
-constraint and smoothness constraints.
-
+As a consequence, dynamic energy is expressed as a weighted combination of holonomic and smoothness constraints
 \begin{align}
-  \WEnergy{dyn} &= \WEnergy{dyn-hol} + \WEnergy{dyn-ori} + \WEnergy{dyn-vel}
+  \Energy{dyn} &= \WEnergy{dyn-hol} + \WEnergy{dyn-ori} + \WEnergy{dyn-vel},
 \end{align}
+where $\lambda_{\text{dyn-hol}}$, $\lambda_{\text{dyn-ori}}$ and $\lambda_{\text{dyn-vel}}$ are the weights of component energies.
 
 \subsection{Size energy}
-
-Prior can include among many other things the size prior on the car.
-
+Size energy imposes prior knowledge on object dimensions as
 \begin{align}
@@
   \Energy{size} &= (\dimsn{i} - \expDimsn)^\top\Sigma_{\expDimsn}^{-1}(\dimsn{i} -
-  \expDimsn)
+  \expDimsn),
 \end{align}
-
-where $\expDimsn$ is the mean TP dimensions and
-$\Sigma_{\expDimsn}$ is the correspondence covariance matrix.
+where $\expDimsn$ and $\Sigma_{\expDimsn}$ are respectively the mean and covariance of object dimensions obtained from the KITTI dataset.
 

### 2016-01-20 CVPR16/rebuttal.tex
add new files for rebuttal

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{2072} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{A Continuous Occlusion Model for Road Scene Understanding}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
\section{Introduction}

After receiving paper reviews, authors may optionally submit a rebuttal to address the reviewers' comments, which will be limited to a {\bf one page} PDF file.  Please follow the steps and style guidelines outlined below for submitting your author response.

Note that, following similar guidelines to previous CVPR conferences, the rebuttal is meant to address only the reviewers' comments and questions. It is not intended to add new material (theorems, algorithms, experiments) which was not included in the original submission. You may optionally add a figure, graph or proof to your rebuttal, but only to better illustrate your answer to the reviewers' comments. These additions must be minimal (as they are meant to address only the reviewers' comments). You must not use the rebuttal to add any new results or contributions.

The rebuttal must adhere to the same blind-submission as the original submission and must comply with this rebuttal-formatted template.

%-------------------------------------------------------------------------

\subsection{Response length}
Author responses must be no longer than 1 page in length including any references and figures.  Overlength responses will simply not be reviewed.  This includes responses where the margins and formatting are deemed to have been significantly altered from those laid down by this style guide.  Note that this \LaTeX\ guide already sets figure captions and references in a smaller font.

%------------------------------------------------------------------------
\section{Formatting your Response}

{\bf Make sure to update the paper title and paper ID in the appropriate place in the tex file.}

All text must be in a two-column format. The total allowable width of the text
area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54 cm) high.
Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch
(0.8 cm) space between them. The top margin should begin
1.0 inch (2.54 cm) from the top edge of the page.  The bottom margin should be
1-1/8 inches (2.86 cm) from the bottom edge of the page for $8.5 \times
11$-inch paper; for A4 paper, approximately 1-5/8 inches (4.13 cm) from the
bottom edge of the page.

Please number all of your sections and any displayed equations.  It is important
for readers to be able to refer to any particular equation.

Wherever Times is specified, Times Roman may also be used.  Main text should be
in 10-point Times, single-spaced. Section headings should be in 10 or 12 point
Times.  All paragraphs should be indented 1 pica (approx. 1/6 inch or 0.422
cm).  Figure and table captions should be 9-point Roman type as in
Figure~\ref{fig:onecol}.

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times, single-spaced,
at the end of your response. When referenced in the text, enclose the citation
number in square brackets, for example~\cite{Authors14}.  Where appropriate,
include the name(s) of editors of referenced books.

\begin{figure}[t]
\begin{center}
\fbox{\rule{0pt}{1.8in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
\end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.  Please ensure that any point you wish to make is resolvable in a printed copy of the response.  Resize fonts in figures to match the font in the body text, and choose line widths which render effectively in print.  Many readers (and reviewers), even of an electronic copy, will choose to print your response in order to read it.  You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use \verb+\includegraphics+, and to specify the  figure width as a multiple of the line width as in the example below
{\small\begin{verbatim}
   \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.eps}
\end{verbatim}
}

{\small
\bibliographystyle{ieee}
\bibliography{rebuttal}
}

\end{document}

### 2016-01-22 CVPR16/rebuttal.tex
1st draft

@@
 
+\usepackage{verbatim}
+\usepackage{bm}
+\usepackage{microtype}
+\usepackage{url}
+\usepackage{multirow}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{booktabs} % for better tables
+
+\usepackage{color}
+\newcommand{\hili}[1]{\colorbox{yellow}{#1}}
+
 % Include other packages here, before hyperref.
@@
 \usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+
+\input{preamble}
+\newcommand{\xmin}{x_\text{min}}
+\newcommand{\ymin}{y_\text{min}}
+\newcommand{\xmax}{x_\text{max}}
+\newcommand{\ymax}{y_\text{max}}
+\DeclareMathOperator*{\argmin}{\arg\min}
+\input{Source/drawingslib}
 
@@
 %%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
-\section{Introduction}
 
-After receiving paper reviews, authors may optionally submit a rebuttal to address the reviewers' comments, which will be limited to a {\bf one page} PDF file.
-Please follow the steps and style guidelines outlined below for submitting your author response.
+As suggested by Reviewers 1 and 2, we have added Table~\ref{tab:notations} for improving the exposition of our methods.
+In addition to feature tracks and detection bounding boxes, we use camera poses and 3D object bounding boxes (estimated respectively using SFM and assuming detection bounding boxes lie on the ground with priors on object dimensions) for computing object-point association probabilities and initializing 3D object localization methods.
 
-Note that, following similar guidelines to previous CVPR conferences, the rebuttal is meant to address only the reviewers' comments and questions.
-It is not intended to add new material (theorems, algorithms, experiments) which was not included in the original submission.
-You may optionally add a figure, graph or proof to your rebuttal, but only to better illustrate your answer to the reviewers' comments.
-These additions must be minimal (as they are meant to address only the reviewers' comments).
-You must not use the rebuttal to add any new results or contributions.
+\begin{table}\centering\footnotesize
+\begin{tabular}{|l|l|l|}
+\hline
+& Symbol & Description \\
+\hline
+\hline
+\multirow{2}{*}{\rotatebox{90}{Input}} & $\bu_j(t)$ & 2D feature track $j$ at time $t$ \\
+					   	& $\bb{i}$ & 2D detection bounding box of object $O_i$ at time $t$ \\
+\hline
+\hline
+\multirow{5}{*}{\rotatebox{90}{Estimated}} & $\bp^c(t)$ & Position of camera at time $t$ \\
+						& $\bomega^c(t)$ & Orientation of camera at time $t$ \\
+						& $\bp_0^i(t)$ & Initial position of object $O_i$ at time $t$ \\
+					    & $\bomega_0^i(t)$ & Initial orientation of object $O_i$ at time $t$ \\
+						& $\bB_0^i$ & Initial 3D dimensions of object $O_i$ (independent of time $t$) \\
 
-The rebuttal must adhere to the same blind-submission as the original submission and must comply with this rebuttal-formatted template.
+\hline
+\hline
+\multirow{4}{*}{\rotatebox{90}{Output}} & $P^{ij}_{\text{assoc}}$ & Probability of associating feature track $j$ with object $O_i$ \\	
+						& $\bp^i(t)$ & Position of object $O_i$ at time $t$ \\
+					    & $\bomega^i(t)$ & Orientation of object $O_i$ at time $t$ \\
+						& $\bB^i$ & 3D dimensions of object $O_i$ (independent of time $t$) \\
+\hline
+\end{tabular}
+\caption{Notation of input and output.}
+\label{tab:notations}
+\end{table}
 
-%-------------------------------------------------------------------------
+Reviewers 1 and 2 mentioned the coarse representation of objects (3D ellipsoids), our aim is to balance between the ease of analytical formulations and the practical requirements of object-point association.
+Reviewer 2 further said that we demonstrated only for a single but important object category (car), which is because it is the only one that we have ground truth data for (KITTI dataset), and there are very few obstacles to apply our methods to other categories as long as we have feature tracks and detection bounding boxes.
 
-\subsection{Response length}
-Author responses must be no longer than 1 page in length including any references and figures.
-Overlength responses will simply not be reviewed.
-This includes responses where the margins and formatting are deemed to have been significantly altered from those laid down by this style guide.
-Note that this \LaTeX\ guide already sets figure captions and references in a smaller font.
+Regarding the complicated graphical model and computational aspect, our current work focuses on the flexibility of our occlusion model, and there are many potential applications while object localization is one of them.
+Future work will invest in speeding up the inference.
+In the following, we will respond to each reviewer's comments:
 
-%------------------------------------------------------------------------
-\section{Formatting your Response}
+\section{Reviewer 1}
 
-{\bf Make sure to update the paper title and paper ID in the appropriate place in the tex file.}
+We thank Reviewer 1 for the suggestion of including the errors corresponding to the initial estimates in Table~\ref{tab:localization}, which clearly shows the benefits of energy minimization.
 
-All text must be in a two-column format. The total allowable width of the text
-area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54 cm) high.
-Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch
-(0.8 cm) space between them. The top margin should begin
-1.0 inch (2.54 cm) from the top edge of the page.  The bottom margin should be
-1-1/8 inches (2.86 cm) from the bottom edge of the page for $8.5 \times
-11$-inch paper; for A4 paper, approximately 1-5/8 inches (4.13 cm) from the
-bottom edge of the page.
+\begin{table}\centering\footnotesize
+\begin{tabular}{|l|l|l|}
+\hline
+Energy & t & dim \\
+\hline
+\hline
+Baseline & \hili{XXX} & \hili{XXX} \\
+Initialization & \hili{XXX} & \hili{XXX} \\
+$\EnergyTrackNoOcc + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$ 
+& 3.95  & 1.72\\        
+$\EnergyTrackNoOcc + \EnergyBBox +\EnergySize+\EnergyDyn$        
+& 4.81  & 2.16\\        
+$\EnergyTrack + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$      
+& 4.05  & {\bf 1.59}\\        
+$\EnergyTrack + \EnergyBBox +\EnergySize+\EnergyDyn$             
+& {\bf 3.24}  & 2.16\\
+\hline
+\end{tabular}
+\caption{Localization experiment results.}
+\label{tab:localization}
+\end{table}
 
-Please number all of your sections and any displayed equations.  It is important
-for readers to be able to refer to any particular equation.
+Equation 4: we use gradient occupancy vector $\nabla {f^i_{occ}}(\bx_j)$ since we want reflection probability to be high near object borders, $\max$ ensures that negative probability due to gradient in the direction opposite to the ray is clipped off, and squaring allows the function to be smooth near zero.
+We normalize $P^{ij}_{\textit{reflection}}(\lambda)$  with respect to different $\lambda$.
+Please refer to Figure 2 for an illustration of reflection probability.
 
-Wherever Times is specified, Times Roman may also be used.  Main text should be
-in 10-point Times, single-spaced. Section headings should be in 10 or 12 point
-Times.  All paragraphs should be indented 1 pica (approx. 1/6 inch or 0.422
-cm).  Figure and table captions should be 9-point Roman type as in
-Figure~\ref{fig:onecol}.
+We compute the normalization factor $Z'$ in Equation 13 numerically using importance sampling.
 
-%-------------------------------------------------------------------------
-\subsection{References}
+\section{Reviewer 2}
 
-List and number all bibliographical references in 9-point Times, single-spaced,
-at the end of your response. When referenced in the text, enclose the citation
-number in square brackets, for example~\cite{Authors14}.  Where appropriate,
-include the name(s) of editors of referenced books.
+Instead of using binary functions, we model objects by translucent functions, which not only accounts for object shape uncertainty but also allows a continuous occlusion model that remains amenable to continuous optimization tools.
 
-\begin{figure}[t]
-\begin{center}
-\fbox{\rule{0pt}{1.8in} \rule{0.9\linewidth}{0pt}}
-   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
-\end{center}
-   \caption{Example of caption.  It is set in Roman so that mathematics
-   (always set in Roman: $B \sin A = A \sin B$) may be included without an
-   ugly clash.}
-\label{fig:long}
-\label{fig:onecol}
-\end{figure}
+Section 4.2: our apologies, we have included all objects in the first equation as follows:
+\begin{multline*}
+  -\log{P(\{ \bp^i(t) , \bomega^i(t) , \bB^i \} | \{\bu_j(t)\} , \{\bb{i}\} )} = -Z + \\ 
+  \lambda_t \sum_{t=s_i}^{e_i} \EnergyTrack
+  + 
+  \lambda_d \sum_{t=s_i}^{e_i} \sum_{i=1}^N \EnergyBBox
+  + 
+  \lambda_{\text{dyn}} \sum_{i=1}^N \EnergyDyn
+  + 
+  \lambda_{\text{size}} \sum_{i=1}^N \EnergySize
+  \enspace,
+\end{multline*}
+and have excluded object poses from the previous time step in Equation 19 as below:
+\begin{align*}
+\Energy{detect}(\{ \relp{i}{t} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}.
+\end{align*}
 
-%-------------------------------------------------------------------------
-\subsection{Illustrations, graphs, and photographs}
+The number of objects is known a priori in our occlusion model (given by object tracking [2]) and is also provided to other methods such as BBox and RAS.
+Outlier feature tracks usually have high reprojection errors and hence low object-point association probabilities while outlier detection bounding boxes are likely to be removed by object tracking [2].
+We use \hili{XXX} sequences from KITTI dataset, which have total \hili{XXX} frames.
+After running object tracking [2], there are total \hili{XXX} objects survived.
 
-All graphics should be centered.
-Please ensure that any point you wish to make is resolvable in a printed copy of the response.
-Resize fonts in figures to match the font in the body text, and choose line widths which render effectively in print.
-Many readers (and reviewers), even of an electronic copy, will choose to print your response in order to read it.
-You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.
+In object-point association experiments, the baseline method (BBox) uses 3D bounding boxes (though they are only for depth ordering).
+The crucial question now is how to probabilistically weigh points closer to the boundary of the 3D bounding box less than points inside the box and our occlusion model is in fact a principle way to do that same thing.
 
-When placing figures in \LaTeX, it's almost always best to use \verb+\includegraphics+, and to specify the  figure width as a multiple of the line width as in the example below
-{\small\begin{verbatim}
-   \usepackage[dvips]{graphicx} ...
-   \includegraphics[width=0.8\linewidth]
-                   {myfile.eps}
-\end{verbatim}
-}
+In localization experiments, we have tried [33] on a few images and it has higher localization accuracy than our method, which is mostly due to its detailed shape model.
+However, it needs a database of CAD models, takes about 30 mins for inference on a single image, and is a discrete model which is not suitable for continuous optimization tools.
+Alternatively, we have added the suggested baseline which robustly fits a 3D bounding box on the reconstructed point cloud (by SFM within detection bounding boxes) and relies on priors on object dimensions for unobservable dimensions.
+We have included the results of this baseline in Table~\ref{tab:localization}.
 
-{\small
-\bibliographystyle{ieee}
-\bibliography{rebuttal}
-}
+\section{Reviewer 3}
+
+Transmission probability only indicates whether a ray is transmissible to a particular depth but does not provide information on which object obstructs the ray at that depth.
+Alternatively, this information is given by the reflection probability.
+Therefore, a combination of transmission and reflection probabilities is more suitable for explaining the image observations.
+
+Regarding the concern about the superiority of our method in Figure 5, we focus on a probabilistic method to incorporate all available information for occlusion reasoning and it is not provided by previous works (in a sense this was also the goal of [32][33] which use CAD models).
 

### 2016-01-22 CVPR16/rebuttal.tex
edit 1st draft

@@
 
-Equation 4: we use gradient occupancy vector $\nabla {f^i_{occ}}(\bx_j)$ since we want reflection probability to be high near object borders, $\max$ ensures that negative probability due to gradient in the direction opposite to the ray is clipped off, and squaring allows the function to be smooth near zero.
+Equation 4: we use gradient vector $\nabla {f^i_{occ}}(\bx_j)$ since we want reflection probability to be high near object borders, $\max$ ensures that negative probability due to gradient in the direction opposite to the ray is clipped off, and squaring allows the function to be smooth near zero.
 We normalize $P^{ij}_{\textit{reflection}}(\lambda)$  with respect to different $\lambda$.
@@
 The number of objects is known a priori in our occlusion model (given by object tracking [2]) and is also provided to other methods such as BBox and RAS.
-Outlier feature tracks usually have high reprojection errors and hence low object-point association probabilities while outlier detection bounding boxes are likely to be removed by object tracking [2].
+Outlier feature tracks usually have high reprojection errors and hence low object-point association probabilities while outlier detection bounding boxes are likely to be filtered out by object tracking [2].
 We use \hili{XXX} sequences from KITTI dataset, which have total \hili{XXX} frames.
@@
 
-In object-point association experiments, the baseline method (BBox) uses 3D bounding boxes (though they are only for depth ordering).
-The crucial question now is how to probabilistically weigh points closer to the boundary of the 3D bounding box less than points inside the box and our occlusion model is in fact a principle way to do that same thing.
+In object-point association experiments, the baseline method (BBox) uses 3D bounding boxes (despite simple depth ordering).
+The crucial question is how we can probabilistically weigh points closer to the boundary of the 3D bounding box less than points inside the box and our occlusion model is a principle way to implement that idea.
 
-In localization experiments, we have tried [33] on a few images and it has higher localization accuracy than our method, which is mostly due to its detailed shape model.
+In localization experiments, we have tested [33] on a few images and it has higher localization accuracy than our method, which is mostly due to its detailed shape model.
 However, it needs a database of CAD models, takes about 30 mins for inference on a single image, and is a discrete model which is not suitable for continuous optimization tools.
-Alternatively, we have added the suggested baseline which robustly fits a 3D bounding box on the reconstructed point cloud (by SFM within detection bounding boxes) and relies on priors on object dimensions for unobservable dimensions.
+Alternatively, we have added the suggested baseline which robustly fits a 3D bounding box on the reconstructed point cloud (by SFM within detection bounding boxes) and relies on object dimension priors for unobservable dimensions.
 We have included the results of this baseline in Table~\ref{tab:localization}.
@@
 Transmission probability only indicates whether a ray is transmissible to a particular depth but does not provide information on which object obstructs the ray at that depth.
-Alternatively, this information is given by the reflection probability.
-Therefore, a combination of transmission and reflection probabilities is more suitable for explaining the image observations.
+Alternatively, this information is given by reflection probability.
+Therefore, a combination of transmission and reflection probabilities is more suitable for explaining image observations.
 
-Regarding the concern about the superiority of our method in Figure 5, we focus on a probabilistic method to incorporate all available information for occlusion reasoning and it is not provided by previous works (in a sense this was also the goal of [32][33] which use CAD models).
+Regarding the concern about the superiority of our method in Figure 5, we focus on a principle method to probabilistically incorporate all available information for occlusion reasoning and it is not provided by previous works (in a sense this was also the goal of [32][33] which use CAD models).
 

### 2016-01-22 CVPR16/rebuttal.tex
Huy's complete draft

@@
 
-Regarding the complicated graphical model and computational aspect, our current work focuses on the flexibility of our occlusion model, and there are many potential applications while object localization is one of them.
+Regarding the complex graphical model and computational aspect, our current work focuses on the flexibility of our occlusion model, and there are many potential applications while object localization is one of them.
 Future work will invest in speeding up the inference.
@@
 
-Equation 4: we use gradient vector $\nabla {f^i_{occ}}(\bx_j)$ since we want reflection probability to be high near object borders, $\max$ ensures that negative probability due to gradient in the direction opposite to the ray is clipped off, and squaring allows the function to be smooth near zero.
-We normalize $P^{ij}_{\textit{reflection}}(\lambda)$  with respect to different $\lambda$.
+In Equation 4, we use gradient vector $\nabla {f^i_{occ}}(\bx_j)$ since we want reflection probability to be high near object borders, $\max$ ensures that negative probability due to gradient in the direction opposite to the ray is clipped off, and squaring allows the function to be smooth near zero.
+We normalize $P^{ij}_{\textit{reflection}}(\lambda)$  with respect to different $\lambda$ (our apologies, we will fix this).
 Please refer to Figure 2 for an illustration of reflection probability.
@@
 
-In localization experiments, we have tested [33] on a few images and it has higher localization accuracy than our method, which is mostly due to its detailed shape model.
-However, it needs a database of CAD models, takes about 30 mins for inference on a single image, and is a discrete model which is not suitable for continuous optimization tools.
-Alternatively, we have added the suggested baseline which robustly fits a 3D bounding box on the reconstructed point cloud (by SFM within detection bounding boxes) and relies on object dimension priors for unobservable dimensions.
-We have included the results of this baseline in Table~\ref{tab:localization}.
+In localization experiments, we have tested [33] on a few images.
+It has higher localization accuracy than our method, which is mostly due to its detailed shape model.
+However, it needs a database of CAD models, takes about 30 minutes for inference on a single image, and is a discrete model which is not suitable for continuous optimization tools.
+Alternatively, we have included in Table~\ref{tab:localization} the suggested baseline, which robustly fits a 3D bounding box on the reconstructed point cloud (by SFM within detection bounding boxes) and relies on object dimension priors for unobservable dimensions.
+
+In a sense Equation 4 reverts to a (squared) Lambertian reflection, which is basically a dot product between surface normal and light direction.
+
+We thank Reviewer 3 for pointing us to recent works on visibility modeling of scenes/point clouds and holistic scene understanding with fast MRF inference.
+These ideas look useful and we will cite these papers if accepted.
 
@@
 
-Regarding the concern about the superiority of our method in Figure 5, we focus on a principle method to probabilistically incorporate all available information for occlusion reasoning and it is not provided by previous works (in a sense this was also the goal of [32][33] which use CAD models).
+Regarding the concern about the superiority of our method in Figure 5, we focus on a principle method to probabilistically incorporate all available information for occlusion reasoning and it is not provided by previous works (in a sense this was also the goal of [32][33]).
+
+About the localization experiment results in Table~\ref{tab:localization}, we observe that using occlusion modeling for feature tracks and detection bounding boxes individually leads to higher translation errors, however using occlusion modeling for both of them yields lower translation errors.
+This is probably due to the values of the parameters that we empirically chose.
+
+For all other minor comments/typos, we will fix them if accepted.
 

### 2016-01-22 CVPR16/rebuttal.tex
Huy's complete draft

@@
 
-We thank Reviewer 3 for pointing us to recent works on visibility modeling of scenes/point clouds and holistic scene understanding with fast MRF inference.
+We thank Reviewer 2 for pointing us to recent works on visibility modeling of scenes/point clouds and indoor scene understanding with fast MRF inference.
 These ideas look useful and we will cite these papers if accepted.
@@
 About the localization experiment results in Table~\ref{tab:localization}, we observe that using occlusion modeling for feature tracks and detection bounding boxes individually leads to higher translation errors, however using occlusion modeling for both of them yields lower translation errors.
-This is probably due to the values of the parameters that we empirically chose.
+This is probably due to the values of parameters that we empirically chose.
 
-For all other minor comments/typos, we will fix them if accepted.
+We will fix all other minor comments/typos if accepted.
 

### 2016-01-23 CVPR16/rebuttal.tex
edit
Edit

@@
 Future work will invest in speeding up the inference.
-In the following, we will respond to each reviewer's comments:
+In the following, we respond to each reviewer's comments:
 
@@
 In Equation 4, we use gradient vector $\nabla {f^i_{occ}}(\bx_j)$ since we want reflection probability to be high near object borders, $\max$ ensures that negative probability due to gradient in the direction opposite to the ray is clipped off, and squaring allows the function to be smooth near zero.
-We normalize $P^{ij}_{\textit{reflection}}(\lambda)$  with respect to different $\lambda$ (our apologies, we will fix this).
+We normalize $P^{ij}_{\textit{reflection}}(\lambda)$  with respect to different $\lambda$ (our apologies, we will add a normalization factor).
 Please refer to Figure 2 for an illustration of reflection probability.

### 2016-01-25 CVPR16/Rebuttal2/rebuttal.tex
draft rebuttal

--- 2016-01-22 CVPR16/rebuttal.tex
@@
 
-%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
+We thank all the reviewers for their feedback, noting our work as interesting and novel.
 
-As suggested by Reviewers 1 and 2, we have added Table~\ref{tab:notations} for improving the exposition of our methods.
+\vspace{-0.4cm}
+\paragraph{(R18, R24) Define inputs and outputs:} As suggested, we will add Table~\ref{tab:notations} to improve exposition.
+
+%As suggested by Reviewers 1 and 2, we have added Table~\ref{tab:notations} for improving the exposition of our methods.
 In addition to feature tracks and detection bounding boxes, we use camera poses and 3D object bounding boxes (estimated respectively using SFM and assuming detection bounding boxes lie on the ground with priors on object dimensions) for computing object-point association probabilities and initializing 3D object localization methods.
 
-\begin{table}\centering\footnotesize
+%\vspace{-0.2cm}
+\begin{table}[!!t]
+\centering\footnotesize
 \begin{tabular}{|l|l|l|}
@@
 					    & $\bomega_0^i(t)$ & Initial orientation of object $O_i$ at time $t$ \\
-						& $\bB_0^i$ & Initial 3D dimensions of object $O_i$ (independent of time $t$) \\
+						& $\bB_0^i$ & Initial 3D dimensions of object $O_i$ (independent of $t$) \\
 
@@
 \end{tabular}
+\vspace{-0.2cm}
 \caption{Notation of input and output.}
 \label{tab:notations}
+\vspace{-0.5cm}
 \end{table}
 
-Reviewers 1 and 2 mentioned the coarse representation of objects (3D ellipsoids), our aim is to balance between the ease of analytical formulations and the practical requirements of object-point association.
+\vspace{-0.4cm}
+\paragraph{(R18, R24) Ellipsoid representation of objects:} Our goal is to balance an analytical formulation towards a continuous probabilistic model, with a shape representation that still yields good results for objects such as cars.
+
+\vspace{-0.4cm}
+\paragraph{(R24) Single but important category of cars:} For evaluation, the KITTI dataset has ground truth 3D boxes only for cars.
+Our model is applicable for any rigid object type for which bounding boxes and point tracks may be obtained.
+
+%Our model is equally applicable to categories such as trucks or pedestrians, but the KITTI dataset has ground truth for evaluation only for cars.
+
+%Reviewers 1 and 2 mentioned the coarse representation of objects (3D ellipsoids), our aim is to balance between the ease of analytical formulations and the practical requirements of object-point association.
 Reviewer 2 further said that we demonstrated only for a single but important object category (car), which is because it is the only one that we have ground truth data for (KITTI dataset), and there are very few obstacles to apply our methods to other categories as long as we have feature tracks and detection bounding boxes.
 
-Regarding the complex graphical model and computational aspect, our current work focuses on the flexibility of our occlusion model, and there are many potential applications while object localization is one of them.
+\vspace{-0.4cm}
+\paragraph{(R24) Complex graphical model for localization:} Our intent is to showcase the flexibility of our occlusion model, which can be used for multiple applications such as point track association or 3D localization.
+Simplified graphical models and faster inference in a particular application are subjects of our future work.
+
+%Regarding the complex graphical model and computational aspect, our current work focuses on the flexibility of our occlusion model, and there are many potential applications while object localization is one of them.
 Future work will invest in speeding up the inference.

### 2016-01-25 CVPR16/rebuttal2.tex
draft rebuttal

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{verbatim}
\usepackage{bm}
\usepackage{microtype}
\usepackage{url}
\usepackage{multirow}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{booktabs} % for better tables

\usepackage{color}
\newcommand{\hili}[1]{\colorbox{yellow}{#1}}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

\input{preamble}
\newcommand{\xmin}{x_\text{min}}
\newcommand{\ymin}{y_\text{min}}
\newcommand{\xmax}{x_\text{max}}
\newcommand{\ymax}{y_\text{max}}
\DeclareMathOperator*{\argmin}{\arg\min}
\input{Source/drawingslib}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{2072} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{A Continuous Occlusion Model for Road Scene Understanding}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

We thank all the reviewers for their feedback, noting our work as interesting and novel.

\vspace{-0.4cm}
\paragraph{R18, R24: Define inputs and outputs} As suggested, we will add Table~\ref{tab:notations} in final version to improve exposition.

\vspace{-0.4cm}
\paragraph{R18, R24: Ellipsoid representation of objects} Our goal is to balance an analytical formulation for a tractable, continuous probabilistic model, with a shape representation that still yields good results for objects such as cars.

\vspace{-0.4cm}
\paragraph{R18: Eqns 4 and 13}
In Eqn 4, the gradient $\nabla {f^i_{occ}}(\bx_j)$ encourages reflection probability to be high near object boundaries, $\max$ ensures that negative probability due to gradient in the direction opposite to the ray is clipped off and squaring allows the function to be smooth near zero. We normalize $P^{ij}_{\textit{reflection}}(\lambda)$  with respect to $\lambda$. We will make these clearer in the final version. Figure 2 illustrates the reflection probability. We compute the normalization factor $Z'$ in Eqn 13 numerically using importance sampling.

\vspace{-0.4cm}
\paragraph{R18, R24: Initialization}
We initialize by fitting a 3D bounding box to detected bounding boxes and estimated ground plane, with a size prior. Initialization errors are \hili{XXX}\% for t and \hili{XXX}\% for dim. They show advantage of our energy minimization and we will add them to Table 2.

\vspace{-0.4cm}
\paragraph{R24: Single but important category of cars} For evaluation, the KITTI dataset has ground truth 3D boxes only for cars. Our model is applicable for any rigid object type for which bounding boxes and point tracks may be obtained.

\vspace{-0.4cm}
\paragraph{R24: Complex graphical model for localization} Our intent is to showcase the flexibility of our occlusion model, which can be used for multiple applications such as point track association or 3D localization. Simplified graphical models and faster inference in a particular application are important subjects of our future work.

\vspace{-0.4cm}
\paragraph{R24: Real-valued occupancy functions}
We model objects as translucent, which not only accounts for shape uncertainty but also allows a probabilistic occlusion model amenable to continuous optimization tools.

\vspace{-0.4cm}
\paragraph{R24: Baselines}
For object-point association, the BBox baseline uses 3D bounding boxes with simple depth ordering. For suggested baseline with less weight closer to the boundary -- in a sense, our association probability is a principled way to compute such a weight. For localization, we note that [33] does not account for point tracks and as R24 notes, uses a database of highly detailed CAD models and discrete modeling, so is not directly comparable. We thank R24 for the suggested baseline that fits a 3D bounding box on the reconstructed point cloud (using SFM within detection bounding boxes), yielding \hili{XXX}\% error in t and \hili{XXX}\% in dim. We will add these in Table 2.
%the results are shown in Table \ref{tab:localization}. 
Here, we rely on size priors for unobservable dimensions in traffic scenes (say, when 3D points on only back of car are visible).

\vspace{-0.4cm}
\paragraph{R24: Typos in equations}
Thanks, $\cE_{\textrm{dyn}}$ and $\cE_{\textrm{size}}$ terms must be summed over all objects ($\cE_{\textrm{track}}$ in Eqn 15 already is), dependence on $\{ \Omega^i (t-1) \}_i$ in Eqn 19 must be dropped.

\vspace{-0.4cm}
\paragraph{R24: Number of objects} 
This is known a priori in our occlusion model (from object tracking [2]) and is also provided to other methods such as BBox and RAS.

\vspace{-0.4cm}
\paragraph{R24: Handling outliers} 
As noted by R24, outliers are inherently handled in our model. Outlier tracks usually have high reprojection errors and thus, low association probabilities. Additionally, outlier detection bounding boxes are likely to be filtered out by object tracking.

\vspace{-0.4cm}
\paragraph{R24: Sequences for experiments} 
We use all the sequences in the KITTI raw dataset (\hili{XXX} sequences, \hili{XXX} frames, \hili{XXX} object tracks).

\vspace{-0.4cm}
\paragraph{R24: Related works}
Thanks, final version will cite these.

\begin{table}[!!t]
\centering\footnotesize
\begin{tabular}{|l|l|l|}
\hline
 & Symbol & Description \\
\hline
\hline
\multirow{2}{*}{\rotatebox{90}{Input}} & $\bu_j(t)$ & 2D feature track $j$ at time $t$ \\
 & $\bb{i}$ & 2D detection bounding box of object $O_i$ at time $t$ \\
\hline
\hline
\multirow{5}{*}{\rotatebox{90}{Estimated}} & $\bp^c(t)$ & Position of camera at time $t$ \\
 & $\bomega^c(t)$ & Orientation of camera at time $t$ \\
 & $\bp_0^i(t)$ & Initial position of object $O_i$ at time $t$ \\
 & $\bomega_0^i(t)$ & Initial orientation of object $O_i$ at time $t$ \\
 & $\bB_0^i$ & Initial 3D dimensions of object $O_i$ (independent of $t$) \\
\hline
\hline
\multirow{4}{*}{\rotatebox{90}{Output}} & $P^{ij}_{\text{assoc}}$ & Probability of associating feature track $j$ with object $O_i$ \\	
 & $\bp^i(t)$ & Position of object $O_i$ at time $t$ \\
 & $\bomega^i(t)$ & Orientation of object $O_i$ at time $t$ \\
 & $\bB^i$ & 3D dimensions of object $O_i$ (independent of time $t$) \\
\hline
\end{tabular}
\vspace{-0.2cm}
\caption{Notation of input and output.}
\label{tab:notations}
\vspace{-0.5cm}
\end{table}

\vspace{-0.4cm}
\paragraph{R26: Superiority over baselines}
Figure 5 is a reasonable comparison along with Table 1 which provides separate results for static and dynamic objects. Methods like BM and RAS fundamentally cannot handle point tracks on static objects. BBox does start with both depth and motion information, but makes a hard assignment. In contrast, our formulation can incorporate point tracks, bounding boxes and detection scores in a unified probabilistic framework.

\vspace{-0.4cm}
\paragraph{R26: Role of reflection and transmission probabilities}
Transmission probability only indicates whether a ray is transmissible to a particular depth, reflection probability indicates which object obstructs the ray at that depth. Thus, a combination of transmission and reflection probabilities is necessary to explain image observations. Lines 260-274 describe this intuition.

\vspace{-0.4cm}
\paragraph{R26: Increase in error with occlusion modeling}
We empirically choose parameters to minimize energy with both bounding box and point track occlusions. The same parameters are used for all experiments. Thus, error might be higher when modeling tracks or bounding boxes individually, but low when considered jointly. These parameters can be learned for a particular localization application, but our focus is more general -- to show that a continuous probabilistic occlusion model can be designed which is flexible enough to simultaneously handle point tracks and bounding boxes.

\vspace{-0.4cm}
\paragraph{R26: Parameters}
The final version will include a detailed list of parameters.

%% \begin{table}\centering\footnotesize
%% \begin{tabular}{|l|l|l|}
%% \hline
%% Energy & t & dim \\
%% \hline
%% \hline
%% Initialization & \hili{XXX} & \hili{XXX} \\
%% Baseline suggested by R24 & \hili{XXX} & \hili{XXX} \\
%% %$\EnergyTrackNoOcc + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$ & 3.95  & 1.72\\        
%% %$\EnergyTrackNoOcc + \EnergyBBox +\EnergySize+\EnergyDyn$ & 4.81  & 2.16\\        
%% %$\EnergyTrack + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$ & 4.05  & {\bf 1.59}\\        
%% %$\EnergyTrack + \EnergyBBox +\EnergySize+\EnergyDyn$ & {\bf 3.24}  & 2.16\\
%% \hline
%% \end{tabular}
%% \vspace{-0.2cm}
%% \caption{Localization experiment results.}
%% \label{tab:localization}
%% \vspace{-0.5cm}
%% \end{table}

%In a sense Equation 4 reverts to a (squared) Lambertian reflection, which is basically a dot product between surface normal and light direction.

%We thank Reviewer 2 for pointing us to recent works on visibility modeling of scenes/point clouds and indoor scene understanding with fast MRF inference. These ideas look useful and we will cite these papers if accepted.

%% Section 4.2: our apologies, we have included all objects in the first equation as follows:
%% \begin{multline*}
%%   -\log{P(\{ \bp^i(t) , \bomega^i(t) , \bB^i \} | \{\bu_j(t)\} , \{\bb{i}\} )} = -Z + \\ 
%%   \lambda_t \sum_{t=s_i}^{e_i} \EnergyTrack
%%   + 
%%   \lambda_d \sum_{t=s_i}^{e_i} \sum_{i=1}^N \EnergyBBox
%%   + 
%%   \lambda_{\text{dyn}} \sum_{i=1}^N \EnergyDyn
%%   + 
%%   \lambda_{\text{size}} \sum_{i=1}^N \EnergySize
%%   \enspace,
%% \end{multline*}
%% and have excluded object poses from the previous time step in Equation 19 as below:
%% \begin{align*}
%% \Energy{detect}(\{ \relp{i}{t} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}.
%% \end{align*}

%The crucial question is how we can probabilistically weigh points closer to the boundary of the 3D bounding box less than points inside the box and our occlusion model is a principle way to implement that idea.

%In localization experiments, we have tested [33] on a few images. It has higher localization accuracy than our method, which is mostly due to its detailed shape model. However, it needs a database of CAD models, takes about 30 minutes for inference on a single image, and is a discrete model which is not suitable for continuous optimization tools. Alternatively, we have included in Table~\ref{tab:localization} the suggested baseline, which robustly fits a 3D bounding box on the reconstructed point cloud (by SFM within detection bounding boxes) and relies on object dimension priors for unobservable dimensions.

%As suggested by Reviewers 1 and 2, we have added Table~\ref{tab:notations} for improving the exposition of our methods. In addition to feature tracks and detection bounding boxes, we use camera poses and 3D object bounding boxes (estimated respectively using SFM and assuming detection bounding boxes lie on the ground with priors on object dimensions) for computing object-point association probabilities and initializing 3D object localization methods.

%Regarding the complex graphical model and computational aspect, our current work focuses on the flexibility of our occlusion model, and there are many potential applications while object localization is one of them. Future work will invest in speeding up the inference. In the following, we will respond to each reviewer's comments:

%The number of objects is known a priori in our occlusion model (given by object tracking [2]) and is also provided to other methods such as BBox and RAS. Outlier feature tracks usually have high reprojection errors and hence low object-point association probabilities while outlier detection bounding boxes are likely to be filtered out by object tracking [2]. We use \hili{XXX} sequences from KITTI dataset, which have total \hili{XXX} frames. After running object tracking [2], there are total \hili{XXX} objects survived.

%In object-point association experiments, the baseline method (BBox) uses 3D bounding boxes (despite simple depth ordering). The crucial question is how we can probabilistically weigh points closer to the boundary of the 3D bounding box less than points inside the box and our occlusion model is a principle way to implement that idea.

%In localization experiments, we have tested [33] on a few images. It has higher localization accuracy than our method, which is mostly due to its detailed shape model. However, it needs a database of CAD models, takes about 30 minutes for inference on a single image, and is a discrete model which is not suitable for continuous optimization tools. Alternatively, we have included in Table~\ref{tab:localization} the suggested baseline, which robustly fits a 3D bounding box on the reconstructed point cloud (by SFM within detection bounding boxes) and relies on object dimension priors for unobservable dimensions.

%Our model is equally applicable to categories such as trucks or pedestrians, but the KITTI dataset has ground truth for evaluation only for cars.

%Reviewers 1 and 2 mentioned the coarse representation of objects (3D ellipsoids), our aim is to balance between the ease of analytical formulations and the practical requirements of object-point association. Reviewer 2 further said that we demonstrated only for a single but important object category (car), which is because it is the only one that we have ground truth data for (KITTI dataset), and there are very few obstacles to apply our methods to other categories as long as we have feature tracks and detection bounding boxes.

%Transmission probability only indicates whether a ray is transmissible to a particular depth but does not provide information on which object obstructs the ray at that depth. Alternatively, this information is given by reflection probability. Therefore, a combination of transmission and reflection probabilities is more suitable for explaining image observations.

%Regarding the concern about the superiority of our method in Figure 5, we focus on a principle method to probabilistically incorporate all available information for occlusion reasoning and it is not provided by previous works (in a sense this was also the goal of [32][33]).

%About the localization experiment results in Table~\ref{tab:localization}, we observe that using occlusion modeling for feature tracks and detection bounding boxes individually leads to higher translation errors, however using occlusion modeling for both of them yields lower translation errors. This is probably due to the values of parameters that we empirically chose.

%We will fix all other minor comments/typos if accepted.

\end{document}

### 2016-01-25 CVPR16/Rebuttal2/Source/_BACKUP_intro.tex
draft rebuttal

--- 2015-11-06 CVPR16/Source/intro.tex
@@
 This is especially significant when objects in 3D space occlude each other with respect to the camera viewpoint.
-In recent years, we have seen remarkable progress in various fields that enable scene understanding, such as structure from motion (SFM) and object detection.
+In recent years, we have seen remarkable progress in various fields that enable scene understanding, such as structure from motion and object detection.
 However, occlusions still present a difficult challenge, with the difficulty of physically modeling them being a major bottleneck.
@@
 This allows assigning probabilities for each point in space belonging to an object, which can explicitly explain image observations and reason about occlusions.
-This is in contrast to prior works that consider occlusions in 2D, either through discrete occluder patterns or models that are not physically interpretable.
+This is in contrast to prior works that consider occlusions in 2D, or through discrete occluder patterns that are not physically interpretable.
 
@@
 While previous approaches to handling occlusion are application-dependent, ours is physically-inspired, thus, flexible enough to be used in a variety of scenarios.
-In this paper, we show that our theory can be used for modeling the association of 3D SFM points with static or dynamic objects (Section \ref{sec:association}), as well as modeling object detection scores in applications like 3D localization (Section \ref{sec:localization}).
-We demonstrate application of our formulations for road scenes from the KITTI dataset \cite{Geiger_etal_2012}.
+In this paper, we show that our theory can be used for modeling the association of 3D structure from motion points with static or dynamic objects, as well as modeling object detection scores in applications like 3D localization.
+We demonstrate application of our formulations for road scenes from the KITTI dataset.
 
-In particular, assigning 2D point tracks to independently moving, but potentially occluding, objects is a fundamental challenge in computer vision problems such as multibody SFM \cite{Ozden_etal_2010}.
+Assigning 2D point tracks to independently moving, but potentially occluding, objects is a fundamental challenge in computer vision problems such as multibody SFM \cite{Ozden_etal_2010}.
 Recent works use motion segmentation \cite{Rao_etal_2010,Brox_Malik_2010} as a precursor to localizing moving objects, which often suffices for moving objects \cite{Tron_Vidal_2007} and has been considered for multibody SFM \cite{Kundu_etal_2011}.
@@
 %In contrast, we leverage the success of 
-Indeed, we show in Section \ref{sec:experiments} that our point track association outperforms state-of-the-art motion segmentation methods, as well as a baseline that uses detection bounding boxes but does not consider occlusions.
+Indeed, we show that our point track association outperforms state-of-the-art motion segmentation methods, as well as a baseline that uses detection bounding boxes but does not consider occlusions.
 
-Another potential application of our proposed model is towards 3D localization in road scenes.
+As another important contribution, we examine the applicability of our proposed model to 3D localization in autonomous driving.
 Prior works such as \cite{Song_Chandraker_2014} combine information from point tracks and detection bounding boxes, but do not consider occlusions for either.
@@
 To summarize, our main contributions are:
-\vspace{-0.2cm}
-\begin{tight_itemize}
-%\setlength\itemsep{0cm}
-\item A novel theoretical model for handling occlusions that is continuous and formulated in 3D.
-\item Unified occlusion handling in various applications, such as 3D points in SFM and bounding boxes in object detection.
+\begin{itemize}
+\setlength\itemsep{0cm}
+\item A novel theoretical model for handling occlusions that is continuous and 3D.
+\item Unification of occlusion handling in different applications, such as points tracks in SFM and object bounding boxes in detection.
 \item Application of our model to association of point tracks with both static and moving objects, improving over motion segmentation and occlusion-unaware baselines.
 \item Application of our unified formulation to 3D localization of traffic participants in road scenes.
-\end{tight_itemize}
+\end{itemize}
 
@@
 
-%The rest of the paper is organized as follows: Section~\ref{sec:related} discusses related work.
+The rest of the paper is organized as follows: Section~\ref{sec:related} discusses related work.
 Section~\ref{sec:setup} describes the proposed continuous occlusion model for road scene understanding.

### 2016-01-25 CVPR16/Rebuttal2/Source/contBBoxModel.tex
draft rebuttal

--- 2015-11-06 CVPR16/Source/contBBoxModel.tex
@@
-\subsubsection{Continuous bounding box energy with occlusion}
-
+\vspace{-0.3cm}
+\paragraph{Continuous bounding box energy with occlusion}
 Object detection is usually followed by non-maximal suppression that results in discarding similar bounding boxes.

### 2016-01-25 CVPR16/Rebuttal2/Source/discussions.tex
draft rebuttal

--- 2015-11-06 CVPR16/Source/discussions.tex
@@
 
-We have presented a continuous model for occlusion modeling in 3D.
-A key advantage is its physically-inspired modeling that lends flexibility towards occlusion reasoning for various elements of scene understanding, such as point tracks, object detection bounding boxes and scores.
+We have presented a theoretically novel continuous model for occlusion reasoning in 3D.
+A key advantage is its physical inspiration that lends flexibility towards occlusion reasoning for varied elements of scene understanding, such as point tracks, object detection bounding boxes and detection scores.
 We demonstrate unified modeling for different applications such as point tracks associations and 3D localization.

### 2016-01-25 CVPR16/Rebuttal2/Source/experiments.tex
draft rebuttal

--- 2015-11-06 CVPR16/Source/experiments.tex
@@
 From these point tracks, we create four different sets of input point tracks, namely all point tracks, occluded point tracks, dynamic point tracks and dynamic and occluded point tracks, to examine various aspects of the methods (our method focuses on occlusion scenes while RAS and BM favour dynamic scenes).
-In addition to point tracks, the parameters of all TPs estimated by the method~\cite{Song_Chandraker_2014} are provided to our method (for computing association probability) and the baseline method (for depth ordering).
+In addition to point tracks, the parameters of all objects estimated by the method of \cite{Song_Chandraker_2015} are provided to our method (for computing association probability) and the baseline method (for depth ordering).
 

### 2016-01-25 CVPR16/Rebuttal2/Source/experiments2.tex
draft rebuttal

--- 2015-11-06 CVPR16/Source/experiments2.tex
@@
 \subsection{Association Experiments}
-\vspace{-0.2cm}
+%\vspace{-0.2cm}
 \paragraph{Setup}
@@
 %\includegraphics[trim=1.0in 0.4in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
-\includegraphics[width=0.9\textwidth]{graphics/figure5.png}
+\includegraphics[width=0.95\textwidth]{graphics/figure5.png}
   \vspace{-0.3cm}
@@
 Note that our method can handle occlusions in both static and dynamic scenes, but motion segmentation focuses on dynamic scenes.
-For a complete evaluation, we create organize the point tracks into four sets: all point tracks, occluded point tracks, dynamic point tracks and dynamic as well as occluded point tracks.
+For a complete evaluation, we organize the point tracks into four sets: all point tracks, occluded point tracks, dynamic point tracks and dynamic as well as occluded point tracks.
 In addition to point tracks, the parameters of all objects (cars) estimated by the method of \cite{Song_Chandraker_2015} are provided to our method (for computing association probability) and the baseline BBox method (for depth ordering).
@@
 \subsection{Localization Experiments}
-We report errors in translation error and dimension estimates, measured in meters per car, in Table~\ref{tab:localizationExperiment}.
+We report errors in translation and dimension estimates, measured in meters per car, in Table~\ref{tab:localizationExperiment}.
+Average depth of cars in the dataset is approximately $20$ meters.
 We compare four combinations of energies.
-The energy $\EnergyTrackNoOcc$ represents the point tracks energy without accounting for occlusion, that is, we model $\EnergyTrack$ in the absence of $\Ptransmission$.
+The energy $\EnergyTrackNoOcc$ represents the point tracks energy without accounting for occlusion, that is, we model $\EnergyTrack$ in the absence of $a^{ij} (\lambda)$.
 Similarly, $\EnergyBBoxNoOcc$ is the energy without the modification of $\Lambda_k$ that accounts for occlusion.
-The results show that the use of continuous occlusion model improves the localization accuracy in terms of the translation error, which is he most significant metric affected by all cues.
-Occlusion modeling for point tracks is always beneficial, while that for detection improves localization, but penalizes dimension since we explicitly allow greater uncertainty in occluded edges of the bounding box.
+We observe that the use of the continuous occlusion model improves the localization accuracy in terms of the translation error, which is the most significant metric affected by all cues.
+Occlusion modeling for detection increases dimension error since we explicitly allow greater uncertainty in occluded edges of the bounding box.
 Note that none of our energies optimize yaw angles for static objects, which can be handled in practice through either the detector orientation or external information such as lane geometry.

### 2016-01-25 CVPR16/Rebuttal2/Source/setup.tex
draft rebuttal

\section{Continuous Occlusion Model}
\label{sec:setup}
We want to solve the problem of segmenting point tracks into object so that the
consensus of points can be used draw inferences about the object. In particular
given a set of correspondence points on consecutive frames $(\trackpj{t},
\trackpj{t-1})$, object localizations $\relp{i}{t}$ and object dimensions
$\dimsn{i}$ we want to figure out which points belong to which object. We call
this the association problem. Even if the pose of the object is not immediately
available we propose the use of hypothesized pose of the object as we show in
the localization estimation experiments.

\def\TP{TP}
A common way of modeling objects, especially traffic participants (TP), in road
scene understanding context is to model the TP as cuboids. However modelingTPs
as cuboids fails to model the uncertainty in the pose and dimensions of TP. Moreover, the cuboid model introduces discontinuity in the problem formulation making
optimization difficulty. With this motivation we propose the use of soft
ellipsoids for modeling TPs that leads to continuous occlusion model that 
accounts for uncertainty in TP position and dimensions.

### 2016-01-25 CVPR16/rebuttal2.tex
changes

@@
 
-\vspace{-0.4cm}
-\paragraph{R24: Handling outliers} 
-As noted by R24, outliers are inherently handled in our model.
+%\vspace{-0.4cm}
+%\paragraph{R24: Handling outliers} 
+%As noted by R24, outliers are inherently handled in our model.
 Outlier tracks usually have high reprojection errors and thus, low association probabilities.
@@
 
-\vspace{-0.4cm}
-\paragraph{R24: Sequences for experiments} 
-We use all the sequences in the KITTI raw dataset (\hili{XXX} sequences, \hili{XXX} frames, \hili{XXX} object tracks).
+%\vspace{-0.4cm}
+%\paragraph{R24: Sequences for experiments} 
+%We use all the sequences in the KITTI raw dataset (\hili{XXX} sequences, \hili{XXX} frames, \hili{XXX} object tracks).
 
@@
 \paragraph{R24: Related works}
-Thanks, final version will cite these.
+Thank you, we will cite them.
 
@@
 \paragraph{R26: Superiority over baselines}
-Figure 5 is a reasonable comparison along with Table 1 which provides separate results for static and dynamic objects.
-Methods like BM and RAS fundamentally cannot handle point tracks on static objects.
+Figure 5 may be considered with Table 1, which provides separate results for static and dynamic objects.
+Methods like BM and RAS cannot handle point tracks on static objects.
 BBox does start with both depth and motion information, but makes a hard assignment.
@@
 \paragraph{R26: Parameters}
-The final version will include a detailed list of parameters.
+We use \hili{XXX}. The final version will include a detailed list of parameters.
 

### 2016-01-25 CVPR16/Source/occlusion.tex
changes

@@
   \vspace{-0.3cm}
-  \caption{\small We represent traffic participants as soft ellipsoids which lead to formulation of transmision and reflection probability.
-This figure shows the reflection probability for the first car which is highest around the camera facing face of the car.
-Also note that transmission probability is inversly proportional to occupancy.}
+  \caption{\small We represent objects as translucent ellipsoids which allows formulation of transmision and reflection probabilities.
+This figure shows the reflection probability for the first object (violet) which is highest closer to the camera.
+Also note that the transmission probability is inversely proportional to occupancy.}
   \label{fig:reflectiontransimission}

### 2016-01-25 CVPR16/supplementarymaterial.tex
changes

@@
 \usepackage{booktabs} % for better tables
+\usepackage{microtype}
 
@@
 \begin{document}
-\title{A Continuous Occlusion Model for Road Scene Understanding}
+\title{Supplement: A Continuous Occlusion Model for Road Scene Understanding}
 
@@
 \label{sec:sigmacomputation}
-Here we present how to compute the parameters of ellipsoids representing the occupancy of traffic participants.
-For an object $O_i$, let $\bB^i = [l~w~h]$ be its 3D dimensions, where $l$, $w$ and $h$ are respectively its length, width, and height on the ground plane, we are interested in calculating the center $\muic$ and spread $\Sigmaicf$ of the ellipsoid representing the occupancy of $O_i$ with respect to the camera coordinate system $\cC$ of the current frame.
+In this section, we present computation of the parameters of ellipsoids representing occupancy of traffic participants.
+For an object $O_i$, let $\bB^i = [l~w~h]$ be its 3D dimensions, where $l$, $w$ and $h$ are its length, width and height on the ground plane, respectively.
+We wish to calculate the center $\muic$ and spread $\Sigmaicf$ of the ellipsoid representing the occupancy of $O_i$ with respect to the camera coordinate system $\cC$ of the current frame.
 
-Consider an object coordinate system $\cO$, which has the same orthonormal axes as the camera coordinate system and the origin at the projected point of the object center to the ground plane.
+Consider an object coordinate system $\cO$, which has the same orthonormal axes as the camera coordinate system and the origin at the projected point of the object center on the ground plane.
 For an object $O_i$, the center $\muit$ and spread $\Sigmait$ of the ellipsoid representing the occupancy of $O_i$ in the object coordinate system are expressed as
@@
 \end{align}
-
 In object coordinates, the ellipsoid equation is written as
@@
 
-Let $\tcmut = \tctot - \muit$, \eqref{equ:ellipsoidobj1} becomes
+Let $\tcmut = \tctot - \muit$, then \eqref{equ:ellipsoidobj1} becomes
 %\begin{align}
@@
 Next, denote $\Sigmaic = \Rctot^\top \Sigmait \Rctot$ and $\muic = - \Rctot^\top
-\tcmut$, \eqref{equ:ellipsoidobj2} becomes
+\tcmut$, then \eqref{equ:ellipsoidobj2} becomes
 \begin{multline}
@@
 \end{multline}
-Finally, denote $\Sigmaicf = \frac{\Sigmaic}{1 - \tcmut^\top \Sigmait \tcmut +
+Finally, denoting $\Sigmaicf = \displaystyle\frac{\Sigmaic}{1 - \tcmut^\top \Sigmait \tcmut +
 \muic^\top\Sigmaic\muic}$, we have the ellipsoid equation in camera coordinates
@@
 \section{Other Energies for 3D Object Localization}
-We present in this section the details of other energies, namely dynamic and size energies (in addition to point track and detection bounding box energies), that are used in our localization experiment.
+This section provides the details of other energies, namely dynamic and size energies (in addition to point track and detection bounding box energies already presented in the main paper), that are used in our localization experiment.
 
@@
 Dynamic energy imposes both temporal smoothness and holonomic constraints.
-In particular, holonomic constraints penalize changes in object position that are not in the direction of object orientation at the previous time step as
+In particular, holonomic constraints penalize changes in object position that are not in the direction of object orientation at the previous time step, as
 \begin{align}
   \label{eq:totalPosTransitionEnergy}
-  \Energy{dyn-hol} = 1 - \ori{i}{t-1} \cdot (\pos{i}{t} - \pos{i}{t-1}),
+  \Energy{dyn-hol} = 1 - \ori{i}{t-1} \cdot (\pos{i}{t} - \pos{i}{t-1}).
 \end{align}
-while temporal smoothness constraints add a penalty for unsmooth changes in object orientation and velocity over consecutive time steps as
+Temporal smoothness constraints add a penalty for unsmooth changes in object orientation and velocity over consecutive time steps, as
 \begin{align}
@@
 \end{align}
-As a consequence, dynamic energy is expressed as a weighted combination of holonomic and smoothness constraints
+The total dynamic energy is expressed as a weighted combination of holonomic and smoothness constraints
 \begin{align}
@@
 \end{align}
-where $\lambda_{\text{dyn-hol}}$, $\lambda_{\text{dyn-ori}}$ and $\lambda_{\text{dyn-vel}}$ are the weights of component energies.
+where $\lambda_{\text{dyn-hol}}$, $\lambda_{\text{dyn-ori}}$ and $\lambda_{\text{dyn-vel}}$ are the weights of the component energies.
 
@@
 \end{align}
-where $\expDimsn$ and $\Sigma_{\expDimsn}$ are respectively the mean and covariance of object dimensions obtained from the KITTI dataset.
+where $\expDimsn$ and $\Sigma_{\expDimsn}$ are the mean and covariance, respectively, of object dimensions obtained from the KITTI dataset.
 

### 2016-01-25 CVPR16/rebuttal2.tex
changes

@@
 
-We thank all the reviewers for their feedback, noting our work as interesting and novel.
+We thank all the reviewers for their feedback and for noting our work as novel, interesting and well-written.
 
 \vspace{-0.4cm}
-\paragraph{R18, R24: Define inputs and outputs} As suggested, we will add Table~\ref{tab:notations} in final version to improve exposition.
+\paragraph{R18, R24: Define inputs and outputs} As suggested, we will add Table~\ref{tab:notations} in the final version to improve exposition.
 
@@
 \vspace{-0.4cm}
-\paragraph{R24: Complex graphical model for localization} Our intent is to showcase the flexibility of our occlusion model, which can be used for multiple applications such as point track association or 3D localization.
+\paragraph{R24: Complex graphical model for localization} 
+Our intent is to show that our occlusion model can be used for multiple applications such as association or localization.
+Simplified graphical models and faster inference in a particular application are important subjects of our future work.
+%Our intent is to showcase the flexibility of our occlusion model, which can be used for multiple applications such as point track association or 3D localization.
 Simplified graphical models and faster inference in a particular application are important subjects of our future work.
@@
 \paragraph{R24: Real-valued occupancy functions}
-We model objects as translucent, which not only accounts for shape uncertainty but also allows a probabilistic occlusion model amenable to continuous optimization tools.
+We model objects as translucent, which not only accounts for shape uncertainty but also allows a probabilistic occlusion model amenable to continuous optimization.
 
@@
 \paragraph{R24: Baselines}
-For object-point association, the BBox baseline uses 3D bounding boxes with simple depth ordering.
-For suggested baseline with less weight closer to the boundary -- in a sense, our association probability is a principled way to compute such a weight.
-For localization, we note that [33] does not account for point tracks and as R24 notes, uses a database of highly detailed CAD models and discrete modeling, so is not directly comparable.
+For object-point association, BBox baseline uses mean depth of 3D bounding boxes for simple depth ordering.
+For suggested baseline with less weight closer to the boundary -- our association probability is a principled way to compute such a weight.
+For localization, we note that [33] does not account for point tracks and as R24 notes, uses a database of highly detailed CAD models and discrete modeling, so might not be directly comparable.
 We thank R24 for the suggested baseline that fits a 3D bounding box on the reconstructed point cloud (using SFM within detection bounding boxes), yielding \hili{XXX}\% error in t and \hili{XXX}\% in dim.
@@
 \vspace{-0.4cm}
-\paragraph{R24: Typos in equations}
+\paragraph{R24: Typos in Eqn 15, 19}
 Thanks, $\cE_{\textrm{dyn}}$ and $\cE_{\textrm{size}}$ terms must be summed over all objects ($\cE_{\textrm{track}}$ in Eqn 15 already is), dependence on $\{ \Omega^i (t-1) \}_i$ in Eqn 19 must be dropped.
@@
 
-%\vspace{-0.4cm}
-%\paragraph{R24: Sequences for experiments} 
-%We use all the sequences in the KITTI raw dataset (\hili{XXX} sequences, \hili{XXX} frames, \hili{XXX} object tracks).
+\vspace{-0.4cm}
+\paragraph{R24: Sequences for experiments} 
+We use 35 sequences of the KITTI raw dataset (10k frames, 634 object tracks).
 
 \vspace{-0.4cm}
-\paragraph{R24: Related works}
-Thank you, we will cite them.
+\paragraph{R24: Other comments}
+Thank you, we will fix typos, include requested details and cite the listed related works.
 
@@
 Figure 5 may be considered with Table 1, which provides separate results for static and dynamic objects.
+Methods like BM and RAS cannot handle point tracks on static objects, while BBox uses depth but makes a heuristic hard assignment.
+In contrast, our formulation can incorporate point tracks, bounding boxes and detection scores in a unified probabilistic framework.
+%Figure 5 may be considered with Table 1, which provides separate results for static and dynamic objects.
 Methods like BM and RAS cannot handle point tracks on static objects.
@@
 \vspace{-0.4cm}
-\paragraph{R26: Increase in error with occlusion modeling}
+\paragraph{R26: Error trends with occlusion modeling}
 We empirically choose parameters to minimize energy with both bounding box and point track occlusions.

### 2016-01-25 CVPR16/rebuttal2.tex
changes

@@
 \hline
-\multirow{5}{*}{\rotatebox{90}{Estimated}} & $\bp^c(t)$ & Position of camera at time $t$ \\
+\multirow{5}{*}{\rotatebox{90}{Est.~for initial.}} & $\bp^c(t)$ & Position of camera at time $t$ \\
  & $\bomega^c(t)$ & Orientation of camera at time $t$ \\

### 2016-01-25 CVPR16/rebuttal2.tex
edit table

--- 2016-01-25 CVPR16/rebuttal2.tex
@@
 \newcommand{\hili}[1]{\colorbox{yellow}{#1}}
+\newcommand\RotText[1]{\rotatebox{90}{\parbox{1.7cm}{\centering#1}}}
 
@@
 \hline
-\multirow{5}{*}{\rotatebox{90}{Estimated}} & $\bp^c(t)$ & Position of camera at time $t$ \\
+\multirow{5}{*}{\RotText{Estimated for initialization}} & $\bp^c(t)$ & Position of camera at time $t$ \\
  & $\bomega^c(t)$ & Orientation of camera at time $t$ \\

### 2016-01-25 CVPR16/rebuttal2.tex
update data and parameters used for eval

@@
 \paragraph{R26: Role of reflection and transmission probabilities}
-Transmission probability only indicates whether a ray is transmissible to a particular depth, reflection probability indicates which object obstructs the ray at that depth.
-Thus, a combination of transmission and reflection probabilities is necessary to explain image observations.
+Transmission probability only indicates if a ray is transmissible to a particular depth, reflection probability indicates which object obstructs the ray at that depth.
+Thus, a combination of transmission and reflection is necessary to explain image observations.
 Lines 260-274 describe this intuition.
@@
 \paragraph{R26: Parameters}
-We use \hili{XXX}. The final version will include a detailed list of parameters.
+We use a total of 35 sequences, 10088 frames, and 634 objects with occlusions of the KITTI dataset.
+Main parameters are $\lambda_{t}$ = 1, $\lambda_{d}$ = 1, $\lambda_{dyn}$ = 10, $\lambda_{size} = 7$.
+The final version will include a detailed list of parameters.
 

### 2016-01-25 CVPR16/rebuttal2.tex
edit params and fit 1 page
changes

@@
 \hline
-\multirow{4}{*}{\rotatebox{90}{Output}} & $P^{ij}_{\text{assoc}}$ & Probability of associating feature track $j$ with object $O_i$ \\	
+\multirow{4}{*}{\rotatebox{90}{Output}} & $P^{ij}_{\text{assoc}}$ & Probability of associating point $j$ with object $O_i$ \\	
  & $\bp^i(t)$ & Position of object $O_i$ at time $t$ \\
@@
 \end{tabular}
-\vspace{-0.2cm}
+\vspace{-0.3cm}
 \caption{Notation of input and output.}
 \label{tab:notations}
-\vspace{-0.5cm}
+\vspace{-0.6cm}
 \end{table}
@@
 \paragraph{R26: Parameters}
-We use a total of 35 sequences, 10088 frames, and 634 objects with occlusions of the KITTI dataset.
-Main parameters are $\lambda_{t}$ = 1, $\lambda_{d}$ = 1, $\lambda_{dyn}$ = 10, $\lambda_{size} = 7$.
-The final version will include a detailed list of parameters.
+We use $\lambda_{t}$ = 1, $\lambda_{d}$ = 1, $\lambda_{dyn}$ = 10, $\lambda_{size} = 7$. The final version will include a detailed list of parameters.
 

### 2016-01-25 CVPR16/rebuttal2.tex
add outlier handling & fit 1 page

@@
 
-\vspace{-0.4cm}
-\paragraph{R18, R24: Define inputs and outputs} As suggested, we will add Table~\ref{tab:notations} in the final version to improve exposition.
+\vspace{-0.5cm}
+\paragraph{R18, R24: Defining inputs and outputs} As suggested, we will add Table~\ref{tab:notations} in the final version to improve exposition.
 
-\vspace{-0.4cm}
+\vspace{-0.5cm}
 \paragraph{R18, R24: Ellipsoid representation of objects} Our goal is to balance an analytical formulation for a tractable, continuous probabilistic model, with a shape representation that still yields good results for objects such as cars.
 
-\vspace{-0.4cm}
+\vspace{-0.5cm}
 \paragraph{R18: Eqns 4 and 13}
@@
 
-\vspace{-0.4cm}
+\vspace{-0.5cm}
 \paragraph{R18, R24: Initialization}
@@
 
-\vspace{-0.4cm}
+\vspace{-0.5cm}
 \paragraph{R24: Single but important category of cars} For evaluation, the KITTI dataset has ground truth 3D boxes only for cars.
@@
 
-\vspace{-0.4cm}
+\vspace{-0.5cm}
 \paragraph{R24: Complex graphical model for localization} 
@@
 
-\vspace{-0.4cm}
+\vspace{-0.5cm}
 \paragraph{R24: Real-valued occupancy functions}
@@
 
-\vspace{-0.4cm}
+\vspace{-0.5cm}
+\paragraph{R24: Handling outliers} 
+As noted by R24, outliers are inherently handled in our model.
+Outlier tracks usually have high reprojection errors and thus, low association probabilities.
+Additionally, outlier detection bounding boxes are likely to be filtered out by object tracking.
+
+\vspace{-0.5cm}
 \paragraph{R24: Baselines}
@@
 
-\vspace{-0.4cm}
+\vspace{-0.5cm}
 \paragraph{R24: Typos in Eqn 15, 19}
@@
 
-\vspace{-0.4cm}
+\vspace{-0.5cm}
 \paragraph{R24: Number of objects} 
@@
 
-%\vspace{-0.4cm}
-%\paragraph{R24: Handling outliers} 
-%As noted by R24, outliers are inherently handled in our model.
-Outlier tracks usually have high reprojection errors and thus, low association probabilities.
-Additionally, outlier detection bounding boxes are likely to be filtered out by object tracking.
-
-\vspace{-0.4cm}
+\vspace{-0.5cm}
 \paragraph{R24: Sequences for experiments} 
@@
 
-\vspace{-0.4cm}
+\vspace{-0.5cm}
 \paragraph{R24: Other comments}
@@
 \end{tabular}
-\vspace{-0.3cm}
+\vspace{-0.35cm}
 \caption{Notation of input and output.}
 \label{tab:notations}
-\vspace{-0.6cm}
+\vspace{-0.7cm}
 \end{table}
 
-\vspace{-0.4cm}
+\vspace{-0.5cm}
 \paragraph{R26: Superiority over baselines}
@@
 
-\vspace{-0.4cm}
+\vspace{-0.5cm}
 \paragraph{R26: Role of reflection and transmission probabilities}
@@
 
-\vspace{-0.4cm}
+\vspace{-0.5cm}
 \paragraph{R26: Error trends with occlusion modeling}
@@
 
-\vspace{-0.4cm}
+\vspace{-0.5cm}
 \paragraph{R26: Parameters}
-We use $\lambda_{t}$ = 1, $\lambda_{d}$ = 1, $\lambda_{dyn}$ = 10, $\lambda_{size} = 7$. The final version will include a detailed list of parameters.
+We use $\lambda_{t}$= 1, $\lambda_{d}$= 1, $\lambda_{dyn}$= 10, $\lambda_{size}$= 7. The final version will include a detailed list of parameters.
 

### 2016-01-26 CVPR16/rebuttal2.tex
add outlier handling & fit 1 page
remove outlier handling

--- 2016-01-25 CVPR16/rebuttal2.tex
@@
 \vspace{-0.4cm}
-\paragraph{R18, R24: Define inputs and outputs} As suggested, we will add Table~\ref{tab:notations} in the final version to improve exposition.
+\paragraph{R18, R24: Defining inputs and outputs} As suggested, we will add Table~\ref{tab:notations} in the final version to improve exposition.
 
@@
 \paragraph{R18, R24: Initialization}
-We initialize by fitting a 3D bounding box to detected bounding boxes and estimated ground plane, with a size prior.
+We initialize by fitting a 3D bounding box to detected bounding boxes and estimated ground plane, with 3D size priors.
 Initialization errors are \hili{XXX}\% for t and \hili{XXX}\% for dim.
@@
 
+%\vspace{-0.4cm}
+%\paragraph{R24: Handling outliers} 
+%As noted by R24, outliers are inherently handled in our model.
+Outlier tracks usually have high reprojection errors and thus, low association probabilities.
+Additionally, outlier detection bounding boxes are likely to be filtered out by object tracking.
+
 \vspace{-0.4cm}
@@
 %the results are shown in Table \ref{tab:localization}. 
-Here, we rely on size priors for unobservable dimensions in traffic scenes (say, when 3D points on only back of car are visible).
+Here, we rely on 3D size priors for unobservable dimensions in traffic scenes (say, when 3D points on only back of car are visible).
 
@@
 This is known a priori in our occlusion model (from object tracking [2]) and is also provided to other methods such as BBox and RAS.
-
-%\vspace{-0.4cm}
-%\paragraph{R24: Handling outliers} 
-%As noted by R24, outliers are inherently handled in our model.
-Outlier tracks usually have high reprojection errors and thus, low association probabilities.
-Additionally, outlier detection bounding boxes are likely to be filtered out by object tracking.
 
@@
 \hline
-\multirow{4}{*}{\rotatebox{90}{Output}} & $P^{ij}_{\text{assoc}}$ & Probability of associating point $j$ with object $O_i$ \\	
+\multirow{4}{*}{\rotatebox{90}{Output}} & $P^{ij}_{\text{assoc}}$ & Probability of associating point track $j$ with object $O_i$ \\	
  & $\bp^i(t)$ & Position of object $O_i$ at time $t$ \\
@@
 \end{tabular}
-\vspace{-0.3cm}
+\vspace{-0.25cm}
 \caption{Notation of input and output.}
 \label{tab:notations}
-\vspace{-0.6cm}
+\vspace{-0.5cm}
 \end{table}
@@
 Methods like BM and RAS cannot handle point tracks on static objects, while BBox uses depth but makes a heuristic hard assignment.
-In contrast, our formulation can incorporate point tracks, bounding boxes and detection scores in a unified probabilistic framework.
+In contrast, our formulation can handle static objects and makes accurate probabilistic soft assignment.
 %Figure 5 may be considered with Table 1, which provides separate results for static and dynamic objects.
@@
 Transmission probability only indicates if a ray is transmissible to a particular depth, reflection probability indicates which object obstructs the ray at that depth.
-Thus, a combination of transmission and reflection is necessary to explain image observations.
+Thus, a combination of transmission and reflection probabilities is necessary to explain image observations.
 Lines 260-274 describe this intuition.
@@
 \paragraph{R26: Parameters}
-We use $\lambda_{t}$ = 1, $\lambda_{d}$ = 1, $\lambda_{dyn}$ = 10, $\lambda_{size} = 7$. The final version will include a detailed list of parameters.
+We use $\lambda_{t}$=1, $\lambda_{d}$=1, $\lambda_{dyn}$=10, $\lambda_{size}$=7. The final version will include a detailed list of parameters.
 
@@
 %% \label{tab:localization}
-%% \vspace{-0.5cm}
+%% \vspace{-0.4cm}
 %% \end{table}

### 2016-01-26 CVPR16/rebuttal2.tex
edit

@@
 \paragraph{R24: Sequences for experiments} 
-We use 35 sequences of the KITTI raw dataset (10k frames, 634 object tracks).
+We use 35 sequences of the KITTI raw dataset (10088 frames, 634 object tracks).
 
@@
 \hline
-\multirow{4}{*}{\rotatebox{90}{Output}} & $P^{ij}_{\text{assoc}}$ & Probability of associating point track $j$ with object $O_i$ \\	
+\multirow{4}{*}{\rotatebox{90}{Output}} & $P^{ij}_{\text{assoc}}$ & Probability of assigning feature track $j$ to object $O_i$ \\	
  & $\bp^i(t)$ & Position of object $O_i$ at time $t$ \\
@@
 \vspace{-0.25cm}
-\caption{Notation of input and output.}
+\caption{Notation of inputs and outputs.}
 \label{tab:notations}
@@
 Methods like BM and RAS cannot handle point tracks on static objects, while BBox uses depth but makes a heuristic hard assignment.
-In contrast, our formulation can handle static objects and makes accurate probabilistic soft assignment.
+In contrast, our formulation can handle point tracks on static objects and makes accurate probabilistic soft assignment.
 %Figure 5 may be considered with Table 1, which provides separate results for static and dynamic objects.
@@
 \paragraph{R26: Role of reflection and transmission probabilities}
-Transmission probability only indicates if a ray is transmissible to a particular depth, reflection probability indicates which object obstructs the ray at that depth.
+Transmission probability only indicates whether a ray is transmissible to a particular depth, reflection probability indicates which object obstructs the ray at that depth.
 Thus, a combination of transmission and reflection probabilities is necessary to explain image observations.

### 2016-01-26 CVPR16/rebuttal2.tex
edit
final

@@
 We initialize by fitting a 3D bounding box to detected bounding boxes and estimated ground plane, with 3D size priors.
-Initialization errors are \hili{XXX}\% for t and \hili{XXX}\% for dim.
+Initialization errors are \textbf{5.61} for t and \textbf{3.23} for dim.
 They show advantage of our energy minimization and we will add them to Table 2.
@@
 For localization, we note that [33] does not account for point tracks and as R24 notes, uses a database of highly detailed CAD models and discrete modeling, so might not be directly comparable.
-We thank R24 for the suggested baseline that fits a 3D bounding box on the reconstructed point cloud (using SFM within detection bounding boxes), yielding \hili{XXX}\% error in t and \hili{XXX}\% in dim.
+We thank R24 for the suggested baseline that fits a 3D bounding box on the reconstructed point cloud (using SFM within detection bounding boxes), yielding errors \textbf{6.87} in t and \textbf{4.02} in dim.
 We will add these in Table 2.
@@
 \paragraph{R26: Superiority over baselines}
-Figure 5 may be considered with Table 1, which provides separate results for static and dynamic objects.
+Figure 5 may be considered with Table 1, which provides results for static and dynamic objects.
 Methods like BM and RAS cannot handle point tracks on static objects, while BBox uses depth but makes a heuristic hard assignment.
-In contrast, our formulation can handle point tracks on static objects and makes accurate probabilistic soft assignment.
+In contrast, our formulation can handle point tracks on static objects and makes accurate probabilistic soft assignments.
 %Figure 5 may be considered with Table 1, which provides separate results for static and dynamic objects.
@@
 \paragraph{R26: Parameters}
-We use $\lambda_{t}$=1, $\lambda_{d}$=1, $\lambda_{dyn}$=10, $\lambda_{size}$=7. The final version will include a detailed list of parameters.
+We use $\lambda_{t}$= 1, $\lambda_{d}$= 1, $\lambda_{dyn}$= 10, $\lambda_{size}$= 7. The final version will include a detailed list of parameters.
 

### 2016-01-26 CVPR16/rebuttal2.tex
changes

@@
 \paragraph{R18, R24: Initialization}
-We initialize by fitting a 3D bounding box to detected bounding boxes and estimated ground plane, with 3D size priors.
-Initialization errors are \textbf{5.61} for t and \textbf{3.23} for dim.
-They show advantage of our energy minimization and we will add them to Table 2.
+To initialize, we fit a 3D bounding box to detection boxes and estimated ground plane, with 3D size priors, yielding errors of \textbf{5.61} for t and \textbf{3.23} for dim (meters per object).
+They show the advantage of our energy minimization and we will add them to Table 2 of the paper.
 
@@
 For suggested baseline with less weight closer to the boundary -- our association probability is a principled way to compute such a weight.
-For localization, we note that [33] does not account for point tracks and as R24 notes, uses a database of highly detailed CAD models and discrete modeling, so might not be directly comparable.
-We thank R24 for the suggested baseline that fits a 3D bounding box on the reconstructed point cloud (using SFM within detection bounding boxes), yielding errors \textbf{6.87} in t and \textbf{4.02} in dim.
-We will add these in Table 2.
+For localization, we note that [33] does not account for point tracks and as R24 notes, uses a database of detailed CAD models and a discrete formulation, so might not be directly comparable.
+We thank R24 for the suggested baseline that fits a 3D bounding box on the reconstructed point cloud (using SFM within detection bounding boxes), yielding errors of \textbf{6.87} in t and \textbf{4.02} in dim (meters per object).
+We will add these to Table 2 of the paper.
 %the results are shown in Table \ref{tab:localization}. 
-Here, we rely on 3D size priors for unobservable dimensions in traffic scenes (say, when 3D points on only back of car are visible).
+Here, we rely on 3D size priors for unobservable dimensions, say, when only 3D points on the back of a car are visible.
 

### 2016-03-22 CVPR16/Source/experiments2.tex
changes
Reduced the size of images to make space in the paper for other tables.

@@
 \newlength{\tblimgwidth}
-\setlength{\tblimgwidth}{0.40\textwidth}
+\setlength{\tblimgwidth}{0.090\textwidth}
 \begin{figure*}[!!t]
   \centering
-  \begin{tabular}{ccc}
-    & Associations & Error in association\\
-    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png} &%
-    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{2em} BM} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png} &%
-    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{2em} RAS} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_RAS-small.png} &%
-    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks-small.png} &%
-    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png} &%
-    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{2em} BM} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png} &%
-    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{2em} RAS} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_RAS-small.png} &%
-    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks-small.png} &%
-    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}
+  \begin{tabular}{cc@{}c@{\hspace{0.1cm}}c@{}c@{}}
+    & Associations & Association Error & Associations & Association Error\\
+    \rotatebox{90}{\hspace{1em} BBox}%
+    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png}%
+    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}%
+    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png}%
+    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
+    \rotatebox{90}{\hspace{1em} BM}%
+    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png}%
+    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}%
+    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png}%
+    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
+    \rotatebox{90}{\hspace{1em} RAS}%
+    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_RAS-small.png}%
+    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_RAS_correct_incorrect-small.png}%
+    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_RAS-small.png}%
+    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
+    \rotatebox{90}{\hspace{1em} Ours}%
+    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks-small.png}%
+    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}%
+    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks-small.png}%
+    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}
   \end{tabular}
   \vspace{-0.3cm}
-  \caption{\small Qualitative results of the association experiment. The left column
-  shows the point track assignments to appropriate objects. Each color represents
-a different object to which point tracks can be associated to. Right column shows the
+  \caption{\small Qualitative results of the association experiment. The odd columns
+  show the point track assignments to appropriate objects. Each color represents
+a different object to which point tracks can be associated to. The even columns show the
 probabilistic error in association: low error points are in blue while high error points are in red.

### 2016-03-22 CVPR16/Source/applications.tex
Added the notations table and made the authors list visible.

@@
 In this section, we highlight the versatility of our occlusion modeling by demonstrating its unified application to two different problems: associating point tracks with objects and 3D object localization using objects and point tracks.
+Inputs and outputs required in both the problems and corresponding notation is tabulated in Table~\ref{tab:notations}.
+
+\newcommand\RotText[1]{\rotatebox{90}{\parbox{1.7cm}{\centering#1}}}
+\begin{table}[!!t]
+\centering\footnotesize
+\begin{tabular}{|l|l|l|}
+\hline
+ & Symbol & Description \\
+\hline
+\hline
+\multirow{2}{*}{\rotatebox{90}{Input}} & $\bu_j(t)$ & 2D feature track $j$ at time $t$ \\
+ & $\bb{i}$ & 2D detection bounding box of object $O_i$ at time $t$ \\
+\hline
+\hline
+\multirow{5}{*}{\RotText{Estimated for initialization}} & $\bp^c(t)$ & Position of camera at time $t$ \\
+ & $\bomega^c(t)$ & Orientation of camera at time $t$ \\
+ & $\bp_0^i(t)$ & Initial position of object $O_i$ at time $t$ \\
+ & $\bomega_0^i(t)$ & Initial orientation of object $O_i$ at time $t$ \\
+ & $\bB_0^i$ & Initial 3D dimensions of object $O_i$ (independent of $t$) \\
+\hline
+\hline
+\multirow{4}{*}{\rotatebox{90}{Output}} & $P^{ij}_{\text{assoc}}$ & Probability of assigning feature track $j$ to object $O_i$ \\	
+ & $\bp^i(t)$ & Position of object $O_i$ at time $t$ \\
+ & $\bomega^i(t)$ & Orientation of object $O_i$ at time $t$ \\
+ & $\bB^i$ & 3D dimensions of object $O_i$ (independent of time $t$) \\
+\hline
+\end{tabular}
+\vspace{-0.25cm}
+\caption{Notation of inputs and outputs.}
+\label{tab:notations}
+\vspace{-0.5cm}
+\end{table}
 

### 2016-03-22 CVPR16/Source/occlusion.tex
Added the normalization factor in equation 4.

@@
 Let $\bK$ be the intrinsic calibration matrix for the camera and $\ray = \displaystyle\frac{\bK^{-1}\bu_j}{\lVert \bK^{-1}\bu_j \rVert}$ be the unit vector along the backprojected ray from the camera center passing through $\bu_j$.
-Then, the probability of reflection at depth $\lambda$ along the ray $\ray$, by an object $O_i$, is determined by the gradient of the object's occupancy function $f_{occ}^i$:
+Then, the probability of reflection at depth $\lambda$ along the ray $\ray$, by an object $O_i$, is determined by the gradient of the object's occupancy function $f_{occ}^i$:%
 \begin{align}
-  P^{ij}_{\textit{reflection}} (\lambda) = (\max \{0, \nabla {f^i_{occ}}(\bx_j)^\top \ray \})^2
+   \Prefl = \frac{1}{\Zrefl}(\max \{0, \nabla {f^i_{occ}}(\bx_j)^\top \ray \})^2
 \label{eq:evalPrefl}
@@
 We note that in the extreme case of an object being Lambertian, the above reverts to a (squared) Lambertian reflection.
+The $\Zrefl$ denotes the normalization factor such that $\int_{0^+}^\infty \Prefl d\lambda = 1$.
 

### 2016-03-23 CVPR16/Source/contBBoxModel.tex
Fixed Equation (15) (19) and the summation over dynamic and size.

@@
 \begin{align}
-  \Energy{detect}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}
+  \Energy{detect}(\{ \relp{i}{t} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}
 \end{align}

### 2016-03-28 CVPR16/Source/experiments2.tex
Addressed other comments from R24. (1) Added one of the references (2) take -> taken (3) Explained how we get the number of cars from detections (4) Added statistics about KITTI dataset (5) Clarified that we use Song and Chandrakar 2014 for initializing 3D location and sizes as well. (6) Added baselines to experiment table (7) Added one line explanation of the baselines (8) Clarified the Lambertian reflection line (9) summer -> sum

@@
 We then show how the proposed model may be applied for 3D localization in road scenes.
-For our experiments, we use the KITTI dataset~\cite{geiger2013vision}, which consists of video sequences of road scenes under a variety of driving conditions.
+For our experiments, we use the KITTI dataset~\cite{geiger2013vision}, which consists of 35 video sequences (10088 frames, 634 object tracks) of road scenes under a variety of driving conditions.
 %It also provides ground truth data for different tasks such as segmentation, detection, tracking and 3D localization.
@@
 For a complete evaluation, we organize the point tracks into four sets: all point tracks, occluded point tracks, dynamic point tracks and dynamic as well as occluded point tracks.
-In addition to point tracks, the parameters of all objects (cars) estimated by the method of \cite{Song_Chandraker_2015} are provided to our method (for computing association probability) and the baseline BBox method (for depth ordering).
+In addition to point tracks, the parameters of all objects (cars)--including their unknown 3D position and sizes--estimated by the method of \cite{Song_Chandraker_2014} are provided to our method (for computing association probability) and the baseline BBox method (for depth ordering).
 
@@
     \toprule
-    Energy & t & dim \\
+    Method & t & dim \\
     \midrule
+    Point cloud fit
+    & 6.87 & 4.02\\
+    Initialization
+    & 5.61 & 3.23\\
     $\EnergyTrackNoOcc + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$ 
@@
 Average depth of cars in the dataset is approximately $20$ meters.
-We compare four combinations of energies.
+We compare four combinations of energies with two baselines.
+We initialize the unknowns using \cite{Song_Chandraker_2014} whose accuracy is reported as \emph{Initialization} in the table.
+We develop a simple baseline by fitting cuboids to the point cloud created by triangulation of point tracks in two successive frames.
+The accuracy of this baseline is reported as \emph{Point cloud fit} in the table.
 The energy $\EnergyTrackNoOcc$ represents the point tracks energy without accounting for occlusion, that is, we model $\EnergyTrack$ in the absence of $a^{ij} (\lambda)$.

### 2016-03-28 CVPR16/Source/occlusion.tex
Addressed other comments from R24. (1) Added one of the references (2) take -> taken (3) Explained how we get the number of cars from detections (4) Added statistics about KITTI dataset (5) Clarified that we use Song and Chandrakar 2014 for initializing 3D location and sizes as well. (6) Added baselines to experiment table (7) Added one line explanation of the baselines (8) Clarified the Lambertian reflection line (9) summer -> sum

@@
 The $\max \{ \}$ ensures that the negative probability due to gradient in the direction opposite to the ray is clipped off and squaring the function allows it to be smooth near zero.
-We note that in the extreme case of an object being Lambertian, the above reverts to a (squared) Lambertian reflection.
+We note that in the extreme case of an object being fully opaque (i.e.
+$\nabla {f^i_{occ}(\bx_j)} \in \{0,1\}$), the above model reverts to a (squared) Lambertian reflection.
 The $\Zrefl$ denotes the normalization factor such that $\int_{0^+}^\infty \Prefl d\lambda = 1$.
@@
 %
-In our formulation of scene occupancy, both opacity and density at a scene point $\bx_j$ are encapsulated within the total occupancy function summer over all objects, $\occftot = \sum_i \occf$.
+In our formulation of scene occupancy, both opacity and density at a scene point $\bx_j$ are encapsulated within the total occupancy function sum over all objects, $\occftot = \sum_i \occf$.
 Further, the domain of our ocupancy function $\occftot$ is $[0, 1]$ instead of $[0, \infty)$ for opacity $\beta$.

### 2016-03-28 CVPR16/Source/related.tex
Addressed other comments from R24. (1) Added one of the references (2) take -> taken (3) Explained how we get the number of cars from detections (4) Added statistics about KITTI dataset (5) Clarified that we use Song and Chandrakar 2014 for initializing 3D location and sizes as well. (6) Added baselines to experiment table (7) Added one line explanation of the baselines (8) Clarified the Lambertian reflection line (9) summer -> sum

@@
 
+One of the models closest to our unified occupancy model was recently presented by Rhodin et al.
+\cite{Rhodin:2015} applied to the problem of pose estimation.
+Although they model transmission probability like we do, they do not model reflectance probability.
+We explicitly model reflectance probability that differentiates between the center and surface of the 3D object.
+
 %Notable monocular frameworks for 3D localization include \cite{Wojek_etal_2013}, which uses partial object detectors for handling occlusions and \cite{Zia_etal_2013,Zia_etal_2014}, which learn a detailed part-based representation of objects from annotated CAD models for reasoning about mutual occlusions.

### 2016-04-06 CVPR16/Source/abstract.tex
Make symbols consistent, Include most of reviewer comments (except for related works by Reviewer 2, Proof reading

--- 2015-11-06 CVPR16/Source/abstract.tex
@@
 \begin{abstract}
-
-We present a physically interpretable, continuous 3D model for handling occlusions with applications to road scene understanding.
+We present a physically interpretable, continuous three-dimensional (3D) model for handling occlusions with applications to road scene understanding.
 We probabilistically assign each point in space to an object with a theoretical modeling of the reflection and transmission probabilities for the corresponding camera ray.
-Our modeling is unified in handling occlusions across a variety of scenarios, such as associating structure from motion point tracks with potentially occluded objects or modeling object detection scores in applications such as 3D localization.
+Our modeling is unified in handling occlusions across a variety of scenarios, such as associating structure from motion (SFM) point tracks with potentially occluding objects or modeling object detection scores in applications such as 3D localization.
 For point track association, our model uniformly handles static and dynamic objects, which is an advantage over motion segmentation approaches traditionally used in multibody SFM.
-Detailed experiments on the KITTI dataset show the superiority of the proposed method over both state-of-the-art motion segmentation and a baseline that heuristically uses detection bounding boxes for resolving occlusions.
+Detailed experiments on the KITTI raw dataset show the superiority of the proposed method over both state-of-the-art motion segmentation and a baseline that heuristically uses detection bounding boxes for resolving occlusions.
 We also demonstrate how our continuous occlusion model may be applied to the task of 3D localization in road scenes.

### 2016-04-06 CVPR16/Source/applications.tex
Fixed Equation (15) (19) and the summation over dynamic and size.
Addressed other comments from R24. (1) Added one of the references (2) take -> taken (3) Explained how we get the number of cars from detections (4) Added statistics about KITTI dataset (5) Clarified that we use Song and Chandrakar 2014 for initializing 3D location and sizes as well. (6) Added baselines to experiment table (7) Added one line explanation of the baselines (8) Clarified the Lambertian reflection line (9) summer -> sum
Make symbols consistent, Include most of reviewer comments (except for related works by Reviewer 2

--- 2015-11-07 CVPR16/Source/applications.tex
@@
 In this section, we highlight the versatility of our occlusion modeling by demonstrating its unified application to two different problems: associating point tracks with objects and 3D object localization using objects and point tracks.
+Table~\ref{tab:notations} summarizes inputs and outputs for these problems.
+
+\newcommand\RotText[1]{\rotatebox{90}{\parbox{1.7cm}{\centering#1}}}
+\begin{table}[!!t]
+\centering\footnotesize
+\begin{tabular}{|l|l|l|}
+\hline
+ & Symbol & Description \\
+\hline
+\hline
+\multirow{2}{*}{\rotatebox{90}{Input}} & $\bu_j(t)$ & 2D feature track $j$ at time $t$ \\
+ & $\bb{i}$ & 2D detection bounding box of object $O_i$ at time $t$ \\
+\hline
+\hline
+\multirow{5}{*}{\RotText{Est. by~\cite{Song_Chandraker_2014} for initialization}} & $\bp^c(t)$ & Position of camera at time $t$ \\
+ & $\bomega^c(t)$ & Orientation of camera at time $t$ \\
+ & $\bp_0^i(t)$ & Initial position of object $O_i$ at time $t$ \\
+ & $\bomega_0^i(t)$ & Initial orientation of object $O_i$ at time $t$ \\
+ & $\bB_0^i$ & Initial 3D dimensions of object $O_i$ \\
+\hline
+\hline
+\multirow{4}{*}{\rotatebox{90}{Output}} & $P^{ij}_{\text{assoc}}$ & Probability of assigning feature track $j$ to object $O_i$ \\	
+ & $\bp^i(t)$ & Position of object $O_i$ at time $t$ \\
+ & $\bomega^i(t)$ & Orientation of object $O_i$ at time $t$ \\
+ & $\bB^i$ & 3D dimensions of object $O_i$ \\
+\hline
+\end{tabular}
+\vspace{-0.25cm}
+\caption{Notation of inputs and outputs for object-point association and 3D object localization. Note that object dimensions are independent of time.}
+\label{tab:notations}
+\vspace{-0.5cm}
+\end{table}
 
@@
 Rather, to compute the association probability between point track $\bu_j$ and object $O_i$, we should also use the reprojection error.
-When the association of point track $\bu_j$ and object $O_i$ is correct and the point of reflection is at depth $\lambda$, the corresponding reprojection error $\Ereproj(\lambda)$ must be zero \eqref{eq:reprojerror}, otherwise the error becomes a measure of distance from the true solution.
+When the association of point track $\bu_j$ and object $O_i$ is correct and the point of reflection is at depth $\lambda$, the corresponding reprojection error $\Ereproj(\lambda)$ must be zero, otherwise the error becomes a measure of distance from the true solution.
 The error $\Ereproj(\lambda)$ can be used for associating point tracks and objects by converting it to the probability domain as
 \begin{align}
-  P^{ij}_{\text{reproj}}(\lambda) = \frac{1}{Z}\exp(-\Ereproj(\lambda)),
+  P^{ij}_{\text{reproj}}(\lambda) = \frac{1}{Z'}\exp(-\Ereproj(\lambda)),
 \label{eq:Passocbyreproj}
 \end{align}
-where $Z$ is the normalization coefficient.
+where $Z'$ is the normalization coefficient.
 
@@
 \begin{align}
-  P^{ij}_{\text{assoc}} = \frac{1}{Z'}\int_0^{\infty} \assocP \exp(-\Ereproj(\lambda))d\lambda,
+  P^{ij}_{\text{assoc}} = \frac{1}{Z"}\int_0^{\infty} \assocP \exp(-\Ereproj(\lambda))d\lambda,
   \label{eq:prob-assoc}
 \end{align}
-where $Z'$ is the new normalization coefficient.
+where $Z"$ is the new normalization coefficient.
 
@@
 
-In contrast to the principled approach above, a heuristic baseline may simply assign a point track to the detection bounding box enclosing it (and background if outside all bounding boxes).
+In contrast to the principled approach above, a heuristic baseline may simply assign a point track to the detection bounding box enclosing it (and the background if outside all bounding boxes).
 For regions where bounding boxes overlap, it may assign point tracks to the object that has the smallest mean depth among the competing bounding boxes.
@@
 
-We exploit in this section the application of our continuous occlusion model to 3D localization in road scenes, which further demonstrates the versatility of the proposed model.
-Given a set of tracked feature points $\{\bu_j(t)\}$ and 2D detection bounding boxes $\{\bb{i}\}$ at frame $t$, the goal is to localize 3D traffic participants (TPs), in particular, for each TP, estimating its position $\bp^i(t)$ and orientation $\bomega^i(t)$ on the ground plane and its 3D dimensions $\bB^i(t)$.
+We exploit in this section the application of our continuous occlusion model to 3D object localization in road scenes, which further demonstrates the versatility of the proposed model.
+Given a set of 2D tracked feature points $\{\bu_j(t)\}$ and 2D detection bounding boxes $\{\bb{i}\}$ at frame $t$, the goal is to localize 3D traffic participants, in particular, for each traffic participant, estimating its position $\bp^i(t)$ and orientation $\bomega^i(t)$ on the ground plane and its 3D dimensions $\bB^i(t)$.
+Please refer to Table~\ref{tab:notations} for a summary of inputs and outputs.
+
 We build a graphical model for representing object relationships and decompose the negative log likelihood as follows
@@
   -\log{P(\{ \bp^i(t) , \bomega^i(t) , \bB^i(t) \} | \{\bu_j(t)\} , \{\bb{i}\} )} = \\
-  -Z 
-   + \sum_{t=s_i}^{e_i} \lambda_t\EnergyTrack
-  + 
-  \sum_{t=s_i}^{e_i}
-  \sum_{i=1}^N  
-  %\sum_{\substack{i \in [1, \dots, N] \\t \in [s_i, \dots e_i]}}
-  \lambda_d\EnergyBBox
+  -\tilde{Z} 
+  + \sum_{t=s_i}^{e_i} \lambda_{\text{track}}\EnergyTrack
+  + \\ 
+  \sum_{t=s_i}^{e_i} \sum_{i=1}^N  
+  \left(
+    \lambda_{\text{detect}}\EnergyBBox
     + \lambda_{\text{dyn}}\EnergyDyn    
     + \lambda_{\text{size}}\EnergySize
+  \right)
   \enspace,
@@
 %
-where $\pEnergy{track}$ and $\Energy{detect}$ reason about image observations such as point tracks and bounding boxes while $\Energy{dyn}$  and $\Energy{size}$ impose smoothness constraints and size priors respectively.
-Here, $\lambda_{t}$, $\lambda_{d}$, $\lambda_{dyn}$, $\lambda_{size}$ are energy weights, $N$ is the number of objects in the sequence, $s_i$ and $t_i$ are respectively the starting and ending frames of object $O_i$ and $Z$ is the normalization coefficient.
+where $\pEnergy{track}$ and $\Energy{detect}$ reason about image observations such as point tracks and bounding boxes, while $\Energy{dyn}$  and $\Energy{size}$ impose smoothness constraints and size priors respectively.
+Here, $\lambda_{\text{track}}$, $\lambda_{\text{detect}}$, $\lambda_{\text{dyn}}$, $\lambda_{\text{size}}$ are energy weights, $N$ is the number of objects in the sequence, $s_i$ and $t_i$ are respectively the starting and ending frames of object $O_i$, and $\tilde{Z}$ is the normalization coefficient.
 Figure~\ref{fig:graphmodel} illustrates an example of the graph and energies.
-Next, we present our unified continuous occlusion modelling for both point track and bounding box energies.
+Next, we present our unified continuous occlusion modeling for both point track and bounding box energies.
 Due to space constraints, we present the details of other energies in the supplementary material.
@@
   \end{tabular}
-  \caption{\small (Top) A sample road scene with occlusions, where the unknowns of each car are modeled as random variables.
-(Bottom) Graphical model for a single frame.
-The six numbered nodes represent the unknown state variables of each car.
-The shaded nodes in the graphical model are observed variables (detection bounding boxes and point tracks), while the colored squares represent various energies that capture object-object interactions.}
+  \caption{\small (Top) A sample road scene with occlusions, where the unknowns of each object are modeled as random variables.
+(Bottom) The graphical model corresponding to the above frame.
+In particular, the numbered nodes denote the unknown state variables of each object (position, orientation, and dimensions), the shaded nodes are observed variables (detection bounding boxes and point tracks), and the colored squares represent various energies that capture object-object interactions.}
   \label{fig:graphmodel}
@@
 \vspace{-0.3cm}
-\paragraph{Continuous point tracks energy with occlusion}
+\paragraph{Continuous point track energy with occlusion}
 %\label{sec:totalContPtTracksEnergy}
-Let $\relp{i}{t}$ be the pose of object $O_i$ with respect to the camera at time $t$.
-We denote $\projectionOf{.}$ and $\invProjectionOftm{.}$ for the forward and inverse projection functions that project a 3D point to the camera image and vice versa.
-Then, the reprojection error for the 2D point $\trackp{t}$ with hypothesized depth $\lambda$, is given by
+Let $\relp{i}{t}$ be the pose of object $O_i$ at time $t$ in world coordinates (computed using the camera pose at time $t$ and the relative pose of object $O_i$ with respect to the camera).
+We denote $\projectionOf{.}$ and $\invProjectionOftm{.}$ as the forward and inverse projection functions that project a 3D point to the 2D image and vice versa.
+Then, the reprojection error for 2D point $\trackp{t}$ with hypothesized depth $\lambda$, is given by
 \begin{equation}
@@
 \end{equation}
-Note that inverse projection $\invProjectionOf{.}$ depends on both the 2D point $\trackp{t}$ and the unknown depth $\lambda$.
-Also note that the inverse projection is dependent on object pose at time $t-1$ while the forward projection depends on pose at time $t$, which can be different.
+Note that the inverse projection $\invProjectionOf{.}$ depends on both the 2D point $\trackp{t}$ and the unknown depth $\lambda$.
+Also note that the inverse projection relies on the object pose at time $t-1$ while the forward projection relies on the object pose at time $t$, which can be different.
 
-For an object $O_i$, let $\{ \Omega (t) \}_i$ be the poses of all occluding objects at time $t$ (inclusive of object $i$) and $ \{ \bB \}_i$ be their corresponding 3D dimensions.
-Then, we model the continuous point tracks energy with explicit occlusion reasoning as the expected reprojection error over the association probability:
+For an object $O_i$, let $\{ \Omega (t) \}_i$ be the poses of all occluding objects at time $t$ (inclusive of object $O_i$) and $ \{ \bB \}_i$ be their corresponding 3D dimensions.
+Then, we model the continuous point track energy with explicit occlusion reasoning as the expected reprojection error over the association probability
 \begin{multline}
@@
     \sum_{j = 1}^{M}
-    \int_1^\infty \assocP\Ereproj(\lambda) d\lambda
+    \int_0^\infty \assocP\Ereproj(\lambda) d\lambda,
 \end{multline}
-where $N$ and $M$ are respectively the number of objects and points and $\assocP$ is the association probability of point $\trackp{t}$ with the object $O_i$ at depth $\lambda$, given by \eqref{eq:defineassocP}.
+where $N$ and $M$ are respectively the number of objects and points and $\assocP$ is the association probability of point $\trackp{t}$ with object $O_i$ at depth $\lambda$, given by \eqref{eq:defineassocP}.
 
@@
 Since we are optimizing over continuous variables, we use Gaussian distribution as the proposal function.
-We choose this over alternatives such as block coordinate descent since they are slower in our experiments.
+We choose this over alternatives such as block-coordinate descent since they are slower in our experiments.
 

### 2016-04-06 CVPR16/Source/contBBoxModel.tex
Addressed other comments from R24. (1) Added one of the references (2) take -> taken (3) Explained how we get the number of cars from detections (4) Added statistics about KITTI dataset (5) Clarified that we use Song and Chandrakar 2014 for initializing 3D location and sizes as well. (6) Added baselines to experiment table (7) Added one line explanation of the baselines (8) Clarified the Lambertian reflection line (9) summer -> sum
Make symbols consistent, Include most of reviewer comments (except for related works by Reviewer 2, Proof reading

@@
 Object detection is usually followed by non-maximal suppression that results in discarding similar bounding boxes.
-When we are jointly optimizing detections with other cues, it is not usually desirable to go with a single bounding box.
-To retain the entire detection output while maintaining the continuous form of our energies, we approximate the distribution of detection scores with a multi-modal sum of Gaussians-like logistic functions.
+When we are jointly optimizing detections with other cues, it is usually not desirable to go with a single bounding box.
+To retain the entire detection output while maintaining the continuous form of our energies, we approximate the distribution of detection scores with a multi-modal sum of Gaussian-like logistic functions.
 In particular, let 2D bounding box $\bb{i}$ be parameterized as a 4D vector $[\minx, \miny, \maxx, \maxy]^\top$.
@@
 \begin{equation}
-S(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \Lambda_k^{-1} \bepsilon_k^{i}(t) \right)
+S(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \bLambda_k^{-1} \bepsilon_k^{i}(t) \right),
 \end{equation}
-where $A_k$ is an amplitude and $\bepsilon_k^{i}(t) = \bb{i}-\mu^{k}_d$, with $\mu^{k}_d$ the mean and $\Lambda_k$ the covariance.
+where $A_k$ is an amplitude and $\bepsilon_k^{i}(t) = \bb{i}-\bmu_k$, with $\bmu_k$ the mean and $\bLambda_k$ the covariance.
 %% %
@@
 We use a non-linear solver to minimize the above, with initialization from non-maximal suppressed outputs.
-The optimization is constrained by the symmetry and positive definiteness of $\Lambda_k^{-1}$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
+The optimization is constrained by the symmetry and positive definiteness of $\bLambda_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
 %Here $\mu^{(d)}_j$ is one of the $k$ modes as a 4D vector representing a single bounding box as $[\minx, \miny, \maxx, \maxy]^\top$.
@@
 With our model of $\Ptrans$ described in Section \ref{sec:ptransmission}, we can
-compute the probability of a point $\u$ in the image to be occluded assuming
-the point is on object $O_i$ with mean depth $\meandepth{i}$ as
+compute the probability of a point $\u$ in the image to be occluded, assuming
+the point is on object $O_i$ with mean depth $\meandepth{i}$, as
 \begin{align}
-  \Theta_{i}(\u, \meandepth{i}) = 1 - \Ptransmission(\meandepth{i}, \u) \enspace .
+  \Theta_{i}(\u, \meandepth{i}) = 1 - \Ptransmission(\meandepth{i}, \u).
 \end{align}
-
 If a portion of our proposed detection bounding box is known to be
-occluded, then we would like to decrease the confidence in the detection score
+occluded, we would like to decrease the confidence in the detection score
 about the localization of that end of the object. Assuming that the occlusion
-is often on the boundary of detection bounding boxes, we want to decrease our
+is often on the boundaries of the detection bounding box, we want to decrease our
 confidence on the mean detection boundaries around the occluded boundaries.
-To re-model our detection scores scaled by continuous occlusion we sample
+To re-model our detection scores scaled by continuous occlusion, we sample
 $\Theta_{i}(\mathbf{u}, \meandepth{i})$ at the hypothesized detection boundaries from
-Gaussian mixture model (GMM) $S(.)$ and we augment the detection boundary covariance matrix by
+the Gaussian mixture model (GMM) $S(.)$ and we augment the detection boundary covariance matrix by
 $\mathcal{P}_{i} = \rho_{i}\rho_{i}^\top$ where $\rho_{i} = \Theta_{i}(\mathbf{u},
-\meandepth{i})$. The new covariance matrix in detection score is given by 
-  $\Lambda'_k = \mathcal{P}_{i} + \Lambda_k$ for all $k$.
-The detection scores GMM with occlusion is given by replacing the covariance
-matrix
+\meandepth{i})$. The new covariance matrix in the detection score is given by 
+  $\bLambda'_k = \mathcal{P}_{i} + \bLambda_k$ for all $k$.
+The detection score GMM $S'(.)$ with explicit occlusion reasoning is given by replacing the covariance
+matrix as follows
 %
 \begin{multline}
-S'(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \Lambda_k^{'-1} \bepsilon_k^{i}(t) \right)
+S'(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \bLambda_k^{'-1} \bepsilon_k^{i}(t) \right).
 \end{multline}
 
-The energy of detection scores is simply take to be the inverse of the detection score.
+The energy of detection scores is simply taken to be the inverse of the detection score as
 \begin{align}
-  \Energy{detect}(\{ \relp{i}{t} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}
+  \Energy{detect}(\{ \relp{i}{t} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}.
 \end{align}

### 2016-04-06 CVPR16/Source/experiments2.tex
Make symbols consistent, Include most of reviewer comments (except for related works by Reviewer 2, Proof reading

--- 2016-03-22 CVPR16/Source/experiments2.tex
@@
 In this section, we benchmark our continuous occlusion model for point-to-object association against the baseline method using detection bounding boxes and state-of-the-art methods for motion segmentation \cite{Rao_etal_2010,Brox_Malik_2010}.
-We then show how the proposed model may be applied for 3D localization in road scenes.
-For our experiments, we use the KITTI dataset~\cite{geiger2013vision}, which consists of video sequences of road scenes under a variety of driving conditions.
+We then show how the proposed model may be applied for 3D object localization in road scenes.
+For our experiments, we use 35 sequences of the KITTI raw dataset~\cite{Geiger_etal_2012}, which are recorded under a variety of driving conditions and include 10,088 frames and 634 object tracks in total.
 %It also provides ground truth data for different tasks such as segmentation, detection, tracking and 3D localization.
@@
 The detection bounding box baseline method (BBox) is as described at the end of Section \ref{sec:association}.
-For motion segmentation, we use robust algebraic segmentation with hybrid perspective constraints (RAS)~\cite{Rao_etal_2010} and spectral clustering with point track spatial affinity (BM)~\cite{Brox_Malik_2010}.
+For motion segmentation, we use robust algebraic segmentation with hybrid perspective constraints (RAS)~\cite{Rao_etal_2010} and spectral clustering with point track spatial affinities (BM)~\cite{Brox_Malik_2010}.
 
@@
   \caption{\small Association errors on different sets of input point tracks.
-Numbers on y-axis represent data sequence numbers in KITTI dataset.
+Numbers on x-axis represent sequence numbers in the KITTI raw dataset.
 Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
@@
   \toprule
-  & Ours & BBox & BM & RAS\\
+  Point tracks & Ours & BBox & BM & RAS\\
   \midrule
-  Dyn. and occ. tracks        & \textbf{13.2} & 21.3 & 30.9 & 30.1 \\
-  Occluded tracks             & \textbf{15.7} & 19.8 & 39.5 & 37.8 \\
-  Dynamic tracks              & \textbf{06.6} & 11.4 & 15.3 & 17.7 \\
-  All tracks                  & \textbf{08.6} & 12.6 & 21.9 & 21.5 \\
+  Dynamic \& occluded         & \textbf{13.2} & 21.3 & 30.9 & 30.1 \\
+  Occluded		              & \textbf{15.7} & 19.8 & 39.5 & 37.8 \\
+  Dynamic		              & \textbf{6.6} & 11.4 & 15.3 & 17.7 \\
+  All		                  & \textbf{8.6} & 12.6 & 21.9 & 21.5 \\
   \bottomrule
 \end{tabular}
-\caption{\small Mean association errors on different sets of input point tracks over all sequences of KITTI dataset.
+\caption{\small Mean association errors on different sets of input point tracks over all sequences.
 Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
@@
   \begin{tabular}{cc@{}c@{\hspace{0.1cm}}c@{}c@{}}
-    & Associations & Association Error & Associations & Association Error\\
+    & Associations & Errors & Associations & Errors\\
     \rotatebox{90}{\hspace{1em} BBox}%
@@
   \vspace{-0.3cm}
-  \caption{\small Qualitative results of the association experiment. The odd columns
+  \caption{\small Qualitative results of the association experiment. The ``Associations" columns
   show the point track assignments to appropriate objects. Each color represents
-a different object to which point tracks can be associated to. The even columns show the
-probabilistic error in association: low error points are in blue while high error points are in red.
+a different object to which point tracks can be associated to. The ``Errors" columns show the
+probabilistic errors in association: low error points are in blue while high error points are in red.
 Note that our method changes smoothly at the object boundaries with
-intermediate probabilities, while the baseline method has merely 0-1 error.}
+intermediate probabilities, while the baseline method has merely 0 and 1 errors.}
 \label{fig:qualitative}
@@
 
-For each sequence of the KITTI dataset, the methods of \cite{Felzenszwalb_etal_2010} and \cite{Choi_Savarese_2010} are used for computing detection bounding boxes and object tracklets, respectively.
+For each sequence, the methods of \cite{Felzenszwalb_etal_2010} and \cite{Choi_Savarese_2010} are used for computing detection bounding boxes and object tracklets, respectively.
 We then apply \cite{Zach2007} to extract point tracks.
@@
 For a complete evaluation, we organize the point tracks into four sets: all point tracks, occluded point tracks, dynamic point tracks and dynamic as well as occluded point tracks.
-In addition to point tracks, the parameters of all objects (cars) estimated by the method of \cite{Song_Chandraker_2015} are provided to our method (for computing association probability) and the baseline BBox method (for depth ordering).
+In addition to point tracks, the parameters (position, orientation, and dimensions) of all objects (cars) estimated by the method of \cite{Song_Chandraker_2014} are provided to our method (for computing association probability) and the baseline BBox method (for depth ordering).
 
@@
 \paragraph{Results}
-Figure~\ref{fig:assoc-occ-results} shows the association errors -- the percentages of point tracks incorrectly assigned to objects -- for all methods on the four sets of input point tracks, for each sequence of the KITTI dataset.
+Figure~\ref{fig:assoc-occ-results} shows the association errors -- the percentages of point tracks incorrectly assigned to objects -- for all methods on the four sets of input point tracks, for each sequence.
 The mean results over all sequences are summarized in Table~\ref{tab:meanAssoc}.
@@
     \toprule
-    Energy & t & dim \\
+    Method & t & dim \\
     \midrule
+    Point cloud fitting
+    & 6.87 & 4.02\\
+    Initialization
+    & 5.61 & 3.23\\
     $\EnergyTrackNoOcc + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$ 
@@
 Average depth of cars in the dataset is approximately $20$ meters.
-We compare four combinations of energies.
+We compare four combinations of energies against the initialization by~\cite{Song_Chandraker_2014} and a simple baseline which fits a 3D cuboid on the 3D point cloud reconstructed using SFM within detection bounding boxes in consecutive frames (for unobservable dimensions, e.g., only the back of a car is visible, we rely on 3D size priors).
+The energy $\EnergyTrackNoOcc$ represents the point track energy without accounting for occlusion, that is, we model $\EnergyTrack$ in the absence of $a^{ij} (\lambda)$.
+Similarly, $\EnergyBBoxNoOcc$ is the bounding box energy without the modification of $\bLambda_k$ that accounts for occlusion.
+
+From Table~\ref{tab:localizationExperiment}, the baseline method has the highest errors, which is likely due to lack of point tracks and incorrect point-to-object associations (using detection bounding boxes).
+Moreover, minimizing different combinations of energies yields lower errors than the initialization by~\cite{Song_Chandraker_2014}, which shows the advantage of our energy minimization.
+Finally, we observe that the use of the continuous occlusion model improves the localization accuracy in terms of the translation error, which is the most significant metric affected by all cues.
+Occlusion modeling for detection increases dimension error since we explicitly allow greater uncertainty in occluded edges of the bounding box.
+Note that none of our energies optimize yaw angles for static objects, which can be handled in practice through either the detector orientation or external information such as lane geometry.
+
+%We report errors in translation and dimension estimates, measured in meters per car, in Table~\ref{tab:localizationExperiment}.
+Average depth of cars in the dataset is approximately $20$ meters.
+We compare four combinations of energies with two baselines.
+We initialize the unknowns using \cite{Song_Chandraker_2014} whose accuracy is reported as \emph{Initialization} in the table.
+We develop a simple baseline by fitting cuboids to the point cloud created by triangulation of point tracks in two successive frames.
+The accuracy of this baseline is reported as \emph{Point cloud fit} in the table.
 The energy $\EnergyTrackNoOcc$ represents the point tracks energy without accounting for occlusion, that is, we model $\EnergyTrack$ in the absence of $a^{ij} (\lambda)$.

### 2016-04-06 CVPR16/Source/intro.tex
Make symbols consistent, Include most of reviewer comments (except for related works by Reviewer 2, Proof reading

@@
 A key advantage afforded by our occlusion model is unification.
-While previous approaches to handling occlusion are application-dependent, ours is physically-inspired, thus, flexible enough to be used in a variety of scenarios.
+While previous approaches to handling occlusions are application-dependent, ours is physically-inspired, thus, flexible enough to be used in a variety of scenarios.
 In this paper, we show that our theory can be used for uniformly modeling the association of SFM point tracks with static or dynamic objects (Section \ref{sec:association}), as well as modeling object detection scores in applications like 3D localization (Section \ref{sec:localization}).
-We demonstrate the application of our formulations for road scenes from the KITTI dataset \cite{Geiger_etal_2012}.
+We demonstrate the application of our formulations for road scenes from the KITTI raw dataset \cite{Geiger_etal_2012}.
 
@@
 Recent works use motion segmentation \cite{Rao_etal_2010,Brox_Malik_2010} as a precursor to localizing objects, which often suffices for moving objects \cite{Tron_Vidal_2007} and has been considered for multibody SFM \cite{Kundu_etal_2011}.
-But motion-based segmentation is not always applicable in road scenes, due to static parked cars, or dynamic cars that move with similar velocities.
+However, motion-based segmentation is not always applicable in road scenes, due to static parked cars, or dynamic cars that move with similar velocities.
 Occlusions make the problem more severe since point tracks get clustered together for static objects and may frequently appear to change association among dynamic objects in 2D.

### 2016-04-06 CVPR16/Source/occlusion.tex
Make symbols consistent, Include most of reviewer comments (except for related works by Reviewer 2, Proof reading

--- 2016-01-25 CVPR16/Source/occlusion.tex
@@
 \def\TP{TP}
-A common parametric modeling for objects, especially traffic participants (TP) in road scene understanding, is as opaque cuboids.\footnote{Notable exceptions exist, such as \cite{Zia_etal_2014}, but we note that such models are expensive, application-specific and still discontinuous.} However such models introduce discontinuities in the problem formulation and do not adequately account for uncertainties in pose and dimensions.
+A common parametric modeling for objects, especially traffic participants in road scene understanding, is as opaque cuboids.\footnote{Notable exceptions exist, such as \cite{Zia_etal_2014,Zia2015}, but we note that such models are expensive, application-specific and still discontinuous.} However, such models introduce discontinuities in the problem formulation and do not adequately account for uncertainties in pose and dimensions.
 With this motivation, we introduce our representation of 3D objects and our modeling of object-object relationships, which lead to a continuous occlusion model that correctly accounts for uncertainties in position and dimensions.
@@
   \vspace{-0.3cm}
-  \caption{\small We represent objects as translucent ellipsoids which allows formulation of transmision and reflection probabilities.
-This figure shows the reflection probability for the first object (violet) which is highest closer to the camera.
-Also note that the transmission probability is inversely proportional to occupancy.}
+  \caption{\small We represent objects as translucent ellipsoids, which leads to formulation of transmission and reflection probabilities.
+This figure shows the reflection probability for the first object (in violet), which has high values around the camera-facing face of the object.
+Also, note that the transmission probability is inversely proportional to occupancy.}
   \label{fig:reflectiontransimission}
@@
 Based on this intuition, we model objects as translucent 3D ellipsoids whose opacity is maximum at the center and falls off towards the edges.
-In particular, we model the occupancy at 3D location $\bx$ corresponding to an object $O_i$ centered at $\bp_i$ as:
+In particular, we model the occupancy at 3D location $\bx$ corresponding to an object $O_i$ centered at $\bp_i$ as
 \begin{align}
-  f^i_{\text{occ}}(\bx) = \cL(\bx; \bp_i, \bSigma_i)
+  f^i_{\text{occ}}(\bx) = \cL(\bx; \bp_i, \bSigma_i),
 \end{align}
@@
 \end{align}
-with $d(\bx, \bp) = (\bx-\bp)^\top\bSigma(\bx-\bp)$ being the Mahalanobis distance.
+with $d(\bx, \bp) = (\bx-\bp)^\top\bSigma^{-1}(\bx-\bp)$ being the Mahalanobis distance.
 We set $k = 10\ln{49}$ as the value that allows the logistic function $\cL$ to drop to $0.98$ at a distance $d = 0.9$ from the object center.
-The spread of the ellipsoid, determined by $\bSigma_i$, depends of the dimensions of the object.
+The spread of the ellipsoid, determined by $\bSigma_i$, depends on the dimensions of the object.
 Please refer to the supplementary material for the computation of $\bSigma_i$ from object dimensions.
@@
 Let $\bK$ be the intrinsic calibration matrix for the camera and $\ray = \displaystyle\frac{\bK^{-1}\bu_j}{\lVert \bK^{-1}\bu_j \rVert}$ be the unit vector along the backprojected ray from the camera center passing through $\bu_j$.
-Then, the probability of reflection at depth $\lambda$ along the ray $\ray$, by an object $O_i$, is determined by the gradient of the object's occupancy function $f_{occ}^i$:
+Then, the probability of reflection at depth $\lambda$ along the ray $\ray$, by an object $O_i$, is determined by the gradient of the object's occupancy function $f_{occ}^i$ as
 \begin{align}
-  P^{ij}_{\textit{reflection}} (\lambda) = (\max \{0, \nabla {f^i_{occ}}(\bx_j)^\top \ray \})^2
+   \Prefl = \frac{1}{Z}(\max \{0, \nabla {f^i_{occ}}(\bx_j)^\top \ray \})^2.
 \label{eq:evalPrefl}
 \end{align}
-The $\max \{ \}$ ensures that the negative probability due to gradient in the direction opposite to the ray is clipped off and squaring the function allows it to be smooth near zero.
-We note that in the extreme case of an object being Lambertian, the above reverts to a (squared) Lambertian reflection.
+The gradient $\nabla {f^i_{occ}}(\bx_j)$ encourages the reflection probability to be high near object boundaries, $\max$ ensures that negative probability due to gradient in the direction opposite to the ray is clipped off and squaring allows the function to be smooth near zero.
+$Z$ denotes the normalization factor.
+We note that in the extreme case of an object being fully opaque (i.e., $\nabla {f^i_{occ}(\bx_j)} \in \{0,1\}$), the above model reverts to a (squared) Lambertian reflection.
+Figure~\ref{fig:reflectiontransimission} shows an example of the reflection probability.
 
@@
 Since we are modeling occupancy as transparency, we derive inspiration from optics for the modeling of translucent objects.
-A model for transmission of light across a distance $\alpha$, through a medium of density $\rho$ and opacity $\beta$ is given by the Beer-Lambert Law:
+A model for transmission of light across a distance $\alpha$, through a medium of density $\rho$ and opacity $\beta$ is given by the Beer-Lambert law as
 \begin{align}
@@
 %
-In our formulation of scene occupancy, both opacity and density at a scene point $\bx_j$ are encapsulated within the total occupancy function summer over all objects, $\occftot = \sum_i \occf$.
-Further, the domain of our ocupancy function $\occftot$ is $[0, 1]$ instead of $[0, \infty)$ for opacity $\beta$.
+In our formulation of scene occupancy, both opacity and density at a scene point $\bx_j$ are encapsulated within the total occupancy function summed over all objects, $\occftot = \sum_i \occf$.
+Further, the domain of our occupancy function $\occftot$ is $[0, 1]$ instead of $[0, \infty)$ for opacity $\beta$.
 Thus, we replace $e^{-\beta\rho}$ by the transparency function $1 - \occftot$ and consequently, the transmission probability over a small distance $d\lambda$ is given by
@@
 \end{align}
-Here, $\prod_{c}^{\lambda}$ represents a \emph{product integral} from $c$ to $\lambda$, where $c$ is the position of camera screen, considered here to be equivalent to the focal length of the camera .\footnote{A product integral is a simple integral in the log domain:
+Here, $\prod_{c}^{\lambda}$ represents a \emph{product integral} from $c$ to $\lambda$, where $c$ is the position of camera screen, considered here to be equivalent to the focal length of the camera .\footnote{A product integral is a simple integral in the log domain
 \vspace{-0.2cm}
@@
 In practice, the integral for transmission probability \eqref{eq:ptrans-integral} is difficult to compute even numerically.
-So we choose a parameterization in the form of a product of sigmoid functions, which is a reasonable approximation to the behaviour of the transmission probability:
+So we choose a parameterization in the form of a product of sigmoid functions, which is a reasonable approximation to the behaviour of the transmission probability as follows
 %
@@
 %
-where $\cL_u(.)$ is sigmoid in image domain, with $\bmu_i$ and $\bGamma_i$ representing the elliptical projection of object $O_i$ in the image and $\cL_{\lambda}(.)$ is sigmoid in the depth domain with $\meandepth{i}$ the mean depth of object $O_i$.
+where $\cL_u(.)$ is sigmoid in the image domain, with $\bmu_i$ and $\bGamma_i$ representing the elliptical projection of object $O_i$ in the image and $\cL_{\lambda}(.)$ is sigmoid in the depth domain, with $\meandepth{i}$ being the mean depth of object $O_i$.
 That is,
@@
 \begin{align}
-\cL_u(\bu; \bmu_i, \bGamma_i) &= \frac{1}{1 + e^{-k_u(1 - (\bu - \bmu_i)^\top \bGamma_i (\bu - \bmu_i))}} \\
-  \cL_{\lambda}(\lambda; \meandepth{i}) &= \frac{1}{1 + e^{-k_d(\lambda - \meandepth{i})}}
+\cL_u(\bu; \bmu_i, \bGamma_i) &= \frac{1}{1 + e^{-k_u(1 - (\bu - \bmu_i)^\top \bGamma_i^{-1} (\bu - \bmu_i))}}, \\
+  \cL_{\lambda}(\lambda; \meandepth{i}) &= \frac{1}{1 + e^{-k_d(\lambda - \meandepth{i})}}.
 \end{align}
 %
-In Figure \ref{fig:compare:exact:approx:ptrans}, we compare the exact and relative formulations of transmission probability given by \eqref{eq:ptrans-integral} and \eqref{eq:evalCumulativePtrans}, respectively.
+In Figure \ref{fig:compare:exact:approx:ptrans}, we compare the exact and approximate formulations of transmission probability given by \eqref{eq:ptrans-integral} and \eqref{eq:evalCumulativePtrans}, respectively.
 Note that the choice of mean depth of the object causes some deviation from the exact transmission probability.
@@
   \vspace{-0.3cm}
-  \caption{\small Comparing the approximate $\Ptrans$ with exact version.
-The drop in approximate version of $\Ptrans$ is delayed because we assume drop at the center of the car rather than camera facing face of the car.}
+  \caption{\small Comparisons between the approximate and exact formulations of $\Ptrans$.
+The drop in the approximate version is delayed because we assume drop at the object center rather than the camera-facing face of the object.}
   \label{fig:compare:exact:approx:ptrans}

### 2016-04-06 CVPR16/Source/applications.tex
Make our use of camera poses and known number of objects clearer

@@
 %\label{sec:totalContPtTracksEnergy}
-Let $\relp{i}{t}$ be the pose of object $O_i$ at time $t$ in world coordinates (computed using the camera pose at time $t$ and the relative pose of object $O_i$ with respect to the camera).
+Let $\relp{i}{t}$ be the pose of object $O_i$ at time $t$ in world coordinates, which is computed using the camera pose at time $t$ and the relative pose of object $O_i$ with respect to the camera at time $t$.
 We denote $\projectionOf{.}$ and $\invProjectionOftm{.}$ as the forward and inverse projection functions that project a 3D point to the 2D image and vice versa.

### 2016-04-06 CVPR16/Source/experiments2.tex
Make our use of camera poses and known number of objects clearer

@@
 For a complete evaluation, we organize the point tracks into four sets: all point tracks, occluded point tracks, dynamic point tracks and dynamic as well as occluded point tracks.
-In addition to point tracks, the parameters (position, orientation, and dimensions) of all objects (cars) estimated by the method of \cite{Song_Chandraker_2014} are provided to our method (for computing association probability) and the baseline BBox method (for depth ordering).
+The parameters (position, orientation, and dimensions) of all objects (cars) estimated by the method of \cite{Song_Chandraker_2014} are provided to our method (for computing association probability) and the baseline BBox method (for depth ordering).
+The number of objects is known a priori in our model (from object tracking~\cite{Choi_Savarese_2010}) and is also provided to other methods such as BBox and RAS.
 

### 2016-04-06 CVPR16/Source/applications.tex
Add citations to the initialization for 3D object localization

@@
 \hline
-\multirow{5}{*}{\RotText{Est. by~\cite{Song_Chandraker_2014} for initialization}} & $\bp^c(t)$ & Position of camera at time $t$ \\
+\multirow{5}{*}{\RotText{Initialization by~\cite{Song_Chandraker_2014}}} & $\bp^c(t)$ & Position of camera at time $t$ \\
  & $\bomega^c(t)$ & Orientation of camera at time $t$ \\

### 2016-04-06 CVPR16/Source/experiments2.tex
Add citations to the initialization for 3D object localization

@@
     & 6.87 & 4.02\\
-    Initialization
+    Initialization by~\cite{Song_Chandraker_2014}
     & 5.61 & 3.23\\

### 2016-04-06 CVPR16/Source/intro.tex
Add citations to the initialization for 3D object localization

@@
 This allows assigning probabilities for each point in space belonging to an object, which can explicitly explain image observations and reason about occlusions.
-This is in contrast to prior works that consider occlusions in 2D, or through discrete occluder patterns or models that are not physically interpretable \cite{Hsiao_Herbert_2012,Pepik_etal_2013,Xiang_Savarese_2013,Zia_etal_2013,Zia_etal_2014}.
+This is in contrast to prior works that consider occlusions in 2D, or through discrete occluder patterns or models that are not physically interpretable \cite{Pepik_etal_2012,Pepik_etal_2013,Xiang_Savarese_2013,Zia_etal_2013,Zia_etal_2014,Zia2015}.
 

### 2016-04-06 CVPR16/Source/related.tex
Make symbols consistent, Include most of reviewer comments (except for related works by Reviewer 2, Proof reading
Add citations to the initialization for 3D object localization

--- 2015-11-07 CVPR16/Source/related.tex
@@
 Occlusion reasoning based on 2D image silhouettes is used to improve detection performance in \cite{Hsiao_Herbert_2012}.
-On the other hand our occlusion reasoning is based on 3D entities.
+On the other hand, our occlusion reasoning is based on 3D entities.
 In recent years, object detectors have also considered occlusion reasoning using 3D cues, often learned from a dataset of CAD models \cite{Pepik_etal_2012,Pepik_etal_2013,Xiang_Savarese_2013}.
@@
 Monocular frameworks like ours have also reasoned about occlusions, for instance, \cite{Wojek_etal_2013} considers partial object detectors.
-A detailed part-based representation of objects based on annotated CAD models is used for monocular scene understanding in \cite{Zia_etal_2013,Zia_etal_2014}, which also allows reasoning about mutual occlusions between objects.
+A detailed part-based representation of objects based on annotated CAD models is used for monocular scene understanding in \cite{Zia_etal_2013,Zia_etal_2014,Zia2015}, which also allows reasoning about mutual occlusions between objects.
 In contrast to these works, our monocular framework uses a physical modeling of occlusion in continuous space and derives unified representations for SFM points and object detection bounding boxes.
 This makes our model more general, extensible and amenable for continuous optimization.
+
+%One of the models closest to our unified occupancy model was recently presented by Rhodin et al.
+\cite{Rhodin:2015} applied to the problem of pose estimation.
+Although they model transmission probability like we do, they do not model reflectance probability.
+We explicitly model reflectance probability that differentiates between the center and surface of the 3D object.
 

### 2016-04-06 CVPR16/Source/contBBoxModel.tex
Parameter settings, Cite related work by Reviewer 2

@@
 \def\u{\mathbf{u}}
-With our model of $\Ptrans$ described in Section \ref{sec:ptransmission}, we can
+With our model of $\Ptrans$ as described in Section \ref{sec:ptransmission}, we can
 compute the probability of a point $\u$ in the image to be occluded, assuming

### 2016-04-06 CVPR16/Source/discussions.tex
Parameter settings, Cite related work by Reviewer 2

@@
 Our future work will explore speeding up the inference, for example, by approximating the graph with a tree using the Chow-Liu method \cite{chow1968approximating}, allowing belief propagation for fast inference.
+Another direction for future work is to replace a single ellipsoid by a set of spheres for modelling a translucent object~\cite{Rhodin2015}, which will better capture object boundary and appearance while remaining a continuous model.
 

### 2016-04-08 CVPR16/Source/applications.tex
update Supp

@@
 We exploit in this section the application of our continuous occlusion model to 3D object localization in road scenes, which further demonstrates the versatility of the proposed model.
-Given a set of 2D tracked feature points $\{\bu_j(t)\}$ and 2D detection bounding boxes $\{\bb{i}\}$ at frame $t$, the goal is to localize 3D traffic participants, in particular, for each traffic participant, estimating its position $\bp^i(t)$ and orientation $\bomega^i(t)$ on the ground plane and its 3D dimensions $\bB^i(t)$.
+Given a set of 2D tracked feature points $\{\bu_j(t)\}$ and 2D detection bounding boxes $\{\bb{i}\}$ at frame $t$, the goal is to localize 3D traffic participants, in particular, for each traffic participant, estimating its position $\bp^i(t)$, orientation $\bomega^i(t)$, and 3D dimensions $\bB^i(t)$ on the ground plane.
 Please refer to Table~\ref{tab:notations} for a summary of inputs and outputs.

### 2016-04-08 CVPR16/supplementarymaterial.tex
Added parameter values used for the experiments.
update Supp

@@
 where $\xt$ is a point in object coordinates.
-Given $\Omega^i$ as the pose of $O_i$ in camera coordinates, we can extract the rotation $\Rctot$ and translation $\tctot$ for converting points in camera coordinates to object coordinates and rewrite \eqref{equ:ellipsoidobj} as
+Given the relative pose of $O_i$ in camera coordinates, we can extract the rotation $\Rctot$ and translation $\tctot$ for converting points in camera coordinates to object coordinates and rewrite \eqref{equ:ellipsoidobj} as
 \begin{align}
@@
 
+\section{Parameter settings}
+\begin{table}[!h]
+  \centering
+\begin{tabular}{cccccc}
+  \toprule
+  Parameters
+  & $\lambda_{\text{track}}$  
+  & $\lambda_{\text{detect}}$ 
+  & $\lambda_{\text{dyn}}$    
+  & $\lambda_{\text{size}}$   
+  & $k$, $k_u$, $k_d$ \\
+  \midrule
+  Value
+  & 1
+  & 1
+  & 10
+  & 7
+  & $10\ln(49)$\\
+  \bottomrule
+\end{tabular}
+\caption{Parameter settings used in our experiments.}
+\label{tab:paramters}
+\end{table}
+
 \begin{comment}

### 2016-04-08 CVPR16/Source/contBBoxModel.tex
Camera ready version

--- 2016-04-06 CVPR16/Source/contBBoxModel.tex
@@
 Object detection is usually followed by non-maximal suppression that results in discarding similar bounding boxes.
-When we are jointly optimizing detections with other cues, it is usually not desirable to go with a single bounding box.
+When we are jointly optimizing detections with other cues, it is usually not desirable to use a single bounding box.
 To retain the entire detection output while maintaining the continuous form of our energies, we approximate the distribution of detection scores with a multi-modal sum of Gaussian-like logistic functions.
@@
 S(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \bLambda_k^{-1} \bepsilon_k^{i}(t) \right),
+\label{eq:GMMscores}
 \end{equation}
@@
 \def\u{\mathbf{u}}
-With our model of $\Ptrans$ described in Section \ref{sec:ptransmission}, we can
+With our model of $\Ptrans$ described in Section \ref{sec:ptransmission}, we 
 compute the probability of a point $\u$ in the image to be occluded, assuming
@@
 \end{align}
-If a portion of our proposed detection bounding box is known to be
-occluded, we would like to decrease the confidence in the detection score
-about the localization of that end of the object. Assuming that the occlusion
-is often on the boundaries of the detection bounding box, we want to decrease our
+If a portion of the proposed detection bounding box is known to be 
+occluded, one would like to decrease the confidence in the detection score 
+about the localization of that end of the object. Assuming that occlusions 
+are more likely on the boundaries of the detection bounding box, we wish to decrease the 
 confidence on the mean detection boundaries around the occluded boundaries.
-To re-model our detection scores scaled by continuous occlusion, we sample
+To re-model detection scores scaled by continuous occlusion, we sample
 $\Theta_{i}(\mathbf{u}, \meandepth{i})$ at the hypothesized detection boundaries from
-the Gaussian mixture model (GMM) $S(.)$ and we augment the detection boundary covariance matrix by
-$\mathcal{P}_{i} = \rho_{i}\rho_{i}^\top$ where $\rho_{i} = \Theta_{i}(\mathbf{u},
-\meandepth{i})$. The new covariance matrix in the detection score is given by 
+the Gaussian mixture model (GMM) $S(.)$ in \eqref{eq:GMMscores} and augment the detection boundary covariance matrix by
+$\mathcal{P}_{i} = \rho_{i}\rho_{i}^\top$, where $\rho_{i} = \Theta_{i}(\mathbf{u},
+\meandepth{i})$. The new covariance matrix for the detection scores is given by 
   $\bLambda'_k = \mathcal{P}_{i} + \bLambda_k$ for all $k$.
 The detection score GMM $S'(.)$ with explicit occlusion reasoning is given by replacing the covariance
-matrix as follows
+matrix, as follows:
 %
@@
 
-The energy of detection scores is simply taken to be the inverse of the detection score as
+The energy of detection scores is simply taken to be the inverse of the above detection score, that is,
 \begin{align}

### 2016-04-08 CVPR16/Source/discussions.tex
Camera ready version

@@
 A key advantage is its physical inspiration that lends flexibility towards occlusion reasoning for varied elements of scene understanding, such as point tracks, object detection bounding boxes and detection scores.
-We demonstrate unified modeling for different applications such as point tracks associations and 3D localization.
-Our occlusion model can uniformly handle static and dynamic objects, which is an advantage over motion segmentation methods for point-object association.
+We demonstrate unified modeling for different applications such as object-point track associations and 3D localization.
+Our occlusion model can uniformly handle static and dynamic objects, which is an advantage over motion segmentation methods for object-point association.
 A challenge is that inference for 3D localization is currently slow, requiring a few minutes per window of frames, which prevents exhaustive cross-validation for tuning of weights.
-Our future work will explore speeding up the inference, for example, by approximating the graph with a tree using the Chow-Liu method \cite{chow1968approximating}, allowing belief propagation for fast inference.
+Our future work will explore speeding up the inference, for example, by approximating the graph with a tree using the Chow-Liu method \cite{chow1968approximating}, which will allow belief propagation for fast inference.
 Another direction for future work is to replace a single ellipsoid by a set of spheres for modelling a translucent object~\cite{Rhodin2015}, which will better capture object boundary and appearance while remaining a continuous model.
+
+\vspace{-0.2cm}
+\paragraph{Acknowledgments}
+This work was part of V.~Dhiman's internship at NEC Labs America, in Cupertino. V.~Dhiman and J.~J.~Corso were also supported by NSF NRI IIS 1522904.
 

### 2016-04-08 CVPR16/Source/experiments2.tex
Update ordering in Figure 6
Parameter settings, Cite related work by Reviewer 2
Camera ready version

@@
 
-In this section, we benchmark our continuous occlusion model for point-to-object association against the baseline method using detection bounding boxes and state-of-the-art methods for motion segmentation \cite{Rao_etal_2010,Brox_Malik_2010}.
+In this section, we benchmark our continuous occlusion model for point-to-object association against the baseline method using detection bounding boxes and state-of-the-art methods for motion segmentation \cite{Brox_Malik_2010,Rao_etal_2010}.
 We then show how the proposed model may be applied for 3D object localization in road scenes.
@@
   \caption{\small Association errors on different sets of input point tracks.
-Numbers on x-axis represent sequence numbers in the KITTI raw dataset.
+Numbers on the x-axis represent sequence numbers in the KITTI raw dataset.
 Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
@@
     & Associations & Errors & Associations & Errors\\
+    \rotatebox{90}{\hspace{1em} RAS}%
+    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_RAS-small.png}%
+    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_RAS_correct_incorrect-small.png}%
+    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_RAS-small.png}%
+    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
+	\rotatebox{90}{\hspace{1em} BM}%
+    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png}%
+    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}%
+    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png}%
+    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\    
     \rotatebox{90}{\hspace{1em} BBox}%
@@
     & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{1em} BM}%
-    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png}%
-    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}%
-    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png}%
-    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
-    \rotatebox{90}{\hspace{1em} RAS}%
-    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_RAS-small.png}%
-    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_RAS_correct_incorrect-small.png}%
-    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_RAS-small.png}%
-    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
     \rotatebox{90}{\hspace{1em} Ours}%
@@
 \subsection{Localization Experiments}
-We report errors in translation and dimension estimates, measured in meters per car, in Table~\ref{tab:localizationExperiment}.
-Average depth of cars in the dataset is approximately $20$ meters.
-We compare four combinations of energies against the initialization by~\cite{Song_Chandraker_2014} and a simple baseline which fits a 3D cuboid on the 3D point cloud reconstructed using SFM within detection bounding boxes in consecutive frames (for unobservable dimensions, e.g., only the back of a car is visible, we rely on 3D size priors).
-The energy $\EnergyTrackNoOcc$ represents the point track energy without accounting for occlusion, that is, we model $\EnergyTrack$ in the absence of $a^{ij} (\lambda)$.
+We report errors in translation and dimension estimates, measured in meters per car, in Table \ref{tab:localizationExperiment}.
+The average depth of cars in the dataset is approximately $20$ meters.
+We compare four combinations of energies against the initialization using \cite{Song_Chandraker_2014} and a simple baseline which fits a 3D cuboid on the 3D point cloud reconstructed using SFM within detection bounding boxes in consecutive frames (for unobservable dimensions, such as when only the back of a car is visible, we rely on 3D size priors).
+The energy $\EnergyTrackNoOcc$ represents the point track energy without accounting for occlusions, that is, we model $\EnergyTrack$ in the absence of $a^{ij} (\lambda)$.
 Similarly, $\EnergyBBoxNoOcc$ is the bounding box energy without the modification of $\bLambda_k$ that accounts for occlusion.
+We use $\lambda_{\text{track}} = 1$, $\lambda_{\text{detect}} = 1$, $\lambda_{\text{dyn}} = 10$, $\lambda_{\text{size}} = 7$.
+Please refer to the supplementary material for a detailed list of parameter settings.
 
 From Table~\ref{tab:localizationExperiment}, the baseline method has the highest errors, which is likely due to lack of point tracks and incorrect point-to-object associations (using detection bounding boxes).
-Moreover, minimizing different combinations of energies yields lower errors than the initialization by~\cite{Song_Chandraker_2014}, which shows the advantage of our energy minimization.
+Moreover, minimizing different combinations of energies yields lower errors than the initialization with \cite{Song_Chandraker_2014}, which shows the advantage of our energy minimization.
 Finally, we observe that the use of the continuous occlusion model improves the localization accuracy in terms of the translation error, which is the most significant metric affected by all cues.

### 2016-04-08 CVPR16/Source/intro.tex
Camera ready version

@@
 In particular, assigning 2D point tracks to independent, but potentially occluding, objects is a fundamental challenge in computer vision problems such as multibody SFM \cite{Ozden_etal_2010}.
-Recent works use motion segmentation \cite{Rao_etal_2010,Brox_Malik_2010} as a precursor to localizing objects, which often suffices for moving objects \cite{Tron_Vidal_2007} and has been considered for multibody SFM \cite{Kundu_etal_2011}.
+Recent works use motion segmentation \cite{Brox_Malik_2010,Rao_etal_2010} as a precursor to localizing objects, which often suffices for moving objects \cite{Tron_Vidal_2007} and has also been considered for multibody SFM \cite{Kundu_etal_2011}.
 However, motion-based segmentation is not always applicable in road scenes, due to static parked cars, or dynamic cars that move with similar velocities.
@@
 %In contrast, we leverage the success of 
-Indeed, we show in Section \ref{sec:experiments} that our point track association outperforms state-of-the-art motion segmentation, as well as a baseline that uses detection bounding boxes but does not consider occlusions.
+Indeed, we show in Section \ref{sec:experiments} that our point track association outperforms state-of-the-art motion segmentation methods, as well as a baseline that uses detection bounding boxes but does not consider occlusions.
 
@@
 In contrast, our unified occlusion model allows a probabilistic soft assignment of point tracks to objects, as well as an occlusion-aware interpretation of object detection outputs.
-Our model is continuous, so remains amenable to the use of continuous optimization tools.
+Our model is continuous, so it remains amenable to the use of continuous optimization tools.
 

### 2016-04-08 CVPR16/Source/occlusion.tex
update Supp
Camera ready version

@@
   \vspace{-0.3cm}
-  \caption{\small We represent objects as translucent ellipsoids, which leads to formulation of transmission and reflection probabilities.
-This figure shows the reflection probability for the first object (in violet), which has high values around the camera-facing face of the object.
+  \caption{\small We represent objects as translucent ellipsoids, which leads to the formulation of transmission and reflection probabilities.
+This figure shows the reflection probability for the first object (in violet), which has high values around the camera-facing side of the object.
 Also, note that the transmission probability is inversely proportional to occupancy.}
@@
 Intuitively, we consider traffic participants to be regions of 3D space with a high probability of occupancy.
-We model the uncertainty in occupancy as a translucency function, with regions more likely to be occupied by an object considered more opaque, while regions more likely to be free space are more transparent.
+We model the uncertainty in occupancy as a translucency function, with regions more likely to be occupied by an object considered more opaque and regions more likely to be free space considered more transparent.
 Based on this intuition, we model objects as translucent 3D ellipsoids whose opacity is maximum at the center and falls off towards the edges.
@@
 \end{align}
-The gradient $\nabla {f^i_{occ}}(\bx_j)$ encourages the reflection probability to be high near object boundaries, $\max$ ensures that negative probability due to gradient in the direction opposite to the ray is clipped off and squaring allows the function to be smooth near zero.
-$Z$ denotes the normalization factor.
-We note that in the extreme case of an object being fully opaque (i.e., $\nabla {f^i_{occ}(\bx_j)} \in \{0,1\}$), the above model reverts to a (squared) Lambertian reflection.
+The gradient $\nabla {f^i_{occ}}(\bx_j)$ encourages the reflection probability to be high near object boundaries, the $\max$ ensures that negative probability due to the gradient in the direction opposite to the ray is clipped off and squaring allows the function to be smooth near zero.
+Here, $Z$ denotes the normalization factor.
+We note that in the extreme case of an object being fully opaque (that is, $\nabla {f^i_{occ}(\bx_j)} \in \{0,1\}$), the above model reverts to a (squared) Lambertian reflection.
 Figure~\ref{fig:reflectiontransimission} shows an example of the reflection probability.
@@
 In practice, the integral for transmission probability \eqref{eq:ptrans-integral} is difficult to compute even numerically.
-So we choose a parameterization in the form of a product of sigmoid functions, which is a reasonable approximation to the behaviour of the transmission probability as follows
+So we choose a parameterization in the form of a product of sigmoid functions, which is a reasonable approximation to the behaviour of the transmission probability, as follows:
 %

### 2016-04-08 CVPR16/Source/related.tex
Camera ready version

@@
 %\cite{Tron_Vidal_2007,Rao_etal_2010}. This also motivates further applications such as object segmentation based on point trajectories \cite{Brox_Malik_2010}. 
-Closer to our application, motion segmentation is also used within multibody SFM frameworks \cite{Ozden_etal_2010,Kundu_etal_2011,Namdev2012}.
+Closer to our application, motion segmentation is also used within multibody SFM frameworks \cite{Kundu_etal_2011,Namdev2012,Ozden_etal_2010}.
 In contrast to these works, our formulation does not distinguish between moving and static objects and also explicitly reasons about occlusions due to 3D object geometries for associating point tracks to individual objects.
@@
 \paragraph{3D localization}
-One of the vital goals of 3D scene understanding is to localize the 3D objects in complex scenes. 
+One of the vital goals of 3D scene understanding is to localize 3D objects in complex scenes. 
 %For instance, using stereo imagery, several visual cues are combined in \cite{Geiger_etal_2014} to simultaneously determine object locations and a rough intersection topology. 
-Monocular frameworks like ours have also reasoned about occlusions, for instance, \cite{Wojek_etal_2013} considers partial object detectors.
+Monocular frameworks like ours have also reasoned about occlusions, for instance, partial object detectors are considered in \cite{Wojek_etal_2013}.
 A detailed part-based representation of objects based on annotated CAD models is used for monocular scene understanding in \cite{Zia_etal_2013,Zia_etal_2014,Zia2015}, which also allows reasoning about mutual occlusions between objects.

### 2016-04-08 CVPR16/supplementarymaterial.tex
update Supp
Camera ready version

--- 2016-01-25 CVPR16/supplementarymaterial.tex
@@
 
-%\cvprfinalcopy % *** Uncomment this line for the final submission
+\cvprfinalcopy % *** Uncomment this line for the final submission
 
@@
 
-\author{Vikas Dhiman\\
-  University of Michigan\\
-  Ann Arbor, MI, USA\\
-{\tt\small dhiman@umich.edu}
-Quoc-Huy Tran\\
-NEC Laboratories America, Inc.\\
-Cupertino, CA, USA\\
-{\tt\small qhtran@nec-labs.com}
+\author{Vikas Dhiman$^\dagger$
 \and
-Manmohan Chandraker\\
-NEC Laboratories America, Inc.\\
-Cupertino, CA, USA\\
-{\tt\small manu@nec-labs.com}
+Quoc-Huy Tran$^*$
 \and
-Jason J Corso\\
-  University of Michigan\\
-  Ann Arbor, MI, USA\\
-{\tt\small jjcorso@eecs.umich.edu}
+Jason J. Corso$^\dagger$
+\and
+Manmohan Chandraker$^*$
+\and
+$^\dagger$ University of Michigan,\\
+Ann Arbor, MI, USA
+%{\tt\small \{dhiman,jjcorso\}@umich.edu}
+\and
+$^*$ NEC Laboratories America, Inc.\\
+Cupertino, CA, USA
+%{\tt\small \{qhtran,manu\}@nec-labs.com}
 }
@@
 
+\section{Parameters value used}
+\begin{table}[!h]
+  \centering
+\begin{tabular}{cccccc}
+  \toprule
+  Parameters
+  & $\lambda_{\text{track}}$  
+  & $\lambda_{\text{detect}}$ 
+  & $\lambda_{\text{dyn}}$    
+  & $\lambda_{\text{size}}$   
+  & $k_u$, $k_d$ \\
+  \midrule
+  Value
+  & 1
+  & 1
+  & 10
+  & 7
+  & $10\ln(49)$\\
+  \bottomrule
+\end{tabular}
+\caption{Parameter values used for experiments}
+\label{tab:paramters}
+\end{table}
+
 \begin{comment}

### 2016-04-08 CVPR16/supplementarymaterial.tex
Camera ready version

@@
 
-\section{Parameters value used}
+\section{Parameter settings}
 \begin{table}[!h]
@@
   \toprule
-  Parameters
+  Parameter
+  & $k$, $k_u$, $k_d$ 
   & $\lambda_{\text{track}}$  
@@
   & $\lambda_{\text{dyn}}$    
-  & $\lambda_{\text{size}}$   
-  & $k_u$, $k_d$ \\
+  & $\lambda_{\text{size}}$\\
+
   \midrule
   Value
+  & $10\ln({49})$
   & 1
@@
   & 10
-  & 7
-  & $10\ln(49)$\\
+  & 7\\
   \bottomrule
 \end{tabular}
-\caption{Parameter values used for experiments}
+\caption{Parameter settings for our experiments.}
 \label{tab:paramters}

### 2016-04-08 CVPR16/Source/applications.tex
Camera ready version

@@
 \hline
-\multirow{5}{*}{\RotText{Initialization by~\cite{Song_Chandraker_2014}}} & $\bp^c(t)$ & Position of camera at time $t$ \\
+\multirow{5}{*}{\RotText{Initialization with~\cite{Song_Chandraker_2014}}} & $\bp^c(t)$ & Position of camera at time $t$ \\
  & $\bomega^c(t)$ & Orientation of camera at time $t$ \\
@@
 
-Given 2D image points $\{\bu_j\}$ which are tracked between consecutive frames and a set of objects $\{O_i\}$ appearing in the frames, we aim to associate $\bu_j$ with $O_i$.
+Given 2D image points $\{\bu_j\}$ that are tracked between consecutive frames and a set of objects $\{O_i\}$ appearing in the frames, we aim to associate $\bu_j$ with $O_i$.
 Based on our continuous occlusion model in Section~\ref{sec:setup}, the association probability $\assocP$ between point track $\bu_j$ and object $O_i$ at depth $\lambda$ can be defined as
@@
 
-Using both of the evidence terms in \eqref{eq:defineassocP} and \eqref{eq:Passocbyreproj}, we can define the new association probability $P^{ij}_{\text{assoc}}$ as follows
+Using both of the evidence terms in \eqref{eq:defineassocP} and \eqref{eq:Passocbyreproj}, we can define the new association probability $P^{ij}_{\text{assoc}}$, as follows:
 \begin{align}
-  P^{ij}_{\text{assoc}} = \frac{1}{Z"}\int_0^{\infty} \assocP \exp(-\Ereproj(\lambda))d\lambda,
+  P^{ij}_{\text{assoc}} = \frac{1}{Z''}\int_0^{\infty} \assocP \exp(-\Ereproj(\lambda))d\lambda,
   \label{eq:prob-assoc}
 \end{align}
-where $Z"$ is the new normalization coefficient.
+where $Z''$ is the new normalization coefficient.
 
@@
 
-We exploit in this section the application of our continuous occlusion model to 3D object localization in road scenes, which further demonstrates the versatility of the proposed model.
-Given a set of 2D tracked feature points $\{\bu_j(t)\}$ and 2D detection bounding boxes $\{\bb{i}\}$ at frame $t$, the goal is to localize 3D traffic participants, in particular, for each traffic participant, estimating its position $\bp^i(t)$, orientation $\bomega^i(t)$, and 3D dimensions $\bB^i(t)$ on the ground plane.
+In this section, we exploit our continuous occlusion model for another application, namely, 3D object localization in road scenes, which further demonstrates its versatility.
+Given a set of 2D tracked feature points $\{\bu_j(t)\}$ and 2D detection bounding boxes $\{\bb{i}\}$ at frame $t$, the goal is to localize 3D traffic participants.
+In particular, for each traffic participant, we wish to estimate its position $\bp^i(t)$ and orientation $\bomega^i(t)$ on the ground plane and its 3D dimensions $\bB^i(t)$.
 Please refer to Table~\ref{tab:notations} for a summary of inputs and outputs.
 
-We build a graphical model for representing object relationships and decompose the negative log likelihood as follows
+We construct a graphical model for representing relationships among objects, as well as between objects and point tracks.
+Figure~\ref{fig:graphmodel} illustrates an example of the graph and energies.
+The negative log likelihood is decomposed as follows:
 %
@@
 Here, $\lambda_{\text{track}}$, $\lambda_{\text{detect}}$, $\lambda_{\text{dyn}}$, $\lambda_{\text{size}}$ are energy weights, $N$ is the number of objects in the sequence, $s_i$ and $t_i$ are respectively the starting and ending frames of object $O_i$, and $\tilde{Z}$ is the normalization coefficient.
-Figure~\ref{fig:graphmodel} illustrates an example of the graph and energies.
 Next, we present our unified continuous occlusion modeling for both point track and bounding box energies.
@@
 \end{multline}
-where $N$ and $M$ are respectively the number of objects and points and $\assocP$ is the association probability of point $\trackp{t}$ with object $O_i$ at depth $\lambda$, given by \eqref{eq:defineassocP}.
+where $N$ and $M$ are, respectively, the number of objects and points and $\assocP$ is the association probability of point $\trackp{t}$ with object $O_i$ at depth $\lambda$, given by \eqref{eq:defineassocP}.
 
@@
 \paragraph{Inference on graphical model}
-We apply Metropolis Hastings method~\cite{mackay1998introduction} for performing inference on the graphical model.
-Since we are optimizing over continuous variables, we use Gaussian distribution as the proposal function.
+We apply the Metropolis-Hastings method~\cite{mackay1998introduction} to perform inference on the graphical model.
+Since we optimize over continuous variables, we use the Gaussian distribution as the proposal function.
 We choose this over alternatives such as block-coordinate descent since they are slower in our experiments.

### 2016-04-09 CVPR16/Source/occlusion.tex
Camera ready version
The fonts need to be embedded which was not true for matlab generated plotPtransimission.

@@
 with $d(\bx, \bp) = (\bx-\bp)^\top\bSigma^{-1}(\bx-\bp)$ being the Mahalanobis distance.
-We set $k = 10\ln{49}$ as the value that allows the logistic function $\cL$ to drop to $0.98$ at a distance $d = 0.9$ from the object center.
+We set $k = 10\ln({49})$ as the value that allows the logistic function $\cL$ to drop to $0.98$ at a distance $d = 0.9$ from the object center.
 The spread of the ellipsoid, determined by $\bSigma_i$, depends on the dimensions of the object.
@@
   \includegraphics[width=0.9\columnwidth]{results/plotPtransmission_exact_vs_approx_pt_vis-small.png}\\
-  \includegraphics[trim=0.0 0 0.3in 0, clip, width=0.9\columnwidth]{results/plotPtransmission_exact_vs_approx.pdf}
+  \includegraphics[trim=0.0 0 0.3in 0, clip, width=0.9\columnwidth]{results/plotPtransmission_exact_vs_approx_embedded_fonts.pdf}
   \vspace{-0.3cm}

### 2016-04-14 CVPR/Source/figure_introduction.tex
Created presentation and poster for mid west vision conference.

--- 2016-04-06 CVPR16/Source/intro.tex
@@
-\section{Introduction}
-
-%Occlusions present a significant challenge to scene understanding.
-
-As a two-dimensional (2D) projection of the three-dimensional (3D) world, image formation is associated with a loss of information.
-This is especially significant when objects in 3D space occlude each other with respect to the camera viewpoint.
-In recent years, we have seen remarkable progress in various aspects of scene understanding, such as structure from motion (SFM) and object detection.
-However, occlusions still present a challenge, with the difficulty of physically modeling them being a major bottleneck.
-%Prior works have considered occlusions in 2D or through discrete occluder patterns
-
-\begin{figure}[!!t]
 \begin{center}
@@
 \label{fig:page1}
-\vspace{-0.4cm}
-\end{figure}
-
-Our main contribution is a novel theoretical model for occlusion handling that is continuous and fully 3D.
-Our model is motivated by insights from computer graphics, whereby we represent objects as translucent 3D ellipsoids.
-In Section \ref{sec:setup}, we develop novel continuous models for representing \emph{transmission} and \emph{reflection} probabilities for each ray emanating from the camera.
-This allows assigning probabilities for each point in space belonging to an object, which can explicitly explain image observations and reason about occlusions.
-This is in contrast to prior works that consider occlusions in 2D, or through discrete occluder patterns or models that are not physically interpretable \cite{Hsiao_Herbert_2012,Pepik_etal_2013,Xiang_Savarese_2013,Zia_etal_2013,Zia_etal_2014}.
-
-A key advantage afforded by our occlusion model is unification.
-While previous approaches to handling occlusions are application-dependent, ours is physically-inspired, thus, flexible enough to be used in a variety of scenarios.
-In this paper, we show that our theory can be used for uniformly modeling the association of SFM point tracks with static or dynamic objects (Section \ref{sec:association}), as well as modeling object detection scores in applications like 3D localization (Section \ref{sec:localization}).
-We demonstrate the application of our formulations for road scenes from the KITTI raw dataset \cite{Geiger_etal_2012}.
-
-In particular, assigning 2D point tracks to independent, but potentially occluding, objects is a fundamental challenge in computer vision problems such as multibody SFM \cite{Ozden_etal_2010}.
-Recent works use motion segmentation \cite{Rao_etal_2010,Brox_Malik_2010} as a precursor to localizing objects, which often suffices for moving objects \cite{Tron_Vidal_2007} and has been considered for multibody SFM \cite{Kundu_etal_2011}.
-However, motion-based segmentation is not always applicable in road scenes, due to static parked cars, or dynamic cars that move with similar velocities.
-Occlusions make the problem more severe since point tracks get clustered together for static objects and may frequently appear to change association among dynamic objects in 2D.
-%In contrast, we leverage the success of 
-Indeed, we show in Section \ref{sec:experiments} that our point track association outperforms state-of-the-art motion segmentation, as well as a baseline that uses detection bounding boxes but does not consider occlusions.
-
-Another potential application of our proposed model is towards 3D localization in road scenes.
-Prior works such as \cite{Song_Chandraker_2015} combine information from point tracks and detection bounding boxes, but do not consider occlusions for either.
-In contrast, our unified occlusion model allows a probabilistic soft assignment of point tracks to objects, as well as an occlusion-aware interpretation of object detection outputs.
-Our model is continuous, so remains amenable to the use of continuous optimization tools.
-
-To summarize, our main contributions are:
-\vspace{-0.2cm}
-\begin{tight_itemize}
-%\setlength\itemsep{0cm}
-\item A novel theoretical model for handling occlusions that is continuous and formulated in 3D.
-\item Unified occlusion handling for point tracks in SFM and bounding boxes and detection scores in object detection.
-\item Application of our model to association of point tracks with both static and moving objects, improving over motion segmentation and occlusion-unaware baselines.
-\item Application of our unified formulation to 3D localization of traffic participants in road scenes.
-\end{tight_itemize}
-
-%A fundamental problem in computer vision is to separate feature points of multiple objects which are tracked through a video sequence.
-The assignments of point tracks to objects can serve as an important preprocessing step for different applications such as 3D localization and reconstruction, where the point tracks associated with an individual object can be used to localize or reconstruct the object in 3D space accurately.
-In this paper, we focus on road scenes in autonomous driving applications which often include dynamic and static objects simultaneously.
-For example, some cars are parked near the curb while other cars are moving on the street.
-
-%Motion segmentation approaches~\cite{Rao_etal_2010,Brox_Malik_2010} usually rely on object motions for clustering point tracks.
-Since point tracks of the same object possess similar motion patterns, these methods generally produce accurate point-to-object associations for dynamic objects~\cite{Tron_Vidal_2007}.
-However, when there are static objects in the scene, their corresponding point tracks are often clustered together, which decreases the performances significantly and makes motion segmentation approaches unsuitable for road scenes with combinations of dynamic and static objects.
-Moreover, object occlusions are frequently involved in road scenes, where cars are relatively close to each other and move in the same directions, which makes the problem of point-to-object association for road scene understanding become more challenging.
-
-%In this work, we first propose to model objects as 3D ellipsoids.
-Motivated by image formulation theory in computer graphics, we then develop novel continuous models for representing \emph{transmission} and \emph{reflection} probabilities, which can explicitly explain image observations and reason about object occlusions.
-Leveraging on the success of object detection and tracking algorithms~\cite{Felzenszwalb_etal_2010,Choi_Savarese_2010}, we assume that detection bounding boxes and object tracklets are provided, thus we concentrate on segmenting point tracks that are computed only within object tracklets~\cite{Zach2007}, including both dynamic and static point tracks.
-As we will show in the experiments, the proposed continuous occlusion modelling method outperforms the baseline method which merely uses bounding boxes for dealing with occlusions.
-Furthermore, our method is not based on object motions and hence does not suffer from static objects as other state-of-the-art motion segmentation methods~\cite{Rao_etal_2010,Brox_Malik_2010}.
-
-%As another important contribution, we examine the applicability of the proposed model for 3D localization in autonomous driving.
-In contrast to the bounding box baseline method, which uses hard assignments of point tracks to objects (i.e., $\{0,1\}$ probabilities), our continuous occlusion modelling method employs soft assignments (i.e., [$0,1$] probabilities).
-Consequently, it offers a \emph{unified} continuous occlusion modelling for both point track and bounding box energies, which allows the use of effective continuous optimization tools.
-As we will show later, the proposed model benefits the task of 3D localization in autonomous driving in terms of lower translation and dimension errors compared to those of~\cite{Song_Chandraker_2014}, which employs bounding boxes for point-to-object associations.
-
-%The rest of the paper is organized as follows: Section~\ref{sec:related} discusses related work.
-Section~\ref{sec:setup} describes the proposed continuous occlusion model for road scene understanding.
-Section~\ref{sec:experiments} presents detailed experiments for point-to-object association and 3D localization.
-Finally, we conclude in Section~\ref{sec:conclusions}.
-
-%The problem of segmenting points to objects often comes up in different computer vision problems especially in multi-body reconstruction and localization.
-Given correspondence points on consecutive frames, the problem becomes one of finding out which points belong to which object, following which one can use the consensus of segmented points to reconstruct or localize the object more accurately.
-Without additional information, this is a very difficult problem as attempted by semantic segmentation and motion segmentation methods.
-However, in the problems like reconstruction and localization one can use the hypothesis of the algorithm as the feedback.
-% What is the problem we are trying to solve, and why is it even important?
-
-% What did we do We propose a novel model for representation of objects in the scene so that point tracks can be probabilistically associated with objects while accounting for object occlusions.
-% Why is it novel
-
-%Although our proposed model is inspired by Milan et al.\cite{Milan_etal_2014}, it is more detailed and more principled than their work.
-Milan et al.
-used soft ellipses and sigmoids to model pedestrians and their occlusions.
-Our reasoning is instead in 3D.
-We use ellipsoids to model objects and reason about their occupancies of the space to model their occlusions.
-% Ok you proposed a model is it of any use
-% How does it compare to state of art
-% We show that our continuous occlusion model achieves significantly lower point-to-object association errors compared to the baseline method using detection bounding boxes and other state-of-the-art methods for motion segmentation~\cite{Brox_Malik_2010, Rao_etal_2010}.
-As a consequence, our model benefits the task of 3D localization of traffic participants in autonomous driving.

### 2016-04-14 poster/poster.tex
Cleaner and working version of repository.
Created presentation and poster for mid west vision conference.

@@
 
-\documentclass[final]{beamer}
+\documentclass[handout,final]{beamer}
 \usepackage{beamerposter}
@@
 
+\usepackage{booktabs}
 \usepackage{bm}
@@
 \tikzset{/tikz/y=2.5cm}
+
+\newcommand{\Ptransmission}{P_{\textit{transmission}}}%
 
@@
 
-\title{3D object localization in road scenes using graphical models}
-\author{Vikas Dhiman \and Manmohan Chandrakar \and Jason J Corso}
-\institute{University of Michigan}
+\title{A Continuous Occlusion Model for Road Scene Understanding}
+\author{Vikas Dhiman$^\dagger$ \and Quoc-Huy Tran$^*$ \and Jason J Corso$^\dagger$ \and Manmohan Chandraker$^*$}
+\institute{$^\dagger$University of Michigan, Ann Arbor, MI \qquad $^*$NEC Labs, Cupertino, CA}
 
@@
       \begin{block}{Introduction}
-        To accomplish fully or partial autonomous driving we need 3D
-        localization of traffic participants in the scene. 
-        Since laser scanners and stable wide--baseline stereo setups are
-        expensive, we focus on solving the problem using monocular video, GPS
-        and maps as our input. Given the video we extract detection bounding
-        boxes, ground plane and point tracks.
-        We formulate the problem of 3D localization in a probabilistic graphical
-        model specifically a factor graph model. We use additional heuristic
-        constraints like collision constraint, that leads to a global consistent solution.
-        Using these multiple sources of information that provide, possibly conflicting, evidence about
-        the location of traffic participant, a consistent meaningful solution must be estimated. 
-        We formulate the problem in factor graph
-        formalism and use off-the-shelf methods for inference.
-
-        % Related work
-        %One of the central goals of 3D scene understanding is to localize the 3D positions and orientations of objects in complex scenes.
-        Using
-        stereo imagery, several visual cues are combined in \cite{Geiger_etal_2014} to
-        simultaneously determine object locations and a rough intersection topology.
-        Similar to us, other works have also considered monocular frameworks. Notably,
-        occlusions are explicitly handled in \cite{Wojek_etal_2013} by considering
-        partial object detectors. A detailed part-based representation of objects based
-        on annotated CAD models is used for monocular scene understanding in
-        \cite{Zia_etal_2013,Zia_etal_2014}, which also allows reasoning about mutual
-        occlusions between objects. In contrast to these works, our monocular framework
-        uses a physical modeling of occlusion in continuous space, which makes it more
-        general, extensible and amenable for continuous optimization.
+        \begin{figure}[!!t]
+          \input{Source/figure_introduction.tex}
+        \end{figure}
       \end{block}
 
-      \begin{block}{Modeling}
+      \begin{block}{Continuous Occlusion Model}
+        \begin{align}
+          f^i_{\text{occ}}(\bx) = \cL(\bx; \bp_i, \bSigma_i),
+        \end{align}
+        \begin{align}
+          P^{ij}_{\textit{observation}} = P^{ij}_{\textit{reflection}}P^{j}_{\textit{transmission}}.
+          \label{eq:imgform}
+        \end{align}
+        \begin{align}
+          \Prefl = \frac{1}{Z}(\max \{0, \nabla {f^i_{occ}}(\bx_j)^\top \ray \})^2.
+          \label{eq:evalPrefl}
+        \end{align}
+
+        \begin{align}
+          P^j_{\textit{transmission}}(\lambda) &= \prod_{c}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda}\\
+          &\approx \prod_i (1 - \cL_u (\bu; \bmu_i, \bGamma_i) \cL_{\lambda}(\lambda; \meandepth{i})).
+          \label{eq:ptrans-integral}
+        \end{align}
+
+        % \begin{figure}
+        %   \usetikzlibrary{calc}
+        %   \centering
+        %   \begin{tikzpicture}
+        %     \input{Source/reflectiontransmissiongraph.tex}
+        %   \end{tikzpicture}
+        %   \vspace{-0.3cm}
+        %   \caption{\small We represent objects as translucent ellipsoids, which leads to the formulation of transmission and reflection probabilities.
+This figure shows the reflection probability for the first object (in violet), which has high values around the camera-facing side of the object.
+Also, note that the transmission probability is inversely proportional to occupancy.}
+        %   \label{fig:reflectiontransimission}
+        %   \vspace{-0.3cm}
+        % \end{figure}
         \begin{figure}
           \centering
-          \newcommand{\imagewidth}{\onecolwid}
-          \input{Source/scenelayoutoverlayCity0961}
-          \caption{A sample road scene with the unknowns of each car modeled as random variables. 
-          The relating energies are shown in Figure~\ref{fig:graphmodel}}
+          \includegraphics[width=0.9\columnwidth]{results/plotPtransmission_exact_vs_approx_pt_vis-small.png}\\
+          \includegraphics[trim=0.0 0 0.3in 0, clip, width=0.9\columnwidth]{results/plotPtransmission_exact_vs_approx_embedded_fonts.pdf}
+          \vspace{-0.3cm}
+          \caption{\small Comparisons between the approximate and exact formulations of $\Ptrans$.
+The drop in the approximate version is delayed because we assume drop at the object center rather than the camera-facing face of the object.}
+          \label{fig:compare:exact:approx:ptrans}
+          \vspace{-0.3cm}
         \end{figure}
+      \end{block}
 
+    \end{column}
+    \begin{column}{\sepwid}\end{column}			% empty spacer column
+    \begin{column}{2.0\onecolwid}
+      \begin{block}{Results}
+        \vspace*{-\baselineskip}
+        \begin{columns}[t]
+          \column{1.000\onecolwid}
+          \begin{table}
+            \begin{tabular}{lrrrr}
+              \toprule
+              Point tracks & Ours & BBox & BM & RAS\\
+              \midrule
+              Dynamic \& occluded         & \textbf{13.2} & 21.3 & 30.9 & 30.1 \\
+              Occluded		              & \textbf{15.7} & 19.8 & 39.5 & 37.8 \\
+              Dynamic		              & \textbf{6.6} & 11.4 & 15.3 & 17.7 \\
+              All		                  & \textbf{8.6} & 12.6 & 21.9 & 21.5 \\
+              \bottomrule
+            \end{tabular}
+            \caption{\small Mean association errors on different sets of input point tracks over all sequences.
+Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
+            \label{tab:meanAssoc}
+          \end{table}
+          \column{1.000\onecolwid}
+          \begin{table}
+            \begin{tabular}{lrr}
+              \toprule
+              Method & t & dim \\
+              \midrule
+              Point cloud fitting
+              & 6.87 & 4.02\\
+              Initialization by~\cite{Song_Chandraker_2014}
+              & 5.61 & 3.23\\
+              $\EnergyTrackNoOcc + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$ 
+              & 3.95  & 1.72\\        
+              $\EnergyTrackNoOcc + \EnergyBBox +\EnergySize+\EnergyDyn$        
+              & 4.81  & 2.16\\        
+              $\EnergyTrack + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$      
+              & 4.05  & {\bf 1.59}\\        
+              $\EnergyTrack + \EnergyBBox +\EnergySize+\EnergyDyn$             
+              & {\bf 3.24}  & 2.16\\
+              \bottomrule
+            \end{tabular}
+            \caption{\small Localization experiment results with different combinations of energies.
+We report translation error (t) and dimension error (dim) in meters per car.
+Yaw angles for static objects are not optimized by our model.
+These experiments use the set of occluded tracks to demonstrate the effect of our modeling.}
+            \label{tab:localizationExperiment}
+          \end{table}
+        \end{columns}
+      \end{block}
+
+      \begin{block}{Association error}
+        \begin{figure}[!!t]
+          \centering
+          \includegraphics[trim=1.0in 0.4in 1.0in 0.2in, clip, width=0.9\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
+          \vspace{-0.3cm}
+          \caption{\small Association errors on different sets of input point tracks.
+Numbers on the x-axis represent sequence numbers in the KITTI raw dataset.
+Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
+          \vspace{-0.3cm}
+          \label{fig:assoc-occ-results}
+        \end{figure}
+        \newlength{\tblimgwidth}
+        \setlength{\tblimgwidth}{0.080\textwidth}
+        \input{Source/figure_assoc_qualitative.tex}
+      \end{block}
+    \end{column}
+    \begin{column}{\sepwid}\end{column}			% empty spacer column
+    \begin{column}{\onecolwid}
+      \begin{block}{Object Point Association}
+        \begin{align}
+          \assocP = \Prefl\Ptrans,
+          \label{eq:defineassocP}
+        \end{align}
+        \begin{align}
+          P^{ij}_{\text{assoc}} = \frac{1}{Z''}\int_0^{\infty} \assocP \exp(-\Ereproj(\lambda))d\lambda,
+          \label{eq:prob-assoc}
+        \end{align}
+      \end{block}
+      \vspace{0.5in}
+      \begin{block}{3D Object Localization}
         \begin{figure}
@@
         \end{figure}
+        \begin{multline*}
+          -\log{P(\{ \bp^i(t) , \bomega^i(t) , \bB^i(t) \} | \{\bu_j(t)\} , \{\bb{i}\} )} = \\
+          -\tilde{Z} 
+          + \sum_{t=s_i}^{e_i} \lambda_{\text{track}}\EnergyTrack
+          + \\ 
+          \sum_{t=s_i}^{e_i} \sum_{i=1}^N  
+          \left(
+            \lambda_{\text{detect}}\EnergyBBox
+            + \lambda_{\text{dyn}}\EnergyDyn    
+            + \lambda_{\text{size}}\EnergySize
+          \right)
+          \enspace,
+        \end{multline*}
+        \begin{equation}
+          \Ereproj(\lambda) = \left\|\trackpj{t} - \projectionOf{\invProjectionOftm{\trackpj{t-1}, \lambda}}\right\|^2.
+          \label{eq:reprojerror}
+        \end{equation}
+        % \begin{figure}
+        %   \centering
+        %   \newcommand{\imagewidth}{\onecolwid}
+        %   \input{Source/scenelayoutoverlayCity0961}
+        %   \caption{A sample road scene with the unknowns of each car modeled as random variables. 
+        %   The relating energies are shown in Figure~\ref{fig:graphmodel}}
+        % \end{figure}
 
       \end{block}
-    \end{column}
-
-  \begin{column}{\sepwid}\end{column}			% empty spacer column
-
-    \begin{column}{\onecolwid}
-      %\begin{block}{}
-        \begin{figure}
-          \centering
-          \input{Source/graphicalmodelTP}
-          \caption{Graphical model showing the factorization of energies for a
-            single car. The six state variables of the car can be divided into
-            pose $\pos{i}{t}$ and dimensions $\dimsn{i}$. Different energies
-          depend only on either of those.}
-        \end{figure}
-      %\end{block}
-
-      \begin{block}{Energies}
-        \begin{table}[h]
-          \begin{tabular}{|l|l|}
-            \hline
-            Symbol & Meaning \\
-            \hline
-            $\pos{i}{t}$ & Position of $i$th car at time $t$\\
-            $\ori{i}{t}$ & Orientation of $i$th car at time $t$\\
-            $\dimsn{i}$ & 3D bounding box of the car (dimensions)\\
-            $\state{i}{t}$ & State of car $=\{\pos{i}{t}, \ori{i}{t}, \dimsn{i}\}$\\
-            $\egop$ & Position of camera at time $t$\\
-            $\egoo$ & Orientation of camera at time $t$\\
-            $\relp{i}{t}$ & Relative car pose w.r.t. camera \\
-            $\tracklets$ & 3D points tracked on car $i$ in its own frame\\
-            $\trackp{t}$ & Projection of $\tracklets$ in camera\\
-            $\projectionOf{.}$ & Projection function for pose $\relp{i}{t}$\\
-            $\bb{i}$ & 2D bounding box of the car in image\\
-            \hline
-          \end{tabular}
-        \end{table}
-
-        Assume conditional independence according to graphical model in
-        Figure~\ref{fig:graphmodel}, the negative log likelihood of required
-        random variables is given by
-        \begin{multline}
-          -\log{P(\{\state{i}{t}\} | \mathbb{E})} = 
-          Z' + 
-          \left(
-            \sum_{i=1}^N \sum_{t=s_i}^{e_i}
-            \WEnergy{lane} \right.\\
-            \left.
-            + \WEnergy{size}
-            + \WEnergy{dyn}
-            + \WEnergy{prior}
-            \vphantom{ \sum_{i=1}^N \sum_{t=s_i}^{e_i} }
-          \right)\\
-          +
-          \left(
-            \sum_{i,j:i\ne j}^N \sum_{t=s_i}^{e_i}  \WEnergyCol
-            + \WpEnergy{box}
-            + \WpEnergy{track}
-          \right)
-          \enspace.
-        \end{multline}
+      \vspace{0.5in}
+      \begin{block}{Conclusions and Future work}
+        \begin{itemize}
+          \item Presented physically interpretable unified occlusion modeling
+          \item The model generalizes to different applications: point association and 3D localization
+          \item Challenges include the slow inference on 3D localization
+        \end{itemize}
       \end{block}
-      \begin{block}{Point tracks with occlusion}
-        We model continuous point tracks energy with explicit occlusion reasoning as
-        the expected re-projection error over the association probability,
-
-        \begin{align}
-          \pEnergy{track}(.) =
-          %\sum_{t = s_i}^{e_i}
-          \sum_{j = 1}^{M}
-          \int_1^\infty \assocP\Ereproj(\lambda) d\lambda
-        \end{align}
-        where $\assocP$ is the association probability of
-        $j$\textsuperscript{th} point with $i$\textsuperscript{th} TP at depth $\lambda$
-        and $\Ereproj(\lambda)$ is the re-projection error given by
-        %
-        \begin{align}
-          \assocP &= \Prefl\Ptrans\\
-          \Ereproj(\lambda) &= \left\|\trackpj{t+1} - \projectionOft{\invProjectionOf{\trackpj{t}, \lambda}}\right\|^2 .
-          \label{eq:reprojerror}
-        \end{align}
-
+      \vspace{0.5in}
+      \begin{block}{Acknowledgements}
+        This work was part of V.~Dhiman's internship at NEC Labs America, in Cupertino. V.~Dhiman and J.~J.~Corso were also supported by NSF NRI IIS 1522904.
       \end{block}
-
-    \end{column}
-
-  \begin{column}{\sepwid}\end{column}			% empty spacer column
-
-    \begin{column}{\onecolwid}
-
-      \begin{block}{Object detection with occlusion}
-        To account for occlusion we weight the error along each side of the
-        bounding box with a visibility fraction that is proportional to
-        unoccluded area around that side:
-        \begin{align}
-          \pEnergy{occ}(.) =
-          \bm{\rho}^{ij}(t)^\top\left|\projectionOf{\dimsn{i}} - \bb{i}\right|
-          \enspace,
-          %\sum_{i=1}^N \sum_{t=s_i}^{e_i}
-          %\sum_kp_{ik}^{\text{track}}(\projectionOf{\dimsn{i}} - \bb{k})^\top \pmb{\rho}(i,j,t)
-        \end{align}
-        where $\bm{\rho}^{ij}(t)$ is the visibility fraction vector of the side
-        of the bounding box.
-
-      \end{block}
-
-      %\begin{block}{Object detection with continuous occlusion}
-      %  The detection scores GMM with occlusion is given by replacing the covariance
-      %  matrix
-      %  %
-      %  \begin{multline}
-      %    S'(\bb{i}) =\\
-      %    \sum_j A_j \exp(-(\bb{i}-\mu^{(d)}_j)^\top \Sigma'^{(d)-1}_j
-      %    (\bb{i}-\mu^{(d)}_j))
-      %  \end{multline}
-
-      %  The energy of detection scores is simply take to be the inverse of the detection score.
-      %  \begin{align}
-      %    \Energy{detect}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}
-      %  \end{align}
-      %\end{block}
-
-      \begin{block}{Other Energies}
-        \begin{description}
-          \item[Lane energy]
-            \begin{multline}
-              \label{eq:laneOrientationEnergy}
-              \Energy{lane} = 
-              \sum_{m \in M_{\text{close}}}
-              (1 - \ori{i}{t} \cdot \text{tan}(L_{m}(k), \pos{i}{t}) )
-              \LaneUncertainty{\pos{i}{t}}
-            \end{multline}
-            where $M_{\text{close}} = \{m : \text{dist}(L_{m}(k), \pos{i}{t}) < 50\} $ is
-            the set of nearby lanes and 
-            \begin{multline}
-              \LaneUncertainty{\pos{i}{t}} = 
-              \frac{1}{1 + \exp{(-q(w_{\text{road}} - \text{dist}(L_{m}(k), \pos{i}{t})))}}
-            \end{multline}
-            for some constant $w_{\text{road}}$ that represents the width of the road.
-
-          \item[Holonomic energy]
-            \begin{align}
-              \label{eq:totalPosTransitionEnergy}
-              \Energy{dyn} = 1 - \ori{i}{t-1} \cdot (\pos{i}{t} - \pos{i}{t-1})
-            \end{align}
-
-            %\begin{align}
-            %  \Energy{dyn-ori} &= \|\ori{i}{t} - \ori{i}{t-1}\|^2\\
-            %  \Energy{dyn-vel} &= \|(\pos{i}{t} - 2\pos{i}{t-1}) + \pos{i}{t-2}\|^2
-            %\end{align}
-
-            %\begin{align}
-            %  \WEnergy{dyn} &= \WEnergy{dyn-hol} + \WEnergy{dyn-ori} + \WEnergy{dyn-vel}
-            %\end{align}
-
-          %\item[Collision Energy]
-          %  \begin{align}
-          %    \label{eq:collisionEnergyHellingerDistance}
-          %    \EnergyCol = -\log\left(
-          %      A_{ij}
-          %      e^{-\frac{1}{8}
-          %        \left(\pos{i}{t} - \pos{j}{t}\right)^\top
-          %        P^{-1}
-          %        \left(\pos{i}{t} - \pos{j}{t}\right)
-          %      }
-          %    \right)
-          %  \end{align}
-
-          \item[Size Prior]
-            \begin{align}
-              \label{eq:totalSizeEnergy}
-              \Energy{size} &= (\dimsn{i} - \expDimsn)^\top\Sigma_{\expDimsn}^{-1}(\dimsn{i} -
-              \expDimsn)
-            \end{align}
-
-            where $\expDimsn$ is the mean TP dimensions and
-            $\Sigma_{\expDimsn}$ is the correspondence covariance matrix.
-
-        \end{description}
-      \end{block}
-      \begin{block}{Experiments and Results}
-        We perform experiments on KITTI \cite{geiger2013vision} dataset.
-        \includegraphics[width=\onecolwid]{results/Visualization/City/2011_09_26_drive_0009/single_window_contPtTracks_size_bboxOcc_yawTstepWiseInference/0000000061.png}\\
-        \includegraphics[width=\onecolwid]{results/Visualization/City/2011_09_26_drive_0009/single_window_lane_size_bboxOcc_yawTstepWiseInference/0000000061.png}\\
-
+      \begin{block}{References}
+        \bibliography{poster}
+        \bibliographystyle{ieee}
       \end{block}
     \end{column}
-
-  \begin{column}{\sepwid}\end{column}			% empty spacer column
-
-    \begin{column}{\onecolwid}
-      \begin{block}{}
-        \includegraphics[width=\onecolwid]{results/Visualization/City/2011_09_26_drive_0009/single_window_contPtTracks_size_bboxOcc_yawTstepWiseInference/0000000063.png}
-      \end{block}
-      \begin{table}
-        \begin{tabular}{|l|l|r|r|r|}
-          \hline
-          Energy & Metric & Occ & Unocc & Total\\
-          \hline
-contPtTracks+size+bboxOcc+yawT  &t  &2.636&4.499&3.351\\
-                                &yaw&0.130&0.201&0.159\\
-                                &dim&0.971&1.042&1.005\\
-          \hline
-contPtTracksNoOcc+size+bbox+yawT&t  &2.648&4.488&3.355\\
-                                &yaw&0.126&0.197&0.156\\
-                                &dim&0.964&1.051&1.006\\
-          \hline
-                  size+bbox+yawT&t  &2.616&4.501&3.349\\
-                                &yaw&0.125&0.231&0.166\\
-                                &dim&0.969&1.024&0.997\\
-          \hline
-               size+bboxOcc+yawT&t  &2.615&4.505&3.350\\
-                                &yaw&0.125&0.231&0.166\\
-                                &dim&0.969&1.008&0.991\\
-          \hline
-          (Init only)           &t  &2.583&4.486&3.321\\
-                                &yaw&0.113&0.181&0.143\\
-                                &dim&0.768&0.864&0.819\\
-          \hline
-
-        \end{tabular}
-      \end{table}
-      \begin{block}{Conclusion}
-        We use Probablistic graphical models to deduce consistent solutions from multiple sources. The results do not match our expectations and hence need further investigation.
-      \end{block}
-      \begin{block}{References}
-        {\small
-          \bibliographystyle{ieee}
-          \bibliography{continuousocclusion}
-        }
-      \end{block}
-    \end{column}
-
-  \begin{column}{\sepwid}\end{column}			% empty spacer column
-
   \end{columns}
 \end{frame}
+
 \end{document}
-
-\setbeamercolor{block alerted title}{fg=black,bg=norange}	% frame color
-\setbeamercolor{block alerted body}{fg=black,bg=white}		% body color
-\begin{alertblock}{Alert Block Colours}
-  You can similarly modify the colours for alert blocks (but try not to overdo it):\\
-  \begin{semiverbatim}
-  {\color{red}\\setbeamercolor}\{block title\}\newline \{fg=black,bg=norange\}
-  \end{semiverbatim}
-  \begin{semiverbatim}
-  {\color{red}\\setbeamercolor}\{block  body\}\newline \{fg=black,bg=white\}
-  \end{semiverbatim}
-\end{alertblock}

### 2016-06-22 CVPR/Source/figure_introduction.tex
Changes

@@
 \begin{center}
-  \includegraphics[width=\linewidth]{graphics/figure1.png}
+  \includegraphics[width=0.8\linewidth]{graphics/figure1.png}
 \end{center}
-\vspace{-0.6cm}
-\caption{\small We propose an occlusion model in 3D that is physically-inspired and continuous.
-Given object detection and SFM point tracks, our unified model probabilistically assigns point tracks to objects and reasons about object detection scores and bounding boxes.
-It uniformly handles static and dynamic objects, thus, outperforms motion segmentation for association problems.
-We also demonstrate occlusion-aware 3D localization in road scenes.}
-\label{fig:page1}

### 2016-06-22 poster/poster.tex
Changes

@@
 \usepackage{tikz}
+\usepackage{multirow}
+\usepackage{booktabs}
 
@@
 \newcommand{\Ptransmission}{P_{\textit{transmission}}}%
+\newcommand\RotText[1]{\rotatebox{90}{\parbox{1.7cm}{\centering#1}}}
+\newcommand{\bepsilon}{{\bm{\epsilon}}}
+\newcommand{\meandepth}[1]{\nu_#1}
+\newcommand{\bLambda}{\bm{\Lambda}}
 
@@
 \title{A Continuous Occlusion Model for Road Scene Understanding}
-\author{Vikas Dhiman$^\dagger$ \and Quoc-Huy Tran$^*$ \and Jason J Corso$^\dagger$ \and Manmohan Chandraker$^*$}
-\institute{$^\dagger$University of Michigan, Ann Arbor, MI \qquad $^*$NEC Labs, Cupertino, CA}
+\author{Vikas Dhiman$^\dagger$ \and Quoc-Huy Tran$^*$ \and Jason J. Corso$^\dagger$ \and Manmohan Chandraker$^*$}
+\institute{$^\dagger$University of Michigan, Ann Arbor, MI \qquad $^*$NEC Laboratories America, Cupertino, CA}
 
@@
         \end{figure}
+        \textbf{Contributions}:
+        \begin{itemize}
+		  \item A novel theoretical model for handling occlusions that is continuous and formulated in 3D.
+		  \item Unified occlusion handling for point tracks in SFM and bounding boxes and detection scores in object detection.
+		  \item Application of our proposed model to association of point tracks with both static and moving objects, improving over motion segmentation and occlusion-unaware baselines.
+		  \item Application of our unified formulation to 3D localization of traffic participants in road scenes.
+		\end{itemize}
       \end{block}
@@
       \begin{block}{Continuous Occlusion Model}
+		\textbf{Occupancy Model}: Traffic participants are represented as translucent 3D ellipsoids whose opacity is maximum at the center and falls off towards the edges.
         \begin{align}
-          f^i_{\text{occ}}(\bx) = \cL(\bx; \bp_i, \bSigma_i),
+          f^i_{\textit{occ}}(\bx) = \cL(\bx; \bp_i, \bSigma_i)
+        \end{align}
+		\textbf{Image Formation}: A point on an object is observed in the camera if: 1) the back-projected ray from the observed image pixel is transmitted through free space until it reaches the object, and 2) the ray encounters an opaque enough object surface and is reflected.
+        \begin{align}
+          P^{ij}_{\textit{observation}} = P^{ij}_{\textit{reflection}}P^{j}_{\textit{transmission}}
         \end{align}
         \begin{align}
-          P^{ij}_{\textit{observation}} = P^{ij}_{\textit{reflection}}P^{j}_{\textit{transmission}}.
-          \label{eq:imgform}
+          P^{ij}_{\textit{reflection}}(\lambda) = \frac{1}{Z}(\max \{0, \nabla {f^i_{occ}}(\bx_j)^\top \ray \})^2
         \end{align}
         \begin{align}
-          \Prefl = \frac{1}{Z}(\max \{0, \nabla {f^i_{occ}}(\bx_j)^\top \ray \})^2.
-          \label{eq:evalPrefl}
-        \end{align}
-
-        \begin{align}
-          P^j_{\textit{transmission}}(\lambda) &= \prod_{c}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda}\\
-          &\approx \prod_i (1 - \cL_u (\bu; \bmu_i, \bGamma_i) \cL_{\lambda}(\lambda; \meandepth{i})).
-          \label{eq:ptrans-integral}
+          P^{j}_{\textit{transmission}}(\lambda) &= \prod_{c}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda}\\
+          &\approx \prod_i (1 - \cL_u (\bu; \bmu_i, \bGamma_i) \cL_{\lambda}(\lambda; \meandepth{i}))
         \end{align}
@@
         \begin{figure}
+  		  \usetikzlibrary{calc}
   		  \centering
-          \includegraphics[width=0.9\columnwidth]{results/plotPtransmission_exact_vs_approx_pt_vis-small.png}\\
-          \includegraphics[trim=0.0 0 0.3in 0, clip, width=0.9\columnwidth]{results/plotPtransmission_exact_vs_approx_embedded_fonts.pdf}
-          \vspace{-0.3cm}
-          \caption{\small Comparisons between the approximate and exact formulations of $\Ptrans$.
-The drop in the approximate version is delayed because we assume drop at the object center rather than the camera-facing face of the object.}
-          \label{fig:compare:exact:approx:ptrans}
-          \vspace{-0.3cm}
+  		  \begin{tikzpicture}
+    			\input{Source/reflectiontransmissiongraph.tex}
+  		  \end{tikzpicture}  			
+  		\end{figure}
+        \begin{figure}
+          \centering
+          \includegraphics[width=0.5\columnwidth]{results/plotPtransmission_exact_vs_approx_pt_vis-small.png}
+          \includegraphics[trim=0 0 0.3 0, clip, width=0.5\columnwidth]{results/plotPtransmission_exact_vs_approx_embedded_fonts.pdf}          
         \end{figure}
@@
     \begin{column}{2.0\onecolwid}
-      \begin{block}{Results}
-        \vspace*{-\baselineskip}
+      \begin{block}{Experiments}
         \begin{columns}[t]
@@
 Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
-            \label{tab:meanAssoc}
           \end{table}
@@
 These experiments use the set of occluded tracks to demonstrate the effect of our modeling.}
-            \label{tab:localizationExperiment}
           \end{table}
         \end{columns}
-      \end{block}
 
-      \begin{block}{Association error}
         \begin{figure}[!!t]
@@
           \includegraphics[trim=1.0in 0.4in 1.0in 0.2in, clip, width=0.9\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
-          \vspace{-0.3cm}
 		  \caption{\small Association errors on different sets of input point tracks.
-Numbers on the x-axis represent sequence numbers in the KITTI raw dataset.
+Numbers on the horizontal axis represent sequence numbers in the KITTI raw dataset.
 Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
-          \vspace{-0.3cm}
-          \label{fig:assoc-occ-results}
         \end{figure}
@@
       \end{block}
+      \smallsize{
+      \textbf{Acknowledgements}
+      This work was part of V.~Dhiman's internship at NEC Laboratories America, Cupertino. V.~Dhiman and J.~J.~Corso were also supported by NSF NRI IIS 1522904.}
     \end{column}
@@
     \begin{column}{\onecolwid}
-      \begin{block}{Object Point Association}
+      \begin{block}{Unified Occlusion Models}
+
+		\begin{table}[!!t]
+		\centering\footnotesize
+		\begin{tabular}{|l|l|l|}
+		\hline
+		 & Symbol & Description \\
+		\hline
+		\hline
+		\multirow{2}{*}{\rotatebox{90}{Input}} & $\bu_j(t)$ & 2D feature track $j$ at time $t$ \\
+		 & $\textbf{d}^i(t)$ & 2D detection bounding box of object $O_i$ at time $t$ \\
+		\hline
+		\hline
+		\multirow{8}{*}{\RotText{Initialization with~\cite{Song_Chandraker_2014}}} & $\bp^c(t)$ & Position of camera at time $t$ \\
+		 & $\bomega^c(t)$ & Orientation of camera at time $t$ \\
+		 & $\bp_0^i(t)$ & Initial position of object $O_i$ at time $t$ \\
+		 & $\bomega_0^i(t)$ & Initial orientation of object $O_i$ at time $t$ \\
+		 & $\bB_0^i$ & Initial 3D dimensions of object $O_i$ \\
+		\hline
+		\hline
+		\multirow{4}{*}{\rotatebox{90}{Output}} & $P^{ij}_{\text{assoc}}$ & Probability of assigning feature track $j$ to object $O_i$ \\	
+		 & $\bp^i(t)$ & Position of object $O_i$ at time $t$ \\
+		 & $\bomega^i(t)$ & Orientation of object $O_i$ at time $t$ \\
+		 & $\bB^i$ & 3D dimensions of object $O_i$ \\
+		\hline
+		\end{tabular}
+		\end{table}
+
+      \textbf{Object-Point Association:}
         \begin{align}
-          \assocP = \Prefl\Ptrans,
-          \label{eq:defineassocP}
+          a^{ij}(\lambda) = P^{ij}_{\textit{reflection}}P^{j}_{\textit{transmission}}
         \end{align}
         \begin{align}
-          P^{ij}_{\text{assoc}} = \frac{1}{Z''}\int_0^{\infty} \assocP \exp(-\Ereproj(\lambda))d\lambda,
-          \label{eq:prob-assoc}
+          P^{ij}_{\textit{assoc}} = \frac{1}{Z}\int_0^{\infty} a^{ij}(\lambda) \exp(-E^{ij}_{\textit{reproj}}(\lambda))d\lambda
         \end{align}
-      \end{block}
-      \vspace{0.5in}
-      \begin{block}{3D Object Localization}
+
+	  \textbf{3D Object Localization:}
 		\begin{figure}
-          \centering
-          \input{Source/graphical_model_multiple}%
-          \caption{Graphical model showing the factor nodes among different
-            cars in the same frame. We assume occlusion relationships between
-            different cars are known and hence the occlusion modeling can be done
-            locally. In this example, the occlusion relationship affects the
-            following pair of cars 6-2, 2-5, 5-1. Cars 3 and 4 are not occluded
-            and hence affected by only unary terms within the frame. We also avoid 
-            collision modeling between unoccluded cars to encourage sparsity.
-          }
-          \label{fig:graphmodel}
+			\newcommand{\imagewidth}{18cm}
+		      \hspace{-0.8cm}
+		    \input{Source/scenelayoutoverlayCity0961} \\
+		      \hspace{-0.8cm}
+		    \input{Source/graphical_model_multiple}        
         \end{figure}	
         \begin{multline*}
-          -\log{P(\{ \bp^i(t) , \bomega^i(t) , \bB^i(t) \} | \{\bu_j(t)\} , \{\bb{i}\} )} = \\
+          -\log{P(\{ \bp^i(t) , \bomega^i(t) , \bB^i(t) \} | \{\bu_j(t)\} , \{\textbf{d}^i(t)\} )} = \\
           -\tilde{Z} 
           + \sum_{t=s_i}^{e_i} \lambda_{\text{track}}\EnergyTrack
-          + \\ 
+          +  
           \sum_{t=s_i}^{e_i} \sum_{i=1}^N  
@@
           \right)
-          \enspace,
+          \enspace
         \end{multline*}        
+        \begin{align}
+		  \pEnergy{track} = \sum_{i=1}^{N} \sum_{j = 1}^{M} \int_0^\infty a^{ij}(\lambda) E^{ij}_{\textit{reproj}}(\lambda) d\lambda
+		\end{align}        
         \begin{equation}
-          \Ereproj(\lambda) = \left\|\trackpj{t} - \projectionOf{\invProjectionOftm{\trackpj{t-1}, \lambda}}\right\|^2.
-          \label{eq:reprojerror}
+			S(\textbf{d}^i(t)) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \bLambda_k^{-1} \bepsilon_k^{i}(t) \right)
 		\end{equation}		
+		\begin{align}
+		  \Theta_{i}(\bu, \meandepth{i}) = 1 - \Ptransmission(\meandepth{i}, \bu)
+		\end{align}		
+		\begin{align}
+		  \Energy{detect} = \frac{1}{S'(\textbf{d}^i(t))}
+		\end{align}
+
         % \begin{figure}
@@
       \end{block}
-      \vspace{0.5in}
-      \begin{block}{Conclusions and Future work}
+      \begin{block}{Conclusion}
         \begin{itemize}
-          \item Presented physically interpretable unified occlusion modeling
-          \item The model generalizes to different applications: point association and 3D localization
-          \item Challenges include the slow inference on 3D localization
+          \item A physically interpretable, continuous model for occlusion reasoning in 3D.
+          \item Unified models for various applications of scene understanding such as object-point association and 3D localization.
+          \item Future work will explore speeding up graphical model inference and more detailed object representation.
         \end{itemize}
       \end{block}
-      \vspace{0.5in}
-      \begin{block}{Acknowledgements}
-        This work was part of V.~Dhiman's internship at NEC Labs America, in Cupertino. V.~Dhiman and J.~J.~Corso were also supported by NSF NRI IIS 1522904.
-      \end{block}
+
       \begin{block}{References}

### 2016-06-22 poster/poster.tex
Changes

@@
               & 5.61 & 3.23\\
-              $\EnergyTrackNoOcc + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$ 
+              $\EnergyTrackNoOcc + \Energy{detectNoOcc} +\EnergySize+\EnergyDyn$ 
               & 3.95  & 1.72\\        
-              $\EnergyTrackNoOcc + \EnergyBBox +\EnergySize+\EnergyDyn$        
+              $\EnergyTrackNoOcc + \Energy{detect} +\EnergySize+\EnergyDyn$        
               & 4.81  & 2.16\\        
-              $\EnergyTrack + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$      
+              $\EnergyTrack + \Energy{detectNoOcc} +\EnergySize+\EnergyDyn$      
               & 4.05  & {\bf 1.59}\\        
-              $\EnergyTrack + \EnergyBBox +\EnergySize+\EnergyDyn$             
+              $\EnergyTrack + \Energy{detectNoOcc} +\EnergySize+\EnergyDyn$             
               & {\bf 3.24}  & 2.16\\
@@
           \left(
-            \lambda_{\text{detect}}\EnergyBBox
+            \lambda_{\text{detect}}\Energy{detect}
             + \lambda_{\text{dyn}}\EnergyDyn    

### 2016-06-22 poster/poster.tex
Changes

@@
         \begin{align}
+	        \occftot = \sum_i \occf      
+        \end{align}
+        \begin{align}
           P^{j}_{\textit{transmission}}(\lambda) &= \prod_{c}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda}\\
@@
               & 4.05  & {\bf 1.59}\\        
-              $\EnergyTrack + \Energy{detectNoOcc} +\EnergySize+\EnergyDyn$             
+              $\EnergyTrack + \Energy{detect} +\EnergySize+\EnergyDyn$             
               & {\bf 3.24}  & 2.16\\
@@
         \begin{align}
-          P^{ij}_{\textit{assoc}} = \frac{1}{Z}\int_0^{\infty} a^{ij}(\lambda) \exp(-E^{ij}_{\textit{reproj}}(\lambda))d\lambda
+          P^{ij}_{\textit{assoc}} = \frac{1}{Z'}\int_0^{\infty} a^{ij}(\lambda) \exp(-E^{ij}_{\textit{reproj}}(\lambda))d\lambda
         \end{align}
@@
 			\newcommand{\imagewidth}{18cm}
-		      \hspace{-0.8cm}
 		    \input{Source/scenelayoutoverlayCity0961} \\
-		      \hspace{-0.8cm}
 		    \input{Source/graphical_model_multiple}        
@@
           -\log{P(\{ \bp^i(t) , \bomega^i(t) , \bB^i(t) \} | \{\bu_j(t)\} , \{\textbf{d}^i(t)\} )} = \\
-          -\tilde{Z} 
+          -Z'' 
           + \sum_{t=s_i}^{e_i} \lambda_{\text{track}}\EnergyTrack
@@
 		\begin{align}
-		  \Theta_{i}(\bu, \meandepth{i}) = 1 - \Ptransmission(\meandepth{i}, \bu)
+		  \Theta_{i}(\bu, \meandepth{i}) = 1 - \Ptransmission(\bu, \meandepth{i})
 		\end{align}		

### 2016-06-23 poster/poster.tex
Changes
Changed the order of figures and justified the itemized lists.

@@
 
+\usepackage{ragged2e}
 \usepackage{booktabs}
@@
         \begin{itemize}
-		  \item A novel theoretical model for handling occlusions that is continuous and formulated in 3D.
+          \item We propose a novel continuous occlusion model in 3D that is
+            physically interpretable.
           \item Unified occlusion handling for point tracks in SFM and bounding boxes and detection scores in object detection.
@@
               \toprule
-              Point tracks & Ours & BBox & BM & RAS\\
+              Point tracks & Ours & BBox & BM~\cite{Brox_Malik_2010} & RAS~\cite{Rao_etal_2010}\\
               \midrule
@@
         \end{columns}
-
+        \newlength{\tblimgwidth}
+        \setlength{\tblimgwidth}{0.080\textwidth}
+        \input{Source/figure_assoc_qualitative.tex}
         \begin{figure}[!!t]
@@
         \end{figure}
-        \newlength{\tblimgwidth}
-        \setlength{\tblimgwidth}{0.080\textwidth}
-        \input{Source/figure_assoc_qualitative.tex}                                
       \end{block}
@@
 		\begin{figure}
-			\newcommand{\imagewidth}{18cm}
+			\newcommand{\imagewidth}{17cm}
 		    \input{Source/scenelayoutoverlayCity0961} \\
@@
       \begin{block}{References}
+      \scriptsize{
         \bibliography{poster}
         \bibliographystyle{ieee}
+      }
       \end{block}

### 2017-11-15 CVPR16/Source/abstract.tex
Fit into the phdpropoal single column format.

@@
-\begin{abstract}
+%\begin{abstract}
+\section{Abstract}
 We present a physically interpretable, continuous three-dimensional (3D) model for handling occlusions with applications to road scene understanding.
@@
 As a notable application, we show how our continuous occlusion model benefits the task of 3D localization in autonomous driving.
-\end{abstract}
+%\end{abstract}

### 2017-11-15 CVPR16/Source/applications.tex
Fit into the phdpropoal single column format.

@@
 \newcommand\RotText[1]{\rotatebox{90}{\parbox{1.7cm}{\centering#1}}}
-\begin{table}[!!t]
+\begin{wraptable}[16]{r}{0.5\textwidth}
 \centering\footnotesize
@@
 \vspace{-0.5cm}
-\end{table}
+\end{wraptable}
 
@@
 
+\begin{wrapfigure}[22]{r}{0.5\textwidth}
+  \centering
+  \begin{tabular}{c}
+    \newcommand{\imagewidth}{7.5cm}
+      \hspace{-0.8cm}
+    \input{Source/scenelayoutoverlayCity0961} \\
+      \hspace{-0.8cm}
+    \input{Source/graphical_model_multiple}
+  \end{tabular}
+  \caption{\small (Top) A sample road scene with occlusions, where the unknowns of each object are modeled as random variables.
+(Bottom) The graphical model corresponding to the above frame.
+In particular, the numbered nodes denote the unknown state variables of each object (position, orientation, and dimensions), the shaded nodes are observed variables (detection bounding boxes and point tracks), and the colored squares represent various energies that capture object-object interactions.}
+  \label{fig:graphmodel}
+\end{wrapfigure}
+
 In this section, we exploit our continuous occlusion model for another application, namely, 3D object localization in road scenes, which further demonstrates its versatility.
@@
 
-\begin{figure}
-  \centering
-  \begin{tabular}{c}
-    \newcommand{\imagewidth}{7.5cm}
-      \hspace{-0.8cm}
-    \input{Source/scenelayoutoverlayCity0961} \\
-      \hspace{-0.8cm}
-    \input{Source/graphical_model_multiple}
-  \end{tabular}
-  \caption{\small (Top) A sample road scene with occlusions, where the unknowns of each object are modeled as random variables.
-(Bottom) The graphical model corresponding to the above frame.
-In particular, the numbered nodes denote the unknown state variables of each object (position, orientation, and dimensions), the shaded nodes are observed variables (detection bounding boxes and point tracks), and the colored squares represent various energies that capture object-object interactions.}
-  \label{fig:graphmodel}
-\end{figure}
-
 \vspace{-0.3cm}
@@
 Then, we model the continuous point track energy with explicit occlusion reasoning as the expected reprojection error over the association probability
-\begin{multline}
+\begin{align}
   %\!\!\!\! \Energy{track}(\relp{i}{t}, \relp{i}{t-1}, \dimsn{i}, \{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i ) 
@@
   \pEnergy{track}(\{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i )
-  \\
+  %\\
     = \sum_{i=1}^{N} 
@@
     \int_0^\infty \assocP\Ereproj(\lambda) d\lambda,
-\end{multline}
+\end{align}
 where $N$ and $M$ are, respectively, the number of objects and points and $\assocP$ is the association probability of point $\trackp{t}$ with object $O_i$ at depth $\lambda$, given by \eqref{eq:defineassocP}.

### 2017-11-15 CVPR16/Source/occlusion.tex
Fit into the phdpropoal single column format.

@@
 
-\begin{figure}
+\begin{wrapfigure}[15]{r}{0.5\textwidth}
   \usetikzlibrary{calc}
@@
   \vspace{-0.3cm}
-\end{figure}
+\end{wrapfigure}
 
@@
 \centering
-  \includegraphics[width=0.9\columnwidth]{results/plotPtransmission_exact_vs_approx_pt_vis-small.png}\\
-  \includegraphics[trim=0.0 0 0.3in 0, clip, width=0.9\columnwidth]{results/plotPtransmission_exact_vs_approx_embedded_fonts.pdf}
+  \includegraphics[width=0.45\textwidth]{results/plotPtransmission_exact_vs_approx_pt_vis-small.png}%\\
+  \includegraphics[trim=0.0 0 0.3in 0, clip, width=0.45\textwidth]{results/plotPtransmission_exact_vs_approx_embedded_fonts.pdf}
   \vspace{-0.3cm}

### 2017-12-01 CVPR16/Source/applications.tex
Changing noration to match rest of the document.

@@
 \centering\footnotesize
-\begin{tabular}{|l|l|l|}
+\begin{tabular}{|l|l|p{0.32\textwidth}|}
 \hline
@@
 \hline
-\multirow{2}{*}{\rotatebox{90}{Input}} & $\bu_j(t)$ & 2D feature track $j$ at time $t$ \\
- & $\bb{i}$ & 2D detection bounding box of object $O_i$ at time $t$ \\
+\multirow{2}{*}{\rotatebox{90}{Input}} & $\impt_j(t)$ & 2D feature track $j$ at time $t$ \\
+ & $\bb{i}$ & 2D detection bounding box of object $\Obj_i$ at time $t$ \\
 \hline
 \hline
-\multirow{5}{*}{\RotText{Initialization with~\cite{Song_Chandraker_2014}}} & $\bp^c(t)$ & Position of camera at time $t$ \\
- & $\bomega^c(t)$ & Orientation of camera at time $t$ \\
- & $\bp_0^i(t)$ & Initial position of object $O_i$ at time $t$ \\
- & $\bomega_0^i(t)$ & Initial orientation of object $O_i$ at time $t$ \\
- & $\bB_0^i$ & Initial 3D dimensions of object $O_i$ \\
+\multirow{5}{*}{\RotText{Initialization with~\cite{Song_Chandraker_2014}}} & $\camO(t)$ & Position of camera at time $t$ \\
+ & $\camR(t)$ & Orientation of camera at time $t$ \\
+ & $\ObjMu_0^i(t)$ & Initial position of object $\Obj_i$ at time $t$ \\
+ & $\ObjR_0^i(t)$ & Initial orientation of object $\Obj_i$ at time $t$ \\
+ & $\BB_0^i$ & Initial 3D dimensions of object $\Obj_i$ \\
 \hline
 \hline
-\multirow{4}{*}{\rotatebox{90}{Output}} & $P^{ij}_{\text{assoc}}$ & Probability of assigning feature track $j$ to object $O_i$ \\	
- & $\bp^i(t)$ & Position of object $O_i$ at time $t$ \\
- & $\bomega^i(t)$ & Orientation of object $O_i$ at time $t$ \\
- & $\bB^i$ & 3D dimensions of object $O_i$ \\
+\multirow{4}{*}{\rotatebox{90}{Output}} & $\PassocR$ & Probability of assigning feature track $j$ to object $\Obj_i$ \\	
+ & $\ObjMu^i(t)$ & Position of object $\Obj_i$ at time $t$ \\
+ & $\ObjR^i(t)$ & Orientation of object $\Obj_i$ at time $t$ \\
+ & $\BB^i$ & 3D dimensions of object $\Obj_i$ \\
 \hline
@@
 
-Given 2D image points $\{\bu_j\}$ that are tracked between consecutive frames and a set of objects $\{O_i\}$ appearing in the frames, we aim to associate $\bu_j$ with $O_i$.
-Based on our continuous occlusion model in Section~\ref{sec:setup}, the association probability $\assocP$ between point track $\bu_j$ and object $O_i$ at depth $\lambda$ can be defined as
+Given 2D image points $\{\impt_j\}$ that are tracked between consecutive frames and a set of objects $\{\Obj_i\}$ appearing in the frames, we aim to associate $\impt_j$ with $\Obj_i$.
+Based on our continuous occlusion model in Section~\ref{sec:setup}, the association probability $\assocP$ between point track $\impt_j$ and object $\Obj_i$ at depth $\lambda$ can be defined as
 \begin{align}
@@
 
-Rather, to compute the association probability between point track $\bu_j$ and object $O_i$, we should also use the reprojection error.
-When the association of point track $\bu_j$ and object $O_i$ is correct and the point of reflection is at depth $\lambda$, the corresponding reprojection error $\Ereproj(\lambda)$ must be zero, otherwise the error becomes a measure of distance from the true solution.
+Rather, to compute the association probability between point track $\impt_j$ and object $\Obj_i$, we should also use the reprojection error.
+When the association of point track $\impt_j$ and object $\Obj_i$ is correct and the point of reflection is at depth $\lambda$, the corresponding reprojection error $\Ereproj(\lambda)$ must be zero, otherwise the error becomes a measure of distance from the true solution.
 The error $\Ereproj(\lambda)$ can be used for associating point tracks and objects by converting it to the probability domain as
@@
 \begin{align}
-  P^{ij}_{\text{assoc}} = \frac{1}{Z''}\int_0^{\infty} \assocP \exp(-\Ereproj(\lambda))d\lambda,
+  \PassocR = \frac{1}{Z''}\int_c^{\infty} \assocP \exp(-\Ereproj(\lambda))d\lambda,
   \label{eq:prob-assoc}
@@
 
-Once we have computed the association probability $P^{ij}_{\text{assoc}}$ for every pair of point tracks and objects, we can assign each point track to the object with the highest association probability.
+\begin{wrapfigure}[18]{r}{0.5\textwidth}
+  \centering\scriptsize
+  \begin{tabular}{c}
+    \newcommand{\imagewidth}{7.5cm}
+      \hspace{-0.8cm}
+    \input{Source/scenelayoutoverlayCity0961} \\
+      \hspace{-0.8cm}
+    \input{Source/graphical_model_multiple}
+  \end{tabular}
+  \caption{(Top) A sample road scene with occlusions, where the unknowns of each object are modeled as random variables.
+(Bottom) The graphical model corresponding to the above frame.
+In particular, the numbered nodes denote the unknown state variables of each object (position, orientation, and dimensions), the shaded nodes are observed variables (detection bounding boxes and point tracks), and the colored squares represent various energies that capture object-object interactions.}
+  \label{fig:graphmodel}
+\end{wrapfigure}
+%
+
+Once we have computed the association probability $\PassocR$ for every pair of point tracks and objects, we can assign each point track to the object with the highest association probability.
 The point tracks having very small association probabilities are assigned to the background.
@@
 
-\begin{wrapfigure}[22]{r}{0.5\textwidth}
-  \centering
-  \begin{tabular}{c}
-    \newcommand{\imagewidth}{7.5cm}
-      \hspace{-0.8cm}
-    \input{Source/scenelayoutoverlayCity0961} \\
-      \hspace{-0.8cm}
-    \input{Source/graphical_model_multiple}
-  \end{tabular}
-  \caption{\small (Top) A sample road scene with occlusions, where the unknowns of each object are modeled as random variables.
-(Bottom) The graphical model corresponding to the above frame.
-In particular, the numbered nodes denote the unknown state variables of each object (position, orientation, and dimensions), the shaded nodes are observed variables (detection bounding boxes and point tracks), and the colored squares represent various energies that capture object-object interactions.}
-  \label{fig:graphmodel}
-\end{wrapfigure}
-
 In this section, we exploit our continuous occlusion model for another application, namely, 3D object localization in road scenes, which further demonstrates its versatility.
-Given a set of 2D tracked feature points $\{\bu_j(t)\}$ and 2D detection bounding boxes $\{\bb{i}\}$ at frame $t$, the goal is to localize 3D traffic participants.
-In particular, for each traffic participant, we wish to estimate its position $\bp^i(t)$ and orientation $\bomega^i(t)$ on the ground plane and its 3D dimensions $\bB^i(t)$.
+Given a set of 2D tracked feature points $\{\impt_j(t)\}$ and 2D detection bounding boxes $\{\bb{i}\}$ at frame $t$, the goal is to localize 3D traffic participants.
+In particular, for each traffic participant, we wish to estimate its position $\ObjMu^i(t)$ and orientation $\ObjR^i(t)$ on the ground plane and its 3D dimensions $\BB^i(t)$.
 Please refer to Table~\ref{tab:notations} for a summary of inputs and outputs.
@@
 \begin{multline*}
-  -\log{P(\{ \bp^i(t) , \bomega^i(t) , \bB^i(t) \} | \{\bu_j(t)\} , \{\bb{i}\} )} = \\
+  -\log{P(\{ \ObjMu^i(t) , \ObjR^i(t) , \BB^i(t) \} | \{\impt_j(t)\} , \{\bb{i}\} )} = \\
   -\tilde{Z} 
@@
 where $\pEnergy{track}$ and $\Energy{detect}$ reason about image observations such as point tracks and bounding boxes, while $\Energy{dyn}$  and $\Energy{size}$ impose smoothness constraints and size priors respectively.
-Here, $\lambda_{\text{track}}$, $\lambda_{\text{detect}}$, $\lambda_{\text{dyn}}$, $\lambda_{\text{size}}$ are energy weights, $N$ is the number of objects in the sequence, $s_i$ and $t_i$ are respectively the starting and ending frames of object $O_i$, and $\tilde{Z}$ is the normalization coefficient.
+Here, $\lambda_{\text{track}}$, $\lambda_{\text{detect}}$, $\lambda_{\text{dyn}}$, $\lambda_{\text{size}}$ are energy weights, $N$ is the number of objects in the sequence, $s_i$ and $t_i$ are respectively the starting and ending frames of object $\Obj_i$, and $\tilde{Z}$ is the normalization coefficient.
 Next, we present our unified continuous occlusion modeling for both point track and bounding box energies.
@@
 %\label{sec:totalContPtTracksEnergy}
-Let $\relp{i}{t}$ be the pose of object $O_i$ at time $t$ in world coordinates, which is computed using the camera pose at time $t$ and the relative pose of object $O_i$ with respect to the camera at time $t$.
+Let $\relp{i}{t}$ be the pose of object $\Obj_i$ at time $t$ in world coordinates, which is computed using the camera pose at time $t$ and the relative pose of object $\Obj_i$ with respect to the camera at time $t$.
 We denote $\projectionOf{.}$ and $\invProjectionOftm{.}$ as the forward and inverse projection functions that project a 3D point to the 2D image and vice versa.
@@
 
-For an object $O_i$, let $\{ \Omega (t) \}_i$ be the poses of all occluding objects at time $t$ (inclusive of object $O_i$) and $ \{ \bB \}_i$ be their corresponding 3D dimensions.
+For an object $\Obj_i$, let $\{ \posealt (t) \}_i$ be the poses of all occluding objects at time $t$ (inclusive of object $\Obj_i$) and $ \{ \BB \}_i$ be their corresponding 3D dimensions.
 Then, we model the continuous point track energy with explicit occlusion reasoning as the expected reprojection error over the association probability
@@
   %\Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = 
-  \pEnergy{track}(\{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i )
+  \pEnergy{track}(\{ \posealt (t) \}_i, \{ \posealt (t-1) \}_i, \{ \BB \}_i )
   %\\
@@
 \end{align}
-where $N$ and $M$ are, respectively, the number of objects and points and $\assocP$ is the association probability of point $\trackp{t}$ with object $O_i$ at depth $\lambda$, given by \eqref{eq:defineassocP}.
+where $N$ and $M$ are, respectively, the number of objects and points and $\assocP$ is the association probability of point $\trackp{t}$ with object $\Obj_i$ at depth $\lambda$, given by \eqref{eq:defineassocP}.
 

### 2017-12-01 CVPR16/Source/contBBoxModel.tex
Fit into the phdpropoal single column format.
Changing noration to match rest of the document.

@@
 \begin{equation}
-S(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \bLambda_k^{-1} \bepsilon_k^{i}(t) \right),
+S(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \bbS_k^{-1} \bepsilon_k^{i}(t) \right),
 \label{eq:GMMscores}
 \end{equation}
-where $A_k$ is an amplitude and $\bepsilon_k^{i}(t) = \bb{i}-\bmu_k$, with $\bmu_k$ the mean and $\bLambda_k$ the covariance.
+where $A_k$ is an amplitude and $\bepsilon_k^{i}(t) = \bb{i}-\bbMu_k$, with $\bbMu_k$ the mean and $\bbS_k$ the covariance.
 %% %
@@
 We use a non-linear solver to minimize the above, with initialization from non-maximal suppressed outputs.
-The optimization is constrained by the symmetry and positive definiteness of $\bLambda_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
+The optimization is constrained by the symmetry and positive definiteness of $\bbS_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
 %Here $\mu^{(d)}_j$ is one of the $k$ modes as a 4D vector representing a single bounding box as $[\minx, \miny, \maxx, \maxy]^\top$.
@@
 \paragraph{Detection scores with occlusion reasoning} 
-\def\u{\mathbf{u}}
 With our model of $\Ptrans$ described in Section \ref{sec:ptransmission}, we 
-compute the probability of a point $\u$ in the image to be occluded, assuming
-the point is on object $O_i$ with mean depth $\meandepth{i}$, as
+compute the probability of a point $\impt$ in the image to be occluded, assuming
+the point is on object $\Obj_i$ with mean depth $\meandepth{i}$, as
 \begin{align}
-  \Theta_{i}(\u, \meandepth{i}) = 1 - \Ptransmission(\meandepth{i}, \u).
+  \Theta_{i}(\impt, \meandepth{i}) = 1 - \PtransR(\meandepth{i}, \impt).
 \end{align}
@@
 To re-model detection scores scaled by continuous occlusion, we sample
-$\Theta_{i}(\mathbf{u}, \meandepth{i})$ at the hypothesized detection boundaries from
+$\Theta_{i}(\impt, \meandepth{i})$ at the hypothesized detection boundaries from
 the Gaussian mixture model (GMM) $S(.)$ in \eqref{eq:GMMscores} and augment the detection boundary covariance matrix by
@@
 \meandepth{i})$. The new covariance matrix for the detection scores is given by 
-  $\bLambda'_k = \mathcal{P}_{i} + \bLambda_k$ for all $k$.
+  $\bbS'_k = \mathcal{P}_{i} + \bbS_k$ for all $k$.
 The detection score GMM $S'(.)$ with explicit occlusion reasoning is given by replacing the covariance
@@
 %
-\begin{multline}
-S'(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \bLambda_k^{'-1} \bepsilon_k^{i}(t) \right).
-\end{multline}
+\begin{align}
+S'(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \bbS_k^{'-1} \bepsilon_k^{i}(t) \right).
+\end{align}
 

### 2017-12-01 CVPR16/Source/experiments2.tex
Created presentation and poster for mid west vision conference.
Fit into the phdpropoal single column format.
Changing noration to match rest of the document.

@@
+\begin{wraptable}[8]{r}{0.5\textwidth}\scriptsize\centering
+\begin{tabular}{lrrrr}
+  \toprule
+  Point tracks & Ours & BBox & BM & RAS\\
+  \midrule
+  Dynamic \& occluded         & \textbf{13.2} & 21.3 & 30.9 & 30.1 \\
+  Occluded		              & \textbf{15.7} & 19.8 & 39.5 & 37.8 \\
+  Dynamic		              & \textbf{6.6} & 11.4 & 15.3 & 17.7 \\
+  All		                  & \textbf{8.6} & 12.6 & 21.9 & 21.5 \\
+  \bottomrule
+\end{tabular}
+\caption{Mean association errors on different sets of input point tracks over all sequences.
+Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
+\label{tab:meanAssoc}
+\end{wraptable}
+%
 \section{Experiments}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \subsection{Association Experiments}
 %\vspace{-0.2cm}
+
 \paragraph{Setup}
@@
 \centering
-%\includegraphics[trim=1.0in 0.4in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
-\includegraphics[width=0.95\textwidth]{graphics/figure5.png}
+\includegraphics[trim=1.0in 0.4in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
+%\includegraphics[width=0.95\textwidth]{graphics/figure5.png}
   \vspace{-0.3cm}
-  \caption{\small Association errors on different sets of input point tracks.
+  \caption{Association errors on different sets of input point tracks.
 Numbers on the x-axis represent sequence numbers in the KITTI raw dataset.
@@
 \end{figure*}
-
-\begin{table}
-\begin{tabular}{lrrrr}
-  \toprule
-  Point tracks & Ours & BBox & BM & RAS\\
-  \midrule
-  Dynamic \& occluded         & \textbf{13.2} & 21.3 & 30.9 & 30.1 \\
-  Occluded		              & \textbf{15.7} & 19.8 & 39.5 & 37.8 \\
-  Dynamic		              & \textbf{6.6} & 11.4 & 15.3 & 17.7 \\
-  All		                  & \textbf{8.6} & 12.6 & 21.9 & 21.5 \\
-  \bottomrule
-\end{tabular}
-\caption{\small Mean association errors on different sets of input point tracks over all sequences.
-Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
-\label{tab:meanAssoc}
-\end{table}
 
@@
   \vspace{-0.3cm}
-  \caption{\small Qualitative results of the association experiment. The ``Associations" columns
+  \caption{Qualitative results of the association experiment. The ``Associations" columns
   show the point track assignments to appropriate objects. Each color represents
@@
 RAS and BM often have the highest errors in Figure~\ref{fig:assoc-occ-results}, thus, the highest mean errors on all sets of input point tracks in Table~\ref{tab:meanAssoc}.
+
+\begin{wraptable}[11]{r}{0.5\textwidth}\scriptsize\centering
+  \begin{tabular}{lrr}
+    \toprule
+    Method & t & dim \\
+    \midrule
+    Point cloud fitting
+    & 6.87 & 4.02\\
+    Initialization by~\cite{Song_Chandraker_2014}
+    & 5.61 & 3.23\\
+    $\EnergyTrackNoOcc + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$ 
+    & 3.95  & 1.72\\        
+    $\EnergyTrackNoOcc + \EnergyBBox +\EnergySize+\EnergyDyn$        
+    & 4.81  & 2.16\\        
+    $\EnergyTrack + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$      
+    & 4.05  & {\bf 1.59}\\        
+    $\EnergyTrack + \EnergyBBox +\EnergySize+\EnergyDyn$             
+    & {\bf 3.24}  & 2.16\\
+    \bottomrule
+  \end{tabular}
+  \caption{Localization experiment results with different combinations of energies.
+We report translation error (t) and dimension error (dim) in meters per car.
+Yaw angles for static objects are not optimized by our model.
+These experiments use the set of occluded tracks to demonstrate the effect of our modeling.}
+  \label{tab:localizationExperiment}
+\end{wraptable}
 
@@
 
-\begin{table}
-  \begin{tabular}{lrr}
-    \toprule
-    Method & t & dim \\
-    \midrule
-    Point cloud fitting
-    & 6.87 & 4.02\\
-    Initialization by~\cite{Song_Chandraker_2014}
-    & 5.61 & 3.23\\
-    $\EnergyTrackNoOcc + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$ 
-    & 3.95  & 1.72\\        
-    $\EnergyTrackNoOcc + \EnergyBBox +\EnergySize+\EnergyDyn$        
-    & 4.81  & 2.16\\        
-    $\EnergyTrack + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$      
-    & 4.05  & {\bf 1.59}\\        
-    $\EnergyTrack + \EnergyBBox +\EnergySize+\EnergyDyn$             
-    & {\bf 3.24}  & 2.16\\
-    \bottomrule
-  \end{tabular}
-  \caption{\small Localization experiment results with different combinations of energies.
-We report translation error (t) and dimension error (dim) in meters per car.
-Yaw angles for static objects are not optimized by our model.
-These experiments use the set of occluded tracks to demonstrate the effect of our modeling.}
-  \label{tab:localizationExperiment}
-\end{table}
-
 \subsection{Localization Experiments}
@@
 The energy $\EnergyTrackNoOcc$ represents the point track energy without accounting for occlusions, that is, we model $\EnergyTrack$ in the absence of $a^{ij} (\lambda)$.
-Similarly, $\EnergyBBoxNoOcc$ is the bounding box energy without the modification of $\bLambda_k$ that accounts for occlusion.
+Similarly, $\EnergyBBoxNoOcc$ is the bounding box energy without the modification of $\bbS_k$ that accounts for occlusion.
 We use $\lambda_{\text{track}} = 1$, $\lambda_{\text{detect}} = 1$, $\lambda_{\text{dyn}} = 10$, $\lambda_{\text{size}} = 7$.

### 2017-12-01 CVPR16/Source/occlusion.tex
Changing noration to match rest of the document.

@@
 
-\begin{wrapfigure}[15]{r}{0.5\textwidth}
+%
+\begin{wrapfigure}[8]{r}{0.5\textwidth}
   \usetikzlibrary{calc}
@@
   \begin{tikzpicture}
+    \scriptsize
     \input{Source/reflectiontransmissiongraph.tex}
@@
   \vspace{-0.3cm}
-  \caption{\small We represent objects as translucent ellipsoids, which leads to the formulation of transmission and reflection probabilities.
+  \caption{We represent objects as translucent ellipsoids, which leads to the formulation of transmission and reflection probabilities.
 This figure shows the reflection probability for the first object (in violet), which has high values around the camera-facing side of the object.
@@
   \vspace{-0.3cm}
-\end{wrapfigure}
-
+\end{wrapfigure}%
+%
 \vspace{-0.3cm}
@@
 Based on this intuition, we model objects as translucent 3D ellipsoids whose opacity is maximum at the center and falls off towards the edges.
-In particular, we model the occupancy at 3D location $\bx$ corresponding to an object $O_i$ centered at $\bp_i$ as
+In particular, we model the occupancy at 3D location $\ptD$ corresponding to an object $\Obj_i$ centered at $\ObjMu_i$ as
 \begin{align}
-  f^i_{\text{occ}}(\bx) = \cL(\bx; \bp_i, \bSigma_i),
+  \OccF(\ptD) = \Logst(\ptD; \ObjMu_i, \ObjSigma_i),
 \end{align}
-where $\cL(\cdot)$ is the logistic function given by
+where $\Logst(\cdot)$ is the logistic function given by
 \begin{align}
-  \cL(\bx; \bp, \bSigma) = \frac{1}{1 + e^{-k(1 - d(\mathbf{x},\bp))}},
+  \Logst(\ptD; \ObjMu, \ObjSigma) = \frac{1}{1 + e^{-k(1 - \mahaF(\ptD,\ObjMu))}},
 \end{align}
-with $d(\bx, \bp) = (\bx-\bp)^\top\bSigma^{-1}(\bx-\bp)$ being the Mahalanobis distance.
-We set $k = 10\ln({49})$ as the value that allows the logistic function $\cL$ to drop to $0.98$ at a distance $d = 0.9$ from the object center.
-The spread of the ellipsoid, determined by $\bSigma_i$, depends on the dimensions of the object.
-Please refer to the supplementary material for the computation of $\bSigma_i$ from object dimensions.
+with $\mahaF(\ptD, \ObjMu) = (\ptD-\ObjMu)^\top\ObjSigma^{-1}(\ptD-\ObjMu)$ being the Mahalanobis distance.
+We set $k = 10\ln({49})$ as the value that allows the logistic function $\Logst$ to drop to $0.98$ at a distance $d = 0.9$ from the object center.
+The spread of the ellipsoid, determined by $\ObjSigma_i$, depends on the dimensions of the object.
+Please refer to the supplementary material for the computation of $\ObjSigma_i$ from object dimensions.
 
@@
 Second, the ray encounters an opaque enough object surface and is reflected.
-More formally, the probability of observation of a point $\bx_j$ on object $O_i$ is given by
+More formally, the probability of observation of a point $\ptD_j$ on object $\Obj_i$ is given by
 \begin{align}
-P^{ij}_{\textit{observation}} = P^{ij}_{\textit{reflection}}P^{j}_{\textit{transmission}}.
+\Pobs = \PreflR \PtransR
 \label{eq:imgform}
@@
 \paragraph{Reflection probability}
-Consider a 3D point $\bx_j$ observed in the image at pixel $\bu_j$.
-Let $\bK$ be the intrinsic calibration matrix for the camera and $\ray = \displaystyle\frac{\bK^{-1}\bu_j}{\lVert \bK^{-1}\bu_j \rVert}$ be the unit vector along the backprojected ray from the camera center passing through $\bu_j$.
-Then, the probability of reflection at depth $\lambda$ along the ray $\ray$, by an object $O_i$, is determined by the gradient of the object's occupancy function $f_{occ}^i$ as
+Consider a 3D point $\ptD_j$ observed in the image at pixel $\impt_j$.
+Let $\intm$ be the intrinsic calibration matrix for the camera and $\ray = \displaystyle\frac{\intm^{-1}\impt_j}{\lVert \intm^{-1}\impt_j \rVert}$ be the unit vector along the backprojected ray from the camera center passing through $\impt_j$.
+Then, the probability of reflection at depth $\dist$ along the ray $\ray$, by an object $\Obj_i$, is determined by the gradient of the object's occupancy function $\OccF^i$ as
 \begin{align}
-   \Prefl = \frac{1}{Z}(\max \{0, \nabla {f^i_{occ}}(\bx_j)^\top \ray \})^2.
+   \Prefl = \frac{1}{Z}(\max \{0, \gOccFi(\ptD_j)^\top \ray \})^2.
 \label{eq:evalPrefl}
 \end{align}
-The gradient $\nabla {f^i_{occ}}(\bx_j)$ encourages the reflection probability to be high near object boundaries, the $\max$ ensures that negative probability due to the gradient in the direction opposite to the ray is clipped off and squaring allows the function to be smooth near zero.
+The gradient $\gOccFi(\ptD_j)$ encourages the reflection probability to be high near object boundaries, the $\max$ ensures that negative probability due to the gradient in the direction opposite to the ray is clipped off and squaring allows the function to be smooth near zero.
 Here, $Z$ denotes the normalization factor.
-We note that in the extreme case of an object being fully opaque (that is, $\nabla {f^i_{occ}(\bx_j)} \in \{0,1\}$), the above model reverts to a (squared) Lambertian reflection.
+We note that in the extreme case of an object being fully opaque (that is, $\gOccFi(\ptD_j) \in \{0,1\}$), the above model reverts to a (squared) Lambertian reflection.
 Figure~\ref{fig:reflectiontransimission} shows an example of the reflection probability.
@@
 %
-In our formulation of scene occupancy, both opacity and density at a scene point $\bx_j$ are encapsulated within the total occupancy function summed over all objects, $\occftot = \sum_i \occf$.
+In our formulation of scene occupancy, both opacity and density at a scene point $\ptD_j$ are encapsulated within the total occupancy function summed over all objects, $\occftot = \sum_i \occf$.
 Further, the domain of our occupancy function $\occftot$ is $[0, 1]$ instead of $[0, \infty)$ for opacity $\beta$.
-Thus, we replace $e^{-\beta\rho}$ by the transparency function $1 - \occftot$ and consequently, the transmission probability over a small distance $d\lambda$ is given by
+Thus, we replace $e^{-\beta\rho}$ by the transparency function $1 - \occftot$ and consequently, the transmission probability over a small distance $d\dist$ is given by
 %
 \begin{align}
-  \!\!\!\! P^j_{\textit{transmission}}(\lambda + d\lambda) = P^j_{\textit{transmission}}(\lambda) (1-\occftot)^{d\lambda}.
+  \!\!\!\! P^j_{\textit{transmission}}(\dist + d\dist) = P^j_{\textit{transmission}}(\dist) (1-\occftot)^{d\dist}.
 \end{align}
 %
-Thus, for an image point $\bu_j$ to correspond to a 3D point $\bx_j$ at depth $\lambda$ along the backprojected ray $\ray$, the ray must be transmitted through space with the probability
+Thus, for an image point $\impt_j$ to correspond to a 3D point $\ptD_j$ at depth $\dist$ along the backprojected ray $\ray$, the ray must be transmitted through space with the probability
 \begin{align}
-P^j_{\textit{transmission}}(\lambda) = \prod_{c}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda}.
+\PtransR(\dist) = \prod_{c}^{\dist} (1 - \occft{\dist \ray})^{d\dist}.
 \label{eq:ptrans-integral}
 \end{align}
-Here, $\prod_{c}^{\lambda}$ represents a \emph{product integral} from $c$ to $\lambda$, where $c$ is the position of camera screen, considered here to be equivalent to the focal length of the camera .\footnote{A product integral is a simple integral in the log domain
+Here, $\prod_{c}^{\dist}$ represents a \emph{product integral} from $c$ to $\dist$, where $c$ is the position of camera screen, considered here to be equivalent to the focal length of the camera .\footnote{A product integral is a simple integral in the log domain
 \vspace{-0.2cm}
 \begin{equation}
-\prod_{c}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} = e^{\int_{c}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}. \nonumber
+\prod_{c}^{\dist} (1 - f_{occ}(\dist \ray))^{d\dist} = e^{\int_{c}^{\dist} \ln{(1 - f_{occ}(\dist \ray))}{d\dist}}. \nonumber
 \end{equation}
@@
 %
-\newcommand{\Ptransmission}{P_{\textit{transmission}}}%
 \begin{align}
-  \Ptransmission^j(\lambda) = \prod_i (1 - \cL_u (\bu; \bmu_i, \bGamma_i) \cL_{\lambda}(\lambda; \meandepth{i})),
+  \PtransR(\dist) = \prod_i (1 - \LogstIm (\impt; \tImMu_i, \tImS_i) \LogstD(\dist; \meandepth{i})),
 \label{eq:evalCumulativePtrans}
@@
 %
-where $\cL_u(.)$ is sigmoid in the image domain, with $\bmu_i$ and $\bGamma_i$ representing the elliptical projection of object $O_i$ in the image and $\cL_{\lambda}(.)$ is sigmoid in the depth domain, with $\meandepth{i}$ being the mean depth of object $O_i$.
+where $\LogstIm(.)$ is sigmoid in the image domain, with $\tImMu_i$ and $\tImS_i$ representing the elliptical projection of object $\Obj_i$ in the image and $\LogstD(.)$ is sigmoid in the depth domain, with $\meandepth{i}$ being the mean depth of object $\Obj_i$.
 That is,
@@
 \begin{align}
-\cL_u(\bu; \bmu_i, \bGamma_i) &= \frac{1}{1 + e^{-k_u(1 - (\bu - \bmu_i)^\top \bGamma_i^{-1} (\bu - \bmu_i))}}, \\
-  \cL_{\lambda}(\lambda; \meandepth{i}) &= \frac{1}{1 + e^{-k_d(\lambda - \meandepth{i})}}.
+\LogstIm(\impt; \tImMu_i, \tImS_i) &= \frac{1}{1 + e^{-k_u(1 - (\impt - \tImMu_i)^\top \tImS_i^{-1} (\impt - \tImMu_i))}}, \\
+  \LogstIm(\dist; \meandepth{i}) &= \frac{1}{1 + e^{-k_d(\dist - \meandepth{i})}}.
 \end{align}
@@
   \vspace{-0.3cm}
-  \caption{\small Comparisons between the approximate and exact formulations of $\Ptrans$.
+  \caption{Comparisons between the approximate and exact formulations of $\Ptrans$.
 The drop in the approximate version is delayed because we assume drop at the object center rather than the camera-facing face of the object.}
